### 2020-10-15 CMPSpaper_writing/CMPSpaper_writing.Rmd
added a structure

---
title: Capitalized Title Here
author:
  # see ?rjournal_article for more information
  - name: Author One
    affiliation: Affiliation
    address:
    - line 1
    - line 2
    url: https://journal.r-project.org
    orcid: 0000-0002-9079-593X
    email:  author1@work
  - name: Author Two
    url: https://journal.r-project.org
    email: author2@work
    orcid: 0000-0002-9079-593X
    affiliation: Affiliation 1
    address:
    - line 1 affiliation 1
    - line 2 affiliation 1
    affiliation2: Affiliation 2
    address2:
    - line 1 affiliation 2
    - line 2 affiliation 2
  - name: Author Three
    url: https://journal.r-project.org
    email: author3@work
    affiliation: Affiliation
    address:
    - line 1 affiliation
    - line 2 affiliation
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble

# per R journal requirement, the bib filename should be the same as the output 
# tex file. Don't forget to rename the bib file and change this example value.
bibliography: RJreferences.bib

output: rticles::rjournal_article
---

## Introduction

Introduce the CMPS method/algorithm

* make it clear that we implemented the algorithm, not created it
* discuss a little that our data preparation method is different from that in the NIST paper. Shiny?

## Implementation

How did we implement the algorithm

* how to present this? examples
* how detailed?

## Results

Present results:

* apply it to Hamby252 -> able to reproduce results in NIST paper qualitatively
* (?) apply it to Hamby44, using Hamby252 (default) parameters
* apply it to Hamby44, using parameters such that `lengths` represents the same actual length (the same amount of pixels of the scan)

## Conclusion

Conclusion and discussion

* (?) potential flaws of the implementation
* Suggestion of how to select parameters
* open source implementation:
  - allow everyone to use, introduce the algorithm to R community
  - in general, open source implementation could reduce the level of ambiguity

### About this format and the R Journal requirements

`rticles::rjournal_article` will help you build the correct files requirements:

* A R file will be generated automatically using `knitr::purl` - see
https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information.
* A tex file will be generated from this Rmd file and correctly included in
`RJwapper.tex` as expected to build `RJwrapper.pdf`.
* All figure files will be kept in the default rmarkdown `*_files` folder. This
happens because `keep_tex = TRUE` by default in `rticles::rjournal_article`
* Only the bib filename is to modifed. An example bib file is included in the
template (`RJreferences.bib`) and you will have to name your bib file as the
tex, R, and pdf files.

### 2020-10-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
updated the paper structure

@@
 
-Introduce the CMPS method/algorithm
+Address the problem: examiner - the two pattern evidence come from the same source or not
+
+criticism of subjective methodology (report, citation) - why we need algorithms
+
+Introduce our methodology - with 3D scans, digital microscope, data and algorithms
+
+hambyset as the dataset
+
+A short example to illustrate how one can use this CMPS package to obtain a comparison
+
+* 2 lands - the same source; 1 land from another; signatures; CMPS score;
+
+briefly talk about the CMPS method/algorithm, provide details in the Implementation section
 
 * make it clear that we implemented the algorithm, not created it
-* discuss a little that our data preparation method is different from that in the NIST paper. Shiny?
+
+outline what is going to come
 
@@
 
-How did we implement the algorithm
+discuss a little that our data preparation method is different from that in the NIST paper. Shiny?
 
-* how to present this? examples
-* how detailed?
+* [how do we get the signatures? ]
+
+description of the algorithm and how did we implement it?
+
+how would people use it?
 
@@
 * apply it to Hamby252 -> able to reproduce results in NIST paper qualitatively
-* (?) apply it to Hamby44, using Hamby252 (default) parameters
-* apply it to Hamby44, using parameters such that `lengths` represents the same actual length (the same amount of pixels of the scan)
+  - exclude some (?) scans because they are bad -> go further in Conclustion
+  - [CHECK] Did researchers exclude those scans in NIST paper?
+* apply it to another dataset, which have a different resolution
+  - potential issues -> go further in Conclusion
+  - need to use a different set of parameters
+* apply it to Hamby44, what did we do?
+  - using parameters such that `lengths` represents the same actual length (the same amount of pixels of the scan)
 
 ## Conclusion
+
+(Our opinions)
 
@@
 * (?) potential flaws of the implementation
+* potential issues related to the algorithm
+  - 6 as a cutoff?
+    - not crossvalidated
+    - estimate KM KNM distribution, etc...
+  - choose parameters
 * Suggestion of how to select parameters
+* what should we do about higher resolution data? what did we do? [CHECK: what did NIST paper do]
+* excluding outliers ? [check NIST paper]
 * open source implementation:

### 2020-12-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
draft 1: added [algorithm, implementation, example]

@@
 
-discuss a little that our data preparation method is different from that in the NIST paper. Shiny?
+[discuss a little that our data preparation method is different from that in the NIST paper. Shiny?]
 
@@
 
-description of the algorithm and how did we implement it?
+[description of the algorithm and how did we implement it?]
 
-how would people use it?
+**Algorithm.**
+
+The CMPS algorithm consists of X steps.
+
+step 1) cut the reference profile into consecutive, non-overlapping and equal-length basis segments;
+
+`get_segs(x, len=50)` implements the first step. It takes a profile in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
+
+step 2) compute the cross-correlation function between each basis segment and the comparison profile;
+
+`get_ccf4` computes the cross-correlation function / correlation coefficient curve between two profiles. This is the function called whenever we need to compute the ccf.
+
+step 3) if the multi segment lengths strategy is being used, each basis segment would increase its length and compute a new cross-correlation function with the comparison profile in order to identify a potential “consistent correlation peak”; if the multi segment lengths strategy is not being used, each segment would then find 5 peaks in its cross-correlation function;
+
+`get_seg_scale` takes a basis segment and increases its segment length. `scale=1` gives the original length of the basis segment. Increasing `scale` by 1 will double the segment length.
+
+`get_ccr_peaks` takes a segment and the comparison profile, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve.
+The number of peaks detected is equal to `npeaks`.
+And we are using `rollapply` to find peaks on the curve effectively.
+
+`get_ccp` checks if the "consistent correlation peak" exists under the framework of multi segment lengths strategy.
+Since we are requiring the highest segment scale identifies only one peak, we just need to check if this peak shows any "consistency".
+In other words, we check if this peak is also identified as a peak in other segment scale levels.
+
+4) determine the congruent registration position with a small tolerance zone and the number of basis segment that agrees with the congruent registration position (the CMPS score).
+
+`get_CMPS` considers all basis segments and their identified peaks to determine the congruent registration position.
+The goal is to find a peak position that is agreed by the most basis segments.
+Since small errors are allowed, a tolerance zone would serve as a selection window.
+`get_CMPS` will move this selection window from left to right and go through all possible positions, and check the number of basis segment that identifies a peak in the selection window for each position.
+Since we are moving this tolerance zone from left to right one unit a time, some consecutive positions are expected to have the same number of basis segments.
+[?.?]In that case the median of all tied and consecutive positions will be chosen as the congruent registration position.
+As long as the congruent registration position is determined, the number of basis segments that identify a peak in this position is the CMPS score.
+
+> [~? 0.078 mm or 50 pixels; 2mm in total? length is 2000? should we use 78 as the segment length? the same for 252 and 44?]
+
+Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified in step 3, and the length of the tolerance zone in step 4.
+In our implementation of the CMPS algorithm we took the original CMPS paper [cite?] as the reference to determine the default values of these parameters.
+
+The main function that follows the CMPS algorithm is called `extract_feature_cmps`. It consists of all steps of the algorithm and receives parameters from the users.
+
+* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in step 1; 
+* `npeaks.set` determines the number of peaks and whether the function uses the multi segment lengths strategy.
+If `npeaks.set` is a numeric vector of length 1, for example `npeaks.set = c(5)`, then the function will not use multi segment lengths and find 5 peaks in the correlation coefficient curve for each basis segment; on the other hand, if the vector length of `npeaks.set` is larger than 1, for example `npeaks.set = c(5, 3, 1)`, the function will take advantage of the multi segment lengths strategy, finding 5 peaks in the original scale, 3 peaks in the second scale and 1 peak in the third scale.
+Note that if the multi segment lengths strategy is being used, the last element of `npeaks.set` should always be 1.
+* `Tx` gives the size of tolerance zone mentioned in step 4;
+* `full_result` determines whether the function outputs a full result. A full result contains XX, while if `full_result = FALSE`, the function will only output the CMPS score of this comparison.
+
+[examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf]
+[https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf]
+
+> [~? should I present the code of the function? in order to explain it]
+
+[how would people use it?]
+
+**Install**
+
+The CMPS package is/not published on CRAN, and can be install and called by
+
+```{r, eval=FALSE}
+install.packages(CMPS)
+```
+
+The development version can be installed by using
+
+```{r, eval=FALSE}
+# install.packages("devtools") 
+devtools::install_github("willju-wangqian/CMPS")
+```
+
+**Examples**
+
+The `CMPS` package contains a simple example to illustrate the basic usage of the package.
+The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [cite?] (Each bullet has six lands).
+The procedure for generating signatures from 3D bullet lands in x3p format is (algorithmic) [and has been discussed above].
+And these two bullets are known to come from the same gun barrel, so for the 36 land-by-land comparisons, 6 of them are KM (known matching) comparisons and 30 are KNM (known non-matching) comparisons.
+To access the example data, one can use
+
+```{r}
+library(CMPS)
+data(bullets)
+```
+
+And anyone who is interested in the data source can find it in `bullets$source`.
+One can use these links to download the original x3p files from [NIST, cite?].
+`bulletxtrctr::read_bullet(urllist = bullets$source)`
+
+**extract_feature_cmps**
+
+`extract_feature_cmps` integrates all steps of the CMPS algorithm. It takes two bullet profiles and computes the CMPS score.
+
+```{r, eval=FALSE}
+extract_feature_cmps(
+  x,
+  y,
+  seg_length = 50,
+  seg_scale_max = 3,
+  Tx = 25,
+  npeaks.set = c(5, 3, 1),
+  full_result = FALSE
+)
+```
+
+The comparison between "bullet 1 - land 2" and "bullet 2 - land 3" is one of the KM comparisons. We can compute the CMPS score using two versions of the CMPS algorithm.
+
+```{r, eval=FALSE}
+land2_3 <- bullets$sigs[bullets$bulletland == "2-3"][[1]]
+land1_2 <- bullets$sigs[bullets$bulletland == "1-2"][[1]]
+
+# compute cmps
+
+# algorithm with multi-peak insepction at three different segment scales
+cmps_with_multi_scale <- extract_feature_cmps(land2_3$sig, land1_2$sig, 
+                                              npeaks.set = c(5,3,1), full_result = TRUE)
+
+# algorithm with multi-peak inspection at the basis scale only
+cmps_without_multi_scale <- extract_feature_cmps(land2_3$sig, land1_2$sig, 
+                                                 npeaks.set = 5, full_result = TRUE)
+```
+
+We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.
 
@@
   - exclude some (?) scans because they are bad -> go further in Conclustion
-  - [CHECK] Did researchers exclude those scans in NIST paper?
+  - [CHECK] Did researchers exclude those scans in NIST paper? First scan, NO
 * apply it to another dataset, which have a different resolution

### 2021-01-21 CMPSpaper_writing/CMPSpaper_writing.Rmd
added "analysis"

@@
 Since small errors are allowed, a tolerance zone would serve as a selection window.
-`get_CMPS` will move this selection window from left to right and go through all possible positions, and check the number of basis segment that identifies a peak in the selection window for each position.
+`get_CMPS` will move this selection window from left to right and go through all possible positions and check the number of basis segment that identifies a peak in the selection window for each position.
 Since we are moving this tolerance zone from left to right one unit a time, some consecutive positions are expected to have the same number of basis segments.
@@
 
-> [~? 0.078 mm or 50 pixels; 2mm in total? length is 2000? should we use 78 as the segment length? the same for 252 and 44?]
-
 Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified in step 3, and the length of the tolerance zone in step 4.
 In our implementation of the CMPS algorithm we took the original CMPS paper [cite?] as the reference to determine the default values of these parameters.
-
 The main function that follows the CMPS algorithm is called `extract_feature_cmps`. It consists of all steps of the algorithm and receives parameters from the users.
@@
 * `Tx` gives the size of tolerance zone mentioned in step 4;
-* `full_result` determines whether the function outputs a full result. A full result contains XX, while if `full_result = FALSE`, the function will only output the CMPS score of this comparison.
+* `include` determines what information should be included in the function output.
+By default, `include = NULL` and the function output will only contain the `CMPS.score`.
+However, besides the most important `CMPS.score`, there are other pieces of information related to the CMPS score that one might be interested in, such as
+  - `nseg`: the number of basis segments we get from the reference profile; this is also the highest possible CMPS score of the comparison;
+  - `congruent.pos`: the congruent registration position;
+  - `congruent.seg.idx`: the indices of all basis segments that agree with the congruent registration position;
+  - `segments`: the list of basis segments used for the computation of CMPS score;
+  - `parameters`: all inputs of `extract_feature_cmps`
+For all possible options of `include`, please check the documentation of `extract_feature_cmps` or using `?extract_feature_cmps`.
+If we want everything to be included in the output, we can use `include = full_result`.
+These additional pieces of information are helpful in terms of understanding how we obtained such CMPS score.
 
@@
 [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf]
-
-> [~? should I present the code of the function? in order to explain it]
-
-[how would people use it?]
 
@@
   seg_length = 50,
-  seg_scale_max = 3,
   Tx = 25,
   npeaks.set = c(5, 3, 1),
-  full_result = FALSE
+  include = NULL
 )
@@
 ```{r, eval=FALSE}
-land2_3 <- bullets$sigs[bullets$bulletland == "2-3"][[1]]
-land1_2 <- bullets$sigs[bullets$bulletland == "1-2"][[1]]
+land2_3 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
+land1_2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]
 
@@
 cmps_with_multi_scale <- extract_feature_cmps(land2_3$sig, land1_2$sig, 
-                                              npeaks.set = c(5,3,1), full_result = TRUE)
+                                              npeaks.set = c(5,3,1), include = "full_result")
 
@@
 cmps_without_multi_scale <- extract_feature_cmps(land2_3$sig, land1_2$sig, 
-                                                 npeaks.set = 5, full_result = TRUE)
+                                                 npeaks.set = 5, include = "full_result")
 ```
 
-We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.
+We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons. (TOBE UPDATED !!!)
+
+```{r}
+#      [,1] [,2] [,3] [,4] [,5] [,6]
+# [1,]    2    5    3    4    3    2
+# [2,]    2    2   13    1    1    1
+# [3,]    1    1    2   11    2    2
+# [4,]    2    1    1    1   10    1
+# [5,]    1    2    1    2    2   15
+# [6,]   14    2    2    2    1    1
+```
+
+**Analysis**
+
+We also implemented graphing tools for analyzing results of the CMPS algorithm.
+The goal is to help users visualize the results, inspect each basis segments and have a better understanding of how the algorithm works.
+We can continue with the example above.
+
+```{r, eval=FALSE}
+source("../../Bullet_Rcode/cmps_plot.R")
+
+sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
+
+```
+
+`cmps_signature_plot` takes the "full result" of `extract_feature_cmps` (setting `include = "full_result"`) and returns a list of 5 elements.
+
+The first element is `segment_shift_plot`.
+On this plot only basis segments that agree with the congruent registration position (the congruent matching profile segments) are plotted along with the comparison profile.
+When plotting, each of those basis segment will be shifted to the position where the basis segment obtains a cross-correlation peak and is within the tolerance zone of the congruent registration position.
+
+```{r, eval=FALSE}
+sig.plot$segment_shift_plot
+```
+
+```{r}
+knitr::include_graphics("img/sigplot1.png", dpi = 100)
+```
+
+The second element is called `signature_shift_plot`.
+On this visual both the reference profile and the comparison profile are plotted.
+The reference profile is aligned with the comparison profile based on the congruent registration position.
+And the congruent matching profile segments are highlighted.
+
+```{r, eval=FALSE}
+sig.plot$signature_shift_plot
+```
+
+```{r}
+knitr::include_graphics("img/sigplot2.png", dpi = 100)
+```
+
+Other elements of this list are `seg_shift`, `sig_shift`, and `seg.pos`.
+These elements are essentially used for generating visuals above but also provide insights about the best fitted position for each congruent matching profile segment and for the reference profile.
+`sig.plot$seg.pos` can also tell us which basis segments are the congruent matching profile segments.
+
+As `cmps_signature_plot` focuses on the signature level, on the other hand, `cmps_segment_plot` focuses on the segment level.
+It not only takes the "full result" of `extract_feature_cmps`, but also takes an argument `seg.idx`, which indicates which segment to be inspected.
+For example, after checking `sig.plot$seg.pos` we noticed that segment 6 is not one of the congruent matching profile segments.
+So we can set `seg.idx = 6` in order to have a closer look at segment 6 and why it disagrees with the congruent registration position.
+`cmps_signature_plot` also returns a list.
+Each element of this list is also a list and corresponds to one segment scale of this basis segment.
+
+```{r, eval=FALSE}
+seg.plot <- cmps_segment_plot(cmps_with_multi_scale, seg.idx = 6)
+```
+
+Take the first element of `seg.plot` as an example, it corresponds to the first segment scale (the original scale) of the 6th basis segment and carries two plots, `segment_plot` and `scale_ccf_plot`.
+
+Remember that when computing the CMPS score, we were using `npeaks.set = c(5, 3, 1)`.
+This means that for the first segment scale, 5 peaks are identified in the cross-correlation curve.
+`segment_plot` plots the 6th basis segment in its first scale at its original position as well as the positions where the basis segment obtains its 5 cross-correlation peaks.
+
+```{r, eval=FALSE}
+seg.plot[[1]]$segment_plot
+```
+
+And the `scale_ccf_plot` plots the cross-correlation curve. We can see that 5 highest peaks are identified and marked on the plot.
+
+```{r, eval=FALSE}
+seg.plot[[1]]$scale_ccf_plot
+```
+
+Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segment.
+
+```{r, eval=FALSE}
+library(ggpubr)
+
+ggarrange(plotlist = unlist(seg.plot, recursive = FALSE),
+          ncol = 2, nrow = 3)
+```
+
+The red vertical dashed line indicates the congruent registration position.
+We can see segment 6 does obtain peaks at scale two and scale three; however, this position doesn't give one of the five highest peaks at scale one.
+As a result, segment 6 fails to identify the ccp (consistent correlation peak) and fails to become one of the congruent matching profile segments (according to the multi segment lengths strategy).
 

### 2021-01-28 CMPSpaper_writing/CMPSpaper_writing.Rmd
added new plots and finished result section

@@
 
+## Background
+
+The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [cite?].
+For each dataset in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels.
+20 of the 35 bullets are known test bullets and 15 of them are unknown bullets.
+Each bullet has six land engraved areas (LEA) whose 3D topographical images were obtained using a NanoFocus lens at 20x magnification and stored in x3p format (XML 3-D Surface Profile).
+
++ hamby
++ x3p
++ bulletxtrctr (crosscut, grooves, ccdata, signature)
++ an shiny app that helps us get better crosscuts and groove locations
++ 1.5625, 1.29
+[how do we get the signatures? ]
+[Note that in the NIST CMPS paper they have another way of getting bullet signatures]
+
 ## Implementation
-
-[discuss a little that our data preparation method is different from that in the NIST paper. Shiny?]
-
-* [how do we get the signatures? ]
-
-[description of the algorithm and how did we implement it?]
 
@@
 
-step 2) compute the cross-correlation function between each basis segment and the comparison profile;
+step 2) each basis segment finds its best registration position on the comparison profile.
+A cross-correlation curve between a basis segment and the comparison profile would be computed, and a registration position is considered as "good" if the basis segment achieves a high cross-correlation value at this position.
+
+Then how should a basis segment find its best registration position?
+[In the original paper] researchers proposed two versions of the CMPS alrorithm that can answer this question.
+The first version is called "multi-peak inspection", and the second version is called "multi-peak inspection at different segment lengths/scales".
+We also refer the second version as the CMPS algorithm using "the multi segment lengths strategy".
+
+Step 2.1) multi-peak inspection: each basis segment identifies positions of 5 (or multiple) highest peaks in the cross-correlation curve.
+Since false positive peaks would stand out when the segment length is short, positions of all 5 peak will be considered as the potential "best" registration position.
+
+Step 2.2) multi segment lengths strategy: for this version of the CMPS algorithm, each basis segment finds only one "best" registration position.
+This "best" registration position can be found by conducting multi-peak inspection multiple rounds.
+The first round is the standard way as we have stated in step 2.1.
+But after the first round, we will increase the segment length, compute a new cross-correlation curve, and again identify multiple peaks in the cross-correlation curve.
+The number of peaks identified in this round is typically less than that in the previous round (say 3 highest peaks) since increasing the segment length can reduce the number of false positive peaks.
+We can repeat this procedure multiple times; however in the last round, only one highest peak should be identified.
+If a position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
+
+<!-- we conduct the "multi-peak inspection at different segment lengths".
+After having the multi-peak inspection for a basis segment of its original length, we then double the segment length by including profiles of half the current length -->
+
+<!-- If the reference profile and the comparison profile matches perfectly, every basis segment should vote for exactly the same registration position.  -->
+
+<!-- compute the cross-correlation function between each basis segment and the comparison profile; -->
 
@@
 
-step 3) if the multi segment lengths strategy is being used, each basis segment would increase its length and compute a new cross-correlation function with the comparison profile in order to identify a potential “consistent correlation peak”; if the multi segment lengths strategy is not being used, each segment would then find 5 peaks in its cross-correlation function;
+<!-- step 3) if the multi segment lengths strategy is being used, each basis segment would increase its length and compute a new cross-correlation function with the comparison profile in order to identify a potential “consistent correlation peak”; if the multi segment lengths strategy is not being used, each segment would then find 5 peaks in its cross-correlation function; -->
 
@@
 Since we are requiring the highest segment scale identifies only one peak, we just need to check if this peak shows any "consistency".
-In other words, we check if this peak is also identified as a peak in other segment scale levels.
+In other words, we check if this peak is also identified as a peak in other segment scales.
 
-4) determine the congruent registration position with a small tolerance zone and the number of basis segment that agrees with the congruent registration position (the CMPS score).
+step 3) determine the congruent registration position with a small tolerance zone and the number of basis segments that take the congruent registration position as their "best" registration position.
+These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of this profile comparison.
 
-`get_CMPS` considers all basis segments and their identified peaks to determine the congruent registration position.
+`get_CMPS` considers all basis segments and their identified peak positions to determine the congruent registration position.
 The goal is to find a peak position that is agreed by the most basis segments.
@@
 
-Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified in step 3, and the length of the tolerance zone in step 4.
+Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified in step 3, and the length of the tolerance zone in step 3.
 In our implementation of the CMPS algorithm we took the original CMPS paper [cite?] as the reference to determine the default values of these parameters.
@@
 
-**Analysis**
+**Visualize and Understand CMPS results**
 
-We also implemented graphing tools for analyzing results of the CMPS algorithm.
-The goal is to help users visualize the results, inspect each basis segments and have a better understanding of how the algorithm works.
-We can continue with the example above.
+We also implemented graphing tools for visualizing results of the CMPS algorithm.
+The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
+Let's continue with the example above and take its results.
 
 ```{r, eval=FALSE}
-source("../../Bullet_Rcode/cmps_plot.R")
-
 sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
-
 ```
@@
 The first element is `segment_shift_plot`.
-On this plot only basis segments that agree with the congruent registration position (the congruent matching profile segments) are plotted along with the comparison profile.
-When plotting, each of those basis segment will be shifted to the position where the basis segment obtains a cross-correlation peak and is within the tolerance zone of the congruent registration position.
+On this plot only basis segments that agree with the congruent registration position (i.e.
+the segments that are congruent matching profile segments) are plotted along with the comparison profile.
+When plotting, each of those basis segments will be shifted to the position where the basis segment obtains a cross-correlation peak and is within the tolerance zone of the congruent registration position.
 
@@
 
-```{r}
+```{r, echo=FALSE, out.width="300px"}
 knitr::include_graphics("img/sigplot1.png", dpi = 100)
@@
 
-```{r}
+```{r, echo=FALSE, out.width="300px"}
 knitr::include_graphics("img/sigplot2.png", dpi = 100)
@@
 
+```{r, echo=FALSE, out.width="300px"}
+knitr::include_graphics("img/segplot1.png", dpi = 100)
+```
+
 And the `scale_ccf_plot` plots the cross-correlation curve. We can see that 5 highest peaks are identified and marked on the plot.
@@
 seg.plot[[1]]$scale_ccf_plot
+```
+
+```{r, echo=FALSE, out.width="300px"}
+knitr::include_graphics("img/segplot2.png", dpi = 100)
 ```
@@
 
+```{r, echo=FALSE, out.width="400px"}
+knitr::include_graphics("img/segplot3.png", dpi = 100)
+```
+
 The red vertical dashed line indicates the congruent registration position.
-We can see segment 6 does obtain peaks at scale two and scale three; however, this position doesn't give one of the five highest peaks at scale one.
-As a result, segment 6 fails to identify the ccp (consistent correlation peak) and fails to become one of the congruent matching profile segments (according to the multi segment lengths strategy).
+We can see that the segment 6 does obtain a peak near to the congruent registration position at scale two and scale three, respectively; however, this position doesn't give one of the five highest peaks at scale one.
+As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi segment lengths strategy.
 
@@
 
-Present results:
+**Metrics Based on CMPS scores**
+
+```{r, eval=FALSE, echo=FALSE}
+hamby252_results <- readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252_results.rds")
+hamby44_results <- readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44_results.rds")
+```
+
+In (NIST's original paper) that presents the CMPS algorithm researchers applied the CMPS method to one of the Hamby set scans (Hamby 252).
+In order to show that our implementation of the CMPS algorithm is able to reproduce the results in (original paper) and is able to be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
+However, since NIST's work is not open-source, we were only able to reproduce the results for Hamby set 252 qualitatively.
+
+The CMPS score can be considered as a similarity score of two profiles.
+Then how can we get a similarity score of two bullets based on CMPS scores?
+In (the original paper) researchers introduced two similarity metrics at the bullet level: $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
+For bullets in Hamby study each bullet has 6 land engraved areas (LEA) profiles.
+In order to compare two bullets there are in total 6 $\times$ 6 LEA profile comparisons and each profile comparison would produce a CMPS score.
+$\mathrm{CMPS_{max}}$ is the highest CMPS score among all profile comparisons.
+And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible average CMPS score of profile comparisons that are in the same phase.
+
+Here are the CMPS scores of all 36 profile comparisons of the bullets in the example above.
+
+[an example that explains cmps.max and cmps.maxbar]
+
+In this example, the $\mathrm{CMPS_{max}}=?$ and $\mathrm{\overline{CMPS}_{max}}=()/6=$.
+
+**Hamby 252**
+
+Figure x shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
+Although the CMPS scores we found here are not exactly the same as those presented in the [original paper] since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising.
+For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM).
+Table x shows some summary statistics.
+
+The parameters we used in `extract_feature_cmps` are:
+
+```{r, eval=FALSE}
+extract_feature_cmps(
+  x, y,
+  seg_length = 50,
+  Tx = 25,
+  npeaks.set = c(5,3,1),
+  include = "nseg"
+)
+```
+
+Note that for Hamby set 44, one unit represents 1.5625 \textmu m so setting `seg_length = 50` makes each basis segment have length 78.125 \textmu m.
+And `Tx = 25` makes the tolerance zone be $\pm 39.0625$ \textmu m.
+This is to mimic the parameters used in the [original paper].
+
+```{r, echo=FALSE, out.width="400px"}
+# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
+knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
+```
+
+[table ???]
+
+Figure x shows the results for Hamby set 44.
+Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged.
+Table x shows some summary statistics for Hamby set 44.
+
+For Hamby set 44, the parameters we used in `extract_feature_cmps` are:
+
+```{r, eval=FALSE}
+extract_feature_cmps(
+  x, y,
+  seg_length = 61, 
+  Tx = 30,
+  npeaks.set = c(5,3,1),
+  include = "nseg"
+)
+```
+
+Note that we used different values here for `seg_length` and `Tx` because our Hamby set 44 scans have a different scanning resolution.
+One unit here represents 1.29 \textmu m.
+So here each basis segment has length 78.69 \textmu m, and the tolerance zone is $\pm 38.7$ \textmu m.
+
+```{r, echo=FALSE, out.width="400px"}
+# [1] "span1=0.25, span2=0.03, rm_outliers"
+knitr::include_graphics("img/hamby44_v1.png", dpi = 100)
+```
+
+Figure x shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`.
+We can see that the separation between KM comparisons and KNM comparisons is increased.
+This shows that the parameters used in the CMPS algorithm can affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
+
+```{r, echo=FALSE, out.width="400px"}
+# [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
+knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
+```
+
+For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures/profiles; however, in this example we used `span1=0.75` and changed the characteristic of those profiles.
+As we can see in figure x, this change also affects the CMPS results.
+
+```{r, echo=FALSE, out.width="400px"}
+# [4] "span1=0.75, span2=0.03, rm_outliers"  
+knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
+```
+
+[The codes generating those results can be found in the appendix. ???]
+
+<!-- Present results: -->
 
@@
   - exclude some (?) scans because they are bad -> go further in Conclustion
-  - [CHECK] Did researchers exclude those scans in NIST paper? First scan, NO
-* apply it to another dataset, which have a different resolution
-  - potential issues -> go further in Conclusion
-  - need to use a different set of parameters
-* apply it to Hamby44, what did we do?
-  - using parameters such that `lengths` represents the same actual length (the same amount of pixels of the scan)
+  - [CHECK] Did researchers exclude those scans in NIST paper? Yes, they removed outliers
+<!-- * apply it to another dataset, which have a different resolution -->
+<!--   - potential issues -> go further in Conclusion -->
+<!--   - need to use a different set of parameters -->
 

### 2021-01-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
added section "background"

@@
 
-Address the problem: examiner - the two pattern evidence come from the same source or not
+The main task of firearm examination is to determine whether two bullets were fired from the same gun barrel or not.
+It has been playing an important role in terms of convictions in the United States criminal justice system.
+However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.
+A report published by the National Academy of Sciences in 2009 states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." This is why we need to develop frameworks and algorithms that can bring an objective and quantitative assessment into the field.
 
-criticism of subjective methodology (report, citation) - why we need algorithms
+The congruent matching profile segment (CMPS) method is one of those algorithms developed by NIST [cite?].
+It is ...
+[briefly talk about the CMPS method / algorithm, provide details in the Implementation section]
+
+However, no open-source implementation.
+
+In this paper, we present an open-source implementation of the CMPS algorithm.
 
 Introduce our methodology - with 3D scans, digital microscope, data and algorithms
-
-hambyset as the dataset
 
@@
 
-briefly talk about the CMPS method/algorithm, provide details in the Implementation section
-
-* make it clear that we implemented the algorithm, not created it
-
 outline what is going to come
@@
 
-The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [cite?].
-For each dataset in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels.
+The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [cite?], and in particular, they are Hamby set 252 and Hamby set 44.
+For each Hamby set in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels.
 20 of the 35 bullets are known test bullets and 15 of them are unknown bullets.
-Each bullet has six land engraved areas (LEA) whose 3D topographical images were obtained using a NanoFocus lens at 20x magnification and stored in x3p format (XML 3-D Surface Profile).
+Each bullet has six land engraved areas (LEA) or land impressions, whose 3D topographical images were obtained and stored in the x3p format (XML 3-D Surface Profile).
+The x3p format provides a standard way of exchanging 2D and 3D profile data.
+It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/] and was adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
+Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
+Hamby set 44 were scanned ...[at CSAFE?]...
+Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project.
 
-+ hamby
-+ x3p
-+ bulletxtrctr (crosscut, grooves, ccdata, signature)
-+ an shiny app that helps us get better crosscuts and groove locations
-+ 1.5625, 1.29
-[how do we get the signatures? ]
+The congruent matching profile segment (CMPS) method is used for "objective comparison of striated tool marks" [original paper], and in our cases it is used for bullet signatures.
+In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` package `x3ptools`[cite?] and `bulletxtrctr`[cite?] with an automated framework proposed in [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS].
+`x3ptools` can be used to process x3p files.
+In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).
+Figure x.a shows a bullet land impression scan of a processed x3p file.
+The raised portion of the surface are groove impressions, and the vertical striation marks between the groove impressions are what we are interested in, called a land impression.
+The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression.
+`bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
+Figure x shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.
+`bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept.
+With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [Cleveland 1979?] and can obtain the bullet signature.
+Figure x illustrates this framework.
+Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
+
 [Note that in the NIST CMPS paper they have another way of getting bullet signatures]

### 2021-02-02 CMPSpaper_writing/CMPSpaper_writing.Rmd
combined intro and background

@@
 The main task of firearm examination is to determine whether two bullets were fired from the same gun barrel or not.
-It has been playing an important role in terms of convictions in the United States criminal justice system.
+It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired.
+Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land impressions, and the areas the marks occupy are called land engraved areas (LEA).
+Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.
 However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.
-A report published by the National Academy of Sciences in 2009 states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." This is why we need to develop frameworks and algorithms that can bring an objective and quantitative assessment into the field.
-
-The congruent matching profile segment (CMPS) method is one of those algorithms developed by NIST [cite?].
-It is ...
-[briefly talk about the CMPS method / algorithm, provide details in the Implementation section]
-
-However, no open-source implementation.
-
-In this paper, we present an open-source implementation of the CMPS algorithm.
-
-Introduce our methodology - with 3D scans, digital microscope, data and algorithms
-
-A short example to illustrate how one can use this CMPS package to obtain a comparison
-
-* 2 lands - the same source; 1 land from another; signatures; CMPS score;
-
-outline what is going to come
-
-## Background
+A report published by the National Academy of Sciences in 2009 states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those critics and concerns, people have been making an effort to build databases and develop frameworks and algorithms that can bring an objective and quantitative assessment into the field.
+The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.
 
@@
 
-The congruent matching profile segment (CMPS) method is used for "objective comparison of striated tool marks" [original paper], and in our cases it is used for bullet signatures.
-In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` package `x3ptools`[cite?] and `bulletxtrctr`[cite?] with an automated framework proposed in [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS].
+The automated framework we used in this paper was proposed by Hare and Hofmann in 2017 [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS?].
+In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` packages `x3ptools`[cite?] and `bulletxtrctr`[cite?].
 `x3ptools` can be used to process x3p files.
@@
 Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
+Note that NIST researchers used a different way of getting the bullet signatures in their paper [cite?].
 
-[Note that in the NIST CMPS paper they have another way of getting bullet signatures]
+Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score.
+The congruent matching profile segment (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [original paper] in 2019, is one such algorithm.
+The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values.
+Then the congruent registration position is the position where the most basis segments find it the "best", and the number of basis segments taking the congruent registration position is the CMPS score.
+The CMPS algorithm can assist firearm examiners with drawing a conclusion, but NIST's implementation of the CMPS algorithm was not released for the public.
+Thus, in this paper we present an open-source implementation of the CMPS algorithm so that everyone can use and improve it.
+With our implementation, one can compute the CMPS score of a comparison using the following code:
+
+```{r, eval=FALSE}
+cmps.result <- extract_feature_cmps(sig1, sig2)
+```
+
+In the example in section "Implementation" we would see that, two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
+We also implemented graphing tools for users to better understand these results as well as the algorithm itself.
+
+The section "Implementation" will go through the algorithm and show how to use the "CMPS" package.
+An example that illustrates the main points are also included.
+The section "Results" presents the results of evaluating the CMPS package using Hamby set 252 and Hamby set 44.
+And the last section covers some final discussion and conclusions.
 
@@
 
-```{r}
+```{r, eval=FALSE}
 library(CMPS)

### 2021-02-04 CMPSpaper_writing/CMPSpaper_writing.Rmd
updated intro, added conclusion

@@
 Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score.
-The congruent matching profile segment (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [original paper] in 2019, is one such algorithm.
+The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [original paper] in 2019, is one such algorithm.
 The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values.
@@
 Other elements of this list are `seg_shift`, `sig_shift`, and `seg.pos`.
-These elements are essentially used for generating visuals above but also provide insights about the best fitted position for each congruent matching profile segment and for the reference profile.
+These elements are essentially used for generating visuals above but also provide insights about the best fitted position for each congruent matching profile segments and for the reference profile.
 `sig.plot$seg.pos` can also tell us which basis segments are the congruent matching profile segments.
@@
 
-Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segment.
+Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segments.
 
@@
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in (original paper) and is able to be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-However, since NIST's work is not open-source, we were only able to reproduce the results for Hamby set 252 qualitatively.
+Since the CMPS algorithm works with, in our case, bullet signatures, we conducted some data-processing.
+For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann using the same set of parameters for both data sets, removed outliers, and obtained bullet signatures for each bullet land impression.
+Note that [in NIST's paper] they used a different framework to obtain bullet signatures.
+However, since NIST's work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
 
@@
 Then how can we get a similarity score of two bullets based on CMPS scores?
-In (the original paper) researchers introduced two similarity metrics at the bullet level: $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-For bullets in Hamby study each bullet has 6 land engraved areas (LEA) profiles.
-In order to compare two bullets there are in total 6 $\times$ 6 LEA profile comparisons and each profile comparison would produce a CMPS score.
+In (the original paper) researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet comparisons based on CMPS scores of bullet signature comparisons.
+For example, there are in total 6 $\times$ 6 LEA profile comparisons in order to compare two bullets in Hamby study since each bullet has 6 LEA profiles.
+And a CMPS score will be found for every profile comparison.
 $\mathrm{CMPS_{max}}$ is the highest CMPS score among all profile comparisons.
@@
 
-Conclusion and discussion
+We presented the CMPS package, an open-source implementation of the congruent matching profile segments (CMPS) algorithm.
+The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
+In this paper, functions included in the package were illustrated along with the basic logic of the CMPS algorithm.
+And we used a small dataset included in the package as an example to explain the usage of the package.
+Some graphing tools were also implemented in the package so that users can visualize results and have a better understanding of both the algorithm and the results.
+We also applied the algorithm to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising.
 
-* (?) potential flaws of the implementation
-* potential issues related to the algorithm
-  - 6 as a cutoff?
-    - not crossvalidated
-    - estimate KM KNM distribution, etc...
-  - choose parameters
-* Suggestion of how to select parameters
-* what should we do about higher resolution data? what did we do? [CHECK: what did NIST paper do]
-* excluding outliers ? [check NIST paper]
-* open source implementation:
-  - allow everyone to use, introduce the algorithm to R community
-  - in general, open source implementation could reduce the level of ambiguity
+From the results of both Hamby set 252 and 44, we can see that the CMPS scores of KM comparisons computed by `extract_feature_cmps` were able to be separated from those of KNM comparisons.
+And at the same time, we can see that CMPS algorithm is sensitive to the choice of parameters such as segment length, number of peaks detected at each segment scale, and congruency tolerance.
+Some parameter choices are better in the sense that they can enlarge the separation between the KM comparisons and the KNM comparisons.
+And the best set of parameters depend on the dataset being used, and the choice of parameters has not been, but should be, cross-validated.
+
+Our open-source implementation introduces the CMPS algorithm to R community and allows everyone to use it for their own projects.
+It would also facilitate future studies on parameter cross-validation and the development of statistical methods to modeling KM and KNM CMPS score distributions.
 

### 2021-02-06 CMPSpaper_writing/CMPSpaper_writing.Rmd
added a figure and numbers in the example

@@
 In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).
-Figure x.a shows a bullet land impression scan of a processed x3p file.
+Figure 1(a) shows a bullet land impression scan of a processed x3p file.
 The raised portion of the surface are groove impressions, and the vertical striation marks between the groove impressions are what we are interested in, called a land impression.
@@
 `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
-Figure x shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.
+Figure 1(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.
 `bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept.
-With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [Cleveland 1979?] and can obtain the bullet signature.
-Figure x illustrates this framework.
+With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [Cleveland 1979?] and obtain the bullet signature.
+Figure 1 illustrates this framework.
 Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
 Note that NIST researchers used a different way of getting the bullet signatures in their paper [cite?].
+
+figure 1:
+
+```{r, echo=FALSE, out.width="400px"}
+knitr::include_graphics("img/figure1.png", dpi = 100)
+```
 
@@
 
-We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons. (TOBE UPDATED !!!)
+We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.
 
@@
 #      [,1] [,2] [,3] [,4] [,5] [,6]
-# [1,]    2    5    3    4    3    2
-# [2,]    2    2   13    1    1    1
-# [3,]    1    1    2   11    2    2
+# [1,]    2    3    2    3    1    2
+# [2,]    2    1   17    1    2    3
+# [3,]    1    1    3   14    2    2
 # [4,]    2    1    1    1   10    1
-# [5,]    1    2    1    2    2   15
-# [6,]   14    2    2    2    1    1
+# [5,]    2    2    1    1    1   15
+# [6,]   16    3    1    2    1    1
 ```
@@
 
-[an example that explains cmps.max and cmps.maxbar]
+```{r}
+#      [,1] [,2] [,3] [,4] [,5] [,6]
+# [1,]    2    3    2    3    1    2
+# [2,]    2    1   17    1    2    3
+# [3,]    1    1    3   14    2    2
+# [4,]    2    1    1    1   10    1
+# [5,]    2    2    1    1    1   15
+# [6,]   16    3    1    2    1    1
+```
 
-In this example, the $\mathrm{CMPS_{max}}=?$ and $\mathrm{\overline{CMPS}_{max}}=()/6=$.
+In this example, the $\mathrm{CMPS_{max}}=17$ and $\mathrm{\overline{CMPS}_{max}}=(16+3+17+14+10+15)/6=12.5$.
 
@@
 
-Figure x shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
+Figure 2 shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
 Although the CMPS scores we found here are not exactly the same as those presented in the [original paper] since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising.
@@
 
+<!-- this is figure 2 -->
 ```{r, echo=FALSE, out.width="400px"}
@@
 
-[table ???]
+table 1:
 
-Figure x shows the results for Hamby set 44.
+<!-- |Parameters             | $\mathrm{CMPS_{max}}$ - KNM's max| $\mathrm{CMPS_{max}}$ - KM's min| $\mathrm{\overline{CMPS}_{max}}$ - KNM's max| $\mathrm{\overline{CMPS}_{max}}$ - KM's min| -->
+<!-- |:----------------------|---------------------------------:|--------------------------------:|--------------------------------------------:|-------------------------------------------:| -->
+<!-- |span1=0.25, (5, 3, 1)  |                                 7|                               10|                                       3.6000|                                      6.6667| -->
+<!-- |span1=0.25, (10, 6, 1) |                                 9|                               13|                                       4.8333|                                      9.1667| -->
+<!-- |span1=0.75, (5, 3, 1)  |                                 6|                               11|                                       3.1667|                                      6.6000| -->
+
+```{r, echo=FALSE}
+# library(knitr)
+# library(kableExtra)
+# rtt <- readRDS("summary_table.rds")
+# colnames(rtt) <- 
+rtt <- data.frame(parameters = c("span1=0.25, (5, 3, 1)", "span1=0.25, (10, 6, 1)", "span1=0.75, (5, 3, 1)"),
+                  p1 = c(7,9,6),
+                  p2 = c(10, 13, 11),
+                  p3 = c(3.6, 4.833, 3.167),
+                  p4 = c(6.667, 9.167, 6.6))
+
+knitr::kable(rtt, 
+             row.names = FALSE, digits = 4,
+             col.names = c("Parameters",
+                           "$\\mathrm{CMPS_{max}}$ - KNM's max",
+                           "$\\mathrm{CMPS_{max}}$ - KM's min",
+                           "$\\mathrm{\\overline{CMPS}_{max}}$ - KNM's max",
+                           "$\\mathrm{\\overline{CMPS}_{max}}$ - KM's min")) 
+```
+
+Figure 3 shows the results for Hamby set 44.
 Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged.
-Table x shows some summary statistics for Hamby set 44.
+Table 1 shows some summary statistics for Hamby set 44.
 
@@
 
+<!-- this is figure 3 -->
+
 ```{r, echo=FALSE, out.width="400px"}
@@
 
-Figure x shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`.
+Figure 4 shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`.
 We can see that the separation between KM comparisons and KNM comparisons is increased.
 This shows that the parameters used in the CMPS algorithm can affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
+
+<!-- this is figure 4 -->
 
@@
 For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures/profiles; however, in this example we used `span1=0.75` and changed the characteristic of those profiles.
-As we can see in figure x, this change also affects the CMPS results.
+As we can see in figure 5, this change also affects the CMPS results.
+
+<!-- this is figure 5 -->
 
@@
 
-<!-- Present results: -->
-
-* apply it to Hamby252 -> able to reproduce results in NIST paper qualitatively
-  - exclude some (?) scans because they are bad -> go further in Conclustion
-  - [CHECK] Did researchers exclude those scans in NIST paper? Yes, they removed outliers
-<!-- * apply it to another dataset, which have a different resolution -->
-<!--   - potential issues -> go further in Conclusion -->
-<!--   - need to use a different set of parameters -->
-
 ## Conclusion
-
-(Our opinions)
 

### 2021-02-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

@@
 title: Capitalized Title Here
+header-includes:
+  - \usepackage{xcolor}
 author:
@@
 
+```{=tex}
+\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
+\newcommand{\wj}[1]{{\textcolor{forestgreen}{#1}}}
+\setlength{\parindent}{0pt}
+```
+
 ## Introduction
 
-The main task of firearm examination is to determine whether two bullets were fired from the same gun barrel or not.
+\hh{Will, it might be better to put the focus of the paper on the open-source implementation of the CMPS algorithm, rather than the examination of bullets.
+You also need to make sure to state early and often that you are not claiming that this algorithm is your idea.
+You are implementing the algorithm described in the paper by NIST researchers.
+}
+
+An important task of firearm examination is \hh{to answer the question of whether wo pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
+Here, in particular, we are interested } to determine whether two bullets were fired from the same gun barrel.
+\hh{Assessing the similarity between two bullets is based on a comparison of their striation marks acquired during the firing process as bullets are propelled through the barrel. }
 It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired.
-Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land impressions, and the areas the marks occupy are called land engraved areas (LEA).
+Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land engravings, and the areas the marks occupy are called land engraved areas (LEA).
 Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.
@@
 
-The automated framework we used in this paper was proposed by Hare and Hofmann in 2017 [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS?].
+The automated framework  used in this paper was proposed by Hare and Hofmann in 2017 [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS?].
 In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` packages `x3ptools`[cite?] and `bulletxtrctr`[cite?].
@@
 
-figure 1:
-
-```{r, echo=FALSE, out.width="400px"}
+```{r, echo=FALSE, out.width="400px", fig.cap="figure captions \\hh{it'd be also good to put in labels for each state.
+I've added a huge arrow to help with the directionality (Stacy said she had trouble) - I like the way you have the order, it might just need some emphasis.
+What do you think of adding a bigger arrow (or arrows) in the back?}"}
 knitr::include_graphics("img/figure1.png", dpi = 100)

### 2021-02-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
pictures
couple of citations

@@
 
+## Background
+
 An important task of firearm examination is \hh{to answer the question of whether wo pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
@@
 
-The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [cite?], and in particular, they are Hamby set 252 and Hamby set 44.
+The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], and in particular, they are Hamby set 252 and Hamby set 44.
 For each Hamby set in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels.
@@
 
-The automated framework  used in this paper was proposed by Hare and Hofmann in 2017 [AUTOMATIC MATCHING OF BULLET LAND IMPRESSIONS?].
+The automated framework  used in this paper was proposed by @aoas.
 In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` packages `x3ptools`[cite?] and `bulletxtrctr`[cite?].
@@
 Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score.
-The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [original paper] in 2019, is one such algorithm.
+The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps] in 2019, is one such algorithm.
 The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values.

### 2021-02-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
added figure captions, added figure 1_v2

@@
 \newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
-\newcommand{\wj}[1]{{\textcolor{forestgreen}{#1}}}
+\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
 \setlength{\parindent}{0pt}
@@
 }
+
+In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
+@cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its usage in examples of comparing bullet signature correlations.
+Although @cmps introduced the algorithm of the CMPS method in their paper, an open-source implementation of this powerful method was missing.
+Thus, our effort here is to introduce the CMPS method to `R` community and provide an open-source implementation of the algorithm for people to use and make further improvements.
+Our implementation was wrapped up into a `R` package called `CMPS`, which is available on GitHub[cite git?].
+In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps and implemented the CMPS algorithm, and present results of applying our implementation to real data.
 
@@
 
+```{r, echo=FALSE, out.width="400px", fig.cap="image of a XXX gun barrel and a fired bullet"}
+knitr::include_graphics("img/barrel_bullet.PNG", dpi = 100)
+```
+
 ```{r, echo=FALSE, out.width="400px", fig.cap="figure captions \\hh{it'd be also good to put in labels for each state.
 I've added a huge arrow to help with the directionality (Stacy said she had trouble) - I like the way you have the order, it might just need some emphasis.
-What do you think of adding a bigger arrow (or arrows) in the back?}"}
-knitr::include_graphics("img/figure1.png", dpi = 100)
+What do you think of adding a bigger arrow (or arrows) in the back?} (a) front view of a scanned land engraved area (LEA).
+The optimized crosscut location is indicated by the white line.
+(b) view of the cross-section of the land engraved area at the white line in (a).
+(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves (d) the crosscut data after chopping the left and right grooves (e) the fitted curvature using LOESS (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
+knitr::include_graphics("img/figure1_v2.PNG", dpi = 100)
 ```
@@
 Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score.
-The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps] in 2019, is one such algorithm.
+The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps], is one such algorithm.
 The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values.
@@
 
-```{r, echo=FALSE, out.width="300px"}
+```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment. "}
 knitr::include_graphics("img/sigplot1.png", dpi = 100)
@@
 
-```{r, echo=FALSE, out.width="300px"}
+```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; the red line shows the reference profile.
+Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.
+"}
 knitr::include_graphics("img/sigplot2.png", dpi = 100)
@@
 
-```{r, echo=FALSE, out.width="300px"}
+```{r, echo=FALSE, out.width="300px", fig.cap="segment_plot for segment 6 at scale 1.
+The original position of segment 6 is indicated by the solid black line.
+Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.
+"}
 knitr::include_graphics("img/segplot1.png", dpi = 100)
@@
 
-```{r, echo=FALSE, out.width="300px"}
+```{r, echo=FALSE, out.width="300px", fig.cap="scale_ccf_plot shows the cross-correlation curve between the comparison profile and segment 6 at scale 1.
+The five highest peaks are marked by dots.
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone.
+We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"}
 knitr::include_graphics("img/segplot2.png", dpi = 100)
@@
 
-Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segments.
+Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segment.
 
@@
 
-```{r, echo=FALSE, out.width="400px"}
+```{r, echo=FALSE, out.width="400px", fig.cap="put segment_plot and scale_ccf_plot of all scales together.
+We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
+Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
+Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."}
 knitr::include_graphics("img/segplot3.png", dpi = 100)

### 2021-02-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits
the changed figure looks great!

@@
 # tex file. Don't forget to rename the bib file and change this example value.
-bibliography: RJreferences.bib
+bibliography: CMPSpaper-writing.bib
 
@@
 
-\hh{Will, it might be better to put the focus of the paper on the open-source implementation of the CMPS algorithm, rather than the examination of bullets.
-You also need to make sure to state early and often that you are not claiming that this algorithm is your idea.
-You are implementing the algorithm described in the paper by NIST researchers.
-}
-
 In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
 @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its usage in examples of comparing bullet signature correlations.
-Although @cmps introduced the algorithm of the CMPS method in their paper, an open-source implementation of this powerful method was missing.
-Thus, our effort here is to introduce the CMPS method to `R` community and provide an open-source implementation of the algorithm for people to use and make further improvements.
-Our implementation was wrapped up into a `R` package called `CMPS`, which is available on GitHub[cite git?].
-In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps and implemented the CMPS algorithm, and present results of applying our implementation to real data.
-
-## Background
+Although @cmps introduced the algorithm of the CMPS method in their paper, \hh{they did not release an implementation of their method}.
+Thus, our effort here is to introduce the CMPS method to the `R` community and provide an open-source implementation of the algorithm for people to use and make further improvements.
+Our implementation is wrapped up into  `R` package  `CMPS`, which is available on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
 
@@
 Here, in particular, we are interested } to determine whether two bullets were fired from the same gun barrel.
-\hh{Assessing the similarity between two bullets is based on a comparison of their striation marks acquired during the firing process as bullets are propelled through the barrel. }
+\hh{Assessing the similarity between two bullets is based on a comparison of  striation marks acquired during the firing process as bullets are propelled through the barrel. }
+
 It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired.
@@
 The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.
+
+In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, and present results of applying our implementation to real data.
+
+## Background
+
+### Hamby Data Set
 
@@
 Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project.
+
+### Extracting signatures from LEAs
 
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="figure captions \\hh{it'd be also good to put in labels for each state.
-I've added a huge arrow to help with the directionality (Stacy said she had trouble) - I like the way you have the order, it might just need some emphasis.
-What do you think of adding a bigger arrow (or arrows) in the back?} (a) front view of a scanned land engraved area (LEA).
+```{r, echo=FALSE, out.width="400px", fig.cap="(a) front view of a scanned land engraved area (LEA).
 The optimized crosscut location is indicated by the white line.
@@
 
+### Conceptual idea of CMPS
 Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score.
@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap="segment_plot for segment 6 at scale 1.
+```{r, echo=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
 The original position of segment 6 is indicated by the solid black line.
@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap="scale_ccf_plot shows the cross-correlation curve between the comparison profile and segment 6 at scale 1.
+```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison profile and segment 6 at scale 1.
 The five highest peaks are marked by dots.
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="put segment_plot and scale_ccf_plot of all scales together.
+```{r, echo=FALSE, out.width="400px", fig.cap="put segment\\_plot and scale\\_ccf\\_plot of all scales together.
 We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).

### 2021-02-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
adding references

@@
     - line 2 affiliation 2
-  - name: Author Three
-    url: https://journal.r-project.org
-    email: author3@work
-    affiliation: Affiliation
-    address:
-    - line 1 affiliation
-    - line 2 affiliation
 abstract: >
@@
 
+ Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.
+
 An important task of firearm examination is \hh{to answer the question of whether wo pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
@@
 \hh{Assessing the similarity between two bullets is based on a comparison of  striation marks acquired during the firing process as bullets are propelled through the barrel. }
-
-It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired.
+\hh{Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope.
+This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].}
+<!--It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired.
 Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land engravings, and the areas the marks occupy are called land engraved areas (LEA).
-Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.
-However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.
-A report published by the National Academy of Sciences in 2009 states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those critics and concerns, people have been making an effort to build databases and develop frameworks and algorithms that can bring an objective and quantitative assessment into the field.
+However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.--> A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those critics and concerns, reseaerchers have been making an effort to build databases [@nistdb] and develop frameworks and algorithms that can bring an objective and quantitative assessment into the field.
 The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.
@@
 Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
-Hamby set 44 were scanned ...[at CSAFE?]...
-Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project.
+Hamby set 44 was scanned \hh{at the Roy J Carver High-Resolution microscopy lab at Iowa State.
+These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu per pixel}.
+Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].
 

### 2021-02-25 CMPSpaper_writing/CMPSpaper_writing.Rmd
small stuff
update tables and figure captions

@@
   - \usepackage{xcolor}
+  - \usepackage{longtable}
 author:
@@
 
+```{r, echo=FALSE}
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  out.width = "\\textwidth",
+  fig.align = "center"
+)
+```
+
 ## Introduction
@@
 
-An important task of firearm examination is \hh{to answer the question of whether wo pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
+An important task of firearm examination is \hh{to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
 Here, in particular, we are interested } to determine whether two bullets were fired from the same gun barrel.
@@
 Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
-Note that NIST researchers used a different way of getting the bullet signatures in their paper [cite?].
+Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].
 
@@
 Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified in step 3, and the length of the tolerance zone in step 3.
-In our implementation of the CMPS algorithm we took the original CMPS paper [cite?] as the reference to determine the default values of these parameters.
+In our implementation of the CMPS algorithm we took the original CMPS paper [@cmps] as the reference to determine the default values of these parameters.
 The main function that follows the CMPS algorithm is called `extract_feature_cmps`. It consists of all steps of the algorithm and receives parameters from the users.
@@
 
-[examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf]
-[https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf]
+<!-- [examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf] -->
+<!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->
 
@@
 <!-- this is figure 2 -->
-```{r, echo=FALSE, out.width="400px"}
+```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) "}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
@@
 
-<!-- |Parameters             | $\mathrm{CMPS_{max}}$ - KNM's max| $\mathrm{CMPS_{max}}$ - KM's min| $\mathrm{\overline{CMPS}_{max}}$ - KNM's max| $\mathrm{\overline{CMPS}_{max}}$ - KM's min| -->
-<!-- |:----------------------|---------------------------------:|--------------------------------:|--------------------------------------------:|-------------------------------------------:| -->
-<!-- |span1=0.25, (5, 3, 1)  |                                 7|                               10|                                       3.6000|                                      6.6667| -->
-<!-- |span1=0.25, (10, 6, 1) |                                 9|                               13|                                       4.8333|                                      9.1667| -->
-<!-- |span1=0.75, (5, 3, 1)  |                                 6|                               11|                                       3.1667|                                      6.6000| -->
-
 ```{r, echo=FALSE}
-# library(knitr)
-# library(kableExtra)
+library(knitr)
+library(kableExtra)
 # rtt <- readRDS("summary_table.rds")
@@
                   p4 = c(6.667, 9.167, 6.6))
+colnames(rtt) <- c("Parameters",
+                   "$\\mathrm{CMPS_{max}}$ KNM's max",
+                   "$\\mathrm{CMPS_{max}}$ KM's min",
+                   "$\\mathrm{\\overline{CMPS}_{max}}$ KNM's max",
+                   "$\\mathrm{\\overline{CMPS}_{max}}$ KM's min")
 
-knitr::kable(rtt, 
-             row.names = FALSE, digits = 4,
-             col.names = c("Parameters",
-                           "$\\mathrm{CMPS_{max}}$ - KNM's max",
-                           "$\\mathrm{CMPS_{max}}$ - KM's min",
-                           "$\\mathrm{\\overline{CMPS}_{max}}$ - KNM's max",
-                           "$\\mathrm{\\overline{CMPS}_{max}}$ - KM's min")) 
+knitr::kable(rtt, "latex", booktabs = TRUE, escape = FALSE,
+             caption = "min and max of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ showing the separation between KNM and KM",
+             row.names = FALSE, digits = 4) %>% 
+  column_spec(2:5, width = "2cm")
 ```
@@
 
-```{r, echo=FALSE, out.width="400px"}
+```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.25"}
 # [1] "span1=0.25, span2=0.03, rm_outliers"
@@
 
-```{r, echo=FALSE, out.width="400px"}
+```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 "}
 # [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
@@
 
-```{r, echo=FALSE, out.width="400px"}
+```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75"}
 # [4] "span1=0.75, span2=0.03, rm_outliers"  

### 2021-02-25 CMPSpaper_writing/CMPSpaper_writing.Rmd
small changes

--- 2021-02-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
   - name: Author One
-    affiliation: Affiliation
+    affiliation: ISU, CSAFE
     address:
@@
     email:  author1@work
-  - name: Author Two
+  - name: Heike Hofmann
     url: https://journal.r-project.org
-    email: author2@work
+    email: hofmann@iastate.edu
     orcid: 0000-0002-9079-593X
-    affiliation: Affiliation 1
+    affiliation: ISU, CSAFE
     address:

### 2021-03-04 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of small edits

@@
 In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
-@cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its usage in examples of comparing bullet signature correlations.
-Although @cmps introduced the algorithm of the CMPS method in their paper, \hh{they did not release an implementation of their method}.
-Thus, our effort here is to introduce the CMPS method to the `R` community and provide an open-source implementation of the algorithm for people to use and make further improvements.
-Our implementation is wrapped up into  `R` package  `CMPS`, which is available on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
+@cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
+Although @cmps described the CMPS algorithm  in their paper, conceptually, \hh{the authors did not release an implementation of their method}.
+Thus, our effort here is to introduce the CMPS method to the `R` community and provide an open-source implementation of the algorithm for people to use, review, and further improvements.
+Our implementation is wrapped up into  `R` package  `CMPS`, available on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
 
@@
 Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land engravings, and the areas the marks occupy are called land engraved areas (LEA).
-However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.--> A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those critics and concerns, reseaerchers have been making an effort to build databases [@nistdb] and develop frameworks and algorithms that can bring an objective and quantitative assessment into the field.
+However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.--> A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases [@nistdb] and develop frameworks and algorithms that  bring an objective and quantitative assessment into the field \hh{XXX cite some of these efforts - make sure to say that it is not an exhaustive list}.
+\hh{XXX The bullet signatures weren't mentioned before - make sure to include that there is a whole section that discusses how bullet signatures are extracted from scans.}
 The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.
@@
 
-The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], and in particular, they are Hamby set 252 and Hamby set 44.
-For each Hamby set in the study, 35 bullets are fired by ten Ruger P-85 pistol barrels.
-20 of the 35 bullets are known test bullets and 15 of them are unknown bullets.
-Each bullet has six land engraved areas (LEA) or land impressions, whose 3D topographical images were obtained and stored in the x3p format (XML 3-D Surface Profile).
+The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019],  in particular, Hamby set 252 and Hamby set 44. 
+For each Hamby set, a total of 35 bullets is fired from ten \hh{consecutively manufactured} Ruger P-85 pistol barrels.
+\hh{Two bullets are fired from each barrel, making up a set of 20 reference bullets.
+An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant.
+The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from.
+The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands \hh{as shown in \autoref{fig:bullet}}.
+During the firing process, grooves and lands are engraved on a bullet.
+Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison.
+For algorithmic purposes, }
+ 3D topographical images \hh{land engraved areas} were obtained and stored in  x3p format (XML 3-D Surface Profile).
 The x3p format provides a standard way of exchanging 2D and 3D profile data.
-It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/] and was adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
+It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/]  adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
 Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
@@
 The automated framework  used in this paper was proposed by @aoas.
-In order to obtain bullet signatures from the x3p files of bullet land impressions, we used `R` packages `x3ptools`[cite?] and `bulletxtrctr`[cite?].
-`x3ptools` can be used to process x3p files.
-In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).
-Figure 1(a) shows a bullet land impression scan of a processed x3p file.
-The raised portion of the surface are groove impressions, and the vertical striation marks between the groove impressions are what we are interested in, called a land impression.
+In order to obtain bullet signatures from the x3p files of bullet land impressions, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
+`x3ptools` \hh{is a package to read, write, and generally, process } x3p files.
+<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).-->
+\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper).
+Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face.
+Engravings are scratch marks.}
+\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area.
+The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks.
 The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression.
 `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
-Figure 1(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.
+\autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.
 `bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept.
-With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [Cleveland 1979?] and obtain the bullet signature.
-Figure 1 illustrates this framework.
+With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature.
+\autoref{fig:process} illustrates this framework.
 Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="image of a XXX gun barrel and a fired bullet"}
+```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="image of a XXX gun barrel and a fired bullet - \\hh{xxx my version of the image still has a groove engraved area marked as a land}"}
 knitr::include_graphics("img/barrel_bullet.PNG", dpi = 100)
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="(a) front view of a scanned land engraved area (LEA).
+```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="(a) front view of a scanned land engraved area (LEA).
 The optimized crosscut location is indicated by the white line.

### 2021-03-04 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of comments

@@
 The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression.
-`bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
+\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description.
+Could you instead describe things conceptually, and then link to the code that does this particular image?} `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal \hh{XXX ideal is a dangerous word} height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
 \autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.

### 2021-03-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
added more citations in bib and revised "extract signature" section

@@
 Although @cmps described the CMPS algorithm  in their paper, conceptually, \hh{the authors did not release an implementation of their method}.
-Thus, our effort here is to introduce the CMPS method to the `R` community and provide an open-source implementation of the algorithm for people to use, review, and further improvements.
+Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source implementation of the algorithm for people to use, review, and further improvements.
 Our implementation is wrapped up into  `R` package  `CMPS`, available on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
@@
 \hh{XXX The bullet signatures weren't mentioned before - make sure to include that there is a whole section that discusses how bullet signatures are extracted from scans.}
-The bullet signatures extracted from the bullet are important in this process since they can well describe the striation marks on the bullet and can well be understood by algorithms.
-
+\wj{The notion of bullet signatures is one of the results of these efforts.
+Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
+Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
+}
 In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, and present results of applying our implementation to real data.
@@
 The automated framework  used in this paper was proposed by @aoas.
-In order to obtain bullet signatures from the x3p files of bullet land impressions, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
+In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
 `x3ptools` \hh{is a package to read, write, and generally, process } x3p files.
@@
 The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks.
-The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land impression.
+The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
 \hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description.
-Could you instead describe things conceptually, and then link to the code that does this particular image?} `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal \hh{XXX ideal is a dangerous word} height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
-\autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land impression and the groove impression.
-`bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land impression in the middle is kept.
-With the groove impressions excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land impression curvature using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature.
+Could you instead describe things conceptually, and then link to the code that does this particular image?}
+
+\wj{The white horizontal line in \autoref{fig:process}(a) indicates this fixed height selected by an algorithm, and \autoref{fig:process}(b) shows the cross-sectional view of the bullet scan at this height.
+Then we can acquire the crosscut data (`ccdata`) of the scan at this height.
+\autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land engraving and the groove engravings.
+The next step is to locate and chop these wedge areas so that only the data of the land engraving in the middle is kept (as shown in \autoref{fig:process}(d)).
+With the groove engravings excluded, we can then smooth out the land engraving curvature (\autoref{fig:process}(e)) using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature (\autoref{fig:process}(f)).
+\autoref{fig:process} illustrates this framework.
+Sometimes the algorithm in our framework cannot determine the valid location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
+Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].}
+
+<!-- `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal \hh{XXX ideal is a dangerous word} height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
+\autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land engraving and the groove engraving.
+`bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land engraving in the middle is kept.
+With the groove engravings excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land engraving curvature using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature.
 \autoref{fig:process} illustrates this framework.
@@
 Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].
+-->
 
 ```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="image of a XXX gun barrel and a fired bullet - \\hh{xxx my version of the image still has a groove engraved area marked as a land}"}
-knitr::include_graphics("img/barrel_bullet.PNG", dpi = 100)
+knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
 ```
 
-```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="(a) front view of a scanned land engraved area (LEA).
-The optimized crosscut location is indicated by the white line.
+```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature.
+(a) front view of a scanned land engraved area (LEA).
+The selected crosscut location is indicated by the white line.
 (b) view of the cross-section of the land engraved area at the white line in (a).
-(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves (d) the crosscut data after chopping the left and right grooves (e) the fitted curvature using LOESS (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
+(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves.
+(d) the crosscut data after chopping the left and right grooves.
+(e) the fitted curvature using LOESS.
+(f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
 knitr::include_graphics("img/figure1_v2.PNG", dpi = 100)
@@
 The `CMPS` package contains a simple example to illustrate the basic usage of the package.
-The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [cite?] (Each bullet has six lands).
+The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 (Each bullet has six lands).
 The procedure for generating signatures from 3D bullet lands in x3p format is (algorithmic) [and has been discussed above].
@@
 And anyone who is interested in the data source can find it in `bullets$source`.
-One can use these links to download the original x3p files from [NIST, cite?].
+One can use these links to download the original x3p files from NIST Ballistics Toolmark Research Database [@nistdb].
 `bulletxtrctr::read_bullet(urllist = bullets$source)`
@@
 
-In (NIST's original paper) that presents the CMPS algorithm researchers applied the CMPS method to one of the Hamby set scans (Hamby 252).
+As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252).
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in (original paper) and is able to be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
 Since the CMPS algorithm works with, in our case, bullet signatures, we conducted some data-processing.
-For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann using the same set of parameters for both data sets, removed outliers, and obtained bullet signatures for each bullet land impression.
-Note that [in NIST's paper] they used a different framework to obtain bullet signatures.
+For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann using the same set of parameters for both data sets, removed outliers, and obtained bullet signatures for each bullet land engraving.
+Note that in the work of @cmps they used a different framework to obtain bullet signatures.
 However, since NIST's work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.

### 2021-03-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
edits through signature extraction

@@
 
-### Extracting signatures from LEAs
+### Extracting signatures from LEA scans
 
@@
 <!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).-->
-\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper).
+<!--\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper).
 Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face.
-Engravings are scratch marks.}
+Engravings are scratch marks.}-->
+\hh{\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.}
 \autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area.
@@
 The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
-\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description.
-Could you instead describe things conceptually, and then link to the code that does this particular image?}
-
-\wj{The white horizontal line in \autoref{fig:process}(a) indicates this fixed height selected by an algorithm, and \autoref{fig:process}(b) shows the cross-sectional view of the bullet scan at this height.
-Then we can acquire the crosscut data (`ccdata`) of the scan at this height.
-\autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land engraving and the groove engravings.
-The next step is to locate and chop these wedge areas so that only the data of the land engraving in the middle is kept (as shown in \autoref{fig:process}(d)).
-With the groove engravings excluded, we can then smooth out the land engraving curvature (\autoref{fig:process}(e)) using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature (\autoref{fig:process}(f)).
-\autoref{fig:process} illustrates this framework.
-Sometimes the algorithm in our framework cannot determine the valid location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
-Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].}
+<!--\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description.
+Could you instead describe things conceptually, and then link to the code that does this particular image?} -->
+The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
+<!--Then we can acquire the crosscut data (`ccdata`) of the scan at this height.
+--> \hh{XXX passive voice for things that are not part of this paper :)}
+Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
+A non-parametric LOESS smooth  [@loess] is fit to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
+\hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
+To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],}   `bulletinspectR` to identify and correct those errors.
+\hh{An example of the extraction process with corresponding code and parameter settings can be found at XXX.}
+Note that \hh{the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.}
 

### 2021-03-11 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple more edits

@@
 ### Conceptual idea of CMPS
-Once we obtain the bullet signatures, we can compare them using an algorithm that computes a similarity score.
-The congruent matching profile segments (CMPS) algorithm, developed by NIST for "objective comparison of striated tool marks" [@cmps], is one such algorithm.
-The main idea of the CMPS algorithm is that, we cut the reference profile (one of the two bullet signatures) into consecutive and non-overlapping basis segments and ask each basis segment to find the "best" registration position on the comparison profile (the other bullet signature) in terms of correlation values.
-Then the congruent registration position is the position where the most basis segments find it the "best", and the number of basis segments taking the congruent registration position is the CMPS score.
-The CMPS algorithm can assist firearm examiners with drawing a conclusion, but NIST's implementation of the CMPS algorithm was not released for the public.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm so that everyone can use and improve it.
+\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX and produce a similarity score (some citations: chumbley score, Ganesh's fix, vorburger's ccf paper, hare).}
+ The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
+The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values.
+\hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
+\hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.} 
+\hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
+ The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}.
+\hh{Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the } CMPS algorithm.
+Thus, in this paper we present an open-source implementation of the CMPS algorithm \hh{in the R package CMPS available from XXX github / CRAN}. 
 With our implementation, one can compute the CMPS score of a comparison using the following code:

### 2021-03-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
step by step instructions

@@
 
-In the example in section "Implementation" we would see that, two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
+\hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}
+
+In the example in section "Implementation" we  see that two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
 We also implemented graphing tools for users to better understand these results as well as the algorithm itself.
@@
 
-The CMPS algorithm consists of X steps.
+The CMPS algorithm consists of \hh{three main} steps:
 
-step 1) cut the reference profile into consecutive, non-overlapping and equal-length basis segments;
+1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
+the command `get_segs(x, len=50)` implements this first step. 
+It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
 
-`get_segs(x, len=50)` implements the first step. It takes a profile in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
+2. **register each basis segment on the comparison profile:** 
+Calculate the cross-correlation curve between a basis segment and the comparison profile.A registration position is considered as "good" if the basis segment achieves a high cross-correlation value at that position.
+The best registration position is decided upon using  a multi-peak inspection with or without different segment lengths:
 
-step 2) each basis segment finds its best registration position on the comparison profile.
-A cross-correlation curve between a basis segment and the comparison profile would be computed, and a registration position is considered as "good" if the basis segment achieves a high cross-correlation value at this position.
-
-Then how should a basis segment find its best registration position?
-[In the original paper] researchers proposed two versions of the CMPS alrorithm that can answer this question.
-The first version is called "multi-peak inspection", and the second version is called "multi-peak inspection at different segment lengths/scales".
-We also refer the second version as the CMPS algorithm using "the multi segment lengths strategy".
-
-Step 2.1) multi-peak inspection: each basis segment identifies positions of 5 (or multiple) highest peaks in the cross-correlation curve.
+    2.1.
+**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of 5 (or multiple) highest peaks in the cross-correlation curve.
 Since false positive peaks would stand out when the segment length is short, positions of all 5 peak will be considered as the potential "best" registration position.
 
-Step 2.2) multi segment lengths strategy: for this version of the CMPS algorithm, each basis segment finds only one "best" registration position.
+    2.2.
+**multi-peak inspection with different segment lengths:** for this version of the CMPS algorithm, each basis segment finds only one "best" registration position.
 This "best" registration position can be found by conducting multi-peak inspection multiple rounds.

### 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits

@@
 
-The CMPS algorithm consists of \hh{three main} steps:
+Conceptually, the CMPS algorithm consists of \hh{three main} steps:
 
 1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
-the command `get_segs(x, len=50)` implements this first step. 
-It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
 
@@
 
+3.
+**determine the congruent registration position** with a small tolerance zone and the number of basis segments that take the congruent registration position as their "best" registration position.
+These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of this profile comparison.
+
 <!-- we conduct the "multi-peak inspection at different segment lengths".
@@
 
-`get_ccf4` computes the cross-correlation function / correlation coefficient curve between two profiles. This is the function called whenever we need to compute the ccf.
+\hh{In the CMPS package, these three steps are implemented using a set of key functions:}
+
+* The command `get_segs(x, len=50)` implements step 1:  It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
+
+* `get_ccf4` computes the cross-correlation function / correlation coefficient curve between two profiles. This is the function called whenever we need to compute the ccf.
 
@@
 
-`get_seg_scale` takes a basis segment and increases its segment length. `scale=1` gives the original length of the basis segment. Increasing `scale` by 1 will double the segment length.
+* `get_seg_scale` takes a basis segment and increases its segment length. `scale=1` gives the original length of the basis segment. Increasing `scale` by 1 will double the segment length.
 
-`get_ccr_peaks` takes a segment and the comparison profile, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve.
+* `get_ccr_peaks` takes a segment and the comparison profile, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve.
 The number of peaks detected is equal to `npeaks`.
@@
 
-`get_ccp` checks if the "consistent correlation peak" exists under the framework of multi segment lengths strategy.
+* `get_ccp` checks if the "consistent correlation peak" exists under the framework of multi segment lengths strategy.
 Since we are requiring the highest segment scale identifies only one peak, we just need to check if this peak shows any "consistency".
@@
 
-step 3) determine the congruent registration position with a small tolerance zone and the number of basis segments that take the congruent registration position as their "best" registration position.
-These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of this profile comparison.
-
-`get_CMPS` considers all basis segments and their identified peak positions to determine the congruent registration position.
+* `get_CMPS` considers all basis segments and their identified peak positions to determine the congruent registration position.
 The goal is to find a peak position that is agreed by the most basis segments.

### 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
code side-by-side?

@@
 
+\hh{XXX Could we move the code into the corresponding figure and show the relevant pieces side by side?
+I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}
 ```{r, eval=FALSE}

### 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
marked further questions

--- 2021-03-18 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
-A non-parametric LOESS smooth  [@loess] is fit to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
+A non-parametric LOESS smooth  [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
 \hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
@@
 \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
+\wj{they didn't talk about a specific threshold or error rates}
  The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}.
@@
 \hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}
+\wj{further question?}
 
@@
 the command `get_segs(x, len=50)` implements this first step. 
-It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
+It takes a profile \hh{XXX profile or signature?} \wj{further question?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
 
@@
 
+<!-- open source -->
+<!-- module -->
+<!-- hamby 44 new data set -->
+<!-- hamby 252 -->
+<!-- threshold -->
+
 ### About this format and the R Journal requirements

### 2021-04-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
steps 1-3

--- 2021-03-31 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 ---
-title: Capitalized Title Here
+title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures
 header-includes:
@@
   # see ?rjournal_article for more information
-  - name: Author One
-    affiliation: ISU, CSAFE
+  - name: Will W. Ju
+    affiliation: Department of Statistics
     address:
-    - line 1
-    - line 2
-    url: https://journal.r-project.org
+    - Center for Statistics and Applications in Forensic Evidence
+    - Iowa State University
+    - 2438 Osborn Dr
+    - Ames, IA 50011
+    url: https://github.com/willju-wangqian
     orcid: 0000-0002-9079-593X
-    email:  author1@work
+    email:  wju@iastate.edu
   - name: Heike Hofmann
-    url: https://journal.r-project.org
+    url: https://github.com/heike
     email: hofmann@iastate.edu
     orcid: 0000-0002-9079-593X
-    affiliation: ISU, CSAFE
+    affiliation: Department of Statistics
     address:
-    - line 1 affiliation 1
-    - line 2 affiliation 1
-    affiliation2: Affiliation 2
-    address2:
-    - line 1 affiliation 2
-    - line 2 affiliation 2
+    - Center for Statistics and Applications in Forensic Evidence
+    - Iowa State University
+    - 2438 Osborn Dr
+    - Ames, IA 50011
 abstract: >
@@
 `x3ptools` \hh{is a package to read, write, and generally, process } x3p files.
+\hh{The `bulletxtrctr` package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.}
 <!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).-->
@@
 Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
-A non-parametric LOESS smooth  [@loess] is fit to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
+A non-parametric LOESS smooth  [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
+\wj{Note that in @cmps bullet signatures are sometimes referred as bullet profiles.
+However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
+Bullet profiles are XXX, while bullet signatures are XXX.}
 \hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
@@
 
-```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="image of a XXX gun barrel and a fired bullet - \\hh{xxx my version of the image still has a groove engraved area marked as a land}"}
+```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)."}
 knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
@@
  The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
-The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values.
+The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile \wj{might reference profile refer to something more general?}  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values.
 \hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
@@
 
+\hh{XXX could you make this example functional?}
 ```{r, eval=FALSE}
@@
 1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
+The command `get_segs(x, len=50)` implements this step:  it takes a bullet signature  in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
 
 2. **register each basis segment on the comparison profile:** 
-Calculate the cross-correlation curve between a basis segment and the comparison profile.A registration position is considered as "good" if the basis segment achieves a high cross-correlation value at that position.
+Calculate the cross-correlation curve between a basis segment and the comparison profile (using function `get_ccf4`).
+A position is considered  "good" if the cross-correlation between the basis segment and the comparison is above a pre-defined threshold. \hh{XXX what is the name of the parameter?} 
 The best registration position is decided upon using  a multi-peak inspection with or without different segment lengths:
@@
     2.1.
-**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of 5 (or multiple) highest peaks in the cross-correlation curve.
-Since false positive peaks would stand out when the segment length is short, positions of all 5 peak will be considered as the potential "best" registration position.
+**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of the top X \hh{parameter name?} highest peaks in the cross-correlation curve.
+Small segment lengths might indicate false positive peaks.
+Therefore all X peaks are considered as candidates for the "best" registration position.
 
@@
 This "best" registration position can be found by conducting multi-peak inspection multiple rounds.
-The first round is the standard way as we have stated in step 2.1.
-But after the first round, we will increase the segment length, compute a new cross-correlation curve, and again identify multiple peaks in the cross-correlation curve.
-The number of peaks identified in this round is typically less than that in the previous round (say 3 highest peaks) since increasing the segment length can reduce the number of false positive peaks.
-We can repeat this procedure multiple times; however in the last round, only one highest peak should be identified.
-If a position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
+The first round is executed as stated in step 2.1.
+After that first round, the segment length is increased, a new cross-correlation curve is computed, and another set of  peaks in the cross-correlation curve is identified together with the candidate positions.
+Typically, fewer number of peaks are identified in this round (because the increased segment length reduces the chance of false positive peaks).
+This process can be repeated multiple times.
+In the last round, only one highest peak should be identified.
+If the same or 'similar enough' (see step 3) position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
 
-3.
-**determine the congruent registration position** with a small tolerance zone and the number of basis segments that take the congruent registration position as their "best" registration position.
-These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of this profile comparison.
+3. **determine the congruent registration position**:
+candidate positions across different segements are compared using a small tolerance \hh{XXX parameter for this} and basis segments with a congruent registration position are determined.
+These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of the comparison.
 
@@
 \hh{In the CMPS package, these three steps are implemented using a set of key functions:}
-
-* The command `get_segs(x, len=50)` implements step 1:  It takes a profile {XXX profile or signature?} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
-
-* `get_ccf4` computes the cross-correlation function / correlation coefficient curve between two profiles. This is the function called whenever we need to compute the ccf.
 
@@
 Since we are moving this tolerance zone from left to right one unit a time, some consecutive positions are expected to have the same number of basis segments.
-[?.?]In that case the median of all tied and consecutive positions will be chosen as the congruent registration position.
+[?.?] In that case the median of all tied and consecutive positions will be chosen as the congruent registration position.
 As long as the congruent registration position is determined, the number of basis segments that identify a peak in this position is the CMPS score.

### 2021-04-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

@@
 A non-parametric LOESS smooth  [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
-\wj{Note that in @cmps bullet signatures are sometimes referred as bullet profiles.
+Note, that in @cmps bullet signatures are  referred to as bullet profiles.
 However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
-Bullet profiles are XXX, while bullet signatures are XXX.}
+\wj{Bullet profiles are \hh{shown in panels (b), (c), and (d) of \autoref{fig:process}}, while \autoref{fig:process}(f) shows the corresponding bullet signature.}
 \hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
@@
  The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
-The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference profile \wj{might reference profile refer to something more general?}  and  for each segment find the "best" registration position on the comparison profile (the other bullet signature) with respect to their cross-correlation values.
+The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference   and  for each segment find the "best" registration position on the comparison  (the other bullet signature) with respect to their cross-correlation values.
 \hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
@@
 \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
-\wj{they didn't talk about a specific threshold or error rates}
+\wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example?
+...
+'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'}
  The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}.

### 2021-04-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment. "}
+```{r, echo=FALSE, out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment.
+"}
 knitr::include_graphics("img/sigplot1.png", dpi = 100)
@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap="The dark grey line shows the comparison profile; the red line shows the reference profile.
+```{r, echo=FALSE, out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background?
+XXX} The dark grey line shows the comparison profile; the red line shows the reference profile.
 Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.

### 2021-04-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
fix profile/signature

@@
 
-1. **cut the reference profile into consecutive, non-overlapping and equal-length basis segments:**
+1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
 The command `get_segs(x, len=50)` implements this step:  it takes a bullet signature  in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
 
-2. **register each basis segment on the comparison profile:** 
-Calculate the cross-correlation curve between a basis segment and the comparison profile (using function `get_ccf4`).
+2. **register each basis segment on the comparison signature:** 
+Calculate the cross-correlation curve between a basis segment and the comparison signature (using function `get_ccf4`).
 A position is considered  "good" if the cross-correlation between the basis segment and the comparison is above a pre-defined threshold. \hh{XXX what is the name of the parameter?} 
@@
 3. **determine the congruent registration position**:
-candidate positions across different segements are compared using a small tolerance \hh{XXX parameter for this} and basis segments with a congruent registration position are determined.
+candidate positions across different segments are compared using a small tolerance \hh{XXX parameter for this} and basis segments with a congruent registration position are determined.
 These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of the comparison.
@@
 
-* `get_ccr_peaks` takes a segment and the comparison profile, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve.
+* `get_ccr_peaks` takes a segment and the comparison signature, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve.
 The number of peaks detected is equal to `npeaks`.
@@
 However, besides the most important `CMPS.score`, there are other pieces of information related to the CMPS score that one might be interested in, such as
-  - `nseg`: the number of basis segments we get from the reference profile; this is also the highest possible CMPS score of the comparison;
+  - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
   - `congruent.pos`: the congruent registration position;
@@
 
-`extract_feature_cmps` integrates all steps of the CMPS algorithm. It takes two bullet profiles and computes the CMPS score.
+`extract_feature_cmps` integrates all steps of the CMPS algorithm. It takes two bullet signatures and computes the CMPS score.
 
@@
 On this plot only basis segments that agree with the congruent registration position (i.e.
-the segments that are congruent matching profile segments) are plotted along with the comparison profile.
+the segments that are congruent matching profile segments) are plotted along with the comparison signature.
 When plotting, each of those basis segments will be shifted to the position where the basis segment obtains a cross-correlation peak and is within the tolerance zone of the congruent registration position.
@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison profile; each red line segment shows one comgruent matching profile segment.
+```{r, echo=FALSE, out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment.
 "}
@@
 The second element is called `signature_shift_plot`.
-On this visual both the reference profile and the comparison profile are plotted.
-The reference profile is aligned with the comparison profile based on the congruent registration position.
+On this visual both the reference signature and the comparison signature are plotted.
+The reference signature is aligned with the comparison signature based on the congruent registration position.
 And the congruent matching profile segments are highlighted.
@@
 ```{r, echo=FALSE, out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background?
-XXX} The dark grey line shows the comparison profile; the red line shows the reference profile.
+XXX} The dark grey line shows the comparison signature; the red line shows the reference signature.
 Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.
@@
 Other elements of this list are `seg_shift`, `sig_shift`, and `seg.pos`.
-These elements are essentially used for generating visuals above but also provide insights about the best fitted position for each congruent matching profile segments and for the reference profile.
+These elements are essentially used for generating visuals above but also provide insights about the best fitted position for each congruent matching profile segments and for the reference signature.
 `sig.plot$seg.pos` can also tell us which basis segments are the congruent matching profile segments.
@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison profile and segment 6 at scale 1.
+```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1.
 The five highest peaks are marked by dots.
@@
 
-The CMPS score can be considered as a similarity score of two profiles.
+The CMPS score can be considered as a similarity score of two signatures.
 Then how can we get a similarity score of two bullets based on CMPS scores?
 In (the original paper) researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet comparisons based on CMPS scores of bullet signature comparisons.
-For example, there are in total 6 $\times$ 6 LEA profile comparisons in order to compare two bullets in Hamby study since each bullet has 6 LEA profiles.
-And a CMPS score will be found for every profile comparison.
-$\mathrm{CMPS_{max}}$ is the highest CMPS score among all profile comparisons.
-And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible average CMPS score of profile comparisons that are in the same phase.
+For example, there are in total 6 $\times$ 6 signature comparisons in order to compare two bullets in Hamby study since each bullet has 6 LEAs and each LEA generates a bullet signature.
+And a CMPS score will be found for every signature comparison.
+$\mathrm{CMPS_{max}}$ is the highest CMPS score among all signature comparisons.
+And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible average CMPS score of signature comparisons that are in the same phase.
 
-Here are the CMPS scores of all 36 profile comparisons of the bullets in the example above.
+Here are the CMPS scores of all 36 signature comparisons of the bullets in the example above.
 
@@
 
-For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures/profiles; however, in this example we used `span1=0.75` and changed the characteristic of those profiles.
+For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures; however, in this example we used `span1=0.75` and changed the characteristic of those signatures.
 As we can see in figure 5, this change also affects the CMPS results.

### 2021-04-12 CMPSpaper_writing/CMPSpaper_writing.Rmd
addressed some problems discussed in the previous meeting

@@
 ### Conceptual idea of CMPS
-\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX and produce a similarity score (some citations: chumbley score, Ganesh's fix, vorburger's ccf paper, hare).}
+\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX} and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940 ].
  The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
@@
 ```{r, eval=FALSE}
-cmps.result <- extract_feature_cmps(sig1, sig2)
+# install.packages("devtools") 
+# devtools::install_github("willju-wangqian/CMPS")
+
+library(CMPS)
+data(bullets)
+
+sig1 <- bullets$sigs[[2]]$sig
+sig2 <- bullets$sigs[[9]]$sig
+sig3 <- bullets$sigs[[10]]$sig
+
+cmps.result.KM <- extract_feature_cmps(sig1, sig2)
+cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
 ```
 
+\wj{In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-matching comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known-non-matching comparison), gets a CMPS score of 2.}
+
 \hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}
-\wj{further question?}
 
-In the example in section "Implementation" we  see that two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
+<!-- In the example in section "Implementation" we see that two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
+-->
+
 We also implemented graphing tools for users to better understand these results as well as the algorithm itself.
@@
 The section "Implementation" will go through the algorithm and show how to use the "CMPS" package.
-An example that illustrates the main points are also included.
+An further example that illustrates the main points are also included.
 The section "Results" presents the results of evaluating the CMPS package using Hamby set 252 and Hamby set 44.
@@
 Calculate the cross-correlation curve between a basis segment and the comparison signature (using function `get_ccf4`).
-A position is considered  "good" if the cross-correlation between the basis segment and the comparison is above a pre-defined threshold. \hh{XXX what is the name of the parameter?} 
+A position is considered "good" \wj{if this position results in a peak in the cross-correlation between the basis segment and the comparison}
+<!-- the cross-correlation between the basis segment and the comparison is above a pre-defined threshold.  -->
 The best registration position is decided upon using a multi-peak inspection with or without different segment lengths:
@@
     2.1.
-**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of the top X \hh{parameter name?} highest peaks in the cross-correlation curve.
+**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of the \wj{top 5 highest peaks (if `npeaks.set = 5`) in the cross-correlation curve}.
 Small segment lengths might indicate false positive peaks.
-Therefore all X peaks are considered as candidates for the "best" registration position.
+Therefore all 5 peaks are considered as candidates for the "best" registration position.
 
@@
 If the same or 'similar enough' (see step 3) position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
+\wj{In order to use this version of the CMPS algorithm, we set `npeaks.set` as a numeric vector of multiple values.
+For example, if we set `npeaks.set = c(5, 3, 1)`, 5 peaks will be identified in the first round, 3 peaks in the second round, and 1 peak in the final round.}
 
 3. **determine the congruent registration position**:
-candidate positions across different segments are compared using a small tolerance \hh{XXX parameter for this} and basis segments with a congruent registration position are determined.
+candidate positions across different segments are compared using a small tolerance \wj{parameter `Tx`} and basis segments with a congruent registration position are determined.
 These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of the comparison.
@@
 ```{r, eval=FALSE}
-land2_3 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
-land1_2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]
+sigs1 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
+sigs2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]
 
@@
 # algorithm with multi-peak insepction at three different segment scales
-cmps_with_multi_scale <- extract_feature_cmps(land2_3$sig, land1_2$sig, 
+cmps_with_multi_scale <- extract_feature_cmps(sigs1$sig, sigs2$sig, 
                                               npeaks.set = c(5,3,1), include = "full_result")
@@
 # algorithm with multi-peak inspection at the basis scale only
-cmps_without_multi_scale <- extract_feature_cmps(land2_3$sig, land1_2$sig, 
+cmps_without_multi_scale <- extract_feature_cmps(sigs1$sig, sigs2$sig, 
                                                  npeaks.set = 5, include = "full_result")

### 2021-04-22 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits

@@
 @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
-Although @cmps described the CMPS algorithm  in their paper, conceptually, \hh{the authors did not release an implementation of their method}.
-Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source implementation of the algorithm for people to use, review, and further improvements.
-Our implementation is wrapped up into  `R` package  `CMPS`, available on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
+Although @cmps conceptually described the CMPS algorithm  in their paper, \hh{the authors did not release an implementation of their method}.
+Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm  to use, review, and  improve.
+Our implementation is made available as part of the  `R` package  `CMPS` on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
 
- Firearm examination has been playing an important role in terms of convictions in the United States criminal justice system.
+ Firearm examination has  played an important role in  convictions in the United States criminal justice system.
+\hh{Do we have a number or a percentage of cases where firearm examination has played a role?
+or maybe gun violence?
+XXX}
 
@@
 
-\wj{In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-matching comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known-non-matching comparison), gets a CMPS score of 2.}
+\wj{In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 2.}
 

### 2021-04-22 CMPSpaper_writing/CMPSpaper_writing.Rmd
comment out
pseudo-code for geom_tile

@@
 
-\hh{XXX How about a barchart with results - or a teaser for an image in the back, that talks about the concept that a CMPS score should be high for two same-source signatures and low for different-source signatures}
-
 <!-- In the example in section "Implementation" we see that two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
@@
 # algorithm with multi-peak insepction at three different segment scales
-cmps_with_multi_scale <- extract_feature_cmps(sigs1$sig, sigs2$sig, 
+cmps_with_multi_scale <- 
+  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                        npeaks.set = c(5,3,1), include = "full_result")
@@
 # algorithm with multi-peak inspection at the basis scale only
-cmps_without_multi_scale <- extract_feature_cmps(sigs1$sig, sigs2$sig, 
+cmps_without_multi_scale <- 
+  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                        npeaks.set = 5, include = "full_result")
@@
 We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.
+
+```{r eval=FALSE}
+dframe %>% 
+  ggplot(aes(x = land1, y = land2, fill = CMPS.score)) +
+    geom_tile() +
+    scale_fill_gradient2(low="darkgrey", high = "darkorange", mid=6) +
+    geom_text(aes(label=CMPS.score))
+```
 

### 2021-04-22 CMPSpaper_writing/CMPSpaper_writing.Rmd
taking include.graphics out for sigplot1 and sigplot2 and replacing by code

@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 library(CMPS)
@@
 
-```{r, eval=FALSE}
+```{r, eval=TRUE}
 sigs1 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
@@
     geom_text(aes(label=CMPS.score))
+
 ```
@@
 The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
-Let's continue with the example above and take its results.
-
-```{r, eval=FALSE}
-sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
-```
+\autoref{fig:sigplot} continues with the example above and take its results.
 
@@
 I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}
+
+<!--
 ```{r, eval=FALSE}
@@
 ```
-
-```{r, echo=FALSE, out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment.
+-->
+```{r sigplot, echo=TRUE,  out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment.
 "}
-knitr::include_graphics("img/sigplot1.png", dpi = 100)
+sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
+sig.plot$segment_shift_plot
+#knitr::include_graphics("img/sigplot1.png", dpi = 100)
 ```
@@
 
+<!--
 ```{r, eval=FALSE}
@@
 ```
+-->
 
-```{r, echo=FALSE, out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background?
+```{r, echo=TRUE, eval=TRUE,  out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background?
 XXX} The dark grey line shows the comparison signature; the red line shows the reference signature.
@@
 "}
-knitr::include_graphics("img/sigplot2.png", dpi = 100)
+sig.plot$signature_shift_plot
+#knitr::include_graphics("img/sigplot2.png", dpi = 100)
 ```
@@
 
-```{r, echo=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
+```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
 The original position of segment 6 is indicated by the solid black line.

### 2021-04-23 CMPSpaper_writing/CMPSpaper_writing.Rmd
code and figure side by side. Still need to get rid of the ```=latex

@@
   - \usepackage{longtable}
+  - \usepackage{adjustbox}            
+  - \usepackage[font=small,skip=5pt]{caption}
+  - \usepackage{subcaption}
+  - \usepackage{afterpage}
 author:
@@
 ```{r, echo=FALSE}
+library(knitr)
+
 knitr::opts_chunk$set(
@@
 )
+```
+
+```{r setup_knitr, echo=FALSE}
+## From Josh O'Brien's stackoverflow answer:
+## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
+## These two settings control text width in codefig vs. usual code blocks
+partWidth <- 35
+fullWidth <- 60
+options(width = fullWidth)
+
+##  (1) CHUNK HOOK FUNCTION
+##   First, to set R's textual output width on a per-chunk basis, we
+## need to define a hook function which temporarily resets global R's
+## option() settings, just for the current chunk
+knit_hooks$set(r.opts = local({
+    ropts <- NA
+    function(before, options, envir) {
+        if (before) {
+            ropts <<- options(options$r.opts)
+        } else {
+            options(ropts)
+        }
+    }
+}))
+
+## (2) OUTPUT HOOK FUNCTION
+
+##   Define a custom output hook function. This function processes _all_
+## evaluated chunks, but will return the same output as the usual one,
+## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
+## case, wrap the usual textual output in LaTeX code placing it in a
+## narrower adjustbox environment and setting the graphics that it
+## produced in another box beside it.
+
+defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
+
+codefigChunkHook <- function(x, options) {
+  main <-  defaultChunkHook(x, options)
+  before <-
+    "\\vspace{1em}
+\\begin{adjustbox}{valign=t}
+\\begin{minipage}{.49\\textwidth}\n"
+  after <-
+    paste("\\vspace{1em}
+\\end{minipage}
+\\begin{minipage}{.49\\textwidth}",
+    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
+                 options[["label"]], "-1.pdf}
+\\end{minipage}
+\\end{adjustbox}"),
+          sep = "\n")
+  ## Was a codefig option supplied in chunk header?
+  ## If so, wrap code block and graphical output with needed LaTeX code.
+  if (!is.null(options$codefig)) {
+    return(sprintf("%s%s\n%s", before, main, after))
+  } else {
+    return(main)
+  }
+}
+
+knit_hooks[["set"]](chunk = codefigChunkHook)
+
+## (3) TEMPLATE
+##   codefig=TRUE is just one of several options needed for the
+## side-by-side code block and a figure to come out right. Rather
+## than typing out each of them in every single chunk header, we
+## define a _template_ which bundles them all together. Then we can
+## set all of those options simply by typing opts.label="codefig".
+
+opts_template[["set"]](
+codefig = list(codefig = TRUE, fig.show = "hide",
+               r.opts = list(width = partWidth),
+               tidy.opts = list(width.cutoff = partWidth)))
 ```
@@
 
-<!--
-```{r, eval=FALSE}
+\begin{figure}
+\begin{subfigure}[t]{\textwidth}
+\caption{\label{fig:sigplot}The dark grey line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
+```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
+sig.plot <- cmps_signature_plot(
+  cmps_with_multi_scale
+)
 sig.plot$segment_shift_plot
 ```
--->
-```{r sigplot, echo=TRUE,  out.width="300px", fig.cap=" \\hh{I don't think we need fig 3 when we have fig 4 XXX} The dark grey line shows the comparison signature; each red line segment shows one comgruent matching profile segment.
-"}
-sig.plot <- cmps_signature_plot(cmps_with_multi_scale)
-sig.plot$segment_shift_plot
-#knitr::include_graphics("img/sigplot1.png", dpi = 100)
+\end{subfigure}
+\begin{subfigure}[t]{\textwidth}
+\caption{\label{fig:sigplot2}The dark grey line shows the comparison signature; the red line shows the reference signature.
+Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
+```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
+sig.plot$signature_shift_plot
 ```
+\end{subfigure}
+\caption{\label{sigplots}\hh{The resulting two figures signature plots. We need a summarizing sentence here.}}
+\end{figure}
 
 The second element is called `signature_shift_plot`.
-On this visual both the reference signature and the comparison signature are plotted.
+\hh{It is shown in \autoref{fig:sigplot2}.} On this visual both the reference signature and the comparison signature are plotted.
 The reference signature is aligned with the comparison signature based on the congruent registration position.
@@
 -->
-
-```{r, echo=TRUE, eval=TRUE,  out.width="300px", fig.cap="  \\hh{ Could you make the cnsidered segments visible, maybe by zebra-striped rectangles in the background?
-XXX} The dark grey line shows the comparison signature; the red line shows the reference signature.
-Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.
-"}
-sig.plot$signature_shift_plot
-#knitr::include_graphics("img/sigplot2.png", dpi = 100)
-```
 

### 2021-04-29 CMPSpaper_writing/CMPSpaper_writing.Rmd
found the place to substitute the ```{=latex}
add other codefig plots

@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, message=FALSE}
 library(knitr)
+library(tidyverse)
+library(bulletxtrctr)
 
@@
   if (!is.null(options$codefig)) {
-    return(sprintf("%s%s\n%s", before, main, after))
+    main <- gsub("```","", main)
+    main <- gsub("=latex","", main)
+    return(sprintf("%s\n%s\n%s", before, main, after))
   } else {
@@
 
-```{r eval=FALSE}
-dframe %>% 
-  ggplot(aes(x = land1, y = land2, fill = CMPS.score)) +
-    geom_tile() +
-    scale_fill_gradient2(low="darkgrey", high = "darkorange", mid=6) +
-    geom_text(aes(label=CMPS.score))
+```{r eval=TRUE, echo=FALSE}
 
+lands <- unique(bullets$bulletland)
+
+comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
+                          stringsAsFactors = FALSE)
+
+comparisons <- comparisons %>% mutate(
+  aligned = purrr::map2(.x = land1, .y = land2, 
+                        .f = function(xx, yy) {
+                          land1 <- bullets$sigs[bullets$bulletland == xx][[1]]
+                          land2 <- bullets$sigs[bullets$bulletland == yy][[1]]
+                          land1$bullet <- "first-land"
+                          land2$bullet <- "second-land"
+
+                          sig_align(land1$sig, land2$sig)
+                        }))
+
+comparisons <- comparisons %>% 
+  mutate(cmps = aligned %>% purrr::map(.f = function(a) {
+    extract_feature_cmps(a$lands$sig1, a$lands$sig2, include = "full")
+  }))
+
+comparisons <- comparisons %>% 
+  mutate(
+    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
+    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
+  )
+
+# dframe <- comparisons %>% select(land1, land2, cmps_score)
+# 
+# dframe %>% 
+#   ggplot(aes(x = land1, y = land2, fill = cmps_score)) +
+#   geom_tile() +
+#   scale_fill_gradientn(
+#     colors=c("darkgrey","darkorange")
+#   ) +
+#   geom_text(aes(label=cmps_score)) +
+#   theme_bw() + 
+#   coord_flip()
+
+comparisons <- comparisons %>%
+  mutate(
+    bulletA = gsub("(\\d)-\\d", "\\1", land1),
+    landA = gsub("\\d-(\\d)", "\\1", land1),
+    bulletB = gsub("(\\d)-\\d", "\\1", land2),
+    landB = gsub("\\d-(\\d)", "\\1", land2)
+  )
+
+# comparisons %>%   
+#   group_by(bulletA, bulletB) %>% tidyr::nest() %>%
+#   mutate(
+#     cmps_max_bar = data %>% purrr::map_dbl(
+#       .f = function(d) max(compute_average_scores(land1 = d$landA,
+#                                                   land2 = d$landB,
+#                                                   d$cmps_score)))
+#   )
+
+dframe <- comparisons %>% select(-aligned, -cmps)
 ```
 
-```{r}
-#      [,1] [,2] [,3] [,4] [,5] [,6]
-# [1,]    2    3    2    3    1    2
-# [2,]    2    1   17    1    2    3
-# [3,]    1    1    3   14    2    2
-# [4,]    2    1    1    1   10    1
-# [5,]    2    2    1    1    1   15
-# [6,]   16    3    1    2    1    1
+```{r, echo=FALSE}
+dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + geom_tile() + 
+  scale_fill_gradient2(low = "gray80", high = "darkorange", midpoint = 6) + 
+  facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
+  ylab("Land A") + theme(aspect.ratio = 1) +
+  geom_text(aes(label=cmps_score)) +
+  theme_bw()
 ```
+
+<!-- ```{r} -->
+<!-- #      [,1] [,2] [,3] [,4] [,5] [,6] -->
+<!-- # [1,]    2    3    2    3    1    2 -->
+<!-- # [2,]    2    1   17    1    2    3 -->
+<!-- # [3,]    1    1    3   14    2    2 -->
+<!-- # [4,]    2    1    1    1   10    1 -->
+<!-- # [5,]    2    2    1    1    1   15 -->
+<!-- # [6,]   16    3    1    2    1    1 -->
+<!-- ``` -->
 
@@
 
-<!--
-```{r, eval=FALSE}
-sig.plot$signature_shift_plot
-```
--->
-
 Other elements of this list are `seg_shift`, `sig_shift`, and `seg.pos`.
@@
 It not only takes the "full result" of `extract_feature_cmps`, but also takes an argument `seg.idx`, which indicates which segment to be inspected.
-For example, after checking `sig.plot$seg.pos` we noticed that segment 6 is not one of the congruent matching profile segments.
+For example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments.
 So we can set `seg.idx = 6` in order to have a closer look at segment 6 and why it disagrees with the congruent registration position.
-`cmps_signature_plot` also returns a list.
-Each element of this list is also a list and corresponds to one segment scale of this basis segment.
-
-```{r, eval=FALSE}
-seg.plot <- cmps_segment_plot(cmps_with_multi_scale, seg.idx = 6)
-```
+`cmps_segment_plot` also returns a list, of which each element corresponds to one segment scale of this basis segment.
+Then for each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.
 
@@
 
-```{r, eval=FALSE}
+And the `scale_ccf_plot` plots the cross-correlation curve. We can see that 5 highest peaks are identified and marked on the plot.
+
+\begin{figure}
+\begin{subfigure}[t]{\textwidth}
+\caption{\label{fig:segplot}segment\_plot for segment 6 at scale 1.
+The original position of segment 6 is indicated by the solid black line.
+Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
+```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
+seg.plot <- cmps_segment_plot(
+  cmps_with_multi_scale, seg.idx = 6
+  )
 seg.plot[[1]]$segment_plot
 ```
+\end{subfigure}
+\begin{subfigure}[t]{\textwidth}
+\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1.
+The five highest peaks are marked by dots.
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone.
+We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment}
+```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
+seg.plot[[1]]$scale_ccf_plot
+```
+\end{subfigure}
+\caption{\label{fig:segplots}some text.}
+\end{figure}
 
-```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
+<!-- ```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
 The original position of segment 6 is indicated by the solid black line.
 Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.
-"}
-knitr::include_graphics("img/segplot1.png", dpi = 100)
-```
+"} -->
+<!-- knitr::include_graphics("img/segplot1.png", dpi = 100) -->
+<!-- ``` -->
 
-And the `scale_ccf_plot` plots the cross-correlation curve. We can see that 5 highest peaks are identified and marked on the plot.
-
-```{r, eval=FALSE}
-seg.plot[[1]]$scale_ccf_plot
-```
-
-```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1.
+<!-- ```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1.
 The five highest peaks are marked by dots.
 The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone.
-We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"}
-knitr::include_graphics("img/segplot2.png", dpi = 100)
-```
+We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"} -->
+<!-- knitr::include_graphics("img/segplot2.png", dpi = 100) -->
+<!-- ``` -->
 
@@
 
-```{r, eval=FALSE}
+\begin{figure}
+\begin{subfigure}[t]{\textwidth}
+\caption{\label{fig:segplot3}put segment\_plot and scale\_ccf\_plot of all scales together.
+We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
+Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
+Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
+```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
 library(ggpubr)
 
-ggarrange(plotlist = unlist(seg.plot, recursive = FALSE),
-          ncol = 2, nrow = 3)
+ggarrange(
+  plotlist = 
+    unlist(seg.plot, 
+           recursive = FALSE),
+  ncol = 2, 
+  nrow = 3)
 ```
+\end{subfigure}
+\caption{\label{fig:seg_all} some text.}
+\end{figure}
 
-```{r, echo=FALSE, out.width="400px", fig.cap="put segment\\_plot and scale\\_ccf\\_plot of all scales together.
+<!-- ```{r, echo=FALSE, out.width="400px", fig.cap="put segment\\_plot and scale\\_ccf\\_plot of all scales together.
 We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
 Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
-Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."}
-knitr::include_graphics("img/segplot3.png", dpi = 100)
-```
+Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."} -->
+<!-- knitr::include_graphics("img/segplot3.png", dpi = 100) -->
+<!-- ``` -->
 

### 2021-04-29 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of questions

--- 2021-04-23 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 
-Conceptually, the CMPS algorithm consists of \hh{three main} steps:
+Conceptually, the CMPS algorithm consists of three main steps:
 
 1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
-The command `get_segs(x, len=50)` implements this step:  it takes a bullet signature  in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
+The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
 
 2. **register each basis segment on the comparison signature:** 
-Calculate the cross-correlation curve between a basis segment and the comparison signature (using function `get_ccf4`).
-A position is considered "good" \wj{if this position results in a peak in the cross-correlation between the basis segment and the comparison}
+Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)`.
+A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
 <!-- the cross-correlation between the basis segment and the comparison is above a pre-defined threshold.  -->
@@
     2.1.
-**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of the \wj{top 5 highest peaks (if `npeaks.set = 5`) in the cross-correlation curve}.
+**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of the top 5 highest peaks (if `npeaks.set = 5`) in the cross-correlation curve.
 Small segment lengths might indicate false positive peaks.
@@
 This process can be repeated multiple times.
-In the last round, only one highest peak should be identified.
+In the last round, only one highest peak should \hh{XXX should?
+this is ambiguous.
+What happens if no peak or multiple peaks are found?} be identified.
 If the same or 'similar enough' (see step 3) position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
@@
 3. **determine the congruent registration position**:
-candidate positions across different segments are compared using a small tolerance \wj{parameter `Tx`} and basis segments with a congruent registration position are determined.
+candidate positions across different segments \hh{XXX how is this done in situation 2.1?
+} are compared using a small tolerance \wj{parameter `Tx`} and basis segments with a congruent registration position are determined.
 These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of the comparison.
@@
 
-```{r, eval=FALSE}
-seg.plot <- cmps_segment_plot(cmps_with_multi_scale, seg.idx = 6)
-```
-
 Take the first element of `seg.plot` as an example, it corresponds to the first segment scale (the original scale) of the 6th basis segment and carries two plots, `segment_plot` and `scale_ccf_plot`.
@@
 
-```{r, eval=FALSE}
+\begin{figure}[htb]
+```{r, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE, fig.cap=" "}
+#knitr::include_graphics("img/segplot1.png", dpi = 100)
+seg.plot <- cmps_segment_plot(
+  cmps_with_multi_scale, seg.idx = 6)
 seg.plot[[1]]$segment_plot
 ```
-
-```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
+\caption{\label{segplot} segment\_plot for segment 6 at scale 1.
 The original position of segment 6 is indicated by the solid black line.
-Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.
-"}
-knitr::include_graphics("img/segplot1.png", dpi = 100)
-```
+Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
+\end{figure}
 

### 2021-04-29 CMPSpaper_writing/CMPSpaper_writing.Rmd
small code, dpi included in options

@@
   out.width = "\\textwidth",
-  fig.align = "center"
+  fig.align = "center",
+#  cache=TRUE,
+  dpi = 100
 )
@@
 \\begin{adjustbox}{valign=t}
-\\begin{minipage}{.49\\textwidth}\n"
+\\begin{minipage}{.39\\textwidth}\n"
   after <-
@@
 \\end{minipage}
-\\begin{minipage}{.49\\textwidth}",
+\\begin{minipage}{.59\\textwidth}",
     paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
@@
     main <- gsub("=latex","", main)
+    main <- paste0("{\\small ", main, "}")
     return(sprintf("%s\n%s\n%s", before, main, after))
@@
 Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)`.
+\hh{XXX position is really the lag - i.e.
+we can compare lags across  different segments.}
 A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
@@
 dframe <- comparisons %>% select(-aligned, -cmps)
+
+dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
+
 ```
@@
 ```{r, echo=FALSE}
-dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + geom_tile() + 
-  scale_fill_gradient2(low = "gray80", high = "darkorange", midpoint = 6) + 
+dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + 
+  geom_tile() + 
+  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
+  scale_colour_manual("Source", values="darkorange") +
   facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
@@
   geom_text(aes(label=cmps_score)) +
-  theme_bw()
+  theme_bw() +
+  theme(aspect.ratio = 1)
 ```
@@
 seg.plot <- cmps_segment_plot(
-  cmps_with_multi_scale, seg.idx = 6
+  cmps_with_multi_scale, 
+  seg.idx = 6
   )
@@
 \begin{figure}
-\begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot3}put segment\_plot and scale\_ccf\_plot of all scales together.
-We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
-Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
-Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
 ```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
@@
 ```
-\end{subfigure}
-\caption{\label{fig:seg_all} some text.}
+\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all scales together.
+We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
+Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
+Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
 \end{figure}

### 2021-05-03 CMPSpaper_writing/CMPSpaper_writing.Rmd
tiles plot

@@
 
-```{r, echo=FALSE}
-dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + 
+```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
+dframe <- dframe %>% mutate(
+  landA = paste0("L", landA),
+  landB = paste0("L", landB),
+  landB = factor(landB, levels = paste0("L", c(2:6,1))),
+  bulletA = paste0("Bullet ", bulletA),
+  bulletB = paste0("Bullet ", bulletB)
+)
+
+dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
   geom_tile() + 
@@
   scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
-  ylab("Land A") + theme(aspect.ratio = 1) +
+  facet_grid(bulletB ~ bulletA) + xlab("Land A") + 
+  ylab("Land B") + theme(aspect.ratio = 1) +
   geom_text(aes(label=cmps_score)) +

### 2021-05-06 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edit in file, maor update of pandoc and tex

@@
 
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
 library(knitr)
@@
 \hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
-\hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.} 
+  \hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
+Low scores between pairs of signatures are attributed to different source pairs.}
   \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
@@
 
-```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
+```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all pairwise comparisons of the six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
 dframe <- dframe %>% mutate(
@@
 
-\hh{XXX Could we move the code into the corresponding figure and show the relevant pieces side by side?
-I'm thinking of examples similar to p.38 in https://journal.r-project.org/archive/2017/RJ-2017-023/RJ-2017-023.pdf}
-
-\begin{figure}
+\begin{figure}[hbt]
 \begin{subfigure}[t]{\textwidth}

### 2021-05-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
algorithm description

@@
 
-2. **register each basis segment on the comparison signature:** 
-Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)`.
-\hh{XXX position is really the lag - i.e.
-we can compare lags across  different segments.}
-A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
-<!-- the cross-correlation between the basis segment and the comparison is above a pre-defined threshold.  -->
+2.
+**identify candidate positions** For each basis segment a set of candidate positions on the reference signature is identified based on the segment's similarity to the reference.
+In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
+In case multiple segment lengths are considered, the length of each basis segment is doubled and these two steps are repeated.
+Only when candidate positions coincide (or are similar enough), they are  considered further.
+
+    2.1 **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
+\hh{The position indicates the lag by which a base segment is moved with respect to its original placement.} A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
+
+    2.2 **Correlation peaks** The parameter `npeaks.set` determines the number of candidate positions and which strategy to  use to combine candidates: If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top 5 peaks in the correlation coefficient curve are identified as candidates  for registration.
+
+    2.3  **Multiple-length segments** If  `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding 5 peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
+Note that in \hh{cite original  paper}  the last element of `npeaks.set` in the multi segment lengths strategy is always set to be 1.
+
+<!--
 The best registration position is decided upon using a multi-peak inspection with or without different segment lengths:
-
-    2.1.
-**multi-peak inspection (without different segment lengths):** each basis segment identifies positions of the top 5 highest peaks (if `npeaks.set = 5`) in the cross-correlation curve.
-Small segment lengths might indicate false positive peaks.
-Therefore all 5 peaks are considered as candidates for the "best" registration position.
 
@@
 For example, if we set `npeaks.set = c(5, 3, 1)`, 5 peaks will be identified in the first round, 3 peaks in the second round, and 1 peak in the final round.}
+-->
 
 3. **determine the congruent registration position**:
-candidate positions across different segments \hh{XXX how is this done in situation 2.1?
-} are compared using a small tolerance \wj{parameter `Tx`} and basis segments with a congruent registration position are determined.
-These segments are called the "congruent matching profile segments" (CMPS), and the number of CMPS is the CMPS score of the comparison.
-
-<!-- we conduct the "multi-peak inspection at different segment lengths".
-After having the multi-peak inspection for a basis segment of its original length, we then double the segment length by including profiles of half the current length -->
-
-<!-- If the reference profile and the comparison profile matches perfectly, every basis segment should vote for exactly the same registration position.  -->
-
-<!-- compute the cross-correlation function between each basis segment and the comparison profile; -->
+each candidate position corresponding to each of the basis segments gets one `vote`.
+Votes for candidate positions within a tolerance of `Tx` are tallied and the position with the highest number of votes gets chosen as the *congruent registration position*.
+Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
+The total number of CMPS is the CMPS score of the comparison.
 
@@
 * `seg_length` specifies the length of basis segments [(in mm?)] mentioned in step 1; 
-* `npeaks.set` determines the number of peaks and whether the function uses the multi segment lengths strategy.
-If `npeaks.set` is a numeric vector of length 1, for example `npeaks.set = c(5)`, then the function will not use multi segment lengths and find 5 peaks in the correlation coefficient curve for each basis segment; on the other hand, if the vector length of `npeaks.set` is larger than 1, for example `npeaks.set = c(5, 3, 1)`, the function will take advantage of the multi segment lengths strategy, finding 5 peaks in the original scale, 3 peaks in the second scale and 1 peak in the third scale.
-Note that if the multi segment lengths strategy is being used, the last element of `npeaks.set` should always be 1.
 * `Tx` gives the size of tolerance zone mentioned in step 4;
+* `npeaks.set` is a (vector of) integer value(s). The parameter determines the number of candidate positions and which strategy to  use to combine candidates.
 * `include` determines what information should be included in the function output.
@@
 
-**Install**
+**Installation**
 
-The CMPS package is/not published on CRAN, and can be install and called by
+The CMPS package is (not) publicly available from CRAN, and can be installed by
 
 ```{r, eval=FALSE}
-install.packages(CMPS)
+install.packages("CMPS")
 ```
 
-The development version can be installed by using
+The development version is available from Github can be installed by using
 
 ```{r, eval=FALSE}
-# install.packages("devtools") 
-devtools::install_github("willju-wangqian/CMPS")
+# install.packages("remotes") 
+remotes::install_github("willju-wangqian/CMPS")
 ```
 
-**Examples**
+**An Example**
 
 The `CMPS` package contains a simple example to illustrate the basic usage of the package.
-The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 (Each bullet has six lands).
-The procedure for generating signatures from 3D bullet lands in x3p format is (algorithmic) [and has been discussed above].
-And these two bullets are known to come from the same gun barrel, so for the 36 land-by-land comparisons, 6 of them are KM (known matching) comparisons and 30 are KNM (known non-matching) comparisons.
-To access the example data, one can use
+The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [@hamby].
+The procedure for generating signatures from high-resolution 3D topographic scans of bullet lands used here follows the methodology described in @aoas (as discussed above).
+The two bullets under consideration here are known to have been fired from the same gun barrel, so for the 36 land-by-land comparisons, 6 comparison are from same-source pairs (known matches) while 30 are from different-source pairs (known non-matches).
+To access the example data, we use
 
@@
 
-And anyone who is interested in the data source can find it in `bullets$source`.
-One can use these links to download the original x3p files from NIST Ballistics Toolmark Research Database [@nistdb].
-`bulletxtrctr::read_bullet(urllist = bullets$source)`
+The `bullets` object is a data frame with 12 rows.
+Each row contains one signature.
+`bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].
 
@@
 
-`extract_feature_cmps` integrates all steps of the CMPS algorithm. It takes two bullet signatures and computes the CMPS score.
+`extract_feature_cmps` integrates all steps of the CMPS algorithm. It takes two bullet signatures and computes the CMPS score. Here, we are using the default values for all of the parameters:
 
@@
 
-The comparison between "bullet 1 - land 2" and "bullet 2 - land 3" is one of the KM comparisons. We can compute the CMPS score using two versions of the CMPS algorithm.
+The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects sigs2 and sig 1, respectively.
+This comparison is one of the KM comparisons.
+We compute the CMPS score using two versions of the CMPS algorithm:
 

### 2021-05-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
we don't need to align signatures before extracting cmps

@@
 
+\hh{How about you go into a description of the results from the function `extract\_feature\_cmps`?}
+
 We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.
 
-```{r eval=TRUE, echo=FALSE}
+```{r alternative, echo = FALSE}
+lands <- unique(bullets$bulletland)
 
+comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
+                          stringsAsFactors = FALSE)
+
+comparisons <- comparisons %>% 
+  left_join(bullets %>% select(bulletland, sig1=sigs),
+            by = c("land1" = "bulletland")) %>%
+  left_join(bullets %>% select(bulletland, sig2=sigs),
+            by = c("land2" = "bulletland"))
+
+comparisons <- comparisons %>% mutate(
+  cmps = purrr::map2(sig1, sig2, .f = function(x, y) {
+    extract_feature_cmps(x$sig, y$sig, include = "full")
+    })
+)
+
+comparisons <- comparisons %>% 
+  mutate(
+    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
+    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
+  )
+
+comparisons <- comparisons %>%
+  mutate(
+    bulletA = gsub("(\\d)-\\d", "\\1", land1),
+    landA = gsub("\\d-(\\d)", "\\1", land1),
+    bulletB = gsub("(\\d)-\\d", "\\1", land2),
+    landB = gsub("\\d-(\\d)", "\\1", land2)
+  )
+
+dframe <- comparisons %>% select(-sig1, -sig2)
+
+dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
+```
+
+```{r eval=FALSE, echo=FALSE}
 lands <- unique(bullets$bulletland)
@@
 
-# dframe <- comparisons %>% select(land1, land2, cmps_score)
-# 
-# dframe %>% 
-#   ggplot(aes(x = land1, y = land2, fill = cmps_score)) +
-#   geom_tile() +
-#   scale_fill_gradientn(
-#     colors=c("darkgrey","darkorange")
-#   ) +
-#   geom_text(aes(label=cmps_score)) +
-#   theme_bw() + 
-#   coord_flip()
-
 comparisons <- comparisons %>%
@@
 
-# comparisons %>%   
-#   group_by(bulletA, bulletB) %>% tidyr::nest() %>%
-#   mutate(
-#     cmps_max_bar = data %>% purrr::map_dbl(
-#       .f = function(d) max(compute_average_scores(land1 = d$landA,
-#                                                   land2 = d$landB,
-#                                                   d$cmps_score)))
-#   )
-
-dframe <- comparisons %>% select(-aligned, -cmps)
+comparisons0 <- comparisons
+dframe0 <- comparisons %>% select(-aligned, -cmps)
 

### 2021-05-19 CMPSpaper_writing/CMPSpaper_writing.Rmd
tiny update

@@
 1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
-The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`.
+The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred as "basis segments".
 

### 2021-05-20 CMPSpaper_writing/CMPSpaper_writing.Rmd
update revision for the algorithm and its following sections

@@
 @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
-Although @cmps conceptually described the CMPS algorithm  in their paper, \hh{the authors did not release an implementation of their method}.
+Although @cmps conceptually described the CMPS algorithm  in their paper, the authors did not release an implementation of their method.
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm  to use, review, and  improve.
@@
 
-An important task of firearm examination is \hh{to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
-Here, in particular, we are interested } to determine whether two bullets were fired from the same gun barrel.
-\hh{Assessing the similarity between two bullets is based on a comparison of  striation marks acquired during the firing process as bullets are propelled through the barrel. }
-\hh{Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope.
-This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].}
-<!--It is achievable because lands in a gun barrel create striation marks on the bullet during the firing process, and it is believed that the same gun barrel will create highly similar striation marks on the bullets it fired.
-Typically the striation marks are created by lands in a barrel, so the striation marks are also sometimes refered as land engravings, and the areas the marks occupy are called land engraved areas (LEA).
-However, in recent years people became more cautious about firearms identification, and criticism of its subjective methodology arose.--> A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases [@nistdb] and develop frameworks and algorithms that bring an objective and quantitative assessment into the field \hh{XXX cite some of these efforts - make sure to say that it is not an exhaustive list}.
-\hh{XXX The bullet signatures weren't mentioned before - make sure to include that there is a whole section that discusses how bullet signatures are extracted from scans.}
-\wj{The notion of bullet signatures is one of the results of these efforts.
+An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
+Here, in particular, we are interested to determine whether two bullets were fired from the same gun barrel.
+Assessing the similarity between two bullets is based on a comparison of  striation marks acquired during the firing process as bullets are propelled through the barrel.
+Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope.
+This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].
+
+A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940;@cmps].
+\wj{Note that this is not an exhaustive list of these efforts.} The notion of bullet signatures is one of the results of these efforts.
 Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
 Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
-}
 In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, and present results of applying our implementation to real data.
@@
 The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019],  in particular, Hamby set 252 and Hamby set 44. 
-For each Hamby set, a total of 35 bullets is fired from ten \hh{consecutively manufactured} Ruger P-85 pistol barrels.
-\hh{Two bullets are fired from each barrel, making up a set of 20 reference bullets.
+For each Hamby set, a total of 35 bullets is fired from ten consecutively manufactured Ruger P-85 pistol barrels.
+Two bullets are fired from each barrel, making up a set of 20 reference bullets.
 An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant.
 The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from.
-The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands \hh{as shown in \autoref{fig:bullet}}.
+The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}.
 During the firing process, grooves and lands are engraved on a bullet.
 Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison.
-For algorithmic purposes, }
-3D topographical images \hh{land engraved areas} were obtained and stored in  x3p format (XML 3-D Surface Profile).
+For algorithmic purposes,
+3D topographical images land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile).
 The x3p format provides a standard way of exchanging 2D and 3D profile data.
@@
 Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
-Hamby set 44 was scanned \hh{at the Roy J Carver High-Resolution microscopy lab at Iowa State.
-These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu per pixel}.
+Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State.
+These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu per pixel.
 Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].
@@
 In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
-`x3ptools` \hh{is a package to read, write, and generally, process } x3p files.
-\hh{The `bulletxtrctr` package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.}
-<!--In the case of Hamby set 252, we need to convert the measurements of x3p files from meters to microns (`x3ptools::x3p_m_to_mum`) and rotate x3p files to make the long axis horizontal (`x3ptools::x3p_rotate`).-->
-  <!--\hh{it's land **engraved** areas, not impressions (that was wrong in Eric's first paper).
-Impressions are marks from impacts, such as the hit of a hammer or the hit from the breech face.
-Engravings are scratch marks.}-->
-  \hh{\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.}
-\autoref{fig:process}(a) shows a \hh{rendering of a 3d scan of a } bullet land  engraved area.
-The raised portion of the surface \hh{on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs)}, \hh{the middle area shows a land-engraved area (LEA) with well expressed} striation marks.
+`x3ptools` is a package to read, write, and generally, process x3p files.
+The `bulletxtrctr` package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
+
+\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.
+\autoref{fig:process}(a) shows a rendering of a 3d scan of a bullet land  engraved area.
+The raised portion of the surface on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs), the middle area shows a land-engraved area (LEA) with well expressed striation marks.
 The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
-<!--\hh{The next section is at an awkward level of detail - there's lots of details, but without the parameter settings it is still not a reproducible description.
-Could you instead describe things conceptually, and then link to the code that does this particular image?} -->
+
 The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
-<!--Then we can acquire the crosscut data (`ccdata`) of the scan at this height.
---> \hh{XXX passive voice for things that are not part of this paper :)}
 Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
@@
 However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
-\wj{Bullet profiles are \hh{shown in panels (b), (c), and (d) of \autoref{fig:process}}, while \autoref{fig:process}(f) shows the corresponding bullet signature.}
-\hh{Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
-To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],}   `bulletinspectR` to identify and correct those errors.
+Bullet profiles are shown in panels (b), (c), and (d) of \autoref{fig:process}, while \autoref{fig:process}(f) shows the corresponding bullet signature.
+Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
+To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],  `bulletinspectR` to identify and correct those errors.
 \hh{An example of the extraction process with corresponding code and parameter settings can be found at XXX.}
-Note that \hh{the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.}
-
-<!-- `bulletxtrctr::x3p_crosscut_optimize` can be used to determine an ideal \hh{XXX ideal is a dangerous word} height, and `bulletxtrctr::x3p_crosscut` can be used to acquire the crosscut data (`ccdata`).
-\autoref{fig:process}(c) shows the typical pattern of the crosscut data, where "wedges" can be found on the left and right side and indicate the boundary between the land engraving and the groove engraving.
-`bulletxtrctr::cc_locate_grooves` is used to locate and chop these wedge areas so that only the curve of the land engraving in the middle is kept.
-With the groove engravings excluded, we then use `bulletxtrctr::cc_get_signature` to smooth out the land engraving curvature using LOESS (locally estimated scatter plot smoothing) [@loess] and obtain the bullet signature.
-\autoref{fig:process} illustrates this framework.
-Sometimes the algorithm in our framework cannot determine the ideal location of the crosscut or the grooves due to the deformation of a bullet, so we also developed a `R` Shiny App called `bulletinspectR` to identify and correct those errors.
-Note that NIST researchers used a different way of getting the bullet signatures in their paper [@cmps].
--->
+Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
 
@@
 The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference   and  for each segment find the "best" registration position on the comparison  (the other bullet signature) with respect to their cross-correlation values.
-\hh{From a comparison of these registration positions, a } **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
-  \hh{High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
-Low scores between pairs of signatures are attributed to different source pairs.}
+From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
+  High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.
   \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
@@
 'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'}
- The CMPS algorithm can assist firearm examiners with drawing a conclusion \hh{about the source of a comparison pair}.
-\hh{Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the } CMPS algorithm.
+ The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
+Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
 Thus, in this paper we present an open-source implementation of the CMPS algorithm \hh{in the R package CMPS available from XXX github / CRAN}. 
@@
 
-\hh{XXX could you make this example functional?}
 ```{r, eval=FALSE}
@@
 
-\wj{In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 2.}
-
-<!-- In the example in section "Implementation" we see that two bullet signatures coming from the same source get a CMPS score of X, while two signatures coming from different sources get a CMPS score of Y.
--->
+In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 1.
 
@@
 
+\wj{the followings are revised}
+
 2.
-**identify candidate positions** For each basis segment a set of candidate positions on the reference signature is identified based on the segment's similarity to the reference.
-In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
+**identify candidate positions:** For each basis segment a set of candidate \wj{registration XXX} positions on the comparison signature is identified based on the segment's similarity to the comparison.
+In a first step, the cross-correlation function of the segment to the comparison is calculated, then a number of positions with high correlation values are identified as candidate positions.
 In case multiple segment lengths are considered, the length of each basis segment is doubled and these two steps are repeated.
 Only when candidate positions coincide (or are similar enough), they are considered further.
+Figure \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
 
-    2.1 **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
-\hh{The position indicates the lag by which a base segment is moved with respect to its original placement.} A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
+    + **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
+The position indicates the lag by which a basis segment is moved with respect to its original placement.
+A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
 
-    2.2 **Correlation peaks** The parameter `npeaks.set` determines the number of candidate positions and which strategy to  use to combine candidates: If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top 5 peaks in the correlation coefficient curve are identified as candidates  for registration.
+    + **Correlation peaks:** The parameter `npeaks.set` in `extract_feature_cmps(...)` determines the number of candidate positions and which strategy to  use to combine candidates: If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top 5 peaks in the cross-correlation curve are identified as candidates for registration.
+This strategy is referred as "multi-peak inspection" in @cmps.
 
-    2.3  **Multiple-length segments** If  `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding 5 peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
-Note that in \hh{cite original  paper}  the last element of `npeaks.set` in the multi segment lengths strategy is always set to be 1.
+    +  **Multiple-length segments:** If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding top 5 peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
+Figure \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+If a single position (with a tolerance zone determined by `Tx`) results in a top peak in the cross-correlation curve in all three scales, it is called a consistent correlation peak and identified as a candidate for registration.
+Note that in @cmps the last element of `npeaks.set` in the multi segment lengths strategy is always set to be 1.
+Additionally, this strategy is also referred as "multi-peak inspection at different segment lengths" in @cmps.
 
-<!--
-The best registration position is decided upon using a multi-peak inspection with or without different segment lengths:
+\wj{revised end}
 
-    2.2.
-**multi-peak inspection with different segment lengths:** for this version of the CMPS algorithm, each basis segment finds only one "best" registration position.
-This "best" registration position can be found by conducting multi-peak inspection multiple rounds.
-The first round is executed as stated in step 2.1.
-After that first round, the segment length is increased, a new cross-correlation curve is computed, and another set of  peaks in the cross-correlation curve is identified together with the candidate positions.
-Typically, fewer number of peaks are identified in this round (because the increased segment length reduces the chance of false positive peaks).
-This process can be repeated multiple times.
-In the last round, only one highest peak should \hh{XXX should?
-this is ambiguous.
-What happens if no peak or multiple peaks are found?} be identified.
-If the same or 'similar enough' (see step 3) position can be identified for all different segment length, this position will be selected as the "best" registration position and is called the "consistent correlation peak" (ccp).
-\wj{In order to use this version of the CMPS algorithm, we set `npeaks.set` as a numeric vector of multiple values.
-For example, if we set `npeaks.set = c(5, 3, 1)`, 5 peaks will be identified in the first round, 3 peaks in the second round, and 1 peak in the final round.}
--->
-
-3. **determine the congruent registration position**:
-each candidate position corresponding to each of the basis segments gets one `vote`.
+3.
+**determine the congruent registration position:** Each candidate position corresponding to each of the basis segments gets one `vote`.
 Votes for candidate positions within a tolerance of `Tx` are tallied and the position with the highest number of votes gets chosen as the *congruent registration position*.
@@
 
-\hh{In the CMPS package, these three steps are implemented using a set of key functions:}
+In the CMPS package, these three steps are implemented using a set of key functions:
 
-<!-- step 3) if the multi segment lengths strategy is being used, each basis segment would increase its length and compute a new cross-correlation function with the comparison profile in order to identify a potential “consistent correlation peak”; if the multi segment lengths strategy is not being used, each segment would then find 5 peaks in its cross-correlation function; -->
+\wj{the followings are revised}
 
-* `get_seg_scale` takes a basis segment and increases its segment length. `scale=1` gives the original length of the basis segment. Increasing `scale` by 1 will double the segment length.
+* `get_seg_scale(segments, nseg, scale = 2)` takes a basis segment and increases its segment length.
+`segments` is a list containing all basis segments, generated by the function `get_segs(...)`; `nseg` is an integer indicating which basis segment the function should work with.
+`scale=1` gives the original length of the basis segment.
+Increasing `scale` by 1 will double the segment length.
 
-* `get_ccr_peaks` takes a segment and the comparison signature, then computes the correlation coefficient curve between them and finds peaks on the correlation coefficient curve.
-The number of peaks detected is equal to `npeaks`.
-And we are using `rollapply` to find peaks on the curve effectively.
+* `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the comparison signature and finds peaks in the cross-correlation curve.
+The number of peaks detected is equal to `npeaks`, which is an integer.
+`segments`, `seg_scale`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the comparison signature.
+If the multi segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each scale of the basis segment.
+The resulting list is called `ccr.list`.
 
-* `get_ccp` checks if the "consistent correlation peak" exists under the framework of multi segment lengths strategy.
-Since we are requiring the highest segment scale identifies only one peak, we just need to check if this peak shows any "consistency".
-In other words, we check if this peak is also identified as a peak in other segment scales.
+* `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak" (defined in algorithm step 2) under the framework of multi segment lengths strategy.
+`ccr.list` is described in the previous bullet point, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
 
-* `get_CMPS` considers all basis segments and their identified peak positions to determine the congruent registration position.
-The goal is to find a peak position that is agreed by the most basis segments.
-Since small errors are allowed, a tolerance zone would serve as a selection window.
-`get_CMPS` will move this selection window from left to right and go through all possible positions and check the number of basis segment that identifies a peak in the selection window for each position.
-Since we are moving this tolerance zone from left to right one unit a time, some consecutive positions are expected to have the same number of basis segments.
-[?.?] In that case the median of all tied and consecutive positions will be chosen as the congruent registration position.
-As long as the congruent registration position is determined, the number of basis segments that identify a peak in this position is the CMPS score.
+* `get_CMPS(input.ccp, Tx = 25)` tallies votes from all basis segments and determines the congruent registration position.
+A position "receives" a vote from a basis segment if this basis segment identifies this position or a closed-enough position (within a tolerance zone defined by `Tx`) as a candidate registration position in algorithm step 2.
+The goal is to find a shift in registration position that is agreed by the most number of basis segments, so the position receiving the most number of votes is the congruent registration position.
+In case of ties the middle position is taken as the congruent registration position.
+Basis segments with the congruent registration position identified are called "congruent matching profile segments" (CMPS).
+The total number of CMPS is the CMPS score.
 
-Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified in step 3, and the length of the tolerance zone in step 3.
+\wj{revised end}
+
+Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified on each scale level in step 2, and the length of the tolerance zone in both step 2 and 3.
 In our implementation of the CMPS algorithm we took the original CMPS paper [@cmps] as the reference to determine the default values of these parameters.
-The main function that follows the CMPS algorithm is called `extract_feature_cmps`. It consists of all steps of the algorithm and receives parameters from the users.
+Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.
 
-* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in step 1; 
-* `Tx` gives the size of tolerance zone mentioned in step 4;
-* `npeaks.set` is a (vector of) integer value(s). The parameter determines the number of candidate positions and which strategy to  use to combine candidates.
-* `include` determines what information should be included in the function output.
-By default, `include = NULL` and the function output will only contain the `CMPS.score`.
-However, besides the most important `CMPS.score`, there are other pieces of information related to the CMPS score that one might be interested in, such as
+The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Default values and some explanations of its parameters are as following:
+
+```{r, eval=FALSE}
+extract_feature_cmps(
+  x,
+  y,
+  seg_length = 50,
+  Tx = 25,
+  npeaks.set = c(5, 3, 1),
+  include = NULL
+)
+```
+
+\wj{the followings are revised}
+* `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
+* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1; 
+* `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3;
+* `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified;
+* `include` determines the output of the function.
+Besides the `CMPS.score`, many details of the comparison might be used to understand how the `CMPS.score` is computed.
+By default, `include = NULL` and the function output will only contain the `CMPS.score`; `include` can also be (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
+if `"full_result"` (or its abbreviation) is specified, the ouput will include everything listed below.
   - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
   - `congruent.pos`: the congruent registration position;
-  - `congruent.seg.idx`: the indices of all basis segments that agree with the congruent registration position;
-  - `segments`: the list of basis segments used for the computation of CMPS score;
-  - `parameters`: all inputs of `extract_feature_cmps`
-For all possible options of `include`, please check the documentation of `extract_feature_cmps` or using `?extract_feature_cmps`.
-If we want everything to be included in the output, we can use `include = full_result`.
-These additional pieces of information are helpful in terms of understanding how we obtained such CMPS score.
+  - `congruent.seg.idx`: the indices of all congruent matching profile segments;
+  - `ccp.list`: a list showing identified candidate positions of all basis segments; 
+  - `pos.df`: a data frame containing all candidate positions and the number of votes they received;
+  - `segments`: a list containing all basis segments;
+  - `parameters`: a list containing all input arguments of `extract_feature_cmps`;
+
+For more details, please check the documentation of `extract_feature_cmps` or use `?extract_feature_cmps`.
+
+\wj{revised end}
 
@@
 
-The `bullets` object is a data frame with 12 rows.
-Each row contains one signature.
+`bullets$sigs` is a list of 12 numeric vectors corresponding to 12 bullet signatures.
 `bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].
 
-**extract_feature_cmps**
-
-`extract_feature_cmps` integrates all steps of the CMPS algorithm. It takes two bullet signatures and computes the CMPS score. Here, we are using the default values for all of the parameters:
-
-```{r, eval=FALSE}
-extract_feature_cmps(
-  x,
-  y,
-  seg_length = 50,
-  Tx = 25,
-  npeaks.set = c(5, 3, 1),
-  include = NULL
-)
-```
-
-The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects sigs2 and sig 1, respectively.
+The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects sigs2 and sigs1, respectively.
 This comparison is one of the KM comparisons.
@@
 
-We can also compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons.
+\wj{revised the following}
+Since `npeaks.set = c(5,3,1)`, `cmps_with_multi_scale` uses the multi segment lengths strategy.
+On the other hand, `cmps_without_multi_scale` doesn't use the multi segment lengths strategy, and each basis segment finds 5 candidate positions due to `npeaks.set = 5`.
+Since `include = "full_result"` the outputs of `extract_feature_cmps(...)` contain everything listed in the previous section.
+Moreover, as mentioned before, multi segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
+\wj{revised end}
+
+We can compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons as well.
 
@@
 
-```{r eval=FALSE, echo=FALSE}
-lands <- unique(bullets$bulletland)
-
-comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
-                          stringsAsFactors = FALSE)
-
-comparisons <- comparisons %>% mutate(
-  aligned = purrr::map2(.x = land1, .y = land2, 
-                        .f = function(xx, yy) {
-                          land1 <- bullets$sigs[bullets$bulletland == xx][[1]]
-                          land2 <- bullets$sigs[bullets$bulletland == yy][[1]]
-                          land1$bullet <- "first-land"
-                          land2$bullet <- "second-land"
-
-                          sig_align(land1$sig, land2$sig)
-                        }))
-
-comparisons <- comparisons %>% 
-  mutate(cmps = aligned %>% purrr::map(.f = function(a) {
-    extract_feature_cmps(a$lands$sig1, a$lands$sig2, include = "full")
-  }))
-
-comparisons <- comparisons %>% 
-  mutate(
-    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
-    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
-  )
-
-comparisons <- comparisons %>%
-  mutate(
-    bulletA = gsub("(\\d)-\\d", "\\1", land1),
-    landA = gsub("\\d-(\\d)", "\\1", land1),
-    bulletB = gsub("(\\d)-\\d", "\\1", land2),
-    landB = gsub("\\d-(\\d)", "\\1", land2)
-  )
-
-comparisons0 <- comparisons
-dframe0 <- comparisons %>% select(-aligned, -cmps)
-
-dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
-
-```
-
 ```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all pairwise comparisons of the six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
@@
 ```
-
-<!-- ```{r} -->
-<!-- #      [,1] [,2] [,3] [,4] [,5] [,6] -->
-<!-- # [1,]    2    3    2    3    1    2 -->
-<!-- # [2,]    2    1   17    1    2    3 -->
-<!-- # [3,]    1    1    3   14    2    2 -->
-<!-- # [4,]    2    1    1    1   10    1 -->
-<!-- # [5,]    2    2    1    1    1   15 -->
-<!-- # [6,]   16    3    1    2    1    1 -->
-<!-- ``` -->
 
@@
 \end{figure}
-
-<!-- ```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1.
-The original position of segment 6 is indicated by the solid black line.
-Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.
-"} -->
-<!-- knitr::include_graphics("img/segplot1.png", dpi = 100) -->
-<!-- ``` -->
-
-<!-- ```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1.
-The five highest peaks are marked by dots.
-The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone.
-We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"} -->
-<!-- knitr::include_graphics("img/segplot2.png", dpi = 100) -->
-<!-- ``` -->
 

### 2021-05-24 CMPSpaper_writing/CMPSpaper_writing.Rmd
revised the section "Visualize and Understand CMPS results"

@@
 
-    + **Correlation peaks:** The parameter `npeaks.set` in `extract_feature_cmps(...)` determines the number of candidate positions and which strategy to  use to combine candidates: If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top 5 peaks in the cross-correlation curve are identified as candidates for registration.
+    + **Correlation peaks:** The parameter `npeaks.set` in `extract_feature_cmps(...)` determines the number of candidate positions and which strategy to  use to combine candidates: If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidates for registration.
 This strategy is referred as "multi-peak inspection" in @cmps.
 
-    +  **Multiple-length segments:** If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding top 5 peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
+    +  **Multiple-length segments:** If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
 Figure \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
@@
 Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.
-
-The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Default values and some explanations of its parameters are as following:
+The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
+Default values and some explanations of its parameters are as following:
 
@@
 The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
-\autoref{fig:sigplot} continues with the example above and take its results.
+Figure \autoref{fig:sigplots} shows the plots generated by the first graphing function, `cmps_signature_plot()`, and continues with the example above.
+`cmps_signature_plot()` takes the output of `extract_feature_cmps(..., include = "full_result")` and returns a list of 5 elements.
+It creates an overall impression of how the reference signature aligns with the comparison signature at the congruent registration position.
 
-`cmps_signature_plot` takes the "full result" of `extract_feature_cmps` (setting `include = "full_result"`) and returns a list of 5 elements.
+*   The first element is a plot called `segment_shift_plot`, which is shown in Figure \autoref{fig:sigplot}.
+On this plot only the congruent matching profile segments are plotted along with the comparison signature at the congruent registration position.
 
-The first element is `segment_shift_plot`.
-On this plot only basis segments that agree with the congruent registration position (i.e.
+<!-- basis segments that agree with the congruent registration position (i.e.
 the segments that are congruent matching profile segments) are plotted along with the comparison signature.
 When plotting, each of those basis segments will be shifted to the position where the basis segment obtains a cross-correlation peak and is within the tolerance zone of the congruent registration position.
+-->
+
+*   The second element is a plot called `signature_shift_plot`, which is shown in \autoref{fig:sigplot2}.
+On this visual both the reference signature and the comparison signature are plotted.
+The reference signature is aligned with the comparison signature based on the congruent registration position.
+And the congruent matching profile segments are highlighted with solid lines.
 
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot}The dark grey line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
+\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
 ```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot2}The dark grey line shows the comparison signature; the red line shows the reference signature.
-Solid part is the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
+\caption{\label{fig:sigplot2}The black line shows the comparison signature; the red line shows the reference signature.
+Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
 ```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
@@
 \end{subfigure}
-\caption{\label{sigplots}\hh{The resulting two figures signature plots. We need a summarizing sentence here.}}
+\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
 \end{figure}
 
-The second element is called `signature_shift_plot`.
-\hh{It is shown in \autoref{fig:sigplot2}.} On this visual both the reference signature and the comparison signature are plotted.
-The reference signature is aligned with the comparison signature based on the congruent registration position.
-And the congruent matching profile segments are highlighted.
+*   Other elements of this list are `seg_shift` and `sig_shift`.
+`sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
 
-Other elements of this list are `seg_shift`, `sig_shift`, and `seg.pos`.
-These elements are essentially used for generating visuals above but also provide insights about the best fitted position for each congruent matching profile segments and for the reference signature.
-`sig.plot$seg.pos` can also tell us which basis segments are the congruent matching profile segments.
+```{r, echo=TRUE, eval=TRUE}
+sig.plot$seg_shift
+```
 
-As `cmps_signature_plot` focuses on the signature level, on the other hand, `cmps_segment_plot` focuses on the segment level.
-It not only takes the "full result" of `extract_feature_cmps`, but also takes an argument `seg.idx`, which indicates which segment to be inspected.
-For example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments.
-So we can set `seg.idx = 6` in order to have a closer look at segment 6 and why it disagrees with the congruent registration position.
-`cmps_segment_plot` also returns a list, of which each element corresponds to one segment scale of this basis segment.
-Then for each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.
+<!-- These elements are essentially used for generating visuals above but also provide insights about the congruent registration position and the candidate positions found by each of the congruent matching profile segments.
+-->
+<!-- which basis segments are the congruent matching profile segments. -->
 
-Take the first element of `seg.plot` as an example, it corresponds to the first segment scale (the original scale) of the 6th basis segment and carries two plots, `segment_plot` and `scale_ccf_plot`.
+As `cmps_signature_plot()` focuses on the signature level, on the other hand, `cmps_segment_plot()` focuses on the segment level.
+It not only takes the "full result" of `extract_feature_cmps()`, but also takes an argument `seg.idx`, indicating which segment to be inspected.
+As shown in Figure \autoref{fig:segplots}, for example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments.
+So we can set `seg.idx = 6` in order to take a closer look at segment 6 and understand the reason why it disagrees with the congruent registration position.
+`cmps_segment_plot()` also returns a list, of which each element corresponds to one segment scale of this basis segment.
+Then at each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.
 
-Remember that when computing the CMPS score, we were using `npeaks.set = c(5, 3, 1)`.
+*   Figure \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at scale one (its original scale).
+Since when computing the CMPS score we used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()`, 5 peaks are identified in the cross-correlation curve at scale one, and segment 6 at scale one is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
+
+<!-- Take the first element of `seg.plot` as an example, it corresponds to the first segment scale (the original scale) of the 6th basis segment and carries two plots, `segment_plot` and `scale_ccf_plot`.
+-->
+<!-- Remember that when computing the CMPS score, we were using `npeaks.set = c(5, 3, 1)`.
 This means that for the first segment scale, 5 peaks are identified in the cross-correlation curve.
 `segment_plot` plots the 6th basis segment in its first scale at its original position as well as the positions where the basis segment obtains its 5 cross-correlation peaks.
+-->
 
-And the `scale_ccf_plot` plots the cross-correlation curve. We can see that 5 highest peaks are identified and marked on the plot.
+*   Figure \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at scale one.
+It shows the cross-correlation curve computed by the comparison signature and the scale-one basis segment 6.
+The five highest peaks are marked by dots on the curve.
 
@@
 The five highest peaks are marked by dots.
-The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone.
-We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment}
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in its highest segment scale; the blue dashed lines show the tolerance zone around the green dashed line.
+We can see here none of the five highest peaks at scale one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi segment lengths strategy.
+Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
 ```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
@@
 \end{subfigure}
-\caption{\label{fig:segplots}some text.}
+\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at scale one}
 \end{figure}
 
-Additionally, if we put `segment_plot` and `scale_ccf_plot` for all three segment scales together, we can have more insights about why segment 6 is not a congruent matching profile segment.
+Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment scales together, as shown in Figure \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
 
@@
 ```
-\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all scales together.
-We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
-Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
-Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
+\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three scales together.
+We are identifying five highest peaks at scale one, three peaks at scale two, and one peak at scale three since npeaks.set = c(5, 3, 1).
+The highest peak position at scale three is marked by the green dashed line across all segment scales, but it doesn't achieve the top five highest peaks at scale one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi segment lengths strategy.}
 \end{figure}
@@
 
-The red vertical dashed line indicates the congruent registration position.
-We can see that the segment 6 does obtain a peak near to the congruent registration position at scale two and scale three, respectively; however, this position doesn't give one of the five highest peaks at scale one.
+In Figure \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
+We can see that the basis segment 6 does obtain a peak near the congruent registration position at scale two and scale three, respectively; however, this position doesn't give one of the five highest peaks at scale one.
 As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi segment lengths strategy.
+The identified top five peaks at scale one are also examples of "false positive" peaks.
+The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at scale two and three by increasing the segment length, which justifies the usage of multi segment lengths strategy.
 

### 2021-05-26 CMPSpaper_writing/CMPSpaper_writing.Rmd
add file path for mac; revised the first section in Result

@@
 Only when candidate positions coincide (or are similar enough), they are considered further.
-Figure \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
+\autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
 
@@
     +  **Multiple-length segments:** If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
-Figure \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+\autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
 If a single position (with a tolerance zone determined by `Tx`) results in a top peak in the cross-correlation curve in all three scales, it is called a consistent correlation peak and identified as a candidate for registration.
@@
 
-We can compute the CMPS scores (using the multi segment lengths strategy) for all 36 land-by-land comparisons as well.
-
 ```{r alternative, echo = FALSE}
@@
 
-```{r tiles, echo=FALSE, fig.cap="Overview of all 36 CMPS scores resulting from a bullet-to-bullet comparison of all pairwise comparisons of the six lands on each bullet.", out.width=".7\\textwidth", fig.align="center"}
-dframe <- dframe %>% mutate(
-  landA = paste0("L", landA),
-  landB = paste0("L", landB),
-  landB = factor(landB, levels = paste0("L", c(2:6,1))),
-  bulletA = paste0("Bullet ", bulletA),
-  bulletB = paste0("Bullet ", bulletB)
-)
-
-dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
-  geom_tile() + 
-  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
-  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Land A") + 
-  ylab("Land B") + theme(aspect.ratio = 1) +
-  geom_text(aes(label=cmps_score)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-```
-
 **Visualize and Understand CMPS results**
@@
 The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
-Figure \autoref{fig:sigplots} shows the plots generated by the first graphing function, `cmps_signature_plot()`, and continues with the example above.
+\autoref{fig:sigplots} shows the plots generated by the first graphing function, `cmps_signature_plot()`, and continues with the example above.
 `cmps_signature_plot()` takes the output of `extract_feature_cmps(..., include = "full_result")` and returns a list of 5 elements.
@@
 
-*   The first element is a plot called `segment_shift_plot`, which is shown in Figure \autoref{fig:sigplot}.
+*   The first element is a plot called `segment_shift_plot`, which is shown in \autoref{fig:sigplot}.
 On this plot only the congruent matching profile segments are plotted along with the comparison signature at the congruent registration position.
@@
 It not only takes the "full result" of `extract_feature_cmps()`, but also takes an argument `seg.idx`, indicating which segment to be inspected.
-As shown in Figure \autoref{fig:segplots}, for example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments.
+As shown in \autoref{fig:segplots}, for example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments.
 So we can set `seg.idx = 6` in order to take a closer look at segment 6 and understand the reason why it disagrees with the congruent registration position.
@@
 
-*   Figure \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at scale one (its original scale).
+*   \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at scale one (its original scale).
 Since when computing the CMPS score we used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()`, 5 peaks are identified in the cross-correlation curve at scale one, and segment 6 at scale one is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
@@
 
-*   Figure \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at scale one.
+*   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at scale one.
 It shows the cross-correlation curve computed by the comparison signature and the scale-one basis segment 6.
@@
 
-Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment scales together, as shown in Figure \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
+Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment scales together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
 
@@
 
-In Figure \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
+In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
 We can see that the basis segment 6 does obtain a peak near the congruent registration position at scale two and scale three, respectively; however, this position doesn't give one of the five highest peaks at scale one.
@@
 As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252).
-In order to show that our implementation of the CMPS algorithm is able to reproduce the results in (original paper) and is able to be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
+In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
 Since the CMPS algorithm works with, in our case, bullet signatures, we conducted some data-processing.
-For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann using the same set of parameters for both data sets, removed outliers, and obtained bullet signatures for each bullet land engraving.
+For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann [@aoas] with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
 Note that in the work of @cmps they used a different framework to obtain bullet signatures.
-However, since NIST's work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
+However, since the work of @cmps is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
 
 The CMPS score can be considered as a similarity score of two signatures.
-Then how can we get a similarity score of two bullets based on CMPS scores?
-In (the original paper) researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet comparisons based on CMPS scores of bullet signature comparisons.
+Then how can we get a similarity score of two bullets based on CMPS scores (each bullet consists of six bullet signatures in our case)?
+In @cmps researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons.
+$\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all pairwise bullet signature comparisons.
+And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of signature comparisons that are in the same phase.
+
+We can continue with the example used in previous sections.
+`bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
+As mentioned before, each bullet has six land engravings, resulting in six bullet signatures.
+Thus, there are 36 pairwise bullet signature comparisons in total.
+We compute the CMPS scores for all 36 comparisons using multi segment lengths strategy with default parameters, and the result is shown in \autoref{fig:tiles}
+
+```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets", out.width=".7\\textwidth", fig.align="center"}
+dframe <- dframe %>% mutate(
+  landA = paste0("L", landA),
+  landB = paste0("L", landB),
+  landB = factor(landB, levels = paste0("L", c(2:6,1))),
+  bulletA = paste0("Bullet ", bulletA),
+  bulletB = paste0("Bullet ", bulletB)
+)
+
+dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
+  geom_tile() + 
+  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
+  scale_colour_manual("Source", values="darkorange") +
+  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  ylab("Bullet2 Lands") + theme(aspect.ratio = 1) +
+  geom_text(aes(label=cmps_score)) +
+  theme_bw() +
+  theme(aspect.ratio = 1)
+```
+
+<!-- based on CMPS scores of bullet signature comparisons.
 For example, there are in total 6 $\times$ 6 signature comparisons in order to compare two bullets in Hamby study since each bullet has 6 LEAs and each LEA generates a bullet signature.
@@
 And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible average CMPS score of signature comparisons that are in the same phase.
+-->
 
-Here are the CMPS scores of all 36 signature comparisons of the bullets in the example above.
+<!-- Here are the CMPS scores of all 36 signature comparisons of the bullets in the example above. -->
 
-```{r}
-#      [,1] [,2] [,3] [,4] [,5] [,6]
-# [1,]    2    3    2    3    1    2
-# [2,]    2    1   17    1    2    3
-# [3,]    1    1    3   14    2    2
-# [4,]    2    1    1    1   10    1
-# [5,]    2    2    1    1    1   15
-# [6,]   16    3    1    2    1    1
-```
+<!-- ```{r} -->
+<!-- #      [,1] [,2] [,3] [,4] [,5] [,6] -->
+<!-- # [1,]    2    3    2    3    1    2 -->
+<!-- # [2,]    2    1   17    1    2    3 -->
+<!-- # [3,]    1    1    3   14    2    2 -->
+<!-- # [4,]    2    1    1    1   10    1 -->
+<!-- # [5,]    2    2    1    1    1   15 -->
+<!-- # [6,]   16    3    1    2    1    1 -->
+<!-- ``` -->
 
-In this example, the $\mathrm{CMPS_{max}}=17$ and $\mathrm{\overline{CMPS}_{max}}=(16+3+17+14+10+15)/6=12.5$.
+In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $(3+17+14+10+15+16)/6=12.5$.
 
@@
 Figure 2 shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
-Although the CMPS scores we found here are not exactly the same as those presented in the [original paper] since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising.
+Although the CMPS scores we found here are not exactly the same as those presented in @cmps since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising.
 For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM).
@@
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, warning=FALSE}
 library(knitr)

### 2021-05-26 CMPSpaper_writing/results_generation.R

@@ -10,9 +10,10 @@ library(parallel)
 # hamby252_results <-
 #   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252_results.rds")
 
-b252.full <-
-  readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
-
+# b252.full <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
+b252.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
 
 # generate bullet_id
 bulletid.tb <- b252.full %>% select(scan_id)
@@ -213,7 +214,8 @@ for (i in 1:3) {
   # include tank-rashed data
   # [TODO] MAKE THIS A CSV FILE
   t1.df <-
-    read_rds("C:/Research/Bullet/Bullet_Rcode/hamby252/t1.df.rds")
+    # read_rds("C:/Research/Bullet/Bullet_Rcode/hamby252/t1.df.rds")
+    read_rds("~/Research/CMPSpaper/preconsideration/t1.df.rds")
   tr.id <-
     c(
       t1.df %>% filter(type == "TR") %>% pull(scan_id) %>% as.character(),
@@ -251,10 +253,15 @@ for (i in 1:3) {
   # add ground-truth for hamby 252
   studyinfo <-
     readxl::read_xlsx(
-      "C:/Research/Bullet/Bullet_Rcode/grooves/NRBTDSearchResults/Hamby (2009) Barrel/StudyInfo.xlsx",
+      "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
       sheet = 3,
       skip = 1
     )
+    # readxl::read_xlsx(
+    #   "C:/Research/Bullet/Bullet_Rcode/grooves/NRBTDSearchResults/Hamby (2009) Barrel/StudyInfo.xlsx",
+    #   sheet = 3,
+    #   skip = 1
+    # )
   
   keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
   keyss <- tibble(specimen = keyss)

### 2021-05-26 CMPSpaper_writing/results_generation44.R

@@ -10,12 +10,17 @@ library(parallel)
 # hamby44_results <-
 #   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44_results.rds")
 
-b44.full <-
-  readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44/hamby44_manual5.rds")
+# b44.full <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44/hamby44_manual5.rds")
+b44.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
 
 # rds file that stores indices of damaged scans
-idf.idx <-
-  readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44/idfidx.rds")
+# idf.idx <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44/idfidx.rds")
+idf.idx <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/idfidx.rds")
+
 idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
 
 

### 2021-05-27 CMPSpaper_writing/results_generation.R
added data files

@@ -9,6 +9,8 @@ library(parallel)
 # from the x3p data, re-run CMPS results for hamby 252
 # hamby252_results <-
 #   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252_results.rds")
+hamby252_results <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby252_results.rds")
 
 # b252.full <-
 #   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
@@ -24,7 +26,104 @@ bulletid.tb <- bulletid.tb %>% mutate(
   bullet_id = paste(barrel_id, bullet)
 )
 
+# remove x3p files
+b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
 
+# get bullet id
+b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
+
+# get all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# remove damaged data
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+# include tank-rashed data
+# [TODO] MAKE THIS A CSV FILE
+t1.df <-
+  # read_rds("C:/Research/Bullet/Bullet_Rcode/hamby252/t1.df.rds")
+  read_rds("~/Research/CMPSpaper/preconsideration/t1.df.rds")
+tr.id <-
+  c(
+    t1.df %>% filter(type == "TR") %>% pull(scan_id) %>% as.character(),
+    "Br6-2-1",
+    "Br9-2-4"
+  )
+
+######################################
+# add ground-truth for hamby 252
+studyinfo <-
+  readxl::read_xlsx(
+    "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+# readxl::read_xlsx(
[…]

### 2021-05-27 CMPSpaper_writing/results_generation44.R

@@ -45,6 +45,7 @@ CMPS_hamby44_results$npeaks.set <-
 CMPS_hamby44_results$seg_length <- as.list(rep(61, 3))
 CMPS_hamby44_results$Tx <- as.list(rep(30, 3))
 CMPS_hamby44_results$titlee <- list()
+CMPS_hamby44_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby44_results$titlee[[i]] <-
     paste0(
@@ -57,6 +58,15 @@ for (i in 1:N) {
       CMPS_hamby44_results$seg_length[[i]],
       ", Tx=",
       CMPS_hamby44_results$Tx[[i]]
+    )
+  CMPS_hamby44_results$filename[[i]] <- 
+    paste(
+      "hamby44",
+      CMPS_hamby44_results$span1[[i]]*100,
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby44_results$seg_length[[i]],
+      CMPS_hamby44_results$Tx[[i]],
+      sep = "_"
     )
 }
 CMPS_hamby44_results$cmps.table <- list()
@@ -172,7 +182,7 @@ for (i in 1:N) {
   ))
   
   ## parallel setup
-  cl <- makeCluster(6)
+  cl <- makeCluster(7)
   
   par.setup <- parLapply(cl, 1:length(cl),
                          function(xx) {
@@ -310,6 +320,16 @@ for (i in 1:N) {
   # save result in a list
   CMPS_hamby44_results$cmps.table[[i]] <- hamby44.cmps
   
+}
+
+################################
+# save data as csv
+data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/"
+
+for(i in 1:N){
+  write.csv(
+    CMPS_hamby44_results$cmps.table[[i]] %>% select(-cmps.table, -cmps.table.m) %>% as.data.frame(),
+    file = paste(data_path, CMPS_hamby44_results$filename[[i]], ".csv", sep = ""))
 }
 
 

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd

@@
     url: https://github.com/willju-wangqian
-    orcid: 0000-0002-9079-593X
     email:  wju@iastate.edu
@@
 1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
-The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred as "basis segments".
+The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
 
@@
 2.
-**identify candidate positions:** For each basis segment a set of candidate \wj{registration XXX} positions on the comparison signature is identified based on the segment's similarity to the comparison.
+**identify candidate positions:** For each basis segment a set of candidate registration  positions on the comparison signature is identified based on the segment's similarity to the comparison.
 In a first step, the cross-correlation function of the segment to the comparison is calculated, then a number of positions with high correlation values are identified as candidate positions.
@@
 \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
-If a single position (with a tolerance zone determined by `Tx`) results in a top peak in the cross-correlation curve in all three scales, it is called a consistent correlation peak and identified as a candidate for registration.
+If a single position (with a tolerance zone determined by `Tx`) results in a top peak in the cross-correlation curve in all three scales, it is called a consistent correlation peak and identified as a candidate position for registration.
 Note that in @cmps the last element of `npeaks.set` in the multi segment lengths strategy is always set to be 1.
 Additionally, this strategy is also referred as "multi-peak inspection at different segment lengths" in @cmps.
-
-\wj{revised end}
 
@@
 The total number of CMPS is the CMPS score of the comparison.
+\hh{XXX what happens when there are ties after the vote?}
 
@@
 `ccr.list` is described in the previous bullet point, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
+\hh{XXX what happens when there is no consistent correlation peak?}
 
-* `get_CMPS(input.ccp, Tx = 25)` tallies votes from all basis segments and determines the congruent registration position.
+* `get_CMPS(input.ccp, Tx = 25)` \hh{XXX how is `get\_CMPS` different from the extract function?} tallies votes from all basis segments and determines the congruent registration position.
 A position "receives" a vote from a basis segment if this basis segment identifies this position or a closed-enough position (within a tolerance zone defined by `Tx`) as a candidate registration position in algorithm step 2.
@@
 The total number of CMPS is the CMPS score.
-
-\wj{revised end}
 

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
add Will's orcid

@@
     email:  wju@iastate.edu
+    orcid: 0000-0002-9977-377X
   - name: Heike Hofmann

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
signatures added

@@
 
-\wj{the followings are revised}
-
 * `get_seg_scale(segments, nseg, scale = 2)` takes a basis segment and increases its segment length.
@@
 
-Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified on each scale level in step 2, and the length of the tolerance zone in both step 2 and 3.
-In our implementation of the CMPS algorithm we took the original CMPS paper [@cmps] as the reference to determine the default values of these parameters.
-Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.
-The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
-Default values and some explanations of its parameters are as following:
+Note that there are \hh{several} parameters in the CMPS algorithm \hh{that are left to} the users \hh{to decide}, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each scale level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
+In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
+\hh{XXX However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
+Further research is needed, until then users are advised to think of default values as starting values and consider alternatives}
+<!--Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
+The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Default values and some explanations of its parameters are as following:
 
@@
 
-\wj{the followings are revised}
+\wj{the followings are revised} \hh{XXX this section feels a bit repetitive}
 * `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
@@
 <!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->
+
+\hh{XXX you need a bit of an overview here on the structure of what is coming next: in the remainder of the paper we showcase the use of the CMPS functionality on some examples ...}
 
@@
 `bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].
+
+\hh{XXX include some signatures here.}
+
+```{r echo=FALSE}
+signatures <- bullets %>% unnest(sigs)
+signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
+  theme_bw() +
+  xlab("Length in mm") +
+  ylab("Relative height in micron")
+```
 

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
ignatures

@@
 
-```{r echo=FALSE}
+```{r echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row.
+Signatures in the second row are ordered to be in phase with the signatures above, i.e.
+..."}
 signatures <- bullets %>% unnest(sigs)
+signatures <- signatures %>% mutate(
+  bulletland = factor(bulletland, levels=c(paste(rep(c(1,2), each=6), c(1:6,2:6,1), sep="-")))
+)
 signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
@@
 The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects sigs2 and sigs1, respectively.
-This comparison is one of the KM comparisons.
+This comparison is \hh{one of a pair of signatures that are known to be a match -- a KM (known match) comparison}.
 We compute the CMPS score using two versions of the CMPS algorithm:

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
added plots

--- 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 library(bulletxtrctr)
+library(knitr)
+library(kableExtra)
 
@@
 3.
-**determine the congruent registration position:** Each candidate position corresponding to each of the basis segments gets one `vote`.
-Votes for candidate positions within a tolerance of `Tx` are tallied and the position with the highest number of votes gets chosen as the *congruent registration position*.
+**determine the congruent registration position:** \wj{A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
+Votes for all candidate positions} are tallied and the position with the highest number of votes gets chosen as the *congruent registration position*.
 Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
@@
 `ccr.list` is described in the previous bullet point, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
-\hh{XXX what happens when there is no consistent correlation peak?}
+\hh{XXX what happens when there is no consistent correlation peak?} `get_ccp(...)` returns `NULL` if there is no consistent correlation peak.
 
@@
 
-The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects sigs2 and sigs1, respectively.
+The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
 This comparison is one of the KM comparisons.
@@
 
-```{r, eval=FALSE, echo=FALSE}
-hamby252_results <- readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252_results.rds")
-hamby44_results <- readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44_results.rds")
+```{r hamby252-data, eval=TRUE, echo=FALSE}
+# for hamby 252
+N <- 3
+CMPS_hamby252_results <- list()
+CMPS_hamby252_results$span1 <- list(0.75, 0.25, 0.25)
+CMPS_hamby252_results$signame <-
+  list("sigs75", "sigs25", "sigs25_1062")
+CMPS_hamby252_results$npeaks.set <-
+  list(c(5, 3, 1),
+       c(5, 3, 1),
+       c(10, 6, 2))
+CMPS_hamby252_results$seg_length <- list(50, 50, 50)
+CMPS_hamby252_results$Tx <- list(25, 25, 25)
+CMPS_hamby252_results$titlee <- list()
+CMPS_hamby252_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby252_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", span1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03, len=",
+      CMPS_hamby252_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby252_results$Tx[[i]]
+    )
+  CMPS_hamby252_results$filename[[i]] <- 
+    paste(
+      "hamby252",
+      CMPS_hamby252_results$span1[[i]]*100,
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby252_results$seg_length[[i]],
+      CMPS_hamby252_results$Tx[[i]],
+      sep = "_"
+    )
+}
+CMPS_hamby252_results$cmps.table <- list()
+CMPS_hamby252_results$plot <- list()
+
+for(i in 1:N){
+  CMPS_hamby252_results$cmps.table[[i]] <- 
+  read.csv(file = paste("./data/", 
+                        CMPS_hamby252_results$filename[[i]], 
+                        ".csv",
+                        sep = ""))
+}
+
+# generate plots
+for (i in 1:3) {
+  hamby252.cmps <- CMPS_hamby252_results$cmps.table[[i]]
+
+  hamby252.plot.list <- list()
+  titlee <- CMPS_hamby252_results$titlee[[i]]
+
+  hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.max.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      fill = "Comparison Type",
+      x = expression(CMPS[max]),
+      title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 27, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank())
+
+  hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.maxbar.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      x = expression(bar(CMPS)[max]),
+      fill = "Comparison Type",
+      title = expression(paste(
+        "Hamby252 - ", bar(CMPS)[max], " Distribution"
+      )),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 24, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank())
+
+  plot <- ggarrange(plotlist = hamby252.plot.list,
+                    nrow = 1,
+                    ncol = 2)
+  CMPS_hamby252_results$plot[[i]] <- plot
+}
+
+```
+
+```{r hamby44-data, eval=TRUE, echo=FALSE}
+N <- 3
+CMPS_hamby44_results <- list()
+CMPS_hamby44_results$span1 <- list(0.25, 0.25, 0.75)
+CMPS_hamby44_results$signame <-
+  list("sigs25_531", "sigs25_1061", "sigs75_531")
+CMPS_hamby44_results$npeaks.set <-
+  list(c(5, 3, 1),
+       c(10, 6, 1),
+       c(5, 3, 1))
+CMPS_hamby44_results$seg_length <- as.list(rep(61, 3))
+CMPS_hamby44_results$Tx <- as.list(rep(30, 3))
+CMPS_hamby44_results$titlee <- list()
+CMPS_hamby44_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby44_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", span1=",
+      CMPS_hamby44_results$span1[[i]],
+      ", span2=0.03, len=",
+      CMPS_hamby44_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby44_results$Tx[[i]]
+    )
+  CMPS_hamby44_results$filename[[i]] <- 
+    paste(
+      "hamby44",
+      CMPS_hamby44_results$span1[[i]]*100,
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby44_results$seg_length[[i]],
+      CMPS_hamby44_results$Tx[[i]],
+      sep = "_"
+    )
+}
+CMPS_hamby44_results$cmps.table <- list()
+CMPS_hamby44_results$plot <- list()
 ```
@@
 
-In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $(3+17+14+10+15+16)/6=12.5$.
+In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score, is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $(3+17+14+10+15+16)/6=12.5$.
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-library(knitr)
-library(kableExtra)
 # rtt <- readRDS("summary_table.rds")

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd

@@
 
+\hh{XXX include some signatures here.}
+
+```{r echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row.
+Signatures in the second row are ordered to be in phase with the signatures above, i.e.
+..."}
+signatures <- bullets %>% unnest(sigs)
+signatures <- signatures %>% mutate(
+  bulletland = factor(bulletland, levels=c(paste(rep(c(1,2), each=6), c(1:6,2:6,1), sep="-")))
+)
+signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
+  theme_bw() +
+  xlab("Length in mm") +
+  ylab("Relative height in micron")
+```
+
 The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
@@
 We compute the CMPS score using two versions of the CMPS algorithm:
+
+one of a pair of signatures that are known to be a match -- a KM (known match) comparison
 

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
merge and add plots generated from data files

@@
 \wj{the followings are revised} \hh{XXX this section feels a bit repetitive}
+
 * `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
@@
 The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
-This comparison is one of the KM comparisons.
+This comparison is one of a pair of signatures that are known to be a match -- a KM (known match) comparison.
 We compute the CMPS score using two versions of the CMPS algorithm:
-
-one of a pair of signatures that are known to be a match -- a KM (known match) comparison
 
@@
 
+```{r, eval=TRUE, echo=TRUE, fig.height=3}
+CMPS_hamby252_results$plot[[1]]
+```
+
 ```{r hamby44-data, eval=TRUE, echo=FALSE}

### 2021-05-28 CMPSpaper_writing/CMPSpaper_writing.Rmd
revised the algorithm section: added the description of the functions into the algorithm section

@@
 \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
-
     + **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
@@
 A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
-
-    + **Correlation peaks:** The parameter `npeaks.set` in `extract_feature_cmps(...)` determines the number of candidate positions and which strategy to  use to combine candidates: If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidates for registration.
-This strategy is referred as "multi-peak inspection" in @cmps.
-
-    +  **Multiple-length segments:** If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, a multi segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
+    + **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
+The latter is also called "multi segment lengths strategy".
+The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:
+        -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
+        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
 \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
-If a single position (with a tolerance zone determined by `Tx`) results in a top peak in the cross-correlation curve in all three scales, it is called a consistent correlation peak and identified as a candidate position for registration.
-Note that in @cmps the last element of `npeaks.set` in the multi segment lengths strategy is always set to be 1.
-Additionally, this strategy is also referred as "multi-peak inspection at different segment lengths" in @cmps.
-
-3.
-**determine the congruent registration position:** \wj{A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
-Votes for all candidate positions} are tallied and the position with the highest number of votes gets chosen as the *congruent registration position*.
-Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
-The total number of CMPS is the CMPS score of the comparison.
-\hh{XXX what happens when there are ties after the vote?}
-
-In the CMPS package, these three steps are implemented using a set of key functions:
-
-* `get_seg_scale(segments, nseg, scale = 2)` takes a basis segment and increases its segment length.
-`segments` is a list containing all basis segments, generated by the function `get_segs(...)`; `nseg` is an integer indicating which basis segment the function should work with.
-`scale=1` gives the original length of the basis segment.
-Increasing `scale` by 1 will double the segment length.
-
-* `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the comparison signature and finds peaks in the cross-correlation curve.
+        -   `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the comparison signature and finds peaks in the cross-correlation curve.
 The number of peaks detected is equal to `npeaks`, which is an integer.
@@
 The resulting list is called `ccr.list`.
+    +  **Multi segment lengths strategy:** with the multi segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment scales.
+Note that in @cmps, a segment at its largest scale always identifies one peak.
+        -   the scaled version of a basis segment is obtained by using function `get_seg_scale(segments, nseg, scale = 2)`.
+`segments` is a list containing all basis segments, generated by the function `get_segs(...)` in step 1; `nseg` is an integer indicating which basis segment the function should work with.
+`scale=1` gives the original length of the basis segment.
+Increasing `scale` by 1 will double the segment length.
+        -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak".
+`ccr.list` is the result of `lapply()` and `get_ccr_peaks(...)`, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
+`get_ccp(...)` returns `NULL` if there is no consistent correlation peak.
 
-* `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak" (defined in algorithm step 2) under the framework of multi segment lengths strategy.
-`ccr.list` is described in the previous bullet point, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
-\hh{XXX what happens when there is no consistent correlation peak?} `get_ccp(...)` returns `NULL` if there is no consistent correlation peak.
+3.
+**determine the congruent registration position:** A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
+Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, \wj{XXX indicating that most of the basis segments find their highly similar counterpart in the comparison signature in terms of correlation at this registration position.} In case of ties the middle position is taken as the congruent registration position.
+Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
+The total number of CMPS is the CMPS score of the comparison.
+`get_CMPS(input.ccp, Tx = 25)` is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (cmps).
 
-* `get_CMPS(input.ccp, Tx = 25)` \hh{XXX how is `get\_CMPS` different from the extract function?} tallies votes from all basis segments and determines the congruent registration position.
-A position "receives" a vote from a basis segment if this basis segment identifies this position or a closed-enough position (within a tolerance zone defined by `Tx`) as a candidate registration position in algorithm step 2.
-The goal is to find a shift in registration position that is agreed by the most number of basis segments, so the position receiving the most number of votes is the congruent registration position.
-In case of ties the middle position is taken as the congruent registration position.
-Basis segments with the congruent registration position identified are called "congruent matching profile segments" (CMPS).
-The total number of CMPS is the CMPS score.
+<!-- In the CMPS package, these three steps are implemented using a set of key functions: -->
 
@@
 <!--Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
-The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Default values and some explanations of its parameters are as following:
+The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Here we present it with its default parameters.
 
@@
 
+We have discussed parameters `seg_length`, `npeaks.set`, and `Tx` in the previous section, and the parameters left are `x`, `y`, and `include`:
+
 * `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
-* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1; 
-* `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3;
-* `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified;
+
+<!-- * `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1;  -->
+<!-- * `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3; -->
+<!-- * `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified; -->
+
 * `include` determines the output of the function.
@@
 
-<!-- ```{r, echo=FALSE, out.width="400px", fig.cap="put segment\\_plot and scale\\_ccf\\_plot of all scales together.
-We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1).
-Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment.
-Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."} -->
-<!-- knitr::include_graphics("img/segplot3.png", dpi = 100) -->
-<!-- ``` -->
-
 In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
@@
 
-<!-- Here are the CMPS scores of all 36 signature comparisons of the bullets in the example above. -->
-
-<!-- ```{r} -->
-<!-- #      [,1] [,2] [,3] [,4] [,5] [,6] -->
-<!-- # [1,]    2    3    2    3    1    2 -->
-<!-- # [2,]    2    1   17    1    2    3 -->
-<!-- # [3,]    1    1    3   14    2    2 -->
-<!-- # [4,]    2    1    1    1   10    1 -->
-<!-- # [5,]    2    2    1    1    1   15 -->
-<!-- # [6,]   16    3    1    2    1    1 -->
-<!-- ``` -->
-
 In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score, is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $(3+17+14+10+15+16)/6=12.5$.

### 2021-06-02 CMPSpaper_writing/CMPSpaper_writing.Rmd
update parameters for plotting

@@
 Since `include = "full_result"` the outputs of `extract_feature_cmps(...)` contain everything listed in the previous section.
-Moreover, as mentioned before, multi segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
+Moreover, \wj{XXX as mentioned before, }multi segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
+\wj{XXX how should we address the advantage of multi segment lengths strategy}
 \wj{revised end}
@@
       ")",
-      ", span1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03, len=",
+      ", len=",
       CMPS_hamby252_results$seg_length[[i]],
        ", Tx=",
-      CMPS_hamby252_results$Tx[[i]]
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
     )
@@
 
+com.title252 <- expression(paste(
+  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
+
 # generate plots
@@
       x = expression(CMPS[max]),
-      title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
+      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
       subtitle = titlee
@@
     theme_bw() +
-    theme(panel.grid.minor = element_blank())
+    theme(panel.grid.minor = element_blank()) +
+    font("x.text", size = 6)
 
@@
       fill = "Comparison Type",
-      title = expression(paste(
-        "Hamby252 - ", bar(CMPS)[max], " Distribution"
-      )),
+      # title = expression(paste(
+      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
+      # )),
       subtitle = titlee
@@
                     nrow = 1,
-                    ncol = 2)
+                    ncol = 2,
+                    common.legend = TRUE, legend = "bottom")
+  plot <- annotate_figure(plot, 
+                          top = text_grob(com.title252))
   CMPS_hamby252_results$plot[[i]] <- plot
@@
 
-```
-
-```{r, eval=TRUE, echo=TRUE, fig.height=3}
-CMPS_hamby252_results$plot[[1]]
 ```
@@
       ")",
-      ", span1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03, len=",
+      ", len=",
       CMPS_hamby44_results$seg_length[[i]],
        ", Tx=",
-      CMPS_hamby44_results$Tx[[i]]
+      CMPS_hamby44_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby44_results$span1[[i]],
+      ", span2=0.03"
     )
@@
 CMPS_hamby44_results$plot <- list()
+
+for(i in 1:N){
+  CMPS_hamby44_results$cmps.table[[i]] <- 
+  read.csv(file = paste("./data/", 
+                        CMPS_hamby44_results$filename[[i]], 
+                        ".csv",
+                        sep = ""))
+}
+
+com.title44 <- expression(paste(
+  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
+
+# generate plots
+for (i in 1:3) {
+  hamby44.cmps <- CMPS_hamby44_results$cmps.table[[i]]
+
+  hamby44.plot.list <- list()
+  titlee <- CMPS_hamby44_results$titlee[[i]]
+
+  hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.max.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      fill = "Comparison Type",
+      x = expression(CMPS[max]),
+      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 27, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank()) +
+    font("x.text", size = 6)
+
+  hamby44.plot.list[[2]] <- hamby44.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.maxbar.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      x = expression(bar(CMPS)[max]),
+      fill = "Comparison Type",
+      # title = expression(paste(
+      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
+      # )),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 24, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank())
+
+  plot <- ggarrange(plotlist = hamby44.plot.list,
+                    nrow = 1,
+                    ncol = 2,
+                    common.legend = TRUE, legend = "bottom")
+  plot <- annotate_figure(plot, 
+                          top = text_grob(com.title44))
+  CMPS_hamby44_results$plot[[i]] <- plot
+}
 ```
@@
 
-Figure 2 shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
+\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
 Although the CMPS scores we found here are not exactly the same as those presented in @cmps since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising.
 For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM).
-Table x shows some summary statistics.
+\autoref{tab:table1} shows some summary statistics.
 
@@
 And `Tx = 25` makes the tolerance zone be $\pm 39.0625$ \textmu m.
-This is to mimic the parameters used in the [original paper].
+This is to mimic the parameters used in @cmps.
 
 <!-- this is figure 2 -->
-```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) "}
+```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) "}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
-knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
+# knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
+CMPS_hamby252_results$plot[[1]]
 ```
 
-table 1:
+Table 1:
 
-```{r, echo=FALSE, warning=FALSE}
+```{r table1, echo=FALSE, warning=FALSE}
 # rtt <- readRDS("summary_table.rds")
@@
 
-Figure 3 shows the results for Hamby set 44.
+\autoref{fig:result1_44} shows the results for Hamby set 44.
 Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged.
-Table 1 shows some summary statistics for Hamby set 44.
+\wj{Table x} shows some summary statistics for Hamby set 44.
 
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.25"}
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.25"}
 # [1] "span1=0.25, span2=0.03, rm_outliers"
-knitr::include_graphics("img/hamby44_v1.png", dpi = 100)
+# knitr::include_graphics("img/hamby44_v1.png", dpi = 100)
+CMPS_hamby44_results$plot[[1]]
 ```
 
-Figure 4 shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`.
+\autoref{fig:result2_44} shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`.
 We can see that the separation between KM comparisons and KNM comparisons is increased.
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 "}
+```{r result2_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 "}
 # [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
-knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
+# knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
+CMPS_hamby44_results$plot[[2]]
 ```
@@
 For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures; however, in this example we used `span1=0.75` and changed the characteristic of those signatures.
-As we can see in figure 5, this change also affects the CMPS results.
+As we can see in \autoref{fig:result3_44}, this change also affects the CMPS results.
 
@@
 
-```{r, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75"}
+```{r result3_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75"}
 # [4] "span1=0.75, span2=0.03, rm_outliers"  
-knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
+# knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
+CMPS_hamby44_results$plot[[3]]
 ```

### 2021-06-02 CMPSpaper_writing/results_generation.R

@@ -142,12 +142,13 @@ for (i in 1:N) {
       "npeaks.set=c(",
       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
       ")",
-      ", span1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03, len=",
+      ", len=",
       CMPS_hamby252_results$seg_length[[i]],
       ", Tx=",
-      CMPS_hamby252_results$Tx[[i]]
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
     )
   CMPS_hamby252_results$filename[[i]] <- 
     paste(
@@ -161,6 +162,10 @@ for (i in 1:N) {
 }
 CMPS_hamby252_results$cmps.table <- list()
 CMPS_hamby252_results$plot <- list()
+
+com.title252 <- expression(paste(
+  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
 
 
 for (i in 1:N) {
@@ -350,7 +355,8 @@ data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/"
 
 for(i in 1:N){
   write.csv(
-    CMPS_hamby252_results$cmps.table[[i]] %>% select(-cmps.table, -cmps.table.m) %>% as.data.frame(),
+    CMPS_hamby252_results$cmps.table[[i]] %>% 
+      select(-cmps.table, -cmps.table.m) %>% as.data.frame(),
     file = paste(data_path, CMPS_hamby252_results$filename[[i]], ".csv", sep = ""))
 }
 
@@ -370,13 +376,13 @@ for (i in 1:3) {
     labs(
       fill = "Comparison Type",
       x = expression(CMPS[max]),
-      title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
+      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
       subtitle = titlee
     ) +
     scale_x_continuous(breaks = seq(0, 27, 1)) +
     theme_bw() +
-    theme(panel.grid.minor = element_blank()) 
-    
+    theme(panel.grid.minor = element_blank()) +
+    font("x.text", size = 6)
   
   hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
[…]

### 2021-06-02 CMPSpaper_writing/results_generation44.R

@@ -52,12 +52,13 @@ for (i in 1:N) {
       "npeaks.set=c(",
       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
       ")",
-      ", span1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03, len=",
+      ", len=",
       CMPS_hamby44_results$seg_length[[i]],
       ", Tx=",
-      CMPS_hamby44_results$Tx[[i]]
+      CMPS_hamby44_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby44_results$span1[[i]],
+      ", span2=0.03"
     )
   CMPS_hamby44_results$filename[[i]] <- 
     paste(
@@ -71,6 +72,10 @@ for (i in 1:N) {
 }
 CMPS_hamby44_results$cmps.table <- list()
 CMPS_hamby44_results$plot <- list()
+
+com.title44 <- expression(paste(
+  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
 
 # remove x3p files
 b44 <- b44.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
@@ -335,7 +340,7 @@ for(i in 1:N){
 
 #################################################
 # generate plots
-for (i in 1:N) {
+for (i in 1:3) {
   hamby44.cmps <- CMPS_hamby44_results$cmps.table[[i]]
   
   hamby44.plot.list <- list()
@@ -344,28 +349,38 @@ for (i in 1:N) {
   hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
     geom_histogram(aes(x = cmps.max.m,
                        fill = as.factor(type_truth)), binwidth = 1) +
-    labs(fill = "Comparison Type",
-         x = expression(CMPS[max]),
-         title = expression(paste("Hamby44 - ", CMPS[max], " Distribution")),
-         subtitle = titlee) + 
-    scale_x_continuous(breaks = seq(0, 27, 1))+
-    theme_bw()+
-    theme(panel.grid.minor = element_blank())
+    labs(
+      fill = "Comparison Type",
+      x = expression(CMPS[max]),
+      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 27, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank()) +
[…]

### 2021-06-03 CMPSpaper_writing/CMPSpaper_writing.Rmd
update CMPS formula

@@
   - \usepackage{afterpage}
+  - \usepackage{bbm}
 author:
@@
 For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann [@aoas] with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
-Note that in the work of @cmps they used a different framework to obtain bullet signatures.
-However, since the work of @cmps is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
+Note that in the work of @cmps researchers used a different framework to obtain bullet signatures.
+However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
 
 The CMPS score can be considered as a similarity score of two signatures.
-Then how can we get a similarity score of two bullets based on CMPS scores (each bullet consists of six bullet signatures in our case)?
-In @cmps researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons.
+Then in order to obtain a similarity score of two bullets based on CMPS scores, researchers in @cmps introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons.
 $\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all pairwise bullet signature comparisons.
 And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of signature comparisons that are in the same phase.
+
+In general, we assume each bullet has $n$ land engravings (in our case $n=6$).
+Let $c_{ij}$ denote the CMPS score of comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
+Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and $\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}$, where $\mathbbm{1}_A$ denotes an indicator function.
+For example, $\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}$ when $n = 6$.
+
+Then we have
+
+$$
+\mathrm{CMPS_{max}} = \max_{i,j} c_{ij}
+$$
+
+and
+
+$$
+\mathrm{\overline{CMPS}_{max}} = \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
+$$
 
@@
 As mentioned before, each bullet has six land engravings, resulting in six bullet signatures.
-Thus, there are 36 pairwise bullet signature comparisons in total.
-We compute the CMPS scores for all 36 comparisons using multi segment lengths strategy with default parameters, and the result is shown in \autoref{fig:tiles}
+Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
+We use multi segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
+We can see that in this example,
+
+$$
+\mathrm{CMPS_{max}} =  \max_{ij} c_{ij} = 17
+$$
+
+and since bullet lands in phase $\mathcal{P}_1$ gives the highest mean CMPS score, we have
+
+$$
+\begin{aligned}
+\mathrm{\overline{CMPS}_{max}} &= \frac{1}{6} \sum_{(i,j) \in \mathcal{P}_1} c_{ij} \\
+                        &= \frac{1}{6} (c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}) \\
+                        &= \frac{1}{6} (3+17+14+10+15+16) \\
+                        &= 12.5
+\end{aligned}
+$$
 
@@
   facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
-  ylab("Bullet2 Lands") + theme(aspect.ratio = 1) +
+  ylab("Bullet2 Lands") + 
   geom_text(aes(label=cmps_score)) +
@@
 
-In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score, is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $(3+17+14+10+15+16)/6=12.5$.
+<!-- In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score, is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $()/6=12.5$.
+-->
 

### 2021-06-03 CMPSpaper_writing/results_generation.R

@@ -420,3 +420,19 @@ ck_idx <- tt1 != tt2
 (1:595)[ck_idx]
 tt1 - tt2
 tt1[ck_idx]
+
+
+### phase
+1 2 3 4 5 6
+2 3 4 5 6 1
+3 4 5 6 1 2
+
+
+
+
+
+
+
+
+
+

### 2021-06-03 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits

@@
 A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940;@cmps].
-\wj{Note that this is not an exhaustive list of these efforts.} The notion of bullet signatures is one of the results of these efforts.
+Note that this is not an exhaustive list of these efforts.
+The notion of bullet signatures is one of the results of these efforts.
 Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
@@
 
-\wj{the followings are revised}
-
 2.
@@
     + **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
-The latter is also called "multi segment lengths strategy".
+The latter is also called "multi-segment lengths strategy".
 The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:
         -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
+        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
 \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
@@
 `segments`, `seg_scale`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the comparison signature.
-If the multi segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each scale of the basis segment.
+If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each scale of the basis segment.
 The resulting list is called `ccr.list`.
-    +  **Multi segment lengths strategy:** with the multi segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment scales.
+    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment scales.
 Note that in @cmps, a segment at its largest scale always identifies one peak.
@@
 **determine the congruent registration position:** A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
-Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, \wj{XXX indicating that most of the basis segments find their highly similar counterpart in the comparison signature in terms of correlation at this registration position.} In case of ties the middle position is taken as the congruent registration position.
+Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*,  indicating that most of the basis segments find their highly similar counterpart in the comparison signature in terms of correlation at this registration position.
+In case of ties the middle position is taken as the congruent registration position.
 Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
@@
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
-\hh{XXX However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
-Further research is needed, until then users are advised to think of default values as starting values and consider alternatives}
-<!--Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
+\hh{However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
+Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.}
+<!--Additionally, as shown in @cmps, using multi-segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
 The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Here we present it with its default parameters.
@@
 
-We have discussed parameters `seg_length`, `npeaks.set`, and `Tx` in the previous section, and the parameters left are `x`, `y`, and `include`:
+Besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx` \hh{the function `extract\_feature\_cmps` allows for the following input from users}:
 
 * `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
-
-<!-- * `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1;  -->
-<!-- * `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3; -->
-<!-- * `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified; -->
 
@@
 
-For more details, please check the documentation of `extract_feature_cmps` or use `?extract_feature_cmps`.
-
-\wj{revised end}
+<!--For more details, please check the documentation of `extract_feature_cmps` or use `?extract_feature_cmps`.-->
 
@@
 
-`bullets$sigs` is a list of 12 numeric vectors corresponding to 12 bullet signatures.
+`bullets$sigs` is a list of 12 numeric vectors corresponding to 12 bullet signatures as shown in \autoref{fig:sigs}.
 `bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].
 
-\hh{XXX include some signatures here.}
-
-```{r echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row.
+```{r sigs, echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row.
 Signatures in the second row are ordered to be in phase with the signatures above, i.e.
-..."}
+matching signatures are displayed on top of each other."}
 signatures <- bullets %>% unnest(sigs)
@@
 \wj{revised the following}
-Since `npeaks.set = c(5,3,1)`, `cmps_with_multi_scale` uses the multi segment lengths strategy.
-On the other hand, `cmps_without_multi_scale` doesn't use the multi segment lengths strategy, and each basis segment finds 5 candidate positions due to `npeaks.set = 5`.
-Since `include = "full_result"` the outputs of `extract_feature_cmps(...)` contain everything listed in the previous section.
-Moreover, \wj{XXX as mentioned before, }multi segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
-\wj{XXX how should we address the advantage of multi segment lengths strategy}
-\wj{revised end}
+In the first example, `npeaks.set` is a vector of three integers.
+This means that  the algorithm uses the multi-segment lengths strategy to create `cmps_with_multi_scale`, while for `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
+We use `include = "full_result"` to capture all results. 
+Moreover, \wj{XXX as mentioned before, }multi-segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
+\wj{XXX how should we address the advantage of multi-segment lengths strategy} \hh{XXX any score based method is walking the line between false positives and false negatives.
+As the number of false positives is reduced (by being more conservatives) the number of false negatives might rise.
+The multi scale method might also be slower because the algorithm is run a couple of times.}
+
+\hh{XXX this is just a single example - a claim of 'more conservative' is quite big. At this point, it is only a claim. How would you go about finding evidence for it? }
 
@@
 The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in its highest segment scale; the blue dashed lines show the tolerance zone around the green dashed line.
-We can see here none of the five highest peaks at scale one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi segment lengths strategy.
+We can see here none of the five highest peaks at scale one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
 Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
@@
 We are identifying five highest peaks at scale one, three peaks at scale two, and one peak at scale three since npeaks.set = c(5, 3, 1).
-The highest peak position at scale three is marked by the green dashed line across all segment scales, but it doesn't achieve the top five highest peaks at scale one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi segment lengths strategy.}
+The highest peak position at scale three is marked by the green dashed line across all segment scales, but it doesn't achieve the top five highest peaks at scale one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
 \end{figure}
@@
 We can see that the basis segment 6 does obtain a peak near the congruent registration position at scale two and scale three, respectively; however, this position doesn't give one of the five highest peaks at scale one.
-As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi segment lengths strategy.
+As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy.
 The identified top five peaks at scale one are also examples of "false positive" peaks.
-The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at scale two and three by increasing the segment length, which justifies the usage of multi segment lengths strategy.
+The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at scale two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.
 
@@
 Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
-We use multi segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
+We use multi-segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
 We can see that in this example,

### 2021-06-03 CMPSpaper_writing/CMPSpaper_writing.Rmd
update tile plot "same land"

@@
   geom_tile() + 
-  geom_tile(aes(colour="same barrel"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
   scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 

### 2021-06-04 CMPSpaper_writing/CMPSpaper_writing.Rmd
edit the paragraph talking about false positives; edit the first part of result section

@@
   # see ?rjournal_article for more information
-  - name: Will W. Ju
+  - name: Wangqian W. Ju
     affiliation: Department of Statistics
@@
 
-\wj{the followings are revised} \hh{XXX this section feels a bit repetitive}
-
-Besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx` \hh{the function `extract\_feature\_cmps` allows for the following input from users}:
+Besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx`, the function `extract_feature_cmps` allows for the following input from users:\wj{XXX the code text is a little bit off}
 
@@
 
-\hh{XXX you need a bit of an overview here on the structure of what is coming next: in the remainder of the paper we showcase the use of the CMPS functionality on some examples ...}
+\wj{In the remainder of the paper we showcase the use of the CMPS functionality on some examples and present the results of applying it to two datasets.}
+<!-- \hh{XXX you need a bit of an overview here on the structure of what is coming next: in the remainder of the paper we showcase the use of the CMPS functionality on some examples ...} -->
 
@@
 
-\hh{How about you go into a description of the results from the function `extract\_feature\_cmps`?}
-
 \wj{revised the following}
@@
 We use `include = "full_result"` to capture all results.
-Moreover, \wj{XXX as mentioned before, }multi-segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
+In this example, the `cmps_with_multi_scale$CMPS.score` is 9, while `cmps_without_multi_scale$CMPS.score` is 12.
+\wj{As discussed in} @cmps, \wj{using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
+As the number of false positives is reduced the number of false negatives might rise.
+More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
+Note that the multi scale method might also be slower because the algorithm is run a couple of times.}
+
+<!-- \wj{XXX as mentioned before, }multi-segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
 \wj{XXX how should we address the advantage of multi-segment lengths strategy} \hh{XXX any score based method is walking the line between false positives and false negatives.
 As the number of false positives is reduced (by being more conservatives) the number of false negatives might rise.
-The multi scale method might also be slower because the algorithm is run a couple of times.}
-
-\hh{XXX this is just a single example - a claim of 'more conservative' is quite big. At this point, it is only a claim. How would you go about finding evidence for it? }
+The multi scale method might also be slower because the algorithm is run a couple of times.} -->
+
+<!-- \hh{XXX this is just a single example - a claim of 'more conservative' is quite big. At this point, it is only a claim. How would you go about finding evidence for it? } -->
 
@@
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-Since the CMPS algorithm works with, in our case, bullet signatures, we conducted some data-processing.
-For both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann [@aoas] with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
-Note that in the work of @cmps researchers used a different framework to obtain bullet signatures.
+Because the CMPS algorithm works with bullet signatures in our case, we conducted some data-processing: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann [@aoas] with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
+Note that researchers of @cmps used a different framework to obtain bullet signatures.
 However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
@@
 The CMPS score can be considered as a similarity score of two signatures.
-Then in order to obtain a similarity score of two bullets based on CMPS scores, researchers in @cmps introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons.
+Then in order to obtain a similarity score of two bullets based on CMPS scores, researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons [@cmps].
 $\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all pairwise bullet signature comparisons.
@@
 $$
-\mathrm{CMPS_{max}} =  \max_{ij} c_{ij} = 17
+\mathrm{CMPS_{max}} =  \max_{i,j} c_{ij} = 17
 $$
@@
 
-```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets", out.width=".7\\textwidth", fig.align="center"}
+```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
+Land engraving pairs generated by the same land (KM comparisons) are highlighted", out.width=".7\\textwidth", fig.align="center"}
 dframe <- dframe %>% mutate(
@@
 
-\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252.
-Although the CMPS scores we found here are not exactly the same as those presented in @cmps since we don't have the exact parameters and functions used by the researchers, the results we obtained are promising.
+\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy.
+Although the CMPS scores we found here are not exactly the same as those presented in @cmps since we don't have the exact parameters and functions used by the researchers, the results we obtained qualitatively agree with their results.
 For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM).
-\autoref{tab:table1} shows some summary statistics.
 
@@
 
-Note that for Hamby set 44, one unit represents 1.5625 \textmu m so setting `seg_length = 50` makes each basis segment have length 78.125 \textmu m.
+Note that for Hamby set 252, one unit represents 1.5625 \textmu m so setting `seg_length = 50` makes each basis segment have length 78.125 \textmu m.
 And `Tx = 25` makes the tolerance zone be $\pm 39.0625$ \textmu m.
@@
 ```
-
-Table 1:
 
@@
 
-\autoref{fig:result1_44} shows the results for Hamby set 44.
-Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged.
-\wj{Table x} shows some summary statistics for Hamby set 44.
-
-For Hamby set 44, the parameters we used in `extract_feature_cmps` are:
+**Hamby 44**
+
+For Hamby set 44 we not only generated comparable results but also used different sets of parameters to examine their potential effects.
+
+\autoref{fig:result1_44} shows the Hamby 44 results that are comparable with Hamby 252 results. The parameters used in `extract_feature_cmps` are:
 
@@
 
-Note that we used different values here for `seg_length` and `Tx` because our Hamby set 44 scans have a different scanning resolution.
-One unit here represents 1.29 \textmu m.
-So here each basis segment has length 78.69 \textmu m, and the tolerance zone is $\pm 38.7$ \textmu m.
-
-<!-- this is figure 3 -->
+Since the Hamby set 44 scans have a different scanning resolution, we need to adjust the value of `seg_length` and `Tx` accordingly.
+One unit in Hamby 44 represents 1.29 \textmu m.
+Thus, we make `seg_length = 61` and `Tx = 30` to ensure that each basis segment has length 78.69 \textmu m, and the tolerance zone is $\pm 38.7$ \textmu m.
+Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged, which motivates us to examine different sets of parameters.
+\autoref{tab:table1} shows some summary statistics.
 
@@
 
-\autoref{fig:result2_44} shows another Hamby set 44 results, but the parameter `npeaks.set` is now `c(10, 6, 1)`.
+\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while fixing other parameters.
+In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
 We can see that the separation between KM comparisons and KNM comparisons is increased.
-This shows that the parameters used in the CMPS algorithm can affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
+This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
 

### 2021-06-04 CMPSpaper_writing/CMPSpaper_writing.Rmd
edit the result section; add one more citation for firearm data;

@@
 ---
-title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures
+title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet  = 
 header-includes:
@@
 
- Firearm examination has  played an important role in  convictions in the United States criminal justice system.
+\wj{XXX According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "More than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms"} [@fbiucr], and firearm examination could play an important role in all these cases.
+ <!-- Firearm examination has  played an important role in  convictions [@fbiucr] in the United States criminal justice system.
 \hh{Do we have a number or a percentage of cases where firearm examination has played a role?
 or maybe gun violence?
-XXX}
-
+XXX} -->
+<!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
 An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
@@
 ### Conceptual idea of CMPS
-\hh{Most algorithms for comparing striation marks are based on the digitized signatures XXX} and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940 ].
+Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940 ].
  The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
@@
   High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.
-  \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?}
-  \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example?
+\wj{However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparison is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
+Further research is needed to understand how to determine the threshold.
+XXX}
+  <!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?} -->
+  <!-- \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example?
 ...
-'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'}
+'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'} -->
  The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
@@
 <!-- this is figure 2 -->
-```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) "}
+```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) ", fig.height=3}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
 # knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
-CMPS_hamby252_results$plot[[1]]
+CMPS_hamby252_results$plot[[2]]
+```
+
+**Hamby 44**
+
+For Hamby set 44 we not only generated comparable results but also used different sets of parameters to examine their potential effects.
+
+\autoref{fig:result1_44} shows the Hamby 44 results that are comparable with Hamby 252 results. The parameters used in `extract_feature_cmps` are:
+
+```{r, eval=FALSE}
+extract_feature_cmps(
+  x, y,
+  seg_length = 61, 
+  Tx = 30,
+  npeaks.set = c(5,3,1),
+  include = "nseg"
+)
+```
+
+Since the Hamby set 44 scans have a different scanning resolution, we need to adjust the value of `seg_length` and `Tx` accordingly.
+One unit in Hamby 44 represents 1.29 \textmu m.
+Thus, we make `seg_length = 61` and `Tx = 30` to ensure that each basis segment has length 78.69 \textmu m, and the tolerance zone is $\pm 38.7$ \textmu m.
+Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged, which motivates us to examine different sets of parameters.
+
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.25", fig.height=3}
+# [1] "span1=0.25, span2=0.03, rm_outliers"
+# knitr::include_graphics("img/hamby44_v1.png", dpi = 100)
+CMPS_hamby44_results$plot[[1]]
+```
+
+\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while fixing other parameters.
+In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
+We can see that the separation between KM comparisons and KNM comparisons is increased.
+This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
+
+<!-- this is figure 4 -->
+
+```{r result2_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 ", fig.height=3}
+# [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
+# knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
+CMPS_hamby44_results$plot[[2]]
+```
+
+For the third result of Hamby 44, we changed a parameter used in the data-processing procedure.
+`span1=0.25` is used in previous results, and we changed it to `span1=0.75` \wj{in this case to make bullet signatures capture more global patterns XXX}.
+<!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
+-->
+As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results. 
+\autoref{tab:table1} presents some summary statistics of the Hamby 44 results above.
+These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
+
+\wj{XXX talk about the table: Not exhaustive, more research is needed to cross-validate the parameters}
+<!-- this is figure 5 -->
+
+```{r result3_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75", fig.height=3}
+# [4] "span1=0.75, span2=0.03, rm_outliers"  
+# knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
+CMPS_hamby44_results$plot[[3]]
 ```
@@
 
-**Hamby 44**
-
-For Hamby set 44 we not only generated comparable results but also used different sets of parameters to examine their potential effects.
-
-\autoref{fig:result1_44} shows the Hamby 44 results that are comparable with Hamby 252 results. The parameters used in `extract_feature_cmps` are:
-
-```{r, eval=FALSE}
-extract_feature_cmps(
-  x, y,
-  seg_length = 61, 
-  Tx = 30,
-  npeaks.set = c(5,3,1),
-  include = "nseg"
-)
-```
-
-Since the Hamby set 44 scans have a different scanning resolution, we need to adjust the value of `seg_length` and `Tx` accordingly.
-One unit in Hamby 44 represents 1.29 \textmu m.
-Thus, we make `seg_length = 61` and `Tx = 30` to ensure that each basis segment has length 78.69 \textmu m, and the tolerance zone is $\pm 38.7$ \textmu m.
-Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged, which motivates us to examine different sets of parameters.
-\autoref{tab:table1} shows some summary statistics.
-
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.25"}
-# [1] "span1=0.25, span2=0.03, rm_outliers"
-# knitr::include_graphics("img/hamby44_v1.png", dpi = 100)
-CMPS_hamby44_results$plot[[1]]
-```
-
-\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while fixing other parameters.
-In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
-We can see that the separation between KM comparisons and KNM comparisons is increased.
-This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
-
-<!-- this is figure 4 -->
-
-```{r result2_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 "}
-# [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
-# knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
-CMPS_hamby44_results$plot[[2]]
-```
-
-For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the signatures; however, in this example we used `span1=0.75` and changed the characteristic of those signatures.
-As we can see in \autoref{fig:result3_44}, this change also affects the CMPS results.
-
-<!-- this is figure 5 -->
-
-```{r result3_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75"}
-# [4] "span1=0.75, span2=0.03, rm_outliers"  
-# knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
-CMPS_hamby44_results$plot[[3]]
-```
-
-[The codes generating those results can be found in the appendix. ???]
+\wj{The codes generating those results can be found in the appendix.XXX}
 

### 2021-06-04 CMPSpaper_writing/results_generation.R

@@ -123,17 +123,18 @@ tmp.tibble <- tmp.tibble %>% mutate(
 )
 
 ### set up parameters
-N <- 3
+N <- 4
 CMPS_hamby252_results <- list()
-CMPS_hamby252_results$span1 <- list(0.75, 0.25, 0.25)
+CMPS_hamby252_results$span1 <- list(0.75, 0.25, 0.25, 0.15)
 CMPS_hamby252_results$signame <-
-  list("sigs75", "sigs25", "sigs25_1062")
+  list("sigs75", "sigs25", "sigs25_1062", "sigs15")
 CMPS_hamby252_results$npeaks.set <-
   list(c(5, 3, 1),
        c(5, 3, 1),
-       c(10, 6, 2))
-CMPS_hamby252_results$seg_length <- list(50, 50, 50)
-CMPS_hamby252_results$Tx <- list(25, 25, 25)
+       c(10, 6, 2),
+       c(5,3,1))
+CMPS_hamby252_results$seg_length <- as.list(rep(50, 4))
+CMPS_hamby252_results$Tx <- as.list(rep(25, 4))
 CMPS_hamby252_results$titlee <- list()
 CMPS_hamby252_results$filename <- list()
 for (i in 1:N) {
@@ -423,15 +424,24 @@ tt1[ck_idx]
 
 
 ### phase
-1 2 3 4 5 6
-2 3 4 5 6 1
-3 4 5 6 1 2
+# 1 2 3 4 5 6
+# 2 3 4 5 6 1
+# 3 4 5 6 1 2
 
 
+(b252$sigs75[[1]] %>% ggplot() +
+  geom_line(aes(x=x, y=sig))) / 
+(b252$sigs25[[1]] %>% ggplot() +
+  geom_line(aes(x=x, y=sig))) / 
+(b252$sigs15[[1]] %>% ggplot() +
+   geom_line(aes(x=x, y=sig)))
 
-
-
-
+(b252$sigs75[[1]] %>% ggplot() +
+    geom_line(aes(x=x, y=value-raw_sig))) / 
+  (b252$sigs25[[1]] %>% ggplot() +
+     geom_line(aes(x=x, y=value-raw_sig))) / 
+  (b252$sigs15[[1]] %>% ggplot() +
+     geom_line(aes(x=x, y=value-raw_sig)))
 
 
 

### 2021-06-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
edited the result and conclusion section

@@
 These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-
-\wj{XXX talk about the table: Not exhaustive, more research is needed to cross-validate the parameters}
+As shown in \autoref{tab:table1}, some parameter settings are better than others in terms of the separation between the two distributions.
+\wj{However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.}
+
 <!-- this is figure 5 -->
@@
 
-We presented the CMPS package, an open-source implementation of the congruent matching profile segments (CMPS) algorithm.
+In this paper we presented the CMPS package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and applied it to two datasets in Hamby study [@hamby] to show its potential for further research.
 The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons. 
-In this paper, functions included in the package were illustrated along with the basic logic of the CMPS algorithm.
-And we used a small dataset included in the package as an example to explain the usage of the package.
-Some graphing tools were also implemented in the package so that users can visualize results and have a better understanding of both the algorithm and the results.
-We also applied the algorithm to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising.
-
-From the results of both Hamby set 252 and 44, we can see that the CMPS scores of KM comparisons computed by `extract_feature_cmps` were able to be separated from those of KNM comparisons.
-And at the same time, we can see that CMPS algorithm is sensitive to the choice of parameters such as segment length, number of peaks detected at each segment scale, and congruency tolerance.
-Some parameter choices are better in the sense that they can enlarge the separation between the KM comparisons and the KNM comparisons.
-And the best set of parameters depend on the dataset being used, and the choice of parameters has not been, but should be, cross-validated.
-
-Our open-source implementation introduces the CMPS algorithm to R community and allows everyone to use it for their own projects.
-It would also facilitate future studies on parameter cross-validation and the development of statistical methods to modeling KM and KNM CMPS score distributions.
+We introduced the basic logic of the CMPS algorithm and how it is implemented in the CMPS package.
+We also showcased the functionality of the CMPS package with a small dataset example that is included in the package.
+In the CMPS package we also implemented some graphing tools for users to visualize results generated by our functions and to have a better understanding of both the algorithm and the results.
+
+Additionally, we applied the CMPS package to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising since we were able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known-match (KM) comparisons and known-nonmatch (KNM) comparisons.
+However, the results of Hamby set 44 suggested that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment scale.
+This indicates that further research is needed to provide a comprehensive cross-validation on parameters used the algorithm.
+Moreover, we might want to compare the two versions of the CMPS algorithm in the future as well.
+
+The CMPS package as an open-source implementation introduces the CMPS algorithm to the `R` community and allows people to use it for their own projects.
+It would also facilitate future studies on parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can potentially be used to estimate error rates or define an identification criterion.
 

### 2021-06-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
update the title

@@
 ---
-title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet  = 
+title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets
 header-includes:

### 2021-06-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
added the CC coverpage; added appendix

@@
 
-# per R journal requirement, the bib filename should be the same as the output 
-# tex file. Don't forget to rename the bib file and change this example value.
 bibliography: CMPSpaper-writing.bib
-
 output: rticles::rjournal_article
+editor_options: 
+  chunk_output_type: inline
 ---
@@
 
+<!-- <div id="refs"></div> -->
+
+\newpage
+
+# Appendix
+
+```{r generate252, echo=TRUE, eval=FALSE}
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+###########
+# from the x3p data, re-run CMPS results for hamby 252
+hamby252_results <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby252_results.rds")
+
+b252.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+# generate bullet_id
+bulletid.tb <- b252.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# remove x3p files
+b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get bullet id
+b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
+
+# get all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# remove damaged data
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+# include tank-rashed data
+t1.df <-
+  read_rds("~/Research/CMPSpaper/preconsideration/t1.df.rds")
+tr.id <-
+  c(
+    t1.df %>% filter(type == "TR") %>% pull(scan_id) %>% as.character(),
+    "Br6-2-1",
+    "Br9-2-4"
+  )
+
+######################################
+# add ground-truth for hamby 252
+studyinfo <-
+  readxl::read_xlsx(
+    "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
+keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
+keyss <- tibble(specimen = keyss)
+keyss <- keyss %>% mutate(
+  barrel = specimen %>% str_split(" "),
+  barrel.id = purrr::map_chr(barrel, function(bb) {
+    bb[1]
+  }),
+  bullet.id = purrr::map_chr(barrel, function(bb) {
+    bb[3]
+  })
+) %>% select(-barrel)
+
+# obtain the matching keys
+keyss <- keyss %>% filter(!(bullet.id %>% str_detect("\\d+")))
+
+tmp.ukn <-
+  tibble(
+    col1 = tmp.tibble$bullet1 %>% str_extract(" [A-Z]") %>% str_trim(),
+    col2 = tmp.tibble$bullet2 %>% str_extract(" [A-Z]") %>% str_trim()
+  )
+
+# left join the ground truth
+tmp.tibble$b1t <-
+  tmp.ukn %>% left_join(keyss, by = c("col1" = "bullet.id")) %>%
+  pull(barrel.id) %>% str_remove("Brl")
+tmp.tibble$b2t <-
+  tmp.ukn %>% left_join(keyss, by = c("col2" = "bullet.id")) %>%
+  pull(barrel.id) %>% str_remove("Brl")
+
+# find KM KNM
+tmp.tibble <- tmp.tibble %>% mutate(
+  b1t = if_else(
+    is.na(b1t),
+    bullet1 %>% str_extract("Br\\d+") %>% str_remove("Br"),
+    b1t
+  ),
+  b2t = if_else(
+    is.na(b2t),
+    bullet2 %>% str_extract("Br\\d+") %>% str_remove("Br"),
+    b2t
+  ),
+  b1t = as.numeric(b1t),
+  b2t = as.numeric(b2t),
+  type_truth = if_else(b1t == b2t, "KM", "KNM")
+)
+
+### set up parameters
+N <- 4
+CMPS_hamby252_results <- list()
+CMPS_hamby252_results$span1 <- list(0.75, 0.25, 0.25, 0.15)
+CMPS_hamby252_results$signame <-
+  list("sigs75", "sigs25", "sigs25_1062", "sigs15")
+CMPS_hamby252_results$npeaks.set <-
+  list(c(5, 3, 1),
+       c(5, 3, 1),
+       c(10, 6, 2),
+       c(5,3,1))
+CMPS_hamby252_results$seg_length <- as.list(rep(50, 4))
+CMPS_hamby252_results$Tx <- as.list(rep(25, 4))
+CMPS_hamby252_results$titlee <- list()
+CMPS_hamby252_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby252_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby252_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby252_results$filename[[i]] <- 
+    paste(
+      "hamby252",
+      CMPS_hamby252_results$span1[[i]]*100,
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby252_results$seg_length[[i]],
+      CMPS_hamby252_results$Tx[[i]],
+      sep = "_"
+    )
+}
+CMPS_hamby252_results$cmps.table <- list()
+CMPS_hamby252_results$plot <- list()
+
+com.title252 <- expression(paste(
+  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
+
+for (i in 1:N) {
+  b252[[CMPS_hamby252_results$signame[[i]]]] <- purrr::map2(
+    .x = b252.full$ccdata,
+    .y = b252.full$grooves,
+    .f = function(x, y) {
+      cc_get_signature(
+        ccdata = x,
+        grooves = y,
+        span1 = CMPS_hamby252_results$span1[[i]],
+        span2 = 0.03
+      )
+    }
+  )
+
+  # process of removing outliers
+  tt <-
+    lapply(b252[[CMPS_hamby252_results$signame[[i]]]], function(x) {
+      x$sig
+    }) %>% unlist()
+  qtt <- quantile(tt, na.rm = TRUE)
+  multi.iqr <- 3
+  outrange <-
+    c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]), qtt[4] + multi.iqr * (qtt[4] -
+                                                                      qtt[2]))
+
+  b252 <- b252 %>% mutate(sigs_main = purrr::map(
+    .x = .data[[CMPS_hamby252_results$signame[[i]]]],
+    .f = function(x) {
+      tmp <- x$sig
+      tmp[tmp < outrange[1] | tmp > outrange[2]] <- NA
+      list(sig = tmp)
+    }
+  ))
+
+  # start the parallel computing
+  system.time({
+    tmp.252.list <- mclapply(p, function(cb.idx) {
+
+      tmp.lands <-
+        c(
+          b252 %>% filter(bullet_id %in% b.cb[, cb.idx][1]) %>% pull(scan_id),
+          b252 %>% filter(bullet_id %in% b.cb[, cb.idx][2]) %>% pull(scan_id)
+        )
+      tmp.comp <-
+        data.frame(expand.grid(land1 = tmp.lands[1:6], land2 = tmp.lands[7:12]),
+                   stringsAsFactors = FALSE)
+
+      tmp.comp$cmps <-
+        purrr::map2(
+          .x = tmp.comp$land1,
+          .y = tmp.comp$land2,
+          .f = function(xx, yy) {
+            sig1 <- b252$sigs_main[b252$scan_id == xx][[1]]$sig
+            sig2 <- b252$sigs_main[b252$scan_id == yy][[1]]$sig
+
+            extract_feature_cmps(
+              sig1,
+              sig2,
+              npeaks.set = CMPS_hamby252_results$npeaks.set[[i]],
+              seg_length = CMPS_hamby252_results$seg_length[[i]],
+              Tx = CMPS_hamby252_results$Tx[[i]],
+              include = "nseg"
+            )
+          }
+        )
+
+      tmp.comp <- tmp.comp %>%
+        mutate(
+          cmps_score = sapply(tmp.comp$cmps, function(x)
+            x$CMPS.score),
+          cmps_nseg = sapply(tmp.comp$cmps, function(x)
+            x$nseg)
+        )
+
+      cmps.table <-
+        tmp.comp %>% select(land1, land2, cmps_score, cmps_nseg)
+
+      tibble(
+        bullet1 = b.cb[, cb.idx][1],
+        bullet2 = b.cb[, cb.idx][2],
+        cmps.table = list(cmps.table)
+      )
+    }, mc.cores = detectCores())
+  })
+
+  hamby252.cmps <- do.call(rbind, tmp.252.list)
+
+  ##################################################
+  # before removing tank-rashed data
+  hamby252.cmps <- hamby252.cmps %>% mutate(
+    cmps.max = cmps.table %>% purrr::map_dbl(
+      .f = function(t) {
+        max(t$cmps_score)
+      }
+    ),
+    cmps.maxbar = cmps.table %>% purrr::map_dbl(
+      .f = function(t) {
+        landidx1 <-
+          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        landidx2 <-
+          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        compute_average_scores(landidx1, landidx2, t$cmps_score) %>% max()
+      }
+    )
+  )
+
+  hamby252.cmps$cmps.table.m <-
+    lapply(hamby252.cmps$cmps.table, function(tt) {
+      tt.idx <- tt %>% rowid_to_column %>%
+        filter(land1 %in% tr.id | land2 %in% tr.id) %>% pull(rowid)
+      tt[tt.idx, "cmps_score"] <- NA
+      tt
+    })
+
+  # after removing tank-rashed data
+  hamby252.cmps <- hamby252.cmps %>% mutate(
+    cmps.max.m = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        max(t$cmps_score, na.rm = TRUE)
+      }
+    ),
+    cmps.maxbar.m = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        landidx1 <-
+          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        landidx2 <-
+          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        compute_average_scores(
+          landidx1, landidx2, t$cmps_score, addNA = TRUE
+        ) %>% max()
+      }
+    )
+  )
+
+  # add type and type_truth
+  hamby252.cmps$type <- tmp.tibble$type
+  hamby252.cmps$type_truth <- tmp.tibble$type_truth
+
+  ###################################
+  # save result in a list
+  CMPS_hamby252_results$cmps.table[[i]] <- hamby252.cmps
+
+}
+
+################################
+# save data as csv
+data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/"
+
+for(i in 1:N){
+  write.csv(
+    CMPS_hamby252_results$cmps.table[[i]] %>% 
+      select(-cmps.table, -cmps.table.m) %>% as.data.frame(),
+    file = paste(
+      data_path, CMPS_hamby252_results$filename[[i]], 
+      ".csv", sep = ""))
+}
+
+#################################################
+# generate plots
+for (i in 1:3) {
+  hamby252.cmps <- CMPS_hamby252_results$cmps.table[[i]]
+
+  hamby252.plot.list <- list()
+  titlee <- CMPS_hamby252_results$titlee[[i]]
+
+  hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.max.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      fill = "Comparison Type",
+      x = expression(CMPS[max]),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 27, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank()) +
+    font("x.text", size = 6)
+
+  hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.maxbar.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      x = expression(bar(CMPS)[max]),
+      fill = "Comparison Type",
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 24, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank())
+
+  plot <- ggarrange(plotlist = hamby252.plot.list,
+                    nrow = 1,
+                    ncol = 2,
+                    common.legend = TRUE, legend = "bottom")
+  plot <- annotate_figure(plot, 
+                          top = text_grob(com.title252))
+  CMPS_hamby252_results$plot[[i]] <- plot
+}
+
+```
+
+```{r generate44, echo=TRUE, eval=FALSE}
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+###########
+# from the x3p data, re-run CMPS results for hamby 44
+b44.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+
+# rds file that stores indices of damaged scans
+idf.idx <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/idfidx.rds")
+
+idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+
+# generate bullet_id
+bulletid.tb <- b44.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+N <- 3
+CMPS_hamby44_results <- list()
+CMPS_hamby44_results$span1 <- list(0.25, 0.25, 0.75)
+CMPS_hamby44_results$signame <-
+  list("sigs25_531", "sigs25_1061", "sigs75_531")
+CMPS_hamby44_results$npeaks.set <-
+  list(c(5, 3, 1),
+       c(10, 6, 1),
+       c(5, 3, 1))
+CMPS_hamby44_results$seg_length <- as.list(rep(61, 3))
+CMPS_hamby44_results$Tx <- as.list(rep(30, 3))
+CMPS_hamby44_results$titlee <- list()
+CMPS_hamby44_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby44_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby44_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby44_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby44_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby44_results$filename[[i]] <- 
+    paste(
+      "hamby44",
+      CMPS_hamby44_results$span1[[i]]*100,
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby44_results$seg_length[[i]],
+      CMPS_hamby44_results$Tx[[i]],
+      sep = "_"
+    )
+}
+CMPS_hamby44_results$cmps.table <- list()
+CMPS_hamby44_results$plot <- list()
+
+com.title44 <- expression(paste(
+  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
+
+# remove x3p files
+b44 <- b44.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get all comparisons
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# get ground-truth
+key.table <- tibble(
+  bullet.id = c(
+    "K",
+    "O",
+    "L",
+    "P",
+    "J",
+    "H",
+    "I",
+    "Y",
+    "G",
+    "E",
+    "U",
+    "X",
+    "F",
+    "T",
+    "S"
+  ),
+  barrel.id = c(1, 2, 3, 4, 4, 5, 5, 6, 6, 7, 7, 7, 8, 9, 10)
+)
+
+tmp.table.44 <- tibble(bullet1 = b.cb[1, ],
+                       bullet2 = b.cb[2, ])
+
+tmp.table.44$b1t <-
+  tmp.table.44$bullet1 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+tmp.table.44$b2t <-
+  tmp.table.44$bullet2 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+
+tmp.table.44$b1b <-
+  tmp.table.44 %>% 
+  left_join(key.table, by = c("b1t" = "bullet.id")) %>% 
+  pull(barrel.id)
+tmp.table.44$b2b <-
+  tmp.table.44 %>% 
+  left_join(key.table, by = c("b2t" = "bullet.id")) %>% 
+  pull(barrel.id)
+
+tmp.table.44 <- tmp.table.44 %>% mutate(
+  b1b = if_else(
+    is.na(b1b),
+    bullet1 %>% str_extract("Barrel \\d+") %>% 
+      str_extract("\\d+") %>% as.numeric(),
+    b1b
+  ),
+  b2b = if_else(
+    is.na(b2b),
+    bullet2 %>% str_extract("Barrel \\d+") %>% 
+      str_extract("\\d+") %>% as.numeric(),
+    b2b
+  ),
+  type_truth = if_else(b1b == b2b, "KM", "KNM")
+)
+
+tmp.table.44 <- tmp.table.44 %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])") ==
+      bullet2 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(
+    bullet1 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])") == "Unknowns B" | 
+      bullet2 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])") == "Unknowns B", 
+    "UKN", 
+    type
+  )
+)
+
+for (i in 1:N) {
+  b44[[CMPS_hamby44_results$signame[[i]]]] <- purrr::map2(
+    .x = b44.full$ccdata,
+    .y = b44.full$grooves,
+    .f = function(x, y) {
+      cc_get_signature(
+        ccdata = x,
+        grooves = y,
+        span1 = CMPS_hamby44_results$span1[[i]],
+        span2 = 0.03
+      )
+    }
+  )
+
+  # process of removing outliers
+  tt <-
+    lapply(b44[[CMPS_hamby44_results$signame[[i]]]], function(x) {
+      x$sig
+    }) %>% unlist()
+  qtt <- quantile(tt, na.rm = TRUE)
+  multi.iqr <- 3
+  outrange <-
+    c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]),
+      qtt[4] + multi.iqr * (qtt[4] - qtt[2]))
+
+  b44 <- b44 %>% mutate(sigs_main = purrr::map(
+    .x = .data[[CMPS_hamby44_results$signame[[i]]]],
+    .f = function(x) {
+      tmp <- x$sig
+      tmp[tmp < outrange[1] | tmp > outrange[2]] <- NA
+      list(sig = tmp)
+    }
+  ))
+
+  ## parallel setup
+  cl <- makeCluster(7)
+
+  par.setup <- parLapply(cl, 1:length(cl),
+                         function(xx) {
+                           library(tidyverse)
+                           library(bulletxtrctr)
+                           library(x3ptools)
+                           library(CMPS)
+                         })
+
+  clusterExport(cl,
+                c("b44", "b.cb", "p",
+                  "CMPS_hamby44_results", "i"),
+                envir = globalenv())
+
+  # start the parallel computing
+  system.time({
+    tmp.44.list <- parLapply(cl, p, function(cb.idx) {
+      tmp.lands <-
+        c(
+          b44 %>% filter(bullet_id %in% b.cb[, cb.idx][1]) %>% pull(scan_id),
+          b44 %>% filter(bullet_id %in% b.cb[, cb.idx][2]) %>% pull(scan_id)
+        )
+      tmp.comp <-
+        data.frame(expand.grid(land1 = tmp.lands[1:6], land2 = tmp.lands[7:12]),
+                   stringsAsFactors = FALSE)
+
+      tmp.comp$cmps <-
+        purrr::map2(
+          .x = tmp.comp$land1,
+          .y = tmp.comp$land2,
+          .f = function(xx, yy) {
+            sig1 <- b44$sigs_main[b44$scan_id == xx][[1]]$sig
+            sig2 <- b44$sigs_main[b44$scan_id == yy][[1]]$sig
+
+            extract_feature_cmps(
+              sig1,
+              sig2,
+              npeaks.set = CMPS_hamby44_results$npeaks.set[[i]],
+              seg_length = CMPS_hamby44_results$seg_length[[i]],
+              Tx = CMPS_hamby44_results$Tx[[i]],
+              include = "nseg"
+            )
+          }
+        )
+
+      tmp.comp <- tmp.comp %>%
+        mutate(
+          cmps_score = sapply(tmp.comp$cmps, function(x)
+            x$CMPS.score),
+          cmps_nseg = sapply(tmp.comp$cmps, function(x)
+            x$nseg)
+        )
+
+      cmps.table <-
+        tmp.comp %>% select(land1, land2, cmps_score, cmps_nseg)
+
+      tibble(
+        bullet1 = b.cb[, cb.idx][1],
+        bullet2 = b.cb[, cb.idx][2],
+        cmps.table = list(cmps.table)
+      )
+    })
+  })
+
+  hamby44.cmps <- do.call(rbind, tmp.44.list)
+
+  stopCluster(cl)
+
+  ##################################################
+  # before removing tank-rashed data
+  hamby44.cmps <- hamby44.cmps %>% mutate(
+    cmps.max = cmps.table %>% purrr::map_dbl(
+      .f = function(t) {
+        max(t$cmps_score)
+      }
+    ),
+    cmps.maxbar = cmps.table %>% purrr::map_dbl(
+      .f = function(t) {
+        landidx1 <-
+          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        landidx2 <-
+          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        compute_average_scores(landidx1, landidx2, t$cmps_score) %>% max()
+      }
+    )
+  )
+
+  hamby44.cmps$cmps.table.m <-
+    lapply(hamby44.cmps$cmps.table, function(tt) {
+      tt.idx <- tt %>% rowid_to_column %>%
+        filter(land1 %in% idf.scan_id |
+                 land2 %in% idf.scan_id) %>% pull(rowid)
+      tt[tt.idx, "cmps_score"] <- NA
+      tt
+    })
+
+  # after removing tank-rashed data
+  hamby44.cmps <- hamby44.cmps %>% mutate(
+    cmps.max.m = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        max(t$cmps_score, na.rm = TRUE)
+      }
+    ),
+    cmps.maxbar.m = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        landidx1 <-
+          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        landidx2 <-
+          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        compute_average_scores(
+          landidx1, landidx2, t$cmps_score, addNA = TRUE
+        ) %>% max()
+      }
+    )
+  )
+
+  # add groundtruth
+  hamby44.cmps$type_truth <- tmp.table.44$type_truth
+  hamby44.cmps$type <- tmp.table.44$type
+
+  # save result in a list
+  CMPS_hamby44_results$cmps.table[[i]] <- hamby44.cmps
+
+}
+
+################################
+# save data as csv
+data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/"
+
+for(i in 1:N){
+  write.csv(
+    CMPS_hamby44_results$cmps.table[[i]] %>% 
+      select(-cmps.table, -cmps.table.m) %>% 
+      as.data.frame(),
+    file = paste(data_path, 
+                 CMPS_hamby44_results$filename[[i]], 
+                 ".csv", sep = ""))
+}
+
+#################################################
+# generate plots
+for (i in 1:3) {
+  hamby44.cmps <- CMPS_hamby44_results$cmps.table[[i]]
+
+  hamby44.plot.list <- list()
+  titlee <- CMPS_hamby44_results$titlee[[i]]
+
+  hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.max.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      fill = "Comparison Type",
+      x = expression(CMPS[max]),
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 27, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank()) +
+    font("x.text", size = 6)
+
+  hamby44.plot.list[[2]] <- hamby44.cmps %>% ggplot() +
+    geom_histogram(aes(x = cmps.maxbar.m,
+                       fill = as.factor(type_truth)), binwidth = 1) +
+    labs(
+      x = expression(bar(CMPS)[max]),
+      fill = "Comparison Type",
+      subtitle = titlee
+    ) +
+    scale_x_continuous(breaks = seq(0, 24, 1)) +
+    theme_bw() +
+    theme(panel.grid.minor = element_blank())
+
+  plot <- ggarrange(plotlist = hamby44.plot.list,
+                    nrow = 1,
+                    ncol = 2,
+                    common.legend = TRUE, legend = "bottom")
+  plot <- annotate_figure(plot, 
+                          top = text_grob(com.title44))
+  CMPS_hamby44_results$plot[[i]] <- plot
+}
+
+```
+
+\newpage
+
 <!-- open source -->
@@
 
-### About this format and the R Journal requirements
-
-`rticles::rjournal_article` will help you build the correct files requirements:
-
-* A R file will be generated automatically using `knitr::purl` - see
-https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information.
-* A tex file will be generated from this Rmd file and correctly included in
-`RJwapper.tex` as expected to build `RJwrapper.pdf`.
-* All figure files will be kept in the default rmarkdown `*_files` folder. This
-happens because `keep_tex = TRUE` by default in `rticles::rjournal_article`
-* Only the bib filename is to modifed. An example bib file is included in the
-template (`RJreferences.bib`) and you will have to name your bib file as the
-tex, R, and pdf files.
+<!-- ### About this format and the R Journal requirements -->
+
+<!-- `rticles::rjournal_article` will help you build the correct files requirements:  -->
+
+<!-- * A R file will be generated automatically using `knitr::purl` - see -->
+<!-- https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information. -->
+<!-- * A tex file will be generated from this Rmd file and correctly included in -->
+<!-- `RJwapper.tex` as expected to build `RJwrapper.pdf`. -->
+<!-- * All figure files will be kept in the default rmarkdown `*_files` folder. This -->
+<!-- happens because `keep_tex = TRUE` by default in `rticles::rjournal_article` -->
+<!-- * Only the bib filename is to modifed. An example bib file is included in the -->
+<!-- template (`RJreferences.bib`) and you will have to name your bib file as the -->
+<!-- tex, R, and pdf files. -->

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of comments

@@
 
-Besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx`, the function `extract_feature_cmps` allows for the following input from users:\wj{XXX the code text is a little bit off}
-
-* `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
-
-* `include` determines the output of the function.
-Besides the `CMPS.score`, many details of the comparison might be used to understand how the `CMPS.score` is computed.
-By default, `include = NULL` and the function output will only contain the `CMPS.score`; `include` can also be (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
-if `"full_result"` (or its abbreviation) is specified, the ouput will include everything listed below.
-  - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
+The function `extract_feature_cmps` allows for the following input from users besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx`:
+
+* `x` and `y` are  two  signatures:  `x` serves as the reference signature (which will be divided into basis segments) and `y` is the comparison signature;
+
+* `include` determines the \hh{format of the function result}.
+Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed.
+By default `include` is set to `NULL` and  only  the `CMPS.score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
+If `include` is specified as `"full_result"` (or its abbreviation), the ouput includes everything listed below.
+  - `nseg`: the number of basis segments  from the reference signature; this is also the highest possible CMPS score of the comparison;
   - `congruent.pos`: the congruent registration position;
@@
   - `ccp.list`: a list showing identified candidate positions of all basis segments; 
-  - `pos.df`: a data frame containing all candidate positions and the number of votes they received;
+  - `pos.df`: a data frame containing all candidate positions and their respective number of votes;
   - `segments`: a list containing all basis segments;
@@
 
-\wj{In the remainder of the paper we showcase the use of the CMPS functionality on some examples and present the results of applying it to two datasets.}
+In the remainder of the paper we showcase the use of the CMPS functionality on some examples and present the results of applying it to two datasets.
 <!-- \hh{XXX you need a bit of an overview here on the structure of what is coming next: in the remainder of the paper we showcase the use of the CMPS functionality on some examples ...} -->
@@
 
-\wj{revised the following}
-In the first example, `npeaks.set` is a vector of three integers.
-This means that  the algorithm uses the multi-segment lengths strategy to create `cmps_with_multi_scale`, while for `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
+In the first example, `npeaks.set` is a vector of three integers, i.e.
+the algorithm uses the multi-segment lengths strategy to create the result object `cmps_with_multi_scale`.
+For `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
 We use `include = "full_result"` to capture all results.
-In this example, the `cmps_with_multi_scale$CMPS.score` is 9, while `cmps_without_multi_scale$CMPS.score` is 12.
-\wj{As discussed in} @cmps, \wj{using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
+In this example, the CMPS is 9 when using multiple segments, and 12 when using a single segment.
+As discussed in @cmps, using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
 As the number of false positives is reduced the number of false negatives might rise.
 More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
-Note that the multi scale method might also be slower because the algorithm is run a couple of times.}
+Note, that the multi scale method is slower because the algorithm is run once for each segment length.
 

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

@@
         -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale.
+        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks \hh{at the first level}, double the segment length and recalculate the cross-correlation function, then identify 3 peaks \hh{at the second level} and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level.
 \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
@@
 The procedure for generating signatures from high-resolution 3D topographic scans of bullet lands used here follows the methodology described in @aoas (as discussed above).
-The two bullets under consideration here are known to have been fired from the same gun barrel, so for the 36 land-by-land comparisons, 6 comparison are from same-source pairs (known matches) while 30 are from different-source pairs (known non-matches).
+The two bullets under consideration are known to have been fired from the same gun barrel, so for the 36 pairwise land-by-land comparisons, six comparison are from same-source pairs (known matches) while thirty are from different-source pairs (known non-matches).
 To access the example data, we use
@@
 
-`bullets$sigs` is a list of 12 numeric vectors corresponding to 12 bullet signatures as shown in \autoref{fig:sigs}.
+`bullets$sigs` is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in \autoref{fig:sigs}.
 `bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].
@@
 
-*   The first element is a plot called `segment_shift_plot`, which is shown in \autoref{fig:sigplot}.
-On this plot only the congruent matching profile segments are plotted along with the comparison signature at the congruent registration position.
+*   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}.
+On this plot the reference signature is drawn as a black line,  congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.
 
@@
 
-*   The second element is a plot called `signature_shift_plot`, which is shown in \autoref{fig:sigplot2}.
-On this visual both the reference signature and the comparison signature are plotted.
-The reference signature is aligned with the comparison signature based on the congruent registration position.
-And the congruent matching profile segments are highlighted with solid lines.
+*   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}.
+This visual presents both the reference signature and the comparison signature.
+The comparison signature is aligned with the reference signature based on the congruent registration position.
+Congruent matching profile segments are highlighted by  solid red lines.
 
@@
 
-As `cmps_signature_plot()` focuses on the signature level, on the other hand, `cmps_segment_plot()` focuses on the segment level.
-It not only takes the "full result" of `extract_feature_cmps()`, but also takes an argument `seg.idx`, indicating which segment to be inspected.
-As shown in \autoref{fig:segplots}, for example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments.
-So we can set `seg.idx = 6` in order to take a closer look at segment 6 and understand the reason why it disagrees with the congruent registration position.
-`cmps_segment_plot()` also returns a list, of which each element corresponds to one segment scale of this basis segment.
+While `cmps_signature_plot()` focuses on the signature level,  `cmps_segment_plot()` focuses on the segment level.
+It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg.idx`, indicating which segment should be inspected.
+When checking `sig.plot$seg_shift` we notice that  segment number 6 is not one of the congruent matching profile segments.
+We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
+\autoref{fig:segplots}  shows the top five registration positions for segment number 6 overlaid on top of the reference signature using hashed lines, the solid line in black shows the original position of the segment (which in this instance is close to the actual registration position).
 Then at each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
typo fixed
fished out a couple more of the scales. Lots more there.

@@
 The section "Implementation" will go through the algorithm and show how to use the "CMPS" package.
-An further example that illustrates the main points are also included.
+A further example that illustrates the main points are also included.
 The section "Results" presents the results of evaluating the CMPS package using Hamby set 252 and Hamby set 44.
@@
         -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks \hh{at the first level}, double the segment length and recalculate the cross-correlation function, then identify 3 peaks \hh{at the second level} and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level.
-\autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+\autoref{fig:seg_all} shows an example of 3 levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
         -   `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the comparison signature and finds peaks in the cross-correlation curve.
@@
 We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
-\autoref{fig:segplots}  shows the top five registration positions for segment number 6 overlaid on top of the reference signature using hashed lines, the solid line in black shows the original position of the segment (which in this instance is close to the actual registration position).
-Then at each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.
-
-*   \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at scale one (its original scale).
-Since when computing the CMPS score we used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()`, 5 peaks are identified in the cross-correlation curve at scale one, and segment 6 at scale one is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
+For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in \autoref{fig:segplots} for the example of segment number 6:
+
+*   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (the top level).
+We used  `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
+Therefore the top five peaks are identified in the cross-correlation curve at level one.
+Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
+The solid black line shows the segment at its original position (which in this example is very close to the actual registration position).
 
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1.
+\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at level 1.
 The five highest peaks are marked by dots.
-The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in its highest segment scale; the blue dashed lines show the tolerance zone around the green dashed line.
-We can see here none of the five highest peaks at scale one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
+We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
 Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
@@
 \end{subfigure}
-\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at scale one}
+\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
 \end{figure}
 
-Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment scales together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
+Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
 

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
change the usage of level/scale

@@
         -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks \hh{at the first level}, double the segment length and recalculate the cross-correlation function, then identify 3 peaks \hh{at the second level} and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level.
-\autoref{fig:seg_all} shows an example of 3 levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks at the first level, double the segment length and recalculate the cross-correlation function, then identify 3 peaks at the second level and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level.
+\autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
         -   `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the comparison signature and finds peaks in the cross-correlation curve.
@@
 `segments`, `seg_scale`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the comparison signature.
-If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each scale of the basis segment.
+If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment.
 The resulting list is called `ccr.list`.
-    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment scales.
-Note that in @cmps, a segment at its largest scale always identifies one peak.
-        -   the scaled version of a basis segment is obtained by using function `get_seg_scale(segments, nseg, scale = 2)`.
+    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak.
+        -   the function `get_seg_scale(segments, nseg, scale = 2)` is used to obtain the scaled version of a basis segment.
 `segments` is a list containing all basis segments, generated by the function `get_segs(...)` in step 1; `nseg` is an integer indicating which basis segment the function should work with.
@@
 
-Note that there are \hh{several} parameters in the CMPS algorithm \hh{that are left to} the users \hh{to decide}, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each scale level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
+Note that there are \hh{several} parameters in the CMPS algorithm \hh{that are left to} the users \hh{to decide}, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
@@
 
-# algorithm with multi-peak insepction at three different segment scales
+# algorithm with multi-peak insepction at three different segment levels
 cmps_with_multi_scale <- 
@@
 More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
-Note, that the multi scale method is slower because the algorithm is run once for each segment length.
+Note, that the multi-segment lengths method is slower because the algorithm is run once for each segment length.
 
@@
 We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
-For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in \autoref{fig:segplots} for the example of segment number 6:
-
-*   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (the top level).
-We used  `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
-Therefore the top five peaks are identified in the cross-correlation curve at level one.
-Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
-The solid black line shows the segment at its original position (which in this example is very close to the actual registration position).
+\autoref{fig:segplots}  shows the top five registration positions for segment number 6 overlaid on top of the reference signature using hashed lines, the solid line in black shows the original position of the segment (which in this instance is close to the actual registration position).
+Then at each segment level, we will have two plots, `segment_plot` and `scale_ccf_plot`.
+
+*   \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at level one (in its original length).
+Since when computing the CMPS score we used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()`, 5 peaks are identified in the cross-correlation curve at level one, and segment 6 at level one is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
 
@@
 
-*   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at scale one.
-It shows the cross-correlation curve computed by the comparison signature and the scale-one basis segment 6.
+*   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
+It shows the cross-correlation curve computed by the comparison signature and the level-one basis segment 6.
 The five highest peaks are marked by dots on the curve.
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot}segment\_plot for segment 6 at scale 1.
+\caption{\label{fig:segplot}segment\_plot for segment 6 at level one.
 The original position of segment 6 is indicated by the solid black line.
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at level 1.
+\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at level one.
 The five highest peaks are marked by dots.
-The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
-We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in its highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
+We can see here none of the five highest peaks at level one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
 Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
@@
 ```
-\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three scales together.
-We are identifying five highest peaks at scale one, three peaks at scale two, and one peak at scale three since npeaks.set = c(5, 3, 1).
-The highest peak position at scale three is marked by the green dashed line across all segment scales, but it doesn't achieve the top five highest peaks at scale one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
+\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
+We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1).
+The highest peak position at level three is marked by the green dashed line across all segment levels, but it doesn't achieve the top five highest peaks at level one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
 \end{figure}
@@
 In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
-We can see that the basis segment 6 does obtain a peak near the congruent registration position at scale two and scale three, respectively; however, this position doesn't give one of the five highest peaks at scale one.
+We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one.
 As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy.
-The identified top five peaks at scale one are also examples of "false positive" peaks.
-The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at scale two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.
+The identified top five peaks at level one are also examples of "false positive" peaks.
+The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.
 
@@
 Additionally, we applied the CMPS package to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising since we were able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known-match (KM) comparisons and known-nonmatch (KNM) comparisons.
-However, the results of Hamby set 44 suggested that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment scale.
+However, the results of Hamby set 44 suggested that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment level.
 This indicates that further research is needed to provide a comprehensive cross-validation on parameters used the algorithm.

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
thanks added

--- 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
     - Ames, IA 50011
+thanks: |
+  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 abstract: >
@@
 ```
-\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three scales together.
-We are identifying five highest peaks at scale one, three peaks at scale two, and one peak at scale three since npeaks.set = c(5, 3, 1).
-The highest peak position at scale three is marked by the green dashed line across all segment scales, but it doesn't achieve the top five highest peaks at scale one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
+\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
+We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since `npeaks.set = c(5, 3, 1)`.
+The highest peak position at scale three is marked by the green dashed line across all segment scales.
+However, the highest peak on level 3 does not coincide with any of the top five highest peaks at level one.
+This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
 \end{figure}

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd

--- 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
-\autoref{fig:segplots}  shows the top five registration positions for segment number 6 overlaid on top of the reference signature using hashed lines, the solid line in black shows the original position of the segment (which in this instance is close to the actual registration position).
-Then at each segment level, we will have two plots, `segment_plot` and `scale_ccf_plot`.
-
-*   \autoref{fig:segplot} is the `segment_plot` of basis segment 6 at level one (in its original length).
-Since when computing the CMPS score we used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()`, 5 peaks are identified in the cross-correlation curve at level one, and segment 6 at level one is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
-
-<!-- Take the first element of `seg.plot` as an example, it corresponds to the first segment scale (the original scale) of the 6th basis segment and carries two plots, `segment_plot` and `scale_ccf_plot`.
--->
-<!-- Remember that when computing the CMPS score, we were using `npeaks.set = c(5, 3, 1)`.
-This means that for the first segment scale, 5 peaks are identified in the cross-correlation curve.
-`segment_plot` plots the 6th basis segment in its first scale at its original position as well as the positions where the basis segment obtains its 5 cross-correlation peaks.
--->
-
+
+For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in \autoref{fig:segplots} for the example of segment number 6:
+
+*   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length).
+We used  `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
+Therefore the top five peaks are identified in the cross-correlation curve at level one.
+Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
+The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
 *   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
@@
 The five highest peaks are marked by dots.
-The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in its highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
-We can see here none of the five highest peaks at level one is within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
+We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
 Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd

@@
 \caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1).
-The highest peak position at level three is marked by the green dashed line across all segment levels, but it doesn't achieve the top five highest peaks at level one, indicating that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
+We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since `npeaks.set = c(5, 3, 1)`.
+The highest peak position at level three is marked by the green dashed line across all segment levels.
+However, the highest peak on level three does not coincide with any of the top five highest peaks at level one.
+This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
 \end{figure}

### 2021-06-08 reproducible/hamby252_result_generater.R
added codes and data for reproducibility

@@ -1,0 +1,370 @@
+##########################
+# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
+#       These rds files contain processed bullet signatures used in the paper
+#       The original data contains x3p objects of large size, so they are not
+#       uploaded to the Github repo
+##########################
+
+## Load the required packages
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+#### code used to load the original data; commented out
+# b252.full <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./reproducible/bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
+keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
+keyss <- tibble(specimen = keyss)
+keyss <- keyss %>% mutate(
+  barrel = specimen %>% str_split(" "),
+  barrel.id = purrr::map_chr(barrel, function(bb) {
[…]

### 2021-06-08 reproducible/hamby44_result_generater.R

@@ -1,0 +1,385 @@
+##########################
+# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
+#       These rds files contain processed bullet signatures used in the paper
+#       The original data contains x3p objects of large size, so they are not
+#       uploaded to the Github repo
+##########################
+
+
+## Load the required packages
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+#### code used to load the original data; commented out
+# b44.full <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
+                "J",
+                "H",
+                "I",
+                "Y",
+                "G",
+                "E",
+                "U",
+                "X",
+                "F",
+                "T",
+                "S"),
+  barrel.id = c(1, 2, 3, 4, 4, 5, 5, 6, 6, 7, 7, 7, 8, 9, 10)
+)
+
+tmp.table.44 <- tibble(bullet1 = b.cb[1,],
+                       bullet2 = b.cb[2,])
+
+tmp.table.44$b1t <-
+  tmp.table.44$bullet1 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+tmp.table.44$b2t <-
[…]

### 2021-06-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
added codes and data for reproducibility
removed appendix; switched the usage of reference and comparison; added link to the github repo

@@
 Bullet profiles are shown in panels (b), (c), and (d) of \autoref{fig:process}, while \autoref{fig:process}(f) shows the corresponding bullet signature.
-Identifiying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
+Identifying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
 To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny],  `bulletinspectR` to identify and correct those errors.
-\hh{An example of the extraction process with corresponding code and parameter settings can be found at XXX.}
+An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
 Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
@@
  The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
-The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the reference   and  for each segment find the "best" registration position on the comparison  (the other bullet signature) with respect to their cross-correlation values.
+The algorithm's main idea  is to take a set of consecutive and non-overlapping basis segments from  the comparison  and  for each segment find the "best" registration position on the reference  (the other bullet signature) with respect to their cross-correlation values.
 From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
+\wj{XXX Note that researchers in} @cmps \wj{refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.}
   High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.
-\wj{However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparison is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
+\wj{However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
 Further research is needed to understand how to determine the threshold.
@@
 Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm \hh{in the R package CMPS available from XXX github / CRAN}. 
+Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package CMPS available from Github \url{https://github.com/willju-wangqian/CMPS}
 With our implementation, one can compute the CMPS score of a comparison using the following code:
@@
 
-1. **cut the reference signature into consecutive, non-overlapping and equal-length basis segments:**
+1. **cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:**
 The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
@@
 2.
-**identify candidate positions:** For each basis segment a set of candidate registration  positions on the comparison signature is identified based on the segment's similarity to the comparison.
-In a first step, the cross-correlation function of the segment to the comparison is calculated, then a number of positions with high correlation values are identified as candidate positions.
+**identify candidate positions:** For each basis segment a set of candidate registration  positions on the comparison signature is identified based on the segment's similarity to the reference signature.
+In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
 In case multiple segment lengths are considered, the length of each basis segment is doubled and these two steps are repeated.
@@
 \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
-    + **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the comparison signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
+    + **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
 The position indicates the lag by which a basis segment is moved with respect to its original placement.
-A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the comparison.
+A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the reference.
     + **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
@@
 \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
-        -   `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the comparison signature and finds peaks in the cross-correlation curve.
+        -   `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the reference signature and finds peaks in the cross-correlation curve.
 The number of peaks detected is equal to `npeaks`, which is an integer.
-`segments`, `seg_scale`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the comparison signature.
+`segments`, `seg_scale`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature.
 If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment.
@@
 **determine the congruent registration position:** A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
-Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*,  indicating that most of the basis segments find their highly similar counterpart in the comparison signature in terms of correlation at this registration position.
+Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*,  indicating that most of the basis segments find their highly similar counterpart in the reference signature in terms of correlation at this registration position.
 In case of ties the middle position is taken as the congruent registration position.
@@
 
-* `x` and `y` are  two  signatures:  `x` serves as the reference signature (which will be divided into basis segments) and `y` is the comparison signature;
+* `x` and `y` are  two  signatures:  `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;
 
@@
 If `include` is specified as `"full_result"` (or its abbreviation), the ouput includes everything listed below.
-  - `nseg`: the number of basis segments  from the reference signature; this is also the highest possible CMPS score of the comparison;
+  - `nseg`: the number of basis segments  from the comparison signature; this is also the highest possible CMPS score of the comparison;
   - `congruent.pos`: the congruent registration position;
@@
 The procedure for generating signatures from high-resolution 3D topographic scans of bullet lands used here follows the methodology described in @aoas (as discussed above).
-The two bullets under consideration are known to have been fired from the same gun barrel, so for the 36 pairwise land-by-land comparisons, six comparison are from same-source pairs (known matches) while thirty are from different-source pairs (known non-matches).
+The two bullets under consideration are known to have been fired from the same gun barrel, so for the 36 pairwise land-by-land comparisons, six comparisons are from same-source pairs (known matches) while thirty are from different-source pairs (known non-matches).
 To access the example data, we use
@@
 The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
-This comparison is one of a pair of signatures that are known to be a match -- a KM (known match) comparison.
+This comparison consists of a pair of signatures that are known to be a match -- a KM (known match) comparison.
 We compute the CMPS score using two versions of the CMPS algorithm:
@@
 `cmps_signature_plot()` takes the output of `extract_feature_cmps(..., include = "full_result")` and returns a list of 5 elements.
-It creates an overall impression of how the reference signature aligns with the comparison signature at the congruent registration position.
+It creates an overall impression of how the comparison signature aligns with the reference signature at the congruent registration position.
 
@@
 *   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}.
-This visual presents both the reference signature and the comparison signature.
+This visual presents both the comparison signature and the reference signature.
 The comparison signature is aligned with the reference signature based on the congruent registration position.
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot2}The black line shows the comparison signature; the red line shows the reference signature.
+\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature.
 Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
@@
 *   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
-It shows the cross-correlation curve computed by the comparison signature and the level-one basis segment 6.
+It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6.
 The five highest peaks are marked by dots on the curve.
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at level one.
+\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one.
 The five highest peaks are marked by dots.
@@
 \caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since `npeaks.set = c(5, 3, 1)`.
+We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1).
 The highest peak position at level three is marked by the green dashed line across all segment levels.
@@
 In general, we assume each bullet has $n$ land engravings (in our case $n=6$).
-Let $c_{ij}$ denote the CMPS score of comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
+Let $c_{ij}$ denote the CMPS score of a comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
 Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and $\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}$, where $\mathbbm{1}_A$ denotes an indicator function.
@@
 
-\wj{The codes generating those results can be found in the appendix.XXX}
+The codes generating those results can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
 
@@
 It would also facilitate future studies on parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can potentially be used to estimate error rates or define an identification criterion.
-
-<!-- <div id="refs"></div> -->
-
-\newpage
-
-# Appendix
-
-```{r generate252, echo=TRUE, eval=FALSE}
-library(tidyverse)
-library(bulletxtrctr)
-library(x3ptools)
-library(CMPS)
-library(ggpubr)
-library(parallel)
-
-###########
-# from the x3p data, re-run CMPS results for hamby 252
-hamby252_results <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/hamby252_results.rds")
-
-b252.full <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
-
-# generate bullet_id
-bulletid.tb <- b252.full %>% select(scan_id)
-bulletid.tb <- bulletid.tb %>% mutate(
-  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
-  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
-  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
-  bullet_id = paste(barrel_id, bullet)
-)
-
-# remove x3p files
-b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
-
-# get bullet id
-b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
-
-# get all comparisons
-b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-# remove damaged data
-tmp.tibble <- tibble(bullet1 = b.cb[1,], 
-                     bullet2 = b.cb[2,])
-
-tmp.tibble <- tmp.tibble %>% mutate(
-  type = if_else(
-    bullet1 %>% str_extract("Br\\d+") ==
-      bullet2 %>% str_extract("Br\\d+"),
-    "KM",
-    "KNM"
-  ),
-  type = if_else(is.na(type), "Ukn", type)
-)
-
-# include tank-rashed data
-t1.df <-
-  read_rds("~/Research/CMPSpaper/preconsideration/t1.df.rds")
-tr.id <-
-  c(
-    t1.df %>% filter(type == "TR") %>% pull(scan_id) %>% as.character(),
-    "Br6-2-1",
-    "Br9-2-4"
-  )
-
-######################################
-# add ground-truth for hamby 252
-studyinfo <-
-  readxl::read_xlsx(
-    "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
-    sheet = 3,
-    skip = 1
-  )
-
-keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
-keyss <- tibble(specimen = keyss)
-keyss <- keyss %>% mutate(
-  barrel = specimen %>% str_split(" "),
-  barrel.id = purrr::map_chr(barrel, function(bb) {
-    bb[1]
-  }),
-  bullet.id = purrr::map_chr(barrel, function(bb) {
-    bb[3]
-  })
-) %>% select(-barrel)
-
-# obtain the matching keys
-keyss <- keyss %>% filter(!(bullet.id %>% str_detect("\\d+")))
-
-tmp.ukn <-
-  tibble(
-    col1 = tmp.tibble$bullet1 %>% str_extract(" [A-Z]") %>% str_trim(),
-    col2 = tmp.tibble$bullet2 %>% str_extract(" [A-Z]") %>% str_trim()
-  )
-
-# left join the ground truth
-tmp.tibble$b1t <-
-  tmp.ukn %>% left_join(keyss, by = c("col1" = "bullet.id")) %>%
-  pull(barrel.id) %>% str_remove("Brl")
-tmp.tibble$b2t <-
-  tmp.ukn %>% left_join(keyss, by = c("col2" = "bullet.id")) %>%
-  pull(barrel.id) %>% str_remove("Brl")
-
-# find KM KNM
-tmp.tibble <- tmp.tibble %>% mutate(
-  b1t = if_else(
-    is.na(b1t),
-    bullet1 %>% str_extract("Br\\d+") %>% str_remove("Br"),
-    b1t
-  ),
-  b2t = if_else(
-    is.na(b2t),
-    bullet2 %>% str_extract("Br\\d+") %>% str_remove("Br"),
-    b2t
-  ),
-  b1t = as.numeric(b1t),
-  b2t = as.numeric(b2t),
-  type_truth = if_else(b1t == b2t, "KM", "KNM")
-)
-
-### set up parameters
-N <- 4
-CMPS_hamby252_results <- list()
-CMPS_hamby252_results$span1 <- list(0.75, 0.25, 0.25, 0.15)
-CMPS_hamby252_results$signame <-
-  list("sigs75", "sigs25", "sigs25_1062", "sigs15")
-CMPS_hamby252_results$npeaks.set <-
-  list(c(5, 3, 1),
-       c(5, 3, 1),
-       c(10, 6, 2),
-       c(5,3,1))
-CMPS_hamby252_results$seg_length <- as.list(rep(50, 4))
-CMPS_hamby252_results$Tx <- as.list(rep(25, 4))
-CMPS_hamby252_results$titlee <- list()
-CMPS_hamby252_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby252_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby252_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby252_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby252_results$filename[[i]] <- 
-    paste(
-      "hamby252",
-      CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby252_results$seg_length[[i]],
-      CMPS_hamby252_results$Tx[[i]],
-      sep = "_"
-    )
-}
-CMPS_hamby252_results$cmps.table <- list()
-CMPS_hamby252_results$plot <- list()
-
-com.title252 <- expression(paste(
-  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for (i in 1:N) {
-  b252[[CMPS_hamby252_results$signame[[i]]]] <- purrr::map2(
-    .x = b252.full$ccdata,
-    .y = b252.full$grooves,
-    .f = function(x, y) {
-      cc_get_signature(
-        ccdata = x,
-        grooves = y,
-        span1 = CMPS_hamby252_results$span1[[i]],
-        span2 = 0.03
-      )
-    }
-  )
-
-  # process of removing outliers
-  tt <-
-    lapply(b252[[CMPS_hamby252_results$signame[[i]]]], function(x) {
-      x$sig
-    }) %>% unlist()
-  qtt <- quantile(tt, na.rm = TRUE)
-  multi.iqr <- 3
-  outrange <-
-    c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]), qtt[4] + multi.iqr * (qtt[4] -
-                                                                      qtt[2]))
-
-  b252 <- b252 %>% mutate(sigs_main = purrr::map(
-    .x = .data[[CMPS_hamby252_results$signame[[i]]]],
-    .f = function(x) {
-      tmp <- x$sig
-      tmp[tmp < outrange[1] | tmp > outrange[2]] <- NA
-      list(sig = tmp)
-    }
-  ))
-
-  # start the parallel computing
-  system.time({
-    tmp.252.list <- mclapply(p, function(cb.idx) {
-
-      tmp.lands <-
-        c(
-          b252 %>% filter(bullet_id %in% b.cb[, cb.idx][1]) %>% pull(scan_id),
-          b252 %>% filter(bullet_id %in% b.cb[, cb.idx][2]) %>% pull(scan_id)
-        )
-      tmp.comp <-
-        data.frame(expand.grid(land1 = tmp.lands[1:6], land2 = tmp.lands[7:12]),
-                   stringsAsFactors = FALSE)
-
-      tmp.comp$cmps <-
-        purrr::map2(
-          .x = tmp.comp$land1,
-          .y = tmp.comp$land2,
-          .f = function(xx, yy) {
-            sig1 <- b252$sigs_main[b252$scan_id == xx][[1]]$sig
-            sig2 <- b252$sigs_main[b252$scan_id == yy][[1]]$sig
-
-            extract_feature_cmps(
-              sig1,
-              sig2,
-              npeaks.set = CMPS_hamby252_results$npeaks.set[[i]],
-              seg_length = CMPS_hamby252_results$seg_length[[i]],
-              Tx = CMPS_hamby252_results$Tx[[i]],
-              include = "nseg"
-            )
-          }
-        )
-
-      tmp.comp <- tmp.comp %>%
-        mutate(
-          cmps_score = sapply(tmp.comp$cmps, function(x)
-            x$CMPS.score),
-          cmps_nseg = sapply(tmp.comp$cmps, function(x)
-            x$nseg)
-        )
-
-      cmps.table <-
-        tmp.comp %>% select(land1, land2, cmps_score, cmps_nseg)
-
-      tibble(
-        bullet1 = b.cb[, cb.idx][1],
-        bullet2 = b.cb[, cb.idx][2],
-        cmps.table = list(cmps.table)
-      )
-    }, mc.cores = detectCores())
-  })
-
-  hamby252.cmps <- do.call(rbind, tmp.252.list)
-
-  ##################################################
-  # before removing tank-rashed data
-  hamby252.cmps <- hamby252.cmps %>% mutate(
-    cmps.max = cmps.table %>% purrr::map_dbl(
-      .f = function(t) {
-        max(t$cmps_score)
-      }
-    ),
-    cmps.maxbar = cmps.table %>% purrr::map_dbl(
-      .f = function(t) {
-        landidx1 <-
-          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        landidx2 <-
-          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        compute_average_scores(landidx1, landidx2, t$cmps_score) %>% max()
-      }
-    )
-  )
-
-  hamby252.cmps$cmps.table.m <-
-    lapply(hamby252.cmps$cmps.table, function(tt) {
-      tt.idx <- tt %>% rowid_to_column %>%
-        filter(land1 %in% tr.id | land2 %in% tr.id) %>% pull(rowid)
-      tt[tt.idx, "cmps_score"] <- NA
-      tt
-    })
-
-  # after removing tank-rashed data
-  hamby252.cmps <- hamby252.cmps %>% mutate(
-    cmps.max.m = cmps.table.m %>% purrr::map_dbl(
-      .f = function(t) {
-        max(t$cmps_score, na.rm = TRUE)
-      }
-    ),
-    cmps.maxbar.m = cmps.table.m %>% purrr::map_dbl(
-      .f = function(t) {
-        landidx1 <-
-          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        landidx2 <-
-          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        compute_average_scores(
-          landidx1, landidx2, t$cmps_score, addNA = TRUE
-        ) %>% max()
-      }
-    )
-  )
-
-  # add type and type_truth
-  hamby252.cmps$type <- tmp.tibble$type
-  hamby252.cmps$type_truth <- tmp.tibble$type_truth
-
-  ###################################
-  # save result in a list
-  CMPS_hamby252_results$cmps.table[[i]] <- hamby252.cmps
-
-}
-
-################################
-# save data as csv
-data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/"
-
-for(i in 1:N){
-  write.csv(
-    CMPS_hamby252_results$cmps.table[[i]] %>% 
-      select(-cmps.table, -cmps.table.m) %>% as.data.frame(),
-    file = paste(
-      data_path, CMPS_hamby252_results$filename[[i]], 
-      ".csv", sep = ""))
-}
-
-#################################################
-# generate plots
-for (i in 1:3) {
-  hamby252.cmps <- CMPS_hamby252_results$cmps.table[[i]]
-
-  hamby252.plot.list <- list()
-  titlee <- CMPS_hamby252_results$titlee[[i]]
-
-  hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.max.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      fill = "Comparison Type",
-      x = expression(CMPS[max]),
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 27, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank()) +
-    font("x.text", size = 6)
-
-  hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.maxbar.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      x = expression(bar(CMPS)[max]),
-      fill = "Comparison Type",
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 24, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank())
-
-  plot <- ggarrange(plotlist = hamby252.plot.list,
-                    nrow = 1,
-                    ncol = 2,
-                    common.legend = TRUE, legend = "bottom")
-  plot <- annotate_figure(plot, 
-                          top = text_grob(com.title252))
-  CMPS_hamby252_results$plot[[i]] <- plot
-}
-
-```
-
-```{r generate44, echo=TRUE, eval=FALSE}
-library(tidyverse)
-library(bulletxtrctr)
-library(x3ptools)
-library(CMPS)
-library(ggpubr)
-library(parallel)
-
-###########
-# from the x3p data, re-run CMPS results for hamby 44
-b44.full <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
-
-# rds file that stores indices of damaged scans
-idf.idx <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/idfidx.rds")
-
-idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
-
-# generate bullet_id
-bulletid.tb <- b44.full %>% select(scan_id)
-bulletid.tb <- bulletid.tb %>% mutate(
-  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
-  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
-  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
-  bullet_id = paste(barrel_id, bullet)
-)
-
-N <- 3
-CMPS_hamby44_results <- list()
-CMPS_hamby44_results$span1 <- list(0.25, 0.25, 0.75)
-CMPS_hamby44_results$signame <-
-  list("sigs25_531", "sigs25_1061", "sigs75_531")
-CMPS_hamby44_results$npeaks.set <-
-  list(c(5, 3, 1),
-       c(10, 6, 1),
-       c(5, 3, 1))
-CMPS_hamby44_results$seg_length <- as.list(rep(61, 3))
-CMPS_hamby44_results$Tx <- as.list(rep(30, 3))
-CMPS_hamby44_results$titlee <- list()
-CMPS_hamby44_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby44_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby44_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby44_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby44_results$filename[[i]] <- 
-    paste(
-      "hamby44",
-      CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby44_results$seg_length[[i]],
-      CMPS_hamby44_results$Tx[[i]],
-      sep = "_"
-    )
-}
-CMPS_hamby44_results$cmps.table <- list()
-CMPS_hamby44_results$plot <- list()
-
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-# remove x3p files
-b44 <- b44.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
-
-# get all comparisons
-b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
-b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-# get ground-truth
-key.table <- tibble(
-  bullet.id = c(
-    "K",
-    "O",
-    "L",
-    "P",
-    "J",
-    "H",
-    "I",
-    "Y",
-    "G",
-    "E",
-    "U",
-    "X",
-    "F",
-    "T",
-    "S"
-  ),
-  barrel.id = c(1, 2, 3, 4, 4, 5, 5, 6, 6, 7, 7, 7, 8, 9, 10)
-)
-
-tmp.table.44 <- tibble(bullet1 = b.cb[1, ],
-                       bullet2 = b.cb[2, ])
-
-tmp.table.44$b1t <-
-  tmp.table.44$bullet1 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
-tmp.table.44$b2t <-
-  tmp.table.44$bullet2 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
-
-tmp.table.44$b1b <-
-  tmp.table.44 %>% 
-  left_join(key.table, by = c("b1t" = "bullet.id")) %>% 
-  pull(barrel.id)
-tmp.table.44$b2b <-
-  tmp.table.44 %>% 
-  left_join(key.table, by = c("b2t" = "bullet.id")) %>% 
-  pull(barrel.id)
-
-tmp.table.44 <- tmp.table.44 %>% mutate(
-  b1b = if_else(
-    is.na(b1b),
-    bullet1 %>% str_extract("Barrel \\d+") %>% 
-      str_extract("\\d+") %>% as.numeric(),
-    b1b
-  ),
-  b2b = if_else(
-    is.na(b2b),
-    bullet2 %>% str_extract("Barrel \\d+") %>% 
-      str_extract("\\d+") %>% as.numeric(),
-    b2b
-  ),
-  type_truth = if_else(b1b == b2b, "KM", "KNM")
-)
-
-tmp.table.44 <- tmp.table.44 %>% mutate(
-  type = if_else(
-    bullet1 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])") ==
-      bullet2 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])"),
-    "KM",
-    "KNM"
-  ),
-  type = if_else(
-    bullet1 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])") == "Unknowns B" | 
-      bullet2 %>% str_extract("(Unknowns|Barrel) (\\d+|[A-Z])") == "Unknowns B", 
-    "UKN", 
-    type
-  )
-)
-
-for (i in 1:N) {
-  b44[[CMPS_hamby44_results$signame[[i]]]] <- purrr::map2(
-    .x = b44.full$ccdata,
-    .y = b44.full$grooves,
-    .f = function(x, y) {
-      cc_get_signature(
-        ccdata = x,
-        grooves = y,
-        span1 = CMPS_hamby44_results$span1[[i]],
-        span2 = 0.03
-      )
-    }
-  )
-
-  # process of removing outliers
-  tt <-
-    lapply(b44[[CMPS_hamby44_results$signame[[i]]]], function(x) {
-      x$sig
-    }) %>% unlist()
-  qtt <- quantile(tt, na.rm = TRUE)
-  multi.iqr <- 3
-  outrange <-
-    c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]),
-      qtt[4] + multi.iqr * (qtt[4] - qtt[2]))
-
-  b44 <- b44 %>% mutate(sigs_main = purrr::map(
-    .x = .data[[CMPS_hamby44_results$signame[[i]]]],
-    .f = function(x) {
-      tmp <- x$sig
-      tmp[tmp < outrange[1] | tmp > outrange[2]] <- NA
-      list(sig = tmp)
-    }
-  ))
-
-  ## parallel setup
-  cl <- makeCluster(7)
-
-  par.setup <- parLapply(cl, 1:length(cl),
-                         function(xx) {
-                           library(tidyverse)
-                           library(bulletxtrctr)
-                           library(x3ptools)
-                           library(CMPS)
-                         })
-
-  clusterExport(cl,
-                c("b44", "b.cb", "p",
-                  "CMPS_hamby44_results", "i"),
-                envir = globalenv())
-
-  # start the parallel computing
-  system.time({
-    tmp.44.list <- parLapply(cl, p, function(cb.idx) {
-      tmp.lands <-
-        c(
-          b44 %>% filter(bullet_id %in% b.cb[, cb.idx][1]) %>% pull(scan_id),
-          b44 %>% filter(bullet_id %in% b.cb[, cb.idx][2]) %>% pull(scan_id)
-        )
-      tmp.comp <-
-        data.frame(expand.grid(land1 = tmp.lands[1:6], land2 = tmp.lands[7:12]),
-                   stringsAsFactors = FALSE)
-
-      tmp.comp$cmps <-
-        purrr::map2(
-          .x = tmp.comp$land1,
-          .y = tmp.comp$land2,
-          .f = function(xx, yy) {
-            sig1 <- b44$sigs_main[b44$scan_id == xx][[1]]$sig
-            sig2 <- b44$sigs_main[b44$scan_id == yy][[1]]$sig
-
-            extract_feature_cmps(
-              sig1,
-              sig2,
-              npeaks.set = CMPS_hamby44_results$npeaks.set[[i]],
-              seg_length = CMPS_hamby44_results$seg_length[[i]],
-              Tx = CMPS_hamby44_results$Tx[[i]],
-              include = "nseg"
-            )
-          }
-        )
-
-      tmp.comp <- tmp.comp %>%
-        mutate(
-          cmps_score = sapply(tmp.comp$cmps, function(x)
-            x$CMPS.score),
-          cmps_nseg = sapply(tmp.comp$cmps, function(x)
-            x$nseg)
-        )
-
-      cmps.table <-
-        tmp.comp %>% select(land1, land2, cmps_score, cmps_nseg)
-
-      tibble(
-        bullet1 = b.cb[, cb.idx][1],
-        bullet2 = b.cb[, cb.idx][2],
-        cmps.table = list(cmps.table)
-      )
-    })
-  })
-
-  hamby44.cmps <- do.call(rbind, tmp.44.list)
-
-  stopCluster(cl)
-
-  ##################################################
-  # before removing tank-rashed data
-  hamby44.cmps <- hamby44.cmps %>% mutate(
-    cmps.max = cmps.table %>% purrr::map_dbl(
-      .f = function(t) {
-        max(t$cmps_score)
-      }
-    ),
-    cmps.maxbar = cmps.table %>% purrr::map_dbl(
-      .f = function(t) {
-        landidx1 <-
-          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        landidx2 <-
-          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        compute_average_scores(landidx1, landidx2, t$cmps_score) %>% max()
-      }
-    )
-  )
-
-  hamby44.cmps$cmps.table.m <-
-    lapply(hamby44.cmps$cmps.table, function(tt) {
-      tt.idx <- tt %>% rowid_to_column %>%
-        filter(land1 %in% idf.scan_id |
-                 land2 %in% idf.scan_id) %>% pull(rowid)
-      tt[tt.idx, "cmps_score"] <- NA
-      tt
-    })
-
-  # after removing tank-rashed data
-  hamby44.cmps <- hamby44.cmps %>% mutate(
-    cmps.max.m = cmps.table.m %>% purrr::map_dbl(
-      .f = function(t) {
-        max(t$cmps_score, na.rm = TRUE)
-      }
-    ),
-    cmps.maxbar.m = cmps.table.m %>% purrr::map_dbl(
-      .f = function(t) {
-        landidx1 <-
-          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        landidx2 <-
-          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
-        compute_average_scores(
-          landidx1, landidx2, t$cmps_score, addNA = TRUE
-        ) %>% max()
-      }
-    )
-  )
-
-  # add groundtruth
-  hamby44.cmps$type_truth <- tmp.table.44$type_truth
-  hamby44.cmps$type <- tmp.table.44$type
-
-  # save result in a list
-  CMPS_hamby44_results$cmps.table[[i]] <- hamby44.cmps
-
-}
-
-################################
-# save data as csv
-data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/"
-
-for(i in 1:N){
-  write.csv(
-    CMPS_hamby44_results$cmps.table[[i]] %>% 
-      select(-cmps.table, -cmps.table.m) %>% 
-      as.data.frame(),
-    file = paste(data_path, 
-                 CMPS_hamby44_results$filename[[i]], 
-                 ".csv", sep = ""))
-}
-
-#################################################
-# generate plots
-for (i in 1:3) {
-  hamby44.cmps <- CMPS_hamby44_results$cmps.table[[i]]
-
-  hamby44.plot.list <- list()
-  titlee <- CMPS_hamby44_results$titlee[[i]]
-
-  hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.max.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      fill = "Comparison Type",
-      x = expression(CMPS[max]),
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 27, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank()) +
-    font("x.text", size = 6)
-
-  hamby44.plot.list[[2]] <- hamby44.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.maxbar.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      x = expression(bar(CMPS)[max]),
-      fill = "Comparison Type",
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 24, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank())
-
-  plot <- ggarrange(plotlist = hamby44.plot.list,
-                    nrow = 1,
-                    ncol = 2,
-                    common.legend = TRUE, legend = "bottom")
-  plot <- annotate_figure(plot, 
-                          top = text_grob(com.title44))
-  CMPS_hamby44_results$plot[[i]] <- plot
-}
-
-```
-
-\newpage
-
-<!-- open source -->
-<!-- module -->
-<!-- hamby 44 new data set -->
-<!-- hamby 252 -->
-<!-- threshold -->
 

### 2021-06-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
added the abstract

@@
 abstract: >
-  An abstract of less than 150 words.
+  In this paper we introduce the R package CMPS, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
+The functionality of the package is showcased by examples of bullet signatures that come with the package.
+Graphing tools are implemented in the package as well for users to assess and understand the CMPS results.
+Initial tests were performed on bullet signatures generated from two sets of 3D scans in Hamby study under the framework suggested by R package bulletxtrctr.
+An open-source implementation facilitates further studies of the algorithm such as cross-validation of parameters and methods comparison.
 preamble: |

### 2021-06-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
color change

@@
     theme(panel.grid.minor = element_blank()) +
-    font("x.text", size = 6)
+    font("x.text", size = 6) +
+    scale_fill_manual(values=c("darkorange", "darkgrey"))
 
@@
     theme_bw() +
-    theme(panel.grid.minor = element_blank())
+    theme(panel.grid.minor = element_blank()) +
+    scale_fill_manual(values=c("darkorange", "darkgrey"))
 
@@
     theme(panel.grid.minor = element_blank()) +
-    font("x.text", size = 6)
+    font("x.text", size = 6)+
+    scale_fill_manual(values=c("darkorange", "darkgrey"))
 
@@
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-Because the CMPS algorithm works with bullet signatures in our case, we conducted some data-processing: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by Hare and Hofmann [@aoas] with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
+Because the CMPS algorithm works with bullet signatures in our case, we conducted some data-processing: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
 Note that researchers of @cmps used a different framework to obtain bullet signatures.
@@
 
-\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while fixing other parameters.
+\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while adjusting other parameters.
 In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
-We can see that the separation between KM comparisons and KNM comparisons is increased.
+We can see that this results in an increased separation between KM comparisons and KNM comparisons.
 This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.

### 2021-06-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits
removed the final colors and had small edits

@@
 
-\wj{XXX According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "More than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms"} [@fbiucr], and firearm examination could play an important role in all these cases.
+According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "More than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms" [@fbiucr], and firearm examination could play an important role in all these cases.
  <!-- Firearm examination has  played an important role in  convictions [@fbiucr] in the United States criminal justice system.
@@
 From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
-\wj{XXX Note that researchers in} @cmps \wj{refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.}
+Note that researchers in @cmps refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.
   High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.
-\wj{However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
+However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
 Further research is needed to understand how to determine the threshold.
-XXX}
   <!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?} -->
@@
 
-Note that there are \hh{several} parameters in the CMPS algorithm \hh{that are left to} the users \hh{to decide}, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
+Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
-\hh{However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
-Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.}
+However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
+Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
 <!--Additionally, as shown in @cmps, using multi-segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
@@
 
-* `include` determines the \hh{format of the function result}.
+* `include` determines the format of the function result.
 Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed.
@@
 
-The CMPS package is (not) publicly available from CRAN, and can be installed by
-
-```{r, eval=FALSE}
-install.packages("CMPS")
-```
-
-The development version is available from Github can be installed by using
+The CMPS package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
+
+<!-- ```{r, eval=FALSE} -->
+<!-- install.packages("CMPS") -->
+<!-- ``` -->
+
+<!-- The development version is available from Github can be installed by using  -->
 
@@
 
-\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while adjusting other parameters.
+\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while holding other parameters fixed.
 In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
@@
 For the third result of Hamby 44, we changed a parameter used in the data-processing procedure.
-`span1=0.25` is used in previous results, and we changed it to `span1=0.75` \wj{in this case to make bullet signatures capture more global patterns XXX}.
+`span1=0.25` is used for the previous results.
+Here, we change the span of 0.75, which captures a more global pattern in the bullet signatures.
 <!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
@@
 As shown in \autoref{tab:table1}, some parameter settings are better than others in terms of the separation between the two distributions.
-\wj{However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.}
+However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.
 

### 2021-06-24 CMPSpaper_writing/CMPSpaper_writing.Rmd
fixed a typo and prepare for tagging CC

@@
 For algorithmic purposes,
-3D topographical images land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile).
+3D topographical images of land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile).
 The x3p format provides a standard way of exchanging 2D and 3D profile data.
@@
 Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State.
-These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu per pixel.
+These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu m per pixel.
 Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].

### 2021-06-24 CMPSpaper_writing/results_generation.R

@@ -9,8 +9,8 @@ library(parallel)
 # from the x3p data, re-run CMPS results for hamby 252
 # hamby252_results <-
 #   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252_results.rds")
-hamby252_results <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/hamby252_results.rds")
+# hamby252_results <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/hamby252_results.rds")
 
 # b252.full <-
 #   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
@@ -52,15 +52,17 @@ tmp.tibble <- tmp.tibble %>% mutate(
 
 # include tank-rashed data
 # [TODO] MAKE THIS A CSV FILE
-t1.df <-
-  # read_rds("C:/Research/Bullet/Bullet_Rcode/hamby252/t1.df.rds")
-  read_rds("~/Research/CMPSpaper/preconsideration/t1.df.rds")
-tr.id <-
-  c(
-    t1.df %>% filter(type == "TR") %>% pull(scan_id) %>% as.character(),
-    "Br6-2-1",
-    "Br9-2-4"
-  )
+# t1.df <-
+#   # read_rds("C:/Research/Bullet/Bullet_Rcode/hamby252/t1.df.rds")
+#   read_rds("~/Research/CMPSpaper/preconsideration/t1.df.rds")
+# tr.id <-
+#   c(
+#     t1.df %>% filter(type == "TR") %>% pull(scan_id) %>% as.character(),
+#     "Br6-2-1",
+#     "Br9-2-4"
+#   )
+
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
 
 ######################################
 # add ground-truth for hamby 252

### 2021-06-24 CMPSpaper_writing/func_collection.R
added code for parameter cross-validation

@@ -1,0 +1,71 @@
+compute_var_ratio <- function(score, label) {
+  score.split <- split(score, label)
+  
+  group.mean <- sapply(score.split, mean, na.rm=TRUE)
+  
+  total.mean <- mean(score, na.rm = TRUE)
+  
+  var.between <- sum((group.mean - total.mean)^2)
+  var.within <- sum(sapply(score.split, var, na.rm = TRUE))
+  
+  var.ratio <- var.between / var.within
+  return(var.ratio)
+}
+
+compute_var_ratio_anova <- function(score, label, MS=TRUE) {
+  score.split <- split(score, label)
+  
+  group.mean <- sapply(score.split, mean, na.rm=TRUE)
+  group.count <- sapply(score.split, function(tt) sum(!is.na(tt)) )
+  total.mean <- mean(score, na.rm = TRUE)
+  
+  k <- length(unique(label))
+  n <- length(score)
+  
+  var.between <- sum((group.mean - total.mean)^2 * group.count)
+  var.within <- sum(sapply(score.split, function(tt) {
+    sum((tt - mean(tt, na.rm = TRUE))^2)
+  })) 
+  
+  var.ratio <- var.between / var.within
+  if(MS) {
+    var.ratio <- var.ratio * (n-k) / (k-1)
+  }
+  return(var.ratio)
+}
+
+## the function re-written from compute_average_scores
+compute_avgscore_denoise <- function (land1, land2, score, addNA = FALSE) 
+{
+  # if (!is.numeric(land1)) 
+  #   land1 <- readr::parse_number(as.character(land1))
+  # if (!is.numeric(land2)) 
+  #   land2 <- readr::parse_number(as.character(land2))
+  # assert_that(is.numeric(land1), is.numeric(land2), is.numeric(score))
+  maxland <- max(land1, land2)
+  fullframe <- data.frame(expand.grid(land1 = 1:maxland, land2 = 1:maxland))
+  bcompare <- data.frame(land1, land2, score)
+  fullframe <- fullframe %>% left_join(bcompare, by = c("land1", 
+                                                        "land2"))
+  fullframe <- fullframe %>% mutate(land1 = factor(land1, levels = 1:maxland), 
+                                    land2 = factor(land2, levels = 1:maxland))
+  matrix <- xtabs(score ~ land1 + land2, data = fullframe, 
[…]

### 2021-06-24 CMPSpaper_writing/parameters_check.R

@@ -1,72 +1,340 @@
-N <- 3
-CMPS_hamby44_results <- list()
-CMPS_hamby44_results$span1 <- list(0.25, 0.25, 0.75)
-CMPS_hamby44_results$signame <-
-  list("sigs25_531", "sigs25_1061", "sigs75_531")
-CMPS_hamby44_results$npeaks.set <-
-  list(c(5, 3, 1),
-       c(10, 6, 1),
-       c(5, 3, 1))
-CMPS_hamby44_results$seg_length <- as.list(rep(61, 3))
-CMPS_hamby44_results$Tx <- as.list(rep(30, 3))
-CMPS_hamby44_results$titlee <- list()
-CMPS_hamby44_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby44_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby44_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby44_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby44_results$filename[[i]] <- 
-    paste(
-      "hamby44",
-      CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby44_results$seg_length[[i]],
-      CMPS_hamby44_results$Tx[[i]],
-      sep = "_"
-    )
-}
-CMPS_hamby44_results$cmps.table <- list()
-CMPS_hamby44_results$plot <- list()
-
-for(i in 1:N){
-  CMPS_hamby44_results$cmps.table[[i]] <- 
-    read.csv(file = paste("./CMPSpaper_writing/data/", 
-                          CMPS_hamby44_results$filename[[i]], 
-                          ".csv",
-                          sep = ""))
-}
-
-tab1 <- CMPS_hamby44_results$cmps.table[[1]] %>% select(cmps.maxbar, type_truth)
-anova(tab1)
-
 library(MASS)
+source("CMPSpaper_writing/func_collection.R")
 
-tab1 <- CMPS_hamby44_results$cmps.table[[1]] %>% dplyr::select(cmps.maxbar, type_truth)
[…]

### 2021-07-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edit

@@
 header-includes:
+  - \usepackage{amsmath}
   - \usepackage{xcolor}
@@
 
-Then we have
-
-$$
-\mathrm{CMPS_{max}} = \max_{i,j} c_{ij}
-$$
-
-and
-
-$$
-\mathrm{\overline{CMPS}_{max}} = \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
-$$
+With that, the two measures to evaluate accuracy used in @cmps are defined as 
+\begin{align}
+\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\
+\mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right].
+\end{align}
+\hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here}
 

### 2021-07-01 CMPSpaper_writing/parameters_check.R
added codes for parameter evaluation

@@ -279,7 +279,17 @@ for (i in 1:4) {
   CMPS_hamby252_results$plot_scaled[[i]] <- plot
 }
 
-check_idx <- 3
+data(bullets)
+land2_3 <- bullets$sigs[bullets$bulletland == "2-3"][[1]]
+land1_2 <- bullets$sigs[bullets$bulletland == "1-2"][[1]]
+cmps_with_multi_scale <- 
+  extract_feature_cmps(land2_3$sig, land1_2$sig, include = "full_result",
+                       seg_length = 50, npeaks.set = c(10,6,4,2,1))
+cmps_with_multi_scale$CMPS.score
+cmps_with_multi_scale$nseg
+
+
+check_idx <- 1
 
 CMPS_hamby252_results$plot_scaled[[check_idx]]
 CMPS_hamby252_results$plot[[check_idx]]
@@ -287,9 +297,12 @@ CMPS_hamby252_results$titlee[[check_idx]]
 # compute variance ratio for the three plots
 with(CMPS_hamby252_results$cmps.table[[check_idx]], {
   cbind(cmps.max.m, cmps.maxbar.m, cmps.denoise, 
-        cmps.max.m_scaled, cmps.maxbar.m_scaled, cmps.denoise_scaled) %>% 
+        cmps.max.m_scaled, cmps.maxbar.m_scaled, cmps.denoise_scaled,
+        cmps.max, cmps.maxbar) %>% 
     apply(2, compute_var_ratio, label = type_truth)
 }) 
+
+
 
 # ANOVA?
 # https://en.wikipedia.org/wiki/F-test

### 2021-07-01 CMPSpaper_writing/results_generation_param.R

@@ -1,0 +1,486 @@
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+
+# b252.full <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
+b252.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+# generate bullet_id
+bulletid.tb <- b252.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# remove x3p files
+b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get bullet id
+b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
+
+# get all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# remove damaged data
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+######################################
+# add ground-truth for hamby 252
+studyinfo <-
+  readxl::read_xlsx(
+    "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+# readxl::read_xlsx(
+#   "C:/Research/Bullet/Bullet_Rcode/grooves/NRBTDSearchResults/Hamby (2009) Barrel/StudyInfo.xlsx",
+#   sheet = 3,
[…]

### 2021-08-05 CMPSpaper_writing/CMPSpaper_writing.Rmd
added pipeline code for hamby44

@@
   theme(aspect.ratio = 1)
+# dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score/cmps_nseg)) +
+#   geom_tile() +
+#   geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) +
+#   scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6/25) +
+#   scale_colour_manual("Source", values="darkorange") +
+#   facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") +
+#   ylab("Bullet2 Lands") +
+#   geom_text(aes(label=round(cmps_score/cmps_nseg, digits = 2))) +
+#   theme_bw() +
+#   theme(aspect.ratio = 1)
 ```

### 2021-08-05 CMPSpaper_writing/plot_generation.R

@@ -76,8 +76,214 @@ dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + geom_tile() +
 
 
 #######################
-# check 1-4 vs 2-5, segment 8
+# check 1-4 vs 2-5, segment 8 -> expected NA, got INF
+
+#########################
+# generate plots for show & tell
+CMPS_hamby252_results <- readRDS("~/Research/CMPSpaper/CMPSpaper_writing/data/h252-seg_length.rds")
+com.title252 <- expression(paste(
+  "Hamby 252 - ", CMPS[max], ", ", bar(CMPS)[max], " and ", bar(CMPS)[diff] ," Distribution"
+))
 
 
+for (i in 1:length(CMPS_hamby252_results$signame)) {
+  CMPS_hamby252_results$cmps.table[[i]] -> hamby252.cmps
+  
+  hamby252.cmps <- hamby252.cmps %>% mutate(
+    cmps.max_scaled = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        max(t$cmps_score_scaled, na.rm = TRUE)
+      }
+    ),
+    cmps.maxbar_scaled = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        landidx1 <-
+          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        landidx2 <-
+          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        compute_average_scores(landidx1, landidx2, t$cmps_score_scaled, addNA = TRUE) %>% max()
+      }
+    ),
+    cmps.max = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        max(t$cmps_score, na.rm = TRUE)
+      }
+    ),
+    cmps.maxbar = cmps.table.m %>% purrr::map_dbl(
+      .f = function(t) {
+        landidx1 <-
+          t$land1 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        landidx2 <-
+          t$land2 %>% as.character() %>% str_sub(-1, -1) %>% as.numeric()
+        compute_average_scores(landidx1, landidx2, t$cmps_score, addNA = TRUE) %>% max()
+      }
+    )
+  )
+  
+  CMPS_hamby252_results$cmps.table[[i]] <- hamby252.cmps
+}
 
+# plot
+CMPS_hamby252_results$plot_scaled <- list()
[…]

### 2021-08-05 CMPSpaper_writing/results_generation_param_44.R

@@ -1,12 +1,3 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
-
-
-## Load the required packages
 library(tidyverse)
 library(bulletxtrctr)
 library(x3ptools)
@@ -14,77 +5,90 @@ library(CMPS)
 library(ggpubr)
 library(parallel)
 
-#### code used to load the original data; commented out
-# b44.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+source("CMPSpaper_writing/func_collection.R")
 
-## Data Processing
+###########
+# from the x3p data, re-run CMPS results for hamby 44
+# hamby44_results <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44_results.rds")
 
-#### load the data from reproducible/bullet_signatures_etc/
-b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
+# b44.full <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44/hamby44_manual5.rds")
+b44.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
 
-#### obtain all comparisons
-bulletid.tb <- b44 %>% select(scan_id)
+# rds file that stores indices of damaged scans
+# idf.idx <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby44/idfidx.rds")
+# idf.idx <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/idfidx.rds")
+# 
+# idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+
+# generate bullet_id
+bulletid.tb <- b44.full %>% select(scan_id)
 bulletid.tb <- bulletid.tb %>% mutate(
   barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
   bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
[…]

### 2021-08-05 CMPSpaper_writing/CMPSpaper_writing.Rmd
to do list :)

@@
 
+\hh{Still to add: the CMPS diff measure, in which you subtract the background. 
+A comparison to results from bulletxtrctr's random forest.}
+\hh{The random forest is spitting out results on a [0-1] interval - so we might need to compare to the adjusted measure.
+That comarison should go into a separate section just before the discussion.
+Like - comparison to other existing methods ...
+special request from Alicia :)}
+
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}

### 2021-08-19 CMPSpaper_writing/CMPSpaper_writing.Rmd
added contents for CMPS_diff, scaled CMPS score, and variance ratio; updated the implementation section to match the current implementation

--- 2021-07-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
-In case multiple segment lengths are considered, the length of each basis segment is doubled and these two steps are repeated.
+In case multiple segment lengths are considered, the length of each basis segment is doubled \wj{by default} and these two steps are repeated.
 Only when candidate positions coincide (or are similar enough), they are considered further.
@@
         -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks at the first level, double the segment length and recalculate the cross-correlation function, then identify 3 peaks at the second level and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level.
-\autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
-        -   `get_ccr_peaks(comp, segments, seg_scale, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or scaled segment and the reference signature and finds peaks in the cross-correlation curve.
+        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: \wj{calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double or increase the legment length to a specified value, recalculate the cross-correlation function, and identify three peaks; repeat this process and identify one peak in the newly computed cross-correlation function.} \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+\wj{Note that in @cmps the segment length is doubled at each level of a basis segment, but users are allowed to choose the segment length at each level in our implementation.}
+        -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
 The number of peaks detected is equal to `npeaks`, which is an integer.
-`segments`, `seg_scale`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature.
+`segments`, `seg_outlength`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature.
 If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment.
 The resulting list is called `ccr.list`.
-    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak.
-        -   the function `get_seg_scale(segments, nseg, scale = 2)` is used to obtain the scaled version of a basis segment.
-`segments` is a list containing all basis segments, generated by the function `get_segs(...)` in step 1; `nseg` is an integer indicating which basis segment the function should work with.
-`scale=1` gives the original length of the basis segment.
-Increasing `scale` by 1 will double the segment length.
+    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
+Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak \wj{, but we do not have this requirement in our implementation}.
+        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the \wj{increased} version of a basis segment.
+`segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased.
+`out_length` \wj{specifies the length of the output segment.}
         -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak".
@@
   npeaks.set = c(5, 3, 1),
-  include = NULL
+  include = NULL,
+  outlength = NULL
 )
@@
 By default `include` is set to `NULL` and  only  the `CMPS.score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
-If `include` is specified as `"full_result"` (or its abbreviation), the ouput includes everything listed below.
+If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.
   - `nseg`: the number of basis segments  from the comparison signature; this is also the highest possible CMPS score of the comparison;
@@
   - `parameters`: a list containing all input arguments of `extract_feature_cmps`;
+
+* `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
+By default `outlength` is set to `NULL`, \wj{indicating that a basis segment should double its segment length at the next level and conforming to the description in} @cmps .
 
@@
     cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
-    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
+    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg),
+    cmps_scaled = cmps_score / cmps_nseg
   )
@@
 
+## Methods Maybe?
+
+**Metrics Based on CMPS scores**
+
+\wj{The CMPS score can be considered as a similarity score of a land-level comparison, involving two bullet signatures generated from two bullet land engravings.
+Since each bullet has 6 land engravings in our case, a comparison of two bullets involves 36 land-level comparisons, resulting in 36 CMPS scores (as shown in \autoref{fig:tiles}).
+In order to obtain a similarity score of a bullet-level comparison summarizing these 36 CMPS scores,} researchers introduced two similarity \wj{metrics (or measures?
+XXX)}, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons [@cmps].
+$\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all land-level comparisons.
+And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of land-level comparisons that are in the same phase.
+
+In general, we assume each bullet has $n$ land engravings (in our case $n=6$).
+Let $c_{ij}$ denote the CMPS score of a comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
+Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and $\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}$, where $\mathbbm{1}_A$ denotes an indicator function.
+For example, $\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}$ when $n = 6$.
+Let $k^*$ denote the index of the highest phase.
+
+With that, the two measures to evaluate accuracy used in @cmps are defined as
+
+\begin{align}
+\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij} \text{ , and} \\
+\mathrm{\overline{CMPS}_{max}} &= \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij} \text{ , where} \\
+k^* &= \text{arg}\max\limits_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
+\end{align}
+
+<!-- \begin{align} -->
+<!-- \mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\ -->
+<!-- \mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]. -->
+<!-- \end{align} -->
+<!-- \hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here} -->
+
+We can continue with the example used in previous sections.
+`bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
+As mentioned before, each bullet has 6 land engravings, resulting in 6 bullet signatures.
+Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
+We use multi-segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
+We can see that in this example,
+
+$$
+\mathrm{CMPS_{max}} =  \max_{i,j} c_{ij} = 17
+$$
+
+and since bullet lands in phase $\mathcal{P}_1$ gives the highest mean CMPS score ($k^* = 1$), we have
+
+$$
+\begin{aligned}
+\mathrm{\overline{CMPS}_{max}} &= \frac{1}{6} \sum_{(i,j) \in \mathcal{P}_1} c_{ij} \\
+                        &= \frac{1}{6} (c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}) \\
+                        &= \frac{1}{6} (3+17+14+10+15+16) \\
+                        &= 12.5
+\end{aligned}
+$$
+
+```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
+Land engraving pairs generated by the same land (KM comparisons) are highlighted", out.width=".7\\textwidth", fig.align="center"}
+dframe <- dframe %>% mutate(
+  landA = paste0("L", landA),
+  landB = paste0("L", landB),
+  landB = factor(landB, levels = paste0("L", c(2:6,1))),
+  bulletA = paste0("Bullet ", bulletA),
+  bulletB = paste0("Bullet ", bulletB)
+)
+
+dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
+  geom_tile() + 
+  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
+  scale_colour_manual("Source", values="darkorange") +
+  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  ylab("Bullet2 Lands") + 
+  geom_text(aes(label=cmps_score)) +
+  theme_bw() +
+  theme(aspect.ratio = 1)
+```
+
+However, both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ consider only relatively high CMPS scores and ignore the rest.
+So we introduce a new metric based on CMPS scores called $\mathrm{\overline{CMPS}_{diff}}$, which is the difference between $\mathrm{\overline{CMPS}_{max}}$ and the mean of all other CMPS scores.
+With our notation above, we have:
+
+\begin{align}
+\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n(n-1)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
+\end{align}
+
+$\mathrm{\overline{CMPS}_{diff}}$ highlights the difference between CMPS scores of matching and non-matching comparisons.
+If two bullets are non-matching, all 36 CMPS scores are expected to be small with relatively the same values, resulting in a $\mathrm{\overline{CMPS}_{diff}}$ value close to 0.
+For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$
+
+**The Scaled CMPS Score**
+
+Another issue with the CMPS score is that the highest possible CMPS score (the total number of basis segments) might differ across comparisons (as shown in \autoref{fig:tiles2}(a)) due to different lengths of bullet signatures and different lengths of basis segments specified by the parameter.
+A CMPS score of 5 might indicate a non-match if the highest possible CMPS score is 30 but indicate a match if the highest possible CMPS score is 6.
+Thus, we introduce the scaled CMPS score, denoted as $c^*_{ij}$.
+Let $s_{ij}$ denote the highest possible CMPS score or the total number of basis segments, we have
+
+\begin{align}
+c^*_{ij} = \frac{c_{ij}}{s_{ij}}
+\end{align}
+
+The scaled CMPS scores of the above example are shown in \autoref{fig:tiles2}(b).
+\wj{Compared with the original CMPS scores, the scaled CMPS scores are more comparable in the sense that they all lie within the interval $(0, 1)$ no matter the choice of the length of the basis segments.
+Note that the scaled CMPS scores can be combined with the CMPS metrics introduced above to obtain their scaled version.} For example,  $\mathrm{\overline{CMPS^*}_{diff}} = 0.498$ for \autoref{fig:tiles2}(b)
+
+```{r tiles2, echo=FALSE, fig.cap="Plot (a) shows the highest possible CMPS scores (the total number of basis segments) for the 36 comparisons.
+(b) shows the scaled CMPS scores for the 36 comparisons.", out.width=".7\\textwidth", fig.align="center"}
+p1 <- dframe %>% ggplot(aes(x = landA, y = landB)) + 
+  geom_tile(fill = "grey") + 
+  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  scale_colour_manual("Source", values="darkorange") +
+  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  ylab("Bullet2 Lands") + 
+  geom_text(aes(label=cmps_nseg)) +
+  theme_bw() +
+  theme(aspect.ratio = 1)
+
+p2 <- dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_scaled)) + 
+  geom_tile() + 
+  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  scale_fill_gradient2("Scaled CMPS", low = "gray80", high = "darkorange", midpoint = 0.3) + 
+  scale_colour_manual("Source", values="darkorange") +
+  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  ylab("Bullet2 Lands") + 
+  geom_text(aes(label=round(cmps_scaled, 2))) +
+  theme_bw() +
+  theme(aspect.ratio = 1)
+
+ggarrange(p1, p2, 
+          common.legend = TRUE, legend = "bottom", labels = c("(a)", "(b)"))
+```
+
+**Variance Ratio**
+
+We now introduce a measure called "variance ratio" that evaluates the separation between two groups.
+Let $n_k$ denote the number of observations in group $k$ and $y_{kl}$ denote the $l$-th observation in group $k$, for $k = 1,2$ and $l = 1, \dots, n_k$.
+Let $\bar{y}_{k.}$ denote the mean value in group $k$ and $\bar{y}_{..}$ denote the overall mean.
+Then we can define the variance ratio $V$ as:
+
+$$
+V = \frac{\sum n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
+$$
+
+This is called "variance ratio" since the numerator evaluates the "variance" between the two groups, and the denominator evaluates the "variance" within each group.
+\wj{Note that this quantity is not equal to the F-statistic in one-way ANOVA since we ignore the degrees of freedom of both the numerator and the denominator.
+We do not need the degrees of freedom because all the variance ratio values compared in the next sections have exactly the same number of observations in both goups (the known-match group and the known-nonmatch group), resulting in exactly the same degrees of freedom.}
+
 ## Results
-
-**Metrics Based on CMPS scores**
 
@@
 
-As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252).
+As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252 \wj{to the best of our knowledge} ).
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-Because the CMPS algorithm works with bullet signatures in our case, we conducted some data-processing: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
-Note that researchers of @cmps used a different framework to obtain bullet signatures.
-However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
-
-The CMPS score can be considered as a similarity score of two signatures.
-Then in order to obtain a similarity score of two bullets based on CMPS scores, researchers introduced two similarity metrics, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons [@cmps].
-$\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all pairwise bullet signature comparisons.
-And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of signature comparisons that are in the same phase.
-
-In general, we assume each bullet has $n$ land engravings (in our case $n=6$).
-Let $c_{ij}$ denote the CMPS score of a comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
-Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and $\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}$, where $\mathbbm{1}_A$ denotes an indicator function.
-For example, $\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}$ when $n = 6$.
-
-With that, the two measures to evaluate accuracy used in @cmps are defined as 
-\begin{align}
-\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\
-\mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right].
-\end{align}
-\hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here}
-
-We can continue with the example used in previous sections.
-`bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
-As mentioned before, each bullet has six land engravings, resulting in six bullet signatures.
-Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
-We use multi-segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
-We can see that in this example,
-
-$$
-\mathrm{CMPS_{max}} =  \max_{i,j} c_{ij} = 17
-$$
-
-and since bullet lands in phase $\mathcal{P}_1$ gives the highest mean CMPS score, we have
-
-$$
-\begin{aligned}
-\mathrm{\overline{CMPS}_{max}} &= \frac{1}{6} \sum_{(i,j) \in \mathcal{P}_1} c_{ij} \\
-                        &= \frac{1}{6} (c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}) \\
-                        &= \frac{1}{6} (3+17+14+10+15+16) \\
-                        &= 12.5
-\end{aligned}
-$$
-
-```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
-Land engraving pairs generated by the same land (KM comparisons) are highlighted", out.width=".7\\textwidth", fig.align="center"}
-dframe <- dframe %>% mutate(
-  landA = paste0("L", landA),
-  landB = paste0("L", landB),
-  landB = factor(landB, levels = paste0("L", c(2:6,1))),
-  bulletA = paste0("Bullet ", bulletA),
-  bulletB = paste0("Bullet ", bulletB)
-)
-
-dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
-  geom_tile() + 
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
-  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
-  ylab("Bullet2 Lands") + 
-  geom_text(aes(label=cmps_score)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-```
-
-<!-- based on CMPS scores of bullet signature comparisons.
-For example, there are in total 6 $\times$ 6 signature comparisons in order to compare two bullets in Hamby study since each bullet has 6 LEAs and each LEA generates a bullet signature.
-And a CMPS score will be found for every signature comparison.
-$\mathrm{CMPS_{max}}$ is the highest CMPS score among all signature comparisons.
-And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible average CMPS score of signature comparisons that are in the same phase.
--->
-
-<!-- In this example, $\mathrm{CMPS_{max}}$, the highest CMPS score, is 17, and $\mathrm{\overline{CMPS}_{max}}$, the highest possible mean CMPS score of comparisons in the same phase, is $()/6=12.5$.
--->
+\wj{For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data}: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
+\wj{More details and code can be found in the Appendix.} Note that researchers of @cmps \wj{applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.} However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
 

### 2021-08-19 code/func_collection.R

@@ -136,3 +136,70 @@ cmps_metric_plot_helper <- function(cmps.metric, metric) {
   return(p)
 }
 
+
+###################
+# update sig_align
+sig_align <- function (sig1, sig2) 
+{
+  assertthat::assert_that(is.numeric(sig1), is.numeric(sig2))
+  sig1 <- CMPS::cmps_na_trim(sig1)
+  sig2 <- CMPS::cmps_na_trim(sig2)
+  
+  n1 <- length(sig1)
+  n2 <- length(sig2)
+  if (n1 > n2) {
+    x <- sig1
+    y <- sig2
+  }
+  else {
+    x <- sig2
+    y <- sig1
+  }
+  cors <- CMPS::get_ccf4(x, y, round(0.75 * min(length(sig1), length(sig2))))
+  lag <- cors$lag[which.max(cors$ccf)]
+  if (lag < 0) {
+    x <- c(rep(NA, abs(lag)), x)
+  }
+  if (lag > 0) {
+    y <- c(rep(NA, lag), y)
+  }
+  delta <- length(x) - length(y)
+  if (delta < 0) 
+    x <- c(x, rep(NA, abs(delta)))
+  if (delta > 0) 
+    y <- c(y, rep(NA, delta))
+  if (n1 > n2) {
+    dframe0 <- data.frame(x = 1:length(x), sig1 = x, sig2 = y)
+  }
+  else {
+    dframe0 <- data.frame(x = 1:length(x), sig1 = y, sig2 = x)
+  }
+  maxcor <- max(cors$ccf, na.rm = TRUE)
+  list(ccf = maxcor, lag = lag, lands = dframe0)
+}
+
+
+get_ccf2 <- function (x, y, min.overlap = round(0.1 * max(length(x), length(y)))) 
+{
+  x <- as.vector(unlist(x))
+  y <- as.vector(unlist(y))
+  nx <- length(x)
+  ny <- length(y)
+  assert_that(is.numeric(x), is.numeric(y))
+  assert_that(nx > 0, ny > 0, nx >= ny)
+  xx <- c(rep(NA, ny - min.overlap), x, rep(NA, ny - min.overlap))
+  yy <- c(y, rep(NA, length(xx) - ny))
+  lag.max <- length(yy) - length(y)
+  lags <- 0:lag.max
+  cors <- sapply(lags, function(lag) {
+    cor(xx, lag(yy, lag), use = "pairwise.complete")
+  })
[…]

### 2021-08-19 code/plot_generation.R

@@ -289,7 +289,72 @@ longer.tt %>%
 
 
 
+##################
+# from the paper
+lands <- unique(bullets$bulletland)
 
+comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
+                          stringsAsFactors = FALSE)
+
+comparisons <- comparisons %>% 
+  left_join(bullets %>% select(bulletland, sig1=sigs),
+            by = c("land1" = "bulletland")) %>%
+  left_join(bullets %>% select(bulletland, sig2=sigs),
+            by = c("land2" = "bulletland"))
+
+comparisons <- comparisons %>% mutate(
+  cmps = purrr::map2(sig1, sig2, .f = function(x, y) {
+    extract_feature_cmps(x$sig, y$sig, include = "full")
+  })
+)
+
+comparisons <- comparisons %>% 
+  mutate(
+    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
+    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
+  )
+
+comparisons <- comparisons %>%
+  mutate(
+    bulletA = gsub("(\\d)-\\d", "\\1", land1),
+    landA = gsub("\\d-(\\d)", "\\1", land1),
+    bulletB = gsub("(\\d)-\\d", "\\1", land2),
+    landB = gsub("\\d-(\\d)", "\\1", land2)
+  )
+
+dframe <- comparisons %>% select(-sig1, -sig2)
+
+dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
+
+dframe <- dframe %>% mutate(
+  landA = paste0("L", landA),
+  landB = paste0("L", landB),
+  landB = factor(landB, levels = paste0("L", c(2:6,1))),
+  bulletA = paste0("Bullet ", bulletA),
+  bulletB = paste0("Bullet ", bulletB)
+)
+
+dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_nseg)) + 
+  geom_tile() + 
+  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  scale_fill_gradient2("Highest Possible cmps", low = "gray80", high = "gray80", midpoint = 24) + 
+  scale_colour_manual("Source", values="darkorange") +
[…]

### 2021-08-19 code/results_generation_param.R

@@ -233,7 +233,6 @@ for (i in 1:N) {
   system.time({
     # tmp.252.list <- parLapply(cl, p, function(cb.idx) {
     tmp.252.list <- mclapply(p, function(cb.idx) {
-      # cat(" ############# \n", "start of ", cb.idx, "\n")
       
       tmp.lands <-
         c(
@@ -439,13 +438,16 @@ table.cmps.diff %>%
                names_to = "score") %>% 
   ggplot(aes(x=npeak, y=value)) +
   geom_bar(aes(fill = score),position = "dodge", stat = "identity") + 
+  ylab("variance ratio") +
   coord_flip() + 
   theme_bw()
 
-order(table.cmps.diff$cmps.diff_scaled, decreasing = TRUE)
-
+# cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff")
 cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff_scaled")
+cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[1]], "cmps.diff_scaled")
 
+CMPS_hamby252_results$signame
+order(table.cmps.diff$cmps.diff_scaled, decreasing = TRUE)
 
 # seg_length
 table.cmps.diff$seg_length <- unlist(CMPS_hamby252_results$seg_length)

### 2021-08-19 code/rf_cmps.R

@@ -1,0 +1,126 @@
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("code/func_collection.R")
+
+#########################
+# run the example in the chapter
+data("bullets")
+bullets$bulletland
+
+lands <- unique(bullets$bulletland)
+comparisons <- data.frame(expand.grid(land1 = lands, land2 = lands), stringsAsFactors = FALSE)
+
+comparisons <- comparisons %>% mutate(aligned = purrr::map2(.x = land1, .y = land2, 
+                                                            .f = function(xx, yy) {
+                                                              land1 <- bullets$sigs[bullets$bulletland == xx][[1]]
+                                                              land2 <- bullets$sigs[bullets$bulletland == yy][[1]]
+                                                              land1$bullet <- "first-land"
+                                                              land2$bullet <- "second-land"
+                                                              
+                                                              # bulletxtrctr::sig_align(land1$sig, land2$sig)
+                                                              sig_align(land1$sig, land2$sig)
+                                                            }))
+
+subset(comparisons, land1 == "2-3" & land2 == "1-2")$aligned[[1]]$lands %>% 
+  mutate(`b2-l3` = sig1, `b1-l2` = sig2) %>% select(-sig1, -sig2) %>% tidyr::gather(sigs, 
+                                                                                    value, `b2-l3`, `b1-l2`) %>% ggplot(aes(x = x, y = value, colour = sigs)) + 
+  geom_line() + theme_bw() + scale_color_brewer(palette = "Dark2")
+
+comparisons <- comparisons %>% mutate(ccf0 = aligned %>% purrr::map_dbl(.f = function(x) extract_feature_ccf(x$lands)), 
+                                      lag0 = aligned %>% purrr::map_dbl(.f = function(x) extract_feature_lag(x$lands)), 
+                                      D0 = aligned %>% purrr::map_dbl(.f = function(x) extract_feature_D(x$lands)), 
+                                      length0 = aligned %>% purrr::map_dbl(.f = function(x) extract_feature_length(x$lands)), 
+                                      overlap0 = aligned %>% purrr::map_dbl(.f = function(x) extract_feature_overlap(x$lands)), 
[…]

### 2021-08-25 code/func_collection.R
added code for computing random forest score

@@ -104,35 +104,68 @@ cmps_metrics_helper <- function(cmps.table) {
   return(result)
 }
 
-cmps_metric_plot_helper <- function(cmps.metric, metric) {
-  scaled <- str_detect(metric, "_scaled")
-  if(scaled) {
-    p <- cmps.metric %>% ggplot() +
-      geom_histogram(aes(x = .data[[metric]],
-                         fill = as.factor(.data$type_truth)), binwidth = 0.04) +
-      labs(
-        x = metric,
-        fill = "Comparison Type",
-        subtitle = titlee
-      ) +
-      scale_x_continuous(breaks = seq(0, 1, 0.05)) +
-      theme_bw() +
-      theme(panel.grid.minor = element_blank()) +
-      scale_fill_manual(values=c("darkorange", "darkgrey"))
-  } else {
-    p <- cmps.metric %>% ggplot() +
-      geom_histogram(aes(x = .data[[metric]],
-                         fill = as.factor(.data$type_truth)), binwidth = 1) +
-      labs(
-        x = metric,
-        fill = "Comparison Type",
-        subtitle = titlee
-      ) +
-      scale_x_continuous(breaks = seq(0, 24, 1)) +
-      theme_bw() +
-      theme(panel.grid.minor = element_blank()) +
-      scale_fill_manual(values=c("darkorange", "darkgrey"))
+score_metrics_helper <- function(cmps.table, score = "cmps_score", scaled = NULL) {
+  
+  landidx1 <- cmps.table$landidx1
+  landidx2 <- cmps.table$landidx2
+  score <- cmps.table[[score]]
+  result <- data.frame(
+    diff = compute_avgscore_denoise(landidx1, landidx2, score, addNA = TRUE),
+    diff.med = compute_avgscore_denoise(landidx1, landidx2, 
+                                             score, FUNC = median, addNA = TRUE),
+    max = max(score, na.rm = TRUE),
+    maxbar = compute_average_scores(landidx1, landidx2, score) %>% max(na.rm = TRUE)
+  )
+  
+  if(!is.null(scaled)) {
+    score_scaled <- cmps.table[[scaled]]
+    result <- result %>% mutate(
+      diff_scaled = compute_avgscore_denoise(landidx1, landidx2, score_scaled, addNA = TRUE),
+      diff.med_scaled = compute_avgscore_denoise(landidx1, landidx2, 
[…]

### 2021-08-25 code/results_generation_param.R

@@ -355,7 +355,8 @@ for (i in 1:N) {
 }
 
 saveRDS(CMPS_hamby252_results, "code/saved_rds/h252_npeak8.rds")
-
+CMPS_hamby252_results <- 
+  readRDS("~/Research/CMPSpaper/code/saved_rds/h252_npeak8.rds")
 
 #################################################
 # generate plots
@@ -443,8 +444,8 @@ table.cmps.diff %>%
   theme_bw()
 
 # cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff")
-cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff_scaled")
-cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[1]], "cmps.diff_scaled")
+metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff_scaled", scaled = TRUE)
+metric_plot_helper(CMPS_hamby252_results$cmps.table[[1]], "cmps.diff_scaled", scaled = TRUE)
 
 CMPS_hamby252_results$signame
 order(table.cmps.diff$cmps.diff_scaled, decreasing = TRUE)

### 2021-08-25 code/rf_cmps.R

@@ -4,6 +4,7 @@ library(x3ptools)
 library(CMPS)
 library(ggpubr)
 library(parallel)
+library(assertthat)
 
 source("code/func_collection.R")
 
@@ -25,6 +26,8 @@ comparisons <- comparisons %>% mutate(aligned = purrr::map2(.x = land1, .y = lan
                                                               # bulletxtrctr::sig_align(land1$sig, land2$sig)
                                                               sig_align(land1$sig, land2$sig)
                                                             }))
+
+purrr::map_dbl(comparisons$aligned, .f = function(x) x$lag)
 
 subset(comparisons, land1 == "2-3" & land2 == "1-2")$aligned[[1]]$lands %>% 
   mutate(`b2-l3` = sig1, `b1-l2` = sig2) %>% select(-sig1, -sig2) %>% tidyr::gather(sigs, 
@@ -58,6 +61,19 @@ comparisons <- comparisons %>% mutate(ccf0 = aligned %>% purrr::map_dbl(.f = fun
 
 ########################
 # test on random forest code
+tmp.lands <-
+  c(
+    b252 %>% filter(bullet_id %in% b.cb[, cb.idx][1]) %>% pull(scan_id),
+    b252 %>% filter(bullet_id %in% b.cb[, cb.idx][2]) %>% pull(scan_id)
+  )
+tmp.comp <-
+  data.frame(expand.grid(land1 = tmp.lands[1:6], land2 = tmp.lands[7:12]),
+             stringsAsFactors = FALSE)
+tmp.comp$landidx1 <- tmp.comp$land1 %>% as.character() %>% str_sub(-1, -1) %>% 
+  as.numeric()
+tmp.comp$landidx2 <- tmp.comp$land2 %>% as.character() %>% str_sub(-1, -1) %>% 
+  as.numeric()
+
 tmp.comp <- tmp.comp %>% 
   mutate(
     aligned = purrr::map2(.x = land1, .y = land2, 
@@ -70,6 +86,13 @@ tmp.comp <- tmp.comp %>%
                             sig_align(land1$sig, land2$sig)
                             # bulletxtrctr::sig_align(land1$sig, land2$sig)
                           }))
+
+tmp.comp$aligned %>% purrr::map_dbl(.f = function(x) x$lag)
[…]

### 2021-08-25 code/rf_cmps_run.R

@@ -1,0 +1,283 @@
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+source("code/func_collection.R")
+
+# b252.full <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
+b252.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+# generate bullet_id
+bulletid.tb <- b252.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# remove x3p files
+b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get bullet id
+b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
+
+# get all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# remove damaged data
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+######################################
+# add ground-truth for hamby 252
+studyinfo <-
+  readxl::read_xlsx(
+    "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+# readxl::read_xlsx(
[…]

### 2021-08-25 CMPSpaper_writing/CMPSpaper_writing.Rmd
added the section introducing sum of squares ratio

@@
 
-**Variance Ratio**
-
-We now introduce a measure called "variance ratio" that evaluates the separation between two groups.
-Let $n_k$ denote the number of observations in group $k$ and $y_{kl}$ denote the $l$-th observation in group $k$, for $k = 1,2$ and $l = 1, \dots, n_k$.
-Let $\bar{y}_{k.}$ denote the mean value in group $k$ and $\bar{y}_{..}$ denote the overall mean.
-Then we can define the variance ratio $V$ as:
+**Sum of Squares Ratio**
+
+We now introduce a measure called "sum of squares ratio" that quantifies the separation between two groups.
+Let $n_T$ denote the total number of observations, $n_k$ denote the number of observations in group $k$, and $y_{kl}$ denote the $l$-th observation in group $k$, for $k = 1,2$ and $l = 1, \dots, n_k$.
+Let $\bar{y}_{k.} = \frac{1}{n_k} \sum_{l=1}^{n_k} y_{kl}$ denote the mean value in group $k$ and $\bar{y}_{..} = \frac{1}{n_T} \left(  \sum_{k} \sum_{l = 1}^{n_k} y_{kl} \right)$ denote the mean value of all observations.
+Since we are interested in the separation between two groups, we can model $y_{kl}$ as:
+
+\begin{align}
+y_{kl} = \mu_k + e_{kl}
+\end{align}
+
+where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations. Then we can define the sum of squares ratio $V$ as:
 
 $$
-V = \frac{\sum n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
+V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
 $$
 
-This is called "variance ratio" since the numerator evaluates the "variance" between the two groups, and the denominator evaluates the "variance" within each group.
-\wj{Note that this quantity is not equal to the F-statistic in one-way ANOVA since we ignore the degrees of freedom of both the numerator and the denominator.
-We do not need the degrees of freedom because all the variance ratio values compared in the next sections have exactly the same number of observations in both goups (the known-match group and the known-nonmatch group), resulting in exactly the same degrees of freedom.}
+The numerator of the sum of squares ratio $V$ quantifies the variation between the two groups, while the denominator quantifies the variation within each group.
+The sum of squares ratio $V$ can be used as an index for evaluating scans, metrics, and different sets of parameters if the same data set is being used.
+Some examples will be presented in the following section.
+If we impose the normality and independence assumptions on the random effects $e_{kl}$, the sum of squares ratio $V$ becomes a scaled F-statistic with degrees of freedom of $k-1$ and $n_T - k$ and $F = \frac{n_T - k}{k- 1} V$.
+If we want to compare different data sets, stating that a certain setup can achieve better separation on one data set than another, we can scale the sum of squares ratio $V$ and obtain the F-statistic to compare the p-values.
+
+\wj{add citation for one way ANOVA?}
+
+With the sum of squares ratio $V$ being defined, we are able to construct a pipeline that aims to find the optimal parameter value for the CMPS algorithm maximizing the sum of squares ratio.
+In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced above and investigate effects of different sets of parameters.
+
+\wj{we might not find the real optimal parameter since the parameter space of npeaks.set is too complicated...}
 

### 2021-08-25 CMPSpaper_writing/CMPSpaper_writing.Rmd
modified result section for hamby 252

@@
 
-$$
+\begin{align}
 V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
-$$
+\end{align}
 
@@
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-\wj{For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data}: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
-\wj{More details and code can be found in the Appendix.} Note that researchers of @cmps \wj{applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.} However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
+\wj{For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix}: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
+Note that researchers of @cmps \wj{applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.} However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
 
@@
 \autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy.
-Although the CMPS scores we found here are not exactly the same as those presented in @cmps since we don't have the exact parameters and functions used by the researchers, the results we obtained qualitatively agree with their results.
-For both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ we can observe a clear separation between the known matching comparisons (KM) and known non-matching comparisons (KNM).
-
-The parameters we used in `extract_feature_cmps` are:
+The parameters we used in `extract_feature_cmps` for the CMPS algorithm are:
 
@@
 
-Note that for Hamby set 252, one unit represents 1.5625 \textmu m so setting `seg_length = 50` makes each basis segment have length 78.125 \textmu m.
-And `Tx = 25` makes the tolerance zone be $\pm 39.0625$ \textmu m.
-This is to mimic the parameters used in @cmps.
+As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in \autoref{fig:result1_252} are qualitatively equivalent to those presented in @cmps, showing a clear separation between the known matching comparisons (KM) group and the known non-matching comparisons (KNM) group for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
+
+Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu for Hamby set 252).
+
+The sum of squares ratios are 20.85 and 29.32 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively. \wj{TODO: add some comments following this result}
+
+```{r, echo=FALSE, eval=FALSE}
+with(CMPS_hamby252_results$cmps.table[[2]], {
+  tibble(cmps.max.m, cmps.maxbar.m) %>% 
+    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+})
+```
 

### 2021-09-01 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edits

@@
 In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
-In case multiple segment lengths are considered, the length of each basis segment is doubled \wj{by default} and these two steps are repeated.
+In case multiple segment lengths are considered, the length of each basis segment is expanded (by default it is doubled) and these two steps are repeated.
 Only when candidate positions coincide (or are similar enough), they are considered further.
@@
         -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: \wj{calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double or increase the legment length to a specified value, recalculate the cross-correlation function, and identify three peaks; repeat this process and identify one peak in the newly computed cross-correlation function.} \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
-\wj{Note that in @cmps the segment length is doubled at each level of a basis segment, but users are allowed to choose the segment length at each level in our implementation.}
+        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
+\autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
         -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
@@
     +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
-Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak \wj{, but we do not have this requirement in our implementation}.
-        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the \wj{increased} version of a basis segment.
+Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.
+        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment.
 `segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased.
-`out_length` \wj{specifies the length of the output segment.}
+`out_length` specifies the length of the output segment.
         -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak".
@@
 * `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
-By default `outlength` is set to `NULL`, \wj{indicating that a basis segment should double its segment length at the next level and conforming to the description in} @cmps .
+By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
 
@@
 
-\wj{The CMPS score can be considered as a similarity score of a land-level comparison, involving two bullet signatures generated from two bullet land engravings.
-Since each bullet has 6 land engravings in our case, a comparison of two bullets involves 36 land-level comparisons, resulting in 36 CMPS scores (as shown in \autoref{fig:tiles}).
-In order to obtain a similarity score of a bullet-level comparison summarizing these 36 CMPS scores,} researchers introduced two similarity \wj{metrics (or measures?
-XXX)}, $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, for bullet-level comparisons [@cmps].
-$\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all land-level comparisons.
-And $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of land-level comparisons that are in the same phase.
+The CMPS algorithm measures the similarity between two signatures resulting in a similarity score of a land-to-level comparison.
+Bullets fired from traditionally rifled barrels have multiple land and groove engraved areas.
+Here, we are working with bullets fired from Ruger P85 barrels with six lands and grooves.
+A comparison of two bullets therefore involves 36 land-to-land comparisons, resulting in 36 CMPS scores (as shown in \autoref{fig:tiles}).
+In order to obtain a single similarity score of a bullet-level comparison, we need to summarize these 36 CMPS scores.
+Two similarity metrics for bullet-level comparisons have been introduced in the literature [@cmps]: $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
+$\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all land-level comparisons, while $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of land-level comparisons that are in the same phase:
 

### 2021-09-02 CMPSpaper_writing/CMPSpaper_writing.Rmd
edits through results section

@@
 
-## Methods Maybe?
+## Evaluation Metrics
 
@@
 If two bullets are non-matching, all 36 CMPS scores are expected to be small with relatively the same values, resulting in a $\mathrm{\overline{CMPS}_{diff}}$ value close to 0.
-For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$
-
-**The Scaled CMPS Score**
+For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$ <br>
+
+**Scaled CMPS Scores**
 
@@
 Thus, we introduce the scaled CMPS score, denoted as $c^*_{ij}$.
-Let $s_{ij}$ denote the highest possible CMPS score or the total number of basis segments, we have
+Let $s_{ij}$ denote the highest possible CMPS score or the total number of basis segments, then the scaled CMPS score $c^*_{ij}$ is defined as the ratio of raw score and maximum score:
 
@@
 The scaled CMPS scores of the above example are shown in \autoref{fig:tiles2}(b).
-\wj{Compared with the original CMPS scores, the scaled CMPS scores are more comparable in the sense that they all lie within the interval $(0, 1)$ no matter the choice of the length of the basis segments.
-Note that the scaled CMPS scores can be combined with the CMPS metrics introduced above to obtain their scaled version.} For example,  $\mathrm{\overline{CMPS^*}_{diff}} = 0.498$ for \autoref{fig:tiles2}(b)
+Compared to the original CMPS scores, scaled scores have values within the interval $(0, 1)$ regardless of the length of the basis segments and therefore make a comparison of values possible across different parameter choices.
+Similarly to the original CMPS scores, we will denote the scaled CMPS scores adjusted for out-of-phase background values by $\mathrm{\overline{CMPS^*}_{diff}}$.
+For example,  $\mathrm{\overline{CMPS^*}_{diff}} = 0.498$ for \autoref{fig:tiles2}(b)
 
@@
 
-We now introduce a measure called "sum of squares ratio" that quantifies the separation between two groups.
+The "sum of squares ratio"  quantifies how well two groups of values separate.
 Let $n_T$ denote the total number of observations, $n_k$ denote the number of observations in group $k$, and $y_{kl}$ denote the $l$-th observation in group $k$, for $k = 1,2$ and $l = 1, \dots, n_k$.
 Let $\bar{y}_{k.} = \frac{1}{n_k} \sum_{l=1}^{n_k} y_{kl}$ denote the mean value in group $k$ and $\bar{y}_{..} = \frac{1}{n_T} \left(  \sum_{k} \sum_{l = 1}^{n_k} y_{kl} \right)$ denote the mean value of all observations.
-Since we are interested in the separation between two groups, we can model $y_{kl}$ as:
+Consider the following model:
 
@@
 \begin{align}
-V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }
+V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }.
 \end{align}
@@
 
-\wj{add citation for one way ANOVA?}
-
-With the sum of squares ratio $V$ being defined, we are able to construct a pipeline that aims to find the optimal parameter value for the CMPS algorithm maximizing the sum of squares ratio.
-In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced above and investigate effects of different sets of parameters.
-
-\wj{we might not find the real optimal parameter since the parameter space of npeaks.set is too complicated...}
+Using the sum of squares ratio $V$ as an evaluation metric, we are able to construct a pipeline that aims to find the optimal parameter value for the CMPS algorithm by maximizing the sum of squares ratio.
+In the following section, we will use this ratio to compare the CMPS metrics introduced earlier and investigate effects of different sets of parameters.
 
@@
 
-As presented in the work of @cmps, researchers applied the CMPS method to one of the Hamby set scans (Hamby 252 \wj{to the best of our knowledge} ).
+As presented in the work of @cmps, researchers applied the CMPS method to scans of one of the Hamby sets.
+While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time.
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-\wj{For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix}: for both Hamby 252 and Hamby 44, we started with x3p files in the database, followed the framework proposed by @aoas with the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
-Note that researchers of @cmps \wj{applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.} However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
+For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix: for both Hamby 252 and Hamby 44, we started with scans in the form of x3p files in the database.
+Following the framework proposed by @aoas, we used the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
+Note that researchers of @cmps applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.
+However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
 
@@
 
-As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in \autoref{fig:result1_252} are qualitatively equivalent to those presented in @cmps, showing a clear separation between the known matching comparisons (KM) group and the known non-matching comparisons (KNM) group for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-
-Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu for Hamby set 252).
-
-The sum of squares ratios are 20.85 and 29.32 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively. \wj{TODO: add some comments following this result}
+As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in \autoref{fig:result1_252} are qualitatively equivalent to those presented in @cmps, showing a clear separation between scores based on comparisons from known matches (KM)  and scores from comparisons of known non-matches (KNM)  for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
+
+Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu m for Hamby set 252).
+
+The sum of squares ratios are 20.85 and 29.32 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
+\hh{This indicates, that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.}
 

### 2021-09-02 CMPSpaper_writing/CMPSpaper_writing.Rmd
update the abstract

--- 2021-08-25 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 abstract: >
-  In this paper we introduce the R package CMPS, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
+  In this paper, we introduce the R package CMPS, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
 The functionality of the package is showcased by examples of bullet signatures that come with the package.
 Graphing tools are implemented in the package as well for users to assess and understand the CMPS results.
-Initial tests were performed on bullet signatures generated from two sets of 3D scans in Hamby study under the framework suggested by R package bulletxtrctr.
-An open-source implementation facilitates further studies of the algorithm such as cross-validation of parameters and methods comparison.
+Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package bulletxtrctr.
+New metrics based on CMPS scores are introduced and compared with existing metrics.
+A measure called Sum of Squares Ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets.
+An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
 preamble: |

### 2021-09-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
added codes for reproducibility; modified the Results section

@@
 
+source("../code/func_collection.R")
+
 knitr::opts_chunk$set(
@@
 
+\wj{Instead of computing the mean CMPS scores of matching and non-matching comparisons, a variation of $\mathrm{\overline{CMPS}_{diff}}$ is to compute the median CMPS scores of matching and non-matching comparisons.
+Computing the median could be beneficial if extreme values are observed for non-matching comparisons.
+More examples are provided in the Results section}
+
 **Scaled CMPS Scores**
@@
 
-```{r hamby252-data, eval=TRUE, echo=FALSE}
+```{r hamby252-data-seg, eval=TRUE, echo=FALSE}
 # for hamby 252
-N <- 3
-CMPS_hamby252_results <- list()
-CMPS_hamby252_results$span1 <- list(0.75, 0.25, 0.25)
-CMPS_hamby252_results$signame <-
-  list("sigs75", "sigs25", "sigs25_1062")
-CMPS_hamby252_results$npeaks.set <-
-  list(c(5, 3, 1),
-       c(5, 3, 1),
-       c(10, 6, 2))
-CMPS_hamby252_results$seg_length <- list(50, 50, 50)
-CMPS_hamby252_results$Tx <- list(25, 25, 25)
+N <- 8 # the number of different sets of parameters
+CMPS_hamby252_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
+CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
+  # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
+
+#### setup npeaks.set
+CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
+
+#### setup seg_length
+CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
+
+#### setup Tx
+CMPS_hamby252_results$Tx <- as.list(rep(25, N))
+
+#### setup outlength
+CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
+
+#### create a plot title and a file name for each set of parameters
 CMPS_hamby252_results$titlee <- list()
@@
     paste(
-      "hamby252",
+      "hamby252_segment",
       CMPS_hamby252_results$span1[[i]]*100,
@@
 }
+
+#### container for the cmps results and corresponding plots
 CMPS_hamby252_results$cmps.table <- list()
@@
 
+#### a global title for Hamby252 plots
+com.title252 <- expression(paste(
+  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
+
 for(i in 1:N){
   CMPS_hamby252_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/", 
+  read.csv(file = paste("./data/hamby252/", 
                         CMPS_hamby252_results$filename[[i]], 
@@
 
+CMPS_hamby252_results_seg <- CMPS_hamby252_results
+
+# generate plots
+# for (i in 1:3) {
+#   hamby252.cmps <- CMPS_hamby252_results$cmps.table[[i]]
+#   
+#   hamby252.plot.list <- list()
+#   titlee <- CMPS_hamby252_results$titlee[[i]]
+#   
+#   hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
+#     geom_histogram(aes(x = cmps.max.m,
+#                        fill = as.factor(type_truth)), binwidth = 1) +
+#     labs(
+#       fill = "Comparison Type",
+#       x = expression(CMPS[max]),
+#       # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
+#       subtitle = titlee
+#     ) +
+#     scale_x_continuous(breaks = seq(0, 27, 1)) +
+#     theme_bw() +
+#     theme(panel.grid.minor = element_blank()) +
+#     font("x.text", size = 6) +
+#     scale_fill_manual(values=c("darkorange", "darkgrey"))
+#     
+#   hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
+#     geom_histogram(aes(x = cmps.maxbar.m,
+#                        fill = as.factor(type_truth)), binwidth = 1) +
+#     labs(
+#       x = expression(bar(CMPS)[max]),
+#       fill = "Comparison Type",
+#       # title = expression(paste(
+#       #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
+#       # )),
+#       subtitle = titlee
+#     ) +
+#     scale_x_continuous(breaks = seq(0, 24, 1)) +
+#     theme_bw() +
+#     theme(panel.grid.minor = element_blank()) +
+#     scale_fill_manual(values=c("darkorange", "darkgrey"))
+#   
+#   plot <- ggarrange(plotlist = hamby252.plot.list,
+#                     nrow = 1,
+#                     ncol = 2,
+#                     common.legend = TRUE, legend = "bottom")
+#   plot <- annotate_figure(plot, 
+#                           top = text_grob(com.title252))
+#   CMPS_hamby252_results$plot[[i]] <- plot
+# }
+
+```
+
+```{r hamby252-data-npeak, eval=TRUE, echo=FALSE}
+N <- 8 # the number of different sets of parameters
+CMPS_hamby252_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
+CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
+# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
+
+#### setup npeaks.set
+CMPS_hamby252_results$npeaks.set <- 
+  list(c(5),
+       c(5,2),
+       c(5,3,1),
+       c(10,6,2),
+       c(6,4,2,1),
+       c(10,7,4,2),
+       c(10,6,4,2,1),
+       c(10,8,6,4,2,1))
+
+#### setup seg_length
+CMPS_hamby252_results$seg_length <- 
+  # as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
+  as.list(rep(50, N))
+
+#### setup Tx
+CMPS_hamby252_results$Tx <- as.list(rep(25, N))
+
+#### setup outlength
+CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
+CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180)
+CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200)
+
+#### create a plot title and a file name for each set of parameters
+CMPS_hamby252_results$titlee <- list()
+CMPS_hamby252_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby252_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby252_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby252_results$filename[[i]] <- 
+    paste(
+      "hamby252_npeak",
+      CMPS_hamby252_results$span1[[i]]*100,
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby252_results$seg_length[[i]],
+      CMPS_hamby252_results$Tx[[i]],
+      sep = "_"
+    )
+}
+
+#### container for the cmps results and corresponding plots
+CMPS_hamby252_results$cmps.table <- list()
+CMPS_hamby252_results$plot <- list()
+
+#### a global title for Hamby252 plots
 com.title252 <- expression(paste(
@@
 
-# generate plots
-for (i in 1:3) {
-  hamby252.cmps <- CMPS_hamby252_results$cmps.table[[i]]
-
-  hamby252.plot.list <- list()
-  titlee <- CMPS_hamby252_results$titlee[[i]]
-
-  hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.max.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      fill = "Comparison Type",
-      x = expression(CMPS[max]),
-      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 27, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank()) +
-    font("x.text", size = 6) +
-    scale_fill_manual(values=c("darkorange", "darkgrey"))
-
-  hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.maxbar.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      x = expression(bar(CMPS)[max]),
-      fill = "Comparison Type",
-      # title = expression(paste(
-      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
-      # )),
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 24, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank()) +
-    scale_fill_manual(values=c("darkorange", "darkgrey"))
-
-  plot <- ggarrange(plotlist = hamby252.plot.list,
-                    nrow = 1,
-                    ncol = 2,
-                    common.legend = TRUE, legend = "bottom")
-  plot <- annotate_figure(plot, 
-                          top = text_grob(com.title252))
-  CMPS_hamby252_results$plot[[i]] <- plot
+for(i in 1:N){
+  CMPS_hamby252_results$cmps.table[[i]] <- 
+  read.csv(file = paste("./data/hamby252/", 
+                        CMPS_hamby252_results$filename[[i]], 
+                        ".csv",
+                        sep = ""))
 }
 
-```
-
-```{r hamby44-data, eval=TRUE, echo=FALSE}
-N <- 3
-CMPS_hamby44_results <- list()
-CMPS_hamby44_results$span1 <- list(0.25, 0.25, 0.75)
+CMPS_hamby252_results_npeak <- CMPS_hamby252_results
+
+```
+
+```{r hamby44-data-seg, eval=TRUE, echo=FALSE}
+N <- 8 # the number of different sets of parameters
+CMPS_hamby44_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
 CMPS_hamby44_results$signame <-
-  list("sigs25_531", "sigs25_1061", "sigs75_531")
+  as.list(rep("sigs25_531", N))
+
+#### setup neapks.set
 CMPS_hamby44_results$npeaks.set <-
-  list(c(5, 3, 1),
-       c(10, 6, 1),
-       c(5, 3, 1))
-CMPS_hamby44_results$seg_length <- as.list(rep(61, 3))
-CMPS_hamby44_results$Tx <- as.list(rep(30, 3))
+  lapply(1:N, function(t) c(5,3,1))
+
+#### setup seg_length
+CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210))
+
+#### setup outlength
+CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
+
+#### setup Tx
+CMPS_hamby44_results$Tx <- as.list(rep(30, N))
+
+#### create a plot title and a file name for each set of parameters
 CMPS_hamby44_results$titlee <- list()
@@
     paste(
-      "hamby44",
+      "hamby44_segment",
       CMPS_hamby44_results$span1[[i]]*100,
@@
 }
+
+#### container for the cmps results and corresponding plots
 CMPS_hamby44_results$cmps.table <- list()
@@
 
+#### a global title for Hamby44 plots
+com.title44 <- expression(paste(
+  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
+
 for(i in 1:N){
   CMPS_hamby44_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/", 
+  read.csv(file = paste("./data/hamby44/", 
                         CMPS_hamby44_results$filename[[i]], 
@@
 
+CMPS_hamby44_results_seg <- CMPS_hamby44_results
+
+```
+
+```{r hamby44-data-npeak, eval=TRUE, echo=FALSE}
+N <- 8 # the number of different sets of parameters
+CMPS_hamby44_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
+CMPS_hamby44_results$signame <-
+  as.list(rep("sigs25_531", N))
+
+#### setup neapks.set
+CMPS_hamby44_results$npeaks.set <-
+  list(c(5),
+       c(5,2),
+       c(5,3,1),
+       c(10,6,2),
+       c(6,4,2,1),
+       c(10,7,4,2),
+       c(10,6,4,2,1),
+       c(10,8,6,4,2,1))
+
+#### setup seg_length
+CMPS_hamby44_results$seg_length <- as.list(rep(61, N))
+
+#### setup outlength
+CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
+CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181)
+CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211)
+
+#### setup Tx
+CMPS_hamby44_results$Tx <- as.list(rep(30, N))
+
+#### create a plot title and a file name for each set of parameters
+CMPS_hamby44_results$titlee <- list()
+CMPS_hamby44_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby44_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby44_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby44_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby44_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby44_results$filename[[i]] <- 
+    paste(
+      "hamby44_npeak",
+      CMPS_hamby44_results$span1[[i]]*100,
+      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
+      CMPS_hamby44_results$seg_length[[i]],
+      CMPS_hamby44_results$Tx[[i]],
+      sep = "_"
+    )
+}
+
+#### container for the cmps results and corresponding plots
+CMPS_hamby44_results$cmps.table <- list()
+CMPS_hamby44_results$plot <- list()
+
+#### a global title for Hamby44 plots
 com.title44 <- expression(paste(
@@
 
-# generate plots
-for (i in 1:3) {
-  hamby44.cmps <- CMPS_hamby44_results$cmps.table[[i]]
-
-  hamby44.plot.list <- list()
-  titlee <- CMPS_hamby44_results$titlee[[i]]
-
-  hamby44.plot.list[[1]] <- hamby44.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.max.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      fill = "Comparison Type",
-      x = expression(CMPS[max]),
-      # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 27, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank()) +
-    font("x.text", size = 6)+
-    scale_fill_manual(values=c("darkorange", "darkgrey"))
-
-  hamby44.plot.list[[2]] <- hamby44.cmps %>% ggplot() +
-    geom_histogram(aes(x = cmps.maxbar.m,
-                       fill = as.factor(type_truth)), binwidth = 1) +
-    labs(
-      x = expression(bar(CMPS)[max]),
-      fill = "Comparison Type",
-      # title = expression(paste(
-      #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
-      # )),
-      subtitle = titlee
-    ) +
-    scale_x_continuous(breaks = seq(0, 24, 1)) +
-    theme_bw() +
-    theme(panel.grid.minor = element_blank()) +
-    scale_fill_manual(values=c("darkorange", "darkgrey"))
-
-  plot <- ggarrange(plotlist = hamby44.plot.list,
-                    nrow = 1,
-                    ncol = 2,
-                    common.legend = TRUE, legend = "bottom")
-  plot <- annotate_figure(plot, 
-                          top = text_grob(com.title44))
-  CMPS_hamby44_results$plot[[i]] <- plot
+for(i in 1:N){
+  CMPS_hamby44_results$cmps.table[[i]] <- 
+  read.csv(file = paste("./data/hamby44/", 
+                        CMPS_hamby44_results$filename[[i]], 
+                        ".csv",
+                        sep = ""))
 }
+
+CMPS_hamby44_results_npeak <- CMPS_hamby44_results
 ```
@@
 
-The sum of squares ratios are 20.85 and 29.32 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
+The sum of squares ratios are 20.64 and 28.96 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
 \hh{This indicates, that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.}
@@
 ```{r, echo=FALSE, eval=FALSE}
-with(CMPS_hamby252_results$cmps.table[[2]], {
-  tibble(cmps.max.m, cmps.maxbar.m) %>% 
+with(CMPS_hamby252_results_npeak$cmps.table[[3]], {
+  tibble(cmps.max, cmps.maxbar) %>% 
     apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
 })
+
+with(CMPS_hamby252_results_seg$cmps.table[[2]], {
+  tibble(cmps.max, cmps.maxbar, cmps.diff, cmps.diff_scaled) %>% 
+    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+})
+
+```
+
+```{r plot_computation, echo=FALSE}
+# 252 - seg
+table.252.cmps_seg <- lapply(CMPS_hamby252_results_seg$cmps.table, function(tt) {
+  type_truth <- tt$type_truth
+  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
+    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+table.252.cmps_seg$seg_length <- unlist(CMPS_hamby252_results_seg$seg_length)
+
+p.seg_252_plot <- table.252.cmps_seg %>%
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+               names_to = "Metric") %>%
+  ggplot(aes(x = seg_length, y = value)) +
+  geom_line(aes(color = Metric)) + 
+  scale_x_continuous(breaks = table.252.cmps_seg$seg_length) +
+  theme_bw() +
+  ggtitle("A Temp Title") +
+  ylab("Sum of Squares Ratio") + 
+  xlab("seg_length")
+
+# 252 - npeak
+table.252.cmps_npeak <- lapply(CMPS_hamby252_results_npeak$cmps.table, function(tt) {
+  type_truth <- tt$type_truth
+  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
+    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks.set %>% 
+  purrr::map(.f = paste, collapse = "-")
+
+p.npeak_252_plot <- table.252.cmps_npeak %>% 
+  mutate(
+    npeak = factor(
+      npeak,
+      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
+  ) %>% 
+  pivot_longer(cols = c(cmps.diff:cmps.maxbar_scaled),
+               names_to = "Metric") %>% 
+  ggplot(aes(x=npeak, y=value)) +
+  geom_bar(aes(fill = Metric),position = "dodge", stat = "identity") + 
+  ylab("Sum of Squares Ratio") +
+  coord_flip() + 
+  theme_bw()
+
+# 44 - seg
+table.44.cmps_seg <- lapply(CMPS_hamby44_results_seg$cmps.table, function(tt) {
+  type_truth <- tt$type_truth
+  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
+    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+table.44.cmps_seg$seg_length <- unlist(CMPS_hamby44_results_seg$seg_length)
+
+p.seg_44_plot <- table.44.cmps_seg %>%
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+               names_to = "Metric") %>%
+  ggplot(aes(x = seg_length, y = value)) +
+  geom_line(aes(color = Metric)) + 
+  scale_x_continuous(breaks = table.44.cmps_seg$seg_length) +
+  theme_bw() +
+  ggtitle("A Temp Title") +
+  ylab("Sum of Squares Ratio") + 
+  xlab("seg_length")
+
+# 44 - npeak
+table.44.cmps_npeak <- lapply(CMPS_hamby44_results_npeak$cmps.table, function(tt) {
+  type_truth <- tt$type_truth
+  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
+    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+table.44.cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks.set %>% 
+  purrr::map(.f = paste, collapse = "-")
+
+p.npeak_44_plot <- table.44.cmps_npeak %>% 
+  mutate(
+    npeak = factor(
+      npeak,
+      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
+  ) %>% 
+  pivot_longer(cols = c(cmps.diff:cmps.maxbar_scaled),
+               names_to = "Metric") %>% 
+  ggplot(aes(x=npeak, y=value)) +
+  geom_bar(aes(fill = Metric),position = "dodge", stat = "identity") + 
+  ylab("Sum of Squares Ratio") +
+  coord_flip() + 
+  theme_bw()
 ```
@@
 # knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
-CMPS_hamby252_results$plot[[2]]
+# CMPS_hamby252_results$plot[[2]]
+
+p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
+                         subtitle = "npeak: 5-3-1, seg_length: 50")
+p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
+                         subtitle = "npeak: 5-3-1, seg_length: 50")
+p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
+               common.legend = TRUE, legend = "bottom")
+p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
+p.result1_252
 ```
@@
 
-For Hamby set 44 we not only generated comparable results but also used different sets of parameters to examine their potential effects.
-
-\autoref{fig:result1_44} shows the Hamby 44 results that are comparable with Hamby 252 results. The parameters used in `extract_feature_cmps` are:
+Similar procedures are applied to Hamby set 44, and \autoref{fig:result1_44} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
+The parameters used in `extract_feature_cmps` are:
 
@@
 
-Since the Hamby set 44 scans have a different scanning resolution, we need to adjust the value of `seg_length` and `Tx` accordingly.
-One unit in Hamby 44 represents 1.29 \textmu m.
-Thus, we make `seg_length = 61` and `Tx = 30` to ensure that each basis segment has length 78.69 \textmu m, and the tolerance zone is $\pm 38.7$ \textmu m.
-Again, we are able to see a clear separation between the KM comparisons and the KNM comparisons, but it would be better if the separation can be further enlarged, which motivates us to examine different sets of parameters.
-
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.25", fig.height=3}
-# [1] "span1=0.25, span2=0.03, rm_outliers"
-# knitr::include_graphics("img/hamby44_v1.png", dpi = 100)
-CMPS_hamby44_results$plot[[1]]
-```
-
-\autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while holding other parameters fixed.
+Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we make `seg_length = 61` and `Tx = 30` to ensure that the setup of Hamby set 44 is similar to that of Hamby set 252, resulting in basis segments of 78.69 \textmu m and the tolerance zone of $\pm 38.7$ \textmu m.
+
+As shown in \autoref{fig:result1_44}, again, we are able to see a clear separation between the known match comparisons and the known non-match comparisons, even though the separation is relatively small compared with that of Hamby set 252, which is also indicated by the sum of squares ratios.
+For this specific set of parameters, the sum of squares ratios are 8.87 and 10.64 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
+This might suggest that we could enlarge the separation in terms of the sum of squares ratio by using other CMPS metrics and other sets of parameters.
+
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1) ", fig.height=3}
+# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
+# knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
+# CMPS_hamby252_results$plot[[2]]
+
+p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
+                         subtitle = "npeak: 5-3-1, seg_length: 61")
+p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
+                         subtitle = "npeak: 5-3-1, seg_length: 61")
+p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
+               common.legend = TRUE, legend = "bottom")
+p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
+p.result1_44
+```
+
+**Comparing CMPS metrics and Parameters**
+
+For both Hamby set 252 and 44, we investigated the effects of different sets of parameters.
+More specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level and modified the parameter `seg_length` that controls the length of a basis segment.
+Then we fixed `seg_length` and examined different values of `npeaks.set`.
+The sum of squares ratios are used to compare among different CMPS metrics and different sets of parameters.
+
+default parameters can be beaten?
+cmps.diff, cmps.maxbar and their scaled version are good? we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
+Note that the goal of these comparisons is not to determine the optimal set of parameters for the CMPS algorithm, but to show a general procedure that can be used for
+
+```{r}
+# CMPS_hamby44_results_seg$cmps.table[[3]] %>% 
+#   metric_plot_helper("cmps.max")
+# 
+# CMPS_hamby252_results_seg$cmps.table[[2]] %>% 
+#   metric_plot_helper("cmps.max")
+```
+
+```{r seg_252_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+p.seg_252_plot
+```
+
+```{r npeak_252_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+p.npeak_252_plot
+```
+
+```{r seg_44_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+p.seg_44_plot
+```
+
+```{r npeak_44_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+p.npeak_44_plot
+```
+
+<!-- \autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while holding other parameters fixed.
 In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
@@
 This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
+-->
 
@@
 # knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
-CMPS_hamby44_results$plot[[2]]
-```
-
-For the third result of Hamby 44, we changed a parameter used in the data-processing procedure.
+# CMPS_hamby44_results$plot[[2]]
+```
+
+<!-- For the third result of Hamby 44, we changed a parameter used in the data-processing procedure.
 `span1=0.25` is used for the previous results.
 Here, we change the span of 0.75, which captures a more global pattern in the bullet signatures.
-<!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
 -->
-As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results. 
-\autoref{tab:table1} presents some summary statistics of the Hamby 44 results above.
+<!-- <!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
+-->
+<!-- As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results.  -->
+<!-- \autoref{tab:table1} presents some summary statistics of the Hamby 44 results above.
 These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
@@
 However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.
+-->
 
@@
 # knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
-CMPS_hamby44_results$plot[[3]]
+# CMPS_hamby44_results$plot[[3]]
 ```
@@
 
-knitr::kable(rtt, "latex", booktabs = TRUE, escape = FALSE,
-             caption = "min and max of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ showing the separation between KNM and KM",
-             row.names = FALSE, digits = 4) %>% 
-  column_spec(2:5, width = "2cm")
+# knitr::kable(rtt, "latex", booktabs = TRUE, escape = FALSE,
+#              caption = "min and max of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ showing the separation between KNM and KM",
+#              row.names = FALSE, digits = 4) %>% 
+#   column_spec(2:5, width = "2cm")
 ```

### 2021-09-09 code/func_collection.R

@@ -1,3 +1,5 @@
+library(assertthat)
+
 compute_var_ratio <- function(score, label) {
   score.split <- split(score, label)
   
@@ -34,14 +36,8 @@ compute_var_ratio_anova <- function(score, label, MS=TRUE) {
   return(var.ratio)
 }
 
-## the function re-written from compute_average_scores
-compute_avgscore_denoise <- function (land1, land2, score, FUNC = mean, addNA = FALSE, na.rm = TRUE) 
+get_all_phases <- function(land1, land2, score, addNA = FALSE)
 {
-  # if (!is.numeric(land1)) 
-  #   land1 <- readr::parse_number(as.character(land1))
-  # if (!is.numeric(land2)) 
-  #   land2 <- readr::parse_number(as.character(land2))
-  # assert_that(is.numeric(land1), is.numeric(land2), is.numeric(score))
   maxland <- max(land1, land2)
   fullframe <- data.frame(expand.grid(land1 = 1:maxland, land2 = 1:maxland))
   bcompare <- data.frame(land1, land2, score)
@@ -62,12 +58,33 @@ compute_avgscore_denoise <- function (land1, land2, score, FUNC = mean, addNA = 
       diag(matrix[, -(1:i)])
     }
   })
+  
+  return(scores.list)
+}
+
+
+## the function re-written from compute_average_scores
+compute_avgscore_denoise <- function (land1, land2, score, FUNC = mean, addNA = FALSE, na.rm = TRUE) 
+{
+  
+  scores.list <- get_all_phases(land1, land2, score, addNA)
+  
+  result <- compute_diff_phase(scores.list, FUNC, na.rm)
+  
+  return(result)
+}
+
+compute_diff_phase <- function(scores.list, FUNC = mean, na.rm = TRUE, both = FALSE)
+{
   scores <- sapply(scores.list, FUNC, na.rm=na.rm)
   max.phase <- which.max(scores)
   result.match <- max(scores, na.rm=na.rm)
-  result.nmatch <- 
-    scores.list[-max.phase] %>% unlist() %>% FUNC(na.rm=na.rm)
-  result.match - result.nmatch
+  result.nmatch <- scores.list[-max.phase] %>% unlist() %>% FUNC(na.rm=na.rm)
+  if(both) {
+    return(c(result.match, result.nmatch))
+  } else {
+    return(result.match - result.nmatch)
+  }
 }
 
[…]

### 2021-09-09 code/results_generation_param.R

@@ -444,8 +444,9 @@ table.cmps.diff %>%
   theme_bw()
 
 # cmps_metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff")
+metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff", scaled = FALSE)
 metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff_scaled", scaled = TRUE)
-metric_plot_helper(CMPS_hamby252_results$cmps.table[[1]], "cmps.diff_scaled", scaled = TRUE)
+metric_plot_helper(CMPS_hamby252_results$cmps.table[[9]], "cmps.diff.med_scaled", scaled = TRUE)
 
 CMPS_hamby252_results$signame
 order(table.cmps.diff$cmps.diff_scaled, decreasing = TRUE)

### 2021-09-09 code/results_generation_param_44.R

@@ -114,23 +114,24 @@ N <- 9
 CMPS_hamby44_results <- list()
 CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
 CMPS_hamby44_results$signame <-
-  # list("n5", "n51", "n52", "n531", "n10-62", "n6421", 
-  #      "n10-742", "n10-6421")
-  list("s30", "s45", "s61", "s90", "s122", "s150", "s180", "s210", "s61-ol")
+  list("n5", "n51", "n52", "n531", "n10-62", "n6421",
+       "n10-742", "n10-6421", "n10-86421")
+  # list("s30", "s45", "s61", "s90", "s122", "s150", "s180", "s210")
 CMPS_hamby44_results$npeaks.set <-
-  # list(c(5),
-  #      c(5,1),
-  #      c(5,2),
-  #      c(5,3,1),
-  #      c(10,6,2),
-  #      c(6,4,2,1),
-  #      c(10,7,4,2),
-  #      c(10,6,4,2,1))
-  lapply(1:N, function(t) c(5,3,1))
-CMPS_hamby44_results$seg_length <- 
-  as.list(c(30, 45, 61, 90, 122, 150, 180, 210, 62))
-CMPS_hamby44_results$outlength <- list()
-CMPS_hamby44_results$outlength[[N]] <- c(62, 122, 183)
+  list(c(5),
+       c(5,1),
+       c(5,2),
+       c(5,3,1),
+       c(10,6,2),
+       c(6,4,2,1),
+       c(10,7,4,2),
+       c(10,6,4,2,1),
+       c(10, 8, 6, 4, 2, 1))
+  # lapply(1:N, function(t) c(5,3,1))
+CMPS_hamby44_results$seg_length <- as.list(rep(61, N))
+  # as.list(c(30, 45, 61, 90, 122, 150, 180, 210))
+CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
+CMPS_hamby44_results$outlength[[N]] <- c(61, 86, 111, 136, 161, 186)
 CMPS_hamby44_results$Tx <- as.list(rep(30, N))
 CMPS_hamby44_results$titlee <- list()
 CMPS_hamby44_results$filename <- list()
@@ -169,20 +170,24 @@ com.title44 <- expression(paste(
 # start of the loop!
 for (i in 1:N) {
   # i <- 1
[…]

### 2021-09-09 code/rf_cmps_run.R

@@ -14,6 +14,8 @@ source("code/func_collection.R")
 b252.full <- 
   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
 
+rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
+
 # generate bullet_id
 bulletid.tb <- b252.full %>% select(scan_id)
 bulletid.tb <- bulletid.tb %>% mutate(
@@ -144,15 +146,15 @@ b252[[CMPS_hamby252_results$signame[[i]]]] <- purrr::map2(
 
 
 # process of removing outliers
-# tt <- lapply(b252[[CMPS_hamby252_results$signame[[i]]]], function(x) {
-#     x$sig
-#   }) %>% unlist()
-# qtt <- quantile(tt, na.rm = TRUE)
-# multi.iqr <- 3
-# outrange <- c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]), 
-#               qtt[4] + multi.iqr * (qtt[4] - qtt[2]))
+tt <- lapply(b252[[CMPS_hamby252_results$signame[[i]]]], function(x) {
+    x$sig
+  }) %>% unlist()
+qtt <- quantile(tt, na.rm = TRUE)
+multi.iqr <- 3
+outrange <- c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]),
+              qtt[4] + multi.iqr * (qtt[4] - qtt[2]))
 
-outrange <- c(-10000, 10000) # without excluding the outliers
+# outrange <- c(-10000, 10000) # without excluding the outliers
 
 b252 <- b252 %>% mutate(sigs_main = purrr::map(
   .x = .data[[CMPS_hamby252_results$signame[[i]]]],
@@ -197,19 +199,24 @@ system.time({
     # compute the rf_score
     tmp.comp <- tmp.comp %>% 
       mutate(
-        striae = aligned %>% purrr::map(.f = sig_cms_max, span = span),
+        striae = aligned %>% purrr::map(.f = sig_cms_max),
         features = purrr::map2(.x = aligned, .y = striae, 
                                .f = my_extract_feature_all, resolution = 1.5625), 
         legacy_features = purrr::map(striae, 
-                                     extract_features_all_legacy, resolution = 1.5625)) %>% 
-      tidyr::unnest(legacy_features)
+                                     extract_features_all_legacy, resolution = 1.5625))
+      # tidyr::unnest(features) # change: instead of legacy_feature
     
[…]

### 2021-09-09 code/rf_cmps_run_44.R

@@ -1,0 +1,285 @@
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+source("code/func_collection.R")
+
+b44.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+
+rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
+
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+
+# generate bullet_id
+bulletid.tb <- b44.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# remove x3p files
+b44 <- b44.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get all comparisons
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# get ground-truth
+key.table <- tibble(
+  bullet.id = c(
+    "K",
+    "O",
+    "L",
+    "P",
+    "J",
+    "H",
+    "I",
+    "Y",
+    "G",
+    "E",
+    "U",
+    "X",
+    "F",
+    "T",
+    "S"
+  ),
+  barrel.id = c(1, 2, 3, 4, 4, 5, 5, 6, 6, 7, 7, 7, 8, 9, 10)
+)
+
+tmp.table.44 <- tibble(bullet1 = b.cb[1, ],
+                       bullet2 = b.cb[2, ])
+
+tmp.table.44$b1t <-
+  tmp.table.44$bullet1 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+tmp.table.44$b2t <-
+  tmp.table.44$bullet2 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+
+tmp.table.44$b1b <-
[…]

### 2021-09-09 code/rf_summary_script.R

@@ -1,0 +1,42 @@
+rf44.container <- list()
+rf44.container[[1]] <- readRDS("~/Research/CMPSpaper/code/saved_rds/h44_rf2_features_rmo.rds")
+  readRDS("~/Research/CMPSpaper/code/saved_rds/h44_rf_features_def.rds")
+rf44.container[[2]] <- 
+  readRDS("~/Research/CMPSpaper/code/saved_rds/h44_rf_legacyfeatures_def.rds")
+
+df.rf <- lapply(rf44.container, function(rf_result) {
+  with(rf_result$rf.table[[1]], {
+    tibble(rf.diff, rf.diff.med, rf.max, rf.maxbar) %>% 
+      apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+  })
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+df.rf$rf <- c("features", "legacy_feature")
+df.rf$span3 <- c("default", "default")
+
+rf252.container <- list()
+rf252.container[[1]] <- readRDS("~/Research/CMPSpaper/code/saved_rds/h252_rf2_features_rmo.rds")
+  readRDS(filepath)
+  readRDS("~/Research/CMPSpaper/code/saved_rds/h252_rf_features_def.rds")
+rf252.container[[2]] <- 
+  readRDS("~/Research/CMPSpaper/code/saved_rds/h252_rf_result_25.rds")
+rf252.container[[3]] <- 
+  readRDS("~/Research/CMPSpaper/code/saved_rds/h252_rf_result_75.rds")
+
+df.rf.252 <- lapply(rf252.container, function(rf_result) {
+  with(rf_result$rf.table[[1]], {
+    tibble(rf.diff, rf.diff.med, rf.max, rf.maxbar) %>% 
+      apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+  })
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+metric_plot_helper(rf252.container[[1]]$rf.table[[1]], "rf.diff.med", scaled = TRUE)
+metric_plot_helper(rf44.container[[1]]$rf.table[[1]], "rf.diff", scaled = TRUE)
+
+
+df.rf.252$rf <- c("features", "legacy_feature", "legacy_feature")
+df.rf.252$span3 <- c("default", "25", "75")
+
+df.rf
+
+df.rf.252

### 2021-09-09 reproducible/hamby252_result_generater.R

@@ -1,370 +1,0 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
-
-## Load the required packages
-library(tidyverse)
-library(bulletxtrctr)
-library(x3ptools)
-library(CMPS)
-library(ggpubr)
-library(parallel)
-
-#### code used to load the original data; commented out
-# b252.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
-
-## Data Processing
-
-#### load the data from reproducible/bullet_signatures_etc/
-b252 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures252.rds")
-
-#### obtain all comparisons
-b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-#### obtained ID for the damaged bullets;
-###### These IDs are identified by using a Shiny App called bulletinspectR
-tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
-
-#### Include the ground truth for Hamby252
-tmp.tibble <- tibble(bullet1 = b.cb[1,], 
-                     bullet2 = b.cb[2,])
-
-tmp.tibble <- tmp.tibble %>% mutate(
-  type = if_else(
-    bullet1 %>% str_extract("Br\\d+") ==
-      bullet2 %>% str_extract("Br\\d+"),
-    "KM",
-    "KNM"
-  ),
-  type = if_else(is.na(type), "Ukn", type)
-)
-
-###### StudyInfo.xlsx provides the ground truth for Hamby252 
-studyinfo <-
-  readxl::read_xlsx(
-    "./reproducible/bullet_signatures_etc/StudyInfo.xlsx",
-    sheet = 3,
-    skip = 1
-  )
-
-keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
-keyss <- tibble(specimen = keyss)
-keyss <- keyss %>% mutate(
-  barrel = specimen %>% str_split(" "),
-  barrel.id = purrr::map_chr(barrel, function(bb) {
[…]

### 2021-09-09 reproducible/hamby252_seg_result_generater.R

@@ -1,0 +1,357 @@
+##########################
+# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
+#       These rds files contain processed bullet signatures used in the paper
+#       The original data contains x3p objects of large size, so they are not
+#       uploaded to the Github repo
+##########################
+
+## Load the required packages
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("code/func_collection.R")
+
+#### code used to load the original data; commented out
+# b252.full <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./reproducible/bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
+keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
+keyss <- tibble(specimen = keyss)
+keyss <- keyss %>% mutate(
+  barrel = specimen %>% str_split(" "),
[…]

### 2021-09-09 reproducible/hamby44_result_generater.R

@@ -1,392 +1,0 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
-
-
-## Load the required packages
-library(tidyverse)
-library(bulletxtrctr)
-library(x3ptools)
-library(CMPS)
-library(ggpubr)
-library(parallel)
-
-#### code used to load the original data; commented out
-# b44.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
-
-## Data Processing
-
-#### load the data from reproducible/bullet_signatures_etc/
-b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
-
-#### obtain all comparisons
-bulletid.tb <- b44 %>% select(scan_id)
-bulletid.tb <- bulletid.tb %>% mutate(
-  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
-  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
-  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
-  bullet_id = paste(barrel_id, bullet)
-)
-b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
-b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-#### import indices of damaged scans
-###### These indices are identified by using a Shiny App called bulletinspectR
-idf.idx <- c(23,35,39,41,102,126,149)
-idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
-
-#### include the ground truth for Hamby44
-key.table <- tibble(
-  bullet.id = c("K",
-                "O",
-                "L",
-                "P",
-                "J",
-                "H",
-                "I",
-                "Y",
-                "G",
-                "E",
-                "U",
-                "X",
-                "F",
-                "T",
-                "S"),
[…]

### 2021-09-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
suggestion for a lollipop visual

@@
 
+p.seg_252_plot <- table.252.cmps_seg %>%
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+               names_to = "Metric") %>%
+  ggplot(aes(x = factor(seg_length))) +
+  geom_bar(aes(weight =  value, fill = Metric), position=position_dodge(width = 0.5), width=.1) +
+  geom_point(aes(y =  value, color = Metric), position=position_dodge(width = 0.5), size = 5) +
+#  scale_x_continuous(breaks = table.252.cmps_seg$seg_length) +
+  theme_bw() +
+  ggtitle("A Temp Title") +
+  ylab("Sum of Squares Ratio") + 
+  xlab("seg_length")
+
 # 252 - npeak

### 2021-09-10 CMPSpaper_writing/CMPSpaper_writing.Rmd
fig 11 + 13

--- 2021-09-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
   chunk_output_type: inline
+  markdown: 
+    wrap: sentence
 ---
@@
 ```
-
+```{=tex}
 \hh{Still to add: the CMPS diff measure, in which you subtract the background. 
@@
 special request from Alicia :)}
-
+```
 ```{r, echo=FALSE, message=FALSE, warning=FALSE}
@@
 library(kableExtra)
+library(patchwork)
 
@@
 or maybe gun violence?
-XXX} -->
-<!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
-An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
+XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide --> An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
 Here, in particular, we are interested to determine whether two bullets were fired from the same gun barrel.
@@
 
-A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification—is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940;@cmps].
+A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940; @cmps].
 Note that this is not an exhaustive list of these efforts.
@@
 Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison.
-For algorithmic purposes,
-3D topographical images of land engraved areas were obtained and stored in  x3p format (XML 3-D Surface Profile).
+For algorithmic purposes, 3D topographical images of land engraved areas were obtained and stored in x3p format (XML 3-D Surface Profile).
 The x3p format provides a standard way of exchanging 2D and 3D profile data.
-It conforms to the ISO5436-2 standard [http://sourceforge.net/p/open-gps/mwiki/X3p/]  adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
+It conforms to the ISO5436-2 standard [<http://sourceforge.net/p/open-gps/mwiki/X3p/>] adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
 Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
@@
 To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], `bulletinspectR` to identify and correct those errors.
-An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
-Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
+An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible} Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
 
@@
 ### Conceptual idea of CMPS
-Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940 ].
+
+Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940].
 The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
@@
 Note that researchers in @cmps refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.
-  High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair. Low scores between pairs of signatures are attributed to different source pairs.
+High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
+Low scores between pairs of signatures are attributed to different source pairs.
 However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
 Further research is needed to understand how to determine the threshold.
-  <!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source? And what was the error rate in their example?} -->
-  <!-- \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example?
+<!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source?
+And what was the error rate in their example?} --> <!-- \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example?
 ...
-'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'} -->
- The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
+'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'} --> The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
 Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package CMPS available from Github \url{https://github.com/willju-wangqian/CMPS}
-With our implementation, one can compute the CMPS score of a comparison using the following code:
+Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package CMPS available from Github \url{https://github.com/willju-wangqian/CMPS} With our implementation, one can compute the CMPS score of a comparison using the following code:
 
@@
 
-1. **cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:**
-The command `get_segs(x, len=50)` implements this step:  it takes  bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
+1.
+**cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command `get_segs(x, len=50)` implements this step: it takes bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
 
@@
     \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
-    + **Calculate the cross-correlation curve:**  Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
+
+    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
 The position indicates the lag by which a basis segment is moved with respect to its original placement.
 A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the reference.
-    + **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
+
+    -   **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
 The latter is also called "multi-segment lengths strategy".
 The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:
+
         -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
@@
 The resulting list is called `ccr.list`.
-    +  **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
+
+    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
 Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.
+
         -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment.
@@
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
-<!--Additionally, as shown in @cmps, using multi-segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
-The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Here we present it with its default parameters.
+<!--Additionally, as shown in @cmps, using multi-segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.--> The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
+Here we present it with its default parameters.
 
@@
 
-* `x` and `y` are  two  signatures:  `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;
-
-* `include` determines the format of the function result.
+-   `x` and `y` are two signatures: `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;
+
+-   `include` determines the format of the function result.
     Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed.
@@
     If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.
+
     -   `nseg`: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
@@
 
-* `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
+-   `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
     By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
@@
 <!-- [examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf] -->
+
 <!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->
@@
 <!-- ```{r, eval=FALSE} -->
+
 <!-- install.packages("CMPS") -->
+
 <!-- ``` -->
@@
 
-In the first example, `npeaks.set` is a vector of three integers, i.e.
-the algorithm uses the multi-segment lengths strategy to create the result object `cmps_with_multi_scale`.
+In the first example, `npeaks.set` is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object `cmps_with_multi_scale`.
 For `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
@@
 
-*   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}.
+-   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}.
 On this plot the reference signature is drawn as a black line, congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.
@@
 
-*   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}.
+-   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}.
 This visual presents both the comparison signature and the reference signature.
@@
 
+```{=tex}
 \begin{figure}[hbt]
@@
 \end{figure}
-
-*   Other elements of this list are `seg_shift` and `sig_shift`.
+```
+-   Other elements of this list are `seg_shift` and `sig_shift`.
 `sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
@@
 -->
+
 <!-- which basis segments are the congruent matching profile segments. -->
@@
 
-*   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length).
+-   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length).
 We used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
@@
 The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
-*   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
+-   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
 It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6.
@@
 
+```{=tex}
 \begin{figure}
@@
 \end{figure}
-
+```
 Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
 
+```{=tex}
 \begin{figure}
@@
 \end{figure}
-
+```
 In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
@@
 
+```{=tex}
 \begin{align}
@@
 \end{align}
-
+```
 <!-- \begin{align} -->
+
 <!-- \mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\ -->
+
 <!-- \mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]. -->
+
 <!-- \end{align} -->
+
 <!-- \hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here} -->
@@
 \end{align}
-
+```
 $\mathrm{\overline{CMPS}_{diff}}$ highlights the difference between CMPS scores of matching and non-matching comparisons.
@@
 \end{align}
-
+```
 The scaled CMPS scores of the above example are shown in \autoref{fig:tiles2}(b).
@@
 \end{align}
-
-where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations. Then we can define the sum of squares ratio $V$ as:
-
+```
+where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations.
+Then we can define the sum of squares ratio $V$ as:
+
+```{=tex}
 \begin{align}
@@
 \end{align}
-
+```
 The numerator of the sum of squares ratio $V$ quantifies the variation between the two groups, while the denominator quantifies the variation within each group.
@@
 
-```{r plot_computation, echo=FALSE}
+```{r color-settings, echo=FALSE}
+
+cols_1 <- c("#C583AE","#FFDFAA", "#748BA7", "#D9F0A0")
+cols_2 <- c("#A45287","#D4AC6A", "#4C688B", "#ABC864")
+# #####  Color Palette by Paletton.com
+# #####  Palette URL: http://paletton.com/#uid=7561m0kllllaFw0g0qFqFg0w0aF
+# 
+# 
+# *** Primary color:
+# 
+#    shade 0 = #832C65 = rgb(131, 44,101) = rgba(131, 44,101,1) = rgb0(0.514,0.173,0.396)
+#    shade 1 = #C583AE = rgb(197,131,174) = rgba(197,131,174,1) = rgb0(0.773,0.514,0.682)
+#    shade 2 = #A45287 = rgb(164, 82,135) = rgba(164, 82,135,1) = rgb0(0.643,0.322,0.529)
+#    shade 3 = #621046 = rgb( 98, 16, 70) = rgba( 98, 16, 70,1) = rgb0(0.384,0.063,0.275)
+#    shade 4 = #42002B = rgb( 66,  0, 43) = rgba( 66,  0, 43,1) = rgb0(0.259,0,0.169)
+# 
+# *** Secondary color (1):
+# 
+#    shade 0 = #AA7F39 = rgb(170,127, 57) = rgba(170,127, 57,1) = rgb0(0.667,0.498,0.224)
+#    shade 1 = #FFDFAA = rgb(255,223,170) = rgba(255,223,170,1) = rgb0(1,0.875,0.667)
+#    shade 2 = #D4AC6A = rgb(212,172,106) = rgba(212,172,106,1) = rgb0(0.831,0.675,0.416)
+#    shade 3 = #805715 = rgb(128, 87, 21) = rgba(128, 87, 21,1) = rgb0(0.502,0.341,0.082)
+#    shade 4 = #553500 = rgb( 85, 53,  0) = rgba( 85, 53,  0,1) = rgb0(0.333,0.208,0)
+# 
+# *** Secondary color (2):
+# 
+#    shade 0 = #2B4970 = rgb( 43, 73,112) = rgba( 43, 73,112,1) = rgb0(0.169,0.286,0.439)
+#    shade 1 = #748BA7 = rgb(116,139,167) = rgba(116,139,167,1) = rgb0(0.455,0.545,0.655)
+#    shade 2 = #4C688B = rgb( 76,104,139) = rgba( 76,104,139,1) = rgb0(0.298,0.408,0.545)
+#    shade 3 = #143054 = rgb( 20, 48, 84) = rgba( 20, 48, 84,1) = rgb0(0.078,0.188,0.329)
+#    shade 4 = #051B38 = rgb(  5, 27, 56) = rgba(  5, 27, 56,1) = rgb0(0.02,0.106,0.22)
+# 
+# *** Complement color:
+# 
+#    shade 0 = #81A035 = rgb(129,160, 53) = rgba(129,160, 53,1) = rgb0(0.506,0.627,0.208)
+#    shade 1 = #D9F0A0 = rgb(217,240,160) = rgba(217,240,160,1) = rgb0(0.851,0.941,0.627)
+#    shade 2 = #ABC864 = rgb(171,200,100) = rgba(171,200,100,1) = rgb0(0.671,0.784,0.392)
+#    shade 3 = #5B7814 = rgb( 91,120, 20) = rgba( 91,120, 20,1) = rgb0(0.357,0.471,0.078)
+#    shade 4 = #395000 = rgb( 57, 80,  0) = rgba( 57, 80,  0,1) = rgb0(0.224,0.314,0)
+# 
+# 
+# #####  Generated by Paletton.com (c) 2002-2014
+```
+
+```{r plot_computation, echo=FALSE, fig.width=8, fig.height = 8, out.width='\\linewidth'}
 # 252 - seg
@@
 
-p.seg_252_plot <- table.252.cmps_seg %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
-               names_to = "Metric") %>%
-  ggplot(aes(x = seg_length, y = value)) +
-  geom_line(aes(color = Metric)) + 
-  scale_x_continuous(breaks = table.252.cmps_seg$seg_length) +
+table.252.cmps_seg.long <- table.252.cmps_seg %>%
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, 
+                        cmps.max, cmps.maxbar), 
+               names_to = "Metric")
+
+table.252.cmps_seg.long <- table.252.cmps_seg.long %>% 
+  mutate(study = "Hamby 252")
+
+# p.seg_252_plot <- table.252.cmps_seg.long %>%
+#   ggplot(aes(x = seg_length, y = value)) +
+#   geom_line(aes(color = Metric)) + 
+#   scale_x_continuous(breaks = table.252.cmps_seg$seg_length) +
+#   theme_bw() +
+#   ggtitle("A Temp Title") +
+#   ylab("Sum of Squares Ratio") + 
+#   xlab("seg_length")
+
+labels <- expression(CMPS[diff], {CMPS^symbol("*")} [diff], CMPS[max], bar(CMPS)[max])
+
+p.seg_252_plot <- table.252.cmps_seg.long %>%
+  ggplot(aes(x = seg_length +3*as.numeric(factor(Metric))-9)) +
+  geom_segment(aes(xend =  seg_length +3*as.numeric(factor(Metric))-9,
+               y = value, yend = 0, colour = Metric)) + 
+#  geom_bar(aes(weight =  value, fill = Metric), 
+#           position=position_dodge(width = 0.6), width=.1) +
+  geom_point(aes(y =  value, color = Metric), 
+             alpha = 0.8,
+             position=position_dodge(width = 0.5), size = 3.5) +
+  scale_x_continuous(breaks = table.252.cmps_seg$seg_length, 
+                     minor_breaks = NULL) +
   theme_bw() +
-  ggtitle("A Temp Title") +
+  theme(legend.position="none") +
+  ggtitle("Results for Hamby 252") +
   ylab("Sum of Squares Ratio") + 
-  xlab("seg_length")
+  xlab("seg_length") +
+  scale_colour_manual(values=cols_2, labels = labels) +
+  scale_fill_manual(values=cols_1, labels = labels)
 
@@
 
-p.seg_44_plot <- table.44.cmps_seg %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
-               names_to = "Metric") %>%
-  ggplot(aes(x = seg_length, y = value)) +
-  geom_line(aes(color = Metric)) + 
-  scale_x_continuous(breaks = table.44.cmps_seg$seg_length) +
+table.44.cmps_seg.long <- table.44.cmps_seg %>%
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, 
+                        cmps.max, cmps.maxbar),
+               names_to = "Metric")
+
+# p.seg_44_plot <- table.44.cmps_seg.long %>%
+#   ggplot(aes(x = seg_length, y = value)) +
+#   geom_line(aes(color = Metric)) + 
+#   scale_x_continuous(breaks = table.44.cmps_seg$seg_length) +
+#   theme_bw() +
+#   ggtitle("A Temp Title") +
+#   ylab("Sum of Squares Ratio") + 
+#   xlab("seg_length")
+
+table.44.cmps_seg.long <- table.44.cmps_seg.long %>% mutate(
+  study = "Hamby 44"
+)
+
+table.cmps_seg.long <- bind_rows(table.44.cmps_seg.long,
+                                 table.252.cmps_seg.long)
+
+p.seg_plot <- table.cmps_seg.long %>%
+  ggplot(aes(x = seg_length+3*as.numeric(factor(Metric))-9)) +
+#  geom_bar(aes(weight =  value, fill = Metric), 
+#           position=position_dodge(width = 0.6), width=.1) +
+  geom_segment(aes(xend = seg_length+3*as.numeric(factor(Metric))-9, 
+                   y = value, yend= 0, color=Metric),
+               position=position_dodge(width = 0.6)) +
+  geom_point(aes(y =  value, color = Metric), 
+             alpha = 0.8,
+             position=position_dodge(width = 0.5), size = 3.5) +
+  scale_x_continuous(breaks = table.44.cmps_seg$seg_length, 
+                     minor_breaks = NULL) +
   theme_bw() +
-  ggtitle("A Temp Title") +
-  ylab("Sum of Squares Ratio") + 
-  xlab("seg_length")
+  theme(legend.position = "bottom") +
+  ylab("Sums of Squares Ratio") + 
+  xlab("Segment length") +
+  scale_colour_manual(values=cols_2, labels = labels) +
+  scale_fill_manual(values=cols_1, labels = labels) + 
+  facet_grid(.~study)
 
@@
 <!-- this is figure 2 -->
+
 ```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) ", fig.height=3}
@@
 default parameters can be beaten?
-cmps.diff, cmps.maxbar and their scaled version are good? we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
+cmps.diff, cmps.maxbar and their scaled version are good?
+we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
 Note that the goal of these comparisons is not to determine the optimal set of parameters for the CMPS algorithm, but to show a general procedure that can be used for
@@
 ```{r seg_252_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
-p.seg_252_plot
+p.seg_plot 
 ```
@@
 
+<!--
 ```{r seg_44_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
-p.seg_44_plot
-```
+#p.seg_44_plot
+```
+-->
 
@@
 -->
+
 <!-- <!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
 -->
+
 <!-- As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results.  -->
+
 <!-- \autoref{tab:table1} presents some summary statistics of the Hamby 44 results above.
@@
 <!-- * A R file will be generated automatically using `knitr::purl` - see -->
+
 <!-- https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information. -->
+
 <!-- * A tex file will be generated from this Rmd file and correctly included in -->
+
 <!-- `RJwapper.tex` as expected to build `RJwrapper.pdf`. -->
+
 <!-- * All figure files will be kept in the default rmarkdown `*_files` folder. This -->
+
 <!-- happens because `keep_tex = TRUE` by default in `rticles::rjournal_article` -->
+
 <!-- * Only the bib filename is to modifed. An example bib file is included in the -->
+
 <!-- template (`RJreferences.bib`) and you will have to name your bib file as the -->
+
 <!-- tex, R, and pdf files. -->

### 2021-09-15 CMPSpaper_writing/CMPSpaper_writing.Rmd
comments added

--- 2021-09-09 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 
+cmps.max is not the best metric to measure similarity 
+the one we prefer
+cmps.diff, cmps.maxbar and their scaled version are good? we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
+
+parameters need cross-validation
+choice of parameters depends on resolution ( scanning process ) and the data set
+determining the source is a harder task for Hamby 44 than for Hamby 252 
 default parameters can be beaten?
-cmps.diff, cmps.maxbar and their scaled version are good? we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
+
 Note that the goal of these comparisons is not to determine the optimal set of parameters for the CMPS algorithm, but to show a general procedure that can be used for 
+a larger database that is representative
+procedure that could be used to reach that point
+
+**Comparing with Random Forest**
+
+Introduce the work , cite the paper 
+CSAFE trained
 

### 2021-09-16 code/compute_ss_original_results.R
add codes and results for the random forest and the original paper

@@ -1,0 +1,58 @@
+library(magrittr, include.only = c("%<>%", "%$%"))
+
+result.container <- list()
+
+result.container$npeak <- c("n5", "n531", "n5", "n531")
+result.container$metrics <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
+
+dd.list <- list()
+
+dd.list[[1]] <- tibble(
+  score = c(9:13, 16:24),
+  freq = c(132, 282, 115, 19, 1, 1, 3,2,4,8,12,7,7,2),
+  type = c(rep("KNM", 5), rep("KM", 9))
+)
+
+dd.list[[2]] <- tibble(
+  score = c(1:5, 14:23),
+  freq = c(7,343,168,24,7,1,1,2,3,6,7,8,8,7,3),
+  type = c(rep("KNM", 5), rep("KM", 10))
+)
+
+dd.list[[3]] <- tibble(
+  score = c(6:9, 13:19),
+  freq = c(2,210,307,30,6,3,9,9,11,7,1),
+  type = c(rep("KNM", 4), rep("KM", 7))
+)
+
+dd.list[[4]] <- tibble(
+  score = c(0:2, 8:17),
+  freq = c(36, 508, 5, 1,3,4,2,11,3,9,8,4,1),
+  type = c(rep("KNM", 3), rep("KM", 10))
+)
+
+result.container$dd.list <- dd.list
+
+result.container <- result.container %>% as_tibble()
+
+result.container %<>% as_tibble()
+
+result.container %<>% mutate(
+  dd.table = purrr::map(dd.list, function(dd) {
+    tibble(score = rep(dd$score, dd$freq),
+           type_truth = rep(dd$type, dd$freq))
+  }),
+  ss.ratio = purrr::map_dbl(dd.table, function(dd) {
+    compute_var_ratio_anova(dd$score, dd$type_truth, MS = FALSE)
+  })
+) 
+
+
+
+
+
+
+
+
+
+

### 2021-09-16 code/rf_summary_script.R

@@ -11,6 +11,8 @@ df.rf <- lapply(rf44.container, function(rf_result) {
   })
 }) %>% do.call(rbind, .) %>% as.data.frame()
 
+rf44.container[[1]]$rf.table[[1]] %>% metric_plot_helper("rf.diff.med", scaled = TRUE)
+
 df.rf$rf <- c("features", "legacy_feature")
 df.rf$span3 <- c("default", "default")
 

### 2021-09-16 reproducible/hamby252_rf_result_generator.R

@@ -147,8 +147,8 @@ b252[[CMPS_hamby252_results$signame[[i]]]] <- purrr::map2(
 
 # process of removing outliers
 tt <- lapply(b252[[CMPS_hamby252_results$signame[[i]]]], function(x) {
-    x$sig
-  }) %>% unlist()
+  x$sig
+}) %>% unlist()
 qtt <- quantile(tt, na.rm = TRUE)
 multi.iqr <- 3
 outrange <- c(qtt[2] - multi.iqr * (qtt[4] - qtt[2]),
@@ -204,7 +204,7 @@ system.time({
                                .f = my_extract_feature_all, resolution = 1.5625), 
         legacy_features = purrr::map(striae, 
                                      extract_features_all_legacy, resolution = 1.5625))
-      # tidyr::unnest(features) # change: instead of legacy_feature
+    # tidyr::unnest(features) # change: instead of legacy_feature
     
     # tmp.comp$rf_score <- predict(bulletxtrctr::rtrees, newdata = tmp.comp, 
     #                             type = "prob")[, 2]
@@ -212,7 +212,7 @@ system.time({
                                  newdata = tmp.comp %>% tidyr::unnest(features) %>% mutate(
                                    abs_lag_mm = abs(lag_mm)
                                  ),
-                                type = "prob")[, 2]
+                                 type = "prob")[, 2]
     
     rf.table <-
       tmp.comp %>% dplyr::select(land1, land2, landidx1, landidx2, 
@@ -250,52 +250,15 @@ hamby252.rf <- hamby252.rf %>% mutate(
   })
 ) %>% tidyr::unnest(metric_list_scaled)
 
-# hamby252.rf <- bind_cols(hamby252.rf %>% dplyr::select(-metric_list), 
-#                            bind_rows(hamby252.rf$metric_list)) 
-
 # add type and type_truth
 hamby252.rf$type <- tmp.tibble$type
 hamby252.rf$type_truth <- tmp.tibble$type_truth
 
-###################################
-# save result in a list
-CMPS_hamby252_results$rf.table[[i]] <- hamby252.rf
+hamby252.csv <- hamby252.rf %>% select(-rf.table, -rf.table.m)
 
-filepath <- "code/saved_rds/h252_rf2_features_rmo.rds"
-
-# saveRDS(CMPS_hamby252_results, filepath)
-
-rf_hamby252_results <- readRDS(filepath)
-
[…]

### 2021-09-16 reproducible/hamby44_rf_result_generator.R

@@ -1,0 +1,266 @@
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+source("code/func_collection.R")
+
+b44.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+
+rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
+
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+
+# generate bullet_id
+bulletid.tb <- b44.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# remove x3p files
+b44 <- b44.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get all comparisons
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# get ground-truth
+key.table <- tibble(
+  bullet.id = c(
+    "K",
+    "O",
+    "L",
+    "P",
+    "J",
+    "H",
+    "I",
+    "Y",
+    "G",
+    "E",
+    "U",
+    "X",
+    "F",
+    "T",
+    "S"
+  ),
+  barrel.id = c(1, 2, 3, 4, 4, 5, 5, 6, 6, 7, 7, 7, 8, 9, 10)
+)
+
+tmp.table.44 <- tibble(bullet1 = b.cb[1, ],
+                       bullet2 = b.cb[2, ])
+
+tmp.table.44$b1t <-
+  tmp.table.44$bullet1 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+tmp.table.44$b2t <-
+  tmp.table.44$bullet2 %>% str_extract("'[A-Z]'") %>% str_extract("[A-Z]")
+
+tmp.table.44$b1b <-
[…]

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
add changes for plots and comments in the Results section

--- 2021-09-10 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 editor_options: 
-  chunk_output_type: inline
+  chunk_output_type: console
   markdown: 
@@
 ```
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
 library(knitr)
@@
 library(bulletxtrctr)
-library(knitr)
 library(kableExtra)
 library(patchwork)
+library(ggpubr)
 
@@
 
-# generate plots
-# for (i in 1:3) {
-#   hamby252.cmps <- CMPS_hamby252_results$cmps.table[[i]]
-#   
-#   hamby252.plot.list <- list()
-#   titlee <- CMPS_hamby252_results$titlee[[i]]
-#   
-#   hamby252.plot.list[[1]] <- hamby252.cmps %>% ggplot() +
-#     geom_histogram(aes(x = cmps.max.m,
-#                        fill = as.factor(type_truth)), binwidth = 1) +
-#     labs(
-#       fill = "Comparison Type",
-#       x = expression(CMPS[max]),
-#       # title = expression(paste("Hamby252 - ", CMPS[max], " Distribution")),
-#       subtitle = titlee
-#     ) +
-#     scale_x_continuous(breaks = seq(0, 27, 1)) +
-#     theme_bw() +
-#     theme(panel.grid.minor = element_blank()) +
-#     font("x.text", size = 6) +
-#     scale_fill_manual(values=c("darkorange", "darkgrey"))
-#     
-#   hamby252.plot.list[[2]] <- hamby252.cmps %>% ggplot() +
-#     geom_histogram(aes(x = cmps.maxbar.m,
-#                        fill = as.factor(type_truth)), binwidth = 1) +
-#     labs(
-#       x = expression(bar(CMPS)[max]),
-#       fill = "Comparison Type",
-#       # title = expression(paste(
-#       #   "Hamby252 - ", bar(CMPS)[max], " Distribution"
-#       # )),
-#       subtitle = titlee
-#     ) +
-#     scale_x_continuous(breaks = seq(0, 24, 1)) +
-#     theme_bw() +
-#     theme(panel.grid.minor = element_blank()) +
-#     scale_fill_manual(values=c("darkorange", "darkgrey"))
-#   
-#   plot <- ggarrange(plotlist = hamby252.plot.list,
-#                     nrow = 1,
-#                     ncol = 2,
-#                     common.legend = TRUE, legend = "bottom")
-#   plot <- annotate_figure(plot, 
-#                           top = text_grob(com.title252))
-#   CMPS_hamby252_results$plot[[i]] <- plot
-# }
-
 ```
@@
 CMPS_hamby44_results_npeak <- CMPS_hamby44_results
+```
+
+```{r rf-data-load, echo=FALSE}
+rf.results <- list()
+rf.results[[1]] <- read.csv(file = "./data/hamby252/hamby252_rf_results.csv")
+rf.results[[2]] <- read.csv(file = "./data/hamby44/hamby44_rf_results.csv")
+
+rf.tt <- lapply(rf.results, function(rf_result) {
+  with(rf_result, {
+    tibble(rf.diff, rf.max, rf.maxbar) %>% 
+      apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+  })
+}) %>% do.call(rbind, .) %>% as_tibble()
+
+colnames(rf.tt) <- c("cmps.diff", "cmps.max", "cmps.maxbar")
+
+rf.tt$study <- c("Hamby 252", "Hamby 44")
+rf.tt <- rf.tt %>% pivot_longer(
+  cols = c("cmps.diff", "cmps.max", "cmps.maxbar"),
+  names_to = "Metric"
+)
+
+rf.tt$npeak <- "RandomForest"
+
+```
+
+```{r ss-original-cmps, echo=FALSE}
+result.container <- list()
+
+result.container$npeak <- c("5*", "5-3-1*", "5*", "5-3-1*")
+result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
+result.container$study <- "Hamby 252"
+
+dd.list <- list()
+
+dd.list[[1]] <- tibble(
+  score = c(9:13, 16:24),
+  freq = c(132, 282, 115, 19, 1, 1, 3,2,4,8,12,7,7,2),
+  type = c(rep("KNM", 5), rep("KM", 9))
+)
+
+dd.list[[2]] <- tibble(
+  score = c(1:5, 14:23),
+  freq = c(7,343,168,24,7,1,1,2,3,6,7,8,8,7,3),
+  type = c(rep("KNM", 5), rep("KM", 10))
+)
+
+dd.list[[3]] <- tibble(
+  score = c(6:9, 13:19),
+  freq = c(2,210,307,30,6,3,9,9,11,7,1),
+  type = c(rep("KNM", 4), rep("KM", 7))
+)
+
+dd.list[[4]] <- tibble(
+  score = c(0:2, 8:17),
+  freq = c(36, 508, 5, 1,3,4,2,11,3,9,8,4,1),
+  type = c(rep("KNM", 3), rep("KM", 10))
+)
+
+result.container$dd.list <- dd.list
+
+result.container <- result.container %>% as_tibble() %>% 
+  mutate(
+    dd.table = purrr::map(dd.list, function(dd) {
+      tibble(score = rep(dd$score, dd$freq),
+             type_truth = rep(dd$type, dd$freq))
+    }),
+    value = purrr::map_dbl(dd.table, function(dd) {
+      compute_var_ratio_anova(dd$score, dd$type_truth, MS = FALSE)
+    })
+  ) 
 ```
@@
 
-# p.seg_252_plot <- table.252.cmps_seg.long %>%
-#   ggplot(aes(x = seg_length, y = value)) +
-#   geom_line(aes(color = Metric)) + 
-#   scale_x_continuous(breaks = table.252.cmps_seg$seg_length) +
-#   theme_bw() +
-#   ggtitle("A Temp Title") +
-#   ylab("Sum of Squares Ratio") + 
-#   xlab("seg_length")
-
-labels <- expression(CMPS[diff], {CMPS^symbol("*")} [diff], CMPS[max], bar(CMPS)[max])
+labels <- expression(bar(CMPS)[diff], {bar(CMPS)^symbol("*")}[diff], CMPS[max], bar(CMPS)[max])
 
@@
                y = value, yend = 0, colour = Metric)) + 
-#  geom_bar(aes(weight =  value, fill = Metric), 
-#           position=position_dodge(width = 0.6), width=.1) +
   geom_point(aes(y =  value, color = Metric), 
@@
 
-# 252 - npeak
-table.252.cmps_npeak <- lapply(CMPS_hamby252_results_npeak$cmps.table, function(tt) {
-  type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks.set %>% 
-  purrr::map(.f = paste, collapse = "-")
-
-p.npeak_252_plot <- table.252.cmps_npeak %>% 
-  mutate(
-    npeak = factor(
-      npeak,
-      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
-  ) %>% 
-  pivot_longer(cols = c(cmps.diff:cmps.maxbar_scaled),
-               names_to = "Metric") %>% 
-  ggplot(aes(x=npeak, y=value)) +
-  geom_bar(aes(fill = Metric),position = "dodge", stat = "identity") + 
-  ylab("Sum of Squares Ratio") +
-  coord_flip() + 
-  theme_bw()
-
 # 44 - seg
@@
 
-# p.seg_44_plot <- table.44.cmps_seg.long %>%
-#   ggplot(aes(x = seg_length, y = value)) +
-#   geom_line(aes(color = Metric)) + 
-#   scale_x_continuous(breaks = table.44.cmps_seg$seg_length) +
-#   theme_bw() +
-#   ggtitle("A Temp Title") +
-#   ylab("Sum of Squares Ratio") + 
-#   xlab("seg_length")
-
 table.44.cmps_seg.long <- table.44.cmps_seg.long %>% mutate(
@@
 
+breaks_fun <- function(x) {
+  if(x[2] < 220) {
+    c(25,  50,  75, 100, 125, 150, 175, 200)
+  } else {
+    c(30, 45,  61,  90, 122, 150, 180, 210)
+  }
+}
+
 p.seg_plot <- table.cmps_seg.long %>%
   ggplot(aes(x = seg_length+3*as.numeric(factor(Metric))-9)) +
-#  geom_bar(aes(weight =  value, fill = Metric), 
-#           position=position_dodge(width = 0.6), width=.1) +
   geom_segment(aes(xend = seg_length+3*as.numeric(factor(Metric))-9, 
@@
              position=position_dodge(width = 0.5), size = 3.5) +
-  scale_x_continuous(breaks = table.44.cmps_seg$seg_length, 
+  facet_grid(.~study, scales = "free_x") +
+  scale_x_continuous(breaks = breaks_fun, 
                      minor_breaks = NULL) +
@@
   scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels) + 
-  facet_grid(.~study)
-
-# 44 - npeak
+  scale_fill_manual(values=cols_1, labels = labels)
+
+# npeak - 252
+table.252.cmps_npeak <- lapply(CMPS_hamby252_results_npeak$cmps.table, function(tt) {
+  type_truth <- tt$type_truth
+  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
+    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
+}) %>% do.call(rbind, .) %>% as.data.frame()
+
+table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks.set %>% 
+  purrr::map(.f = paste, collapse = "-") %>% sapply(as.character)
+
+table.252.cmps_npeak.longer <- table.252.cmps_npeak %>% as_tibble() %>% 
+  filter(npeak %in% c("5", "5-3-1", "10-8-6-4-2-1", "10-7-4-2")) %>% 
+  mutate(
+    npeak = factor(
+      npeak,
+      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
+  ) %>% 
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+               names_to = "Metric") 
+table.252.cmps_npeak.longer$study <- "Hamby 252"
+
+# npeak - 44
 table.44.cmps_npeak <- lapply(CMPS_hamby44_results_npeak$cmps.table, function(tt) {
@@
 table.44.cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks.set %>% 
-  purrr::map(.f = paste, collapse = "-")
-
-p.npeak_44_plot <- table.44.cmps_npeak %>% 
+  purrr::map(.f = paste, collapse = "-") %>% sapply(as.character)
+
+table.44.cmps_npeak.longer <- table.44.cmps_npeak %>% as_tibble() %>% 
+  filter(npeak %in% c("5", "5-3-1", "10-8-6-4-2-1", "10-7-4-2")) %>% 
   mutate(
@@
   ) %>% 
-  pivot_longer(cols = c(cmps.diff:cmps.maxbar_scaled),
-               names_to = "Metric") %>% 
-  ggplot(aes(x=npeak, y=value)) +
-  geom_bar(aes(fill = Metric),position = "dodge", stat = "identity") + 
-  ylab("Sum of Squares Ratio") +
+  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+               names_to = "Metric") 
+table.44.cmps_npeak.longer$study <- "Hamby 44"
+
+selected_var <- c("npeak", "Metric", "study", "value")
+
+table.cmps_neapk.long <- bind_rows(
+  table.252.cmps_npeak.longer %>% select(all_of(selected_var)),
+  table.44.cmps_npeak.longer %>% select(all_of(selected_var)),
+  rf.tt %>% select(all_of(selected_var)),
+  result.container %>% select(all_of(selected_var))
+)
+
+order.level <- table.cmps_neapk.long %>% 
+  filter(Metric == "cmps.maxbar", study == "Hamby 252") %>%
+  {.$npeak[order(.$value, decreasing = FALSE)]}
+
+table.cmps_neapk.long <- table.cmps_neapk.long %>% mutate(
+  npeak = factor(npeak, levels = order.level)
+)
+
+npeak_convert <- with(table.cmps_neapk.long, {
+  tt <- tibble(npeak = levels(npeak))
+  tt$xstart <- seq.int(from = 0, by = 20, length.out = length(tt$npeak))
+  tt
+})
+
+table.cmps_neapk.long <- table.cmps_neapk.long %>% left_join(
+  npeak_convert,
+  by = "npeak"
+)
+
+p.npeak_plot <- table.cmps_neapk.long %>%
+  ggplot(aes(x = xstart + 3*as.numeric(factor(Metric))-9)) +
+  geom_segment(aes(xend = xstart + 3*as.numeric(factor(Metric))-9, 
+                   y = value, yend= 0, color=Metric),
+               position=position_dodge(width = 0.6)) +
+  geom_point(aes(y =  value, color = Metric), 
+             alpha = 0.8,
+             position=position_dodge(width = 0.5), size = 3.5) +
+  facet_grid(.~study) +
+  scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak ) +
   coord_flip() +
-  theme_bw()
+  theme_bw() +
+  theme(legend.position = "bottom") +
+  ylab("Sums of Squares Ratio") + 
+  xlab("npeak") +
+  scale_colour_manual(values=cols_2, labels = labels) +
+  scale_fill_manual(values=cols_1, labels = labels) 
 ```
@@
 p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
-                         subtitle = "npeak: 5-3-1, seg_length: 50")
+                         subtitle = "npeak: 5-3-1, seg_length: 50") +
+  xlab(labels[3])
 p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
-                         subtitle = "npeak: 5-3-1, seg_length: 50")
+                         subtitle = "npeak: 5-3-1, seg_length: 50") +
+  xlab(labels[4])
 p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
@@
 p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
-                         subtitle = "npeak: 5-3-1, seg_length: 61")
+                         subtitle = "npeak: 5-3-1, seg_length: 61") +
+  xlab(labels[3])
 p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
-                         subtitle = "npeak: 5-3-1, seg_length: 61")
+                         subtitle = "npeak: 5-3-1, seg_length: 61") +
+  xlab(labels[4])
 p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
@@
 
+```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+p.seg_plot 
+```
+
+```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+p.npeak_plot
+```
+
+\wj{new added the following}
+
 For both Hamby set 252 and 44, we investigated the effects of different sets of parameters.
-More specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level and modified the parameter `seg_length` that controls the length of a basis segment.
-Then we fixed `seg_length` and examined different values of `npeaks.set`.
-The sum of squares ratios are used to compare among different CMPS metrics and different sets of parameters.
-
-default parameters can be beaten?
-cmps.diff, cmps.maxbar and their scaled version are good?
-we suggest cmps.diff_scaled since it's more comparable and summarizes more information?
-Note that the goal of these comparisons is not to determine the optimal set of parameters for the CMPS algorithm, but to show a general procedure that can be used for
-
-```{r}
-# CMPS_hamby44_results_seg$cmps.table[[3]] %>% 
-#   metric_plot_helper("cmps.max")
-# 
-# CMPS_hamby252_results_seg$cmps.table[[2]] %>% 
-#   metric_plot_helper("cmps.max")
-```
-
-```{r seg_252_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
-p.seg_plot 
-```
-
-```{r npeak_252_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
-p.npeak_252_plot
-```
-
-<!--
-```{r seg_44_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
-#p.seg_44_plot
-```
--->
-
-```{r npeak_44_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
-p.npeak_44_plot
-```
+More specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length` that controls the length of a basis segment.
+As shown in \autoref{fig:param_seg_plot}, the default values of `seg_length` that we used for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics we are using, when `npeaks.set = c(5,3,1)`.
+However, better choices also exist.
+For example, \autoref{fig:param_seg_plot} suggests that basis segment length of 75 might be a better choice than the default value for Hamby 252; basis segment length of 122 result in a higher value of sum of squares ratio for Hamby 44.
+
+Additionally, we fixed `seg_length` to be the default values and examined different choices of `npeaks.set`.
+As shown in \autoref{fig:param_npeak_plot}, `npeaks.set = c(5,3,1)`, the default value of `npeaks.set` leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` could result in higher value of the sum of squares ratio.
+
+As for comparing different CMPS metrics, the results might suggest that using $\mathrm{CMPS_{max}}$ produces the least amount of separation, compared with other CMPS metrics.
+They might also suggest that $\mathrm{\overline{CMPS}_{diff}}$ and $\mathrm{\overline{CMPS^*}_{diff}}$, the two metrics we proposed above, can lead to equally good or even better results as $\mathrm{\overline{CMPS}_{max}}$ can lead to.
+Since $\mathrm{\overline{CMPS^*}_{diff}}$ relies on the scaled CMPS scores that is more comparable to other similarity scores and summarizes the out-of-phase background CMPS scores, we might choose $\mathrm{\overline{CMPS^*}_{diff}}$ over other CMPS metrics.
+
+What we can also observe in \autoref{fig:param_seg_plot} and \autoref{fig:param_npeak_plot} is that the values of the sum of squares ratio for Hamby 44 is lower than those for Hamby 252. 
+This might be because determining the source is a harder task for Hamby 44 than for Hamby 252, but also suggests that the choice of parameters also depends on the resolution or the scanning process of the data set.
+The same set of parameters might work for one data set, but not work for another.
+
+The purpose of the results shown in \autoref{fig:param_seg_plot} and \autoref{fig:param_npeak_plot} is not to determine the "best" parameters for the CMPS algorithm, but to show that the sum of squares ratio can be used as an evaluation measure to compare different parameters, metrics, or scans.
+A pipeline that maximizes the sum of squares ratio might help researchers determine the set of parameters that work best for their data. 
+But a large database that is representative is what we really need in order to fully understand and cross-validate the parameters of the CMPS algorithm.
+
+**Comparing with the Original Results and the Random Forest model**
+
+@cmps presents the histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` with Hamby 252.
+We computed the sum of squares ratios according to those histograms and included the results in \autoref{fig:param_npeak_plot} as well.
+They are marked by an asterisk at the top right corner in \autoref{fig:param_npeak_plot}.
+The sum of squares ratios we obtained for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` is slightly higher than those obtained from the histograms of @cmps. 
+\wj{One interesting observation is that cmps.max works pretty well for 531 in nist's paper... do we need to include this?XXX}
+Since the researchers of @cmps did not use $\mathrm{\overline{CMPS}_{diff}}$ or $\mathrm{\overline{CMPS^*}_{diff}}$, and they did not apply the CMPS algorithm to the Hamby set 44, we were not able to compare those results.
+
+In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores for different metrics. 
+A random forest model can be used for both classification and regression. 
+It is an ensemble learning method that takes advantage of multiple predictive features.
+The random forest model we used here was presented in XXX and trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE).
+Similarly to the CMPS algorithm, this random forest model produces a random forest score that lies between the interval $(0, 1)$ for each land-by-land comparison.
+So the random forest scores are more comparable to the scaled CMPS scores.
+We applied the logic of $\mathrm{{CMPS}_{max}}$, $\mathrm{\overline{CMPS}_{max}}$, and $\mathrm{\overline{CMPS}_{diff}}$ to the random forest scores and obtained results of the random forest model for different metrics.
+As shown in \autoref{fig:param_npeak_plot}, the random forest model does not achieve the sum of squares ratio as high as those achieved by the top CMPS algorithms for Hamby 252, but it does achieve better results for Hamby 44.
+This might suggest researchers to include the CMPS score as an additional feature in the random forest model training.
+
+Introduce the work , cite the paper
 

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

@@
 
-rf.tt$npeak <- "RandomForest"
+rf.tt$npeak <- "RF score (Hare et al)"
 
@@
 
-result.container$npeak <- c("5*", "5-3-1*", "5*", "5-3-1*")
+result.container$npeak <- c("5*", "5-3-1*", "5* (Chen et al)", "5-3-1* (Chen et al)")
 result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
@@
 
-```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter \\texttt{seg\\_length}).
+Only the $\\mathrm{CMPS_{max}}$ metric suggests that the default values for the basis segment length result in the best separation.
+Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones.
+For Hamby 252 these metrics agree that a segment length of 75 and a segment length of 122 for Hamby 44 yield better results", fig.height=3, warning = FALSE}
 p.seg_plot 
@@
 
-```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3}
+```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3, warning = FALSE}
 p.npeak_plot
@@
 
-\wj{new added the following}
-
-For both Hamby set 252 and 44, we investigated the effects of different sets of parameters.
-More specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length` that controls the length of a basis segment.
-As shown in \autoref{fig:param_seg_plot}, the default values of `seg_length` that we used for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics we are using, when `npeaks.set = c(5,3,1)`.
-However, better choices also exist.
-For example, \autoref{fig:param_seg_plot} suggests that basis segment length of 75 might be a better choice than the default value for Hamby 252; basis segment length of 122 result in a higher value of sum of squares ratio for Hamby 44.
-
+We investigated the effects of different sets of parameters at the example of both Hamby sets 252 and 44.
+More specifically, we investigated the separation achieved using the CMPS implementation under various segment lengths (controlled by the parameter   `seg_length`).
+Specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length`.
+\autoref{fig:param_seg_plot} shows that the default values of `seg_length`  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
+However, we also see, that for Hamby set 252 a basis segment length of 75 is a better choice than the default segment length; a basis segment length of 122 results in a higher value of sum of squares ratio for Hamby 44.
+
+\hh{edits up to here}
 Additionally, we fixed `seg_length` to be the default values and examined different choices of `npeaks.set`.

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
last couple of edits

@@
 
-rf.tt$npeak <- "RF score (Hare et al)"
+rf.tt$npeak <- "RF score* (Hare et al)"
 
@@
   ylab("Sum of Squares Ratio") + 
-  xlab("seg_length") +
+  xlab("Segment Length") +
   scale_colour_manual(values=cols_2, labels = labels) +
@@
   ylab("Sums of Squares Ratio") + 
-  xlab("npeak") +
+  xlab("Number of Peaks") +
   scale_colour_manual(values=cols_2, labels = labels) +
@@
 
-```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3, warning = FALSE}
+```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of CMPS results based on different strategies of number of peak selections.
+\\hh{5-3-1 should be next to 5-3-1*}.
+Starred results compare CMPS performance with results published in the literature.
+", fig.height=3, warning = FALSE}
 p.npeak_plot
@@
 
-\hh{edits up to here}
-Additionally, we fixed `seg_length` to be the default values and examined different choices of `npeaks.set`.
-As shown in \autoref{fig:param_npeak_plot}, `npeaks.set = c(5,3,1)`, the default value of `npeaks.set` leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` could result in higher value of the sum of squares ratio.
-
-As for comparing different CMPS metrics, the results might suggest that using $\mathrm{CMPS_{max}}$ produces the least amount of separation, compared with other CMPS metrics.
-They might also suggest that $\mathrm{\overline{CMPS}_{diff}}$ and $\mathrm{\overline{CMPS^*}_{diff}}$, the two metrics we proposed above, can lead to equally good or even better results as $\mathrm{\overline{CMPS}_{max}}$ can lead to.
-Since $\mathrm{\overline{CMPS^*}_{diff}}$ relies on the scaled CMPS scores that is more comparable to other similarity scores and summarizes the out-of-phase background CMPS scores, we might choose $\mathrm{\overline{CMPS^*}_{diff}}$ over other CMPS metrics.
+\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using different stategies for identifying peaks in the correlation structure between signatures.
+Basis segment length is fixed to the default level for this evaluation.
+As can be seen in \autoref{fig:param_npeak_plot}, the default value of `npeaks.set` (`npeaks.set = c(5,3,1)`) leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` match and  exceed this sum of squares ratio value.
+
+As seen before, the results suggest that the $\mathrm{CMPS_{max}}$ metric produces the least amount of separation compared with the other three CMPS metrics.
+They also suggest that the two newly proposed metrics, $\mathrm{\overline{CMPS}_{diff}}$ and $\mathrm{\overline{CMPS^*}_{diff}}$,  lead to equally good or even better results as $\mathrm{\overline{CMPS}_{max}}$.
+Because $\mathrm{\overline{CMPS^*}_{diff}}$ relies on a scaled version of CMPS scores it is more comparable to other similarity scores and summarizes the out-of-phase background CMPS scores, making it superior to the other CMPS metrics.
 
@@
 This might be because determining the source is a harder task for Hamby 44 than for Hamby 252, but also suggests that the choice of parameters also depends on the resolution or the scanning process of the data set.
-The same set of parameters might work for one data set, but not work for another.
+The same set of parameters might work for one data set, but not work equally well for another.
 
@@
 
-@cmps presents the histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` with Hamby 252.
-We computed the sum of squares ratios according to those histograms and included the results in \autoref{fig:param_npeak_plot} as well.
+@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` with (presumably) Hamby 252.
+The values in these histograms allow us to calculate the sum of squares ratios and include the results in \autoref{fig:param_npeak_plot} as well.
 They are marked by an asterisk at the top right corner in \autoref{fig:param_npeak_plot}.
 The sum of squares ratios we obtained for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` is slightly higher than those obtained from the histograms of @cmps. 
-\wj{One interesting observation is that cmps.max works pretty well for 531 in nist's paper... do we need to include this?XXX}
+\wj{One interesting observation is that cmps.max works pretty well for 531 in nist's paper... do we need to include this?XXX} \hh{no need}
 Since the researchers of @cmps did not use $\mathrm{\overline{CMPS}_{diff}}$ or $\mathrm{\overline{CMPS^*}_{diff}}$, and they did not apply the CMPS algorithm to the Hamby set 44, we were not able to compare those results.
 
-In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores for different metrics. 
-A random forest model can be used for both classification and regression. 
-It is an ensemble learning method that takes advantage of multiple predictive features.
-The random forest model we used here was presented in XXX and trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE).
-Similarly to the CMPS algorithm, this random forest model produces a random forest score that lies between the interval $(0, 1)$ for each land-by-land comparison.
-So the random forest scores are more comparable to the scaled CMPS scores.
+In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
+<!--A random forest model can be used for both classification and regression. 
+It is an ensemble learning method that takes advantage of multiple predictive features.-->
+The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package `bulletxtrctr` [@bulletxtrctr].
+Similarly to the CMPS algorithm, this random forest model produces a  score to quantify the similarity of a land-by-land comparison.
+The RF scores lie in an interval of [0,1] making them most comparable to the scaled CMPS scores.
 We applied the logic of $\mathrm{{CMPS}_{max}}$, $\mathrm{\overline{CMPS}_{max}}$, and $\mathrm{\overline{CMPS}_{diff}}$ to the random forest scores and obtained results of the random forest model for different metrics.
 As shown in \autoref{fig:param_npeak_plot}, the random forest model does not achieve the sum of squares ratio as high as those achieved by the top CMPS algorithms for Hamby 252, but it does achieve better results for Hamby 44.
-This might suggest researchers to include the CMPS score as an additional feature in the random forest model training.
-
-Introduce the work , cite the paper
+This might suggest that an inclusion of the CMPS score as an additional feature in the random forest model training might be beneficial for an overall separation to determine source.
 
@@
 
-The codes generating those results can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
+The code generating all results of this manuscript can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
 
@@
 
-In this paper we presented the CMPS package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and applied it to two datasets in Hamby study [@hamby] to show its potential for further research.
+In this paper we present the CMPS package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
 The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
-We introduced the basic logic of the CMPS algorithm and how it is implemented in the CMPS package.
-We also showcased the functionality of the CMPS package with a small dataset example that is included in the package.
-In the CMPS package we also implemented some graphing tools for users to visualize results generated by our functions and to have a better understanding of both the algorithm and the results.
-
-Additionally, we applied the CMPS package to two datasets in Hamby study (Hamby set 252 and Hamby set 44), and the results we obtained were promising since we were able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known-match (KM) comparisons and known-nonmatch (KNM) comparisons.
-However, the results of Hamby set 44 suggested that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment level.
+We introduce the basic logic of the CMPS algorithm and lay out its implementation in the CMPS package.
+We also showcase the functionality of the CMPS package with a small dataset example that is included in the package.
+In the CMPS package we  implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
+
+Additionally, we apply the CMPS package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).
+The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known-match (KM) comparisons and known-nonmatch (KNM) comparisons in another bullet study.
+However, the results of Hamby set 44 suggest that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment level.
 This indicates that further research is needed to provide a comprehensive cross-validation on parameters used the algorithm.
-Moreover, we might want to compare the two versions of the CMPS algorithm in the future as well.
-
-The CMPS package as an open-source implementation introduces the CMPS algorithm to the `R` community and allows people to use it for their own projects.
+
+The CMPS package provides an open-source implementation and introduces the CMPS algorithm to the `R` community.
+
+\hh{XXX Which 'It' are you referring to?}
 It would also facilitate future studies on parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can potentially be used to estimate error rates or define an identification criterion.

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
some text for the caption

--- 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 
-result.container$npeak <- c("5*", "5-3-1*", "5* (Chen et al)", "5-3-1* (Chen et al)")
+result.container$npeak <- 
+  c("5* (Chen et al)", "5-3-1* (Chen et al)", "5* (Chen et al)", "5-3-1* (Chen et al)")
 result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
@@
   ylab("Sums of Squares Ratio") + 
-  xlab("npeak") +
+  xlab("npeaks.set") + 
   scale_colour_manual(values=cols_2, labels = labels) +
@@
 
-```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; removed outliers; seg\\_length = 50, Tx = 25, npeaks.set = c(5,3,1) ", fig.height=3}
+```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
@@
 p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
-                         subtitle = "npeak: 5-3-1, seg_length: 50") +
+                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
   xlab(labels[3])
 p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
-                         subtitle = "npeak: 5-3-1, seg_length: 50") +
+                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
   xlab(labels[4])
@@
 
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1) ", fig.height=3}
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
@@
 p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
-                         subtitle = "npeak: 5-3-1, seg_length: 61") +
+                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
   xlab(labels[3])
 p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
-                         subtitle = "npeak: 5-3-1, seg_length: 61") +
+                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
   xlab(labels[4])
@@
 
-```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Some caption", fig.height=3, warning = FALSE}
+```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of results from the CMPS algorithm based on different number of peaks identified at each segment level (parameter \\texttt{npeaks.set}).
+", fig.height=3, warning = FALSE}
 p.npeak_plot
@@
 
-<!-- \autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while holding other parameters fixed.
-In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
-We can see that this results in an increased separation between KM comparisons and KNM comparisons.
-This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
--->
-
-<!-- this is figure 4 -->
-
-```{r result2_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 ", fig.height=3}
-# [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
-# knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
-# CMPS_hamby44_results$plot[[2]]
-```
-
-<!-- For the third result of Hamby 44, we changed a parameter used in the data-processing procedure.
-`span1=0.25` is used for the previous results.
-Here, we change the span of 0.75, which captures a more global pattern in the bullet signatures.
--->
-
-<!-- <!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
--->
-
-<!-- As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results.  -->
-
-<!-- \autoref{tab:table1} presents some summary statistics of the Hamby 44 results above.
-These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-As shown in \autoref{tab:table1}, some parameter settings are better than others in terms of the separation between the two distributions.
-However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.
--->
-
-<!-- this is figure 5 -->
-
-```{r result3_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75", fig.height=3}
-# [4] "span1=0.75, span2=0.03, rm_outliers"  
-# knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
-# CMPS_hamby44_results$plot[[3]]
-```
-
-```{r table1, echo=FALSE, warning=FALSE}
-# rtt <- readRDS("summary_table.rds")
-# colnames(rtt) <- 
-rtt <- data.frame(parameters = c("span1=0.25, (5, 3, 1)", "span1=0.25, (10, 6, 1)", "span1=0.75, (5, 3, 1)"),
-                  p1 = c(7,9,6),
-                  p2 = c(10, 13, 11),
-                  p3 = c(3.6, 4.833, 3.167),
-                  p4 = c(6.667, 9.167, 6.6))
-colnames(rtt) <- c("Parameters",
-                   "$\\mathrm{CMPS_{max}}$ KNM's max",
-                   "$\\mathrm{CMPS_{max}}$ KM's min",
-                   "$\\mathrm{\\overline{CMPS}_{max}}$ KNM's max",
-                   "$\\mathrm{\\overline{CMPS}_{max}}$ KM's min")
-
-# knitr::kable(rtt, "latex", booktabs = TRUE, escape = FALSE,
-#              caption = "min and max of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ showing the separation between KNM and KM",
-#              row.names = FALSE, digits = 4) %>% 
-#   column_spec(2:5, width = "2cm")
-```
-
 The codes generating those results can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd

--- 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 
-<!-- \autoref{fig:result2_44} shows another Hamby set 44 results, but we changed the value of `npeaks.set` while holding other parameters fixed.
-In this result, `npeaks.set` is `c(10,6,1)` instead of `c(5,3,1)`.
-We can see that this results in an increased separation between KM comparisons and KNM comparisons.
-This shows that the parameters used in the CMPS algorithm could potentially affect the CMPS results, and an open-source implementation of the algorithm will facilitate efforts of cross-validating these parameters.
--->
-
-<!-- this is figure 4 -->
-
-```{r result2_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(10,6,1), span1=0.25 ", fig.height=3}
-# [5] "span1=0.25, span2=0.03, rm_outliers, c(10,6,1)"
-# knitr::include_graphics("img/hamby44_c1_v1.png", dpi = 100)
-# CMPS_hamby44_results$plot[[2]]
-```
-
-<!-- For the third result of Hamby 44, we changed a parameter used in the data-processing procedure.
-`span1=0.25` is used for the previous results.
-Here, we change the span of 0.75, which captures a more global pattern in the bullet signatures.
--->
-
-<!-- <!-- For the results above we used `span1=0.25` in the function `cc_get_signature` when computing the  = ; however, in this example we used `span1=0.75` and changed the characteristic of those  = .
--->
-
-<!-- As we can see in \autoref{fig:result3_44}, changing some characteristics of bullet signatures will also change the final CMPS results.  -->
-
-<!-- \autoref{tab:table1} presents some summary statistics of the Hamby 44 results above.
-These summary statistics are used to show the separation between the KM and KNM groups in the distribution of both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-As shown in \autoref{tab:table1}, some parameter settings are better than others in terms of the separation between the two distributions.
-However, we are not suggesting any set of parameters to users since further research is needed to provide a comprehensive cross-validation on these parameters, which can be facilitated by an open-source implementation of the CMPS algorithm.
--->
-
-<!-- this is figure 5 -->
-
-```{r result3_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; removed outliers; seg\\_length = 61, Tx = 30, npeaks.set = c(5,3,1), span1=0.75", fig.height=3}
-# [4] "span1=0.75, span2=0.03, rm_outliers"  
-# knitr::include_graphics("img/hamby44_c2_v1.png", dpi = 100)
-# CMPS_hamby44_results$plot[[3]]
-```
-
-```{r table1, echo=FALSE, warning=FALSE}
-# rtt <- readRDS("summary_table.rds")
-# colnames(rtt) <- 
-rtt <- data.frame(parameters = c("span1=0.25, (5, 3, 1)", "span1=0.25, (10, 6, 1)", "span1=0.75, (5, 3, 1)"),
-                  p1 = c(7,9,6),
-                  p2 = c(10, 13, 11),
-                  p3 = c(3.6, 4.833, 3.167),
-                  p4 = c(6.667, 9.167, 6.6))
-colnames(rtt) <- c("Parameters",
-                   "$\\mathrm{CMPS_{max}}$ KNM's max",
-                   "$\\mathrm{CMPS_{max}}$ KM's min",
-                   "$\\mathrm{\\overline{CMPS}_{max}}$ KNM's max",
-                   "$\\mathrm{\\overline{CMPS}_{max}}$ KM's min")
-
-# knitr::kable(rtt, "latex", booktabs = TRUE, escape = FALSE,
-#              caption = "min and max of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ showing the separation between KNM and KM",
-#              row.names = FALSE, digits = 4) %>% 
-#   column_spec(2:5, width = "2cm")
-```
-
 The code generating all results of this manuscript can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}

### 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
added caption and cleaned the comments

@@
 ```
-```{=tex}
-\hh{Still to add: the CMPS diff measure, in which you subtract the background. 
-A comparison to results from bulletxtrctr's random forest.}
-\hh{The random forest is spitting out results on a [0-1] interval - so we might need to compare to the adjusted measure.
-That comarison should go into a separate section just before the discussion.
-Like - comparison to other existing methods ...
-special request from Alicia :)}
-```
+
 ```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
@@
 or maybe gun violence?
-XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide --> An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
+XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
+An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
 Here, in particular, we are interested to determine whether two bullets were fired from the same gun barrel.
@@
 
-### Hamby Data Set
+**Hamby Data Set**
+<!-- ### Hamby Data Set -->
 
@@
 
-### Extracting signatures from LEA scans
+**Extracting signatures from LEA scans**
+<!-- ### Extracting signatures from LEA scans -->
 
@@
 
-### Conceptual idea of CMPS
+**Conceptual idea of CMPS**
+<!-- ### Conceptual idea of CMPS -->
 
@@
 Further research is needed to understand how to determine the threshold.
-<!-- \hh{XXX What threshold did @cmps identify as the boundary between different source and same source?
-And what was the error rate in their example?} --> <!-- \wj{they didn't talk about a specific threshold or error rates} \hh{XXX Is there a way to infer the error based on the example?
-...
-'while the authors did not mention a specific threshold of the CMPS to distinguish between same-source and different-source comparison, a CMPS value of Y results in an error rate of Z in the example.'} --> The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
+The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
 Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
@@
 
-**Algorithm.**
+**Algorithm**
 
@@
 
-<!-- In the CMPS package, these three steps are implemented using a set of key functions: -->
-
 Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
@@
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
-<!--Additionally, as shown in @cmps, using multi-segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.--> The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
+The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
 Here we present it with its default parameters.
@@
 In the remainder of the paper we showcase the use of the CMPS functionality on some examples and present the results of applying it to two datasets.
-<!-- \hh{XXX you need a bit of an overview here on the structure of what is coming next: in the remainder of the paper we showcase the use of the CMPS functionality on some examples ...} -->
 
@@
 The CMPS package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
-
-<!-- ```{r, eval=FALSE} -->
-
-<!-- install.packages("CMPS") -->
-
-<!-- ``` -->
-
-<!-- The development version is available from Github can be installed by using  -->
 
@@
 
-<!-- \wj{XXX as mentioned before, }multi-segment lengths strategy provides a more conservative ways of finding candidate positions, so the `CMPS.score` of `cmps_with_multi_scale` is 9, while that of `cmps_without_multi_scale` is 12.
-\wj{XXX how should we address the advantage of multi-segment lengths strategy} \hh{XXX any score based method is walking the line between false positives and false negatives.
-As the number of false positives is reduced (by being more conservatives) the number of false negatives might rise.
-The multi scale method might also be slower because the algorithm is run a couple of times.} -->
-
-<!-- \hh{XXX this is just a single example - a claim of 'more conservative' is quite big. At this point, it is only a claim. How would you go about finding evidence for it? } -->
-
 ```{r alternative, echo = FALSE}
@@
 On this plot the reference signature is drawn as a black line, congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.
-
-<!-- basis segments that agree with the congruent registration position (i.e.
-the segments that are congruent matching profile segments) are plotted along with the comparison signature.
-When plotting, each of those basis segments will be shifted to the position where the basis segment obtains a cross-correlation peak and is within the tolerance zone of the congruent registration position.
--->
 
@@
 ```
-
-<!-- These elements are essentially used for generating visuals above but also provide insights about the congruent registration position and the candidate positions found by each of the congruent matching profile segments.
--->
-
-<!-- which basis segments are the congruent matching profile segments. -->
 
@@
 ```
-<!-- \begin{align} -->
-
-<!-- \mathrm{CMPS_{max}} &= \max_{i,j} c_{ij}, \text{and }\\ -->
-
-<!-- \mathrm{\overline{CMPS}_{max}} &= \max_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]. -->
-
-<!-- \end{align} -->
-
-<!-- \hh{XXX point out that neither of these measures evaluates the non-matches, and introduce CMPS diff here} -->
 
@@
 
-\wj{Instead of computing the mean CMPS scores of matching and non-matching comparisons, a variation of $\mathrm{\overline{CMPS}_{diff}}$ is to compute the median CMPS scores of matching and non-matching comparisons.
+<!-- ??? We shouldn't talk about the median version, should we? -->
+
+<!-- \wj{Instead of computing the mean CMPS scores of matching and non-matching comparisons, a variation of $\mathrm{\overline{CMPS}_{diff}}$ is to compute the median CMPS scores of matching and non-matching comparisons.
 Computing the median could be beneficial if extreme values are observed for non-matching comparisons.
-More examples are provided in the Results section}
+More examples are provided in the Results section} -->
 
@@
 The scaled CMPS scores of the above example are shown in \autoref{fig:tiles2}(b).
-Compared to the original CMPS scores, scaled scores have values within the interval $(0, 1)$ regardless of the length of the basis segments and therefore make a comparison of values possible across different parameter choices.
+Compared to the original CMPS scores, scaled scores have values within the interval $[0, 1]$ regardless of the length of the basis segments and therefore make a comparison of values possible across different parameter choices.
 Similarly to the original CMPS scores, we will denote the scaled CMPS scores adjusted for out-of-phase background values by $\mathrm{\overline{CMPS^*}_{diff}}$.
@@
 
+rf.tt$cmps.diff_scaled <- rf.tt$cmps.diff
+
 rf.tt$study <- c("Hamby 252", "Hamby 44")
 rf.tt <- rf.tt %>% pivot_longer(
-  cols = c("cmps.diff", "cmps.max", "cmps.maxbar"),
+  cols = c("cmps.diff", "cmps.max", "cmps.maxbar", "cmps.diff_scaled"),
   names_to = "Metric"
@@
 The sum of squares ratios are 20.64 and 28.96 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-\hh{This indicates, that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.}
+This indicates, that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.
 
@@
 
-cols_1 <- c("#C583AE","#FFDFAA", "#748BA7", "#D9F0A0")
-cols_2 <- c("#A45287","#D4AC6A", "#4C688B", "#ABC864")
+cols_1 <- c("#748BA7", "#C583AE","#FFDFAA", "#D9F0A0")
+cols_2 <- c("#4C688B", "#A45287","#D4AC6A", "#ABC864")
 # #####  Color Palette by Paletton.com
@@
 
-labels <- expression(bar(CMPS)[diff], {bar(CMPS)^symbol("*")}[diff], CMPS[max], bar(CMPS)[max])
+labels <- expression( CMPS[max], bar(CMPS)[diff], {bar(CMPS)^symbol("*")}[diff], bar(CMPS)[max])
 
@@
 
+table.cmps_neapk.long <- table.cmps_neapk.long %>% mutate(
+  rf_status = if_else(npeak == "RF score* (Hare et al)",
+                      TRUE, FALSE)
+)
+
+table.cmps_neapk.long$Metric <- 
+  table.cmps_neapk.long$Metric %>% 
+  factor(levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
+
 p.npeak_plot <- table.cmps_neapk.long %>%
@@
                position=position_dodge(width = 0.6)) +
-  geom_point(aes(y =  value, color = Metric), 
+  geom_point(aes(y =  value, color = Metric, shape = rf_status), 
              alpha = 0.8,
@@
   facet_grid(.~study) +
+  ylab("Sums of Squares Ratio") + 
+  xlab("Number of Peaks") +
+  coord_flip() +
   scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak ) +
-  coord_flip() +
   theme_bw() +
   theme(legend.position = "bottom") +
-  ylab("Sums of Squares Ratio") + 
-  xlab("Number of Peaks") +
+  guides(shape = FALSE) + 
+  scale_shape_manual(values = c(16, 1)) +
   scale_colour_manual(values=cols_2, labels = labels) +
@@
 ```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
-# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
-# knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
-# CMPS_hamby252_results$plot[[2]]
-
 p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
@@
 Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones.
-For Hamby 252 these metrics agree that a segment length of 75 and a segment length of 122 for Hamby 44 yield better results", fig.height=3, warning = FALSE}
+For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results", fig.height=3, warning = FALSE}
 p.seg_plot 
@@
 ```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of CMPS results based on different strategies of number of peak selections.
-\\hh{5-3-1 should be next to 5-3-1*}.
 Starred results compare CMPS performance with results published in the literature.
-", fig.height=3, warning = FALSE}
+Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but the random forest scores with the same logic.
+Since random forest scores lie within the interval $[0, 1]$, scaling the random forest scores will not change the results.", fig.height=3, warning = FALSE}
 p.npeak_plot
@@
 The sum of squares ratios we obtained for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` is slightly higher than those obtained from the histograms of @cmps. 
-\wj{One interesting observation is that cmps.max works pretty well for 531 in nist's paper... do we need to include this?XXX} \hh{no need}
+It's curious to see that for the Hamby 252 results published in @cmps the $\mathrm{{CMPS}_{max}}$ metric achieves values of the sum of squares ratio higher than those achieved by the $\mathrm{\overline{CMPS}_{max}}$ metric.
+
 Since the researchers of @cmps did not use $\mathrm{\overline{CMPS}_{diff}}$ or $\mathrm{\overline{CMPS^*}_{diff}}$, and they did not apply the CMPS algorithm to the Hamby set 44, we were not able to compare those results.
@@
 In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
-<!--A random forest model can be used for both classification and regression. 
-It is an ensemble learning method that takes advantage of multiple predictive features.-->
 The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package `bulletxtrctr` [@bulletxtrctr].
@@
 
-\hh{XXX Which 'It' are you referring to?}
-It would also facilitate future studies on parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can potentially be used to estimate error rates or define an identification criterion.
+Open-source implementations not only allow a peer-review but also facilitate further research, such as parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can then be used for error-rate estimations and fair applications that were called for by the PCAST [@pcast] report.
 

### 2021-09-16 code/func_collection.R

@@ -62,7 +62,6 @@ get_all_phases <- function(land1, land2, score, addNA = FALSE)
   return(scores.list)
 }
 
-
 ## the function re-written from compute_average_scores
 compute_avgscore_denoise <- function (land1, land2, score, FUNC = mean, addNA = FALSE, na.rm = TRUE) 
 {

### 2021-09-21 CMPSpaper_writing/CMPSpaper_writing.Rmd
get rid of warning

@@
   theme(legend.position = "bottom") +
-  guides(shape = FALSE) + 
+  guides(shape = "none") + 
   scale_shape_manual(values = c(16, 1)) +
@@
 
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE}
 p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",

### 2021-09-23 CMPSpaper_writing/CMPSpaper_writing.Rmd
fixed an error in the plot

--- 2021-09-16 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
   theme_bw() +
-  theme(legend.position="none") +
+  # theme(legend.position="none") +
   ggtitle("Results for Hamby 252") +
@@
 p.seg_plot <- table.cmps_seg.long %>%
-  ggplot(aes(x = seg_length+3*as.numeric(factor(Metric))-9)) +
-  geom_segment(aes(xend = seg_length+3*as.numeric(factor(Metric))-9, 
+  mutate(
+    Metric = factor(Metric,
+                    levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
+  ) %>% 
+  ggplot(aes(x = seg_length+3*as.numeric((Metric))-9)) +
+  geom_segment(aes(xend = seg_length+3*as.numeric((Metric))-9, 
                    y = value, yend= 0, color=Metric),

### 2021-09-23 CMPSpaper_writing/CMPSpaper_writing.Rmd
updated the package name, added new contents for the Introduction and Conclusion

@@
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-Our implementation is made available as part of the `R` package `CMPS` on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
+Our implementation is made available as part of the `R` package `cmpsR` on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
 
@@
 Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
-In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, and present results of applying our implementation to real data.
+In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, \wj{propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison, } and present results of applying our implementation to real data.
 
@@
 
-library(CMPS)
+library(cmpsR)
 data(bullets)
@@
 A further example that illustrates the main points are also included.
-The section "Results" presents the results of evaluating the CMPS package using Hamby set 252 and Hamby set 44.
+The section "Results" presents the results of evaluating the `cmpsR` package using Hamby set 252 and Hamby set 44.
 And the last section covers some final discussion and conclusions.
@@
     The total number of CMPS is the CMPS score of the comparison.
-    `get_CMPS(input.ccp, Tx = 25)` is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (cmps).
+    `get_CMPS(input.ccp, Tx = 25)` is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
 
@@
 
-The CMPS package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
+The `cmpsR` package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
 
@@
 
-The `CMPS` package contains a simple example to illustrate the basic usage of the package.
+The `cmpsR` package contains a simple example to illustrate the basic usage of the package.
 The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [@hamby].
@@
 ```{r, eval=TRUE}
-library(CMPS)
+library(cmpsR)
 data(bullets)
@@
 
-In this paper we present the CMPS package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
+In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
 The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
-We introduce the basic logic of the CMPS algorithm and lay out its implementation in the CMPS package.
-We also showcase the functionality of the CMPS package with a small dataset example that is included in the package.
-In the CMPS package we  implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
-
-Additionally, we apply the CMPS package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).
-The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known-match (KM) comparisons and known-nonmatch (KNM) comparisons in another bullet study.
-However, the results of Hamby set 44 suggest that the CMPS method is sensitive to the choice of parameters in the algorithm, such as the length of basis segments and the number of peaks detected at each segment level.
-This indicates that further research is needed to provide a comprehensive cross-validation on parameters used the algorithm.
-
-The CMPS package provides an open-source implementation and introduces the CMPS algorithm to the `R` community.
+We introduce the basic logic of the CMPS algorithm and lay out its implementation in the `cmpsR` package.
+We also showcase the functionality of the `cmpsR` package with a small dataset example that is included in the package.
+In the `cmpsR` package we implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
+
+\wj{Additionally, we propose new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
+We also introduce a principled evaluation framework of algorithmic results based on a measure called the sum of squares ratio. 
+We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
+}
+<!-- Additionally, we apply the `cmpsR` package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).  -->
+The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
+\wj{However, the comparisons among different sets of parameters suggest that the optimal choice of the parameters varies for different datasets. 
+And further research can follow the proposed evaluation framework to have a comprehensive cross-validation on parameters used the algorithm.
+Furthermore, we compared our implemented CMPS algorithm with the random forest model proposed by @aoas and suggest adding the CMPS score as an additional feature in the random forest model.}
+
+The `cmpsR` package provides an open-source implementation and introduces the CMPS algorithm to the `R` community.
 

### 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
added the cover letter

@@
 
+## Cover Letter
+
+Dear Professor Di Cook,
+
+In our submission An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets to the R Journal, we introduce the R package cmpsR, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm first described by Chen et al (2019).
+The CMPS algorithm is used for objective comparison of striated tool marks, and in our case, we apply the cmpsR implementation to bullet signatures extracted from 3D scans of bullet land engravings.
+The usage of the cmpsR implementation is discussed in our paper, but it is not our main focus: instead, we focus on the challenges of reproducing, evaluating, and making comparisons of the algorithmic results.
+
+We are highlighting the need for a principled evaluation framework in order to compare algorithmic results generated from various parameter settings and different models.
+Our discussion of this framework demonstrates the importance of an open-source implementation in effectively conducting further research.
+
+In this paper, we proposed new metrics based on CMPS scores to assure that the results of the CMPS algorithm are comparable to other existing methods; we developed a new method to quantify the effects of an algorithm on the bullet data, suggesting a principled evaluation framework; we make the cmpsR package open-source and all code and intermediate data used in the paper available to the public, acknowledging the components needed for computational reproducibility.
+As a result, we think the paper extends well beyond the cmpsR package vignette, providing useful methodologies to anyone interested in assessments and comparisons of algorithmic results.
+
+Thank you for your consideration,
+
+Wangqian Ju and Heike Hofmann
+
 <!-- ### About this format and the R Journal requirements -->

### 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
small changes to the intro, not sue why the color doesn't show up

@@
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-Our implementation is made available as part of the `R` package `cmpsR` on GitHub at \url{https://github.com/willju-wangqian/CMPS}.
+Our implementation is made available as part of the `R` package `cmpsR` on GitHub at \url{https://github.com/willju-wangqian/cmpsR}.
 
 According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "More than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms" [@fbiucr], and firearm examination could play an important role in all these cases.
+\hh{XXX the new data for 2020 came out on Sep 27 - homicides are up by close to 30%.
+We might want to mention that.}
 <!-- Firearm examination has  played an important role in  convictions [@fbiucr] in the United States criminal justice system.
@@
 Assessing the similarity between two bullets is based on a comparison of striation marks acquired during the firing process as bullets are propelled through the barrel.
-Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope.
+Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
 This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].
@@
 Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
-In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, \wj{propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison, } and present results of applying our implementation to real data.
+In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison,  and present results of applying our implementation to real data.
 
@@
 The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], in particular, Hamby set 252 and Hamby set 44.
-For each Hamby set, a total of 35 bullets is fired from ten consecutively manufactured Ruger P-85 pistol barrels.
+For each Hamby set, a total of 35 bullets is fired from (the same) ten consecutively manufactured Ruger P-85 pistol barrels.
 Two bullets are fired from each barrel, making up a set of 20 reference bullets.
@@
 To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], `bulletinspectR` to identify and correct those errors.
-An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible} Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
+An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
+Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
 
@@
 From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
-Note that researchers in @cmps refers the origin of basis segments as the reference, but in this paper we refer it as the comparison.
+Note that researchers in @cmps refers to the origin of basis segments as the reference, but in this paper we refer to it as the comparison.
 High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
 Low scores between pairs of signatures are attributed to different source pairs.
-However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not mentioned in @cmps and depends on the underlying structure of the data and the choice of parameters.
-Further research is needed to understand how to determine the threshold.
+However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not provided in @cmps, instead the threshold depends on the underlying structure of the data and the choice of parameters.
+\hh{XXX  In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on a wished-for outcome.
+}
+Further research is needed to understand how to determine optimal threshold settings.
 The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
 Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package CMPS available from Github \url{https://github.com/willju-wangqian/CMPS} With our implementation, one can compute the CMPS score of a comparison using the following code:
+Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package cmpsR available from Github \url{https://github.com/willju-wangqian/cmpsR}.
+This publicly available implementation calculates the CMPS score of a comparison using the following code:
 
@@
 
-The section "Implementation" will go through the algorithm and show how to use the "CMPS" package.
+The section "Implementation" will go through the algorithm and show how to use the \pkg{cmpsR} package. 
 A further example that illustrates the main points are also included.
 The section "Results" presents the results of evaluating the `cmpsR` package using Hamby set 252 and Hamby set 44.
-And the last section covers some final discussion and conclusions.
+The results from Hamby set 252 are used to verify that our implementation is, at least qualitatively, comparable to the algorithm described in @nist.
+Results from Hamby 44 show the need for a further investigation of the parameter choices even in the case of bullets fired from the same barrels.
+\hh{We suggest a sum of square ratio ...}
+The last section covers some final discussion and conclusions.
 

### 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
cover letter reads well

@@
 
+\hh{XXX Will, the conclusion needs to be a bit more than just a summary of what we did in the paper - think of it as a summary plus either the limitations of our approach, or next steps that should be done but goes beyond this paper.}
+
 In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
@@
 We are highlighting the need for a principled evaluation framework in order to compare algorithmic results generated from various parameter settings and different models.
-Our discussion of this framework demonstrates the importance of an open-source implementation in effectively conducting further research.
+Our discussion of this framework demonstrates the importance of an open-source implementation to effectively conduct further research.
 
 In this paper, we proposed new metrics based on CMPS scores to assure that the results of the CMPS algorithm are comparable to other existing methods; we developed a new method to quantify the effects of an algorithm on the bullet data, suggesting a principled evaluation framework; we make the cmpsR package open-source and all code and intermediate data used in the paper available to the public, acknowledging the components needed for computational reproducibility.
-As a result, we think the paper extends well beyond the cmpsR package vignette, providing useful methodologies to anyone interested in assessments and comparisons of algorithmic results.
+As a result, we think the paper extends well beyond the cmpsR package vignette, providing useful methodology to anyone interested in assessments and comparisons of algorithmic results.
 

### 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
small edit

@@
 
-In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
+In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets from the Hamby study [@hamby] to show its potential for further research.
 The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.

### 2021-10-07 CMPSpaper_writing/CMPSpaper_writing.Rmd

--- 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 abstract: >
-  In this paper, we introduce the R package CMPS, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
+  In this paper, we introduce the R package cmpsR, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
 The functionality of the package is showcased by examples of bullet signatures that come with the package.
@@
 #  cache=TRUE,
-  dpi = 100
+  dpi = 100,
+  warning = FALSE
 )
@@
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-Our implementation is made available as part of the `R` package `cmpsR` on GitHub at \url{https://github.com/willju-wangqian/cmpsR}.
+Our implementation is made available as part of the `R` package \pkg{cmpsR} on GitHub at \url{https://github.com/willju-wangqian/cmpsR}.
 
@@
 Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package cmpsR available from Github \url{https://github.com/willju-wangqian/cmpsR}.
+Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from Github \url{https://github.com/willju-wangqian/cmpsR}.
 This publicly available implementation calculates the CMPS score of a comparison using the following code:
@@
 The section "Implementation" will go through the algorithm and show how to use the \pkg{cmpsR} package. 
-A further example that illustrates the main points are also included.
-The section "Results" presents the results of evaluating the `cmpsR` package using Hamby set 252 and Hamby set 44.
-The results from Hamby set 252 are used to verify that our implementation is, at least qualitatively, comparable to the algorithm described in @nist.
+A further example that illustrates the main points is also included.
+The section "Results" presents the results of evaluating the \pkg{cmpsR} package using Hamby set 252 and Hamby set 44.
+The results from Hamby set 252 are used to verify that our implementation is, at least qualitatively, comparable to the algorithm described in @cmps.
 Results from Hamby 44 show the need for a further investigation of the parameter choices even in the case of bullets fired from the same barrels.
-\hh{We suggest a sum of square ratio ...}
+\wj{We suggest new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.}
+<!-- \hh{We suggest a sum of square ratio ...} -->
 The last section covers some final discussion and conclusions.
@@
 
-In the remainder of the paper we showcase the use of the CMPS functionality on some examples and present the results of applying it to two datasets.
+In the remainder of the paper we showcase the use of the \pkg{cmpsR} functionality on some examples and present the results of applying it to two datasets.
 
@@
 
-The `cmpsR` package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
+The \pkg{cmpsR} package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
 
@@
 # install.packages("remotes") 
-remotes::install_github("willju-wangqian/CMPS")
+remotes::install_github("willju-wangqian/cmpsR")
 ```
@@
 
-The `cmpsR` package contains a simple example to illustrate the basic usage of the package.
+The \pkg{cmpsR} package contains a simple example to illustrate the basic usage of the package.
 The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [@hamby].
@@
 We investigated the effects of different sets of parameters at the example of both Hamby sets 252 and 44.
-More specifically, we investigated the separation achieved using the CMPS implementation under various segment lengths (controlled by the parameter   `seg_length`).
+More specifically, we investigated the separation achieved using the \pkg{cmpsR} implementation under various segment lengths (controlled by the parameter `seg_length`).
 Specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length`.
@@
 
-\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using different stategies for identifying peaks in the correlation structure between signatures.
+\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using different strategies for identifying peaks in the correlation structure between signatures.
 Basis segment length is fixed to the default level for this evaluation.
@@
 
-In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
+In this paper we present the \pkg{cmpsR} package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
 The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
-We introduce the basic logic of the CMPS algorithm and lay out its implementation in the `cmpsR` package.
-We also showcase the functionality of the `cmpsR` package with a small dataset example that is included in the package.
-In the `cmpsR` package we implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
+We introduce the basic logic of the CMPS algorithm and lay out its implementation in the \pkg{cmpsR} package.
+We also showcase the functionality of the \pkg{cmpsR} package with a small dataset example that is included in the package.
+In the \pkg{cmpsR} package we implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
 
@@
 }
-<!-- Additionally, we apply the `cmpsR` package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).  -->
+<!-- Additionally, we apply the \pkg{cmpsR} package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).  -->
 The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
@@
 
-The `cmpsR` package provides an open-source implementation and introduces the CMPS algorithm to the `R` community.
-
+\wj{The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards the world of open science, which is important to fields like the forensic science where transparency and accuracy are critical to fair justice.
 Open-source implementations not only allow a peer-review but also facilitate further research, such as parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can then be used for error-rate estimations and fair applications that were called for by the PCAST [@pcast] report.
+However, having open-source implementations is not enough for open science. 
+In order to actually build the world of open science, many other efforts, such as open evaluation, open access publication, open educational resources, etc., are still needed. 
+The database built and maintained by the National Institute of Standards and Technology is a good example of open data. 
+And what we are aiming for is an open system that is able to collect open results, compare multiple algorithms using multiple datasets, and evaluate algorithmic variation and accuracy. 
+The evaluation metric we proposed in this paper can be used to compare different algorithms or even different datasets and is a snippet of this open system. 
+But the core of this open system is the open science culture and contributions of the community.}
 

### 2021-10-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
tiny edits

@@
 \wj{Additionally, we propose new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
-We also introduce a principled evaluation framework of algorithmic results based on a measure called the sum of squares ratio. 
+We also introduce a principled evaluation framework of algorithmic results using  a measure based on the sum of squares ratio. 
 We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
@@
 The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
-\wj{However, the comparisons among different sets of parameters suggest that the optimal choice of the parameters varies for different datasets. 
-And further research can follow the proposed evaluation framework to have a comprehensive cross-validation on parameters used the algorithm.
-Furthermore, we compared our implemented CMPS algorithm with the random forest model proposed by @aoas and suggest adding the CMPS score as an additional feature in the random forest model.}
-
-\wj{The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards the world of open science, which is important to fields like the forensic science where transparency and accuracy are critical to fair justice.
+\wj{However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.
+We propose an evaluation framework that allows a comprehensive cross-validation of parameter settings used in the algorithm for future research.
+Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.}
+
+\wj{The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards in the framework of open science.
+Open science is particularly important to fields like forensic science where transparency and accuracy are critical to fair justice.
 Open-source implementations not only allow a peer-review but also facilitate further research, such as parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can then be used for error-rate estimations and fair applications that were called for by the PCAST [@pcast] report.
@@
 The database built and maintained by the National Institute of Standards and Technology is a good example of open data. 
-And what we are aiming for is an open system that is able to collect open results, compare multiple algorithms using multiple datasets, and evaluate algorithmic variation and accuracy. 
+What we are aiming for is an open system that is able to collect open results, compare multiple algorithms using multiple datasets, and evaluate algorithmic variation and accuracy. 
 The evaluation metric we proposed in this paper can be used to compare different algorithms or even different datasets and is a snippet of this open system. 

### 2021-10-13 cover_letter.Rmd
modify file names for R journal submission

--- 2021-09-30 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 ---
-title: An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets
-header-includes:
-  - \usepackage{amsmath}
-  - \usepackage{xcolor}
-  - \usepackage{longtable}
-  - \usepackage{adjustbox}            
-  - \usepackage[font=small,skip=5pt]{caption}
-  - \usepackage{subcaption}
-  - \usepackage{afterpage}
-  - \usepackage{bbm}
-author:
-  # see ?rjournal_article for more information
-  - name: Wangqian W. Ju
-    affiliation: Department of Statistics
-    address:
-    - Center for Statistics and Applications in Forensic Evidence
-    - Iowa State University
-    - 2438 Osborn Dr
-    - Ames, IA 50011
-    url: https://github.com/willju-wangqian
-    email:  wju@iastate.edu
-    orcid: 0000-0002-9977-377X
-  - name: Heike Hofmann
-    url: https://github.com/heike
-    email: hofmann@iastate.edu
-    orcid: 0000-0002-9079-593X
-    affiliation: Department of Statistics
-    address:
-    - Center for Statistics and Applications in Forensic Evidence
-    - Iowa State University
-    - 2438 Osborn Dr
-    - Ames, IA 50011
-thanks: |
-  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
-abstract: >
-  In this paper, we introduce the R package CMPS, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
-The functionality of the package is showcased by examples of bullet signatures that come with the package.
-Graphing tools are implemented in the package as well for users to assess and understand the CMPS results.
-Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package bulletxtrctr.
-New metrics based on CMPS scores are introduced and compared with existing metrics.
-A measure called Sum of Squares Ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets.
-An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
-preamble: |
-  % Any extra LaTeX you need in the preamble
-
-bibliography: CMPSpaper-writing.bib
-output: rticles::rjournal_article
-editor_options: 
-  chunk_output_type: console
-  markdown: 
-    wrap: sentence
+title: "cover_letter"
+author: "xxx"
+date: "10/13/2021"
+output: html_document
 ---
-
-```{=tex}
-\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
-\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
-\setlength{\parindent}{0pt}
-```
-
-```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
-library(knitr)
-library(tidyverse)
-library(bulletxtrctr)
-library(kableExtra)
-library(patchwork)
-library(ggpubr)
-
-source("../code/func_collection.R")
-
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  out.width = "\\textwidth",
-  fig.align = "center",
-#  cache=TRUE,
-  dpi = 100
-)
-```
-
-```{r setup_knitr, echo=FALSE}
-## From Josh O'Brien's stackoverflow answer:
-## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
-## These two settings control text width in codefig vs. usual code blocks
-partWidth <- 35
-fullWidth <- 60
-options(width = fullWidth)
-
-##  (1) CHUNK HOOK FUNCTION
-##   First, to set R's textual output width on a per-chunk basis, we
-## need to define a hook function which temporarily resets global R's
-## option() settings, just for the current chunk
-knit_hooks$set(r.opts = local({
-    ropts <- NA
-    function(before, options, envir) {
-        if (before) {
-            ropts <<- options(options$r.opts)
-        } else {
-            options(ropts)
-        }
-    }
-}))
-
-## (2) OUTPUT HOOK FUNCTION
-
-##   Define a custom output hook function. This function processes _all_
-## evaluated chunks, but will return the same output as the usual one,
-## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
-## case, wrap the usual textual output in LaTeX code placing it in a
-## narrower adjustbox environment and setting the graphics that it
-## produced in another box beside it.
-
-defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
-
-codefigChunkHook <- function(x, options) {
-  main <-  defaultChunkHook(x, options)
-  before <-
-    "\\vspace{1em}
-\\begin{adjustbox}{valign=t}
-\\begin{minipage}{.39\\textwidth}\n"
-  after <-
-    paste("\\vspace{1em}
-\\end{minipage}
-\\begin{minipage}{.59\\textwidth}",
-    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
-                 options[["label"]], "-1.pdf}
-\\end{minipage}
-\\end{adjustbox}"),
-          sep = "\n")
-  ## Was a codefig option supplied in chunk header?
-  ## If so, wrap code block and graphical output with needed LaTeX code.
-  if (!is.null(options$codefig)) {
-    main <- gsub("```","", main)
-    main <- gsub("=latex","", main)
-    main <- paste0("{\\small ", main, "}")
-    return(sprintf("%s\n%s\n%s", before, main, after))
-  } else {
-    return(main)
-  }
-}
-
-knit_hooks[["set"]](chunk = codefigChunkHook)
-
-## (3) TEMPLATE
-##   codefig=TRUE is just one of several options needed for the
-## side-by-side code block and a figure to come out right. Rather
-## than typing out each of them in every single chunk header, we
-## define a _template_ which bundles them all together. Then we can
-## set all of those options simply by typing opts.label="codefig".
-
-opts_template[["set"]](
-codefig = list(codefig = TRUE, fig.show = "hide",
-               r.opts = list(width = partWidth),
-               tidy.opts = list(width.cutoff = partWidth)))
-```
-
-## Introduction
-
-In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
-@cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
-Although @cmps conceptually described the CMPS algorithm in their paper, the authors did not release an implementation of their method.
-Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-Our implementation is made available as part of the `R` package `cmpsR` on GitHub at \url{https://github.com/willju-wangqian/cmpsR}.
-
-According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "More than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms" [@fbiucr], and firearm examination could play an important role in all these cases.
-\hh{XXX the new data for 2020 came out on Sep 27 - homicides are up by close to 30%.
-We might want to mention that.}
-<!-- Firearm examination has  played an important role in  convictions [@fbiucr] in the United States criminal justice system.
-\hh{Do we have a number or a percentage of cases where firearm examination has played a role?
-or maybe gun violence?
-XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
-An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
-Here, in particular, we are interested to determine whether two bullets were fired from the same gun barrel.
-Assessing the similarity between two bullets is based on a comparison of striation marks acquired during the firing process as bullets are propelled through the barrel.
-Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
-This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].
-
-A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940; @cmps].
-Note that this is not an exhaustive list of these efforts.
-The notion of bullet signatures is one of the results of these efforts.
-Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
-Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
-In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison,  and present results of applying our implementation to real data.
-
-## Background
-
-**Hamby Data Set**
-<!-- ### Hamby Data Set -->
-
-The datasets we worked with come from the James Hamby Consecutively Rifled Ruger Barrel Study [@brundage; @hamby; @Hamby:2019], in particular, Hamby set 252 and Hamby set 44.
-For each Hamby set, a total of 35 bullets is fired from (the same) ten consecutively manufactured Ruger P-85 pistol barrels.
-Two bullets are fired from each barrel, making up a set of 20 reference bullets.
-An additional 15 bullets are fired from these ten barrels in a fashion unknown to the study participant.
-The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from.
-The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}.
-During the firing process, grooves and lands are engraved on a bullet.
-Firearms examiners use striation marks on land engraved areas (LEAs) for their visual comparison.
-For algorithmic purposes, 3D topographical images of land engraved areas were obtained and stored in x3p format (XML 3-D Surface Profile).
-The x3p format provides a standard way of exchanging 2D and 3D profile data.
-It conforms to the ISO5436-2 standard [<http://sourceforge.net/p/open-gps/mwiki/X3p/>] adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
-Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
-Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State.
-These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu m per pixel.
-Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].
-
-**Extracting signatures from LEA scans**
-<!-- ### Extracting signatures from LEA scans -->
-
-The automated framework used in this paper was proposed by @aoas.
-In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
-`x3ptools` is a package to read, write, and generally, process x3p files.
-The `bulletxtrctr` package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
-
-\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.
-\autoref{fig:process}(a) shows a rendering of a 3d scan of a bullet land engraved area.
-The raised portion of the surface on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs), the middle area shows a land-engraved area (LEA) with well expressed striation marks.
-The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
-
-The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
-Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
-A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
-Note, that in @cmps bullet signatures are referred to as bullet profiles.
-However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
-Bullet profiles are shown in panels (b), (c), and (d) of \autoref{fig:process}, while \autoref{fig:process}(f) shows the corresponding bullet signature.
-Identifying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
-To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], `bulletinspectR` to identify and correct those errors.
-An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
-Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
-
-```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)."}
-knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
-```
-
-```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature.
-(a) front view of a scanned land engraved area (LEA).
-The selected crosscut location is indicated by the white line.
-(b) view of the cross-section of the land engraved area at the white line in (a).
-(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves.
-(d) the crosscut data after chopping the left and right grooves.
-(e) the fitted curvature using LOESS.
-(f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
-knitr::include_graphics("img/figure1_v2.PNG", dpi = 100)
-```
-
-**Conceptual idea of CMPS**
-<!-- ### Conceptual idea of CMPS -->
-
-Most algorithms for comparing striation marks are based on the digitized signatures and produce a similarity score [@song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940].
-The congruent matching profile segments (CMPS) algorithm, developed by @cmps for "objective comparison of striated tool marks", is one such algorithm.
-The algorithm's main idea is to take a set of consecutive and non-overlapping basis segments from the comparison and for each segment find the "best" registration position on the reference (the other bullet signature) with respect to their cross-correlation values.
-From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
-Note that researchers in @cmps refers to the origin of basis segments as the reference, but in this paper we refer to it as the comparison.
-High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
-Low scores between pairs of signatures are attributed to different source pairs.
-However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not provided in @cmps, instead the threshold depends on the underlying structure of the data and the choice of parameters.
-\hh{XXX  In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on a wished-for outcome.
-}
-Further research is needed to understand how to determine optimal threshold settings.
-The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
-Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package cmpsR available from Github \url{https://github.com/willju-wangqian/cmpsR}.
-This publicly available implementation calculates the CMPS score of a comparison using the following code:
-
-```{r, eval=FALSE}
-# install.packages("devtools") 
-# devtools::install_github("willju-wangqian/CMPS")
-
-library(cmpsR)
-data(bullets)
-
-sig1 <- bullets$sigs[[2]]$sig
-sig2 <- bullets$sigs[[9]]$sig
-sig3 <- bullets$sigs[[10]]$sig
-
-cmps.result.KM <- extract_feature_cmps(sig1, sig2)
-cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
-```
-
-In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 1.
-
-We also implemented graphing tools for users to better understand these results as well as the algorithm itself.
-
-The section "Implementation" will go through the algorithm and show how to use the \pkg{cmpsR} package. 
-A further example that illustrates the main points are also included.
-The section "Results" presents the results of evaluating the `cmpsR` package using Hamby set 252 and Hamby set 44.
-The results from Hamby set 252 are used to verify that our implementation is, at least qualitatively, comparable to the algorithm described in @nist.
-Results from Hamby 44 show the need for a further investigation of the parameter choices even in the case of bullets fired from the same barrels.
-\hh{We suggest a sum of square ratio ...}
-The last section covers some final discussion and conclusions.
-
-## Implementation
-
-**Algorithm**
-
-Conceptually, the CMPS algorithm consists of three main steps:
-
-1.
-**cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command `get_segs(x, len=50)` implements this step: it takes bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
-
-2.
-**identify candidate positions:** For each basis segment a set of candidate registration positions on the comparison signature is identified based on the segment's similarity to the reference signature.
-    In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
-    In case multiple segment lengths are considered, the length of each basis segment is expanded (by default it is doubled) and these two steps are repeated.
-    Only when candidate positions coincide (or are similar enough), they are considered further.
-    \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
-
-    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
-The position indicates the lag by which a basis segment is moved with respect to its original placement.
-A position is considered "good" if it results in a peak in the cross-correlation between the basis segment and the reference.
-
-    -   **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
-The latter is also called "multi-segment lengths strategy".
-The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:
-
-        -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
-\autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
-Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
-        -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
-The number of peaks detected is equal to `npeaks`, which is an integer.
-`segments`, `seg_outlength`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature.
-If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment.
-The resulting list is called `ccr.list`.
-
-    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
-Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.
-
-        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment.
-`segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased.
-`out_length` specifies the length of the output segment.
-        -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak".
-`ccr.list` is the result of `lapply()` and `get_ccr_peaks(...)`, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
-`get_ccp(...)` returns `NULL` if there is no consistent correlation peak.
-
-3.
-**determine the congruent registration position:** A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
-    Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, indicating that most of the basis segments find their highly similar counterpart in the reference signature in terms of correlation at this registration position.
-    In case of ties the middle position is taken as the congruent registration position.
-    Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
-    The total number of CMPS is the CMPS score of the comparison.
-    `get_CMPS(input.ccp, Tx = 25)` is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
-
-Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
-In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
-However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
-Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
-The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
-Here we present it with its default parameters.
-
-```{r, eval=FALSE}
-extract_feature_cmps(
-  x,
-  y,
-  seg_length = 50,
-  Tx = 25,
-  npeaks.set = c(5, 3, 1),
-  include = NULL,
-  outlength = NULL
-)
-```
-
-The function `extract_feature_cmps` allows for the following input from users besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx`:
-
--   `x` and `y` are two signatures: `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;
-
--   `include` determines the format of the function result.
-    Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed.
-    By default `include` is set to `NULL` and only the `CMPS.score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
-    If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.
-
-    -   `nseg`: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
-    -   `congruent.pos`: the congruent registration position;
-    -   `congruent.seg.idx`: the indices of all congruent matching profile segments;
-    -   `ccp.list`: a list showing identified candidate positions of all basis segments;
-    -   `pos.df`: a data frame containing all candidate positions and their respective number of votes;
-    -   `segments`: a list containing all basis segments;
-    -   `parameters`: a list containing all input arguments of `extract_feature_cmps`;
-
--   `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
-    By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
-
-<!--For more details, please check the documentation of `extract_feature_cmps` or use `?extract_feature_cmps`.-->
-
-<!-- [examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf] -->
-
-<!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->
-
-In the remainder of the paper we showcase the use of the CMPS functionality on some examples and present the results of applying it to two datasets.
-
-**Installation**
-
-The `cmpsR` package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
-
-```{r, eval=FALSE}
-# install.packages("remotes") 
-remotes::install_github("willju-wangqian/CMPS")
-```
-
-**An Example**
-
-The `cmpsR` package contains a simple example to illustrate the basic usage of the package.
-The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [@hamby].
-The procedure for generating signatures from high-resolution 3D topographic scans of bullet lands used here follows the methodology described in @aoas (as discussed above).
-The two bullets under consideration are known to have been fired from the same gun barrel, so for the 36 pairwise land-by-land comparisons, six comparisons are from same-source pairs (known matches) while thirty are from different-source pairs (known non-matches).
-To access the example data, we use
-
-```{r, eval=TRUE}
-library(cmpsR)
-data(bullets)
-```
-
-`bullets$sigs` is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in \autoref{fig:sigs}.
-`bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan from the NIST Ballistics Toolmark Research Database [@nistdb].
-
-```{r sigs, echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row.
-Signatures in the second row are ordered to be in phase with the signatures above, i.e.
-matching signatures are displayed on top of each other."}
-signatures <- bullets %>% unnest(sigs)
-signatures <- signatures %>% mutate(
-  bulletland = factor(bulletland, levels=c(paste(rep(c(1,2), each=6), c(1:6,2:6,1), sep="-")))
-)
-signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
-  theme_bw() +
-  xlab("Length in mm") +
-  ylab("Relative height in micron")
-```
-
-The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
-This comparison consists of a pair of signatures that are known to be a match -- a KM (known match) comparison.
-We compute the CMPS score using two versions of the CMPS algorithm:
-
-```{r, eval=TRUE}
-sigs1 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
-sigs2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]
-
-# compute cmps
-
-# algorithm with multi-peak insepction at three different segment levels
-cmps_with_multi_scale <- 
-  extract_feature_cmps(sigs1$sig, sigs2$sig, 
-                       npeaks.set = c(5,3,1), include = "full_result")
-
-# algorithm with multi-peak inspection at the basis scale only
-cmps_without_multi_scale <- 
-  extract_feature_cmps(sigs1$sig, sigs2$sig, 
-                       npeaks.set = 5, include = "full_result")
-```
-
-In the first example, `npeaks.set` is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object `cmps_with_multi_scale`.
-For `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
-We use `include = "full_result"` to capture all results.
-In this example, the CMPS is 9 when using multiple segments, and 12 when using a single segment.
-As discussed in @cmps, using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
-As the number of false positives is reduced the number of false negatives might rise.
-More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
-Note, that the multi-segment lengths method is slower because the algorithm is run once for each segment length.
-
-```{r alternative, echo = FALSE}
-lands <- unique(bullets$bulletland)
-
-comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
-                          stringsAsFactors = FALSE)
-
-comparisons <- comparisons %>% 
-  left_join(bullets %>% select(bulletland, sig1=sigs),
-            by = c("land1" = "bulletland")) %>%
-  left_join(bullets %>% select(bulletland, sig2=sigs),
-            by = c("land2" = "bulletland"))
-
-comparisons <- comparisons %>% mutate(
-  cmps = purrr::map2(sig1, sig2, .f = function(x, y) {
-    extract_feature_cmps(x$sig, y$sig, include = "full")
-    })
-)
-
-comparisons <- comparisons %>% 
-  mutate(
-    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
-    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg),
-    cmps_scaled = cmps_score / cmps_nseg
-  )
-
-comparisons <- comparisons %>%
-  mutate(
-    bulletA = gsub("(\\d)-\\d", "\\1", land1),
-    landA = gsub("\\d-(\\d)", "\\1", land1),
-    bulletB = gsub("(\\d)-\\d", "\\1", land2),
-    landB = gsub("\\d-(\\d)", "\\1", land2)
-  )
-
-dframe <- comparisons %>% select(-sig1, -sig2)
-
-dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
-```
-
-**Visualize and Understand CMPS results**
-
-We also implemented graphing tools for visualizing results of the CMPS algorithm.
-The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
-\autoref{fig:sigplots} shows the plots generated by the first graphing function, `cmps_signature_plot()`, and continues with the example above.
-`cmps_signature_plot()` takes the output of `extract_feature_cmps(..., include = "full_result")` and returns a list of 5 elements.
-It creates an overall impression of how the comparison signature aligns with the reference signature at the congruent registration position.
-
--   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}.
-On this plot the reference signature is drawn as a black line, congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.
-
--   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}.
-This visual presents both the comparison signature and the reference signature.
-The comparison signature is aligned with the reference signature based on the congruent registration position.
-Congruent matching profile segments are highlighted by solid red lines.
-
-```{=tex}
-\begin{figure}[hbt]
-\begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
-```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-sig.plot <- cmps_signature_plot(
-  cmps_with_multi_scale
-)
-sig.plot$segment_shift_plot
-```
-\end{subfigure}
-\begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature.
-Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
-```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-sig.plot$signature_shift_plot
-```
-\end{subfigure}
-\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
-\end{figure}
-```
--   Other elements of this list are `seg_shift` and `sig_shift`.
-`sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
-
-```{r, echo=TRUE, eval=TRUE}
-sig.plot$seg_shift
-```
-
-While `cmps_signature_plot()` focuses on the signature level, `cmps_segment_plot()` focuses on the segment level.
-It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg.idx`, indicating which segment should be inspected.
-When checking `sig.plot$seg_shift` we notice that segment number 6 is not one of the congruent matching profile segments.
-We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
-
-For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in \autoref{fig:segplots} for the example of segment number 6:
-
--   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length).
-We used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
-Therefore the top five peaks are identified in the cross-correlation curve at level one.
-Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
-The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
--   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
-It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6.
-The five highest peaks are marked by dots on the curve.
-
-```{=tex}
-\begin{figure}
-\begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot}segment\_plot for segment 6 at level one.
-The original position of segment 6 is indicated by the solid black line.
-Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
-```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-seg.plot <- cmps_segment_plot(
-  cmps_with_multi_scale, 
-  seg.idx = 6
-)
-seg.plot[[1]]$segment_plot
-```
-\end{subfigure}
-\begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one.
-The five highest peaks are marked by dots.
-The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
-We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
-Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
-```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-seg.plot[[1]]$scale_ccf_plot
-```
-\end{subfigure}
-\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
-\end{figure}
-```
-Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
-
-```{=tex}
-\begin{figure}
-```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-library(ggpubr)
-
-ggarrange(
-  plotlist = 
-    unlist(seg.plot, 
-           recursive = FALSE),
-  ncol = 2, 
-  nrow = 3)
-```
-\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1).
-The highest peak position at level three is marked by the green dashed line across all segment levels.
-However, the highest peak on level three does not coincide with any of the top five highest peaks at level one.
-This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
-\end{figure}
-```
-In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
-We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one.
-As a result, segment 6 fails to identify the consistent correlation peak (ccp) and fails to become one of the congruent matching profile segments according to the multi-segment lengths strategy.
-The identified top five peaks at level one are also examples of "false positive" peaks.
-The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.
-
-## Evaluation Metrics
-
-**Metrics Based on CMPS scores**
-
-The CMPS algorithm measures the similarity between two signatures resulting in a similarity score of a land-to-level comparison.
-Bullets fired from traditionally rifled barrels have multiple land and groove engraved areas.
-Here, we are working with bullets fired from Ruger P85 barrels with six lands and grooves.
-A comparison of two bullets therefore involves 36 land-to-land comparisons, resulting in 36 CMPS scores (as shown in \autoref{fig:tiles}).
-In order to obtain a single similarity score of a bullet-level comparison, we need to summarize these 36 CMPS scores.
-Two similarity metrics for bullet-level comparisons have been introduced in the literature [@cmps]: $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-$\mathrm{CMPS_{max}}$ is the highest CMPS score obtained among all land-level comparisons, while $\mathrm{\overline{CMPS}_{max}}$ is the highest possible mean CMPS score of land-level comparisons that are in the same phase:
-
-In general, we assume each bullet has $n$ land engravings (in our case $n=6$).
-Let $c_{ij}$ denote the CMPS score of a comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
-Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and $\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}$, where $\mathbbm{1}_A$ denotes an indicator function.
-For example, $\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}$ when $n = 6$.
-Let $k^*$ denote the index of the highest phase.
-
-With that, the two measures to evaluate accuracy used in @cmps are defined as
-
-```{=tex}
-\begin{align}
-\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij} \text{ , and} \\
-\mathrm{\overline{CMPS}_{max}} &= \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij} \text{ , where} \\
-k^* &= \text{arg}\max\limits_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
-\end{align}
-```
-
-We can continue with the example used in previous sections.
-`bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
-As mentioned before, each bullet has 6 land engravings, resulting in 6 bullet signatures.
-Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
-We use multi-segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
-We can see that in this example,
-
-$$
-\mathrm{CMPS_{max}} =  \max_{i,j} c_{ij} = 17
-$$
-
-and since bullet lands in phase $\mathcal{P}_1$ gives the highest mean CMPS score ($k^* = 1$), we have
-
-$$
-\begin{aligned}
-\mathrm{\overline{CMPS}_{max}} &= \frac{1}{6} \sum_{(i,j) \in \mathcal{P}_1} c_{ij} \\
-                        &= \frac{1}{6} (c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}) \\
-                        &= \frac{1}{6} (3+17+14+10+15+16) \\
-                        &= 12.5
-\end{aligned}
-$$
-
-```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
-Land engraving pairs generated by the same land (KM comparisons) are highlighted", out.width=".7\\textwidth", fig.align="center"}
-dframe <- dframe %>% mutate(
-  landA = paste0("L", landA),
-  landB = paste0("L", landB),
-  landB = factor(landB, levels = paste0("L", c(2:6,1))),
-  bulletA = paste0("Bullet ", bulletA),
-  bulletB = paste0("Bullet ", bulletB)
-)
-
-dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_score)) + 
-  geom_tile() + 
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
-  scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) + 
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
-  ylab("Bullet2 Lands") + 
-  geom_text(aes(label=cmps_score)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-```
-
-However, both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ consider only relatively high CMPS scores and ignore the rest.
-So we introduce a new metric based on CMPS scores called $\mathrm{\overline{CMPS}_{diff}}$, which is the difference between $\mathrm{\overline{CMPS}_{max}}$ and the mean of all other CMPS scores.
-With our notation above, we have:
-
-```{=tex}
-\begin{align}
-\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n(n-1)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
-\end{align}
-```
-$\mathrm{\overline{CMPS}_{diff}}$ highlights the difference between CMPS scores of matching and non-matching comparisons.
-If two bullets are non-matching, all 36 CMPS scores are expected to be small with relatively the same values, resulting in a $\mathrm{\overline{CMPS}_{diff}}$ value close to 0.
-For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$ <br>
-
-<!-- ??? We shouldn't talk about the median version, should we? -->
-
-<!-- \wj{Instead of computing the mean CMPS scores of matching and non-matching comparisons, a variation of $\mathrm{\overline{CMPS}_{diff}}$ is to compute the median CMPS scores of matching and non-matching comparisons.
-Computing the median could be beneficial if extreme values are observed for non-matching comparisons.
-More examples are provided in the Results section} -->
-
-**Scaled CMPS Scores**
-
-Another issue with the CMPS score is that the highest possible CMPS score (the total number of basis segments) might differ across comparisons (as shown in \autoref{fig:tiles2}(a)) due to different lengths of bullet signatures and different lengths of basis segments specified by the parameter.
-A CMPS score of 5 might indicate a non-match if the highest possible CMPS score is 30 but indicate a match if the highest possible CMPS score is 6.
-Thus, we introduce the scaled CMPS score, denoted as $c^*_{ij}$.
-Let $s_{ij}$ denote the highest possible CMPS score or the total number of basis segments, then the scaled CMPS score $c^*_{ij}$ is defined as the ratio of raw score and maximum score:
-
-```{=tex}
-\begin{align}
-c^*_{ij} = \frac{c_{ij}}{s_{ij}}
-\end{align}
-```
-The scaled CMPS scores of the above example are shown in \autoref{fig:tiles2}(b).
-Compared to the original CMPS scores, scaled scores have values within the interval $[0, 1]$ regardless of the length of the basis segments and therefore make a comparison of values possible across different parameter choices.
-Similarly to the original CMPS scores, we will denote the scaled CMPS scores adjusted for out-of-phase background values by $\mathrm{\overline{CMPS^*}_{diff}}$.
-For example, $\mathrm{\overline{CMPS^*}_{diff}} = 0.498$ for \autoref{fig:tiles2}(b)
-
-```{r tiles2, echo=FALSE, fig.cap="Plot (a) shows the highest possible CMPS scores (the total number of basis segments) for the 36 comparisons.
-(b) shows the scaled CMPS scores for the 36 comparisons.", out.width=".7\\textwidth", fig.align="center"}
-p1 <- dframe %>% ggplot(aes(x = landA, y = landB)) + 
-  geom_tile(fill = "grey") + 
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
-  ylab("Bullet2 Lands") + 
-  geom_text(aes(label=cmps_nseg)) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-
-p2 <- dframe %>% ggplot(aes(x = landA, y = landB, fill = cmps_scaled)) + 
-  geom_tile() + 
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
-  scale_fill_gradient2("Scaled CMPS", low = "gray80", high = "darkorange", midpoint = 0.3) + 
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
-  ylab("Bullet2 Lands") + 
-  geom_text(aes(label=round(cmps_scaled, 2))) +
-  theme_bw() +
-  theme(aspect.ratio = 1)
-
-ggarrange(p1, p2, 
-          common.legend = TRUE, legend = "bottom", labels = c("(a)", "(b)"))
-```
-
-**Sum of Squares Ratio**
-
-The "sum of squares ratio" quantifies how well two groups of values separate.
-Let $n_T$ denote the total number of observations, $n_k$ denote the number of observations in group $k$, and $y_{kl}$ denote the $l$-th observation in group $k$, for $k = 1,2$ and $l = 1, \dots, n_k$.
-Let $\bar{y}_{k.} = \frac{1}{n_k} \sum_{l=1}^{n_k} y_{kl}$ denote the mean value in group $k$ and $\bar{y}_{..} = \frac{1}{n_T} \left( \sum_{k} \sum_{l = 1}^{n_k} y_{kl} \right)$ denote the mean value of all observations.
-Consider the following model:
-
-```{=tex}
-\begin{align}
-y_{kl} = \mu_k + e_{kl}
-\end{align}
-```
-where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations.
-Then we can define the sum of squares ratio $V$ as:
-
-```{=tex}
-\begin{align}
-V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }.
-\end{align}
-```
-The numerator of the sum of squares ratio $V$ quantifies the variation between the two groups, while the denominator quantifies the variation within each group.
-The sum of squares ratio $V$ can be used as an index for evaluating scans, metrics, and different sets of parameters if the same data set is being used.
-Some examples will be presented in the following section.
-If we impose the normality and independence assumptions on the random effects $e_{kl}$, the sum of squares ratio $V$ becomes a scaled F-statistic with degrees of freedom of $k-1$ and $n_T - k$ and $F = \frac{n_T - k}{k- 1} V$.
-If we want to compare different data sets, stating that a certain setup can achieve better separation on one data set than another, we can scale the sum of squares ratio $V$ and obtain the F-statistic to compare the p-values.
-
-Using the sum of squares ratio $V$ as an evaluation metric, we are able to construct a pipeline that aims to find the optimal parameter value for the CMPS algorithm by maximizing the sum of squares ratio.
-In the following section, we will use this ratio to compare the CMPS metrics introduced earlier and investigate effects of different sets of parameters.
-
-## Results
-
-```{r hamby252-data-seg, eval=TRUE, echo=FALSE}
-# for hamby 252
-N <- 8 # the number of different sets of parameters
-CMPS_hamby252_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
-  # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
-
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
-
-#### setup seg_length
-CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
-
-#### setup Tx
-CMPS_hamby252_results$Tx <- as.list(rep(25, N))
-
-#### setup outlength
-CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby252_results$titlee <- list()
-CMPS_hamby252_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby252_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby252_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby252_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby252_results$filename[[i]] <- 
-    paste(
-      "hamby252_segment",
-      CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby252_results$seg_length[[i]],
-      CMPS_hamby252_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby252_results$cmps.table <- list()
-CMPS_hamby252_results$plot <- list()
-
-#### a global title for Hamby252 plots
-com.title252 <- expression(paste(
-  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby252_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby252/", 
-                        CMPS_hamby252_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby252_results_seg <- CMPS_hamby252_results
-
-```
-
-```{r hamby252-data-npeak, eval=TRUE, echo=FALSE}
-N <- 8 # the number of different sets of parameters
-CMPS_hamby252_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
-# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
-
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- 
-  list(c(5),
-       c(5,2),
-       c(5,3,1),
-       c(10,6,2),
-       c(6,4,2,1),
-       c(10,7,4,2),
-       c(10,6,4,2,1),
-       c(10,8,6,4,2,1))
-
-#### setup seg_length
-CMPS_hamby252_results$seg_length <- 
-  # as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
-  as.list(rep(50, N))
-
-#### setup Tx
-CMPS_hamby252_results$Tx <- as.list(rep(25, N))
-
-#### setup outlength
-CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
-CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180)
-CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200)
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby252_results$titlee <- list()
-CMPS_hamby252_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby252_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby252_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby252_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby252_results$filename[[i]] <- 
-    paste(
-      "hamby252_npeak",
-      CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby252_results$seg_length[[i]],
-      CMPS_hamby252_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby252_results$cmps.table <- list()
-CMPS_hamby252_results$plot <- list()
-
-#### a global title for Hamby252 plots
-com.title252 <- expression(paste(
-  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby252_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby252/", 
-                        CMPS_hamby252_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby252_results_npeak <- CMPS_hamby252_results
-
-```
-
-```{r hamby44-data-seg, eval=TRUE, echo=FALSE}
-N <- 8 # the number of different sets of parameters
-CMPS_hamby44_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby44_results$signame <-
-  as.list(rep("sigs25_531", N))
-
-#### setup neapks.set
-CMPS_hamby44_results$npeaks.set <-
-  lapply(1:N, function(t) c(5,3,1))
-
-#### setup seg_length
-CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210))
-
-#### setup outlength
-CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
-
-#### setup Tx
-CMPS_hamby44_results$Tx <- as.list(rep(30, N))
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby44_results$titlee <- list()
-CMPS_hamby44_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby44_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby44_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby44_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby44_results$filename[[i]] <- 
-    paste(
-      "hamby44_segment",
-      CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby44_results$seg_length[[i]],
-      CMPS_hamby44_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby44_results$cmps.table <- list()
-CMPS_hamby44_results$plot <- list()
-
-#### a global title for Hamby44 plots
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby44_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby44/", 
-                        CMPS_hamby44_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby44_results_seg <- CMPS_hamby44_results
-
-```
-
-```{r hamby44-data-npeak, eval=TRUE, echo=FALSE}
-N <- 8 # the number of different sets of parameters
-CMPS_hamby44_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby44_results$signame <-
-  as.list(rep("sigs25_531", N))
-
-#### setup neapks.set
-CMPS_hamby44_results$npeaks.set <-
-  list(c(5),
-       c(5,2),
-       c(5,3,1),
-       c(10,6,2),
-       c(6,4,2,1),
-       c(10,7,4,2),
-       c(10,6,4,2,1),
-       c(10,8,6,4,2,1))
-
-#### setup seg_length
-CMPS_hamby44_results$seg_length <- as.list(rep(61, N))
-
-#### setup outlength
-CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
-CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181)
-CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211)
-
-#### setup Tx
-CMPS_hamby44_results$Tx <- as.list(rep(30, N))
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby44_results$titlee <- list()
-CMPS_hamby44_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby44_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby44_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby44_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby44_results$filename[[i]] <- 
-    paste(
-      "hamby44_npeak",
-      CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby44_results$seg_length[[i]],
-      CMPS_hamby44_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby44_results$cmps.table <- list()
-CMPS_hamby44_results$plot <- list()
-
-#### a global title for Hamby44 plots
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby44_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby44/", 
-                        CMPS_hamby44_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby44_results_npeak <- CMPS_hamby44_results
-```
-
-```{r rf-data-load, echo=FALSE}
-rf.results <- list()
-rf.results[[1]] <- read.csv(file = "./data/hamby252/hamby252_rf_results.csv")
-rf.results[[2]] <- read.csv(file = "./data/hamby44/hamby44_rf_results.csv")
-
-rf.tt <- lapply(rf.results, function(rf_result) {
-  with(rf_result, {
-    tibble(rf.diff, rf.max, rf.maxbar) %>% 
-      apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
-  })
-}) %>% do.call(rbind, .) %>% as_tibble()
-
-colnames(rf.tt) <- c("cmps.diff", "cmps.max", "cmps.maxbar")
-
-rf.tt$cmps.diff_scaled <- rf.tt$cmps.diff
-
-rf.tt$study <- c("Hamby 252", "Hamby 44")
-rf.tt <- rf.tt %>% pivot_longer(
-  cols = c("cmps.diff", "cmps.max", "cmps.maxbar", "cmps.diff_scaled"),
-  names_to = "Metric"
-)
-
-rf.tt$npeak <- "RF score* (Hare et al)"
-
-```
-
-```{r ss-original-cmps, echo=FALSE}
-result.container <- list()
-
-result.container$npeak <- 
-  c("5* (Chen et al)", "5-3-1* (Chen et al)", "5* (Chen et al)", "5-3-1* (Chen et al)")
-result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
-result.container$study <- "Hamby 252"
-
-dd.list <- list()
-
-dd.list[[1]] <- tibble(
-  score = c(9:13, 16:24),
-  freq = c(132, 282, 115, 19, 1, 1, 3,2,4,8,12,7,7,2),
-  type = c(rep("KNM", 5), rep("KM", 9))
-)
-
-dd.list[[2]] <- tibble(
-  score = c(1:5, 14:23),
-  freq = c(7,343,168,24,7,1,1,2,3,6,7,8,8,7,3),
-  type = c(rep("KNM", 5), rep("KM", 10))
-)
-
-dd.list[[3]] <- tibble(
-  score = c(6:9, 13:19),
-  freq = c(2,210,307,30,6,3,9,9,11,7,1),
-  type = c(rep("KNM", 4), rep("KM", 7))
-)
-
-dd.list[[4]] <- tibble(
-  score = c(0:2, 8:17),
-  freq = c(36, 508, 5, 1,3,4,2,11,3,9,8,4,1),
-  type = c(rep("KNM", 3), rep("KM", 10))
-)
-
-result.container$dd.list <- dd.list
-
-result.container <- result.container %>% as_tibble() %>% 
-  mutate(
-    dd.table = purrr::map(dd.list, function(dd) {
-      tibble(score = rep(dd$score, dd$freq),
-             type_truth = rep(dd$type, dd$freq))
-    }),
-    value = purrr::map_dbl(dd.table, function(dd) {
-      compute_var_ratio_anova(dd$score, dd$type_truth, MS = FALSE)
-    })
-  ) 
-```
-
-As presented in the work of @cmps, researchers applied the CMPS method to scans of one of the Hamby sets.
-While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time.
-In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix: for both Hamby 252 and Hamby 44, we started with scans in the form of x3p files in the database.
-Following the framework proposed by @aoas, we used the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
-Note that researchers of @cmps applied the CMPS algorithm to bullet signatures as well but used a framework different from ours.
-However, since their work is not open-source, we were not able to follow their framework and were only able to reproduce the results for Hamby set 252 qualitatively.
-
-**Hamby 252**
-
-\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy.
-The parameters we used in `extract_feature_cmps` for the CMPS algorithm are:
-
-```{r, eval=FALSE}
-extract_feature_cmps(
-  x, y,
-  seg_length = 50,
-  Tx = 25,
-  npeaks.set = c(5,3,1),
-  include = "nseg"
-)
-```
-
-As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in \autoref{fig:result1_252} are qualitatively equivalent to those presented in @cmps, showing a clear separation between scores based on comparisons from known matches (KM) and scores from comparisons of known non-matches (KNM) for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-
-Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu m for Hamby set 252).
-
-The sum of squares ratios are 20.64 and 28.96 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-This indicates, that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.
-
-```{r, echo=FALSE, eval=FALSE}
-with(CMPS_hamby252_results_npeak$cmps.table[[3]], {
-  tibble(cmps.max, cmps.maxbar) %>% 
-    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
-})
-
-with(CMPS_hamby252_results_seg$cmps.table[[2]], {
-  tibble(cmps.max, cmps.maxbar, cmps.diff, cmps.diff_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
-})
-
-```
-
-```{r color-settings, echo=FALSE}
-
-cols_1 <- c("#748BA7", "#C583AE","#FFDFAA", "#D9F0A0")
-cols_2 <- c("#4C688B", "#A45287","#D4AC6A", "#ABC864")
-# #####  Color Palette by Paletton.com
-# #####  Palette URL: http://paletton.com/#uid=7561m0kllllaFw0g0qFqFg0w0aF
-# 
-# 
-# *** Primary color:
-# 
-#    shade 0 = #832C65 = rgb(131, 44,101) = rgba(131, 44,101,1) = rgb0(0.514,0.173,0.396)
-#    shade 1 = #C583AE = rgb(197,131,174) = rgba(197,131,174,1) = rgb0(0.773,0.514,0.682)
-#    shade 2 = #A45287 = rgb(164, 82,135) = rgba(164, 82,135,1) = rgb0(0.643,0.322,0.529)
-#    shade 3 = #621046 = rgb( 98, 16, 70) = rgba( 98, 16, 70,1) = rgb0(0.384,0.063,0.275)
-#    shade 4 = #42002B = rgb( 66,  0, 43) = rgba( 66,  0, 43,1) = rgb0(0.259,0,0.169)
-# 
-# *** Secondary color (1):
-# 
-#    shade 0 = #AA7F39 = rgb(170,127, 57) = rgba(170,127, 57,1) = rgb0(0.667,0.498,0.224)
-#    shade 1 = #FFDFAA = rgb(255,223,170) = rgba(255,223,170,1) = rgb0(1,0.875,0.667)
-#    shade 2 = #D4AC6A = rgb(212,172,106) = rgba(212,172,106,1) = rgb0(0.831,0.675,0.416)
-#    shade 3 = #805715 = rgb(128, 87, 21) = rgba(128, 87, 21,1) = rgb0(0.502,0.341,0.082)
-#    shade 4 = #553500 = rgb( 85, 53,  0) = rgba( 85, 53,  0,1) = rgb0(0.333,0.208,0)
-# 
-# *** Secondary color (2):
-# 
-#    shade 0 = #2B4970 = rgb( 43, 73,112) = rgba( 43, 73,112,1) = rgb0(0.169,0.286,0.439)
-#    shade 1 = #748BA7 = rgb(116,139,167) = rgba(116,139,167,1) = rgb0(0.455,0.545,0.655)
-#    shade 2 = #4C688B = rgb( 76,104,139) = rgba( 76,104,139,1) = rgb0(0.298,0.408,0.545)
-#    shade 3 = #143054 = rgb( 20, 48, 84) = rgba( 20, 48, 84,1) = rgb0(0.078,0.188,0.329)
-#    shade 4 = #051B38 = rgb(  5, 27, 56) = rgba(  5, 27, 56,1) = rgb0(0.02,0.106,0.22)
-# 
-# *** Complement color:
-# 
-#    shade 0 = #81A035 = rgb(129,160, 53) = rgba(129,160, 53,1) = rgb0(0.506,0.627,0.208)
-#    shade 1 = #D9F0A0 = rgb(217,240,160) = rgba(217,240,160,1) = rgb0(0.851,0.941,0.627)
-#    shade 2 = #ABC864 = rgb(171,200,100) = rgba(171,200,100,1) = rgb0(0.671,0.784,0.392)
-#    shade 3 = #5B7814 = rgb( 91,120, 20) = rgba( 91,120, 20,1) = rgb0(0.357,0.471,0.078)
-#    shade 4 = #395000 = rgb( 57, 80,  0) = rgba( 57, 80,  0,1) = rgb0(0.224,0.314,0)
-# 
-# 
-# #####  Generated by Paletton.com (c) 2002-2014
-```
-
-```{r plot_computation, echo=FALSE, fig.width=8, fig.height = 8, out.width='\\linewidth'}
-# 252 - seg
-table.252.cmps_seg <- lapply(CMPS_hamby252_results_seg$cmps.table, function(tt) {
-  type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.252.cmps_seg$seg_length <- unlist(CMPS_hamby252_results_seg$seg_length)
-
-table.252.cmps_seg.long <- table.252.cmps_seg %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, 
-                        cmps.max, cmps.maxbar), 
-               names_to = "Metric")
-
-table.252.cmps_seg.long <- table.252.cmps_seg.long %>% 
-  mutate(study = "Hamby 252")
-
-labels <- expression( CMPS[max], bar(CMPS)[diff], {bar(CMPS)^symbol("*")}[diff], bar(CMPS)[max])
-
-p.seg_252_plot <- table.252.cmps_seg.long %>%
-  ggplot(aes(x = seg_length +3*as.numeric(factor(Metric))-9)) +
-  geom_segment(aes(xend =  seg_length +3*as.numeric(factor(Metric))-9,
-               y = value, yend = 0, colour = Metric)) + 
-  geom_point(aes(y =  value, color = Metric), 
-             alpha = 0.8,
-             position=position_dodge(width = 0.5), size = 3.5) +
-  scale_x_continuous(breaks = table.252.cmps_seg$seg_length, 
-                     minor_breaks = NULL) +
-  theme_bw() +
-  # theme(legend.position="none") +
-  ggtitle("Results for Hamby 252") +
-  ylab("Sum of Squares Ratio") + 
-  xlab("Segment Length") +
-  scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels)
-
-# 44 - seg
-table.44.cmps_seg <- lapply(CMPS_hamby44_results_seg$cmps.table, function(tt) {
-  type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.44.cmps_seg$seg_length <- unlist(CMPS_hamby44_results_seg$seg_length)
-
-table.44.cmps_seg.long <- table.44.cmps_seg %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, 
-                        cmps.max, cmps.maxbar),
-               names_to = "Metric")
-
-table.44.cmps_seg.long <- table.44.cmps_seg.long %>% mutate(
-  study = "Hamby 44"
-)
-
-table.cmps_seg.long <- bind_rows(table.44.cmps_seg.long,
-                                 table.252.cmps_seg.long)
-
-breaks_fun <- function(x) {
-  if(x[2] < 220) {
-    c(25,  50,  75, 100, 125, 150, 175, 200)
-  } else {
-    c(30, 45,  61,  90, 122, 150, 180, 210)
-  }
-}
-
-p.seg_plot <- table.cmps_seg.long %>%
-  mutate(
-    Metric = factor(Metric,
-                    levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
-  ) %>% 
-  ggplot(aes(x = seg_length+3*as.numeric((Metric))-9)) +
-  geom_segment(aes(xend = seg_length+3*as.numeric((Metric))-9, 
-                   y = value, yend= 0, color=Metric),
-               position=position_dodge(width = 0.6)) +
-  geom_point(aes(y =  value, color = Metric), 
-             alpha = 0.8,
-             position=position_dodge(width = 0.5), size = 3.5) +
-  facet_grid(.~study, scales = "free_x") +
-  scale_x_continuous(breaks = breaks_fun, 
-                     minor_breaks = NULL) +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  ylab("Sums of Squares Ratio") + 
-  xlab("Segment length") +
-  scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels)
-
-# npeak - 252
-table.252.cmps_npeak <- lapply(CMPS_hamby252_results_npeak$cmps.table, function(tt) {
-  type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks.set %>% 
-  purrr::map(.f = paste, collapse = "-") %>% sapply(as.character)
-
-table.252.cmps_npeak.longer <- table.252.cmps_npeak %>% as_tibble() %>% 
-  filter(npeak %in% c("5", "5-3-1", "10-8-6-4-2-1", "10-7-4-2")) %>% 
-  mutate(
-    npeak = factor(
-      npeak,
-      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
-  ) %>% 
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
-               names_to = "Metric") 
-table.252.cmps_npeak.longer$study <- "Hamby 252"
-
-# npeak - 44
-table.44.cmps_npeak <- lapply(CMPS_hamby44_results_npeak$cmps.table, function(tt) {
-  type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.44.cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks.set %>% 
-  purrr::map(.f = paste, collapse = "-") %>% sapply(as.character)
-
-table.44.cmps_npeak.longer <- table.44.cmps_npeak %>% as_tibble() %>% 
-  filter(npeak %in% c("5", "5-3-1", "10-8-6-4-2-1", "10-7-4-2")) %>% 
-  mutate(
-    npeak = factor(
-      npeak,
-      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
-  ) %>% 
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
-               names_to = "Metric") 
-table.44.cmps_npeak.longer$study <- "Hamby 44"
-
-selected_var <- c("npeak", "Metric", "study", "value")
-
-table.cmps_neapk.long <- bind_rows(
-  table.252.cmps_npeak.longer %>% select(all_of(selected_var)),
-  table.44.cmps_npeak.longer %>% select(all_of(selected_var)),
-  rf.tt %>% select(all_of(selected_var)),
-  result.container %>% select(all_of(selected_var))
-)
-
-order.level <- table.cmps_neapk.long %>% 
-  filter(Metric == "cmps.maxbar", study == "Hamby 252") %>%
-  {.$npeak[order(.$value, decreasing = FALSE)]}
-
-table.cmps_neapk.long <- table.cmps_neapk.long %>% mutate(
-  npeak = factor(npeak, levels = order.level)
-)
-
-npeak_convert <- with(table.cmps_neapk.long, {
-  tt <- tibble(npeak = levels(npeak))
-  tt$xstart <- seq.int(from = 0, by = 20, length.out = length(tt$npeak))
-  tt
-})
-
-table.cmps_neapk.long <- table.cmps_neapk.long %>% left_join(
-  npeak_convert,
-  by = "npeak"
-)
-
-table.cmps_neapk.long <- table.cmps_neapk.long %>% mutate(
-  rf_status = if_else(npeak == "RF score* (Hare et al)",
-                      TRUE, FALSE)
-)
-
-table.cmps_neapk.long$Metric <- 
-  table.cmps_neapk.long$Metric %>% 
-  factor(levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
-
-p.npeak_plot <- table.cmps_neapk.long %>%
-  ggplot(aes(x = xstart + 3*as.numeric(factor(Metric))-9)) +
-  geom_segment(aes(xend = xstart + 3*as.numeric(factor(Metric))-9, 
-                   y = value, yend= 0, color=Metric),
-               position=position_dodge(width = 0.6)) +
-  geom_point(aes(y =  value, color = Metric, shape = rf_status), 
-             alpha = 0.8,
-             position=position_dodge(width = 0.5), size = 3.5) +
-  facet_grid(.~study) +
-  ylab("Sums of Squares Ratio") + 
-  xlab("Number of Peaks") +
-  coord_flip() +
-  scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak ) +
-  theme_bw() +
-  theme(legend.position = "bottom") +
-  guides(shape = "none") + 
-  scale_shape_manual(values = c(16, 1)) +
-  scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels) 
-```
-
-<!-- this is figure 2 -->
-
-```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
-# [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"  
-# knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
-# CMPS_hamby252_results$plot[[2]]
-
-p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
-  xlab(labels[3])
-p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
-  xlab(labels[4])
-p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
-               common.legend = TRUE, legend = "bottom")
-p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
-p.result1_252
-```
-
-**Hamby 44**
-
-Similar procedures are applied to Hamby set 44, and \autoref{fig:result1_44} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-The parameters used in `extract_feature_cmps` are:
-
-```{r, eval=FALSE}
-extract_feature_cmps(
-  x, y,
-  seg_length = 61, 
-  Tx = 30,
-  npeaks.set = c(5,3,1),
-  include = "nseg"
-)
-```
-
-Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we make `seg_length = 61` and `Tx = 30` to ensure that the setup of Hamby set 44 is similar to that of Hamby set 252, resulting in basis segments of 78.69 \textmu m and the tolerance zone of $\pm 38.7$ \textmu m.
-
-As shown in \autoref{fig:result1_44}, again, we are able to see a clear separation between the known match comparisons and the known non-match comparisons, even though the separation is relatively small compared with that of Hamby set 252, which is also indicated by the sum of squares ratios.
-For this specific set of parameters, the sum of squares ratios are 8.87 and 10.64 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-This might suggest that we could enlarge the separation in terms of the sum of squares ratio by using other CMPS metrics and other sets of parameters.
-
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE}
-p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
-  xlab(labels[3])
-p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
-  xlab(labels[4])
-p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
-               common.legend = TRUE, legend = "bottom")
-p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
-p.result1_44
-```
-
-**Comparing CMPS metrics and Parameters**
-
-```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter \\texttt{seg\\_length}).
-Only the $\\mathrm{CMPS_{max}}$ metric suggests that the default values for the basis segment length result in the best separation.
-Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones.
-For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results", fig.height=3, warning = FALSE}
-p.seg_plot 
-```
-
-```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of CMPS results based on different strategies of number of peak selections.
-Starred results compare CMPS performance with results published in the literature.
-Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but the random forest scores with the same logic.
-Since random forest scores lie within the interval $[0, 1]$, scaling the random forest scores will not change the results.", fig.height=3, warning = FALSE}
-p.npeak_plot
-```
-
-We investigated the effects of different sets of parameters at the example of both Hamby sets 252 and 44.
-More specifically, we investigated the separation achieved using the CMPS implementation under various segment lengths (controlled by the parameter   `seg_length`).
-Specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length`.
-\autoref{fig:param_seg_plot} shows that the default values of `seg_length`  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
-However, we also see, that for Hamby set 252 a basis segment length of 75 is a better choice than the default segment length; a basis segment length of 122 results in a higher value of sum of squares ratio for Hamby 44.
-
-\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using different stategies for identifying peaks in the correlation structure between signatures.
-Basis segment length is fixed to the default level for this evaluation.
-As can be seen in \autoref{fig:param_npeak_plot}, the default value of `npeaks.set` (`npeaks.set = c(5,3,1)`) leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` match and  exceed this sum of squares ratio value.
-
-As seen before, the results suggest that the $\mathrm{CMPS_{max}}$ metric produces the least amount of separation compared with the other three CMPS metrics.
-They also suggest that the two newly proposed metrics, $\mathrm{\overline{CMPS}_{diff}}$ and $\mathrm{\overline{CMPS^*}_{diff}}$,  lead to equally good or even better results as $\mathrm{\overline{CMPS}_{max}}$.
-Because $\mathrm{\overline{CMPS^*}_{diff}}$ relies on a scaled version of CMPS scores it is more comparable to other similarity scores and summarizes the out-of-phase background CMPS scores, making it superior to the other CMPS metrics.
-
-What we can also observe in \autoref{fig:param_seg_plot} and \autoref{fig:param_npeak_plot} is that the values of the sum of squares ratio for Hamby 44 is lower than those for Hamby 252. 
-This might be because determining the source is a harder task for Hamby 44 than for Hamby 252, but also suggests that the choice of parameters also depends on the resolution or the scanning process of the data set.
-The same set of parameters might work for one data set, but not work equally well for another.
-
-The purpose of the results shown in \autoref{fig:param_seg_plot} and \autoref{fig:param_npeak_plot} is not to determine the "best" parameters for the CMPS algorithm, but to show that the sum of squares ratio can be used as an evaluation measure to compare different parameters, metrics, or scans.
-A pipeline that maximizes the sum of squares ratio might help researchers determine the set of parameters that work best for their data. 
-But a large database that is representative is what we really need in order to fully understand and cross-validate the parameters of the CMPS algorithm.
-
-**Comparing with the Original Results and the Random Forest model**
-
-@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` with (presumably) Hamby 252.
-The values in these histograms allow us to calculate the sum of squares ratios and include the results in \autoref{fig:param_npeak_plot} as well.
-They are marked by an asterisk at the top right corner in \autoref{fig:param_npeak_plot}.
-The sum of squares ratios we obtained for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` is slightly higher than those obtained from the histograms of @cmps. 
-It's curious to see that for the Hamby 252 results published in @cmps the $\mathrm{{CMPS}_{max}}$ metric achieves values of the sum of squares ratio higher than those achieved by the $\mathrm{\overline{CMPS}_{max}}$ metric.
-
-Since the researchers of @cmps did not use $\mathrm{\overline{CMPS}_{diff}}$ or $\mathrm{\overline{CMPS^*}_{diff}}$, and they did not apply the CMPS algorithm to the Hamby set 44, we were not able to compare those results.
-
-In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
-The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package `bulletxtrctr` [@bulletxtrctr].
-Similarly to the CMPS algorithm, this random forest model produces a  score to quantify the similarity of a land-by-land comparison.
-The RF scores lie in an interval of [0,1] making them most comparable to the scaled CMPS scores.
-We applied the logic of $\mathrm{{CMPS}_{max}}$, $\mathrm{\overline{CMPS}_{max}}$, and $\mathrm{\overline{CMPS}_{diff}}$ to the random forest scores and obtained results of the random forest model for different metrics.
-As shown in \autoref{fig:param_npeak_plot}, the random forest model does not achieve the sum of squares ratio as high as those achieved by the top CMPS algorithms for Hamby 252, but it does achieve better results for Hamby 44.
-This might suggest that an inclusion of the CMPS score as an additional feature in the random forest model training might be beneficial for an overall separation to determine source.
-
-The code generating all results of this manuscript can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
-
-## Conclusion
-
-\hh{XXX Will, the conclusion needs to be a bit more than just a summary of what we did in the paper - think of it as a summary plus either the limitations of our approach, or next steps that should be done but goes beyond this paper.}
-
-In this paper we present the `cmpsR` package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets from the Hamby study [@hamby] to show its potential for further research.
-The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
-We introduce the basic logic of the CMPS algorithm and lay out its implementation in the `cmpsR` package.
-We also showcase the functionality of the `cmpsR` package with a small dataset example that is included in the package.
-In the `cmpsR` package we implement some graphing tools for users to visualize results and to gain a better understanding of both the algorithm and the results.
-
-\wj{Additionally, we propose new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
-We also introduce a principled evaluation framework of algorithmic results based on a measure called the sum of squares ratio. 
-We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
-}
-<!-- Additionally, we apply the `cmpsR` package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).  -->
-The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
-\wj{However, the comparisons among different sets of parameters suggest that the optimal choice of the parameters varies for different datasets. 
-And further research can follow the proposed evaluation framework to have a comprehensive cross-validation on parameters used the algorithm.
-Furthermore, we compared our implemented CMPS algorithm with the random forest model proposed by @aoas and suggest adding the CMPS score as an additional feature in the random forest model.}
-
-The `cmpsR` package provides an open-source implementation and introduces the CMPS algorithm to the `R` community.
-
-Open-source implementations not only allow a peer-review but also facilitate further research, such as parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can then be used for error-rate estimations and fair applications that were called for by the PCAST [@pcast] report.
 
@@
 Wangqian Ju and Heike Hofmann
-
-<!-- ### About this format and the R Journal requirements -->
-
-<!-- `rticles::rjournal_article` will help you build the correct files requirements:  -->
-
-<!-- * A R file will be generated automatically using `knitr::purl` - see -->
-
-<!-- https://bookdown.org/yihui/rmarkdown-cookbook/purl.html for more information. -->
-
-<!-- * A tex file will be generated from this Rmd file and correctly included in -->
-
-<!-- `RJwapper.tex` as expected to build `RJwrapper.pdf`. -->
-
-<!-- * All figure files will be kept in the default rmarkdown `*_files` folder. This -->
-
-<!-- happens because `keep_tex = TRUE` by default in `rticles::rjournal_article` -->
-
-<!-- * Only the bib filename is to modifed. An example bib file is included in the -->
-
-<!-- template (`RJreferences.bib`) and you will have to name your bib file as the -->
-
-<!-- tex, R, and pdf files. -->

### 2021-10-13 ju-hofmann/ju-hofmann.Rmd
modify file names for R journal submission

--- 2021-10-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
@@
 
-bibliography: CMPSpaper-writing.bib
+bibliography: ju-hofmann.bib
 output: rticles::rjournal_article
@@
 \\begin{minipage}{.59\\textwidth}",
-    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
+    paste0("\\includegraphics[width=\\textwidth]{ju-hofmann_files/figure-latex/",
                  options[["label"]], "-1.pdf}
@@
 ```{r bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)."}
-knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
+# knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
+knitr::include_graphics("ju-hofmann_files/figure-latex/barrel_bullet_ps.png", dpi = 100)
 ```
@@
 (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
-knitr::include_graphics("img/figure1_v2.PNG", dpi = 100)
+knitr::include_graphics("ju-hofmann_files/figure-latex/figure1_v2.png", dpi = 100)
 ```
@@
 
-## Cover Letter
-
-Dear Professor Di Cook,
-
-In our submission An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets to the R Journal, we introduce the R package cmpsR, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm first described by Chen et al (2019).
-The CMPS algorithm is used for objective comparison of striated tool marks, and in our case, we apply the cmpsR implementation to bullet signatures extracted from 3D scans of bullet land engravings.
-The usage of the cmpsR implementation is discussed in our paper, but it is not our main focus: instead, we focus on the challenges of reproducing, evaluating, and making comparisons of the algorithmic results.
-
-We are highlighting the need for a principled evaluation framework in order to compare algorithmic results generated from various parameter settings and different models.
-Our discussion of this framework demonstrates the importance of an open-source implementation to effectively conduct further research.
-
-In this paper, we proposed new metrics based on CMPS scores to assure that the results of the CMPS algorithm are comparable to other existing methods; we developed a new method to quantify the effects of an algorithm on the bullet data, suggesting a principled evaluation framework; we make the cmpsR package open-source and all code and intermediate data used in the paper available to the public, acknowledging the components needed for computational reproducibility.
-As a result, we think the paper extends well beyond the cmpsR package vignette, providing useful methodology to anyone interested in assessments and comparisons of algorithmic results.
-
-Thank you for your consideration,
-
-Wangqian Ju and Heike Hofmann
-
 <!-- ### About this format and the R Journal requirements -->

### 2021-10-13 ju-hofmann/ju-hofmann.tex
modify file names for R journal submission

% !TeX root = RJwrapper.tex
\title{An Open-Source Implementation of the CMPS Algorithm for Assessing
Similarity of Bullets}
\author{by Wangqian W. Ju and Heike Hofmann}

\maketitle

\abstract{%
In this paper, we introduce the R package cmpsR, an open-source
implementation of the Congruent Matching Profile Segments (CMPS) method
developed at the National Institute of Standards and Technology (NIST)
for objective comparison of striated tool marks. The functionality of
the package is showcased by examples of bullet signatures that come with
the package. Graphing tools are implemented in the package as well for
users to assess and understand the CMPS results. Initial tests were
performed on bullet signatures generated from two sets of 3D scans in
the Hamby study under the framework suggested by the R package
bulletxtrctr. New metrics based on CMPS scores are introduced and
compared with existing metrics. A measure called Sum of Squares Ratio is
included, and how it can be used for evaluating different scans,
metrics, or parameters is showcased with the Hamby study data sets. An
open-source implementation of the CMPS algorithm makes the algorithm
more accessible, generates reproducible results, and facilitates further
studies of the algorithm such as methods comparison.
}

\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
\setlength{\parindent}{0pt}

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

In this paper we present an open-source implementation of the algorithm
of the Congruent Matching Profile Segments (CMPS) method. \citet{cmps}
developed the CMPS method for ``objective comparison of striated tool
marks'' and demonstrated its use in some examples of comparing bullet
signature correlations. Although \citet{cmps} conceptually described the
CMPS algorithm in their paper, the authors did not release an
implementation of their method. Thus, our effort here is to introduce
the CMPS method to the \texttt{R} \citep{R} community and provide an
open-source, publicly available implementation of the algorithm to use,
review, and improve. Our implementation is made available as part of the
\texttt{R} package \pkg{cmpsR} on GitHub at
\url{https://github.com/willju-wangqian/cmpsR}.

According to the Uniform Crime Reporting Program of FBI (Federal Bureau
of Investigation), ``More than 73 percent (73.7) of the homicides for
which the FBI received weapons data in 2019 involved the use of
firearms'' \citep{fbiucr}, and firearm examination could play an
important role in all these cases. \textbackslash hh\{XXX the new data
for 2020 came out on Sep 27 - homicides are up by close to 30\%. We
might want to mention that.\} An important task of firearm examination
is to answer the question of whether two pieces of evidence come from
the same source or whether a piece of evidence matches a sample obtained
from a specific firearm. Here, in particular, we are interested to
determine whether two bullets were fired from the same gun barrel.
Assessing the similarity between two bullets is based on a comparison of
striation marks acquired during the firing process as bullets are
propelled through the barrel. Current state of art sees firearms
examiners make an assessment of similarity based on a visual comparison,
generally, using a comparison microscope \citep{afte}. This practice has
been criticized for its lack of objectivity and the associated problem
in calculating an error rate \citep{pcast}.

A report published by \citet{nrc} states that ``{[}m{]}uch forensic
evidence-including, for example, bite marks and firearm and toolmark
identification---is introduced in criminal trials without any meaningful
scientific validation, determination of error rates, or reliability
testing to explain the limits of the discipline.'' To overcome those
criticisms and concerns, researchers have been making an effort to build
databases and develop frameworks and algorithms that bring an objective
and quantitative assessment into the field
\citetext{\citealp[\citet{brundage}, \citet{hamby}, \citet{Hamby:2019},
\citet{song2005}, \citet{ChumbleyL_Scott2010VoTM}, \citet{aoas},
\citet{pmid30444940}]{nistdb}; \citealp{cmps}}. Note that this is not an
exhaustive list of these efforts. The notion of bullet signatures is one
of the results of these efforts. Bullet signatures can be extracted from
bullet land engraved areas (LEAs), typically one for each land engraved
area, and how those bullet signatures are extracted from scans will be
discussed in the Background section. Since bullet signatures can
numerically describe the striation marks on the bullet and can be
understood by algorithms, they played an important role in bringing
objectivity into the field. In the following sections we will: review
the background of bullet signature comparisons, discuss how we followed
the idea described by \citet{cmps} for the implementation of the CMPS
algorithm, propose new metrics based on the CMPS score and a principled
evaluation framework for algorithmic results comparison, and present
results of applying our implementation to real data.

\hypertarget{background}{%
\subsection{Background}\label{background}}

\textbf{Hamby Data Set}

The datasets we worked with come from the James Hamby Consecutively
Rifled Ruger Barrel Study \citep{brundage, hamby, Hamby:2019}, in
particular, Hamby set 252 and Hamby set 44. For each Hamby set, a total
of 35 bullets is fired from (the same) ten consecutively manufactured
Ruger P-85 pistol barrels. Two bullets are fired from each barrel,
making up a set of 20 reference bullets. An additional 15 bullets are
fired from these ten barrels in a fashion unknown to the study
participant. The aim of the Hamby Study was to have firearms examiners
identify which barrel each of the 15 questioned bullets was fired from.
The Ruger P-85 barrels are traditionally rifled barrels with six grooves
and lands as shown in \autoref{fig:bullet}. During the firing process,
grooves and lands are engraved on a bullet. Firearms examiners use
striation marks on land engraved areas (LEAs) for their visual
comparison. For algorithmic purposes, 3D topographical images of land
engraved areas were obtained and stored in x3p format (XML 3-D Surface
Profile). The x3p format provides a standard way of exchanging 2D and 3D
profile data. It conforms to the ISO5436-2 standard
{[}\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}{]} adopted by the
OpenFMC (Open Forensic Metrology Consortium), a group of firearm
forensics researchers who contributes to the establishment of best
practices of using metrology in forensic science. Hamby set 252 were
scanned using a NanoFocus lens at 20x magnification with the scan
resolution being 1.5625 \textmu m \(\times\) 1.5625 \textmu m per pixel.
Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy
lab at Iowa State. These scans were acquired with a Sensofar Confocal
Light Microscope at 20x magnification for a nominal resolution of 0.645
\textmu m \(\times\) 0.645 \textmu m per pixel. Both Hamby set 252 and
Hamby set 44 are publicly available on the NIST Ballistics Database
Project \citep{nistdb}.

\textbf{Extracting signatures from LEA scans}

The automated framework used in this paper was proposed by \citet{aoas}.
In order to obtain bullet signatures from the x3p files of bullet land
engravings, we use the \texttt{R} packages \texttt{x3ptools}
\citep{x3ptools} and \texttt{bulletxtrctr} \citep{bulletxtrctr}.
\texttt{x3ptools} is a package to read, write, and generally, process
x3p files. The \texttt{bulletxtrctr} package implements a pipeline for
extracting and comparing signatures from scans of land-engraved areas.

\autoref{fig:process} gives an overview of all of the steps in the
process from scan to signatures. \autoref{fig:process}(a) shows a
rendering of a 3d scan of a bullet land engraved area. The raised
portion of the surface on the left and right of the scan are parts of
the adjacent groove engraved areas (GEAs), the middle area shows a
land-engraved area (LEA) with well expressed striation marks. The first
step of obtaining the bullet signature is to extract a cross-section at
a fixed height along the land engraving.

The white horizontal line in \autoref{fig:process}(a) indicates which
cross-section was identified by the algorithm to represent the LEA;
\autoref{fig:process}(b) shows the corresponding cross-sectional view.
Groove engraved areas are removed from the analysis as indicated by the
vertical blue lines in \autoref{fig:process}(c) and
\autoref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess}
is fitted to capture the bullet curvature (\autoref{fig:process}(e))
and, finally, the \textbf{bullet signature} (\autoref{fig:process}(f))
is obtained as residuals of the cross-section and the fitted smooth.
Note, that in \citet{cmps} bullet signatures are referred to as bullet
profiles. However, to avoid confusion, we distinguish the notion of
bullet signatures from bullet profiles. Bullet profiles are shown in
panels (b), (c), and (d) of \autoref{fig:process}, while
\autoref{fig:process}(f) shows the corresponding bullet signature.
Identifying the groove engraved areas correctly is fundamental for a
correct down-stream analysis of the signatures. To allow for a
human-in-the middle inspection and intervention we have provided an
interactive web-application, implemented as \texttt{R} Shiny App
\citep{shiny}, \texttt{bulletinspectR} to identify and correct those
errors. An example of the extraction process with corresponding code and
parameter settings can be found on Github at
\url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
Note that the process of extracting signatures might be different from
the one used in \citet{cmps} because no code or parameter settings are
made available publicly.

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=.8\textwidth]{ju-hofmann_files/figure-latex/barrel_bullet_ps}

}

\caption[Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)]{Photo of a traditionally rifled gun barrel (left) and a fired bullet (right).}\label{fig:bullet}
\end{figure}
\end{Schunk}

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=.9\textwidth]{ju-hofmann_files/figure-latex/figure1_v2}

}

\caption[A framework of obtaining a bullet signature]{A framework of obtaining a bullet signature. (a) front view of a scanned land engraved area (LEA). The selected crosscut location is indicated by the white line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves. (d) the crosscut data after chopping the left and right grooves. (e) the fitted curvature using LOESS. (f) after removing the curvature from the crosscut data, the bullet signature is obtained}\label{fig:process}
\end{figure}
\end{Schunk}

\textbf{Conceptual idea of CMPS}

Most algorithms for comparing striation marks are based on the digitized
signatures and produce a similarity score
\citep[\citet{ChumbleyL_Scott2010VoTM}, \citet{aoas},
\citet{pmid30444940}]{song2005}. The congruent matching profile segments
(CMPS) algorithm, developed by \citet{cmps} for ``objective comparison
of striated tool marks'', is one such algorithm. The algorithm's main
idea is to take a set of consecutive and non-overlapping basis segments
from the comparison and for each segment find the ``best'' registration
position on the reference (the other bullet signature) with respect to
their cross-correlation values. From a comparison of these registration
positions, a \textbf{congruent registration position} is identified, and
the number of basis segments taking the congruent registration position
is the CMPS score. Note that researchers in \citet{cmps} refers to the
origin of basis segments as the reference, but in this paper we refer to
it as the comparison. High CMPS scores are achieved between more similar
signatures and are therefore indicative of a same-source pair. Low
scores between pairs of signatures are attributed to different source
pairs. However, a specific threshold of the CMPS score to distinguish
between same-source and different-source comparisons is not provided in
\citet{cmps}, instead the threshold depends on the underlying structure
of the data and the choice of parameters.
\hh{XXX  In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on a wished-for outcome. }
Further research is needed to understand how to determine optimal
threshold settings. The CMPS algorithm can assist firearm examiners with
drawing a conclusion about the source of a comparison pair.
Unfortunately, \citet{cmps} did not release any code or specific
parameter settings for their implementation of the CMPS algorithm. Thus,
in this paper we present an open-source implementation of the CMPS
algorithm in the R package \pkg{cmpsR} available from Github
\url{https://github.com/willju-wangqian/cmpsR}. This publicly available
implementation calculates the CMPS score of a comparison using the
following code:

\begin{Schunk}
\begin{Sinput}
# install.packages("devtools") 
# devtools::install_github("willju-wangqian/CMPS")

library(cmpsR)
data(bullets)

sig1 <- bullets$sigs[[2]]$sig
sig2 <- bullets$sigs[[9]]$sig
sig3 <- bullets$sigs[[10]]$sig

cmps.result.KM <- extract_feature_cmps(sig1, sig2)
cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
\end{Sinput}
\end{Schunk}

In this example, the comparison between \texttt{sig1} and \texttt{sig2},
two signatures coming from the same source (a known-match comparison),
gets a CMPS score of 17; the comparison between \texttt{sig1} and
\texttt{sig3}, two signatures coming from different sources (a known
non-match comparison), gets a CMPS score of 1.

We also implemented graphing tools for users to better understand these
results as well as the algorithm itself.

The section ``Implementation'' will go through the algorithm and show
how to use the \pkg{cmpsR} package. A further example that illustrates
the main points is also included. The section ``Results'' presents the
results of evaluating the \pkg{cmpsR} package using Hamby set 252 and
Hamby set 44. The results from Hamby set 252 are used to verify that our
implementation is, at least qualitatively, comparable to the algorithm
described in \citet{cmps}. Results from Hamby 44 show the need for a
further investigation of the parameter choices even in the case of
bullets fired from the same barrels.
\wj{We suggest new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.}
The last section covers some final discussion and conclusions.

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

\textbf{Algorithm}

Conceptually, the CMPS algorithm consists of three main steps:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \textbf{cut the comparison signature into consecutive, non-overlapping
  and equal-length basis segments:} The command
  \texttt{get\_segs(x,\ len=50)} implements this step: it takes bullet
  signature \texttt{x} in the format of a numeric vector and cuts it
  into consecutive, non-overlapping and equal-length segments of length
  \texttt{len}, which are referred to as ``basis segments''.
\item
  \textbf{identify candidate positions:} For each basis segment a set of
  candidate registration positions on the comparison signature is
  identified based on the segment's similarity to the reference
  signature. In a first step, the cross-correlation function of the
  segment to the reference is calculated, then a number of positions
  with high correlation values are identified as candidate positions. In
  case multiple segment lengths are considered, the length of each basis
  segment is expanded (by default it is doubled) and these two steps are
  repeated. Only when candidate positions coincide (or are similar
  enough), they are considered further. \autoref{fig:segplots} and
  \autoref{fig:seg_all} illustrate these ideas.

  \begin{itemize}
  \item
    \textbf{Calculate the cross-correlation curve:} Calculate the
    cross-correlation curve between a basis segment \texttt{x} and the
    reference signature \texttt{y} using the function
    \texttt{get\_ccf4(x,\ y,\ ...)} as shown in \autoref{fig:segplot2}.
    The position indicates the lag by which a basis segment is moved
    with respect to its original placement. A position is considered
    ``good'' if it results in a peak in the cross-correlation between
    the basis segment and the reference.
  \item
    \textbf{Correlation peaks:} Two strategies referred to as
    ``multi-peak inspection'' and ``multi-peak inspection at different
    segment lengths'' in \citet{cmps} are used for identifying positions
    of correlation peaks as candidate positions. The latter is also
    called ``multi-segment lengths strategy''. The parameter
    \texttt{npeaks.set} in \texttt{extract\_feature\_cmps(...)}
    determines which strategy to use and the number of candidate
    positions:

    \begin{itemize}
    \tightlist
    \item
      If \texttt{npeaks.set} is an integer vector of length 1, for
      example \texttt{npeaks.set\ =\ 5}, the positions of the top five
      peaks in the cross-correlation curve are identified as candidate
      positions for registration.
    \item
      If \texttt{npeaks.set} is an integer vector of length more than 1,
      for example \texttt{npeaks.set\ =\ c(5,\ 3,\ 1)}, the
      multi-segment lengths strategy will be used: calculate the
      cross-correlation function between a basis segment and the
      reference and identify positions of the top five peaks; double the
      segment length to a specified value, re-calculate the
      cross-correlation function, and identify three peaks; repeat this
      process and identify a single peak in the newly computed
      cross-correlation function. \autoref{fig:seg_all} shows an example
      of three levels of basis segment 6 and their corresponding
      cross-correlation curves and identified peaks. Note that in
      \citet{cmps} the segment length is doubled at each level of a
      basis segment, but in the present implementation users are allowed
      to choose the segment length at each level.
    \item
      \texttt{get\_ccr\_peaks(comp,\ segments,\ seg\_outlength,\ nseg\ =\ 1,\ npeaks\ =\ 5)}
      computes the cross-correlation curve between a basis or increased
      segment and the reference signature and finds peaks in the
      cross-correlation curve. The number of peaks detected is equal to
      \texttt{npeaks}, which is an integer. \texttt{segments},
      \texttt{seg\_outlength}, and \texttt{nseg} determines the segment
      in the cross-correlation computation, and \texttt{comp} gives the
      reference signature. If the multi-segment lengths strategy is
      used, then \texttt{get\_ccr\_peaks(...)} is called in a
      \texttt{lapply()} for each level of the basis segment. The
      resulting list is called \texttt{ccr.list}.
    \end{itemize}
  \item
    \textbf{multi-segment lengths strategy:} with the multi-segment
    lengths strategy being used, a position is identified as a candidate
    position for registration and is called as a ``consistent
    correlation peak'' if it results in a top peak in the
    cross-correlation curve with a tolerance zone determined by
    \texttt{Tx} in all segment levels. Note that in \citet{cmps}, a
    segment at its largest scale (highest level) always identifies one
    peak, but we do not have this requirement in our implementation.

    \begin{itemize}
    \tightlist
    \item
      the function
      \texttt{get\_seg\_scale(segments,\ nseg,\ out\_length)} is used to
      obtain the (potentially increased) version of a basis segment.
      \texttt{segments}, which is a list containing all basis segments
      generated by the function \texttt{get\_segs(...)} in step 1, and
      \texttt{nseg} are used to determine the basis segment to be
      increased. \texttt{out\_length} specifies the length of the output
      segment.
    \item
      \texttt{get\_ccp(ccr.list,\ Tx\ =\ 25)} tries to identify the
      ``consistent correlation peak''. \texttt{ccr.list} is the result
      of \texttt{lapply()} and \texttt{get\_ccr\_peaks(...)}, and
      \texttt{Tx} determines the size of a tolerance zone used in
      identifying the consistent correlation peak.
      \texttt{get\_ccp(...)} returns \texttt{NULL} if there is no
      consistent correlation peak.
    \end{itemize}
  \end{itemize}
\item
  \textbf{determine the congruent registration position:} A candidate
  position ``receives'' \texttt{votes} from basis segments that identify
  it or a close position within a tolerance zone of \texttt{Tx} as a
  candidate position in step 2. Votes for all candidate positions are
  tallied, and the position with the highest number of votes gets chosen
  as the \emph{congruent registration position}, indicating that most of
  the basis segments find their highly similar counterpart in the
  reference signature in terms of correlation at this registration
  position. In case of ties the middle position is taken as the
  congruent registration position. Basis segments with a congruent
  registration position are called ``congruent matching profile
  segments'' (CMPS). The total number of CMPS is the CMPS score of the
  comparison. \texttt{get\_CMPS(input.ccp,\ Tx\ =\ 25)} is the function
  that tallies the votes and determines the congruent registration
  position and congruent matching profile segments (CMPS).
\end{enumerate}

Note that there are several parameters in the CMPS algorithm that are
left to the users to decide, such as the length of basis segments
\texttt{seg\_length} in step 1, the number of peaks \texttt{npeaks.set}
identified on each level in step 2, and the length of the tolerance zone
\texttt{Tx} in both step 2 and 3. In our implementation of the CMPS
algorithm we used the parameters given in the original CMPS paper
\citep{cmps} as the default values for these parameters. However, the
authors state that no cross-validation has been done - there might be
also issues with respect to resolution of the scans. Further research is
needed, until then users are advised to think of default values as
starting values and consider alternatives. The main function that
combines all steps in the CMPS algorithm described above is called
\texttt{extract\_feature\_cmps(...)}. Here we present it with its
default parameters.

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x,
  y,
  seg_length = 50,
  Tx = 25,
  npeaks.set = c(5, 3, 1),
  include = NULL,
  outlength = NULL
)
\end{Sinput}
\end{Schunk}

The function \texttt{extract\_feature\_cmps} allows for the following
input from users besides the previously discussed parameters
\texttt{seg\_length}, \texttt{npeaks.set}, and \texttt{Tx}:

\begin{itemize}
\item
  \texttt{x} and \texttt{y} are two signatures: \texttt{x} serves as the
  comparison signature (which will be divided into basis segments) and
  \texttt{y} is the reference signature;
\item
  \texttt{include} determines the format of the function result. Besides
  the \texttt{CMPS.score}, other aspects of the comparison help in
  understanding how the \texttt{CMPS.score} is computed. By default
  \texttt{include} is set to \texttt{NULL} and only the
  \texttt{CMPS.score} is returned; further results are included when
  \texttt{include} is (an abbreviation of) one of or a vector of the
  following strings:
  \texttt{"nseg",\ "congruent.pos",\ "congruent.seg.idx",\ "segments",\ "parameters"},
  and \texttt{"full\_result"}. If \texttt{include} is specified as
  \texttt{"full\_result"} (or its abbreviation), the output includes
  everything listed below.

  \begin{itemize}
  \tightlist
  \item
    \texttt{nseg}: the number of basis segments from the comparison
    signature; this is also the highest possible CMPS score of the
    comparison;
  \item
    \texttt{congruent.pos}: the congruent registration position;
  \item
    \texttt{congruent.seg.idx}: the indices of all congruent matching
    profile segments;
  \item
    \texttt{ccp.list}: a list showing identified candidate positions of
    all basis segments;
  \item
    \texttt{pos.df}: a data frame containing all candidate positions and
    their respective number of votes;
  \item
    \texttt{segments}: a list containing all basis segments;
  \item
    \texttt{parameters}: a list containing all input arguments of
    \texttt{extract\_feature\_cmps};
  \end{itemize}
\item
  \texttt{outlength} specifies the segment length of a basis segment at
  each level under the multi-segment lengths strategy. By default
  \texttt{outlength} is set to \texttt{NULL}, indicating that a basis
  segment should double its segment length at the next level and
  conforming to the description in \citet{cmps} .
\end{itemize}

In the remainder of the paper we showcase the use of the \pkg{cmpsR}
functionality on some examples and present the results of applying it to
two datasets.

\textbf{Installation}

The \pkg{cmpsR} package is not publicly available from CRAN yet, and its
development version is available from Github and can be installed by

\begin{Schunk}
\begin{Sinput}
# install.packages("remotes") 
remotes::install_github("willju-wangqian/cmpsR")
\end{Sinput}
\end{Schunk}

\textbf{An Example}

The \pkg{cmpsR} package contains a simple example to illustrate the
basic usage of the package. The data in this example are twelve bullet
signatures obtained from two bullets in Hamby set 252 \citep{hamby}. The
procedure for generating signatures from high-resolution 3D topographic
scans of bullet lands used here follows the methodology described in
\citet{aoas} (as discussed above). The two bullets under consideration
are known to have been fired from the same gun barrel, so for the 36
pairwise land-by-land comparisons, six comparisons are from same-source
pairs (known matches) while thirty are from different-source pairs
(known non-matches). To access the example data, we use

\begin{Schunk}
\begin{Sinput}
library(cmpsR)
\end{Sinput}
\begin{Soutput}
#> 
#> Attaching package: 'cmpsR'
\end{Soutput}
\begin{Soutput}
#> The following objects are masked _by_ '.GlobalEnv':
#> 
#>     compute_diff_phase, compute_score_metrics,
#>     get_all_phases, metric_plot_helper
\end{Soutput}
\begin{Sinput}
data(bullets)
\end{Sinput}
\end{Schunk}

\texttt{bullets\$sigs} is a list of twelve numeric vectors corresponding
to the twelve bullet signatures shown in \autoref{fig:sigs}.
\texttt{bullets\$source} contains the URLs to the corresponding x3p file
containing the topographic scan from the NIST Ballistics Toolmark
Research Database \citep{nistdb}.

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigs-1}

}

\caption[Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row]{Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row. Signatures in the second row are ordered to be in phase with the signatures above, i.e. matching signatures are displayed on top of each other.}\label{fig:sigs}
\end{figure}
\end{Schunk}

The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored
in objects \texttt{sigs2} and \texttt{sigs1}, respectively. This
comparison consists of a pair of signatures that are known to be a match
-- a KM (known match) comparison. We compute the CMPS score using two
versions of the CMPS algorithm:

\begin{Schunk}
\begin{Sinput}
sigs1 <- bullets$sigs[bullets$bulletland == "2-5"][[1]]
sigs2 <- bullets$sigs[bullets$bulletland == "1-4"][[1]]

# compute cmps

# algorithm with multi-peak insepction at three different segment levels
cmps_with_multi_scale <- 
  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                       npeaks.set = c(5,3,1), include = "full_result")

# algorithm with multi-peak inspection at the basis scale only
cmps_without_multi_scale <- 
  extract_feature_cmps(sigs1$sig, sigs2$sig, 
                       npeaks.set = 5, include = "full_result")
\end{Sinput}
\end{Schunk}

In the first example, \texttt{npeaks.set} is a vector of three integers,
i.e.~the algorithm uses the multi-segment lengths strategy to create the
result object \texttt{cmps\_with\_multi\_scale}. For
\texttt{cmps\_without\_multi\_scale} each basis segment is linked to the
top 5 candidate positions. We use \texttt{include\ =\ "full\_result"} to
capture all results. In this example, the CMPS is 9 when using multiple
segments, and 12 when using a single segment. As discussed in
\citet{cmps}, using multi-segment lengths strategy can reduce the number
of false positives when identifying candidate positions; however, any
score based method is walking the line between false positives and false
negatives. As the number of false positives is reduced the number of
false negatives might rise. More discussion and comparisons between the
two versions of the CMPS algorithm will be presented in later sections.
Note, that the multi-segment lengths method is slower because the
algorithm is run once for each segment length.

\textbf{Visualize and Understand CMPS results}

We also implemented graphing tools for visualizing results of the CMPS
algorithm. The goal is to provide users with tools to inspect each of
the basis segments and to help them have a better understanding of how
the algorithm works. \autoref{fig:sigplots} shows the plots generated by
the first graphing function, \texttt{cmps\_signature\_plot()}, and
continues with the example above. \texttt{cmps\_signature\_plot()} takes
the output of
\texttt{extract\_feature\_cmps(...,\ include\ =\ "full\_result")} and
returns a list of 5 elements. It creates an overall impression of how
the comparison signature aligns with the reference signature at the
congruent registration position.

\begin{itemize}
\item
  The first element is a plot called \texttt{segment\_shift\_plot},
  shown in \autoref{fig:sigplot}. On this plot the reference signature
  is drawn as a black line, congruent matching profile segments from the
  comparison signature are overlaid in red at the congruent registration
  position.
\item
  The second plot is called \texttt{signature\_shift\_plot}, shown in
  \autoref{fig:sigplot2}. This visual presents both the comparison
  signature and the reference signature. The comparison signature is
  aligned with the reference signature based on the congruent
  registration position. Congruent matching profile segments are
  highlighted by solid red lines.
\end{itemize}

\begin{figure}[hbt]
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
sig.plot <- cmps_signature_plot(
  cmps_with_multi_scale
)
sig.plot$segment_shift_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigplot-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:sigplot2}The black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
sig.plot$signature_shift_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/sigplot2-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\caption{\label{fig:sigplots} Two visual outputs of cmps\_signature\_plot()}
\end{figure}

\begin{itemize}
\tightlist
\item
  Other elements of this list are \texttt{seg\_shift} and
  \texttt{sig\_shift}. \texttt{sig\_shift} gives the congruent
  registration position, while \texttt{seg\_shift} is a data frame
  showing the congruent matching profile segments and their identified
  candidate position closest to the congruent registration position.
\end{itemize}

\begin{Schunk}
\begin{Sinput}
sig.plot$seg_shift
\end{Sinput}
\begin{Soutput}
#>    seg.idx seg.shift
#> 7        7         0
#> 8        8        -1
#> 14      14         5
#> 16      16         8
#> 17      17         8
#> 18      18         8
#> 19      19         9
#> 20      20         9
#> 22      22        12
\end{Soutput}
\end{Schunk}

While \texttt{cmps\_signature\_plot()} focuses on the signature level,
\texttt{cmps\_segment\_plot()} focuses on the segment level. It provides
the ``full result'' of \texttt{extract\_feature\_cmps()}, but also takes
an argument, \texttt{seg.idx}, indicating which segment should be
inspected. When checking \texttt{sig.plot\$seg\_shift} we notice that
segment number 6 is not one of the congruent matching profile segments.
We can therefore set \texttt{seg.idx\ =\ 6} in
\texttt{cmps\_segment\_plot()} and investigate the reason why this
segment disagrees with the congruent registration position.

For each segment scale, we have two plots: \texttt{segment\_plot} and
\texttt{scale\_ccf\_plot}, as shown in \autoref{fig:segplots} for the
example of segment number 6:

\begin{itemize}
\tightlist
\item
  \autoref{fig:segplot} is the \texttt{segment\_plot} for basis segment
  6 at level one (in its original length). We used
  \texttt{npeaks.set\ =\ c(5,\ 3,\ 1)} in
  \texttt{extract\_feature\_cmps()} when calculating the CMPS score.
  Therefore the top five peaks are identified in the cross-correlation
  curve at level one. Segment 6 is plotted at the positions where these
  5 peaks are identified with dashed lines in the
  \texttt{segment\_plot}. The solid thick black line shows the segment
  at its original position (which in this example is very close to the
  actual registration position).
\item
  \autoref{fig:segplot2} is the \texttt{scale\_ccf\_plot} of basis
  segment 6 at level one. It shows the cross-correlation curve computed
  by the reference signature and the level-one basis segment 6. The five
  highest peaks are marked by dots on the curve.
\end{itemize}

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at level one. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, 
  seg.idx = 6
)
seg.plot[[1]]$segment_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the reference signature and segment 6 at level one. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line. We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy. Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
seg.plot[[1]]$scale_ccf_plot
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot2-1.pdf}
\end{minipage}
\end{adjustbox}
\end{subfigure}
\caption{\label{fig:segplots} Two plots used to investigate basis segment 6 at level one}
\end{figure}

Additionally, users can have more insights about why segment 6 is not a
congruent matching profile segment if we put the \texttt{segment\_plot}
and \texttt{scale\_ccf\_plot} of all three segment levels together, as
shown in \autoref{fig:seg_all} with the help of
\texttt{ggpubr::ggarrange()}.

\begin{figure}
\vspace{1em}
\begin{adjustbox}{valign=t}
\begin{minipage}{.39\textwidth}

{\small {}
\begin{Schunk}
\begin{Sinput}
library(ggpubr)

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
\end{Sinput}
\end{Schunk}
}
\vspace{1em}
\end{minipage}
\begin{minipage}{.59\textwidth}
\includegraphics[width=\textwidth]{ju-hofmann_files/figure-latex/segplot3-1.pdf}
\end{minipage}
\end{adjustbox}
\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together. We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1). The highest peak position at level three is marked by the green dashed line across all segment levels. However, the highest peak on level three does not coincide with any of the top five highest peaks at level one. This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.}
\end{figure}

In \autoref{fig:seg_all}, the red vertical dashed line indicates the
congruent registration position. We can see that the basis segment 6
does obtain a peak near the congruent registration position at level two
and level three, respectively; however, this position doesn't give one
of the five highest peaks at level one. As a result, segment 6 fails to
identify the consistent correlation peak (ccp) and fails to become one
of the congruent matching profile segments according to the
multi-segment lengths strategy. The identified top five peaks at level
one are also examples of ``false positive'' peaks. The ``true positive''
peak (the peak within the tolerance zone of the congruent registration
position) is identified at level two and three by increasing the segment
length, which justifies the usage of multi-segment lengths strategy.

\hypertarget{evaluation-metrics}{%
\subsection{Evaluation Metrics}\label{evaluation-metrics}}

\textbf{Metrics Based on CMPS scores}

The CMPS algorithm measures the similarity between two signatures
resulting in a similarity score of a land-to-level comparison. Bullets
fired from traditionally rifled barrels have multiple land and groove
engraved areas. Here, we are working with bullets fired from Ruger P85
barrels with six lands and grooves. A comparison of two bullets
therefore involves 36 land-to-land comparisons, resulting in 36 CMPS
scores (as shown in \autoref{fig:tiles}). In order to obtain a single
similarity score of a bullet-level comparison, we need to summarize
these 36 CMPS scores. Two similarity metrics for bullet-level
comparisons have been introduced in the literature \citep{cmps}:
\(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\).
\(\mathrm{CMPS_{max}}\) is the highest CMPS score obtained among all
land-level comparisons, while \(\mathrm{\overline{CMPS}_{max}}\) is the
highest possible mean CMPS score of land-level comparisons that are in
the same phase:

In general, we assume each bullet has \(n\) land engravings (in our case
\(n=6\)). Let \(c_{ij}\) denote the CMPS score of a comparison between
bullet 1 land \(i\) and bullet 2 land \(j\), for \(i,j = 1, \dots, n\).
Let \(\mathcal{P}_k\) denote bullet land pairs in phase \(k\) for
\(k = 0, \dots, n-1\), and
\(\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}\),
where \(\mathbbm{1}_A\) denotes an indicator function. For example,
\(\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}\) when
\(n = 6\). Let \(k^*\) denote the index of the highest phase.

With that, the two measures to evaluate accuracy used in \citet{cmps}
are defined as

\begin{align}
\mathrm{CMPS_{max}} &= \max_{i,j} c_{ij} \text{ , and} \\
\mathrm{\overline{CMPS}_{max}} &= \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij} \text{ , where} \\
k^* &= \text{arg}\max\limits_{k} \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_k} c_{ij}\right]
\end{align}

We can continue with the example used in previous sections.
\texttt{bullets} contains bullet signatures of two bullets,
\texttt{bullet1} and \texttt{bullet2}. As mentioned before, each bullet
has 6 land engravings, resulting in 6 bullet signatures. Thus, there are
36 pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\)
values in total. We use multi-segment lengths strategy with default
parameters to compute these CMPS scores, and the result is shown in
\autoref{fig:tiles}. We can see that in this example,

\[
\mathrm{CMPS_{max}} =  \max_{i,j} c_{ij} = 17
\]

and since bullet lands in phase \(\mathcal{P}_1\) gives the highest mean
CMPS score (\(k^* = 1\)), we have

\[
\begin{aligned}
\mathrm{\overline{CMPS}_{max}} &= \frac{1}{6} \sum_{(i,j) \in \mathcal{P}_1} c_{ij} \\
                        &= \frac{1}{6} (c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}) \\
                        &= \frac{1}{6} (3+17+14+10+15+16) \\
                        &= 12.5
\end{aligned}
\]

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=.7\textwidth]{ju-hofmann_files/figure-latex/tiles-1}

}

\caption[CMPS scores of all 36 pairwise bullet signature comparisons for two bullets]{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets. Land engraving pairs generated by the same land (KM comparisons) are highlighted}\label{fig:tiles}
\end{figure}
\end{Schunk}

However, both \(\mathrm{CMPS_{max}}\) and
\(\mathrm{\overline{CMPS}_{max}}\) consider only relatively high CMPS
scores and ignore the rest. So we introduce a new metric based on CMPS
scores called \(\mathrm{\overline{CMPS}_{diff}}\), which is the
difference between \(\mathrm{\overline{CMPS}_{max}}\) and the mean of
all other CMPS scores. With our notation above, we have:

\begin{align}
\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n(n-1)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
\end{align}

\(\mathrm{\overline{CMPS}_{diff}}\) highlights the difference between
CMPS scores of matching and non-matching comparisons. If two bullets are
non-matching, all 36 CMPS scores are expected to be small with
relatively the same values, resulting in a
\(\mathrm{\overline{CMPS}_{diff}}\) value close to 0. For the example
above, \(\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97\)

\textbf{Scaled CMPS Scores}

Another issue with the CMPS score is that the highest possible CMPS
score (the total number of basis segments) might differ across
comparisons (as shown in \autoref{fig:tiles2}(a)) due to different
lengths of bullet signatures and different lengths of basis segments
specified by the parameter. A CMPS score of 5 might indicate a non-match
if the highest possible CMPS score is 30 but indicate a match if the
highest possible CMPS score is 6. Thus, we introduce the scaled CMPS
score, denoted as \(c^*_{ij}\). Let \(s_{ij}\) denote the highest
possible CMPS score or the total number of basis segments, then the
scaled CMPS score \(c^*_{ij}\) is defined as the ratio of raw score and
maximum score:

\begin{align}
c^*_{ij} = \frac{c_{ij}}{s_{ij}}
\end{align}

The scaled CMPS scores of the above example are shown in
\autoref{fig:tiles2}(b). Compared to the original CMPS scores, scaled
scores have values within the interval \([0, 1]\) regardless of the
length of the basis segments and therefore make a comparison of values
possible across different parameter choices. Similarly to the original
CMPS scores, we will denote the scaled CMPS scores adjusted for
out-of-phase background values by \(\mathrm{\overline{CMPS^*}_{diff}}\).
For example, \(\mathrm{\overline{CMPS^*}_{diff}} = 0.498\) for
\autoref{fig:tiles2}(b)

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=.7\textwidth]{ju-hofmann_files/figure-latex/tiles2-1}

}

\caption[Plot (a) shows the highest possible CMPS scores (the total number of basis segments) for the 36 comparisons]{Plot (a) shows the highest possible CMPS scores (the total number of basis segments) for the 36 comparisons. (b) shows the scaled CMPS scores for the 36 comparisons.}\label{fig:tiles2}
\end{figure}
\end{Schunk}

\textbf{Sum of Squares Ratio}

The ``sum of squares ratio'' quantifies how well two groups of values
separate. Let \(n_T\) denote the total number of observations, \(n_k\)
denote the number of observations in group \(k\), and \(y_{kl}\) denote
the \(l\)-th observation in group \(k\), for \(k = 1,2\) and
\(l = 1, \dots, n_k\). Let
\(\bar{y}_{k.} = \frac{1}{n_k} \sum_{l=1}^{n_k} y_{kl}\) denote the mean
value in group \(k\) and
\(\bar{y}_{..} = \frac{1}{n_T} \left( \sum_{k} \sum_{l = 1}^{n_k} y_{kl} \right)\)
denote the mean value of all observations. Consider the following model:

\begin{align}
y_{kl} = \mu_k + e_{kl}
\end{align}

where \(\mu_k\) is the true mean of group \(k\) and \(e_{kl}\) is a
random effect of different observations. Then we can define the sum of
squares ratio \(V\) as:

\begin{align}
V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }.
\end{align}

The numerator of the sum of squares ratio \(V\) quantifies the variation
between the two groups, while the denominator quantifies the variation
within each group. The sum of squares ratio \(V\) can be used as an
index for evaluating scans, metrics, and different sets of parameters if
the same data set is being used. Some examples will be presented in the
following section. If we impose the normality and independence
assumptions on the random effects \(e_{kl}\), the sum of squares ratio
\(V\) becomes a scaled F-statistic with degrees of freedom of \(k-1\)
and \(n_T - k\) and \(F = \frac{n_T - k}{k- 1} V\). If we want to
compare different data sets, stating that a certain setup can achieve
better separation on one data set than another, we can scale the sum of
squares ratio \(V\) and obtain the F-statistic to compare the p-values.

Using the sum of squares ratio \(V\) as an evaluation metric, we are
able to construct a pipeline that aims to find the optimal parameter
value for the CMPS algorithm by maximizing the sum of squares ratio. In
the following section, we will use this ratio to compare the CMPS
metrics introduced earlier and investigate effects of different sets of
parameters.

\hypertarget{results}{%
\subsection{Results}\label{results}}

As presented in the work of \citet{cmps}, researchers applied the CMPS
method to scans of one of the Hamby sets. While it is not explicitly
stated in the paper, we presume this to be Hamby 252, as only those
scans were publicly available at the time. In order to show that our
implementation of the CMPS algorithm is able to reproduce the results in
\citet{cmps} and be used for other data sets, we applied our
implementation to both Hamby set 252 and Hamby set 44. For the purpose
of reproducibility, we present how we obtained bullet signatures from
the Hamby set data and include code in the appendix: for both Hamby 252
and Hamby 44, we started with scans in the form of x3p files in the
database. Following the framework proposed by \citet{aoas}, we used the
same set of parameters, removed damaged bullet scans, obtained bullet
signatures for each bullet land engraving, and removed outliers in
bullet signatures. Note that researchers of \citet{cmps} applied the
CMPS algorithm to bullet signatures as well but used a framework
different from ours. However, since their work is not open-source, we
were not able to follow their framework and were only able to reproduce
the results for Hamby set 252 qualitatively.

\textbf{Hamby 252}

\autoref{fig:result1_252} shows the distribution of
\(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\) after we
applied the CMPS algorithm to Hamby set 252 with the multi-segment
lengths strategy. The parameters we used in
\texttt{extract\_feature\_cmps} for the CMPS algorithm are:

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x, y,
  seg_length = 50,
  Tx = 25,
  npeaks.set = c(5,3,1),
  include = "nseg"
)
\end{Sinput}
\end{Schunk}

As noted above, the CMPS scores we found here are not exactly the same
as those presented in \citet{cmps} since we were not able to follow
their framework, but the results presented in \autoref{fig:result1_252}
are qualitatively equivalent to those presented in \citet{cmps}, showing
a clear separation between scores based on comparisons from known
matches (KM) and scores from comparisons of known non-matches (KNM) for
both \(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\).

Additionally, to mimic the parameters used in \citet{cmps}, we set
\texttt{seg\_length\ =\ 50} and \texttt{Tx\ =\ 25} to make sure that
each basis segment has length of 78.125 \textmu m and the tolerance zone
is \(\pm 39.0625\) \textmu m (one unit represents 1.5625 \textmu m for
Hamby set 252).

The sum of squares ratios are 20.64 and 28.96 for
\(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\),
respectively. This indicates, that even though scores from
\(\mathrm{CMPS_{max}}\) for known-match comparisons are larger than
scores from the averaged version of \(\mathrm{\overline{CMPS}_{max}}\),
these scores achieve a better separation between the two groups of
comparisons.

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/result1_252-1}

}

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks.set = c(5,3,1)} }\label{fig:result1_252}
\end{figure}
\end{Schunk}

\textbf{Hamby 44}

Similar procedures are applied to Hamby set 44, and
\autoref{fig:result1_44} shows the distribution of
\(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\),
respectively. The parameters used in \texttt{extract\_feature\_cmps}
are:

\begin{Schunk}
\begin{Sinput}
extract_feature_cmps(
  x, y,
  seg_length = 61, 
  Tx = 30,
  npeaks.set = c(5,3,1),
  include = "nseg"
)
\end{Sinput}
\end{Schunk}

Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we
make \texttt{seg\_length\ =\ 61} and \texttt{Tx\ =\ 30} to ensure that
the setup of Hamby set 44 is similar to that of Hamby set 252, resulting
in basis segments of 78.69 \textmu m and the tolerance zone of
\(\pm 38.7\) \textmu m.

As shown in \autoref{fig:result1_44}, again, we are able to see a clear
separation between the known match comparisons and the known non-match
comparisons, even though the separation is relatively small compared
with that of Hamby set 252, which is also indicated by the sum of
squares ratios. For this specific set of parameters, the sum of squares
ratios are 8.87 and 10.64 for \(\mathrm{CMPS_{max}}\) and
\(\mathrm{\overline{CMPS}_{max}}\), respectively. This might suggest
that we could enlarge the separation in terms of the sum of squares
ratio by using other CMPS metrics and other sets of parameters.

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/result1_44-1}

}

\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks.set = c(5,3,1)} }\label{fig:result1_44}
\end{figure}
\end{Schunk}

\textbf{Comparing CMPS metrics and Parameters}

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/param_seg_plot-1}

}

\caption{Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter \texttt{seg\_length}). Only the $\mathrm{CMPS_{max}}$ metric suggests that the default values for the basis segment length result in the best separation. Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones. For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results}\label{fig:param_seg_plot}
\end{figure}
\end{Schunk}

\begin{Schunk}
\begin{figure}

{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/param_npeak_plot-1}

}

\caption[Comparison of CMPS results based on different strategies of number of peak selections]{Comparison of CMPS results based on different strategies of number of peak selections. Starred results compare CMPS performance with results published in the literature. Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but the random forest scores with the same logic. Since random forest scores lie within the interval $[0, 1]$, scaling the random forest scores will not change the results.}\label{fig:param_npeak_plot}
\end{figure}
\end{Schunk}

We investigated the effects of different sets of parameters at the
example of both Hamby sets 252 and 44. More specifically, we
investigated the separation achieved using the \pkg{cmpsR}
implementation under various segment lengths (controlled by the
parameter \texttt{seg\_length}). Specifically, we fixed the parameter
\texttt{npeaks.set} that controls the number of peaks at each segment
level to be \texttt{npeaks.set\ =\ c(5,3,1)} and modified the parameter
\texttt{seg\_length}. \autoref{fig:param_seg_plot} shows that the
default values of \texttt{seg\_length} for Hamby 252 and Hamby 44 (50
for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and
78.69 \textmu m, respectively) result in high values of the sum of
squares ratio, no matter which CMPS metrics are used for an evaluation.
However, we also see, that for Hamby set 252 a basis segment length of
75 is a better choice than the default segment length; a basis segment
length of 122 results in a higher value of sum of squares ratio for
Hamby 44.

\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using
different strategies for identifying peaks in the correlation structure
between signatures. Basis segment length is fixed to the default level
for this evaluation. As can be seen in \autoref{fig:param_npeak_plot},
the default value of \texttt{npeaks.set}
(\texttt{npeaks.set\ =\ c(5,3,1)}) leads to promising results in terms
of the sum of squares ratio; however, other choices of
\texttt{npeaks.set} match and exceed this sum of squares ratio value.

As seen before, the results suggest that the \(\mathrm{CMPS_{max}}\)
metric produces the least amount of separation compared with the other
three CMPS metrics. They also suggest that the two newly proposed
metrics, \(\mathrm{\overline{CMPS}_{diff}}\) and
\(\mathrm{\overline{CMPS^*}_{diff}}\), lead to equally good or even
better results as \(\mathrm{\overline{CMPS}_{max}}\). Because
\(\mathrm{\overline{CMPS^*}_{diff}}\) relies on a scaled version of CMPS
scores it is more comparable to other similarity scores and summarizes
the out-of-phase background CMPS scores, making it superior to the other
CMPS metrics.

What we can also observe in \autoref{fig:param_seg_plot} and
\autoref{fig:param_npeak_plot} is that the values of the sum of squares
ratio for Hamby 44 is lower than those for Hamby 252. This might be
because determining the source is a harder task for Hamby 44 than for
Hamby 252, but also suggests that the choice of parameters also depends
on the resolution or the scanning process of the data set. The same set
of parameters might work for one data set, but not work equally well for
another.

The purpose of the results shown in \autoref{fig:param_seg_plot} and
\autoref{fig:param_npeak_plot} is not to determine the ``best''
parameters for the CMPS algorithm, but to show that the sum of squares
ratio can be used as an evaluation measure to compare different
parameters, metrics, or scans. A pipeline that maximizes the sum of
squares ratio might help researchers determine the set of parameters
that work best for their data. But a large database that is
representative is what we really need in order to fully understand and
cross-validate the parameters of the CMPS algorithm.

\textbf{Comparing with the Original Results and the Random Forest model}

\citet{cmps} present histograms of \(\mathrm{CMPS_{max}}\) and
\(\mathrm{\overline{CMPS}_{max}}\) for \texttt{npeaks.set\ =\ 5} and
\texttt{npeaks.set\ =\ c(5,3,1)} with (presumably) Hamby 252. The values
in these histograms allow us to calculate the sum of squares ratios and
include the results in \autoref{fig:param_npeak_plot} as well. They are
marked by an asterisk at the top right corner in
\autoref{fig:param_npeak_plot}. The sum of squares ratios we obtained
for \texttt{npeaks.set\ =\ 5} and \texttt{npeaks.set\ =\ c(5,3,1)} is
slightly higher than those obtained from the histograms of \citet{cmps}.
It's curious to see that for the Hamby 252 results published in
\citet{cmps} the \(\mathrm{{CMPS}_{max}}\) metric achieves values of the
sum of squares ratio higher than those achieved by the
\(\mathrm{\overline{CMPS}_{max}}\) metric.

Since the researchers of \citet{cmps} did not use
\(\mathrm{\overline{CMPS}_{diff}}\) or
\(\mathrm{\overline{CMPS^*}_{diff}}\), and they did not apply the CMPS
algorithm to the Hamby set 44, we were not able to compare those
results.

In \autoref{fig:param_npeak_plot}, we also included the sum of squares
ratios computed from the random forest scores \citep{aoas} for different
metrics. The random forest model presented in \citet{aoas} was trained
at the Center for Statistics and Applications in Forensic Evidence
(CSAFE) and is publicly available in the R package \texttt{bulletxtrctr}
\citep{bulletxtrctr}. Similarly to the CMPS algorithm, this random
forest model produces a score to quantify the similarity of a
land-by-land comparison. The RF scores lie in an interval of {[}0,1{]}
making them most comparable to the scaled CMPS scores. We applied the
logic of \(\mathrm{{CMPS}_{max}}\), \(\mathrm{\overline{CMPS}_{max}}\),
and \(\mathrm{\overline{CMPS}_{diff}}\) to the random forest scores and
obtained results of the random forest model for different metrics. As
shown in \autoref{fig:param_npeak_plot}, the random forest model does
not achieve the sum of squares ratio as high as those achieved by the
top CMPS algorithms for Hamby 252, but it does achieve better results
for Hamby 44. This might suggest that an inclusion of the CMPS score as
an additional feature in the random forest model training might be
beneficial for an overall separation to determine source.

The code generating all results of this manuscript can be found on
Github at
\url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

\hh{XXX Will, the conclusion needs to be a bit more than just a summary of what we did in the paper - think of it as a summary plus either the limitations of our approach, or next steps that should be done but goes beyond this paper.}

In this paper we present the \pkg{cmpsR} package, an open-source
implementation of the Congruent Matching Profile Segments (CMPS)
algorithm \citep{cmps}, and apply it to two datasets in Hamby study
\citep{hamby} to show its potential for further research. The CMPS
algorithm was proposed by NIST in 2019 and was made for objective tool
marks comparisons. We introduce the basic logic of the CMPS algorithm
and lay out its implementation in the \pkg{cmpsR} package. We also
showcase the functionality of the \pkg{cmpsR} package with a small
dataset example that is included in the package. In the \pkg{cmpsR}
package we implement some graphing tools for users to visualize results
and to gain a better understanding of both the algorithm and the
results.

\wj{Additionally, we propose new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
We also introduce a principled evaluation framework of algorithmic results using  a measure based on the sum of squares ratio. 
We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio. }

The results obtained are promising: we were both able to reproduce the
results in \citet{cmps} qualitatively and achieve a clear separation
between the known match (KM) comparisons and known non-match (KNM)
comparisons in another bullet study.
\wj{However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets. We propose an evaluation framework that allows a comprehensive cross-validation of parameter settings used in the algorithm for future research. 
Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.}

\wj{The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards in the framework of open science. Open science is particularly important to fields like forensic science where transparency and accuracy are critical to fair justice. 
Open-source implementations not only allow a peer-review but also facilitate further research, such as parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can then be used for error-rate estimations and fair applications that were called for by the PCAST [@pcast] report.
However, having open-source implementations is not enough for open science. 
In order to actually build the world of open science, many other efforts, such as open evaluation, open access publication, open educational resources, etc., are still needed. 
The database built and maintained by the National Institute of Standards and Technology is a good example of open data. 
What we are aiming for is an open system that is able to collect open results, compare multiple algorithms using multiple datasets, and evaluate algorithmic variation and accuracy. 
The evaluation metric we proposed in this paper can be used to compare different algorithms or even different datasets and is a snippet of this open system. 
But the core of this open system is the open science culture and contributions of the community.}

\bibliography{ju-hofmann.bib}

\address{%
Wangqian W. Ju\\
Department of Statistics\\%
Center for Statistics and Applications in Forensic Evidence\\ Iowa State
University\\ 2438 Osborn Dr\\ Ames, IA 50011\\
%
\url{https://github.com/willju-wangqian}%
\\\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}%
\\\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}
}

\address{%
Heike Hofmann\\
Department of Statistics\\%
Center for Statistics and Applications in Forensic Evidence\\ Iowa State
University\\ 2438 Osborn Dr\\ Ames, IA 50011\\
%
\url{https://github.com/heike}%
\\\textit{ORCiD: \href{https://orcid.org/0000-0002-9079-593X}{0000-0002-9079-593X}}%
\\\href{mailto:hofmann@iastate.edu}{\nolinkurl{hofmann@iastate.edu}}
}

### 2021-10-13 ju-hofmann/ju-hofmann.R

@@ -1,0 +1,983 @@
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE------
+library(knitr)
+library(tidyverse)
+library(bulletxtrctr)
+library(kableExtra)
+library(patchwork)
+library(ggpubr)
+
+source("../code/func_collection.R")
+
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  out.width = "\\textwidth",
+  fig.align = "center",
+#  cache=TRUE,
+  dpi = 100,
+  warning = FALSE
+)
+
+
+## ----setup_knitr, echo=FALSE------------------------------
+## From Josh O'Brien's stackoverflow answer:
+## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
+## These two settings control text width in codefig vs. usual code blocks
+partWidth <- 35
+fullWidth <- 60
+options(width = fullWidth)
+
+##  (1) CHUNK HOOK FUNCTION
+##   First, to set R's textual output width on a per-chunk basis, we
+## need to define a hook function which temporarily resets global R's
+## option() settings, just for the current chunk
+knit_hooks$set(r.opts = local({
+    ropts <- NA
+    function(before, options, envir) {
+        if (before) {
+            ropts <<- options(options$r.opts)
+        } else {
+            options(ropts)
+        }
+    }
+}))
+
+## (2) OUTPUT HOOK FUNCTION
+
+##   Define a custom output hook function. This function processes _all_
+## evaluated chunks, but will return the same output as the usual one,
+## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
+## case, wrap the usual textual output in LaTeX code placing it in a
+## narrower adjustbox environment and setting the graphics that it
+## produced in another box beside it.
+
+defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
+
+codefigChunkHook <- function(x, options) {
+  main <-  defaultChunkHook(x, options)
+  before <-
+    "\\vspace{1em}
+\\begin{adjustbox}{valign=t}
+\\begin{minipage}{.39\\textwidth}\n"
+  after <-
+    paste("\\vspace{1em}
+\\end{minipage}
+\\begin{minipage}{.59\\textwidth}",
[…]

### 2021-10-14 ju-hofmann/ju-hofmann.Rmd
fulfilled the "marking text" section (hopefully)

@@
 abstract: >
-  In this paper, we introduce the R package cmpsR, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
+  In this paper, we introduce the R package \pkg{cmpsR}, an open-source implementation of the Congruent Matching Profile Segments (CMPS) method developed at the National Institute of Standards and Technology (NIST) for objective comparison of striated tool marks.
 The functionality of the package is showcased by examples of bullet signatures that come with the package.
 Graphing tools are implemented in the package as well for users to assess and understand the CMPS results.
-Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package bulletxtrctr.
+Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package \pkg{bulletxtrctr}.
 New metrics based on CMPS scores are introduced and compared with existing metrics.
-A measure called Sum of Squares Ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets.
+A measure called Sum of squares ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets.
 An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
@@
   dpi = 100,
-  warning = FALSE
+  warning = FALSE,
+  message = FALSE
 )
@@
 
-**Hamby Data Set**
+**Hamby data set**
 <!-- ### Hamby Data Set -->
@@
 The automated framework used in this paper was proposed by @aoas.
-In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
-`x3ptools` is a package to read, write, and generally, process x3p files.
-The `bulletxtrctr` package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
+In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages \pkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
+\pkg{x3ptools} is a package to read, write, and generally, process x3p files.
+The \pkg{bulletxtrctr} package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
 
@@
 Identifying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
-To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], `bulletinspectR` to identify and correct those errors.
+To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
 An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
@@
 
-In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 1.
+In this example, the comparison between \code{sig1} and \code{sig2}, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between \code{sig1} and \code{sig3}, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 1.
 
@@
 1.
-**cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command `get_segs(x, len=50)` implements this step: it takes bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
+**cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command \code{get\_segs(x, len=50)} implements this step: it takes bullet signature \code{x} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length \code{len}, which are referred to as "basis segments".
 
@@
 
-    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in \autoref{fig:segplot2}.
+    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment \code{x} and the reference signature \code{y} using the function \code{get\_ccf4(x, y, ...)} as shown in \autoref{fig:segplot2}.
 The position indicates the lag by which a basis segment is moved with respect to its original placement.
@@
 The latter is also called "multi-segment lengths strategy".
-The parameter `npeaks.set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:
-
-        -   If `npeaks.set` is an integer vector of length 1, for example `npeaks.set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
+The parameter \code{npeaks.set} in \code{extract\_feature\_cmps(...)} determines which strategy to use and the number of candidate positions:
+
+        -   If \code{npeaks.set} is an integer vector of length 1, for example \code{npeaks.set = 5}, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
+        -   If \code{npeaks.set} is an integer vector of length more than 1, for example \code{npeaks.set = c(5, 3, 1)}, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
 \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
 Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
-        -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
-The number of peaks detected is equal to `npeaks`, which is an integer.
-`segments`, `seg_outlength`, and `nseg` determines the segment in the cross-correlation computation, and `comp` gives the reference signature.
-If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment.
-The resulting list is called `ccr.list`.
-
-    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
+        -   \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)} computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
+The number of peaks detected is equal to \code{npeaks}, which is an integer.
+\code{segments}, \code{seg\_outlength}, and \code{nseg} determines the segment in the cross-correlation computation, and \code{comp} gives the reference signature.
+If the multi-segment lengths strategy is used, then \code{get\_ccr\_peaks(...)} is called in a \code{lapply()} for each level of the basis segment.
+The resulting list is called \code{ccr.list}.
+
+    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by \code{Tx} in all segment levels.
 Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.
 
-        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment.
-`segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased.
-`out_length` specifies the length of the output segment.
-        -   `get_ccp(ccr.list, Tx = 25)` tries to identify the "consistent correlation peak".
-`ccr.list` is the result of `lapply()` and `get_ccr_peaks(...)`, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
-`get_ccp(...)` returns `NULL` if there is no consistent correlation peak.
+        -   the function \code{get\_seg\_scale(segments, nseg, out\_length)} is used to obtain the (potentially increased) version of a basis segment.
+\code{segments}, which is a list containing all basis segments generated by the function \code{get\_segs(...)} in step 1, and \code{nseg} are used to determine the basis segment to be increased.
+\code{out\_length} specifies the length of the output segment.
+        -   \code{get\_ccp(ccr.list, Tx = 25)} tries to identify the "consistent correlation peak".
+\code{ccr.list} is the result of \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx} determines the size of a tolerance zone used in identifying the consistent correlation peak.
+\code{get\_ccp(...)} returns \code{NULL} if there is no consistent correlation peak.
 
 3.
-**determine the congruent registration position:** A candidate position "receives" `votes` from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
+**determine the congruent registration position:** A candidate position "receives" votes from basis segments that identify it or a close position within a tolerance zone of \code{Tx} as a candidate position in step 2.
     Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, indicating that most of the basis segments find their highly similar counterpart in the reference signature in terms of correlation at this registration position.
@@
     The total number of CMPS is the CMPS score of the comparison.
-    `get_CMPS(input.ccp, Tx = 25)` is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
-
-Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
+    \code{get\_CMPS(input.ccp, Tx = 25)} is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
+
+Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks.set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
@@
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
-The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
+The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
 Here we present it with its default parameters.
@@
 
-The function `extract_feature_cmps` allows for the following input from users besides the previously discussed parameters `seg_length`, `npeaks.set`, and `Tx`:
-
--   `x` and `y` are two signatures: `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;
-
--   `include` determines the format of the function result.
-    Besides the `CMPS.score`, other aspects of the comparison help in understanding how the `CMPS.score` is computed.
-    By default `include` is set to `NULL` and only the `CMPS.score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`.
-    If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.
-
-    -   `nseg`: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
-    -   `congruent.pos`: the congruent registration position;
-    -   `congruent.seg.idx`: the indices of all congruent matching profile segments;
-    -   `ccp.list`: a list showing identified candidate positions of all basis segments;
-    -   `pos.df`: a data frame containing all candidate positions and their respective number of votes;
-    -   `segments`: a list containing all basis segments;
-    -   `parameters`: a list containing all input arguments of `extract_feature_cmps`;
-
--   `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
-    By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
+The function \code{extract\_feature\_cmps} allows for the following input from users besides the previously discussed parameters \code{seg\_length}, \code{npeaks.set}, and \code{Tx}:
+
+-   \code{x} and \code{y} are two signatures: \code{x} serves as the comparison signature (which will be divided into basis segments) and \code{y} is the reference signature;
+
+-   \code{include} determines the format of the function result.
+    Besides the \code{CMPS.score}, other aspects of the comparison help in understanding how the \code{CMPS.score} is computed.
+    By default \code{include} is set to \code{NULL} and only the \code{CMPS.score} is returned; further results are included when \code{include} is (an abbreviation of) one of or a vector of the following strings: \code{"nseg"}, \code{"congruent.pos"}, \code{"congruent.seg.idx"}, \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}.
+    If \code{include} is specified as \code{"full\_result"} (or its abbreviation), the output includes everything listed below.
+
+    -   \code{nseg}: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
+    -   \code{congruent.pos}: the congruent registration position;
+    -   \code{congruent.seg.idx}: the indices of all congruent matching profile segments;
+    -   \code{ccp.list}: a list showing identified candidate positions of all basis segments;
+    -   \code{pos.df}: a data frame containing all candidate positions and their respective number of votes;
+    -   \code{segments}: a list containing all basis segments;
+    -   \code{parameters}: a list containing all input arguments of \code{extract\_feature\_cmps};
+
+-   \code{outlength} specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
+    By default \code{outlength} is set to \code{NULL}, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
 
@@
 
-**An Example**
+**An example**
 
@@
 
-`bullets$sigs` is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in \autoref{fig:sigs}.
-`bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan from the NIST Ballistics Toolmark Research Database [@nistdb].
+\code{bullets\$sigs} is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in \autoref{fig:sigs}.
+\code{bullets\$source} contains the URLs to the corresponding x3p file containing the topographic scan from the NIST Ballistics Toolmark Research Database [@nistdb].
 
@@
 
-The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
+The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects \code{sigs2} and \code{sigs1}, respectively.
 This comparison consists of a pair of signatures that are known to be a match -- a KM (known match) comparison.
@@
 
-In the first example, `npeaks.set` is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object `cmps_with_multi_scale`.
-For `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
-We use `include = "full_result"` to capture all results.
+In the first example, \code{npeaks.set} is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object \code{cmps\_with\_multi\_scale}.
+For \code{cmps\_without\_multi\_scale} each basis segment is linked to the top 5 candidate positions.
+We use \code{include = "full\_result"} to capture all results.
 In this example, the CMPS is 9 when using multiple segments, and 12 when using a single segment.
@@
 
-**Visualize and Understand CMPS results**
+**Visualize and understand CMPS results**
 
@@
 The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
-\autoref{fig:sigplots} shows the plots generated by the first graphing function, `cmps_signature_plot()`, and continues with the example above.
-`cmps_signature_plot()` takes the output of `extract_feature_cmps(..., include = "full_result")` and returns a list of 5 elements.
+\autoref{fig:sigplots} shows the plots generated by the first graphing function, \code{cmps\_signature\_plot()}, and continues with the example above.
+\code{cmps\_signature\_plot()} takes the output of \code{extract\_feature\_cmps(..., include = "full\_result")} and returns a list of 5 elements.
 It creates an overall impression of how the comparison signature aligns with the reference signature at the congruent registration position.
 
--   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}.
+-   The first element is a plot called \code{segment\_shift\_plot}, shown in \autoref{fig:sigplot}.
 On this plot the reference signature is drawn as a black line, congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.
 
--   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}.
+-   The second plot is called \code{signature\_shift\_plot}, shown in \autoref{fig:sigplot2}.
 This visual presents both the comparison signature and the reference signature.
@@
 ```
--   Other elements of this list are `seg_shift` and `sig_shift`.
-`sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
+-   Other elements of this list are \code{seg\_shift} and \code{sig\_shift}.
+\code{sig\_shift} gives the congruent registration position, while \code{seg\_shift} is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
 
@@
 
-While `cmps_signature_plot()` focuses on the signature level, `cmps_segment_plot()` focuses on the segment level.
-It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg.idx`, indicating which segment should be inspected.
-When checking `sig.plot$seg_shift` we notice that segment number 6 is not one of the congruent matching profile segments.
-We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
-
-For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in \autoref{fig:segplots} for the example of segment number 6:
-
--   \autoref{fig:segplot} is the `segment_plot` for basis segment 6 at level one (in its original length).
-We used `npeaks.set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
+While \code{cmps\_signature\_plot()} focuses on the signature level, \code{cmps\_segment\_plot()} focuses on the segment level.
+It provides the "full result" of \code{extract\_feature\_cmps()}, but also takes an argument, \code{seg.idx}, indicating which segment should be inspected.
+When checking \code{sig.plot\$seg\_shift} we notice that segment number 6 is not one of the congruent matching profile segments.
+We can therefore set \code{seg.idx = 6} in \code{cmps\_segment\_plot()} and investigate the reason why this segment disagrees with the congruent registration position.
+
+For each segment scale, we have two plots: \code{segment\_plot} and \code{scale\_ccf\_plot}, as shown in \autoref{fig:segplots} for the example of segment number 6:
+
+-   \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6 at level one (in its original length).
+We used \code{npeaks.set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when calculating the CMPS score.
 Therefore the top five peaks are identified in the cross-correlation curve at level one.
-Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
+Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the \code{segment\_plot}.
 The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
--   \autoref{fig:segplot2} is the `scale_ccf_plot` of basis segment 6 at level one.
+-   \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment 6 at level one.
 It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6.
@@
 ```
-Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of `ggpubr::ggarrange()`.
+Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the \code{segment\_plot} and \code{scale\_ccf\_plot} of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of \code{ggpubr::ggarrange()}.
 
@@
 
-## Evaluation Metrics
-
-**Metrics Based on CMPS scores**
+## Evaluation metrics
+
+**Metrics based on CMPS scores**
 
@@
 We can continue with the example used in previous sections.
-`bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
+\code{bullets} contains bullet signatures of two bullets, \code{bullet1} and \code{bullet2}.
 As mentioned before, each bullet has 6 land engravings, resulting in 6 bullet signatures.
@@
 
-**Scaled CMPS Scores**
+**Scaled CMPS scores**
 
@@
 
-**Sum of Squares Ratio**
+**Sum of squares ratio**
 
@@
 \autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy.
-The parameters we used in `extract_feature_cmps` for the CMPS algorithm are:
+The parameters we used in \code{extract\_feature\_cmps} for the CMPS algorithm are:
 
@@
 
-Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu m for Hamby set 252).
+Additionally, to mimic the parameters used in @cmps, we set \code{seg\_length = 50} and \code{Tx = 25} to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu m for Hamby set 252).
 
@@
 Similar procedures are applied to Hamby set 44, and \autoref{fig:result1_44} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-The parameters used in `extract_feature_cmps` are:
+The parameters used in \code{extract\_feature\_cmps} are:
 
@@
 
-Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we make `seg_length = 61` and `Tx = 30` to ensure that the setup of Hamby set 44 is similar to that of Hamby set 252, resulting in basis segments of 78.69 \textmu m and the tolerance zone of $\pm 38.7$ \textmu m.
+Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we make \code{seg\_length = 61} and \code{Tx = 30} to ensure that the setup of Hamby set 44 is similar to that of Hamby set 252, resulting in basis segments of 78.69 \textmu m and the tolerance zone of $\pm 38.7$ \textmu m.
 
@@
 
-**Comparing CMPS metrics and Parameters**
+**Comparing CMPS metrics and parameters**
 
@@
 We investigated the effects of different sets of parameters at the example of both Hamby sets 252 and 44.
-More specifically, we investigated the separation achieved using the \pkg{cmpsR} implementation under various segment lengths (controlled by the parameter `seg_length`).
-Specifically, we fixed the parameter `npeaks.set` that controls the number of peaks at each segment level to be `npeaks.set = c(5,3,1)` and modified the parameter `seg_length`.
-\autoref{fig:param_seg_plot} shows that the default values of `seg_length`  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
+More specifically, we investigated the separation achieved using the \pkg{cmpsR} implementation under various segment lengths (controlled by the parameter \code{seg\_length}).
+Specifically, we fixed the parameter \code{npeaks.set} that controls the number of peaks at each segment level to be \code{npeaks.set = c(5,3,1)} and modified the parameter \code{seg\_length}.
+\autoref{fig:param_seg_plot} shows that the default values of \code{seg\_length}  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
 However, we also see, that for Hamby set 252 a basis segment length of 75 is a better choice than the default segment length; a basis segment length of 122 results in a higher value of sum of squares ratio for Hamby 44.
@@
 Basis segment length is fixed to the default level for this evaluation.
-As can be seen in \autoref{fig:param_npeak_plot}, the default value of `npeaks.set` (`npeaks.set = c(5,3,1)`) leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks.set` match and  exceed this sum of squares ratio value.
+As can be seen in \autoref{fig:param_npeak_plot}, the default value of \code{npeaks.set} (\code{npeaks.set = c(5,3,1)}) leads to promising results in terms of the sum of squares ratio; however, other choices of \code{npeaks.set} match and  exceed this sum of squares ratio value.
 
@@
 
-**Comparing with the Original Results and the Random Forest model**
-
-@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` with (presumably) Hamby 252.
+**Comparing with original results and the random forest model**
+
+@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for \code{npeaks.set = 5} and \code{npeaks.set = c(5,3,1)} with (presumably) Hamby 252.
 The values in these histograms allow us to calculate the sum of squares ratios and include the results in \autoref{fig:param_npeak_plot} as well.
 They are marked by an asterisk at the top right corner in \autoref{fig:param_npeak_plot}.
-The sum of squares ratios we obtained for `npeaks.set = 5` and `npeaks.set = c(5,3,1)` is slightly higher than those obtained from the histograms of @cmps. 
+The sum of squares ratios we obtained for \code{npeaks.set = 5} and \code{npeaks.set = c(5,3,1)} is slightly higher than those obtained from the histograms of @cmps. 
 It's curious to see that for the Hamby 252 results published in @cmps the $\mathrm{{CMPS}_{max}}$ metric achieves values of the sum of squares ratio higher than those achieved by the $\mathrm{\overline{CMPS}_{max}}$ metric.
@@
 In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
-The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package `bulletxtrctr` [@bulletxtrctr].
+The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package \pkg{bulletxtrctr} [@bulletxtrctr].
 Similarly to the CMPS algorithm, this random forest model produces a  score to quantify the similarity of a land-by-land comparison.

### 2021-10-14 CMPSpaper_writing/CMPSpaper_writing.Rmd
small changes

@@
 It conforms to the ISO5436-2 standard [<http://sourceforge.net/p/open-gps/mwiki/X3p/>] adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
-Hamby set 252 were scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
+Hamby set 252 was scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
 Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy lab at Iowa State.
@@
 
-The automated framework used in this paper was proposed by @aoas.
-In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
+The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages `x3ptools` [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
 `x3ptools` is a package to read, write, and generally, process x3p files.

### 2021-10-14 ju-hofmann/ju-hofmann.Rmd

@@
 
-The automated framework used in this paper was proposed by @aoas.
-In order to obtain bullet signatures from the x3p files of bullet land engravings, we use the `R` packages \pkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
+The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages \pkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
 \pkg{x3ptools} is a package to read, write, and generally, process x3p files.

### 2021-10-14 ju-hofmann/ju-hofmann.tex

@@
 \abstract{%
-In this paper, we introduce the R package cmpsR, an open-source
+In this paper, we introduce the R package \pkg{cmpsR}, an open-source
 implementation of the Congruent Matching Profile Segments (CMPS) method
@@
 the Hamby study under the framework suggested by the R package
-bulletxtrctr. New metrics based on CMPS scores are introduced and
-compared with existing metrics. A measure called Sum of Squares Ratio is
+\pkg{bulletxtrctr}. New metrics based on CMPS scores are introduced and
+compared with existing metrics. A measure called Sum of squares ratio is
 included, and how it can be used for evaluating different scans,
@@
 
-\textbf{Hamby Data Set}
+\textbf{Hamby data set}
 
@@
 In order to obtain bullet signatures from the x3p files of bullet land
-engravings, we use the \texttt{R} packages \texttt{x3ptools}
-\citep{x3ptools} and \texttt{bulletxtrctr} \citep{bulletxtrctr}.
-\texttt{x3ptools} is a package to read, write, and generally, process
-x3p files. The \texttt{bulletxtrctr} package implements a pipeline for
+engravings, we use the \texttt{R} packages \pkg{x3ptools}
+\citep{x3ptools} and \pkg{bulletxtrctr} \citep{bulletxtrctr}.
+\pkg{x3ptools} is a package to read, write, and generally, process x3p
+files. The \pkg{bulletxtrctr} package implements a pipeline for
 extracting and comparing signatures from scans of land-engraved areas.
@@
 interactive web-application, implemented as \texttt{R} Shiny App
-\citep{shiny}, \texttt{bulletinspectR} to identify and correct those
+\citep{shiny}, \pkg{bulletinspectR} to identify and correct those
 errors. An example of the extraction process with corresponding code and
@@
 
-In this example, the comparison between \texttt{sig1} and \texttt{sig2},
-two signatures coming from the same source (a known-match comparison),
-gets a CMPS score of 17; the comparison between \texttt{sig1} and
-\texttt{sig3}, two signatures coming from different sources (a known
-non-match comparison), gets a CMPS score of 1.
+In this example, the comparison between \code{sig1} and \code{sig2}, two
+signatures coming from the same source (a known-match comparison), gets
+a CMPS score of 17; the comparison between \code{sig1} and \code{sig3},
+two signatures coming from different sources (a known non-match
+comparison), gets a CMPS score of 1.
 
@@
   and equal-length basis segments:} The command
-  \texttt{get\_segs(x,\ len=50)} implements this step: it takes bullet
-  signature \texttt{x} in the format of a numeric vector and cuts it
-  into consecutive, non-overlapping and equal-length segments of length
-  \texttt{len}, which are referred to as ``basis segments''.
+  \code{get\_segs(x, len=50)} implements this step: it takes bullet
+  signature \code{x} in the format of a numeric vector and cuts it into
+  consecutive, non-overlapping and equal-length segments of length
+  \code{len}, which are referred to as ``basis segments''.
 \item
@@
     \textbf{Calculate the cross-correlation curve:} Calculate the
-    cross-correlation curve between a basis segment \texttt{x} and the
-    reference signature \texttt{y} using the function
-    \texttt{get\_ccf4(x,\ y,\ ...)} as shown in \autoref{fig:segplot2}.
-    The position indicates the lag by which a basis segment is moved
-    with respect to its original placement. A position is considered
-    ``good'' if it results in a peak in the cross-correlation between
-    the basis segment and the reference.
+    cross-correlation curve between a basis segment \code{x} and the
+    reference signature \code{y} using the function
+    \code{get\_ccf4(x, y, ...)} as shown in \autoref{fig:segplot2}. The
+    position indicates the lag by which a basis segment is moved with
+    respect to its original placement. A position is considered ``good''
+    if it results in a peak in the cross-correlation between the basis
+    segment and the reference.
   \item
@@
     called ``multi-segment lengths strategy''. The parameter
-    \texttt{npeaks.set} in \texttt{extract\_feature\_cmps(...)}
-    determines which strategy to use and the number of candidate
-    positions:
+    \code{npeaks.set} in \code{extract\_feature\_cmps(...)} determines
+    which strategy to use and the number of candidate positions:
 
@@
     \item
-      If \texttt{npeaks.set} is an integer vector of length 1, for
-      example \texttt{npeaks.set\ =\ 5}, the positions of the top five
-      peaks in the cross-correlation curve are identified as candidate
-      positions for registration.
-    \item
-      If \texttt{npeaks.set} is an integer vector of length more than 1,
-      for example \texttt{npeaks.set\ =\ c(5,\ 3,\ 1)}, the
-      multi-segment lengths strategy will be used: calculate the
-      cross-correlation function between a basis segment and the
-      reference and identify positions of the top five peaks; double the
-      segment length to a specified value, re-calculate the
-      cross-correlation function, and identify three peaks; repeat this
-      process and identify a single peak in the newly computed
-      cross-correlation function. \autoref{fig:seg_all} shows an example
-      of three levels of basis segment 6 and their corresponding
-      cross-correlation curves and identified peaks. Note that in
-      \citet{cmps} the segment length is doubled at each level of a
-      basis segment, but in the present implementation users are allowed
-      to choose the segment length at each level.
-    \item
-      \texttt{get\_ccr\_peaks(comp,\ segments,\ seg\_outlength,\ nseg\ =\ 1,\ npeaks\ =\ 5)}
+      If \code{npeaks.set} is an integer vector of length 1, for example
+      \code{npeaks.set = 5}, the positions of the top five peaks in the
+      cross-correlation curve are identified as candidate positions for
+      registration.
+    \item
+      If \code{npeaks.set} is an integer vector of length more than 1,
+      for example \code{npeaks.set = c(5, 3, 1)}, the multi-segment
+      lengths strategy will be used: calculate the cross-correlation
+      function between a basis segment and the reference and identify
+      positions of the top five peaks; double the segment length to a
+      specified value, re-calculate the cross-correlation function, and
+      identify three peaks; repeat this process and identify a single
+      peak in the newly computed cross-correlation function.
+      \autoref{fig:seg_all} shows an example of three levels of basis
+      segment 6 and their corresponding cross-correlation curves and
+      identified peaks. Note that in \citet{cmps} the segment length is
+      doubled at each level of a basis segment, but in the present
+      implementation users are allowed to choose the segment length at
+      each level.
+    \item
+      \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)}
       computes the cross-correlation curve between a basis or increased
@@
       cross-correlation curve. The number of peaks detected is equal to
-      \texttt{npeaks}, which is an integer. \texttt{segments},
-      \texttt{seg\_outlength}, and \texttt{nseg} determines the segment
-      in the cross-correlation computation, and \texttt{comp} gives the
+      \code{npeaks}, which is an integer. \code{segments},
+      \code{seg\_outlength}, and \code{nseg} determines the segment in
+      the cross-correlation computation, and \code{comp} gives the
       reference signature. If the multi-segment lengths strategy is
-      used, then \texttt{get\_ccr\_peaks(...)} is called in a
-      \texttt{lapply()} for each level of the basis segment. The
-      resulting list is called \texttt{ccr.list}.
+      used, then \code{get\_ccr\_peaks(...)} is called in a
+      \code{lapply()} for each level of the basis segment. The resulting
+      list is called \code{ccr.list}.
     \end{itemize}
@@
     cross-correlation curve with a tolerance zone determined by
-    \texttt{Tx} in all segment levels. Note that in \citet{cmps}, a
+    \code{Tx} in all segment levels. Note that in \citet{cmps}, a
     segment at its largest scale (highest level) always identifies one
@@
     \item
-      the function
-      \texttt{get\_seg\_scale(segments,\ nseg,\ out\_length)} is used to
-      obtain the (potentially increased) version of a basis segment.
-      \texttt{segments}, which is a list containing all basis segments
-      generated by the function \texttt{get\_segs(...)} in step 1, and
-      \texttt{nseg} are used to determine the basis segment to be
-      increased. \texttt{out\_length} specifies the length of the output
+      the function \code{get\_seg\_scale(segments, nseg, out\_length)}
+      is used to obtain the (potentially increased) version of a basis
+      segment. \code{segments}, which is a list containing all basis
+      segments generated by the function \code{get\_segs(...)} in step
+      1, and \code{nseg} are used to determine the basis segment to be
+      increased. \code{out\_length} specifies the length of the output
       segment.
     \item
-      \texttt{get\_ccp(ccr.list,\ Tx\ =\ 25)} tries to identify the
-      ``consistent correlation peak''. \texttt{ccr.list} is the result
-      of \texttt{lapply()} and \texttt{get\_ccr\_peaks(...)}, and
-      \texttt{Tx} determines the size of a tolerance zone used in
-      identifying the consistent correlation peak.
-      \texttt{get\_ccp(...)} returns \texttt{NULL} if there is no
-      consistent correlation peak.
+      \code{get\_ccp(ccr.list, Tx = 25)} tries to identify the
+      ``consistent correlation peak''. \code{ccr.list} is the result of
+      \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx}
+      determines the size of a tolerance zone used in identifying the
+      consistent correlation peak. \code{get\_ccp(...)} returns
+      \code{NULL} if there is no consistent correlation peak.
     \end{itemize}
@@
   \textbf{determine the congruent registration position:} A candidate
-  position ``receives'' \texttt{votes} from basis segments that identify
-  it or a close position within a tolerance zone of \texttt{Tx} as a
-  candidate position in step 2. Votes for all candidate positions are
-  tallied, and the position with the highest number of votes gets chosen
-  as the \emph{congruent registration position}, indicating that most of
-  the basis segments find their highly similar counterpart in the
-  reference signature in terms of correlation at this registration
-  position. In case of ties the middle position is taken as the
-  congruent registration position. Basis segments with a congruent
-  registration position are called ``congruent matching profile
-  segments'' (CMPS). The total number of CMPS is the CMPS score of the
-  comparison. \texttt{get\_CMPS(input.ccp,\ Tx\ =\ 25)} is the function
-  that tallies the votes and determines the congruent registration
-  position and congruent matching profile segments (CMPS).
+  position ``receives'' votes from basis segments that identify it or a
+  close position within a tolerance zone of \code{Tx} as a candidate
+  position in step 2. Votes for all candidate positions are tallied, and
+  the position with the highest number of votes gets chosen as the
+  \emph{congruent registration position}, indicating that most of the
+  basis segments find their highly similar counterpart in the reference
+  signature in terms of correlation at this registration position. In
+  case of ties the middle position is taken as the congruent
+  registration position. Basis segments with a congruent registration
+  position are called ``congruent matching profile segments'' (CMPS).
+  The total number of CMPS is the CMPS score of the comparison.
+  \code{get\_CMPS(input.ccp, Tx = 25)} is the function that tallies the
+  votes and determines the congruent registration position and congruent
+  matching profile segments (CMPS).
 \end{enumerate}
@@
 left to the users to decide, such as the length of basis segments
-\texttt{seg\_length} in step 1, the number of peaks \texttt{npeaks.set}
+\code{seg\_length} in step 1, the number of peaks \code{npeaks.set}
 identified on each level in step 2, and the length of the tolerance zone
-\texttt{Tx} in both step 2 and 3. In our implementation of the CMPS
+\code{Tx} in both step 2 and 3. In our implementation of the CMPS
 algorithm we used the parameters given in the original CMPS paper
@@
 combines all steps in the CMPS algorithm described above is called
-\texttt{extract\_feature\_cmps(...)}. Here we present it with its
-default parameters.
+\code{extract\_feature\_cmps(...)}. Here we present it with its default
+parameters.
 
@@
 
-The function \texttt{extract\_feature\_cmps} allows for the following
+The function \code{extract\_feature\_cmps} allows for the following
 input from users besides the previously discussed parameters
-\texttt{seg\_length}, \texttt{npeaks.set}, and \texttt{Tx}:
+\code{seg\_length}, \code{npeaks.set}, and \code{Tx}:
 
@@
 \item
-  \texttt{x} and \texttt{y} are two signatures: \texttt{x} serves as the
+  \code{x} and \code{y} are two signatures: \code{x} serves as the
   comparison signature (which will be divided into basis segments) and
-  \texttt{y} is the reference signature;
-\item
-  \texttt{include} determines the format of the function result. Besides
-  the \texttt{CMPS.score}, other aspects of the comparison help in
-  understanding how the \texttt{CMPS.score} is computed. By default
-  \texttt{include} is set to \texttt{NULL} and only the
-  \texttt{CMPS.score} is returned; further results are included when
-  \texttt{include} is (an abbreviation of) one of or a vector of the
-  following strings:
-  \texttt{"nseg",\ "congruent.pos",\ "congruent.seg.idx",\ "segments",\ "parameters"},
-  and \texttt{"full\_result"}. If \texttt{include} is specified as
-  \texttt{"full\_result"} (or its abbreviation), the output includes
-  everything listed below.
+  \code{y} is the reference signature;
+\item
+  \code{include} determines the format of the function result. Besides
+  the \code{CMPS.score}, other aspects of the comparison help in
+  understanding how the \code{CMPS.score} is computed. By default
+  \code{include} is set to \code{NULL} and only the \code{CMPS.score} is
+  returned; further results are included when \code{include} is (an
+  abbreviation of) one of or a vector of the following strings:
+  \code{"nseg"}, \code{"congruent.pos"}, \code{"congruent.seg.idx"},
+  \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}. If
+  \code{include} is specified as \code{"full\_result"} (or its
+  abbreviation), the output includes everything listed below.
 
@@
   \item
-    \texttt{nseg}: the number of basis segments from the comparison
+    \code{nseg}: the number of basis segments from the comparison
     signature; this is also the highest possible CMPS score of the
@@
   \item
-    \texttt{congruent.pos}: the congruent registration position;
-  \item
-    \texttt{congruent.seg.idx}: the indices of all congruent matching
+    \code{congruent.pos}: the congruent registration position;
+  \item
+    \code{congruent.seg.idx}: the indices of all congruent matching
     profile segments;
   \item
-    \texttt{ccp.list}: a list showing identified candidate positions of
+    \code{ccp.list}: a list showing identified candidate positions of
     all basis segments;
   \item
-    \texttt{pos.df}: a data frame containing all candidate positions and
+    \code{pos.df}: a data frame containing all candidate positions and
     their respective number of votes;
   \item
-    \texttt{segments}: a list containing all basis segments;
-  \item
-    \texttt{parameters}: a list containing all input arguments of
-    \texttt{extract\_feature\_cmps};
+    \code{segments}: a list containing all basis segments;
+  \item
+    \code{parameters}: a list containing all input arguments of
+    \code{extract\_feature\_cmps};
   \end{itemize}
 \item
-  \texttt{outlength} specifies the segment length of a basis segment at
+  \code{outlength} specifies the segment length of a basis segment at
   each level under the multi-segment lengths strategy. By default
-  \texttt{outlength} is set to \texttt{NULL}, indicating that a basis
+  \code{outlength} is set to \code{NULL}, indicating that a basis
   segment should double its segment length at the next level and
@@
 
-\textbf{An Example}
+\textbf{An example}
 
@@
 library(cmpsR)
-\end{Sinput}
-\begin{Soutput}
-#> 
-#> Attaching package: 'cmpsR'
-\end{Soutput}
-\begin{Soutput}
-#> The following objects are masked _by_ '.GlobalEnv':
-#> 
-#>     compute_diff_phase, compute_score_metrics,
-#>     get_all_phases, metric_plot_helper
-\end{Soutput}
-\begin{Sinput}
 data(bullets)
@@
 
-\texttt{bullets\$sigs} is a list of twelve numeric vectors corresponding
+\code{bullets\$sigs} is a list of twelve numeric vectors corresponding
 to the twelve bullet signatures shown in \autoref{fig:sigs}.
-\texttt{bullets\$source} contains the URLs to the corresponding x3p file
+\code{bullets\$source} contains the URLs to the corresponding x3p file
 containing the topographic scan from the NIST Ballistics Toolmark
@@
 The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored
-in objects \texttt{sigs2} and \texttt{sigs1}, respectively. This
-comparison consists of a pair of signatures that are known to be a match
--- a KM (known match) comparison. We compute the CMPS score using two
-versions of the CMPS algorithm:
+in objects \code{sigs2} and \code{sigs1}, respectively. This comparison
+consists of a pair of signatures that are known to be a match -- a KM
+(known match) comparison. We compute the CMPS score using two versions
+of the CMPS algorithm:
 
@@
 
-In the first example, \texttt{npeaks.set} is a vector of three integers,
+In the first example, \code{npeaks.set} is a vector of three integers,
 i.e.~the algorithm uses the multi-segment lengths strategy to create the
-result object \texttt{cmps\_with\_multi\_scale}. For
-\texttt{cmps\_without\_multi\_scale} each basis segment is linked to the
-top 5 candidate positions. We use \texttt{include\ =\ "full\_result"} to
+result object \code{cmps\_with\_multi\_scale}. For
+\code{cmps\_without\_multi\_scale} each basis segment is linked to the
+top 5 candidate positions. We use \code{include = "full\_result"} to
 capture all results. In this example, the CMPS is 9 when using multiple
@@
 
-\textbf{Visualize and Understand CMPS results}
+\textbf{Visualize and understand CMPS results}
 
@@
 the algorithm works. \autoref{fig:sigplots} shows the plots generated by
-the first graphing function, \texttt{cmps\_signature\_plot()}, and
-continues with the example above. \texttt{cmps\_signature\_plot()} takes
+the first graphing function, \code{cmps\_signature\_plot()}, and
+continues with the example above. \code{cmps\_signature\_plot()} takes
 the output of
-\texttt{extract\_feature\_cmps(...,\ include\ =\ "full\_result")} and
-returns a list of 5 elements. It creates an overall impression of how
-the comparison signature aligns with the reference signature at the
+\code{extract\_feature\_cmps(..., include = "full\_result")} and returns
+a list of 5 elements. It creates an overall impression of how the
+comparison signature aligns with the reference signature at the
 congruent registration position.
@@
 \item
-  The first element is a plot called \texttt{segment\_shift\_plot},
-  shown in \autoref{fig:sigplot}. On this plot the reference signature
-  is drawn as a black line, congruent matching profile segments from the
+  The first element is a plot called \code{segment\_shift\_plot}, shown
+  in \autoref{fig:sigplot}. On this plot the reference signature is
+  drawn as a black line, congruent matching profile segments from the
   comparison signature are overlaid in red at the congruent registration
@@
 \item
-  The second plot is called \texttt{signature\_shift\_plot}, shown in
+  The second plot is called \code{signature\_shift\_plot}, shown in
   \autoref{fig:sigplot2}. This visual presents both the comparison
@@
 \item
-  Other elements of this list are \texttt{seg\_shift} and
-  \texttt{sig\_shift}. \texttt{sig\_shift} gives the congruent
-  registration position, while \texttt{seg\_shift} is a data frame
-  showing the congruent matching profile segments and their identified
-  candidate position closest to the congruent registration position.
+  Other elements of this list are \code{seg\_shift} and
+  \code{sig\_shift}. \code{sig\_shift} gives the congruent registration
+  position, while \code{seg\_shift} is a data frame showing the
+  congruent matching profile segments and their identified candidate
+  position closest to the congruent registration position.
 \end{itemize}
@@
 
-While \texttt{cmps\_signature\_plot()} focuses on the signature level,
-\texttt{cmps\_segment\_plot()} focuses on the segment level. It provides
-the ``full result'' of \texttt{extract\_feature\_cmps()}, but also takes
-an argument, \texttt{seg.idx}, indicating which segment should be
-inspected. When checking \texttt{sig.plot\$seg\_shift} we notice that
+While \code{cmps\_signature\_plot()} focuses on the signature level,
+\code{cmps\_segment\_plot()} focuses on the segment level. It provides
+the ``full result'' of \code{extract\_feature\_cmps()}, but also takes
+an argument, \code{seg.idx}, indicating which segment should be
+inspected. When checking \code{sig.plot\$seg\_shift} we notice that
 segment number 6 is not one of the congruent matching profile segments.
-We can therefore set \texttt{seg.idx\ =\ 6} in
-\texttt{cmps\_segment\_plot()} and investigate the reason why this
-segment disagrees with the congruent registration position.
-
-For each segment scale, we have two plots: \texttt{segment\_plot} and
-\texttt{scale\_ccf\_plot}, as shown in \autoref{fig:segplots} for the
+We can therefore set \code{seg.idx = 6} in \code{cmps\_segment\_plot()}
+and investigate the reason why this segment disagrees with the congruent
+registration position.
+
+For each segment scale, we have two plots: \code{segment\_plot} and
+\code{scale\_ccf\_plot}, as shown in \autoref{fig:segplots} for the
 example of segment number 6:
@@
 \item
-  \autoref{fig:segplot} is the \texttt{segment\_plot} for basis segment
-  6 at level one (in its original length). We used
-  \texttt{npeaks.set\ =\ c(5,\ 3,\ 1)} in
-  \texttt{extract\_feature\_cmps()} when calculating the CMPS score.
-  Therefore the top five peaks are identified in the cross-correlation
-  curve at level one. Segment 6 is plotted at the positions where these
-  5 peaks are identified with dashed lines in the
-  \texttt{segment\_plot}. The solid thick black line shows the segment
-  at its original position (which in this example is very close to the
-  actual registration position).
-\item
-  \autoref{fig:segplot2} is the \texttt{scale\_ccf\_plot} of basis
-  segment 6 at level one. It shows the cross-correlation curve computed
-  by the reference signature and the level-one basis segment 6. The five
+  \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6
+  at level one (in its original length). We used
+  \code{npeaks.set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when
+  calculating the CMPS score. Therefore the top five peaks are
+  identified in the cross-correlation curve at level one. Segment 6 is
+  plotted at the positions where these 5 peaks are identified with
+  dashed lines in the \code{segment\_plot}. The solid thick black line
+  shows the segment at its original position (which in this example is
+  very close to the actual registration position).
+\item
+  \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment
+  6 at level one. It shows the cross-correlation curve computed by the
+  reference signature and the level-one basis segment 6. The five
   highest peaks are marked by dots on the curve.
@@
 Additionally, users can have more insights about why segment 6 is not a
-congruent matching profile segment if we put the \texttt{segment\_plot}
-and \texttt{scale\_ccf\_plot} of all three segment levels together, as
+congruent matching profile segment if we put the \code{segment\_plot}
+and \code{scale\_ccf\_plot} of all three segment levels together, as
 shown in \autoref{fig:seg_all} with the help of
-\texttt{ggpubr::ggarrange()}.
+\code{ggpubr::ggarrange()}.
 
@@
 \hypertarget{evaluation-metrics}{%
-\subsection{Evaluation Metrics}\label{evaluation-metrics}}
-
-\textbf{Metrics Based on CMPS scores}
+\subsection{Evaluation metrics}\label{evaluation-metrics}}
+
+\textbf{Metrics based on CMPS scores}
 
@@
 We can continue with the example used in previous sections.
-\texttt{bullets} contains bullet signatures of two bullets,
-\texttt{bullet1} and \texttt{bullet2}. As mentioned before, each bullet
-has 6 land engravings, resulting in 6 bullet signatures. Thus, there are
-36 pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\)
-values in total. We use multi-segment lengths strategy with default
-parameters to compute these CMPS scores, and the result is shown in
+\code{bullets} contains bullet signatures of two bullets, \code{bullet1}
+and \code{bullet2}. As mentioned before, each bullet has 6 land
+engravings, resulting in 6 bullet signatures. Thus, there are 36
+pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\) values
+in total. We use multi-segment lengths strategy with default parameters
+to compute these CMPS scores, and the result is shown in
 \autoref{fig:tiles}. We can see that in this example,
@@
 
-\textbf{Scaled CMPS Scores}
+\textbf{Scaled CMPS scores}
 
@@
 
-\textbf{Sum of Squares Ratio}
+\textbf{Sum of squares ratio}
 
@@
 lengths strategy. The parameters we used in
-\texttt{extract\_feature\_cmps} for the CMPS algorithm are:
+\code{extract\_feature\_cmps} for the CMPS algorithm are:
 
@@
 Additionally, to mimic the parameters used in \citet{cmps}, we set
-\texttt{seg\_length\ =\ 50} and \texttt{Tx\ =\ 25} to make sure that
-each basis segment has length of 78.125 \textmu m and the tolerance zone
-is \(\pm 39.0625\) \textmu m (one unit represents 1.5625 \textmu m for
+\code{seg\_length = 50} and \code{Tx = 25} to make sure that each basis
+segment has length of 78.125 \textmu m and the tolerance zone is
+\(\pm 39.0625\) \textmu m (one unit represents 1.5625 \textmu m for
 Hamby set 252).
@@
 \(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\),
-respectively. The parameters used in \texttt{extract\_feature\_cmps}
-are:
+respectively. The parameters used in \code{extract\_feature\_cmps} are:
 
@@
 Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we
-make \texttt{seg\_length\ =\ 61} and \texttt{Tx\ =\ 30} to ensure that
-the setup of Hamby set 44 is similar to that of Hamby set 252, resulting
-in basis segments of 78.69 \textmu m and the tolerance zone of
-\(\pm 38.7\) \textmu m.
+make \code{seg\_length = 61} and \code{Tx = 30} to ensure that the setup
+of Hamby set 44 is similar to that of Hamby set 252, resulting in basis
+segments of 78.69 \textmu m and the tolerance zone of \(\pm 38.7\)
+\textmu m.
 
@@
 
-\textbf{Comparing CMPS metrics and Parameters}
+\textbf{Comparing CMPS metrics and parameters}
 
@@
 implementation under various segment lengths (controlled by the
-parameter \texttt{seg\_length}). Specifically, we fixed the parameter
-\texttt{npeaks.set} that controls the number of peaks at each segment
-level to be \texttt{npeaks.set\ =\ c(5,3,1)} and modified the parameter
-\texttt{seg\_length}. \autoref{fig:param_seg_plot} shows that the
-default values of \texttt{seg\_length} for Hamby 252 and Hamby 44 (50
-for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and
-78.69 \textmu m, respectively) result in high values of the sum of
-squares ratio, no matter which CMPS metrics are used for an evaluation.
-However, we also see, that for Hamby set 252 a basis segment length of
-75 is a better choice than the default segment length; a basis segment
-length of 122 results in a higher value of sum of squares ratio for
-Hamby 44.
+parameter \code{seg\_length}). Specifically, we fixed the parameter
+\code{npeaks.set} that controls the number of peaks at each segment
+level to be \code{npeaks.set = c(5,3,1)} and modified the parameter
+\code{seg\_length}. \autoref{fig:param_seg_plot} shows that the default
+values of \code{seg\_length} for Hamby 252 and Hamby 44 (50 for Hamby
+252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69
+\textmu m, respectively) result in high values of the sum of squares
+ratio, no matter which CMPS metrics are used for an evaluation. However,
+we also see, that for Hamby set 252 a basis segment length of 75 is a
+better choice than the default segment length; a basis segment length of
+122 results in a higher value of sum of squares ratio for Hamby 44.
 
@@
 for this evaluation. As can be seen in \autoref{fig:param_npeak_plot},
-the default value of \texttt{npeaks.set}
-(\texttt{npeaks.set\ =\ c(5,3,1)}) leads to promising results in terms
-of the sum of squares ratio; however, other choices of
-\texttt{npeaks.set} match and exceed this sum of squares ratio value.
+the default value of \code{npeaks.set} (\code{npeaks.set = c(5,3,1)})
+leads to promising results in terms of the sum of squares ratio;
+however, other choices of \code{npeaks.set} match and exceed this sum of
+squares ratio value.
 
@@
 
-\textbf{Comparing with the Original Results and the Random Forest model}
+\textbf{Comparing with original results and the random forest model}
 
 \citet{cmps} present histograms of \(\mathrm{CMPS_{max}}\) and
-\(\mathrm{\overline{CMPS}_{max}}\) for \texttt{npeaks.set\ =\ 5} and
-\texttt{npeaks.set\ =\ c(5,3,1)} with (presumably) Hamby 252. The values
-in these histograms allow us to calculate the sum of squares ratios and
+\(\mathrm{\overline{CMPS}_{max}}\) for \code{npeaks.set = 5} and
+\code{npeaks.set = c(5,3,1)} with (presumably) Hamby 252. The values in
+these histograms allow us to calculate the sum of squares ratios and
 include the results in \autoref{fig:param_npeak_plot} as well. They are
@@
 \autoref{fig:param_npeak_plot}. The sum of squares ratios we obtained
-for \texttt{npeaks.set\ =\ 5} and \texttt{npeaks.set\ =\ c(5,3,1)} is
-slightly higher than those obtained from the histograms of \citet{cmps}.
-It's curious to see that for the Hamby 252 results published in
-\citet{cmps} the \(\mathrm{{CMPS}_{max}}\) metric achieves values of the
-sum of squares ratio higher than those achieved by the
+for \code{npeaks.set = 5} and \code{npeaks.set = c(5,3,1)} is slightly
+higher than those obtained from the histograms of \citet{cmps}. It's
+curious to see that for the Hamby 252 results published in \citet{cmps}
+the \(\mathrm{{CMPS}_{max}}\) metric achieves values of the sum of
+squares ratio higher than those achieved by the
 \(\mathrm{\overline{CMPS}_{max}}\) metric.
@@
 at the Center for Statistics and Applications in Forensic Evidence
-(CSAFE) and is publicly available in the R package \texttt{bulletxtrctr}
+(CSAFE) and is publicly available in the R package \pkg{bulletxtrctr}
 \citep{bulletxtrctr}. Similarly to the CMPS algorithm, this random

### 2021-10-14 ju-hofmann/ju-hofmann.Rmd
proof read

@@
 @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
-Although @cmps conceptually described the CMPS algorithm in their paper, the authors did not release an implementation of their method.
+Although @cmps conceptually describe the CMPS algorithm in their paper, the authors did not release an implementation of their method.
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
@@
 Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
-This practice has been criticized for its lack of objectivity and the associated problem in calculating an error rate [@pcast].
-
-A report published by @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940; @cmps].
+This practice has been criticized for its lack of objectivity and the associated problem of determining valid error rates [@pcast].
+
+A report published by the @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field \hh{XXX could you summarize the main contribution of each of these papers in at most a sentence?} [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940; @cmps].
 Note that this is not an exhaustive list of these efforts.
@@
 These scans were acquired with a Sensofar Confocal Light Microscope at 20x magnification for a nominal resolution of 0.645 \textmu m $\times$ 0.645 \textmu m per pixel.
-Both Hamby set 252 and Hamby set 44 are publicly available on the NIST Ballistics Database Project [@nistdb].
+Both Hamby set 252 and Hamby set 44 are publicly available from the NIST Ballistics Database Project [@nistdb].
 
@@
 
-The white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
+The thin white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
 Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
@@
 ```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature.
-(a) front view of a scanned land engraved area (LEA).
-The selected crosscut location is indicated by the white line.
+(a) rendering from the 3d topographic scan of a land engraved area (LEA).
+The selected crosscut location is indicated by a thin white horizontal line.
 (b) view of the cross-section of the land engraved area at the white line in (a).
@@
 From a comparison of these registration positions, a **congruent registration position** is identified, and the number of basis segments taking the congruent registration position is the CMPS score.
-Note that researchers in @cmps refers to the origin of basis segments as the reference, but in this paper we refer to it as the comparison.
+Note that researchers in @cmps refer to the origin of basis segments as the reference, but in this paper we refer to it as the comparison signature.
 High CMPS scores are achieved between more similar signatures and are therefore indicative of a same-source pair.
@@
 However, a specific threshold of the CMPS score to distinguish between same-source and different-source comparisons is not provided in @cmps, instead the threshold depends on the underlying structure of the data and the choice of parameters.
-\hh{XXX  In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on a wished-for outcome.
-}
+In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on whether they are witnesses for the defense or the prosecution.
 Further research is needed to understand how to determine optimal threshold settings.
 The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
-Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.
+<!--Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.-->
 Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from Github \url{https://github.com/willju-wangqian/cmpsR}.
@@
 A further example that illustrates the main points is also included.
+In the section on 'Evaluation metrics" we introduce new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.
 The section "Results" presents the results of evaluating the \pkg{cmpsR} package using Hamby set 252 and Hamby set 44.
@@
 Results from Hamby 44 show the need for a further investigation of the parameter choices even in the case of bullets fired from the same barrels.
-\wj{We suggest new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.}
 <!-- \hh{We suggest a sum of square ratio ...} -->
@@
 ```{r tiles, echo=FALSE, fig.cap="CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
-Land engraving pairs generated by the same land (KM comparisons) are highlighted", out.width=".7\\textwidth", fig.align="center"}
+Land engraving pairs generated by the same land (KM comparisons) are highlighted.
+\\hh{Note that in this example the axis along Bullet 2 starts with Land 2.
+This corresponds to Phase 2 in equation XXX}", out.width=".7\\textwidth", fig.align="center"}
 dframe <- dframe %>% mutate(
@@
 While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time.
+\hh{XXX Let's take out this statement once we hear back from NIST}
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
@@
 
-\hh{XXX Will, the conclusion needs to be a bit more than just a summary of what we did in the paper - think of it as a summary plus either the limitations of our approach, or next steps that should be done but goes beyond this paper.}
+\hh{XXX Additional line for the conclusion: Hamby sets 44 and 252 were taken with different resolution scanning devices.
+The bullets for Hamby 44 and Hamby 252 are fired from the same ten consecutively rifled P-85 Ruger barrels.
+The difference in parameter settings is therefore quite surprising.
+As next steps we need validation studies - trying out the CMPS algorithm on firearms and ammunition combinations that are different to test the limits of the algorithm.
+XXX shoutout to Susan's paper?
+- will look up the reference }
 

### 2021-10-14 ju-hofmann/ju-hofmann.tex
proof read

@@
 marks'' and demonstrated its use in some examples of comparing bullet
-signature correlations. Although \citet{cmps} conceptually described the
+signature correlations. Although \citet{cmps} conceptually describe the
 CMPS algorithm in their paper, the authors did not release an
@@
 been criticized for its lack of objectivity and the associated problem
-in calculating an error rate \citep{pcast}.
-
-A report published by \citet{nrc} states that ``{[}m{]}uch forensic
+of determining valid error rates \citep{pcast}.
+
+A report published by the \citet{nrc} states that ``{[}m{]}uch forensic
 evidence-including, for example, bite marks and firearm and toolmark
@@
 and quantitative assessment into the field
+\hh{XXX could you summarize the main contribution of each of these papers in at most a sentence?}
 \citetext{\citealp[\citet{brundage}, \citet{hamby}, \citet{Hamby:2019},
@@
 forensics researchers who contributes to the establishment of best
-practices of using metrology in forensic science. Hamby set 252 were
+practices of using metrology in forensic science. Hamby set 252 was
 scanned using a NanoFocus lens at 20x magnification with the scan
@@
 \textmu m \(\times\) 0.645 \textmu m per pixel. Both Hamby set 252 and
-Hamby set 44 are publicly available on the NIST Ballistics Database
+Hamby set 44 are publicly available from the NIST Ballistics Database
 Project \citep{nistdb}.
@@
 
-The automated framework used in this paper was proposed by \citet{aoas}.
-In order to obtain bullet signatures from the x3p files of bullet land
-engravings, we use the \texttt{R} packages \pkg{x3ptools}
-\citep{x3ptools} and \pkg{bulletxtrctr} \citep{bulletxtrctr}.
-\pkg{x3ptools} is a package to read, write, and generally, process x3p
-files. The \pkg{bulletxtrctr} package implements a pipeline for
-extracting and comparing signatures from scans of land-engraved areas.
+The automated framework for extracting signatures from x3p files used in
+this paper was proposed by \citet{aoas} and is implemented in the
+\texttt{R} packages \pkg{x3ptools} \citep{x3ptools} and
+\pkg{bulletxtrctr} \citep{bulletxtrctr}. \pkg{x3ptools} is a package to
+read, write, and generally, process x3p files. The \pkg{bulletxtrctr}
+package implements a pipeline for extracting and comparing signatures
+from scans of land-engraved areas.
 
@@
 
-The white horizontal line in \autoref{fig:process}(a) indicates which
-cross-section was identified by the algorithm to represent the LEA;
-\autoref{fig:process}(b) shows the corresponding cross-sectional view.
-Groove engraved areas are removed from the analysis as indicated by the
-vertical blue lines in \autoref{fig:process}(c) and
+The thin white horizontal line in \autoref{fig:process}(a) indicates
+which cross-section was identified by the algorithm to represent the
+LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional
+view. Groove engraved areas are removed from the analysis as indicated
+by the vertical blue lines in \autoref{fig:process}(c) and
 \autoref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess}
@@
 \caption[A framework of obtaining a bullet signature]{A framework of obtaining a bullet signature.
-(a) front view of a scanned land engraved area (LEA).
-The selected crosscut location is indicated by the white line.
+(a) rendering from the 3d topographic scan of a land engraved area (LEA).
+The selected crosscut location is indicated by a thin white horizontal line.
 (b) view of the cross-section of the land engraved area at the white line in (a).
@@
 the number of basis segments taking the congruent registration position
-is the CMPS score. Note that researchers in \citet{cmps} refers to the
+is the CMPS score. Note that researchers in \citet{cmps} refer to the
 origin of basis segments as the reference, but in this paper we refer to
-it as the comparison. High CMPS scores are achieved between more similar
-signatures and are therefore indicative of a same-source pair. Low
-scores between pairs of signatures are attributed to different source
-pairs. However, a specific threshold of the CMPS score to distinguish
-between same-source and different-source comparisons is not provided in
-\citet{cmps}, instead the threshold depends on the underlying structure
-of the data and the choice of parameters.
-\hh{XXX  In a legal setting this variability is problematic because it allows for situations in which experts could choose parameters based on a wished-for outcome. }
-Further research is needed to understand how to determine optimal
-threshold settings. The CMPS algorithm can assist firearm examiners with
-drawing a conclusion about the source of a comparison pair.
-Unfortunately, \citet{cmps} did not release any code or specific
-parameter settings for their implementation of the CMPS algorithm. Thus,
-in this paper we present an open-source implementation of the CMPS
-algorithm in the R package \pkg{cmpsR} available from Github
+it as the comparison signature. High CMPS scores are achieved between
+more similar signatures and are therefore indicative of a same-source
+pair. Low scores between pairs of signatures are attributed to different
+source pairs. However, a specific threshold of the CMPS score to
+distinguish between same-source and different-source comparisons is not
+provided in \citet{cmps}, instead the threshold depends on the
+underlying structure of the data and the choice of parameters. In a
+legal setting this variability is problematic because it allows for
+situations in which experts could choose parameters based on whether
+they are witnesses for the defense or the prosecution. Further research
+is needed to understand how to determine optimal threshold settings. The
+CMPS algorithm can assist firearm examiners with drawing a conclusion
+about the source of a comparison pair. Thus, in this paper we present an
+open-source implementation of the CMPS algorithm in the R package
+\pkg{cmpsR} available from Github
 \url{https://github.com/willju-wangqian/cmpsR}. This publicly available
@@
 how to use the \pkg{cmpsR} package. A further example that illustrates
-the main points is also included. The section ``Results'' presents the
-results of evaluating the \pkg{cmpsR} package using Hamby set 252 and
-Hamby set 44. The results from Hamby set 252 are used to verify that our
-implementation is, at least qualitatively, comparable to the algorithm
-described in \citet{cmps}. Results from Hamby 44 show the need for a
-further investigation of the parameter choices even in the case of
-bullets fired from the same barrels.
-\wj{We suggest new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.}
-The last section covers some final discussion and conclusions.
+the main points is also included. In the section on 'Evaluation metrics"
+we introduce new CMPS metrics that summarize land-level CMPS scores and
+a sum of squares ratio that can be used to evaluate algorithmic results.
+The section ``Results'' presents the results of evaluating the
+\pkg{cmpsR} package using Hamby set 252 and Hamby set 44. The results
+from Hamby set 252 are used to verify that our implementation is, at
+least qualitatively, comparable to the algorithm described in
+\citet{cmps}. Results from Hamby 44 show the need for a further
+investigation of the parameter choices even in the case of bullets fired
+from the same barrels. The last section covers some final discussion and
+conclusions.
 
@@
 
-\caption[CMPS scores of all 36 pairwise bullet signature comparisons for two bullets]{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
-Land engraving pairs generated by the same land (KM comparisons) are highlighted}\label{fig:tiles}
+\caption{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
+Land engraving pairs generated by the same land (KM comparisons) are highlighted.
+\hh{Note that in this example the axis along Bullet 2 starts with Land 2.
+This corresponds to Phase 2 in equation XXX}}\label{fig:tiles}
 \end{figure}
@@
 %
-\url{https://github.com/willju-wangqian}%
-\\\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}%
-\\\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}
+\url{https://github.com/willju-wangqian}\\%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}\\%
+\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}%
 }
@@
 %
-\url{https://github.com/heike}%
-\\\textit{ORCiD: \href{https://orcid.org/0000-0002-9079-593X}{0000-0002-9079-593X}}%
-\\\href{mailto:hofmann@iastate.edu}{\nolinkurl{hofmann@iastate.edu}}
-}
+\url{https://github.com/heike}\\%
+\textit{ORCiD: \href{https://orcid.org/0000-0002-9079-593X}{0000-0002-9079-593X}}\\%
+\href{mailto:hofmann@iastate.edu}{\nolinkurl{hofmann@iastate.edu}}%
+}

### 2021-10-14 ju-hofmann/ju-hofmann.R

@@ -15,7 +15,8 @@ knitr::opts_chunk$set(
   fig.align = "center",
 #  cache=TRUE,
   dpi = 100,
-  warning = FALSE
+  warning = FALSE,
+  message = FALSE
 )
 
 
@@ -63,7 +64,7 @@ codefigChunkHook <- function(x, options) {
     paste("\\vspace{1em}
 \\end{minipage}
 \\begin{minipage}{.59\\textwidth}",
-    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
+    paste0("\\includegraphics[width=\\textwidth]{ju-hofmann_files/figure-latex/",
                  options[["label"]], "-1.pdf}
 \\end{minipage}
 \\end{adjustbox}"),
@@ -97,11 +98,12 @@ codefig = list(codefig = TRUE, fig.show = "hide",
 
 
 ## ----bullet, echo=FALSE, out.width=".8\\textwidth", fig.cap="Photo of a traditionally rifled gun barrel (left) and a fired bullet (right)."----
-knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
+# knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
+knitr::include_graphics("ju-hofmann_files/figure-latex/barrel_bullet_ps.png", dpi = 100)
 
 
-## ----process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature. (a) front view of a scanned land engraved area (LEA). The selected crosscut location is indicated by the white line. (b) view of the cross-section of the land engraved area at the white line in (a). (c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves. (d) the crosscut data after chopping the left and right grooves. (e) the fitted curvature using LOESS. (f) after removing the curvature from the crosscut data, the bullet signature is obtained"----
-knitr::include_graphics("img/figure1_v2.PNG", dpi = 100)
[…]

### 2021-10-20 ju-hofmann/ju-hofmann.Rmd
correct a figure label

@@
                          subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
-  xlab(labels[3])
+  xlab(labels[1])
 p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
@@
   xlab(labels[4])
+
 p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
@@
                          subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
-  xlab(labels[3])
+  xlab(labels[1])
 p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
@@
 
+<!-- ```{r plot_thisisus} -->
+<!-- rf.252.plot <- metric_plot_helper(rf.results[[1]], "rf.diff", scaled = TRUE, -->
+<!--                                   subtitle = "random forest scores with metric diff") + -->
+<!--   xlab(expression(RF[diff])) + -->
+<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
+<!-- cmps.252.plot <- metric_plot_helper(CMPS_hamby252_results_npeak$cmps.table[[8]], "cmps.diff_scaled",  -->
+<!--                                     scaled = TRUE, subtitle = "CMPS, 10-8-6-4-2-1, 50") + -->
+<!--   xlab(labels[3]) + -->
+<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
+
+<!-- rf.44.plot <- metric_plot_helper(rf.results[[2]], "rf.diff", scaled = TRUE, -->
+<!--                                   subtitle = "random forest scores with metric diff") + -->
+<!--   xlab(expression(RF[diff])) + -->
+<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
+<!-- cmps.44.plot <- metric_plot_helper(CMPS_hamby44_results_npeak$cmps.table[[6]], "cmps.diff_scaled",  -->
+<!--                                     scaled = TRUE, subtitle = "CMPS, 10-7-4-2, 61") + -->
+<!--   xlab(labels[3]) + -->
+<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
+
+<!-- p.thisisus252 <- ggarrange(plotlist = list(cmps.252.plot, rf.252.plot), nrow = 1, ncol = 2, -->
+<!--                common.legend = TRUE, legend = "bottom") -->
+<!-- p.thisisus252 <-  -->
+<!--   annotate_figure(p.thisisus252,  -->
+<!--                   top = text_grob("Hamby 252 - Random Forest and CMPS")) -->
+
+<!-- p.thisisus44 <- ggarrange(plotlist = list(cmps.44.plot, rf.44.plot), nrow = 1, ncol = 2, -->
+<!--                common.legend = TRUE, legend = "bottom") -->
+<!-- p.thisisus44 <-  -->
+<!--   annotate_figure(p.thisisus44,  -->
+<!--                   top = text_grob("Hamby 44 - Random Forest and CMPS")) -->
+
+<!-- ``` -->
+
 <!-- ### About this format and the R Journal requirements -->

### 2021-10-21 ju-hofmann/ju-hofmann.Rmd
modified the citation in intro and conclusion

@@
 
-According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "More than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms" [@fbiucr], and firearm examination could play an important role in all these cases.
-\hh{XXX the new data for 2020 came out on Sep 27 - homicides are up by close to 30%.
-We might want to mention that.}
+<!-- According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms" [@fbiucr], and firearm examination could play an important role in all these cases.
+-->
+<!-- \hh{XXX the new data for 2020 came out on Sep 27 - homicides are up by close to 30%. We might want to mention that.} -->
+<!-- https://s3-us-gov-west-1.amazonaws.com/cg-d4b776d0-d898-4153-90c8-8336f86bdfec/CIUS/downloads/2020/expanded-homicide-2020.zip -->
 <!-- Firearm examination has  played an important role in  convictions [@fbiucr] in the United States criminal justice system.
@@
 XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
+\wj{According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms", and the number of cases that involved the use of firearms in 2020 increased by close to 30 percent (29.3) compared to that in 2019 [@fbiucr].
+Firearm examination could play an important role in all these cases.
+}
 An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
@@
 
-A report published by the @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field \hh{XXX could you summarize the main contribution of each of these papers in at most a sentence?} [@nistdb, @brundage, @hamby, @Hamby:2019, @song2005, @ChumbleyL_Scott2010VoTM, @aoas, @pmid30444940; @cmps].
+<!-- \hh{XXX could you summarize the main contribution of each of these papers in at most a sentence?} -->
+A report published by the @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field.
+\wj{The database} of @nistdb and data sets of @brundage, @hamby, @Hamby:2019 provide great open data resources for research.
+Algorithms that can be validated and tested and generate quantitative results are developed for 2D and 3D surface texture [@song2005], tool marks [@ChumbleyL_Scott2010VoTM], and striae on Land Engraved Areas (LEAs) of bullets [@aoas, @pmid30444940, @cmps].
 Note that this is not an exhaustive list of these efforts.
-The notion of bullet signatures is one of the results of these efforts.
+\wj{The notion of bullet signatures is one of the results of these efforts, and we will use it to explain the CMPS algorithm and showcase} the \pkg{cmpsR} implementation.
 Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
@@
 If we impose the normality and independence assumptions on the random effects $e_{kl}$, the sum of squares ratio $V$ becomes a scaled F-statistic with degrees of freedom of $k-1$ and $n_T - k$ and $F = \frac{n_T - k}{k- 1} V$.
-If we want to compare different data sets, stating that a certain setup can achieve better separation on one data set than another, we can scale the sum of squares ratio $V$ and obtain the F-statistic to compare the p-values.
-
-Using the sum of squares ratio $V$ as an evaluation metric, we are able to construct a pipeline that aims to find the optimal parameter value for the CMPS algorithm by maximizing the sum of squares ratio.
-In the following section, we will use this ratio to compare the CMPS metrics introduced earlier and investigate effects of different sets of parameters.
+If we want to compare different data sets, stating that a certain setup can achieve better separation on one data set than another, we can scale the sum of squares ratio $V$ and obtain the F-statistic and obtain the corresponding p-value as an index for comparison.
+
+Using the sum of squares ratio $V$ as an evaluation metric, we are able to construct a pipeline that aims to find the optimal parameter values for the CMPS algorithm by maximizing the sum of squares ratio.
+\wj{Note that other measures of an algorithm, such as the accuracy and the AUC (Area Under the Curve), are also important and useful.
+But when algorithms achieve 100 percent accuracy and AUC of value 1, we need another measure like the sum of squares ratio to further distinguish the performance of algorithms.} In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced earlier and investigate effects of different parameter settings.
 
@@
 The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
-\wj{However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.
-We propose an evaluation framework that allows a comprehensive cross-validation of parameter settings used in the algorithm for future research.
-Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.}
+\wj{However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.}
+
+\wj{Note that Hamby sets 44 and 252 were taken with different resolution scanning devices.
+The bullets for Hamby 44 and Hamby 252 are fired from the same ten consecutively rifled P-85 Ruger barrels.
+The difference in parameter settings is therefore quite surprising.
+As next steps we need validation studies - trying out the CMPS algorithm on firearms and ammunition combinations that are different to test the limits of the algorithm.
+The evaluation framework we proposed based on the sum of squares ratio will facilitate such studies and other validation of the algorithm.}
+
+\wj{Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.}
 

### 2021-10-28 ju-hofmann/ju-hofmann.Rmd
final proofread?

@@
 XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
-\wj{According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms", and the number of cases that involved the use of firearms in 2020 increased by close to 30 percent (29.3) compared to that in 2019 [@fbiucr].
+According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 \hh{is this really 2020 or should it be 2019?}involved the use of firearms", and the number of cases that involved the use of firearms in 2020 increased by close to 30 percent (29.3) compared to that in 2019 [@fbiucr].
 Firearm examination could play an important role in all these cases.
-}
 An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
@@
 A report published by the @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field.
-\wj{The database} of @nistdb and data sets of @brundage, @hamby, @Hamby:2019 provide great open data resources for research.
+The database of @nistdb with digital 3d topographic scans from various studies by @brundage, @hamby, @Hamby:2019 and others, provides a great resource for researchers.
 Algorithms that can be validated and tested and generate quantitative results are developed for 2D and 3D surface texture [@song2005], tool marks [@ChumbleyL_Scott2010VoTM], and striae on Land Engraved Areas (LEAs) of bullets [@aoas, @pmid30444940, @cmps].
-Note that this is not an exhaustive list of these efforts.
-\wj{The notion of bullet signatures is one of the results of these efforts, and we will use it to explain the CMPS algorithm and showcase} the \pkg{cmpsR} implementation.
+<!--Note that this is not an exhaustive list of these efforts.-->
+The notion of bullet signatures is one of the results of these efforts, and we will use it to explain the CMPS algorithm and showcase the \pkg{cmpsR} implementation.
 Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
-Since bullet signatures can numerically describe the striation marks on the bullet and can be understood by algorithms, they played an important role in bringing objectivity into the field.
+Bullet signatures capture striation marks on the bullet in a numeric format and therefore serve as the foundation for algorithms.
+These scans played an important role in bringing objectivity into the field.
 In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison,  and present results of applying our implementation to real data.
@@
 Using the sum of squares ratio $V$ as an evaluation metric, we are able to construct a pipeline that aims to find the optimal parameter values for the CMPS algorithm by maximizing the sum of squares ratio.
-\wj{Note that other measures of an algorithm, such as the accuracy and the AUC (Area Under the Curve), are also important and useful.
-But when algorithms achieve 100 percent accuracy and AUC of value 1, we need another measure like the sum of squares ratio to further distinguish the performance of algorithms.} In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced earlier and investigate effects of different parameter settings.
+Note that other measures of an algorithm, such as the accuracy and the AUC (Area Under the Curve), are also important and useful.
+But when algorithms achieve 100 percent accuracy and AUC value of 1, we need other measures such as the sum of squares ratio to further distinguish the performance of algorithms.
+In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced earlier and investigate effects of different parameter settings.
 
@@
 
-\hh{XXX Additional line for the conclusion: Hamby sets 44 and 252 were taken with different resolution scanning devices.
-The bullets for Hamby 44 and Hamby 252 are fired from the same ten consecutively rifled P-85 Ruger barrels.
-The difference in parameter settings is therefore quite surprising.
-As next steps we need validation studies - trying out the CMPS algorithm on firearms and ammunition combinations that are different to test the limits of the algorithm.
-XXX shoutout to Susan's paper?
-- will look up the reference }
-
 In this paper we present the \pkg{cmpsR} package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
@@
 
-\wj{Additionally, we propose new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
+Additionally, we propose two new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
 We also introduce a principled evaluation framework of algorithmic results using  a measure based on the sum of squares ratio. 
 We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
-}
 <!-- Additionally, we apply the \pkg{cmpsR} package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).  -->
 The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
-\wj{However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.}
-
-\wj{Note that Hamby sets 44 and 252 were taken with different resolution scanning devices.
+However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.
+
+Note, that the main difference between Hamby sets 44 and 252 is that they were taken with different resolution scanning devices.
 The bullets for Hamby 44 and Hamby 252 are fired from the same ten consecutively rifled P-85 Ruger barrels.
-The difference in parameter settings is therefore quite surprising.
-As next steps we need validation studies - trying out the CMPS algorithm on firearms and ammunition combinations that are different to test the limits of the algorithm.
-The evaluation framework we proposed based on the sum of squares ratio will facilitate such studies and other validation of the algorithm.}
-
-\wj{Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.}
-
-\wj{The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards in the framework of open science.
+The difference in parameter settings for optimal differentiation between same-source comparisons and different-source comparisons is therefore quite surprising.
+As next steps we need validation studies, similar to @vanderplas - trying out the CMPS algorithm on firearms and ammunition combinations that are different to test the limits of the algorithm.
+The evaluation framework we proposed based on the sum of squares ratio will facilitate such studies and other validation of the algorithm.
+
+Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.
+
+The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards in the framework of open science.
 Open science is particularly important to fields like forensic science where transparency and accuracy are critical to fair justice.
@@
 The evaluation metric we proposed in this paper can be used to compare different algorithms or even different datasets and is a snippet of this open system. 
-But the core of this open system is the open science culture and contributions of the community.}
+But the core of this open system is the open science culture and contributions of the community.
 

### 2021-10-28 ju-hofmann/ju-hofmann.tex
final proofread?

@@
 According to the Uniform Crime Reporting Program of FBI (Federal Bureau
-of Investigation), ``More than 73 percent (73.7) of the homicides for
-which the FBI received weapons data in 2019 involved the use of
-firearms'' \citep{fbiucr}, and firearm examination could play an
-important role in all these cases. \textbackslash hh\{XXX the new data
-for 2020 came out on Sep 27 - homicides are up by close to 30\%. We
-might want to mention that.\} An important task of firearm examination
-is to answer the question of whether two pieces of evidence come from
-the same source or whether a piece of evidence matches a sample obtained
-from a specific firearm. Here, in particular, we are interested to
-determine whether two bullets were fired from the same gun barrel.
-Assessing the similarity between two bullets is based on a comparison of
-striation marks acquired during the firing process as bullets are
-propelled through the barrel. Current state of art sees firearms
-examiners make an assessment of similarity based on a visual comparison,
-generally, using a comparison microscope \citep{afte}. This practice has
-been criticized for its lack of objectivity and the associated problem
-of determining valid error rates \citep{pcast}.
+of Investigation), ``more than 76 percent (76.7) of the homicides for
+which the FBI received weapons data in 2020
+\hh{is this really 2020 or should it be 2019?}involved the use of
+firearms'', and the number of cases that involved the use of firearms in
+2020 increased by close to 30 percent (29.3) compared to that in 2019
+\citep{fbiucr}. Firearm examination could play an important role in all
+these cases. An important task of firearm examination is to answer the
+question of whether two pieces of evidence come from the same source or
+whether a piece of evidence matches a sample obtained from a specific
+firearm. Here, in particular, we are interested to determine whether two
+bullets were fired from the same gun barrel. Assessing the similarity
+between two bullets is based on a comparison of striation marks acquired
+during the firing process as bullets are propelled through the barrel.
+Current state of art sees firearms examiners make an assessment of
+similarity based on a visual comparison, generally, using a comparison
+microscope \citep{afte}. This practice has been criticized for its lack
+of objectivity and the associated problem of determining valid error
+rates \citep{pcast}.
 
@@
 databases and develop frameworks and algorithms that bring an objective
-and quantitative assessment into the field
-\hh{XXX could you summarize the main contribution of each of these papers in at most a sentence?}
-\citetext{\citealp[\citet{brundage}, \citet{hamby}, \citet{Hamby:2019},
-\citet{song2005}, \citet{ChumbleyL_Scott2010VoTM}, \citet{aoas},
-\citet{pmid30444940}]{nistdb}; \citealp{cmps}}. Note that this is not an
-exhaustive list of these efforts. The notion of bullet signatures is one
-of the results of these efforts. Bullet signatures can be extracted from
+and quantitative assessment into the field. The database of
+\citet{nistdb} with digital 3d topographic scans from various studies by
+\citet{brundage}, \citet{hamby}, \citet{Hamby:2019} and others, provides
+a great resource for researchers. Algorithms that can be validated and
+tested and generate quantitative results are developed for 2D and 3D
+surface texture \citep{song2005}, tool marks
+\citep{ChumbleyL_Scott2010VoTM}, and striae on Land Engraved Areas
+(LEAs) of bullets \citep[\citet{pmid30444940}, \citet{cmps}]{aoas}. The
+notion of bullet signatures is one of the results of these efforts, and
+we will use it to explain the CMPS algorithm and showcase the
+\pkg{cmpsR} implementation. Bullet signatures can be extracted from
 bullet land engraved areas (LEAs), typically one for each land engraved
 area, and how those bullet signatures are extracted from scans will be
-discussed in the Background section. Since bullet signatures can
-numerically describe the striation marks on the bullet and can be
-understood by algorithms, they played an important role in bringing
-objectivity into the field. In the following sections we will: review
-the background of bullet signature comparisons, discuss how we followed
-the idea described by \citet{cmps} for the implementation of the CMPS
-algorithm, propose new metrics based on the CMPS score and a principled
-evaluation framework for algorithmic results comparison, and present
-results of applying our implementation to real data.
+discussed in the Background section. Bullet signatures capture striation
+marks on the bullet in a numeric format and therefore serve as the
+foundation for algorithms. These scans played an important role in
+bringing objectivity into the field. In the following sections we will:
+review the background of bullet signature comparisons, discuss how we
+followed the idea described by \citet{cmps} for the implementation of
+the CMPS algorithm, propose new metrics based on the CMPS score and a
+principled evaluation framework for algorithmic results comparison, and
+present results of applying our implementation to real data.
 
@@
 better separation on one data set than another, we can scale the sum of
-squares ratio \(V\) and obtain the F-statistic to compare the p-values.
+squares ratio \(V\) and obtain the F-statistic and obtain the
+corresponding p-value as an index for comparison.
 
@@
 able to construct a pipeline that aims to find the optimal parameter
-value for the CMPS algorithm by maximizing the sum of squares ratio. In
-the following section, we will use this ratio to compare the CMPS
-metrics introduced earlier and investigate effects of different sets of
-parameters.
+values for the CMPS algorithm by maximizing the sum of squares ratio.
+Note that other measures of an algorithm, such as the accuracy and the
+AUC (Area Under the Curve), are also important and useful. But when
+algorithms achieve 100 percent accuracy and AUC value of 1, we need
+other measures such as the sum of squares ratio to further distinguish
+the performance of algorithms. In the following section, we will use the
+sum of squares ratio to compare the CMPS metrics introduced earlier and
+investigate effects of different parameter settings.
 
@@
 stated in the paper, we presume this to be Hamby 252, as only those
-scans were publicly available at the time. In order to show that our
-implementation of the CMPS algorithm is able to reproduce the results in
-\citet{cmps} and be used for other data sets, we applied our
-implementation to both Hamby set 252 and Hamby set 44. For the purpose
-of reproducibility, we present how we obtained bullet signatures from
-the Hamby set data and include code in the appendix: for both Hamby 252
-and Hamby 44, we started with scans in the form of x3p files in the
-database. Following the framework proposed by \citet{aoas}, we used the
-same set of parameters, removed damaged bullet scans, obtained bullet
-signatures for each bullet land engraving, and removed outliers in
-bullet signatures. Note that researchers of \citet{cmps} applied the
-CMPS algorithm to bullet signatures as well but used a framework
-different from ours. However, since their work is not open-source, we
-were not able to follow their framework and were only able to reproduce
-the results for Hamby set 252 qualitatively.
+scans were publicly available at the time.
+\hh{XXX Let's take out this statement once we hear back from NIST} In
+order to show that our implementation of the CMPS algorithm is able to
+reproduce the results in \citet{cmps} and be used for other data sets,
+we applied our implementation to both Hamby set 252 and Hamby set 44.
+For the purpose of reproducibility, we present how we obtained bullet
+signatures from the Hamby set data and include code in the appendix: for
+both Hamby 252 and Hamby 44, we started with scans in the form of x3p
+files in the database. Following the framework proposed by \citet{aoas},
+we used the same set of parameters, removed damaged bullet scans,
+obtained bullet signatures for each bullet land engraving, and removed
+outliers in bullet signatures. Note that researchers of \citet{cmps}
+applied the CMPS algorithm to bullet signatures as well but used a
+framework different from ours. However, since their work is not
+open-source, we were not able to follow their framework and were only
+able to reproduce the results for Hamby set 252 qualitatively.
 
@@
 
-\hh{XXX Will, the conclusion needs to be a bit more than just a summary of what we did in the paper - think of it as a summary plus either the limitations of our approach, or next steps that should be done but goes beyond this paper.}
-
 In this paper we present the \pkg{cmpsR} package, an open-source
@@
 
-\wj{Additionally, we propose new metrics based on the CMPS scores and compare the new metrics with the existing metrics. 
-We also introduce a principled evaluation framework of algorithmic results using  a measure based on the sum of squares ratio. 
-We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
-}
-
-The results obtained are promising: we were both able to reproduce the
-results in \citet{cmps} qualitatively and achieve a clear separation
-between the known match (KM) comparisons and known non-match (KNM)
-comparisons in another bullet study.
-\wj{However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.
-We propose an evaluation framework that allows a comprehensive cross-validation of parameter settings used in the algorithm for future research.
-Comparisons of the R implementation of the CMPS algorithm with the random forest model proposed by @aoas  suggest that adding the CMPS score as an additional feature in the random forest model might add further separation between known match (KM) comparisons and known non-match (KNM) comparisons.}
-
-\wj{The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards in the framework of open science.
-Open science is particularly important to fields like forensic science where transparency and accuracy are critical to fair justice.
-Open-source implementations not only allow a peer-review but also facilitate further research, such as parameter cross-validations, method comparisons, and the development of statistical methods for modeling KM and KNM CMPS score distributions, which can then be used for error-rate estimations and fair applications that were called for by the PCAST [@pcast] report.
-However, having open-source implementations is not enough for open science. 
-In order to actually build the world of open science, many other efforts, such as open evaluation, open access publication, open educational resources, etc., are still needed. 
-The database built and maintained by the National Institute of Standards and Technology is a good example of open data. 
-What we are aiming for is an open system that is able to collect open results, compare multiple algorithms using multiple datasets, and evaluate algorithmic variation and accuracy. 
-The evaluation metric we proposed in this paper can be used to compare different algorithms or even different datasets and is a snippet of this open system. 
-But the core of this open system is the open science culture and contributions of the community.}
+Additionally, we propose two new metrics based on the CMPS scores and
+compare the new metrics with the existing metrics. We also introduce a
+principled evaluation framework of algorithmic results using a measure
+based on the sum of squares ratio. We showcase the implementation with
+two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare
+the CMPS algorithm using different sets of parameters and different
+metrics, following the evaluation framework based on the sum of squares
+ratio. The results obtained are promising: we were both able to
+reproduce the results in \citet{cmps} qualitatively and achieve a clear
+separation between the known match (KM) comparisons and known non-match
+(KNM) comparisons in another bullet study. However, the comparisons
+among different sets of parameters suggest that the optimal choice for
+parameter settings vary between different datasets.
+
+Note, that the main difference between Hamby sets 44 and 252 is that
+they were taken with different resolution scanning devices. The bullets
+for Hamby 44 and Hamby 252 are fired from the same ten consecutively
+rifled P-85 Ruger barrels. The difference in parameter settings for
+optimal differentiation between same-source comparisons and
+different-source comparisons is therefore quite surprising. As next
+steps we need validation studies, similar to \citet{vanderplas} - trying
+out the CMPS algorithm on firearms and ammunition combinations that are
+different to test the limits of the algorithm. The evaluation framework
+we proposed based on the sum of squares ratio will facilitate such
+studies and other validation of the algorithm.
+
+Comparisons of the R implementation of the CMPS algorithm with the
+random forest model proposed by \citet{aoas} suggest that adding the
+CMPS score as an additional feature in the random forest model might add
+further separation between known match (KM) comparisons and known
+non-match (KNM) comparisons.
+
+The open-source implementation of the CMPS algorithm provided by the
+\pkg{cmpsR} package is just one step towards in the framework of open
+science. Open science is particularly important to fields like forensic
+science where transparency and accuracy are critical to fair justice.
+Open-source implementations not only allow a peer-review but also
+facilitate further research, such as parameter cross-validations, method
+comparisons, and the development of statistical methods for modeling KM
+and KNM CMPS score distributions, which can then be used for error-rate
+estimations and fair applications that were called for by the PCAST
+\citep{pcast} report. However, having open-source implementations is not
+enough for open science. In order to actually build the world of open
+science, many other efforts, such as open evaluation, open access
+publication, open educational resources, etc., are still needed. The
+database built and maintained by the National Institute of Standards and
+Technology is a good example of open data. What we are aiming for is an
+open system that is able to collect open results, compare multiple
+algorithms using multiple datasets, and evaluate algorithmic variation
+and accuracy. The evaluation metric we proposed in this paper can be
+used to compare different algorithms or even different datasets and is a
+snippet of this open system. But the core of this open system is the
+open science culture and contributions of the community.
 

### 2021-10-28 ju-hofmann/ju-hofmann.R

@@ -943,10 +943,11 @@ p.npeak_plot <- table.cmps_neapk.long %>%
 
 p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max", 
                          subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
-  xlab(labels[3])
+  xlab(labels[1])
 p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
                          subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
   xlab(labels[4])
+
 p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
                common.legend = TRUE, legend = "bottom")
 p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
@@ -966,7 +967,7 @@ p.result1_252
 ## ----result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE----
 p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
                          subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
-  xlab(labels[3])
+  xlab(labels[1])
 p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
                          subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
   xlab(labels[4])

### 2021-10-28 ju-hofmann/ju-hofmann.Rmd
clarification

@@
 XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
-According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 \hh{is this really 2020 or should it be 2019?}involved the use of firearms", and the number of cases that involved the use of firearms in 2020 increased by close to 30 percent (29.3) compared to that in 2019 [@fbiucr].
-Firearm examination could play an important role in all these cases.
+According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms".
+[@fbiucr] At the same time, the number of homicides jumped between 2019 and 2020 by more than \hh{XXX} percent (\hh{XXX}).
+This increase is unprecedented  and highlights the important role that  firearm examination plays in all these cases.
 An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.

### 2021-11-11 ju-hofmann/ju-hofmann.Rmd
added 2020 fbi ucr citation; update with package publication on CRAN

@@
 
-<!-- According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 73 percent (73.7) of the homicides for which the FBI received weapons data in 2019 involved the use of firearms" [@fbiucr], and firearm examination could play an important role in all these cases.
--->
-<!-- \hh{XXX the new data for 2020 came out on Sep 27 - homicides are up by close to 30%. We might want to mention that.} -->
 <!-- https://s3-us-gov-west-1.amazonaws.com/cg-d4b776d0-d898-4153-90c8-8336f86bdfec/CIUS/downloads/2020/expanded-homicide-2020.zip -->
@@
 XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
-According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms".
-[@fbiucr] At the same time, the number of homicides jumped between 2019 and 2020 by more than \hh{XXX} percent (\hh{XXX}).
+According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms" [@fbiucr].
+At the same time, the number of murder victims jumped between 2019 and 2020 by more than 23 percent (23.4) to 17754 [@fbiucr20].
 This increase is unprecedented  and highlights the important role that  firearm examination plays in all these cases.
+<!-- homicides in 2019: 14391; in 2020: 17754 -->
 An important task of firearm examination is to answer the question of whether two pieces of evidence come from the same source or whether a piece of evidence matches a sample obtained from a specific firearm.
@@
 
-<!-- \hh{XXX could you summarize the main contribution of each of these papers in at most a sentence?} -->
 A report published by the @nrc states that "[m]uch forensic evidence-including, for example, bite marks and firearm and toolmark identification---is introduced in criminal trials without any meaningful scientific validation, determination of error rates, or reliability testing to explain the limits of the discipline." To overcome those criticisms and concerns, researchers have been making an effort to build databases and develop frameworks and algorithms that bring an objective and quantitative assessment into the field.
-The database of @nistdb with digital 3d topographic scans from various studies by @brundage, @hamby, @Hamby:2019 and others, provides a great resource for researchers.
+The database of @nistdb with digital 3D topographic scans from various studies by @brundage, @hamby, @Hamby:2019 and others, provides a great resource for researchers.
 Algorithms that can be validated and tested and generate quantitative results are developed for 2D and 3D surface texture [@song2005], tool marks [@ChumbleyL_Scott2010VoTM], and striae on Land Engraved Areas (LEAs) of bullets [@aoas, @pmid30444940, @cmps].
@@
 \autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.
-\autoref{fig:process}(a) shows a rendering of a 3d scan of a bullet land engraved area.
+\autoref{fig:process}(a) shows a rendering of a 3D scan of a bullet land engraved area.
 The raised portion of the surface on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs), the middle area shows a land-engraved area (LEA) with well expressed striation marks.
@@
 ```{r process, echo=FALSE, out.width=".9\\textwidth", fig.cap="A framework of obtaining a bullet signature.
-(a) rendering from the 3d topographic scan of a land engraved area (LEA).
+(a) rendering from the 3D topographic scan of a land engraved area (LEA).
 The selected crosscut location is indicated by a thin white horizontal line.
@@
 <!--Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.-->
-Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from Github \url{https://github.com/willju-wangqian/cmpsR}.
+Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github \url{https://github.com/willju-wangqian/cmpsR}.
 This publicly available implementation calculates the CMPS score of a comparison using the following code:
@@
 ```{r, eval=FALSE}
-# install.packages("devtools") 
-# devtools::install_github("willju-wangqian/CMPS")
+# install.packages("cmpsR")
 
@@
 Results from Hamby 44 show the need for a further investigation of the parameter choices even in the case of bullets fired from the same barrels.
-<!-- \hh{We suggest a sum of square ratio ...} -->
 The last section covers some final discussion and conclusions.
@@
 
-The \pkg{cmpsR} package is not publicly available from CRAN yet, and its development version is available from Github and can be installed by
+The \pkg{cmpsR} package is publicly available from CRAN and can be installed by
+
+```{r, eval=FALSE}
+install.packages("cmpsR") 
+```
+
+Moreover, its development version is also available from Github and can be installed by
 
@@
 Let $c_{ij}$ denote the CMPS score of a comparison between bullet 1 land $i$ and bullet 2 land $j$, for $i,j = 1, \dots, n$.
-Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and $\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}$, where $\mathbbm{1}_A$ denotes an indicator function.
+Let $\mathcal{P}_k$ denote bullet land pairs in phase $k$ for $k = 0, \dots, n-1$, and
+
+```{=tex}
+\begin{align}
+\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; \; j = (i + k) \;\mathrm{mod}\; n \}
+\end{align}
+```
+
+, where `mod` denotes the modulo operation.
 For example, $\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}$ when $n = 6$.
@@
 Land engraving pairs generated by the same land (KM comparisons) are highlighted.
-\\hh{Note that in this example the axis along Bullet 2 starts with Land 2.
-This corresponds to Phase 2 in equation XXX}", out.width=".7\\textwidth", fig.align="center"}
+Note that in this example the axis along Bullet 2 starts with Land 2.
+This corresponds to Phase 1 in equation (1).", out.width=".7\\textwidth", fig.align="center"}
 dframe <- dframe %>% mutate(
@@
 While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time.
-\hh{XXX Let's take out this statement once we hear back from NIST}
+(We have asked the authors of @cmps, and we are still waiting for the replies.)
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.

### 2021-11-11 code/plot_generation.R

@@ -1,4 +1,4 @@
-library(CMPS)
+library(cmpsR)
 library(tidyverse)
 library(bulletxtrctr)
 library(x3ptools)
@@ -30,7 +30,8 @@ comparisons <- comparisons %>%
 comparisons <- comparisons %>% 
   mutate(
     cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
-    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
+    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg),
+    cmps_scaled = cmps_score / cmps_nseg
   )
 
 # dframe <- comparisons %>% select(land1, land2, cmps_score)
@@ -52,8 +53,17 @@ comparisons <- comparisons %>%
     bulletA = gsub("(\\d)-\\d", "\\1", land1),
     landA = gsub("\\d-(\\d)", "\\1", land1),
     bulletB = gsub("(\\d)-\\d", "\\1", land2),
-    landB = gsub("\\d-(\\d)", "\\1", land2)
+    landB = gsub("\\d-(\\d)", "\\1", land2),
+    
   )
+
+comparisons <- comparisons %>% mutate(
+  landA = paste0("L", landA),
+  landB = paste0("L", landB),
+  landB = factor(landB, levels = paste0("L", c(2:6,1))),
+  bulletA = paste0("Bullet ", bulletA),
+  bulletB = paste0("Bullet ", bulletB)
+)
 
 comparisons %>%   
   group_by(bulletA, bulletB) %>% tidyr::nest() %>%
@@ -66,11 +76,11 @@ comparisons %>%
 
 dframe <- comparisons %>% select(-aligned, -cmps)
 
-dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + geom_tile() + 
-  scale_fill_gradient2(low = "gray80", high = "darkorange", midpoint = 6) + 
+dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_scaled)) + geom_tile() + 
+  scale_fill_gradient2(low = "gray80", high = "darkorange", midpoint = 0.4) + 
   facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
   ylab("Land A") + theme(aspect.ratio = 1) +
-  geom_text(aes(label=cmps_score)) +
+  geom_text(aes(label=round(cmps_scaled, 2))) +
   theme_bw()
 
 

### 2021-11-18 cover_letter/cover_letter.Rmd
re-structure reproducibility folder, check point 1

--- 2021-10-13 cover_letter.Rmd
@@
 ---
-title: "cover_letter"
-author: "xxx"
+title: "Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets"
+author: "Wangqian Ju and Heike Hofmann"
 date: "10/13/2021"
-output: html_document
+output:
+  pdf_document: default
+  html_document: default
 ---
-
-## Cover Letter
 
@@
 Wangqian Ju and Heike Hofmann
+
+Below is an explanation of non-standard files/folders included with the submission.
+
++   **data** folder: contains data to demonstrate the cmpsR package and reproduce various results in the paper. 
++   **reproducible** folder: contains R scripts and data necessary to reproduce all aspects of this submission.
++   **ju-hofmann_files/figure-latex** folder: contains figures and plots used in the paper

### 2021-11-18 reproducible/rda_generator.R

@@ -1,0 +1,329 @@
+###############################
+# Note: Please set the working 
+# directory so that "./data-csv/"
+# is available
+###############################
+
+###############################
+# for the random forest model
+rf.results <- list()
+rf.results[[1]] <- read.csv(file = "./data-csv/hamby252/hamby252_rf_results.csv")
+rf.results[[2]] <- read.csv(file = "./data-csv/hamby44/hamby44_rf_results.csv")
+
+###############################
+# hamby 252 segments
+N <- 8 # the number of different sets of parameters
+CMPS_hamby252_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
+CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
+# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
+
+#### setup npeaks.set
+CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
+
+#### setup seg_length
+CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
+
+#### setup Tx
+CMPS_hamby252_results$Tx <- as.list(rep(25, N))
+
+#### setup outlength
+CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
+
+#### create a plot title and a file name for each set of parameters
+CMPS_hamby252_results$titlee <- list()
+CMPS_hamby252_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby252_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby252_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby252_results$filename[[i]] <- 
+    paste(
+      "hamby252_segment",
+      CMPS_hamby252_results$span1[[i]]*100,
[…]

### 2021-11-18 ju-hofmann/ju-hofmann.Rmd
re-structure reproducible folder, completed

@@
 
-source("../code/func_collection.R")
+# source("../code/func_collection.R")
 
@@
 #  cache=TRUE,
-  dpi = 100,
+  dpi = 144,
   warning = FALSE,
@@
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-Our implementation is made available as part of the `R` package \pkg{cmpsR} on GitHub at \url{https://github.com/willju-wangqian/cmpsR}.
+<!-- Our implementation is made available as part of the `R` package \pkg{cmpsR} on GitHub at \url{https://github.com/willju-wangqian/cmpsR}. -->
+\wj{change}
+Our implementation is made available as part of the `R` package \pkg{cmpsR} on CRAN.
 
@@
 Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
+\wj{can be found in the supplementary materials of this paper? }
 
@@
 # knitr::include_graphics("img/barrel_bullet_ps.png", dpi = 100)
-knitr::include_graphics("ju-hofmann_files/figure-latex/barrel_bullet_ps.png", dpi = 100)
+knitr::include_graphics("ju-hofmann_files/figure-latex/barrel_bullet_ps.png", dpi = 144)
 ```
@@
 (f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
-knitr::include_graphics("ju-hofmann_files/figure-latex/figure1_v2.png", dpi = 100)
+knitr::include_graphics("ju-hofmann_files/figure-latex/figure1_v2.png", dpi = 144)
 ```
@@
 The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
-<!--Unfortunately, @cmps did not release any code or specific parameter settings for their implementation of the CMPS algorithm.-->
 Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github \url{https://github.com/willju-wangqian/cmpsR}.
 This publicly available implementation calculates the CMPS score of a comparison using the following code:
+\wj{ignore github?}
 
@@
 For the example above, $\mathrm{\overline{CMPS}_{diff}} = 12.5 - 1.53 = 10.97$ <br>
-
-<!-- ??? We shouldn't talk about the median version, should we? -->
-
-<!-- \wj{Instead of computing the mean CMPS scores of matching and non-matching comparisons, a variation of $\mathrm{\overline{CMPS}_{diff}}$ is to compute the median CMPS scores of matching and non-matching comparisons.
-Computing the median could be beneficial if extreme values are observed for non-matching comparisons.
-More examples are provided in the Results section} -->
 
@@
 
-```{r hamby252-data-seg, eval=TRUE, echo=FALSE}
-# for hamby 252
-N <- 8 # the number of different sets of parameters
-CMPS_hamby252_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
-  # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
-
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
-
-#### setup seg_length
-CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
-
-#### setup Tx
-CMPS_hamby252_results$Tx <- as.list(rep(25, N))
-
-#### setup outlength
-CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby252_results$titlee <- list()
-CMPS_hamby252_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby252_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby252_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby252_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby252_results$filename[[i]] <- 
-    paste(
-      "hamby252_segment",
-      CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby252_results$seg_length[[i]],
-      CMPS_hamby252_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby252_results$cmps.table <- list()
-CMPS_hamby252_results$plot <- list()
+```{r load-results, eval=TRUE, echo=FALSE}
+all_results_container <- readRDS("data/CMPSpaper_results.rds")
+
+CMPS_hamby252_results_seg <- all_results_container$h252_seg
+CMPS_hamby252_results_npeak <- all_results_container$h252_npeak
+CMPS_hamby44_results_seg <- all_results_container$h44_seg
+CMPS_hamby44_results_npeak <- all_results_container$h44_npeak
+rf.results <- all_results_container$rf
+
+#### a global title for Hamby44 plots
+com.title44 <- expression(paste(
+  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
+))
 
@@
 ))
-
-for(i in 1:N){
-  CMPS_hamby252_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby252/", 
-                        CMPS_hamby252_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby252_results_seg <- CMPS_hamby252_results
-
-```
-
-```{r hamby252-data-npeak, eval=TRUE, echo=FALSE}
-N <- 8 # the number of different sets of parameters
-CMPS_hamby252_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
-# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
-
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- 
-  list(c(5),
-       c(5,2),
-       c(5,3,1),
-       c(10,6,2),
-       c(6,4,2,1),
-       c(10,7,4,2),
-       c(10,6,4,2,1),
-       c(10,8,6,4,2,1))
-
-#### setup seg_length
-CMPS_hamby252_results$seg_length <- 
-  # as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
-  as.list(rep(50, N))
-
-#### setup Tx
-CMPS_hamby252_results$Tx <- as.list(rep(25, N))
-
-#### setup outlength
-CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
-CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180)
-CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200)
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby252_results$titlee <- list()
-CMPS_hamby252_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby252_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby252_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby252_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby252_results$filename[[i]] <- 
-    paste(
-      "hamby252_npeak",
-      CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby252_results$seg_length[[i]],
-      CMPS_hamby252_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby252_results$cmps.table <- list()
-CMPS_hamby252_results$plot <- list()
-
-#### a global title for Hamby252 plots
-com.title252 <- expression(paste(
-  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby252_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby252/", 
-                        CMPS_hamby252_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby252_results_npeak <- CMPS_hamby252_results
-
-```
-
-```{r hamby44-data-seg, eval=TRUE, echo=FALSE}
-N <- 8 # the number of different sets of parameters
-CMPS_hamby44_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby44_results$signame <-
-  as.list(rep("sigs25_531", N))
-
-#### setup neapks.set
-CMPS_hamby44_results$npeaks.set <-
-  lapply(1:N, function(t) c(5,3,1))
-
-#### setup seg_length
-CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210))
-
-#### setup outlength
-CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
-
-#### setup Tx
-CMPS_hamby44_results$Tx <- as.list(rep(30, N))
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby44_results$titlee <- list()
-CMPS_hamby44_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby44_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby44_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby44_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby44_results$filename[[i]] <- 
-    paste(
-      "hamby44_segment",
-      CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby44_results$seg_length[[i]],
-      CMPS_hamby44_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby44_results$cmps.table <- list()
-CMPS_hamby44_results$plot <- list()
-
-#### a global title for Hamby44 plots
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby44_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby44/", 
-                        CMPS_hamby44_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby44_results_seg <- CMPS_hamby44_results
-
-```
-
-```{r hamby44-data-npeak, eval=TRUE, echo=FALSE}
-N <- 8 # the number of different sets of parameters
-CMPS_hamby44_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby44_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby44_results$signame <-
-  as.list(rep("sigs25_531", N))
-
-#### setup neapks.set
-CMPS_hamby44_results$npeaks.set <-
-  list(c(5),
-       c(5,2),
-       c(5,3,1),
-       c(10,6,2),
-       c(6,4,2,1),
-       c(10,7,4,2),
-       c(10,6,4,2,1),
-       c(10,8,6,4,2,1))
-
-#### setup seg_length
-CMPS_hamby44_results$seg_length <- as.list(rep(61, N))
-
-#### setup outlength
-CMPS_hamby44_results$outlength <- vector(mode = "list", length = N)
-CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181)
-CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211)
-
-#### setup Tx
-CMPS_hamby44_results$Tx <- as.list(rep(30, N))
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby44_results$titlee <- list()
-CMPS_hamby44_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby44_results$titlee[[i]] <-
-    paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby44_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby44_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby44_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby44_results$filename[[i]] <- 
-    paste(
-      "hamby44_npeak",
-      CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
-      CMPS_hamby44_results$seg_length[[i]],
-      CMPS_hamby44_results$Tx[[i]],
-      sep = "_"
-    )
-}
-
-#### container for the cmps results and corresponding plots
-CMPS_hamby44_results$cmps.table <- list()
-CMPS_hamby44_results$plot <- list()
-
-#### a global title for Hamby44 plots
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
-
-for(i in 1:N){
-  CMPS_hamby44_results$cmps.table[[i]] <- 
-  read.csv(file = paste("./data/hamby44/", 
-                        CMPS_hamby44_results$filename[[i]], 
-                        ".csv",
-                        sep = ""))
-}
-
-CMPS_hamby44_results_npeak <- CMPS_hamby44_results
-```
-
-```{r rf-data-load, echo=FALSE}
-rf.results <- list()
-rf.results[[1]] <- read.csv(file = "./data/hamby252/hamby252_rf_results.csv")
-rf.results[[2]] <- read.csv(file = "./data/hamby44/hamby44_rf_results.csv")
-
+```
+
+<!-- ```{r hamby252-data-seg, eval=TRUE, echo=FALSE} -->
+<!-- # for hamby 252 -->
+<!-- N <- 8 # the number of different sets of parameters -->
+<!-- CMPS_hamby252_results <- list() # a container for everything -->
+
+<!-- #### setup span1 -->
+<!-- CMPS_hamby252_results$span1 <- as.list(rep(0.25, N)) -->
+
+<!-- #### setup signature name -->
+<!-- CMPS_hamby252_results$signame <- as.list(rep("sigs25", N)) -->
+<!--   # list("sigs75", "sigs25", "sigs25_1062", "sigs15") -->
+
+<!-- #### setup npeaks.set -->
+<!-- CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1)) -->
+
+<!-- #### setup seg_length -->
+<!-- CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200)) -->
+
+<!-- #### setup Tx -->
+<!-- CMPS_hamby252_results$Tx <- as.list(rep(25, N)) -->
+
+<!-- #### setup outlength -->
+<!-- CMPS_hamby252_results$outlength <- vector(mode = "list", length = N) -->
+
+<!-- #### create a plot title and a file name for each set of parameters -->
+<!-- CMPS_hamby252_results$titlee <- list() -->
+<!-- CMPS_hamby252_results$filename <- list() -->
+<!-- for (i in 1:N) { -->
+<!--   CMPS_hamby252_results$titlee[[i]] <- -->
+<!--     paste0( -->
+<!--       "npeaks.set=c(", -->
+<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","), -->
+<!--       ")", -->
+<!--       ", len=", -->
+<!--       CMPS_hamby252_results$seg_length[[i]], -->
+<!--       ", Tx=", -->
+<!--       CMPS_hamby252_results$Tx[[i]], -->
+<!--       ", \nspan1=", -->
+<!--       CMPS_hamby252_results$span1[[i]], -->
+<!--       ", span2=0.03" -->
+<!--     ) -->
+<!--   CMPS_hamby252_results$filename[[i]] <-  -->
+<!--     paste( -->
+<!--       "hamby252_segment", -->
+<!--       CMPS_hamby252_results$span1[[i]]*100, -->
+<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"), -->
+<!--       CMPS_hamby252_results$seg_length[[i]], -->
+<!--       CMPS_hamby252_results$Tx[[i]], -->
+<!--       sep = "_" -->
+<!--     ) -->
+<!-- } -->
+
+<!-- #### container for the cmps results and corresponding plots -->
+<!-- CMPS_hamby252_results$cmps.table <- list() -->
+<!-- CMPS_hamby252_results$plot <- list() -->
+
+<!-- #### a global title for Hamby252 plots -->
+<!-- com.title252 <- expression(paste( -->
+<!--   "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
+<!-- )) -->
+
+<!-- for(i in 1:N){ -->
+<!--   CMPS_hamby252_results$cmps.table[[i]] <-  -->
+<!--   read.csv(file = paste("./data/hamby252/",  -->
+<!--                         CMPS_hamby252_results$filename[[i]],  -->
+<!--                         ".csv", -->
+<!--                         sep = "")) -->
+<!-- } -->
+
+<!-- CMPS_hamby252_results_seg <- CMPS_hamby252_results -->
+
+<!-- ``` -->
+
+<!-- ```{r hamby252-data-npeak, eval=TRUE, echo=FALSE} -->
+<!-- N <- 8 # the number of different sets of parameters -->
+<!-- CMPS_hamby252_results <- list() # a container for everything -->
+
+<!-- #### setup span1 -->
+<!-- CMPS_hamby252_results$span1 <- as.list(rep(0.25, N)) -->
+
+<!-- #### setup signature name -->
+<!-- CMPS_hamby252_results$signame <- as.list(rep("sigs25", N)) -->
+<!-- # list("sigs75", "sigs25", "sigs25_1062", "sigs15") -->
+
+<!-- #### setup npeaks.set -->
+<!-- CMPS_hamby252_results$npeaks.set <-  -->
+<!--   list(c(5), -->
+<!--        c(5,2), -->
+<!--        c(5,3,1), -->
+<!--        c(10,6,2), -->
+<!--        c(6,4,2,1), -->
+<!--        c(10,7,4,2), -->
+<!--        c(10,6,4,2,1), -->
+<!--        c(10,8,6,4,2,1)) -->
+
+<!-- #### setup seg_length -->
+<!-- CMPS_hamby252_results$seg_length <-  -->
+<!--   # as.list(c(25, 50, 75, 100, 125, 150, 175, 200)) -->
+<!--   as.list(rep(50, N)) -->
+
+<!-- #### setup Tx -->
+<!-- CMPS_hamby252_results$Tx <- as.list(rep(25, N)) -->
+
+<!-- #### setup outlength -->
+<!-- CMPS_hamby252_results$outlength <- vector(mode = "list", length = N) -->
+<!-- CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180) -->
+<!-- CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200) -->
+
+<!-- #### create a plot title and a file name for each set of parameters -->
+<!-- CMPS_hamby252_results$titlee <- list() -->
+<!-- CMPS_hamby252_results$filename <- list() -->
+<!-- for (i in 1:N) { -->
+<!--   CMPS_hamby252_results$titlee[[i]] <- -->
+<!--     paste0( -->
+<!--       "npeaks.set=c(", -->
+<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","), -->
+<!--       ")", -->
+<!--       ", len=", -->
+<!--       CMPS_hamby252_results$seg_length[[i]], -->
+<!--       ", Tx=", -->
+<!--       CMPS_hamby252_results$Tx[[i]], -->
+<!--       ", \nspan1=", -->
+<!--       CMPS_hamby252_results$span1[[i]], -->
+<!--       ", span2=0.03" -->
+<!--     ) -->
+<!--   CMPS_hamby252_results$filename[[i]] <-  -->
+<!--     paste( -->
+<!--       "hamby252_npeak", -->
+<!--       CMPS_hamby252_results$span1[[i]]*100, -->
+<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"), -->
+<!--       CMPS_hamby252_results$seg_length[[i]], -->
+<!--       CMPS_hamby252_results$Tx[[i]], -->
+<!--       sep = "_" -->
+<!--     ) -->
+<!-- } -->
+
+<!-- #### container for the cmps results and corresponding plots -->
+<!-- CMPS_hamby252_results$cmps.table <- list() -->
+<!-- CMPS_hamby252_results$plot <- list() -->
+
+<!-- #### a global title for Hamby252 plots -->
+<!-- com.title252 <- expression(paste( -->
+<!--   "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
+<!-- )) -->
+
+<!-- for(i in 1:N){ -->
+<!--   CMPS_hamby252_results$cmps.table[[i]] <-  -->
+<!--   read.csv(file = paste("./data/hamby252/",  -->
+<!--                         CMPS_hamby252_results$filename[[i]],  -->
+<!--                         ".csv", -->
+<!--                         sep = "")) -->
+<!-- } -->
+
+<!-- CMPS_hamby252_results_npeak <- CMPS_hamby252_results -->
+
+<!-- ``` -->
+
+<!-- ```{r hamby44-data-seg, eval=TRUE, echo=FALSE} -->
+<!-- N <- 8 # the number of different sets of parameters -->
+<!-- CMPS_hamby44_results <- list() # a container for everything -->
+
+<!-- #### setup span1 -->
+<!-- CMPS_hamby44_results$span1 <- as.list(rep(0.25, N)) -->
+
+<!-- #### setup signature name -->
+<!-- CMPS_hamby44_results$signame <- -->
+<!--   as.list(rep("sigs25_531", N)) -->
+
+<!-- #### setup neapks.set -->
+<!-- CMPS_hamby44_results$npeaks.set <- -->
+<!--   lapply(1:N, function(t) c(5,3,1)) -->
+
+<!-- #### setup seg_length -->
+<!-- CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210)) -->
+
+<!-- #### setup outlength -->
+<!-- CMPS_hamby44_results$outlength <- vector(mode = "list", length = N) -->
+
+<!-- #### setup Tx -->
+<!-- CMPS_hamby44_results$Tx <- as.list(rep(30, N)) -->
+
+<!-- #### create a plot title and a file name for each set of parameters -->
+<!-- CMPS_hamby44_results$titlee <- list() -->
+<!-- CMPS_hamby44_results$filename <- list() -->
+<!-- for (i in 1:N) { -->
+<!--   CMPS_hamby44_results$titlee[[i]] <- -->
+<!--     paste0( -->
+<!--       "npeaks.set=c(", -->
+<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","), -->
+<!--       ")", -->
+<!--       ", len=", -->
+<!--       CMPS_hamby44_results$seg_length[[i]], -->
+<!--       ", Tx=", -->
+<!--       CMPS_hamby44_results$Tx[[i]], -->
+<!--       ", \nspan1=", -->
+<!--       CMPS_hamby44_results$span1[[i]], -->
+<!--       ", span2=0.03" -->
+<!--     ) -->
+<!--   CMPS_hamby44_results$filename[[i]] <-  -->
+<!--     paste( -->
+<!--       "hamby44_segment", -->
+<!--       CMPS_hamby44_results$span1[[i]]*100, -->
+<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"), -->
+<!--       CMPS_hamby44_results$seg_length[[i]], -->
+<!--       CMPS_hamby44_results$Tx[[i]], -->
+<!--       sep = "_" -->
+<!--     ) -->
+<!-- } -->
+
+<!-- #### container for the cmps results and corresponding plots -->
+<!-- CMPS_hamby44_results$cmps.table <- list() -->
+<!-- CMPS_hamby44_results$plot <- list() -->
+
+<!-- #### a global title for Hamby44 plots -->
+<!-- com.title44 <- expression(paste( -->
+<!--   "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
+<!-- )) -->
+
+<!-- for(i in 1:N){ -->
+<!--   CMPS_hamby44_results$cmps.table[[i]] <-  -->
+<!--   read.csv(file = paste("./data/hamby44/",  -->
+<!--                         CMPS_hamby44_results$filename[[i]],  -->
+<!--                         ".csv", -->
+<!--                         sep = "")) -->
+<!-- } -->
+
+<!-- CMPS_hamby44_results_seg <- CMPS_hamby44_results -->
+
+<!-- ``` -->
+
+<!-- ```{r hamby44-data-npeak, eval=TRUE, echo=FALSE} -->
+<!-- N <- 8 # the number of different sets of parameters -->
+<!-- CMPS_hamby44_results <- list() # a container for everything -->
+
+<!-- #### setup span1 -->
+<!-- CMPS_hamby44_results$span1 <- as.list(rep(0.25, N)) -->
+
+<!-- #### setup signature name -->
+<!-- CMPS_hamby44_results$signame <- -->
+<!--   as.list(rep("sigs25_531", N)) -->
+
+<!-- #### setup neapks.set -->
+<!-- CMPS_hamby44_results$npeaks.set <- -->
+<!--   list(c(5), -->
+<!--        c(5,2), -->
+<!--        c(5,3,1), -->
+<!--        c(10,6,2), -->
+<!--        c(6,4,2,1), -->
+<!--        c(10,7,4,2), -->
+<!--        c(10,6,4,2,1), -->
+<!--        c(10,8,6,4,2,1)) -->
+
+<!-- #### setup seg_length -->
+<!-- CMPS_hamby44_results$seg_length <- as.list(rep(61, N)) -->
+
+<!-- #### setup outlength -->
+<!-- CMPS_hamby44_results$outlength <- vector(mode = "list", length = N) -->
+<!-- CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181) -->
+<!-- CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211) -->
+
+<!-- #### setup Tx -->
+<!-- CMPS_hamby44_results$Tx <- as.list(rep(30, N)) -->
+
+<!-- #### create a plot title and a file name for each set of parameters -->
+<!-- CMPS_hamby44_results$titlee <- list() -->
+<!-- CMPS_hamby44_results$filename <- list() -->
+<!-- for (i in 1:N) { -->
+<!--   CMPS_hamby44_results$titlee[[i]] <- -->
+<!--     paste0( -->
+<!--       "npeaks.set=c(", -->
+<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","), -->
+<!--       ")", -->
+<!--       ", len=", -->
+<!--       CMPS_hamby44_results$seg_length[[i]], -->
+<!--       ", Tx=", -->
+<!--       CMPS_hamby44_results$Tx[[i]], -->
+<!--       ", \nspan1=", -->
+<!--       CMPS_hamby44_results$span1[[i]], -->
+<!--       ", span2=0.03" -->
+<!--     ) -->
+<!--   CMPS_hamby44_results$filename[[i]] <-  -->
+<!--     paste( -->
+<!--       "hamby44_npeak", -->
+<!--       CMPS_hamby44_results$span1[[i]]*100, -->
+<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"), -->
+<!--       CMPS_hamby44_results$seg_length[[i]], -->
+<!--       CMPS_hamby44_results$Tx[[i]], -->
+<!--       sep = "_" -->
+<!--     ) -->
+<!-- } -->
+
+<!-- #### container for the cmps results and corresponding plots -->
+<!-- CMPS_hamby44_results$cmps.table <- list() -->
+<!-- CMPS_hamby44_results$plot <- list() -->
+
+<!-- #### a global title for Hamby44 plots -->
+<!-- com.title44 <- expression(paste( -->
+<!--   "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
+<!-- )) -->
+
+<!-- for(i in 1:N){ -->
+<!--   CMPS_hamby44_results$cmps.table[[i]] <-  -->
+<!--   read.csv(file = paste("./data/hamby44/",  -->
+<!--                         CMPS_hamby44_results$filename[[i]],  -->
+<!--                         ".csv", -->
+<!--                         sep = "")) -->
+<!-- } -->
+
+<!-- CMPS_hamby44_results_npeak <- CMPS_hamby44_results -->
+
+<!-- ``` -->
+
+<!-- ```{r rf-data-load, echo=FALSE} -->
+<!-- rf.results <- list() -->
+<!-- rf.results[[1]] <- read.csv(file = "./data/hamby252/hamby252_rf_results.csv") -->
+<!-- rf.results[[2]] <- read.csv(file = "./data/hamby44/hamby44_rf_results.csv") -->
+<!-- ``` -->
+
+```{r rf-data-process, echo=FALSE}
 rf.tt <- lapply(rf.results, function(rf_result) {
@@
     tibble(rf.diff, rf.max, rf.maxbar) %>% 
-      apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+      apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
   })
@@
     value = purrr::map_dbl(dd.table, function(dd) {
-      compute_var_ratio_anova(dd$score, dd$type_truth, MS = FALSE)
+      compute_ss_ratio(dd$score, dd$type_truth, MS = FALSE)
     })
@@
 While it is not explicitly stated in the paper, we presume this to be Hamby 252, as only those scans were publicly available at the time. 
-(We have asked the authors of @cmps, and we are still waiting for the replies.)
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
@@
   tibble(cmps.max, cmps.maxbar) %>% 
-    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+    apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
 })
@@
   tibble(cmps.max, cmps.maxbar, cmps.diff, cmps.diff_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label = type_truth, MS = FALSE)
+    apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
 })
@@
   tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_var_ratio_anova, label=type_truth, MS=FALSE)
+    apply(2, compute_ss_ratio, label=type_truth, MS=FALSE)
 }) %>% do.call(rbind, .) %>% as.data.frame()
@@
 The code generating all results of this manuscript can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
+\wj{in the supplementary materials?}
 
@@
 
+## Supplementary materials
+
+The zip file "supplementary-files.zip" contains R scripts for reproducing all aspects of this paper.
+
+**Data**
+
+The processed data of Hamby set 252 and Hamby set 44 are stored in two `.rds` files:
+
+-   [`BulletSignatures252.rds`](https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/BulletSignatures252.rds)
+-   [`BulletSignatures44.rds`](https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/BulletSignatures44.rds)
+
+And the ground truth of Hamby set 252 is provided in [`StudyInfo.xlsx`](https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/StudyInfo.xlsx)
+
+Due to the size of the file, these processed data are not included in the "supplementary-files.zip", but the links are provided for download.
+
+In order to reproduce the results in the paper, please download "BulletSignatures252.rds", "BulletSignatures44.rds", and "StudyInfo.xlsx" and save them in a folder named "bullet_signatures_etc".
+And place the folder "bullet_signatures_etc" into the folder of all the R scripts of "supplementary-files.zip".
+
+Please check out the folder structure of [the `reproducible` folder](https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible) for reference.
+
+**File description**
+
+-   `hamby*_result_generator.R`: these R scripts take the processed data of Hamby set 252 and Hamby set 44, generate preliminary results used in the paper, and save the results in the `.csv` format in the folder `data-csv`.
+-   `rds_generator.R`: this R script takes the generated `.csv` files and produce `CMPSpaper_results.rds`.
+`CMPSpaper_results.rds` is identical to `data/CMPSpaper_results.rds` and is used generate figures and other results presented in the paper.
+-   `func_collection.R`: this R script contains some helper functions used by other R scripts.
+
 <!-- ```{r plot_thisisus} -->

### 2021-11-18 reproducible/func_collection.R

@@ -1,0 +1,361 @@
+library(assertthat)
+
+compute_var_ratio <- function(score, label) {
+  score.split <- split(score, label)
+  
+  group.mean <- sapply(score.split, mean, na.rm=TRUE)
+  
+  total.mean <- mean(score, na.rm = TRUE)
+  
+  var.between <- sum((group.mean - total.mean)^2)
+  var.within <- sum(sapply(score.split, var, na.rm = TRUE))
+  
+  var.ratio <- var.between / var.within
+  return(var.ratio)
+}
+
+compute_var_ratio_anova <- function(score, label, MS=TRUE) {
+  score.split <- split(score, label)
+  
+  group.mean <- sapply(score.split, mean, na.rm=TRUE)
+  group.count <- sapply(score.split, function(tt) sum(!is.na(tt)) )
+  total.mean <- mean(score, na.rm = TRUE)
+  
+  k <- length(unique(label))
+  n <- length(score)
+  
+  var.between <- sum((group.mean - total.mean)^2 * group.count)
+  var.within <- sum(sapply(score.split, function(tt) {
+    sum((tt - mean(tt, na.rm = TRUE))^2)
+  })) 
+  
+  var.ratio <- var.between / var.within
+  if(MS) {
+    var.ratio <- var.ratio * (n-k) / (k-1)
+  }
+  return(var.ratio)
+}
+
+get_all_phases <- function(land1, land2, score, addNA = FALSE)
+{
+  maxland <- max(land1, land2)
+  fullframe <- data.frame(expand.grid(land1 = 1:maxland, land2 = 1:maxland))
+  bcompare <- data.frame(land1, land2, score)
+  fullframe <- fullframe %>% left_join(bcompare, by = c("land1", 
+                                                        "land2"))
+  fullframe <- fullframe %>% mutate(land1 = factor(land1, levels = 1:maxland), 
+                                    land2 = factor(land2, levels = 1:maxland))
+  matrix <- xtabs(score ~ land1 + land2, data = fullframe, 
+                  addNA = addNA)/xtabs(~land1 + land2, data = fullframe, 
+                                       addNA = addNA)
+  matrix <- cbind(matrix, matrix)
+  scores.list <- 1:maxland %>% lapply(FUN = function(i) {
+    if (i == 1) {
+      diag(matrix)
+    }
+    else {
+      i <- i - 1
[…]

### 2021-11-18 reproducible/hamby252_npeak_result_generator.R

@@ -1,28 +1,28 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr)
+library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
 library(parallel)
 
-source("code/func_collection.R")
+source("func_collection.R")
 
-#### code used to load the original data; commented out
-# b252.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+data_path <- "./data-csv/hamby252/"
 
 ## Data Processing
 
 #### load the data from reproducible/bullet_signatures_etc/
-b252 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures252.rds")
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
 
 #### obtain all comparisons
 b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
@@ -49,7 +49,7 @@ tmp.tibble <- tmp.tibble %>% mutate(
 ###### StudyInfo.xlsx provides the ground truth for Hamby252 
 studyinfo <-
   readxl::read_xlsx(
-    "./reproducible/bullet_signatures_etc/StudyInfo.xlsx",
+    "./bullet_signatures_etc/StudyInfo.xlsx",
     sheet = 3,
     skip = 1
   )
@@ -315,8 +315,7 @@ for (i in 1:N) {
   
 }
 
-#### code used to save results as csv files used in the paper; commented out
-data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/hamby252/"
+#### code used to save results as csv files 
 for(i in 1:N){
   write.csv(
     CMPS_hamby252_results$cmps.table[[i]] %>%

### 2021-11-18 reproducible/hamby252_rf_result_generator.R

@@ -1,5 +1,15 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
 library(tidyverse)
-library(bulletxtrctr)
+library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
@@ -7,26 +17,27 @@ library(parallel)
 library(assertthat)
 require(randomForest)
 
-source("code/func_collection.R")
+source("func_collection.R")
 
-# b252.full <-
-#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
-b252.full <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+data_path <- "./data-csv/hamby252/"
 
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
+b252$sig_rf <- b252$sigs25
+
+####
+# Note: if this random forest is not published yet by the time of reproduction, 
+# please contact the author of the paper
 rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
 
 # generate bullet_id
-bulletid.tb <- b252.full %>% select(scan_id)
+bulletid.tb <- b252 %>% select(scan_id)
 bulletid.tb <- bulletid.tb %>% mutate(
   barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
   bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
   land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
   bullet_id = paste(barrel_id, bullet)
 )
-
-# remove x3p files
-b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
 
 # get bullet id
 b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
[…]

### 2021-11-18 reproducible/hamby252_seg_result_generator.R

@@ -1,28 +1,28 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr)
+library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
 library(parallel)
 
-source("code/func_collection.R")
+source("func_collection.R")
 
-#### code used to load the original data; commented out
-# b252.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+data_path <- "./data-csv/hamby252/"
 
 ## Data Processing
 
 #### load the data from reproducible/bullet_signatures_etc/
-b252 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures252.rds")
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
 
 #### obtain all comparisons
 b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
@@ -49,7 +49,7 @@ tmp.tibble <- tmp.tibble %>% mutate(
 ###### StudyInfo.xlsx provides the ground truth for Hamby252 
 studyinfo <-
   readxl::read_xlsx(
-    "./reproducible/bullet_signatures_etc/StudyInfo.xlsx",
+    "./bullet_signatures_etc/StudyInfo.xlsx",
     sheet = 3,
     skip = 1
   )
@@ -304,7 +304,6 @@ for (i in 1:N) {
 }
 
 #### code used to save results as csv files used in the paper; commented out
-data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/hamby252/"
 for(i in 1:N){
   write.csv(
     CMPS_hamby252_results$cmps.table[[i]] %>%

### 2021-11-18 reproducible/hamby44_npeak_result_generator.R

@@ -1,29 +1,28 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
 
+# set the working directory
+# setwd("~/your-path/supplementary-files")
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr)
+library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
 library(parallel)
 
-source("code/func_collection.R")
+source("func_collection.R")
 
-#### code used to load the original data; commented out
-# b44.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+data_path <- "./data-csv/hamby44/"
 
 ## Data Processing
 
 #### load the data from reproducible/bullet_signatures_etc/
-b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
 
 #### obtain all comparisons
 bulletid.tb <- b44 %>% select(scan_id)
@@ -318,8 +317,7 @@ for (i in 1:N) {
   
 }
 
-#### code used to save results as csv files used in the paper; commented out
-data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/hamby44/"
+#### code used to save results as csv files
 for(i in 1:N){
   write.csv(
     CMPS_hamby44_results$cmps.table[[i]] %>% select(-cmps.table, -cmps.table.m) %>% as.data.frame(),

### 2021-11-18 reproducible/hamby44_rf_result_generator.R

@@ -1,5 +1,15 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
 library(tidyverse)
-library(bulletxtrctr)
+library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
@@ -7,27 +17,33 @@ library(parallel)
 library(assertthat)
 require(randomForest)
 
-source("code/func_collection.R")
+source("func_collection.R")
 
-b44.full <- 
-  readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+data_path <- "./data-csv/hamby44/"
 
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
+b44$sig_rf <- b44$sigs25_531
+
+####
+# Note: if this random forest is not published yet by the time of reproduction, 
+# please contact the author of the paper
 rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
 
 idf.idx <- c(23,35,39,41,102,126,149)
-idf.scan_id <- b44.full %>% slice(idf.idx) %>% .$scan_id
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
 
 # generate bullet_id
-bulletid.tb <- b44.full %>% select(scan_id)
+bulletid.tb <- b44 %>% select(scan_id)
 bulletid.tb <- bulletid.tb %>% mutate(
   barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
   bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
   land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
   bullet_id = paste(barrel_id, bullet)
 )
-
-# remove x3p files
-b44 <- b44.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
 
 # get all comparisons
[…]

### 2021-11-18 reproducible/hamby44_seg_result_generator.R

@@ -1,29 +1,28 @@
-##########################
-# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
-#       These rds files contain processed bullet signatures used in the paper
-#       The original data contains x3p objects of large size, so they are not
-#       uploaded to the Github repo
-##########################
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
 
+# set the working directory
+# setwd("~/your-path/supplementary-files")
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr)
+library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
 library(parallel)
 
-source("code/func_collection.R")
+source("func_collection.R")
 
-#### code used to load the original data; commented out
-# b44.full <- 
-#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+data_path <- "./data-csv/hamby44/"
 
 ## Data Processing
 
 #### load the data from reproducible/bullet_signatures_etc/
-b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
 
 #### obtain all comparisons
 bulletid.tb <- b44 %>% select(scan_id)
@@ -309,8 +308,7 @@ for (i in 1:N) {
   
 }
 
-#### code used to save results as csv files used in the paper; commented out
-data_path <- "~/Research/CMPSpaper/CMPSpaper_writing/data/hamby44/"
+#### code used to save results as csv files
 for(i in 1:N){
   write.csv(
     CMPS_hamby44_results$cmps.table[[i]] %>% select(-cmps.table, -cmps.table.m) %>% as.data.frame(),

### 2021-11-18 reproducible/rds_generator.R

@@ -66,10 +66,6 @@ for (i in 1:N) {
 CMPS_hamby252_results$cmps.table <- list()
 CMPS_hamby252_results$plot <- list()
 
-#### a global title for Hamby252 plots
-com.title252 <- expression(paste(
-  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
 
 for(i in 1:N){
   CMPS_hamby252_results$cmps.table[[i]] <- 
@@ -149,10 +145,6 @@ for (i in 1:N) {
 CMPS_hamby252_results$cmps.table <- list()
 CMPS_hamby252_results$plot <- list()
 
-#### a global title for Hamby252 plots
-com.title252 <- expression(paste(
-  "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
 
 for(i in 1:N){
   CMPS_hamby252_results$cmps.table[[i]] <- 
@@ -221,10 +213,6 @@ for (i in 1:N) {
 CMPS_hamby44_results$cmps.table <- list()
 CMPS_hamby44_results$plot <- list()
 
-#### a global title for Hamby44 plots
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
 
 for(i in 1:N){
   CMPS_hamby44_results$cmps.table[[i]] <- 
@@ -301,11 +289,6 @@ for (i in 1:N) {
 #### container for the cmps results and corresponding plots
 CMPS_hamby44_results$cmps.table <- list()
 CMPS_hamby44_results$plot <- list()
-
-#### a global title for Hamby44 plots
-com.title44 <- expression(paste(
-  "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution"
-))
 
 for(i in 1:N){
   CMPS_hamby44_results$cmps.table[[i]] <- 

### 2021-11-18 ju-hofmann/ju-hofmann.R
ready to re-submit, check point 1, before switch to rtools

@@ -1,144 +1,129 @@
-## ----setup, echo=FALSE, message=FALSE, warning=FALSE------
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE---------
 library(knitr)
-library(tidyverse)
-library(bulletxtrctr)
 library(kableExtra)
+library(tidyverse)
 library(patchwork)
 library(ggpubr)
 
-source("../code/func_collection.R")
-
-knitr::opts_chunk$set(
-  collapse = TRUE,
-  comment = "#>",
-  out.width = "\\textwidth",
-  fig.align = "center",
-#  cache=TRUE,
-  dpi = 100,
-  warning = FALSE,
-  message = FALSE
-)
-
-
-## ----setup_knitr, echo=FALSE------------------------------
-## From Josh O'Brien's stackoverflow answer:
-## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
-## These two settings control text width in codefig vs. usual code blocks
-partWidth <- 35
-fullWidth <- 60
-options(width = fullWidth)
-
-##  (1) CHUNK HOOK FUNCTION
-##   First, to set R's textual output width on a per-chunk basis, we
-## need to define a hook function which temporarily resets global R's
-## option() settings, just for the current chunk
-knit_hooks$set(r.opts = local({
-    ropts <- NA
-    function(before, options, envir) {
-        if (before) {
-            ropts <<- options(options$r.opts)
-        } else {
-            options(ropts)
-        }
-    }
-}))
-
-## (2) OUTPUT HOOK FUNCTION
-
-##   Define a custom output hook function. This function processes _all_
-## evaluated chunks, but will return the same output as the usual one,
-## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
-## case, wrap the usual textual output in LaTeX code placing it in a
-## narrower adjustbox environment and setting the graphics that it
-## produced in another box beside it.
-
-defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
-
-codefigChunkHook <- function(x, options) {
-  main <-  defaultChunkHook(x, options)
-  before <-
-    "\\vspace{1em}
-\\begin{adjustbox}{valign=t}
-\\begin{minipage}{.39\\textwidth}\n"
-  after <-
-    paste("\\vspace{1em}
-\\end{minipage}
[…]

### 2021-11-18 reproducible/hamby252_rf_result_generator.R

@@ -9,7 +9,10 @@
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
@@ -25,10 +28,7 @@ data_path <- "./data-csv/hamby252/"
 b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
 b252$sig_rf <- b252$sigs25
 
-####
-# Note: if this random forest is not published yet by the time of reproduction, 
-# please contact the author of the paper
-rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
+rf.model <- readRDS("./csafe_rf2.rds")
 
 # generate bullet_id
 bulletid.tb <- b252 %>% select(scan_id)

### 2021-11-18 reproducible/hamby252_seg_result_generator.R

@@ -9,7 +9,10 @@
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
 library(x3ptools)
 library(CMPS)
 library(ggpubr)

### 2021-11-18 reproducible/hamby44_rf_result_generator.R

@@ -9,7 +9,10 @@
 
 ## Load the required packages
 library(tidyverse)
-library(bulletxtrctr) # devtools::install_github("heike/bulletxtrctr")
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
 library(x3ptools)
 library(CMPS)
 library(ggpubr)
@@ -28,10 +31,7 @@ data_path <- "./data-csv/hamby44/"
 b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
 b44$sig_rf <- b44$sigs25_531
 
-####
-# Note: if this random forest is not published yet by the time of reproduction, 
-# please contact the author of the paper
-rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
+rf.model <- readRDS("./csafe_rf2.rds")
 
 idf.idx <- c(23,35,39,41,102,126,149)
 idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id

### 2021-11-18 reproducible/rds_generator.R

@@ -1,7 +1,6 @@
 ###############################
-# Note: Please set the working 
-# directory so that "./data-csv/"
-# is available
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that ./data-csv/" is available
 ###############################
 
 ###############################

### 2022-03-24 submissions/resubmission-ju-hofmann/ju-hofmann.Rmd
reorganize the folder

--- 2021-11-18 ju-hofmann/ju-hofmann.Rmd
@@
 library(knitr)
+library(kableExtra)
 library(tidyverse)
-library(bulletxtrctr)
-library(kableExtra)
 library(patchwork)
 library(ggpubr)
-
-# source("../code/func_collection.R")
 
@@
 )
+
 ```
@@
 
+```{r func, echo=FALSE}
+bootstrap_k <- function(scores, k, K, value) {
+  res <- replicate(K, {
+    mean(sample(scores, size = k, replace = TRUE), na.rm = TRUE)
+  })
+  sum(res >= value) / K
+}
+
+compute_average_scores <- function(land1, land2, score, addNA = FALSE) {
+  if (!is.numeric(land1)) land1 <- readr::parse_number(as.character(land1))
+  if (!is.numeric(land2)) land2 <- readr::parse_number(as.character(land2))
+  # assert_that(is.numeric(land1), is.numeric(land2), is.numeric(score))
+
+  maxland <- max(land1, land2)
+  fullframe <- data.frame(expand.grid(land1 = 1:maxland, land2 = 1:maxland))
+  bcompare <- data.frame(land1, land2, score)
+
+  fullframe <- fullframe %>% left_join(bcompare, by = c("land1", "land2"))
+
+  fullframe <- fullframe %>% mutate(
+    land1 = factor(land1, levels = 1:maxland),
+    land2 = factor(land2, levels = 1:maxland)
+  )
+  # get averages, just in case
+  matrix <- xtabs(score ~ land1 + land2,
+    data = fullframe, addNA = addNA
+  ) / xtabs(~land1 + land2, data = fullframe, addNA = addNA)
+
+  matrix <- cbind(matrix, matrix)
+
+  scores <- 1:maxland %>% sapply(FUN = function(i) {
+    if (i == 1) {
+      mean(diag(matrix), na.rm = TRUE)
+    } else {
+      i <- i - 1
+      mean(diag(matrix[, -(1:i)]), na.rm = TRUE)
+    }
+  })
+  scores
+}
+
+bullet_to_land_predict <- function(land1, land2, scores, difference, alpha = 0.05, addNA = FALSE) {
+  if (!is.numeric(land1)) land1 <- readr::parse_number(as.character(land1))
+  if (!is.numeric(land2)) land2 <- readr::parse_number(as.character(land2))
+  avgs <- compute_average_scores(land2, land1, scores, addNA)
+
+  p <- max(c(land1, land2))
+  boot <- bootstrap_k(scores, p, 1000, max(avgs)) < alpha
+  if (!is.numeric(boot)) {
+    boot <- bootstrap_k(scores, p, 1000, max(avgs)) < alpha
+    #     print("boot is not numeric")
+    #      browser()
+  }
+
+  getdiff <- diff(sort(-avgs))[1]
+  if (!is.numeric(getdiff)) print("getdiff is not numeric") # browser()
+  if (getdiff > difference & boot) {
+    # pick the maximum to determine the phase
+    idx <- which.max(avgs)
+    dd <- data.frame(
+      land1,
+      land2
+    ) %>%
+      mutate_if(function(.) !is.numeric(.), parse_number)
+    dd$diff <- (dd$land1 - dd$land2) %% p + 1
+
+    return(dd$diff == idx)
+  } else {
+    return(rep(FALSE, length = length(land1)))
+  }
+}
+```
+
 ## Introduction
@@
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-<!-- Our implementation is made available as part of the `R` package \pkg{cmpsR} on GitHub at \url{https://github.com/willju-wangqian/cmpsR}. -->
-\wj{change}
 Our implementation is made available as part of the `R` package \pkg{cmpsR} on CRAN.
 
-<!-- https://s3-us-gov-west-1.amazonaws.com/cg-d4b776d0-d898-4153-90c8-8336f86bdfec/CIUS/downloads/2020/expanded-homicide-2020.zip -->
-<!-- Firearm examination has  played an important role in  convictions [@fbiucr] in the United States criminal justice system.
-\hh{Do we have a number or a percentage of cases where firearm examination has played a role?
-or maybe gun violence?
-XXX} --> <!-- https://ucr.fbi.gov/crime-in-the-u.s/2019/crime-in-the-u.s.-2019/topic-pages/expanded-homicide -->
 According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms" [@fbiucr].
@@
 The x3p format provides a standard way of exchanging 2D and 3D profile data.
-It conforms to the ISO5436-2 standard [<http://sourceforge.net/p/open-gps/mwiki/X3p/>] adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
+It conforms to [the ISO5436-2 standard](http://sourceforge.net/p/open-gps/mwiki/X3p/) adopted by the OpenFMC (Open Forensic Metrology Consortium), a group of firearm forensics researchers who contributes to the establishment of best practices of using metrology in forensic science.
 Hamby set 252 was scanned using a NanoFocus lens at 20x magnification with the scan resolution being 1.5625 \textmu m $\times$ 1.5625 \textmu m per pixel.
@@
 To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
-An example of the extraction process with corresponding code and parameter settings can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
+An example of the extraction process with corresponding code and parameter settings can be found in the "Supplementary materials".
 Note that the process of extracting signatures might be different from the one used in @cmps because no code or parameter settings are made available publicly.
-\wj{can be found in the supplementary materials of this paper? }
 
@@
 The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
-Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github \url{https://github.com/willju-wangqian/cmpsR}.
+Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github.
 This publicly available implementation calculates the CMPS score of a comparison using the following code:
-\wj{ignore github?}
 
@@
     By default \code{outlength} is set to \code{NULL}, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
-
-<!--For more details, please check the documentation of `extract_feature_cmps` or use `?extract_feature_cmps`.-->
-
-<!-- [examples https://journal.r-project.org/archive/2019/RJ-2019-044/RJ-2019-044.pdf] -->
-
-<!-- [https://journal.r-project.org/archive/2019/RJ-2019-002/RJ-2019-002.pdf] -->
 
@@
 ```
-
-<!-- ```{r hamby252-data-seg, eval=TRUE, echo=FALSE} -->
-<!-- # for hamby 252 -->
-<!-- N <- 8 # the number of different sets of parameters -->
-<!-- CMPS_hamby252_results <- list() # a container for everything -->
-
-<!-- #### setup span1 -->
-<!-- CMPS_hamby252_results$span1 <- as.list(rep(0.25, N)) -->
-
-<!-- #### setup signature name -->
-<!-- CMPS_hamby252_results$signame <- as.list(rep("sigs25", N)) -->
-<!--   # list("sigs75", "sigs25", "sigs25_1062", "sigs15") -->
-
-<!-- #### setup npeaks.set -->
-<!-- CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1)) -->
-
-<!-- #### setup seg_length -->
-<!-- CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200)) -->
-
-<!-- #### setup Tx -->
-<!-- CMPS_hamby252_results$Tx <- as.list(rep(25, N)) -->
-
-<!-- #### setup outlength -->
-<!-- CMPS_hamby252_results$outlength <- vector(mode = "list", length = N) -->
-
-<!-- #### create a plot title and a file name for each set of parameters -->
-<!-- CMPS_hamby252_results$titlee <- list() -->
-<!-- CMPS_hamby252_results$filename <- list() -->
-<!-- for (i in 1:N) { -->
-<!--   CMPS_hamby252_results$titlee[[i]] <- -->
-<!--     paste0( -->
-<!--       "npeaks.set=c(", -->
-<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","), -->
-<!--       ")", -->
-<!--       ", len=", -->
-<!--       CMPS_hamby252_results$seg_length[[i]], -->
-<!--       ", Tx=", -->
-<!--       CMPS_hamby252_results$Tx[[i]], -->
-<!--       ", \nspan1=", -->
-<!--       CMPS_hamby252_results$span1[[i]], -->
-<!--       ", span2=0.03" -->
-<!--     ) -->
-<!--   CMPS_hamby252_results$filename[[i]] <-  -->
-<!--     paste( -->
-<!--       "hamby252_segment", -->
-<!--       CMPS_hamby252_results$span1[[i]]*100, -->
-<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"), -->
-<!--       CMPS_hamby252_results$seg_length[[i]], -->
-<!--       CMPS_hamby252_results$Tx[[i]], -->
-<!--       sep = "_" -->
-<!--     ) -->
-<!-- } -->
-
-<!-- #### container for the cmps results and corresponding plots -->
-<!-- CMPS_hamby252_results$cmps.table <- list() -->
-<!-- CMPS_hamby252_results$plot <- list() -->
-
-<!-- #### a global title for Hamby252 plots -->
-<!-- com.title252 <- expression(paste( -->
-<!--   "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
-<!-- )) -->
-
-<!-- for(i in 1:N){ -->
-<!--   CMPS_hamby252_results$cmps.table[[i]] <-  -->
-<!--   read.csv(file = paste("./data/hamby252/",  -->
-<!--                         CMPS_hamby252_results$filename[[i]],  -->
-<!--                         ".csv", -->
-<!--                         sep = "")) -->
-<!-- } -->
-
-<!-- CMPS_hamby252_results_seg <- CMPS_hamby252_results -->
-
-<!-- ``` -->
-
-<!-- ```{r hamby252-data-npeak, eval=TRUE, echo=FALSE} -->
-<!-- N <- 8 # the number of different sets of parameters -->
-<!-- CMPS_hamby252_results <- list() # a container for everything -->
-
-<!-- #### setup span1 -->
-<!-- CMPS_hamby252_results$span1 <- as.list(rep(0.25, N)) -->
-
-<!-- #### setup signature name -->
-<!-- CMPS_hamby252_results$signame <- as.list(rep("sigs25", N)) -->
-<!-- # list("sigs75", "sigs25", "sigs25_1062", "sigs15") -->
-
-<!-- #### setup npeaks.set -->
-<!-- CMPS_hamby252_results$npeaks.set <-  -->
-<!--   list(c(5), -->
-<!--        c(5,2), -->
-<!--        c(5,3,1), -->
-<!--        c(10,6,2), -->
-<!--        c(6,4,2,1), -->
-<!--        c(10,7,4,2), -->
-<!--        c(10,6,4,2,1), -->
-<!--        c(10,8,6,4,2,1)) -->
-
-<!-- #### setup seg_length -->
-<!-- CMPS_hamby252_results$seg_length <-  -->
-<!--   # as.list(c(25, 50, 75, 100, 125, 150, 175, 200)) -->
-<!--   as.list(rep(50, N)) -->
-
-<!-- #### setup Tx -->
-<!-- CMPS_hamby252_results$Tx <- as.list(rep(25, N)) -->
-
-<!-- #### setup outlength -->
-<!-- CMPS_hamby252_results$outlength <- vector(mode = "list", length = N) -->
-<!-- CMPS_hamby252_results$outlength[[7]] <- c(60, 90, 120, 150, 180) -->
-<!-- CMPS_hamby252_results$outlength[[8]] <- c(50,75,100,125,150,200) -->
-
-<!-- #### create a plot title and a file name for each set of parameters -->
-<!-- CMPS_hamby252_results$titlee <- list() -->
-<!-- CMPS_hamby252_results$filename <- list() -->
-<!-- for (i in 1:N) { -->
-<!--   CMPS_hamby252_results$titlee[[i]] <- -->
-<!--     paste0( -->
-<!--       "npeaks.set=c(", -->
-<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","), -->
-<!--       ")", -->
-<!--       ", len=", -->
-<!--       CMPS_hamby252_results$seg_length[[i]], -->
-<!--       ", Tx=", -->
-<!--       CMPS_hamby252_results$Tx[[i]], -->
-<!--       ", \nspan1=", -->
-<!--       CMPS_hamby252_results$span1[[i]], -->
-<!--       ", span2=0.03" -->
-<!--     ) -->
-<!--   CMPS_hamby252_results$filename[[i]] <-  -->
-<!--     paste( -->
-<!--       "hamby252_npeak", -->
-<!--       CMPS_hamby252_results$span1[[i]]*100, -->
-<!--       paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"), -->
-<!--       CMPS_hamby252_results$seg_length[[i]], -->
-<!--       CMPS_hamby252_results$Tx[[i]], -->
-<!--       sep = "_" -->
-<!--     ) -->
-<!-- } -->
-
-<!-- #### container for the cmps results and corresponding plots -->
-<!-- CMPS_hamby252_results$cmps.table <- list() -->
-<!-- CMPS_hamby252_results$plot <- list() -->
-
-<!-- #### a global title for Hamby252 plots -->
-<!-- com.title252 <- expression(paste( -->
-<!--   "Hamby 252 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
-<!-- )) -->
-
-<!-- for(i in 1:N){ -->
-<!--   CMPS_hamby252_results$cmps.table[[i]] <-  -->
-<!--   read.csv(file = paste("./data/hamby252/",  -->
-<!--                         CMPS_hamby252_results$filename[[i]],  -->
-<!--                         ".csv", -->
-<!--                         sep = "")) -->
-<!-- } -->
-
-<!-- CMPS_hamby252_results_npeak <- CMPS_hamby252_results -->
-
-<!-- ``` -->
-
-<!-- ```{r hamby44-data-seg, eval=TRUE, echo=FALSE} -->
-<!-- N <- 8 # the number of different sets of parameters -->
-<!-- CMPS_hamby44_results <- list() # a container for everything -->
-
-<!-- #### setup span1 -->
-<!-- CMPS_hamby44_results$span1 <- as.list(rep(0.25, N)) -->
-
-<!-- #### setup signature name -->
-<!-- CMPS_hamby44_results$signame <- -->
-<!--   as.list(rep("sigs25_531", N)) -->
-
-<!-- #### setup neapks.set -->
-<!-- CMPS_hamby44_results$npeaks.set <- -->
-<!--   lapply(1:N, function(t) c(5,3,1)) -->
-
-<!-- #### setup seg_length -->
-<!-- CMPS_hamby44_results$seg_length <- as.list(c(30, 45, 61, 90, 122, 150, 180, 210)) -->
-
-<!-- #### setup outlength -->
-<!-- CMPS_hamby44_results$outlength <- vector(mode = "list", length = N) -->
-
-<!-- #### setup Tx -->
-<!-- CMPS_hamby44_results$Tx <- as.list(rep(30, N)) -->
-
-<!-- #### create a plot title and a file name for each set of parameters -->
-<!-- CMPS_hamby44_results$titlee <- list() -->
-<!-- CMPS_hamby44_results$filename <- list() -->
-<!-- for (i in 1:N) { -->
-<!--   CMPS_hamby44_results$titlee[[i]] <- -->
-<!--     paste0( -->
-<!--       "npeaks.set=c(", -->
-<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","), -->
-<!--       ")", -->
-<!--       ", len=", -->
-<!--       CMPS_hamby44_results$seg_length[[i]], -->
-<!--       ", Tx=", -->
-<!--       CMPS_hamby44_results$Tx[[i]], -->
-<!--       ", \nspan1=", -->
-<!--       CMPS_hamby44_results$span1[[i]], -->
-<!--       ", span2=0.03" -->
-<!--     ) -->
-<!--   CMPS_hamby44_results$filename[[i]] <-  -->
-<!--     paste( -->
-<!--       "hamby44_segment", -->
-<!--       CMPS_hamby44_results$span1[[i]]*100, -->
-<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"), -->
-<!--       CMPS_hamby44_results$seg_length[[i]], -->
-<!--       CMPS_hamby44_results$Tx[[i]], -->
-<!--       sep = "_" -->
-<!--     ) -->
-<!-- } -->
-
-<!-- #### container for the cmps results and corresponding plots -->
-<!-- CMPS_hamby44_results$cmps.table <- list() -->
-<!-- CMPS_hamby44_results$plot <- list() -->
-
-<!-- #### a global title for Hamby44 plots -->
-<!-- com.title44 <- expression(paste( -->
-<!--   "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
-<!-- )) -->
-
-<!-- for(i in 1:N){ -->
-<!--   CMPS_hamby44_results$cmps.table[[i]] <-  -->
-<!--   read.csv(file = paste("./data/hamby44/",  -->
-<!--                         CMPS_hamby44_results$filename[[i]],  -->
-<!--                         ".csv", -->
-<!--                         sep = "")) -->
-<!-- } -->
-
-<!-- CMPS_hamby44_results_seg <- CMPS_hamby44_results -->
-
-<!-- ``` -->
-
-<!-- ```{r hamby44-data-npeak, eval=TRUE, echo=FALSE} -->
-<!-- N <- 8 # the number of different sets of parameters -->
-<!-- CMPS_hamby44_results <- list() # a container for everything -->
-
-<!-- #### setup span1 -->
-<!-- CMPS_hamby44_results$span1 <- as.list(rep(0.25, N)) -->
-
-<!-- #### setup signature name -->
-<!-- CMPS_hamby44_results$signame <- -->
-<!--   as.list(rep("sigs25_531", N)) -->
-
-<!-- #### setup neapks.set -->
-<!-- CMPS_hamby44_results$npeaks.set <- -->
-<!--   list(c(5), -->
-<!--        c(5,2), -->
-<!--        c(5,3,1), -->
-<!--        c(10,6,2), -->
-<!--        c(6,4,2,1), -->
-<!--        c(10,7,4,2), -->
-<!--        c(10,6,4,2,1), -->
-<!--        c(10,8,6,4,2,1)) -->
-
-<!-- #### setup seg_length -->
-<!-- CMPS_hamby44_results$seg_length <- as.list(rep(61, N)) -->
-
-<!-- #### setup outlength -->
-<!-- CMPS_hamby44_results$outlength <- vector(mode = "list", length = N) -->
-<!-- CMPS_hamby44_results$outlength[[7]] <- c(61, 91, 121, 151, 181) -->
-<!-- CMPS_hamby44_results$outlength[[8]] <- c(61, 91, 121, 151, 181, 211) -->
-
-<!-- #### setup Tx -->
-<!-- CMPS_hamby44_results$Tx <- as.list(rep(30, N)) -->
-
-<!-- #### create a plot title and a file name for each set of parameters -->
-<!-- CMPS_hamby44_results$titlee <- list() -->
-<!-- CMPS_hamby44_results$filename <- list() -->
-<!-- for (i in 1:N) { -->
-<!--   CMPS_hamby44_results$titlee[[i]] <- -->
-<!--     paste0( -->
-<!--       "npeaks.set=c(", -->
-<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","), -->
-<!--       ")", -->
-<!--       ", len=", -->
-<!--       CMPS_hamby44_results$seg_length[[i]], -->
-<!--       ", Tx=", -->
-<!--       CMPS_hamby44_results$Tx[[i]], -->
-<!--       ", \nspan1=", -->
-<!--       CMPS_hamby44_results$span1[[i]], -->
-<!--       ", span2=0.03" -->
-<!--     ) -->
-<!--   CMPS_hamby44_results$filename[[i]] <-  -->
-<!--     paste( -->
-<!--       "hamby44_npeak", -->
-<!--       CMPS_hamby44_results$span1[[i]]*100, -->
-<!--       paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"), -->
-<!--       CMPS_hamby44_results$seg_length[[i]], -->
-<!--       CMPS_hamby44_results$Tx[[i]], -->
-<!--       sep = "_" -->
-<!--     ) -->
-<!-- } -->
-
-<!-- #### container for the cmps results and corresponding plots -->
-<!-- CMPS_hamby44_results$cmps.table <- list() -->
-<!-- CMPS_hamby44_results$plot <- list() -->
-
-<!-- #### a global title for Hamby44 plots -->
-<!-- com.title44 <- expression(paste( -->
-<!--   "Hamby 44 - ", CMPS[max], " and ", bar(CMPS)[max], " Distribution" -->
-<!-- )) -->
-
-<!-- for(i in 1:N){ -->
-<!--   CMPS_hamby44_results$cmps.table[[i]] <-  -->
-<!--   read.csv(file = paste("./data/hamby44/",  -->
-<!--                         CMPS_hamby44_results$filename[[i]],  -->
-<!--                         ".csv", -->
-<!--                         sep = "")) -->
-<!-- } -->
-
-<!-- CMPS_hamby44_results_npeak <- CMPS_hamby44_results -->
-
-<!-- ``` -->
-
-<!-- ```{r rf-data-load, echo=FALSE} -->
-<!-- rf.results <- list() -->
-<!-- rf.results[[1]] <- read.csv(file = "./data/hamby252/hamby252_rf_results.csv") -->
-<!-- rf.results[[2]] <- read.csv(file = "./data/hamby44/hamby44_rf_results.csv") -->
-<!-- ``` -->
 
@@
 
-The code generating all results of this manuscript can be found on Github at \url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
-\wj{in the supplementary materials?}
+For details about the implementation, examples and results, please refer to the "Supplementary materials".
 
@@
 
-**Data**
+**Data not included in "supplementary-files.zip"**
 
@@
 
-<!-- ```{r plot_thisisus} -->
-<!-- rf.252.plot <- metric_plot_helper(rf.results[[1]], "rf.diff", scaled = TRUE, -->
-<!--                                   subtitle = "random forest scores with metric diff") + -->
-<!--   xlab(expression(RF[diff])) + -->
-<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
-<!-- cmps.252.plot <- metric_plot_helper(CMPS_hamby252_results_npeak$cmps.table[[8]], "cmps.diff_scaled",  -->
-<!--                                     scaled = TRUE, subtitle = "CMPS, 10-8-6-4-2-1, 50") + -->
-<!--   xlab(labels[3]) + -->
-<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
-
-<!-- rf.44.plot <- metric_plot_helper(rf.results[[2]], "rf.diff", scaled = TRUE, -->
-<!--                                   subtitle = "random forest scores with metric diff") + -->
-<!--   xlab(expression(RF[diff])) + -->
-<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
-<!-- cmps.44.plot <- metric_plot_helper(CMPS_hamby44_results_npeak$cmps.table[[6]], "cmps.diff_scaled",  -->
-<!--                                     scaled = TRUE, subtitle = "CMPS, 10-7-4-2, 61") + -->
-<!--   xlab(labels[3]) + -->
-<!--   scale_x_continuous(breaks = seq(0, 1, by = 0.1)) -->
-
-<!-- p.thisisus252 <- ggarrange(plotlist = list(cmps.252.plot, rf.252.plot), nrow = 1, ncol = 2, -->
-<!--                common.legend = TRUE, legend = "bottom") -->
-<!-- p.thisisus252 <-  -->
-<!--   annotate_figure(p.thisisus252,  -->
-<!--                   top = text_grob("Hamby 252 - Random Forest and CMPS")) -->
-
-<!-- p.thisisus44 <- ggarrange(plotlist = list(cmps.44.plot, rf.44.plot), nrow = 1, ncol = 2, -->
-<!--                common.legend = TRUE, legend = "bottom") -->
-<!-- p.thisisus44 <-  -->
-<!--   annotate_figure(p.thisisus44,  -->
-<!--                   top = text_grob("Hamby 44 - Random Forest and CMPS")) -->
-
-<!-- ``` -->
+**Data included in "supplementary-files.zip"**
+
+-   `data-csv`: this folder contains `.csv` files we generated using R scripts `hamby*_result_generator.R` 
+-   `CMPSpaper_results.rds`: this is the `.rds` file we generated using R script `rds_generator.R`
+
+These data can be used as reference or example results of the reproducible codes
+
+-   `csafe_rf2.rds`: this `.rds` file contains the random forest model used in this paper
 

### 2022-03-24 submissions/resubmission-ju-hofmann/ju-hofmann.tex
reorganize the folder

--- 2021-10-28 ju-hofmann/ju-hofmann.tex
@@
 review, and improve. Our implementation is made available as part of the
-\texttt{R} package \pkg{cmpsR} on GitHub at
-\url{https://github.com/willju-wangqian/cmpsR}.
+\texttt{R} package \pkg{cmpsR} on CRAN.
 
@@
 of Investigation), ``more than 76 percent (76.7) of the homicides for
-which the FBI received weapons data in 2020
-\hh{is this really 2020 or should it be 2019?}involved the use of
-firearms'', and the number of cases that involved the use of firearms in
-2020 increased by close to 30 percent (29.3) compared to that in 2019
-\citep{fbiucr}. Firearm examination could play an important role in all
-these cases. An important task of firearm examination is to answer the
-question of whether two pieces of evidence come from the same source or
-whether a piece of evidence matches a sample obtained from a specific
-firearm. Here, in particular, we are interested to determine whether two
-bullets were fired from the same gun barrel. Assessing the similarity
-between two bullets is based on a comparison of striation marks acquired
-during the firing process as bullets are propelled through the barrel.
-Current state of art sees firearms examiners make an assessment of
-similarity based on a visual comparison, generally, using a comparison
-microscope \citep{afte}. This practice has been criticized for its lack
-of objectivity and the associated problem of determining valid error
-rates \citep{pcast}.
+which the FBI received weapons data in 2020 involved the use of
+firearms'' \citep{fbiucr}. At the same time, the number of murder
+victims jumped between 2019 and 2020 by more than 23 percent (23.4) to
+17754 \citep{fbiucr20}. This increase is unprecedented and highlights
+the important role that firearm examination plays in all these cases. An
+important task of firearm examination is to answer the question of
+whether two pieces of evidence come from the same source or whether a
+piece of evidence matches a sample obtained from a specific firearm.
+Here, in particular, we are interested to determine whether two bullets
+were fired from the same gun barrel. Assessing the similarity between
+two bullets is based on a comparison of striation marks acquired during
+the firing process as bullets are propelled through the barrel. Current
+state of art sees firearms examiners make an assessment of similarity
+based on a visual comparison, generally, using a comparison microscope
+\citep{afte}. This practice has been criticized for its lack of
+objectivity and the associated problem of determining valid error rates
+\citep{pcast}.
 
@@
 and quantitative assessment into the field. The database of
-\citet{nistdb} with digital 3d topographic scans from various studies by
+\citet{nistdb} with digital 3D topographic scans from various studies by
 \citet{brundage}, \citet{hamby}, \citet{Hamby:2019} and others, provides
@@
 Profile). The x3p format provides a standard way of exchanging 2D and 3D
-profile data. It conforms to the ISO5436-2 standard
-{[}\url{http://sourceforge.net/p/open-gps/mwiki/X3p/}{]} adopted by the
-OpenFMC (Open Forensic Metrology Consortium), a group of firearm
-forensics researchers who contributes to the establishment of best
-practices of using metrology in forensic science. Hamby set 252 was
-scanned using a NanoFocus lens at 20x magnification with the scan
-resolution being 1.5625 \textmu m \(\times\) 1.5625 \textmu m per pixel.
-Hamby set 44 was scanned at the Roy J Carver High-Resolution microscopy
-lab at Iowa State. These scans were acquired with a Sensofar Confocal
-Light Microscope at 20x magnification for a nominal resolution of 0.645
-\textmu m \(\times\) 0.645 \textmu m per pixel. Both Hamby set 252 and
-Hamby set 44 are publicly available from the NIST Ballistics Database
-Project \citep{nistdb}.
+profile data. It conforms to
+\href{http://sourceforge.net/p/open-gps/mwiki/X3p/}{the ISO5436-2
+standard} adopted by the OpenFMC (Open Forensic Metrology Consortium), a
+group of firearm forensics researchers who contributes to the
+establishment of best practices of using metrology in forensic science.
+Hamby set 252 was scanned using a NanoFocus lens at 20x magnification
+with the scan resolution being 1.5625 \textmu m \(\times\) 1.5625
+\textmu m per pixel. Hamby set 44 was scanned at the Roy J Carver
+High-Resolution microscopy lab at Iowa State. These scans were acquired
+with a Sensofar Confocal Light Microscope at 20x magnification for a
+nominal resolution of 0.645 \textmu m \(\times\) 0.645 \textmu m per
+pixel. Both Hamby set 252 and Hamby set 44 are publicly available from
+the NIST Ballistics Database Project \citep{nistdb}.
 
@@
 process from scan to signatures. \autoref{fig:process}(a) shows a
-rendering of a 3d scan of a bullet land engraved area. The raised
+rendering of a 3D scan of a bullet land engraved area. The raised
 portion of the surface on the left and right of the scan are parts of
@@
 errors. An example of the extraction process with corresponding code and
-parameter settings can be found on Github at
-\url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}.
-Note that the process of extracting signatures might be different from
-the one used in \citet{cmps} because no code or parameter settings are
-made available publicly.
+parameter settings can be found in the ``Supplementary materials''. Note
+that the process of extracting signatures might be different from the
+one used in \citet{cmps} because no code or parameter settings are made
+available publicly.
 
@@
 \caption[A framework of obtaining a bullet signature]{A framework of obtaining a bullet signature.
-(a) rendering from the 3d topographic scan of a land engraved area (LEA).
+(a) rendering from the 3D topographic scan of a land engraved area (LEA).
 The selected crosscut location is indicated by a thin white horizontal line.
@@
 open-source implementation of the CMPS algorithm in the R package
-\pkg{cmpsR} available from Github
-\url{https://github.com/willju-wangqian/cmpsR}. This publicly available
+\pkg{cmpsR} available from both CRAN and Github. This publicly available
 implementation calculates the CMPS score of a comparison using the
@@
 \begin{Sinput}
-# install.packages("devtools") 
-# devtools::install_github("willju-wangqian/CMPS")
+# install.packages("cmpsR")
 
@@
 
-The \pkg{cmpsR} package is not publicly available from CRAN yet, and its
-development version is available from Github and can be installed by
+The \pkg{cmpsR} package is publicly available from CRAN and can be
+installed by
+
+\begin{Schunk}
+\begin{Sinput}
+install.packages("cmpsR") 
+\end{Sinput}
+\end{Schunk}
+
+Moreover, its development version is also available from Github and can
+be installed by
 
@@
 \(k = 0, \dots, n-1\), and
-\(\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; j = (i + k) - n \cdot \mathbbm{1}_{i + k > n} \}\),
-where \(\mathbbm{1}_A\) denotes an indicator function. For example,
+
+\begin{align}
+\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; \; j = (i + k) \;\mathrm{mod}\; n \}
+\end{align}
+
+, where \texttt{mod} denotes the modulo operation. For example,
 \(\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}\) when
@@
 
-\caption{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
+\caption[CMPS scores of all 36 pairwise bullet signature comparisons for two bullets]{CMPS scores of all 36 pairwise bullet signature comparisons for two bullets.
 Land engraving pairs generated by the same land (KM comparisons) are highlighted.
-\hh{Note that in this example the axis along Bullet 2 starts with Land 2.
-This corresponds to Phase 2 in equation XXX}}\label{fig:tiles}
+Note that in this example the axis along Bullet 2 starts with Land 2.
+This corresponds to Phase 1 in equation (1).}\label{fig:tiles}
 \end{figure}
@@
 stated in the paper, we presume this to be Hamby 252, as only those
-scans were publicly available at the time.
-\hh{XXX Let's take out this statement once we hear back from NIST} In
-order to show that our implementation of the CMPS algorithm is able to
-reproduce the results in \citet{cmps} and be used for other data sets,
-we applied our implementation to both Hamby set 252 and Hamby set 44.
-For the purpose of reproducibility, we present how we obtained bullet
-signatures from the Hamby set data and include code in the appendix: for
-both Hamby 252 and Hamby 44, we started with scans in the form of x3p
-files in the database. Following the framework proposed by \citet{aoas},
-we used the same set of parameters, removed damaged bullet scans,
-obtained bullet signatures for each bullet land engraving, and removed
-outliers in bullet signatures. Note that researchers of \citet{cmps}
-applied the CMPS algorithm to bullet signatures as well but used a
-framework different from ours. However, since their work is not
-open-source, we were not able to follow their framework and were only
-able to reproduce the results for Hamby set 252 qualitatively.
+scans were publicly available at the time. In order to show that our
+implementation of the CMPS algorithm is able to reproduce the results in
+\citet{cmps} and be used for other data sets, we applied our
+implementation to both Hamby set 252 and Hamby set 44. For the purpose
+of reproducibility, we present how we obtained bullet signatures from
+the Hamby set data and include code in the appendix: for both Hamby 252
+and Hamby 44, we started with scans in the form of x3p files in the
+database. Following the framework proposed by \citet{aoas}, we used the
+same set of parameters, removed damaged bullet scans, obtained bullet
+signatures for each bullet land engraving, and removed outliers in
+bullet signatures. Note that researchers of \citet{cmps} applied the
+CMPS algorithm to bullet signatures as well but used a framework
+different from ours. However, since their work is not open-source, we
+were not able to follow their framework and were only able to reproduce
+the results for Hamby set 252 qualitatively.
 
@@
 
-The code generating all results of this manuscript can be found on
-Github at
-\url{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}
+For details about the implementation, examples and results, please refer
+to the ``Supplementary materials''.
 
@@
 
+\hypertarget{supplementary-materials}{%
+\subsection{Supplementary materials}\label{supplementary-materials}}
+
+The zip file ``supplementary-files.zip'' contains R scripts for
+reproducing all aspects of this paper.
+
+\textbf{Data not included in ``supplementary-files.zip''}
+
+The processed data of Hamby set 252 and Hamby set 44 are stored in two
+\texttt{.rds} files:
+
+\begin{itemize}
+\tightlist
+\item
+  \href{https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/BulletSignatures252.rds}{\texttt{BulletSignatures252.rds}}
+\item
+  \href{https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/BulletSignatures44.rds}{\texttt{BulletSignatures44.rds}}
+\end{itemize}
+
+And the ground truth of Hamby set 252 is provided in
+\href{https://github.com/willju-wangqian/CMPSpaper/blob/main/reproducible/bullet_signatures_etc/StudyInfo.xlsx}{\texttt{StudyInfo.xlsx}}
+
+Due to the size of the file, these processed data are not included in
+the ``supplementary-files.zip'', but the links are provided for
+download.
+
+In order to reproduce the results in the paper, please download
+``BulletSignatures252.rds'', ``BulletSignatures44.rds'', and
+``StudyInfo.xlsx'' and save them in a folder named
+``bullet\_signatures\_etc''. And place the folder
+``bullet\_signatures\_etc'' into the folder of all the R scripts of
+``supplementary-files.zip''.
+
+Please check out the folder structure of
+\href{https://github.com/willju-wangqian/CMPSpaper/tree/main/reproducible}{the
+\texttt{reproducible} folder} for reference.
+
+\textbf{File description}
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{hamby*\_result\_generator.R}: these R scripts take the
+  processed data of Hamby set 252 and Hamby set 44, generate preliminary
+  results used in the paper, and save the results in the \texttt{.csv}
+  format in the folder \texttt{data-csv}.
+\item
+  \texttt{rds\_generator.R}: this R script takes the generated
+  \texttt{.csv} files and produce \texttt{CMPSpaper\_results.rds}.
+  \texttt{CMPSpaper\_results.rds} is identical to
+  \texttt{data/CMPSpaper\_results.rds} and is used generate figures and
+  other results presented in the paper.
+\item
+  \texttt{func\_collection.R}: this R script contains some helper
+  functions used by other R scripts.
+\end{itemize}
+
+\textbf{Data included in ``supplementary-files.zip''}
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{data-csv}: this folder contains \texttt{.csv} files we
+  generated using R scripts \texttt{hamby*\_result\_generator.R}
+\item
+  \texttt{CMPSpaper\_results.rds}: this is the \texttt{.rds} file we
+  generated using R script \texttt{rds\_generator.R}
+\end{itemize}
+
+These data can be used as reference or example results of the
+reproducible codes
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{csafe\_rf2.rds}: this \texttt{.rds} file contains the random
+  forest model used in this paper
+\end{itemize}
+
 \bibliography{ju-hofmann.bib}

### 2022-03-24 submissions/submission-ju-hofmann/ju-hofmann.tex
reorganize the folder

--- 2021-10-28 ju-hofmann/ju-hofmann.tex
@@
 open-source implementation of the CMPS algorithm in the R package
-\pkg{cmpsR} available from Github
+\pkg{cmpsR} available from both CRAN and Github
 \url{https://github.com/willju-wangqian/cmpsR}. This publicly available
@@
 scans were publicly available at the time.
-\hh{XXX Let's take out this statement once we hear back from NIST} In
-order to show that our implementation of the CMPS algorithm is able to
+(\hh{We have asked the authors of}
+\citet{cmps}\hh{, and we are still waiting for the replies.}) In order
+to show that our implementation of the CMPS algorithm is able to
 reproduce the results in \citet{cmps} and be used for other data sets,
@@
 %
-\url{https://github.com/willju-wangqian}\\%
-\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}\\%
-\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}%
+\url{https://github.com/willju-wangqian}%
+\\\textit{ORCiD: \href{https://orcid.org/0000-0002-9977-377X}{0000-0002-9977-377X}}%
+\\\href{mailto:wju@iastate.edu}{\nolinkurl{wju@iastate.edu}}
 }
@@
 %
-\url{https://github.com/heike}\\%
-\textit{ORCiD: \href{https://orcid.org/0000-0002-9079-593X}{0000-0002-9079-593X}}\\%
-\href{mailto:hofmann@iastate.edu}{\nolinkurl{hofmann@iastate.edu}}%
-}
+\url{https://github.com/heike}%
+\\\textit{ORCiD: \href{https://orcid.org/0000-0002-9079-593X}{0000-0002-9079-593X}}%
+\\\href{mailto:hofmann@iastate.edu}{\nolinkurl{hofmann@iastate.edu}}
+}

### 2022-03-24 submissions/resubmission-ju-hofmann2/ju-hofmann.R

@@ -1,0 +1,675 @@
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE----------------------
+library(knitr)
+library(kableExtra)
+library(tidyverse)
+library(patchwork)
+library(ggpubr)
+
+## ----func, echo=FALSE-----------------------------------------------------
+bootstrap_k <- function(scores, k, K, value) {
+  res <- replicate(K, {
+    mean(sample(scores, size = k, replace = TRUE), na.rm = TRUE)
+  })
+  sum(res >= value) / K
+}
+
+compute_average_scores <- function(land1, land2, score, addNA = FALSE) {
+  if (!is.numeric(land1)) land1 <- readr::parse_number(as.character(land1))
+  if (!is.numeric(land2)) land2 <- readr::parse_number(as.character(land2))
+  # assert_that(is.numeric(land1), is.numeric(land2), is.numeric(score))
+
+  maxland <- max(land1, land2)
+  fullframe <- data.frame(expand.grid(land1 = 1:maxland, land2 = 1:maxland))
+  bcompare <- data.frame(land1, land2, score)
+
+  fullframe <- fullframe %>% left_join(bcompare, by = c("land1", "land2"))
+
+  fullframe <- fullframe %>% mutate(
+    land1 = factor(land1, levels = 1:maxland),
+    land2 = factor(land2, levels = 1:maxland)
+  )
+  # get averages, just in case
+  matrix <- xtabs(score ~ land1 + land2,
+    data = fullframe, addNA = addNA
+  ) / xtabs(~land1 + land2, data = fullframe, addNA = addNA)
+
+  matrix <- cbind(matrix, matrix)
+
+  scores <- 1:maxland %>% sapply(FUN = function(i) {
+    if (i == 1) {
+      mean(diag(matrix), na.rm = TRUE)
+    } else {
+      i <- i - 1
+      mean(diag(matrix[, -(1:i)]), na.rm = TRUE)
+    }
+  })
+  scores
+}
+
+bullet_to_land_predict <- function(land1, land2, scores, difference, alpha = 0.05, addNA = FALSE) {
+  if (!is.numeric(land1)) land1 <- readr::parse_number(as.character(land1))
+  if (!is.numeric(land2)) land2 <- readr::parse_number(as.character(land2))
+  avgs <- compute_average_scores(land2, land1, scores, addNA)
+
+  p <- max(c(land1, land2))
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_npeak_result_generator.R

@@ -1,0 +1,371 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("func_collection.R")
+
+data_path <- "./data-csv/hamby252/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
+keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
+keyss <- tibble(specimen = keyss)
+keyss <- keyss %>% mutate(
+  barrel = specimen %>% str_split(" "),
+  barrel.id = purrr::map_chr(barrel, function(bb) {
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_rf_result_generator.R

@@ -1,0 +1,269 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+source("func_collection.R")
+
+data_path <- "./data-csv/hamby252/"
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
+b252$sig_rf <- b252$sigs25
+
+rf.model <- readRDS("./csafe_rf2.rds")
+
+# generate bullet_id
+bulletid.tb <- b252 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# get bullet id
+b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
+
+# get all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# remove damaged data
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+######################################
+# add ground-truth for hamby 252
+studyinfo <-
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_seg_result_generator.R

@@ -1,0 +1,359 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("func_collection.R")
+
+data_path <- "./data-csv/hamby252/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
+keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
+keyss <- tibble(specimen = keyss)
+keyss <- keyss %>% mutate(
+  barrel = specimen %>% str_split(" "),
+  barrel.id = purrr::map_chr(barrel, function(bb) {
+    bb[1]
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_npeak_result_generator.R

@@ -1,0 +1,372 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("func_collection.R")
+
+data_path <- "./data-csv/hamby44/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
+                "J",
+                "H",
+                "I",
+                "Y",
+                "G",
+                "E",
+                "U",
+                "X",
+                "F",
+                "T",
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_rf_result_generator.R

@@ -1,0 +1,265 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+source("func_collection.R")
+
+data_path <- "./data-csv/hamby44/"
+
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
+b44$sig_rf <- b44$sigs25_531
+
+rf.model <- readRDS("./csafe_rf2.rds")
+
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+# generate bullet_id
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# get all comparisons
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# get ground-truth
+key.table <- tibble(
+  bullet.id = c(
+    "K",
+    "O",
+    "L",
+    "P",
+    "J",
+    "H",
+    "I",
+    "Y",
+    "G",
+    "E",
+    "U",
+    "X",
+    "F",
+    "T",
+    "S"
+  ),
+  barrel.id = c(1, 2, 3, 4, 4, 5, 5, 6, 6, 7, 7, 7, 8, 9, 10)
+)
+
+tmp.table.44 <- tibble(bullet1 = b.cb[1, ],
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_seg_result_generator.R

@@ -1,0 +1,363 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+###############################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr)) {
+  devtools::install_github("heike/bulletxtrctr")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("func_collection.R")
+
+data_path <- "./data-csv/hamby44/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
+                "J",
+                "H",
+                "I",
+                "Y",
+                "G",
+                "E",
+                "U",
+                "X",
+                "F",
+                "T",
+                "S"),
[…]

### 2022-03-24 submissions/resubmission-ju-hofmann2/supplementary-files/rds_generator.R

@@ -1,0 +1,311 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that ./data-csv/" is available
+###############################
+
+###############################
+# for the random forest model
+rf.results <- list()
+rf.results[[1]] <- read.csv(file = "./data-csv/hamby252/hamby252_rf_results.csv")
+rf.results[[2]] <- read.csv(file = "./data-csv/hamby44/hamby44_rf_results.csv")
+
+###############################
+# hamby 252 segments
+N <- 8 # the number of different sets of parameters
+CMPS_hamby252_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
+CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
+# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
+
+#### setup npeaks.set
+CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
+
+#### setup seg_length
+CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
+
+#### setup Tx
+CMPS_hamby252_results$Tx <- as.list(rep(25, N))
+
+#### setup outlength
+CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
+
+#### create a plot title and a file name for each set of parameters
+CMPS_hamby252_results$titlee <- list()
+CMPS_hamby252_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby252_results$titlee[[i]] <-
+    paste0(
+      "npeaks.set=c(",
+      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby252_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby252_results$filename[[i]] <- 
+    paste(
+      "hamby252_segment",
+      CMPS_hamby252_results$span1[[i]]*100,
[…]

### 2022-03-24 submissions/submission-ju-hofmann/ju-hofmann.R

@@ -1,0 +1,986 @@
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE------
+library(knitr)
+library(tidyverse)
+library(bulletxtrctr)
+library(kableExtra)
+library(patchwork)
+library(ggpubr)
+
+source("../code/func_collection.R")
+
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  out.width = "\\textwidth",
+  fig.align = "center",
+#  cache=TRUE,
+  dpi = 100,
+  warning = FALSE,
+  message = FALSE
+)
+
+
+## ----setup_knitr, echo=FALSE------------------------------
+## From Josh O'Brien's stackoverflow answer:
+## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
+## These two settings control text width in codefig vs. usual code blocks
+partWidth <- 35
+fullWidth <- 60
+options(width = fullWidth)
+
+##  (1) CHUNK HOOK FUNCTION
+##   First, to set R's textual output width on a per-chunk basis, we
+## need to define a hook function which temporarily resets global R's
+## option() settings, just for the current chunk
+knit_hooks$set(r.opts = local({
+    ropts <- NA
+    function(before, options, envir) {
+        if (before) {
+            ropts <<- options(options$r.opts)
+        } else {
+            options(ropts)
+        }
+    }
+}))
+
+## (2) OUTPUT HOOK FUNCTION
+
+##   Define a custom output hook function. This function processes _all_
+## evaluated chunks, but will return the same output as the usual one,
+## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
+## case, wrap the usual textual output in LaTeX code placing it in a
+## narrower adjustbox environment and setting the graphics that it
+## produced in another box beside it.
+
+defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
+
+codefigChunkHook <- function(x, options) {
+  main <-  defaultChunkHook(x, options)
+  before <-
+    "\\vspace{1em}
+\\begin{adjustbox}{valign=t}
+\\begin{minipage}{.39\\textwidth}\n"
+  after <-
+    paste("\\vspace{1em}
+\\end{minipage}
[…]

### 2022-03-24 submissions/submission-ju-hofmann/reproducible/hamby252_npeak_result_generator.R

@@ -1,0 +1,369 @@
+##########################
+# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
+#       These rds files contain processed bullet signatures used in the paper
+#       The original data contains x3p objects of large size, so they are not
+#       uploaded to the Github repo
+##########################
+
+## Load the required packages
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("code/func_collection.R")
+
+#### code used to load the original data; commented out
+# b252.full <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./reproducible/bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
+keyss <- studyinfo$`Specimen ID`[-length(studyinfo$`Specimen ID`)]
+keyss <- tibble(specimen = keyss)
+keyss <- keyss %>% mutate(
+  barrel = specimen %>% str_split(" "),
[…]

### 2022-03-24 submissions/submission-ju-hofmann/reproducible/hamby252_rf_result_generator.R

@@ -1,0 +1,264 @@
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+source("code/func_collection.R")
+
+# b252.full <-
+#   readRDS("C:/Research/Bullet/Bullet_Rcode/hamby252/bullets_hamby252_Sep9.rds")
+b252.full <- 
+  readRDS("~/Research/CMPSpaper/preconsideration/bullets_hamby252_Sep9.rds")
+
+rf.model <- readRDS("~/Desktop/csafe_rf2.rds")
+
+# generate bullet_id
+bulletid.tb <- b252.full %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+
+# remove x3p files
+b252 <- b252.full %>% select(-x3p,-crosscut,-grooves,-ccdata)
+
+# get bullet id
+b252$bullet_id <- bulletid.tb %>% pull(bullet_id)
+
+# get all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+# remove damaged data
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+######################################
+# add ground-truth for hamby 252
+studyinfo <-
+  readxl::read_xlsx(
+    "~/Research/CMPSpaper/preconsideration/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+# readxl::read_xlsx(
[…]

### 2022-03-24 submissions/submission-ju-hofmann/reproducible/hamby44_npeak_result_generator.R

@@ -1,0 +1,371 @@
+##########################
+# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
+#       These rds files contain processed bullet signatures used in the paper
+#       The original data contains x3p objects of large size, so they are not
+#       uploaded to the Github repo
+##########################
+
+
+## Load the required packages
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("code/func_collection.R")
+
+#### code used to load the original data; commented out
+# b44.full <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
+                "J",
+                "H",
+                "I",
+                "Y",
+                "G",
+                "E",
+                "U",
+                "X",
+                "F",
+                "T",
[…]

### 2022-03-24 submissions/submission-ju-hofmann/reproducible/hamby44_seg_result_generator.R

@@ -1,0 +1,362 @@
+##########################
+# Note: This R script uses rds files in reproducible/bullet_signatures_etc/
+#       These rds files contain processed bullet signatures used in the paper
+#       The original data contains x3p objects of large size, so they are not
+#       uploaded to the Github repo
+##########################
+
+
+## Load the required packages
+library(tidyverse)
+library(bulletxtrctr)
+library(x3ptools)
+library(CMPS)
+library(ggpubr)
+library(parallel)
+
+source("code/func_collection.R")
+
+#### code used to load the original data; commented out
+# b44.full <- 
+#   readRDS("~/Research/CMPSpaper/preconsideration/hamby44_manual5.rds")
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./reproducible/bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
+                "J",
+                "H",
+                "I",
+                "Y",
+                "G",
+                "E",
+                "U",
+                "X",
+                "F",
+                "T",
[…]

### 2022-03-27 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
ready for parallel testing on Windows

--- 2022-03-24 submissions/resubmission-ju-hofmann/ju-hofmann.Rmd
@@
 )
-
 ```
@@
 \\begin{minipage}{.59\\textwidth}",
-    paste0("\\includegraphics[width=\\textwidth]{ju-hofmann_files/figure-latex/",
+      paste0(
+        "\\includegraphics[width=\\textwidth]{ju-hofmann_files/figure-latex/",
         options[["label"]], "-1.pdf}
 \\end{minipage}
-\\end{adjustbox}"),
-          sep = "\n")
+\\end{adjustbox}"
+      ),
+      sep = "\n"
+    )
   ## Was a codefig option supplied in chunk header?
@@
   if (!is.null(options$codefig)) {
-    main <- gsub("```","", main)
-    main <- gsub("=latex","", main)
+    main <- gsub("```", "", main)
+    main <- gsub("=latex", "", main)
     main <- paste0("{\\small ", main, "}")
@@
 opts_template[["set"]](
-codefig = list(codefig = TRUE, fig.show = "hide",
+  codefig = list(
+    codefig = TRUE, fig.show = "hide",
     r.opts = list(width = partWidth),
-               tidy.opts = list(width.cutoff = partWidth)))
+    tidy.opts = list(width.cutoff = partWidth)
+))
 ```
@@
     data = fullframe, addNA = addNA
-  ) / xtabs(~land1 + land2, data = fullframe, addNA = addNA)
+  ) / xtabs(~ land1 + land2, data = fullframe, addNA = addNA)
 
@@
 
-cmps.result.KM <- extract_feature_cmps(sig1, sig2)
-cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
+cmps_result_KM <- extract_feature_cmps(sig1, sig2)
+cmps_result_KNM <- extract_feature_cmps(sig1, sig3)
 ```
@@
 The latter is also called "multi-segment lengths strategy".
-The parameter \code{npeaks.set} in \code{extract\_feature\_cmps(...)} determines which strategy to use and the number of candidate positions:
-
-        -   If \code{npeaks.set} is an integer vector of length 1, for example \code{npeaks.set = 5}, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If \code{npeaks.set} is an integer vector of length more than 1, for example \code{npeaks.set = c(5, 3, 1)}, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
+The parameter \code{npeaks\_set} in \code{extract\_feature\_cmps(...)} determines which strategy to use and the number of candidate positions:
+
+        -   If \code{npeaks\_set} is an integer vector of length 1, for example \code{npeaks\_set = 5}, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
+        -   If \code{npeaks\_set} is an integer vector of length more than 1, for example \code{npeaks\_set = c(5, 3, 1)}, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
 \autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
@@
 If the multi-segment lengths strategy is used, then \code{get\_ccr\_peaks(...)} is called in a \code{lapply()} for each level of the basis segment.
-The resulting list is called \code{ccr.list}.
+The resulting list is called \code{ccr\_list}.
 
@@
 \code{out\_length} specifies the length of the output segment.
-        -   \code{get\_ccp(ccr.list, Tx = 25)} tries to identify the "consistent correlation peak".
-\code{ccr.list} is the result of \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx} determines the size of a tolerance zone used in identifying the consistent correlation peak.
+        -   \code{get\_ccp(ccr\_list, Tx = 25)} tries to identify the "consistent correlation peak".
+\code{ccr\_list} is the result of \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx} determines the size of a tolerance zone used in identifying the consistent correlation peak.
 \code{get\_ccp(...)} returns \code{NULL} if there is no consistent correlation peak.
@@
     The total number of CMPS is the CMPS score of the comparison.
-    \code{get\_CMPS(input.ccp, Tx = 25)} is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
-
-Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks.set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
+    \code{get\_CMPS(input\_ccp, Tx = 25)} is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
+
+Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
@@
   Tx = 25,
-  npeaks.set = c(5, 3, 1),
+  npeaks_set = c(5, 3, 1),
   include = NULL,
@@
 
-The function \code{extract\_feature\_cmps} allows for the following input from users besides the previously discussed parameters \code{seg\_length}, \code{npeaks.set}, and \code{Tx}:
+The function \code{extract\_feature\_cmps} allows for the following input from users besides the previously discussed parameters \code{seg\_length}, \code{npeaks\_set}, and \code{Tx}:
 
@@
 -   \code{include} determines the format of the function result.
-    Besides the \code{CMPS.score}, other aspects of the comparison help in understanding how the \code{CMPS.score} is computed.
-    By default \code{include} is set to \code{NULL} and only the \code{CMPS.score} is returned; further results are included when \code{include} is (an abbreviation of) one of or a vector of the following strings: \code{"nseg"}, \code{"congruent.pos"}, \code{"congruent.seg.idx"}, \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}.
+    Besides the \code{CMPS\_score}, other aspects of the comparison help in understanding how the \code{CMPS\_score} is computed.
+    By default \code{include} is set to \code{NULL} and only the \code{CMPS\_score} is returned; further results are included when \code{include} is (an abbreviation of) one of or a vector of the following strings: \code{"nseg"}, \code{"congruent\_pos"}, \code{"congruent\_seg\_idx"}, \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}.
     If \code{include} is specified as \code{"full\_result"} (or its abbreviation), the output includes everything listed below.
@@
     -   \code{nseg}: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
-    -   \code{congruent.pos}: the congruent registration position;
-    -   \code{congruent.seg.idx}: the indices of all congruent matching profile segments;
-    -   \code{ccp.list}: a list showing identified candidate positions of all basis segments;
-    -   \code{pos.df}: a data frame containing all candidate positions and their respective number of votes;
+    -   \code{congruent\_pos}: the congruent registration position;
+    -   \code{congruent\_seg\_idx}: the indices of all congruent matching profile segments;
+    -   \code{ccp\_list}: a list showing identified candidate positions of all basis segments;
+    -   \code{pos\_df}: a data frame containing all candidate positions and their respective number of votes;
     -   \code{segments}: a list containing all basis segments;
@@
 signatures <- signatures %>% mutate(
-  bulletland = factor(bulletland, levels=c(paste(rep(c(1,2), each=6), c(1:6,2:6,1), sep="-")))
-)
-signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
+  bulletland = factor(bulletland, levels = c(paste(rep(c(1, 2), each = 6), c(1:6, 2:6, 1), sep = "-")))
+)
+signatures %>% ggplot(aes(x = x / 1000, y = sig)) +
+  geom_line() +
+  facet_wrap(~bulletland, ncol = 6) +
   theme_bw() +
@@
   extract_feature_cmps(sigs1$sig, sigs2$sig,
-                       npeaks.set = c(5,3,1), include = "full_result")
+    npeaks_set = c(5, 3, 1), include = "full_result"
+  )
 
@@
   extract_feature_cmps(sigs1$sig, sigs2$sig,
-                       npeaks.set = 5, include = "full_result")
-```
-
-In the first example, \code{npeaks.set} is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object \code{cmps\_with\_multi\_scale}.
+    npeaks_set = 5, include = "full_result"
+  )
+```
+
+In the first example, \code{npeaks\_set} is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object \code{cmps\_with\_multi\_scale}.
 For \code{cmps\_without\_multi\_scale} each basis segment is linked to the top 5 candidate positions.
@@
 comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]),
-                          stringsAsFactors = FALSE)
+  stringsAsFactors = FALSE
+)
 
 comparisons <- comparisons %>%
-  left_join(bullets %>% select(bulletland, sig1=sigs),
-            by = c("land1" = "bulletland")) %>%
-  left_join(bullets %>% select(bulletland, sig2=sigs),
-            by = c("land2" = "bulletland"))
+  left_join(bullets %>% select(bulletland, sig1 = sigs),
+    by = c("land1" = "bulletland")
+  ) %>%
+  left_join(bullets %>% select(bulletland, sig2 = sigs),
+    by = c("land2" = "bulletland")
+  )
 
@@
   mutate(
-    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
+    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS_score),
     cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg),
@@
 
-dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
+dframe$samesource <- with(dframe, bullet_to_land_predict(land1 = landA, land2 = landB, cmps_score, difference = 1))
 ```
@@
 ```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-sig.plot <- cmps_signature_plot(
+sig_plot <- cmps_signature_plot(
   cmps_with_multi_scale
 )
-sig.plot$segment_shift_plot
+sig_plot$segment_shift_plot
 ```
@@
 ```{r sigplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-sig.plot$signature_shift_plot
+sig_plot$signature_shift_plot
 ```
@@
 ```{r, echo=TRUE, eval=TRUE}
-sig.plot$seg_shift
+sig_plot$seg_shift
 ```
@@
 While \code{cmps\_signature\_plot()} focuses on the signature level, \code{cmps\_segment\_plot()} focuses on the segment level.
-It provides the "full result" of \code{extract\_feature\_cmps()}, but also takes an argument, \code{seg.idx}, indicating which segment should be inspected.
-When checking \code{sig.plot\$seg\_shift} we notice that segment number 6 is not one of the congruent matching profile segments.
-We can therefore set \code{seg.idx = 6} in \code{cmps\_segment\_plot()} and investigate the reason why this segment disagrees with the congruent registration position.
+It provides the "full result" of \code{extract\_feature\_cmps()}, but also takes an argument, \code{seg\_idx}, indicating which segment should be inspected.
+When checking \code{sig\_plot\$seg\_shift} we notice that segment number 6 is not one of the congruent matching profile segments.
+We can therefore set \code{seg\_idx = 6} in \code{cmps\_segment\_plot()} and investigate the reason why this segment disagrees with the congruent registration position.
 
@@
 -   \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6 at level one (in its original length).
-We used \code{npeaks.set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when calculating the CMPS score.
+We used \code{npeaks\_set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when calculating the CMPS score.
 Therefore the top five peaks are identified in the cross-correlation curve at level one.
@@
 ```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-seg.plot <- cmps_segment_plot(
+seg_plot <- cmps_segment_plot(
   cmps_with_multi_scale,
-  seg.idx = 6
-)
-seg.plot[[1]]$segment_plot
+  seg_idx = 6
+)
+seg_plot[[1]]$segment_plot
 ```
@@
 ```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
-seg.plot[[1]]$scale_ccf_plot
+seg_plot[[1]]$scale_ccf_plot
 ```
@@
   plotlist =
-    unlist(seg.plot, 
-           recursive = FALSE),
+    unlist(seg_plot,
+      recursive = FALSE
+    ),
   ncol = 2,
-  nrow = 3)
+  nrow = 3
+)
 ```
 \caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1).
+We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1).
 The highest peak position at level three is marked by the green dashed line across all segment levels.
@@
   landB = paste0("L", landB),
-  landB = factor(landB, levels = paste0("L", c(2:6,1))),
+  landB = factor(landB, levels = paste0("L", c(2:6, 1))),
   bulletA = paste0("Bullet ", bulletA),
@@
   geom_tile() +
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  geom_tile(aes(colour = "same land"), fill = NA, data = dframe %>% filter(samesource), size = 1) +
   scale_fill_gradient2("CMPS score", low = "gray80", high = "darkorange", midpoint = 6) +
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  scale_colour_manual("Source", values = "darkorange") +
+  facet_grid(bulletB ~ bulletA) +
+  xlab("Bullet1 Lands") +
   ylab("Bullet2 Lands") +
-  geom_text(aes(label=cmps_score)) +
+  geom_text(aes(label = cmps_score)) +
   theme_bw() +
@@
   geom_tile(fill = "grey") +
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  geom_tile(aes(colour = "same land"), fill = NA, data = dframe %>% filter(samesource), size = 1) +
+  scale_colour_manual("Source", values = "darkorange") +
+  facet_grid(bulletB ~ bulletA) +
+  xlab("Bullet1 Lands") +
   ylab("Bullet2 Lands") +
-  geom_text(aes(label=cmps_nseg)) +
+  geom_text(aes(label = cmps_nseg)) +
   theme_bw() +
@@
   geom_tile() +
-  geom_tile(aes(colour="same land"), fill=NA, data = dframe %>% filter(samesource), size=1) + 
+  geom_tile(aes(colour = "same land"), fill = NA, data = dframe %>% filter(samesource), size = 1) +
   scale_fill_gradient2("Scaled CMPS", low = "gray80", high = "darkorange", midpoint = 0.3) +
-  scale_colour_manual("Source", values="darkorange") +
-  facet_grid(bulletB ~ bulletA) + xlab("Bullet1 Lands") + 
+  scale_colour_manual("Source", values = "darkorange") +
+  facet_grid(bulletB ~ bulletA) +
+  xlab("Bullet1 Lands") +
   ylab("Bullet2 Lands") +
-  geom_text(aes(label=round(cmps_scaled, 2))) +
+  geom_text(aes(label = round(cmps_scaled, 2))) +
   theme_bw() +
@@
 ggarrange(p1, p2,
-          common.legend = TRUE, legend = "bottom", labels = c("(a)", "(b)"))
+  common.legend = TRUE, legend = "bottom", labels = c("(a)", "(b)")
+)
 ```
@@
   })
-}) %>% do.call(rbind, .) %>% as_tibble()
+}) %>%
+  do.call(rbind, .) %>%
+  as_tibble()
 
@@
 rf.tt$npeak <- "RF score* (Hare et al)"
-
 ```
@@
   score = c(9:13, 16:24),
-  freq = c(132, 282, 115, 19, 1, 1, 3,2,4,8,12,7,7,2),
+  freq = c(132, 282, 115, 19, 1, 1, 3, 2, 4, 8, 12, 7, 7, 2),
   type = c(rep("KNM", 5), rep("KM", 9))
@@
   score = c(1:5, 14:23),
-  freq = c(7,343,168,24,7,1,1,2,3,6,7,8,8,7,3),
+  freq = c(7, 343, 168, 24, 7, 1, 1, 2, 3, 6, 7, 8, 8, 7, 3),
   type = c(rep("KNM", 5), rep("KM", 10))
@@
   score = c(6:9, 13:19),
-  freq = c(2,210,307,30,6,3,9,9,11,7,1),
+  freq = c(2, 210, 307, 30, 6, 3, 9, 9, 11, 7, 1),
   type = c(rep("KNM", 4), rep("KM", 7))
@@
   score = c(0:2, 8:17),
-  freq = c(36, 508, 5, 1,3,4,2,11,3,9,8,4,1),
+  freq = c(36, 508, 5, 1, 3, 4, 2, 11, 3, 9, 8, 4, 1),
   type = c(rep("KNM", 3), rep("KM", 10))
@@
 
-result.container <- result.container %>% as_tibble() %>% 
+result.container <- result.container %>%
+  as_tibble() %>%
   mutate(
     dd.table = purrr::map(dd.list, function(dd) {
-      tibble(score = rep(dd$score, dd$freq),
-             type_truth = rep(dd$type, dd$freq))
+      tibble(
+        score = rep(dd$score, dd$freq),
+        type_truth = rep(dd$type, dd$freq)
+      )
     }),
@@
   Tx = 25,
-  npeaks.set = c(5,3,1),
+  npeaks_set = c(5, 3, 1),
   include = "nseg"
@@
 })
-
 ```
@@
 
-cols_1 <- c("#748BA7", "#C583AE","#FFDFAA", "#D9F0A0")
-cols_2 <- c("#4C688B", "#A45287","#D4AC6A", "#ABC864")
+cols_1 <- c("#748BA7", "#C583AE", "#FFDFAA", "#D9F0A0")
+cols_2 <- c("#4C688B", "#A45287", "#D4AC6A", "#ABC864")
 # #####  Color Palette by Paletton.com
@@
   type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_ss_ratio, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
+  tt %>%
+    select(cmps.diff:cmps.maxbar_scaled) %>%
+    apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
+}) %>%
+  do.call(rbind, .) %>%
+  as.data.frame()
 
@@
 table.252.cmps_seg.long <- table.252.cmps_seg %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, 
-                        cmps.max, cmps.maxbar), 
-               names_to = "Metric")
+  pivot_longer(
+    cols = c(
+      cmps.diff, cmps.diff_scaled,
+      cmps.max, cmps.maxbar
+    ),
+    names_to = "Metric"
+  )
 
@@
 
-labels <- expression( CMPS[max], bar(CMPS)[diff], {bar(CMPS)^symbol("*")}[diff], bar(CMPS)[max])
+labels <- expression(
+  CMPS[max],
+  bar(CMPS)[diff],
+  {
+    bar(CMPS)^symbol("*")
+  }[diff],
+  bar(CMPS)[max]
+)
 
 p.seg_252_plot <- table.252.cmps_seg.long %>%
-  ggplot(aes(x = seg_length +3*as.numeric(factor(Metric))-9)) +
-  geom_segment(aes(xend =  seg_length +3*as.numeric(factor(Metric))-9,
-               y = value, yend = 0, colour = Metric)) + 
+  ggplot(aes(x = seg_length + 3 * as.numeric(factor(Metric)) - 9)) +
+  geom_segment(aes(
+    xend = seg_length + 3 * as.numeric(factor(Metric)) - 9,
+    y = value, yend = 0, colour = Metric
+  )) +
   geom_point(aes(y = value, color = Metric),
     alpha = 0.8,
-             position=position_dodge(width = 0.5), size = 3.5) +
-  scale_x_continuous(breaks = table.252.cmps_seg$seg_length, 
-                     minor_breaks = NULL) +
+    position = position_dodge(width = 0.5), size = 3.5
+  ) +
+  scale_x_continuous(
+    breaks = table.252.cmps_seg$seg_length,
+    minor_breaks = NULL
+  ) +
   theme_bw() +
@@
   xlab("Segment Length") +
-  scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels)
+  scale_colour_manual(values = cols_2, labels = labels) +
+  scale_fill_manual(values = cols_1, labels = labels)
 
@@
 table.44.cmps_seg.long <- table.44.cmps_seg %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, 
-                        cmps.max, cmps.maxbar),
-               names_to = "Metric")
+  pivot_longer(
+    cols = c(
+      cmps.diff, cmps.diff_scaled,
+      cmps.max, cmps.maxbar
+    ),
+    names_to = "Metric"
+  )
 
@@
 
-table.cmps_seg.long <- bind_rows(table.44.cmps_seg.long,
-                                 table.252.cmps_seg.long)
+table.cmps_seg.long <- bind_rows(
+  table.44.cmps_seg.long,
+  table.252.cmps_seg.long
+)
 
 breaks_fun <- function(x) {
-  if(x[2] < 220) {
+  if (x[2] < 220) {
     c(25, 50, 75, 100, 125, 150, 175, 200)
@@
     Metric = factor(Metric,
-                    levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
+      levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar")
+    )
   ) %>%
-  ggplot(aes(x = seg_length+3*as.numeric((Metric))-9)) +
-  geom_segment(aes(xend = seg_length+3*as.numeric((Metric))-9, 
-                   y = value, yend= 0, color=Metric),
-               position=position_dodge(width = 0.6)) +
+  ggplot(aes(x = seg_length + 3 * as.numeric((Metric)) - 9)) +
+  geom_segment(aes(
+    xend = seg_length + 3 * as.numeric((Metric)) - 9,
+    y = value, yend = 0, color = Metric
+  ),
+  position = position_dodge(width = 0.6)
+  ) +
   geom_point(aes(y = value, color = Metric),
     alpha = 0.8,
-             position=position_dodge(width = 0.5), size = 3.5) +
-  facet_grid(.~study, scales = "free_x") +
-  scale_x_continuous(breaks = breaks_fun, 
-                     minor_breaks = NULL) +
+    position = position_dodge(width = 0.5), size = 3.5
+  ) +
+  facet_grid(. ~ study, scales = "free_x") +
+  scale_x_continuous(
+    breaks = breaks_fun,
+    minor_breaks = NULL
+  ) +
   theme_bw() +
@@
   xlab("Segment length") +
-  scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels)
+  scale_colour_manual(values = cols_2, labels = labels) +
+  scale_fill_manual(values = cols_1, labels = labels)
 
@@
   type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_ss_ratio, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks.set %>% 
-  purrr::map(.f = paste, collapse = "-") %>% sapply(as.character)
-
-table.252.cmps_npeak.longer <- table.252.cmps_npeak %>% as_tibble() %>% 
+  tt %>%
+    select(cmps.diff:cmps.maxbar_scaled) %>%
+    apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
+}) %>%
+  do.call(rbind, .) %>%
+  as.data.frame()
+
+table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks_set %>%
+  purrr::map(.f = paste, collapse = "-") %>%
+  sapply(as.character)
+
+table.252.cmps_npeak.longer <- table.252.cmps_npeak %>%
+  as_tibble() %>%
   filter(npeak %in% c("5", "5-3-1", "10-8-6-4-2-1", "10-7-4-2")) %>%
@@
       npeak,
-      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
+      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)]
+    )
   ) %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
-               names_to = "Metric") 
+  pivot_longer(
+    cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+    names_to = "Metric"
+  )
 table.252.cmps_npeak.longer$study <- "Hamby 252"
@@
   type_truth <- tt$type_truth
-  tt %>% select(cmps.diff:cmps.maxbar_scaled) %>% 
-    apply(2, compute_ss_ratio, label=type_truth, MS=FALSE)
-}) %>% do.call(rbind, .) %>% as.data.frame()
-
-table.44.cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks.set %>% 
-  purrr::map(.f = paste, collapse = "-") %>% sapply(as.character)
-
-table.44.cmps_npeak.longer <- table.44.cmps_npeak %>% as_tibble() %>% 
+  tt %>%
+    select(cmps.diff:cmps.maxbar_scaled) %>%
+    apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
+}) %>%
+  do.call(rbind, .) %>%
+  as.data.frame()
+
+table.44.cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks_set %>%
+  purrr::map(.f = paste, collapse = "-") %>%
+  sapply(as.character)
+
+table.44.cmps_npeak.longer <- table.44.cmps_npeak %>%
+  as_tibble() %>%
   filter(npeak %in% c("5", "5-3-1", "10-8-6-4-2-1", "10-7-4-2")) %>%
@@
       npeak,
-      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)])
+      levels = npeak[order(cmps.diff_scaled, decreasing = FALSE)]
+    )
   ) %>%
-  pivot_longer(cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
-               names_to = "Metric") 
+  pivot_longer(
+    cols = c(cmps.diff, cmps.diff_scaled, cmps.max, cmps.maxbar),
+    names_to = "Metric"
+  )
 table.44.cmps_npeak.longer$study <- "Hamby 44"
@@
   filter(Metric == "cmps.maxbar", study == "Hamby 252") %>%
-  {.$npeak[order(.$value, decreasing = FALSE)]}
+  {
+    .$npeak[order(.$value, decreasing = FALSE)]
+  }
 
@@
   rf_status = if_else(npeak == "RF score* (Hare et al)",
-                      TRUE, FALSE)
+    TRUE, FALSE
+  )
 )
@@
 p.npeak_plot <- table.cmps_neapk.long %>%
-  ggplot(aes(x = xstart + 3*as.numeric(factor(Metric))-9)) +
-  geom_segment(aes(xend = xstart + 3*as.numeric(factor(Metric))-9, 
-                   y = value, yend= 0, color=Metric),
-               position=position_dodge(width = 0.6)) +
+  ggplot(aes(x = xstart + 3 * as.numeric(factor(Metric)) - 9)) +
+  geom_segment(aes(
+    xend = xstart + 3 * as.numeric(factor(Metric)) - 9,
+    y = value, yend = 0, color = Metric
+  ),
+  position = position_dodge(width = 0.6)
+  ) +
   geom_point(aes(y = value, color = Metric, shape = rf_status),
     alpha = 0.8,
-             position=position_dodge(width = 0.5), size = 3.5) +
-  facet_grid(.~study) +
+    position = position_dodge(width = 0.5), size = 3.5
+  ) +
+  facet_grid(. ~ study) +
   ylab("Sums of Squares Ratio") +
@@
   coord_flip() +
-  scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak ) +
+  scale_x_continuous(breaks = npeak_convert$xstart, labels = npeak_convert$npeak) +
   theme_bw() +
@@
   scale_shape_manual(values = c(16, 1)) +
-  scale_colour_manual(values=cols_2, labels = labels) +
-  scale_fill_manual(values=cols_1, labels = labels) 
+  scale_colour_manual(values = cols_2, labels = labels) +
+  scale_fill_manual(values = cols_1, labels = labels)
 ```
@@
 
-```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3}
+```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"
@@
 p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
+  subtitle = "npeaks_set: 5-3-1, seg_length: 50"
+) +
   xlab(labels[1])
 p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 50") +
+  subtitle = "npeaks_set: 5-3-1, seg_length: 50"
+) +
   xlab(labels[4])
 
-p.result1_252 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
-               common.legend = TRUE, legend = "bottom")
+p.result1_252 <- ggarrange(
+  plotlist = list(p1, p2), nrow = 1, ncol = 2,
+  common.legend = TRUE, legend = "bottom"
+)
 p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
@@
   Tx = 30,
-  npeaks.set = c(5,3,1),
+  npeaks_set = c(5, 3, 1),
   include = "nseg"
@@
 
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks.set = c(5,3,1)} ", fig.height=3, warning=FALSE}
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3, warning=FALSE}
 p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
+  subtitle = "npeaks_set: 5-3-1, seg_length: 61"
+) +
   xlab(labels[1])
 p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
-                         subtitle = "npeaks.set: 5-3-1, seg_length: 61") +
+  subtitle = "npeaks_set: 5-3-1, seg_length: 61"
+) +
   xlab(labels[4])
-p.result1_44 <- ggarrange(plotlist = list(p1, p2), nrow = 1, ncol = 2,
-               common.legend = TRUE, legend = "bottom")
+p.result1_44 <- ggarrange(
+  plotlist = list(p1, p2), nrow = 1, ncol = 2,
+  common.legend = TRUE, legend = "bottom"
+)
 p.result1_44 <- annotate_figure(p.result1_44, top = text_grob(com.title44))
@@
 More specifically, we investigated the separation achieved using the \pkg{cmpsR} implementation under various segment lengths (controlled by the parameter \code{seg\_length}).
-Specifically, we fixed the parameter \code{npeaks.set} that controls the number of peaks at each segment level to be \code{npeaks.set = c(5,3,1)} and modified the parameter \code{seg\_length}.
+Specifically, we fixed the parameter \code{npeaks\_set} that controls the number of peaks at each segment level to be \code{npeaks\_set = c(5,3,1)} and modified the parameter \code{seg\_length}.
 \autoref{fig:param_seg_plot} shows that the default values of \code{seg\_length}  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
@@
 Basis segment length is fixed to the default level for this evaluation.
-As can be seen in \autoref{fig:param_npeak_plot}, the default value of \code{npeaks.set} (\code{npeaks.set = c(5,3,1)}) leads to promising results in terms of the sum of squares ratio; however, other choices of \code{npeaks.set} match and  exceed this sum of squares ratio value.
+As can be seen in \autoref{fig:param_npeak_plot}, the default value of \code{npeaks\_set} (\code{npeaks\_set = c(5,3,1)}) leads to promising results in terms of the sum of squares ratio; however, other choices of \code{npeaks\_set} match and  exceed this sum of squares ratio value.
 
@@
 
-@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for \code{npeaks.set = 5} and \code{npeaks.set = c(5,3,1)} with (presumably) Hamby 252.
+@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for \code{npeaks\_set = 5} and \code{npeaks\_set = c(5,3,1)} with (presumably) Hamby 252.
 The values in these histograms allow us to calculate the sum of squares ratios and include the results in \autoref{fig:param_npeak_plot} as well.
 They are marked by an asterisk at the top right corner in \autoref{fig:param_npeak_plot}.
-The sum of squares ratios we obtained for \code{npeaks.set = 5} and \code{npeaks.set = c(5,3,1)} is slightly higher than those obtained from the histograms of @cmps. 
+The sum of squares ratios we obtained for \code{npeaks\_set = 5} and \code{npeaks\_set = c(5,3,1)} is slightly higher than those obtained from the histograms of @cmps. 
 It's curious to see that for the Hamby 252 results published in @cmps the $\mathrm{{CMPS}_{max}}$ metric achieves values of the sum of squares ratio higher than those achieved by the $\mathrm{\overline{CMPS}_{max}}$ metric.

### 2022-03-27 submissions/resubmission-ju-hofmann2/ju-hofmann.tex
ready for parallel testing on Windows

--- 2022-03-24 submissions/resubmission-ju-hofmann/ju-hofmann.tex
@@
 
-cmps.result.KM <- extract_feature_cmps(sig1, sig2)
-cmps.result.KNM <- extract_feature_cmps(sig1, sig3)
+cmps_result_KM <- extract_feature_cmps(sig1, sig2)
+cmps_result_KNM <- extract_feature_cmps(sig1, sig3)
 \end{Sinput}
@@
     called ``multi-segment lengths strategy''. The parameter
-    \code{npeaks.set} in \code{extract\_feature\_cmps(...)} determines
+    \code{npeaks\_set} in \code{extract\_feature\_cmps(...)} determines
     which strategy to use and the number of candidate positions:
@@
     \item
-      If \code{npeaks.set} is an integer vector of length 1, for example
-      \code{npeaks.set = 5}, the positions of the top five peaks in the
-      cross-correlation curve are identified as candidate positions for
-      registration.
-    \item
-      If \code{npeaks.set} is an integer vector of length more than 1,
-      for example \code{npeaks.set = c(5, 3, 1)}, the multi-segment
+      If \code{npeaks\_set} is an integer vector of length 1, for
+      example \code{npeaks\_set = 5}, the positions of the top five
+      peaks in the cross-correlation curve are identified as candidate
+      positions for registration.
+    \item
+      If \code{npeaks\_set} is an integer vector of length more than 1,
+      for example \code{npeaks\_set = c(5, 3, 1)}, the multi-segment
       lengths strategy will be used: calculate the cross-correlation
@@
       \code{lapply()} for each level of the basis segment. The resulting
-      list is called \code{ccr.list}.
+      list is called \code{ccr\_list}.
     \end{itemize}
@@
     \item
-      \code{get\_ccp(ccr.list, Tx = 25)} tries to identify the
-      ``consistent correlation peak''. \code{ccr.list} is the result of
+      \code{get\_ccp(ccr\_list, Tx = 25)} tries to identify the
+      ``consistent correlation peak''. \code{ccr\_list} is the result of
       \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx}
@@
   The total number of CMPS is the CMPS score of the comparison.
-  \code{get\_CMPS(input.ccp, Tx = 25)} is the function that tallies the
+  \code{get\_CMPS(input\_ccp, Tx = 25)} is the function that tallies the
   votes and determines the congruent registration position and congruent
@@
 left to the users to decide, such as the length of basis segments
-\code{seg\_length} in step 1, the number of peaks \code{npeaks.set}
+\code{seg\_length} in step 1, the number of peaks \code{npeaks\_set}
 identified on each level in step 2, and the length of the tolerance zone
@@
 input from users besides the previously discussed parameters
-\code{seg\_length}, \code{npeaks.set}, and \code{Tx}:
+\code{seg\_length}, \code{npeaks\_set}, and \code{Tx}:
 
@@
   \code{include} determines the format of the function result. Besides
-  the \code{CMPS.score}, other aspects of the comparison help in
-  understanding how the \code{CMPS.score} is computed. By default
-  \code{include} is set to \code{NULL} and only the \code{CMPS.score} is
-  returned; further results are included when \code{include} is (an
+  the \code{CMPS\_score}, other aspects of the comparison help in
+  understanding how the \code{CMPS\_score} is computed. By default
+  \code{include} is set to \code{NULL} and only the \code{CMPS\_score}
+  is returned; further results are included when \code{include} is (an
   abbreviation of) one of or a vector of the following strings:
-  \code{"nseg"}, \code{"congruent.pos"}, \code{"congruent.seg.idx"},
+  \code{"nseg"}, \code{"congruent\_pos"}, \code{"congruent\_seg\_idx"},
   \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}. If
@@
   \item
-    \code{congruent.pos}: the congruent registration position;
-  \item
-    \code{congruent.seg.idx}: the indices of all congruent matching
+    \code{congruent\_pos}: the congruent registration position;
+  \item
+    \code{congruent\_seg\_idx}: the indices of all congruent matching
     profile segments;
   \item
-    \code{ccp.list}: a list showing identified candidate positions of
+    \code{ccp\_list}: a list showing identified candidate positions of
     all basis segments;
   \item
-    \code{pos.df}: a data frame containing all candidate positions and
+    \code{pos\_df}: a data frame containing all candidate positions and
     their respective number of votes;
@@
   extract_feature_cmps(sigs1$sig, sigs2$sig,
-                       npeaks.set = 5, include = "full_result")
+    npeaks_set = 5, include = "full_result"
+  )
 \end{Sinput}
@@
 
-In the first example, \code{npeaks.set} is a vector of three integers,
+In the first example, \code{npeaks\_set} is a vector of three integers,
 i.e.~the algorithm uses the multi-segment lengths strategy to create the
@@
 \begin{Sinput}
-sig.plot <- cmps_signature_plot(
+sig_plot <- cmps_signature_plot(
   cmps_with_multi_scale
 )
-sig.plot$segment_shift_plot
+sig_plot$segment_shift_plot
 \end{Sinput}
@@
 \begin{Sinput}
-sig.plot$signature_shift_plot
+sig_plot$signature_shift_plot
 \end{Sinput}
@@
 \begin{Sinput}
-sig.plot$seg_shift
+sig_plot$seg_shift
 \end{Sinput}
 \begin{Soutput}
-#>    seg.idx seg.shift
+#>    seg_idx seg_shift
 #> 7        7         0
@@
 the ``full result'' of \code{extract\_feature\_cmps()}, but also takes
-an argument, \code{seg.idx}, indicating which segment should be
-inspected. When checking \code{sig.plot\$seg\_shift} we notice that
+an argument, \code{seg\_idx}, indicating which segment should be
+inspected. When checking \code{sig\_plot\$seg\_shift} we notice that
 segment number 6 is not one of the congruent matching profile segments.
-We can therefore set \code{seg.idx = 6} in \code{cmps\_segment\_plot()}
+We can therefore set \code{seg\_idx = 6} in \code{cmps\_segment\_plot()}
 and investigate the reason why this segment disagrees with the congruent
@@
   at level one (in its original length). We used
-  \code{npeaks.set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when
-  calculating the CMPS score. Therefore the top five peaks are
+  \code{npeaks\_set = c(5, 3, 1)} in \code{extract\_feature\_cmps()}
+  when calculating the CMPS score. Therefore the top five peaks are
   identified in the cross-correlation curve at level one. Segment 6 is
@@
 \begin{Sinput}
-seg.plot <- cmps_segment_plot(
+seg_plot <- cmps_segment_plot(
   cmps_with_multi_scale,
-  seg.idx = 6
+  seg_idx = 6
 )
-seg.plot[[1]]$segment_plot
+seg_plot[[1]]$segment_plot
 \end{Sinput}
@@
 \begin{Sinput}
-seg.plot[[1]]$scale_ccf_plot
+seg_plot[[1]]$scale_ccf_plot
 \end{Sinput}
@@
   plotlist =
-    unlist(seg.plot, 
-           recursive = FALSE),
+    unlist(seg_plot,
+      recursive = FALSE
+    ),
   ncol = 2,
-  nrow = 3)
+  nrow = 3
+)
 \end{Sinput}
@@
 \caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks.set = c(5, 3, 1).
+We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1).
 The highest peak position at level three is marked by the green dashed line across all segment levels.
@@
 
-\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks.set = c(5,3,1)} }\label{fig:result1_252}
+\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_252}
 \end{figure}
@@
 
-\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks.set = c(5,3,1)} }\label{fig:result1_44}
+\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_44}
 \end{figure}
@@
 parameter \code{seg\_length}). Specifically, we fixed the parameter
-\code{npeaks.set} that controls the number of peaks at each segment
-level to be \code{npeaks.set = c(5,3,1)} and modified the parameter
+\code{npeaks\_set} that controls the number of peaks at each segment
+level to be \code{npeaks\_set = c(5,3,1)} and modified the parameter
 \code{seg\_length}. \autoref{fig:param_seg_plot} shows that the default
@@
 for this evaluation. As can be seen in \autoref{fig:param_npeak_plot},
-the default value of \code{npeaks.set} (\code{npeaks.set = c(5,3,1)})
+the default value of \code{npeaks\_set} (\code{npeaks\_set = c(5,3,1)})
 leads to promising results in terms of the sum of squares ratio;
-however, other choices of \code{npeaks.set} match and exceed this sum of
-squares ratio value.
+however, other choices of \code{npeaks\_set} match and exceed this sum
+of squares ratio value.
 
@@
 \citet{cmps} present histograms of \(\mathrm{CMPS_{max}}\) and
-\(\mathrm{\overline{CMPS}_{max}}\) for \code{npeaks.set = 5} and
-\code{npeaks.set = c(5,3,1)} with (presumably) Hamby 252. The values in
+\(\mathrm{\overline{CMPS}_{max}}\) for \code{npeaks\_set = 5} and
+\code{npeaks\_set = c(5,3,1)} with (presumably) Hamby 252. The values in
 these histograms allow us to calculate the sum of squares ratios and
@@
 \autoref{fig:param_npeak_plot}. The sum of squares ratios we obtained
-for \code{npeaks.set = 5} and \code{npeaks.set = c(5,3,1)} is slightly
+for \code{npeaks\_set = 5} and \code{npeaks\_set = c(5,3,1)} is slightly
 higher than those obtained from the histograms of \citet{cmps}. It's

### 2022-03-27 submissions/resubmission-ju-hofmann2/supplementary-files/rds_generator.R

@@ -21,8 +21,8 @@ CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
 CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
 # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
 
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
+#### setup npeaks_set
+CMPS_hamby252_results$npeaks_set <- lapply(1:N, function(t) c(5,3,1))
 
 #### setup seg_length
 CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
@@ -39,8 +39,8 @@ CMPS_hamby252_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby252_results$titlee[[i]] <-
     paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      "npeaks_set=c(",
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = ","),
       ")",
       ", len=",
       CMPS_hamby252_results$seg_length[[i]],
@@ -54,7 +54,7 @@ for (i in 1:N) {
     paste(
       "hamby252_segment",
       CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = "-"),
       CMPS_hamby252_results$seg_length[[i]],
       CMPS_hamby252_results$Tx[[i]],
       sep = "_"
@@ -88,8 +88,8 @@ CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
 CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
 # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
 
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- 
+#### setup npeaks_set
+CMPS_hamby252_results$npeaks_set <- 
   list(c(5),
        c(5,2),
        c(5,3,1),
@@ -118,8 +118,8 @@ CMPS_hamby252_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby252_results$titlee[[i]] <-
     paste0(
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/func_collection.R
update all the generator R files so that they can work with Windows

@@ -1,361 +1,361 @@
-library(assertthat)
-
-compute_var_ratio <- function(score, label) {
-  score.split <- split(score, label)
-  
-  group.mean <- sapply(score.split, mean, na.rm=TRUE)
-  
-  total.mean <- mean(score, na.rm = TRUE)
-  
-  var.between <- sum((group.mean - total.mean)^2)
-  var.within <- sum(sapply(score.split, var, na.rm = TRUE))
-  
-  var.ratio <- var.between / var.within
-  return(var.ratio)
-}
-
-compute_var_ratio_anova <- function(score, label, MS=TRUE) {
-  score.split <- split(score, label)
-  
-  group.mean <- sapply(score.split, mean, na.rm=TRUE)
-  group.count <- sapply(score.split, function(tt) sum(!is.na(tt)) )
-  total.mean <- mean(score, na.rm = TRUE)
-  
-  k <- length(unique(label))
-  n <- length(score)
-  
-  var.between <- sum((group.mean - total.mean)^2 * group.count)
-  var.within <- sum(sapply(score.split, function(tt) {
-    sum((tt - mean(tt, na.rm = TRUE))^2)
-  })) 
-  
-  var.ratio <- var.between / var.within
-  if(MS) {
-    var.ratio <- var.ratio * (n-k) / (k-1)
-  }
-  return(var.ratio)
-}
-
-get_all_phases <- function(land1, land2, score, addNA = FALSE)
-{
-  maxland <- max(land1, land2)
-  fullframe <- data.frame(expand.grid(land1 = 1:maxland, land2 = 1:maxland))
-  bcompare <- data.frame(land1, land2, score)
-  fullframe <- fullframe %>% left_join(bcompare, by = c("land1", 
-                                                        "land2"))
-  fullframe <- fullframe %>% mutate(land1 = factor(land1, levels = 1:maxland), 
-                                    land2 = factor(land2, levels = 1:maxland))
-  matrix <- xtabs(score ~ land1 + land2, data = fullframe, 
-                  addNA = addNA)/xtabs(~land1 + land2, data = fullframe, 
-                                       addNA = addNA)
-  matrix <- cbind(matrix, matrix)
-  scores.list <- 1:maxland %>% lapply(FUN = function(i) {
-    if (i == 1) {
-      diag(matrix)
-    }
-    else {
-      i <- i - 1
-      diag(matrix[, -(1:i)])
-    }
-  })
-  
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_npeak_result_generator.R

@@ -1,5 +1,5 @@
 ###############################
-# Note: read reproducible-readme.md first before reproducing the results
+# Note: please read reproducible-readme.md first before reproducing the results
 # Please set the working directory properly so that func_collection.R and 
 # the data files mentioned in reproducible-readme.md are available
 ###############################
@@ -10,15 +10,15 @@
 ## Load the required packages
 library(tidyverse)
 if(!require(bulletxtrctr)) {
-  devtools::install_github("heike/bulletxtrctr")
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
   library(bulletxtrctr)
 }
 library(x3ptools)
-library(CMPS)
+library(cmpsR)
 library(ggpubr)
 library(parallel)
 
-source("func_collection.R")
+# source("func_collection.R")
 
 data_path <- "./data-csv/hamby252/"
 
@@ -114,8 +114,8 @@ CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
 CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
 # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
 
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- 
+#### setup npeaks_set
+CMPS_hamby252_results$npeaks_set <- 
   list(c(5),
        c(5,2),
        c(5,3,1),
@@ -144,8 +144,8 @@ CMPS_hamby252_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby252_results$titlee[[i]] <-
     paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      "npeaks_set=c(",
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = ","),
       ")",
       ", len=",
       CMPS_hamby252_results$seg_length[[i]],
@@ -159,7 +159,7 @@ for (i in 1:N) {
     paste(
       "hamby252_npeak",
       CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = "-"),
       CMPS_hamby252_results$seg_length[[i]],
       CMPS_hamby252_results$Tx[[i]],
       sep = "_"
@@ -216,9 +216,17 @@ for (i in 1:N) {
   ))
   
   
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_rf_result_generator.R

@@ -1,5 +1,5 @@
 ###############################
-# Note: read reproducible-readme.md first before reproducing the results
+# Note: please read reproducible-readme.md first before reproducing the results
 # Please set the working directory properly so that func_collection.R and 
 # the data files mentioned in reproducible-readme.md are available
 ###############################
@@ -10,17 +10,54 @@
 ## Load the required packages
 library(tidyverse)
 if(!require(bulletxtrctr)) {
-  devtools::install_github("heike/bulletxtrctr")
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
   library(bulletxtrctr)
 }
 library(x3ptools)
-library(CMPS)
+library(cmpsR)
 library(ggpubr)
 library(parallel)
 library(assertthat)
 require(randomForest)
 
-source("func_collection.R")
+# define a local function for performing feature extraction in bulletxtrctr
+my_extract_feature_all <- function (aligned, striae, resolution, tmpfile = NULL, ...)
+{
+  feature <- value <- NULL
+  assert_that(!is.null(aligned), !is.null(striae), msg = "aligned and striae must not be NULL")
+  features <- apropos("^extract_feature_") # change: added a start anchor
+  features <- features[!str_detect(features, "extract_feature_cmps")] # change: exclude _cmps from the search list
+  dots <- list(...)
+  values <- features %>% purrr::map_dbl(.f = function(f) {
+    fun <- getFromNamespace(f, asNamespace("bulletxtrctr"))
+    fun_args <- names(formals(fun))
+    matching_args <- dots[names(dots) %in% fun_args]
+    if ("aligned" %in% fun_args) {
+      matching_args$aligned <- aligned$lands
+    }
+    if ("striae" %in% fun_args) {
+      matching_args$striae <- striae$lines
+    }
+    if ("resolution" %in% fun_args) {
+      matching_args$resolution <- resolution
+    }
+    res <- do.call(fun, matching_args)
+    res
+  })
+  dframe <- data.frame(feature = gsub("extract_feature_", "",
+                                      features), value = values) %>% spread(feature, value)
+  if (!is.null(tmpfile)) {
+    if (file.exists(tmpfile)) {
+      write.table(dframe, file = tmpfile, sep = ",", append = TRUE,
+                  col.names = FALSE, row.names = FALSE)
+    }
+    else {
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_seg_result_generator.R

@@ -1,5 +1,5 @@
 ###############################
-# Note: read reproducible-readme.md first before reproducing the results
+# Note: please read reproducible-readme.md first before reproducing the results
 # Please set the working directory properly so that func_collection.R and 
 # the data files mentioned in reproducible-readme.md are available
 ###############################
@@ -10,15 +10,15 @@
 ## Load the required packages
 library(tidyverse)
 if(!require(bulletxtrctr)) {
-  devtools::install_github("heike/bulletxtrctr")
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
   library(bulletxtrctr)
 }
 library(x3ptools)
-library(CMPS)
+library(cmpsR)
 library(ggpubr)
 library(parallel)
 
-source("func_collection.R")
+# source("func_collection.R")
 
 data_path <- "./data-csv/hamby252/"
 
@@ -114,8 +114,8 @@ CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
 CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
   # list("sigs75", "sigs25", "sigs25_1062", "sigs15")
 
-#### setup npeaks.set
-CMPS_hamby252_results$npeaks.set <- lapply(1:N, function(t) c(5,3,1))
+#### setup npeaks_set
+CMPS_hamby252_results$npeaks_set <- lapply(1:N, function(t) c(5,3,1))
 
 #### setup seg_length
 CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
@@ -132,8 +132,8 @@ CMPS_hamby252_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby252_results$titlee[[i]] <-
     paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = ","),
+      "npeaks_set=c(",
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = ","),
       ")",
       ", len=",
       CMPS_hamby252_results$seg_length[[i]],
@@ -147,7 +147,7 @@ for (i in 1:N) {
     paste(
       "hamby252_segment",
       CMPS_hamby252_results$span1[[i]]*100,
-      paste(CMPS_hamby252_results$npeaks.set[[i]], collapse = "-"),
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = "-"),
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_npeak_result_generator.R

@@ -1,5 +1,5 @@
 ###############################
-# Note: read reproducible-readme.md first before reproducing the results
+# Note: please read reproducible-readme.md first before reproducing the results
 # Please set the working directory properly so that func_collection.R and 
 # the data files mentioned in reproducible-readme.md are available
 ###############################
@@ -10,15 +10,15 @@
 ## Load the required packages
 library(tidyverse)
 if(!require(bulletxtrctr)) {
-  devtools::install_github("heike/bulletxtrctr")
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
   library(bulletxtrctr)
 }
 library(x3ptools)
-library(CMPS)
+library(cmpsR)
 library(ggpubr)
 library(parallel)
 
-source("func_collection.R")
+# source("func_collection.R")
 
 data_path <- "./data-csv/hamby44/"
 
@@ -121,7 +121,7 @@ CMPS_hamby44_results$signame <-
   as.list(rep("sigs25_531", N))
 
 #### setup neapks.set
-CMPS_hamby44_results$npeaks.set <-
+CMPS_hamby44_results$npeaks_set <-
   list(c(5),
        c(5,2),
        c(5,3,1),
@@ -148,8 +148,8 @@ CMPS_hamby44_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby44_results$titlee[[i]] <-
     paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
+      "npeaks_set=c(",
+      paste(CMPS_hamby44_results$npeaks_set[[i]], collapse = ","),
       ")",
       ", len=",
       CMPS_hamby44_results$seg_length[[i]],
@@ -163,7 +163,7 @@ for (i in 1:N) {
     paste(
       "hamby44_npeak",
       CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
+      paste(CMPS_hamby44_results$npeaks_set[[i]], collapse = "-"),
       CMPS_hamby44_results$seg_length[[i]],
       CMPS_hamby44_results$Tx[[i]],
       sep = "_"
@@ -218,10 +218,18 @@ for (i in 1:N) {
     }
   ))
   
+  cl <- parallel::makeCluster(detectCores())
+  par.setup <- parLapply(cl, 1:length(cl),
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_rf_result_generator.R

@@ -1,5 +1,5 @@
 ###############################
-# Note: read reproducible-readme.md first before reproducing the results
+# Note: please read reproducible-readme.md first before reproducing the results
 # Please set the working directory properly so that func_collection.R and 
 # the data files mentioned in reproducible-readme.md are available
 ###############################
@@ -10,17 +10,54 @@
 ## Load the required packages
 library(tidyverse)
 if(!require(bulletxtrctr)) {
-  devtools::install_github("heike/bulletxtrctr")
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
   library(bulletxtrctr)
 }
 library(x3ptools)
-library(CMPS)
+library(cmpsR)
 library(ggpubr)
 library(parallel)
 library(assertthat)
 require(randomForest)
 
-source("func_collection.R")
+# define a local function for performing feature extraction in bulletxtrctr
+my_extract_feature_all <- function (aligned, striae, resolution, tmpfile = NULL, ...)
+{
+  feature <- value <- NULL
+  assert_that(!is.null(aligned), !is.null(striae), msg = "aligned and striae must not be NULL")
+  features <- apropos("^extract_feature_") # change: added a start anchor
+  features <- features[!str_detect(features, "extract_feature_cmps")] # change: exclude _cmps from the search list
+  dots <- list(...)
+  values <- features %>% purrr::map_dbl(.f = function(f) {
+    fun <- getFromNamespace(f, asNamespace("bulletxtrctr"))
+    fun_args <- names(formals(fun))
+    matching_args <- dots[names(dots) %in% fun_args]
+    if ("aligned" %in% fun_args) {
+      matching_args$aligned <- aligned$lands
+    }
+    if ("striae" %in% fun_args) {
+      matching_args$striae <- striae$lines
+    }
+    if ("resolution" %in% fun_args) {
+      matching_args$resolution <- resolution
+    }
+    res <- do.call(fun, matching_args)
+    res
+  })
+  dframe <- data.frame(feature = gsub("extract_feature_", "",
+                                      features), value = values) %>% spread(feature, value)
+  if (!is.null(tmpfile)) {
+    if (file.exists(tmpfile)) {
+      write.table(dframe, file = tmpfile, sep = ",", append = TRUE,
+                  col.names = FALSE, row.names = FALSE)
+    }
+    else {
[…]

### 2022-03-28 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_seg_result_generator.R

@@ -1,5 +1,5 @@
 ###############################
-# Note: read reproducible-readme.md first before reproducing the results
+# Note: please read reproducible-readme.md first before reproducing the results
 # Please set the working directory properly so that func_collection.R and 
 # the data files mentioned in reproducible-readme.md are available
 ###############################
@@ -10,15 +10,15 @@
 ## Load the required packages
 library(tidyverse)
 if(!require(bulletxtrctr)) {
-  devtools::install_github("heike/bulletxtrctr")
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
   library(bulletxtrctr)
 }
 library(x3ptools)
-library(CMPS)
+library(cmpsR)
 library(ggpubr)
 library(parallel)
 
-source("func_collection.R")
+# source("func_collection.R")
 
 data_path <- "./data-csv/hamby44/"
 
@@ -121,7 +121,7 @@ CMPS_hamby44_results$signame <-
   as.list(rep("sigs25_531", N))
 
 #### setup neapks.set
-CMPS_hamby44_results$npeaks.set <-
+CMPS_hamby44_results$npeaks_set <-
   lapply(1:N, function(t) c(5,3,1))
 
 #### setup seg_length
@@ -139,8 +139,8 @@ CMPS_hamby44_results$filename <- list()
 for (i in 1:N) {
   CMPS_hamby44_results$titlee[[i]] <-
     paste0(
-      "npeaks.set=c(",
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = ","),
+      "npeaks_set=c(",
+      paste(CMPS_hamby44_results$npeaks_set[[i]], collapse = ","),
       ")",
       ", len=",
       CMPS_hamby44_results$seg_length[[i]],
@@ -154,7 +154,7 @@ for (i in 1:N) {
     paste(
       "hamby44_segment",
       CMPS_hamby44_results$span1[[i]]*100,
-      paste(CMPS_hamby44_results$npeaks.set[[i]], collapse = "-"),
+      paste(CMPS_hamby44_results$npeaks_set[[i]], collapse = "-"),
       CMPS_hamby44_results$seg_length[[i]],
       CMPS_hamby44_results$Tx[[i]],
       sep = "_"
@@ -209,10 +209,18 @@ for (i in 1:N) {
     }
   ))
   
+  cl <- parallel::makeCluster(detectCores())
+  par.setup <- parLapply(cl, 1:length(cl),
[…]

### 2022-03-29 review_responds/review-responds-ju-hofmann2.md
added the new revision and response to the reviews

---
output:
  pdf_document: default
  html_document: default
---

## Overview

We thank you for all the encouraging words in the reviews. Your encouragement means a lot!

## R Code and **cmpsR** package

> The coding style is not consistent through the article. For instance, in certain places, the objects have "." whereas the other places have "_" (cmps.result.KM, cmps_with_multi_scale). Please make sure that the coding style is kept consistent throughout the article.

Thank you for your advice. The coding style is now consistent both throughout the article and in the `cmpsR` package.

> In supplementary materials, all the functions are placed in a single file named 'func_collection.R'. Please make sure that only similar functions are placed in one file and the file is named such that the name reflects the type of functions within it. This will mean that the file 'func_collection.R' is split into multiple files.

`func_collection.R` is now removed from the supplementary materials since the most helper functions are included in the `cmpsR` package.

> line 70: there is a global assignment for current.max in the function get_CMPS. And it seems a bit confusing for the user who wants to access the code. I suggest that to avoid this global assignment when building a package. I think current.max = max(pos.df$cmps) is equivalent to what is written in the function.

This global assignment is now removed and is replaced by an equivalent for loop.

> Some codes are commented, such as line 50 and line 53 in cmps.R. I suggest removing them as
they are not executed, and they might confuse the user who wants to view the code.

All the irrelevant commented codes are removed.

> In script get_ccf4.R, function get_ccf5 and get_ccf4 appear to be mostly identical to each other, except one is calling the C++ code for computing cross-correlation, and the other is written in R.
It will be good to add a few more explanations on these two functions in the documentation.

`get_ccf5()` is now removed from the package. This `R` version of `get_ccf4()` is only needed for us to have a backup and is not used anywhere in the package. Now it's backed up outside the package.

> Hamby44_npeak_result_*.R - Line 17: it seems there is no package called CMPS (it might be cmpsR?)
>
> hamby44_npeak_result_generator.R : The parallelization in ~line 223 in is not working under the window environment, but the following code can make the program works by replacing the mclapply(...) with

We have corrected the package names in `Hamby44_npeak_result_*.R` and modified the parallelization so that it works on both Mac and Windows environments.

#### Note on the **cmpsR** package
\

Note that all the updates of the `cmpsR` package are only available on [github](https://github.com/willju-wangqian/cmpsR) and have not submitted to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother CRAN team for multiple times. Please make sure that you have the most updated version of the `cmpsR` package (version 0.1.2) from [github](https://github.com/willju-wangqian/cmpsR) before you execute any `R` codes that depends on it.

## Article

> Page 1 the last third line: had already defined the Land Engraved Areas (LEAs) in the last fifth line.

The second "Land Engraved Areas (LEAs)" is replaced by "LEAs".

> Page 4, get_segs(x,len=50). Is the len = 50 is the default argument of the function? How does the length of segments is determined? Will the performance of the algorithm change for different
values of len?

We added more details of the parameter `len` in the article. As discussed in the "Algorithm" section after the introduction of the steps, the default values of these parameters are given in the original CMPS paper (Chen et al., 2019) but no cross-validation has been done. The choices of these parameters will affect the final result of the algorithm, and the proposed evaluation framework based on the "Sum of Squares Ratio" could be used to evaluate the parameter choices.

> Page 8, cmps_signature_plot(...). It will be good to add legends within the plot for the black/red
solid line and the red dotted line, and the grey boxes in Figure 4a seem almost invisible.

We have added the legend for the lines presented in Figure 4b. And the grey boxes in Figure 4a is now darker than before.

> Figure 9 and Figure 10 on page 14 and page 15: Is there any overlap between KM and KNM? The counts for KM is very small. It might be good to convert the count into probability. (i.e. hist(...,
probability = TRUE))

Thank you for your suggestion. There is no overlap between KM and KNM in Figure 9 and Figure 10. And in order to make the counts more visible, we have converted the counts to XXX

## Reference

Z. Chen, W. Chu, J. A. Soons, R. M. Thompson, J. Song, and X. Zhao. Fired bullet signature correlation using the Congruent Matching Profile Segments (CMPS) method. Forensic Science International, 305: Article 109964, (10 pages), 2019. ISSN 0379-0738. doi: https://doi.org/10.1016/j.forsciint.2019.109964.

### 2022-03-29 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
added the new revision and response to the reviews

@@
 }
+
+library(ggrepel)
+
+add_labels_repel <- function(plot) {
+  plotting_data <- ggplot_build(plot)$data[[1]]
+  plotting_data <- plotting_data %>% filter(density != 0)
+  plot + geom_text_repel(data = plotting_data,
+    aes(x=.data$x, y=.data$density, label=round(.data$density, 3)),
+    direction = "y"
+  )
+}
+
+ADD_LABELS_HIST <- TRUE
 ```
@@
 The notion of bullet signatures is one of the results of these efforts, and we will use it to explain the CMPS algorithm and showcase the \pkg{cmpsR} implementation.
-Bullet signatures can be extracted from bullet land engraved areas (LEAs), typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
+Bullet signatures can be extracted from bullet LEAs, typically one for each land engraved area, and how those bullet signatures are extracted from scans will be discussed in the Background section.
 Bullet signatures capture striation marks on the bullet in a numeric format and therefore serve as the foundation for algorithms.
@@
 **cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command \code{get\_segs(x, len=50)} implements this step: it takes bullet signature \code{x} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length \code{len}, which are referred to as "basis segments".
+\wj{Note that the parameter} \code{len} \wj{determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison.
+The default value of} \code{len} \wj{is 50, which will result in about 25 basis segments for the example data of the package.
+}
 
@@
 
-Note that there are several parameters in the CMPS algorithm that are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
+Note that there are several parameters in the CMPS algorithm that \wj{will affect the final results and} are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
-However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans.
+However, the authors state that no cross-validation has been done - there might also be issues with respect to resolution of the scans.
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
+\wj{However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters.
+}
 The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
@@
 
-p1 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max",
-  subtitle = "npeaks_set: 5-3-1, seg_length: 50"
-) +
+p1 <- metric_plot_helper(
+  CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max",
+  subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
   xlab(labels[1])
-p2 <- metric_plot_helper(CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
-  subtitle = "npeaks_set: 5-3-1, seg_length: 50"
-) +
+p2 <- metric_plot_helper(
+  CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
+  subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
   xlab(labels[4])
+
+if (ADD_LABELS_HIST) {
+  p1 <- add_labels_repel(p1)
+  p2 <- add_labels_repel(p2)
+}
 
@@
 )
+
 p.result1_252 <- annotate_figure(p.result1_252, top = text_grob(com.title252))
@@
 ```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3, warning=FALSE}
-p1 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
-  subtitle = "npeaks_set: 5-3-1, seg_length: 61"
-) +
+p1 <- metric_plot_helper(
+  CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.max",
+  subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
   xlab(labels[1])
-p2 <- metric_plot_helper(CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
-  subtitle = "npeaks_set: 5-3-1, seg_length: 61"
-) +
+p2 <- metric_plot_helper(
+  CMPS_hamby44_results_seg$cmps.table[[3]], "cmps.maxbar",
+  subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
   xlab(labels[4])
+
+if (ADD_LABELS_HIST) {
+  p1 <- add_labels_repel(p1)
+  p2 <- add_labels_repel(p2)
+}
+
 p.result1_44 <- ggarrange(
@@
 -   `hamby*_result_generator.R`: these R scripts take the processed data of Hamby set 252 and Hamby set 44, generate preliminary results used in the paper, and save the results in the `.csv` format in the folder `data-csv`.
+Please make sure that the package versions of `bulletxtrctr` and `cmpsR` meet the requirements.
 -   `rds_generator.R`: this R script takes the generated `.csv` files and produce `CMPSpaper_results.rds`.
 `CMPSpaper_results.rds` is identical to `data/CMPSpaper_results.rds` and is used generate figures and other results presented in the paper.
--   `func_collection.R`: this R script contains some helper functions used by other R scripts.
 

### 2022-03-29 submissions/resubmission-ju-hofmann2/ju-hofmann.tex
added the new revision and response to the reviews

@@
 \pkg{cmpsR} implementation. Bullet signatures can be extracted from
-bullet land engraved areas (LEAs), typically one for each land engraved
-area, and how those bullet signatures are extracted from scans will be
-discussed in the Background section. Bullet signatures capture striation
-marks on the bullet in a numeric format and therefore serve as the
-foundation for algorithms. These scans played an important role in
-bringing objectivity into the field. In the following sections we will:
-review the background of bullet signature comparisons, discuss how we
-followed the idea described by \citet{cmps} for the implementation of
-the CMPS algorithm, propose new metrics based on the CMPS score and a
-principled evaluation framework for algorithmic results comparison, and
-present results of applying our implementation to real data.
+bullet LEAs, typically one for each land engraved area, and how those
+bullet signatures are extracted from scans will be discussed in the
+Background section. Bullet signatures capture striation marks on the
+bullet in a numeric format and therefore serve as the foundation for
+algorithms. These scans played an important role in bringing objectivity
+into the field. In the following sections we will: review the background
+of bullet signature comparisons, discuss how we followed the idea
+described by \citet{cmps} for the implementation of the CMPS algorithm,
+propose new metrics based on the CMPS score and a principled evaluation
+framework for algorithmic results comparison, and present results of
+applying our implementation to real data.
 
@@
 how to use the \pkg{cmpsR} package. A further example that illustrates
-the main points is also included. In the section on 'Evaluation metrics"
-we introduce new CMPS metrics that summarize land-level CMPS scores and
-a sum of squares ratio that can be used to evaluate algorithmic results.
-The section ``Results'' presents the results of evaluating the
-\pkg{cmpsR} package using Hamby set 252 and Hamby set 44. The results
-from Hamby set 252 are used to verify that our implementation is, at
-least qualitatively, comparable to the algorithm described in
-\citet{cmps}. Results from Hamby 44 show the need for a further
-investigation of the parameter choices even in the case of bullets fired
-from the same barrels. The last section covers some final discussion and
-conclusions.
+the main points is also included. In the section on 'Evaluation
+metrics'' we introduce new CMPS metrics that summarize land-level CMPS
+scores and a sum of squares ratio that can be used to evaluate
+algorithmic results. The section ``Results'' presents the results of
+evaluating the \pkg{cmpsR} package using Hamby set 252 and Hamby set 44.
+The results from Hamby set 252 are used to verify that our
+implementation is, at least qualitatively, comparable to the algorithm
+described in \citet{cmps}. Results from Hamby 44 show the need for a
+further investigation of the parameter choices even in the case of
+bullets fired from the same barrels. The last section covers some final
+discussion and conclusions.
 
@@
   \code{len}, which are referred to as ``basis segments''.
+  \wj{Note that the parameter} \code{len}
+  \wj{determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison. The default value of}
+  \code{len}
+  \wj{is 50, which will result in about 25 basis segments for the example data of the package. }
 \item
@@
 
-Note that there are several parameters in the CMPS algorithm that are
-left to the users to decide, such as the length of basis segments
-\code{seg\_length} in step 1, the number of peaks \code{npeaks\_set}
-identified on each level in step 2, and the length of the tolerance zone
-\code{Tx} in both step 2 and 3. In our implementation of the CMPS
-algorithm we used the parameters given in the original CMPS paper
-\citep{cmps} as the default values for these parameters. However, the
-authors state that no cross-validation has been done - there might be
-also issues with respect to resolution of the scans. Further research is
-needed, until then users are advised to think of default values as
-starting values and consider alternatives. The main function that
-combines all steps in the CMPS algorithm described above is called
-\code{extract\_feature\_cmps(...)}. Here we present it with its default
-parameters.
+Note that there are several parameters in the CMPS algorithm that
+\wj{will affect the final results and} are left to the users to decide,
+such as the length of basis segments \code{seg\_length} in step 1, the
+number of peaks \code{npeaks\_set} identified on each level in step 2,
+and the length of the tolerance zone \code{Tx} in both step 2 and 3. In
+our implementation of the CMPS algorithm we used the parameters given in
+the original CMPS paper \citep{cmps} as the default values for these
+parameters. However, the authors state that no cross-validation has been
+done - there might also be issues with respect to resolution of the
+scans. Further research is needed, until then users are advised to think
+of default values as starting values and consider alternatives.
+\wj{However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters. }
+The main function that combines all steps in the CMPS algorithm
+described above is called \code{extract\_feature\_cmps(...)}. Here we
+present it with its default parameters.
 

### 2022-03-29 submissions/resubmission-ju-hofmann2/ju-hofmann.R

@@ -1,11 +1,108 @@
-## ----setup, echo=FALSE, message=FALSE, warning=FALSE----------------------
+# Generated by `rjournal_article()` using `knitr::purl()`: do not edit by hand
+# Please edit ju-hofmann.Rmd to modify this file
+
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE------
 library(knitr)
 library(kableExtra)
 library(tidyverse)
 library(patchwork)
 library(ggpubr)
 
-## ----func, echo=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  out.width = "\\textwidth",
+  fig.align = "center",
+  #  cache=TRUE,
+  dpi = 144,
+  warning = FALSE,
+  message = FALSE
+)
+
+
+## ----setup_knitr, echo=FALSE------------------------------
+## From Josh O'Brien's stackoverflow answer:
+## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
+## These two settings control text width in codefig vs. usual code blocks
+partWidth <- 35
+fullWidth <- 60
+options(width = fullWidth)
+
+##  (1) CHUNK HOOK FUNCTION
+##   First, to set R's textual output width on a per-chunk basis, we
+## need to define a hook function which temporarily resets global R's
+## option() settings, just for the current chunk
+knit_hooks$set(r.opts = local({
+  ropts <- NA
+  function(before, options, envir) {
+    if (before) {
+      ropts <<- options(options$r.opts)
+    } else {
+      options(ropts)
+    }
+  }
+}))
+
+## (2) OUTPUT HOOK FUNCTION
+
+##   Define a custom output hook function. This function processes _all_
+## evaluated chunks, but will return the same output as the usual one,
+## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
+## case, wrap the usual textual output in LaTeX code placing it in a
+## narrower adjustbox environment and setting the graphics that it
+## produced in another box beside it.
+
+defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
+
+codefigChunkHook <- function(x, options) {
[…]

### 2022-03-29 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
update variable names in ju-hofmann.R

@@
 CMPS_hamby44_results_npeak <- all_results_container$h44_npeak
-rf.results <- all_results_container$rf
+rf_results <- all_results_container$rf
 
@@
 ```{r rf-data-process, echo=FALSE}
-rf.tt <- lapply(rf.results, function(rf_result) {
+rf_tt <- lapply(rf_results, function(rf_result) {
   with(rf_result, {
@@
 
-colnames(rf.tt) <- c("cmps.diff", "cmps.max", "cmps.maxbar")
-
-rf.tt$cmps.diff_scaled <- rf.tt$cmps.diff
-
-rf.tt$study <- c("Hamby 252", "Hamby 44")
-rf.tt <- rf.tt %>% pivot_longer(
+colnames(rf_tt) <- c("cmps.diff", "cmps.max", "cmps.maxbar")
+
+rf_tt$cmps.diff_scaled <- rf_tt$cmps.diff
+
+rf_tt$study <- c("Hamby 252", "Hamby 44")
+rf_tt <- rf_tt %>% pivot_longer(
   cols = c("cmps.diff", "cmps.max", "cmps.maxbar", "cmps.diff_scaled"),
@@
 
-rf.tt$npeak <- "RF score* (Hare et al)"
+rf_tt$npeak <- "RF score* (Hare et al)"
 ```
@@
 ```{r ss-original-cmps, echo=FALSE}
-result.container <- list()
-
-result.container$npeak <-
+result_container <- list()
+
+result_container$npeak <-
   c("5* (Chen et al)", "5-3-1* (Chen et al)", "5* (Chen et al)", "5-3-1* (Chen et al)")
-result.container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
-result.container$study <- "Hamby 252"
-
-dd.list <- list()
-
-dd.list[[1]] <- tibble(
+result_container$Metric <- c("cmps.max", "cmps.max", "cmps.maxbar", "cmps.maxbar")
+result_container$study <- "Hamby 252"
+
+dd_list <- list()
+
+dd_list[[1]] <- tibble(
   score = c(9:13, 16:24),
@@
 
-dd.list[[2]] <- tibble(
+dd_list[[2]] <- tibble(
   score = c(1:5, 14:23),
@@
 
-dd.list[[3]] <- tibble(
+dd_list[[3]] <- tibble(
   score = c(6:9, 13:19),
@@
 
-dd.list[[4]] <- tibble(
+dd_list[[4]] <- tibble(
   score = c(0:2, 8:17),
@@
 
-result.container$dd.list <- dd.list
-
-result.container <- result.container %>%
+result_container$dd_list <- dd_list
+
+result_container <- result_container %>%
   as_tibble() %>%
   mutate(
-    dd.table = purrr::map(dd.list, function(dd) {
+    dd_table = purrr::map(dd_list, function(dd) {
       tibble(
@@
     }),
-    value = purrr::map_dbl(dd.table, function(dd) {
+    value = purrr::map_dbl(dd_table, function(dd) {
       compute_ss_ratio(dd$score, dd$type_truth, MS = FALSE)
@@
 # 252 - seg
-table.252.cmps_seg <- lapply(CMPS_hamby252_results_seg$cmps.table, function(tt) {
+table_252_cmps_seg <- lapply(CMPS_hamby252_results_seg$cmps.table, function(tt) {
   type_truth <- tt$type_truth
@@
 
-table.252.cmps_seg$seg_length <- unlist(CMPS_hamby252_results_seg$seg_length)
-
-table.252.cmps_seg.long <- table.252.cmps_seg %>%
+table_252_cmps_seg$seg_length <- unlist(CMPS_hamby252_results_seg$seg_length)
+
+table_252_cmps_seg.long <- table_252_cmps_seg %>%
   pivot_longer(
@@
 
-table.252.cmps_seg.long <- table.252.cmps_seg.long %>%
+table_252_cmps_seg.long <- table_252_cmps_seg.long %>%
   mutate(study = "Hamby 252")
@@
 
-p.seg_252_plot <- table.252.cmps_seg.long %>%
+p.seg_252_plot <- table_252_cmps_seg.long %>%
   ggplot(aes(x = seg_length + 3 * as.numeric(factor(Metric)) - 9)) +
@@
   scale_x_continuous(
-    breaks = table.252.cmps_seg$seg_length,
+    breaks = table_252_cmps_seg$seg_length,
     minor_breaks = NULL
@@
 # 44 - seg
-table.44.cmps_seg <- lapply(CMPS_hamby44_results_seg$cmps.table, function(tt) {
+table_44_cmps_seg <- lapply(CMPS_hamby44_results_seg$cmps.table, function(tt) {
   type_truth <- tt$type_truth
@@
 
-table.44.cmps_seg$seg_length <- unlist(CMPS_hamby44_results_seg$seg_length)
-
-table.44.cmps_seg.long <- table.44.cmps_seg %>%
+table_44_cmps_seg$seg_length <- unlist(CMPS_hamby44_results_seg$seg_length)
+
+table_44_cmps_seg.long <- table_44_cmps_seg %>%
   pivot_longer(
@@
 
-table.44.cmps_seg.long <- table.44.cmps_seg.long %>% mutate(
+table_44_cmps_seg.long <- table_44_cmps_seg.long %>% mutate(
   study = "Hamby 44"
@@
 table.cmps_seg.long <- bind_rows(
-  table.44.cmps_seg.long,
-  table.252.cmps_seg.long
+  table_44_cmps_seg.long,
+  table_252_cmps_seg.long
 )
@@
 # npeak - 252
-table.252.cmps_npeak <- lapply(CMPS_hamby252_results_npeak$cmps.table, function(tt) {
+table_252_cmps_npeak <- lapply(CMPS_hamby252_results_npeak$cmps.table, function(tt) {
   type_truth <- tt$type_truth
@@
 
-table.252.cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks_set %>%
+table_252_cmps_npeak$npeak <- CMPS_hamby252_results_npeak$npeaks_set %>%
   purrr::map(.f = paste, collapse = "-") %>%
@@
 
-table.252.cmps_npeak.longer <- table.252.cmps_npeak %>%
+table_252_cmps_npeak.longer <- table_252_cmps_npeak %>%
   as_tibble() %>%
@@
   )
-table.252.cmps_npeak.longer$study <- "Hamby 252"
+table_252_cmps_npeak.longer$study <- "Hamby 252"
 
 # npeak - 44
-table.44.cmps_npeak <- lapply(CMPS_hamby44_results_npeak$cmps.table, function(tt) {
+table_44_cmps_npeak <- lapply(CMPS_hamby44_results_npeak$cmps.table, function(tt) {
   type_truth <- tt$type_truth
@@
 
-table.44.cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks_set %>%
+table_44_cmps_npeak$npeak <- CMPS_hamby44_results_npeak$npeaks_set %>%
   purrr::map(.f = paste, collapse = "-") %>%
@@
 
-table.44.cmps_npeak.longer <- table.44.cmps_npeak %>%
+table_44_cmps_npeak.longer <- table_44_cmps_npeak %>%
   as_tibble() %>%
@@
   )
-table.44.cmps_npeak.longer$study <- "Hamby 44"
+table_44_cmps_npeak.longer$study <- "Hamby 44"
 
@@
 
-table.cmps_neapk.long <- bind_rows(
-  table.252.cmps_npeak.longer %>% select(all_of(selected_var)),
-  table.44.cmps_npeak.longer %>% select(all_of(selected_var)),
-  rf.tt %>% select(all_of(selected_var)),
-  result.container %>% select(all_of(selected_var))
-)
-
-order.level <- table.cmps_neapk.long %>%
+table_cmps_neapk.long <- bind_rows(
+  table_252_cmps_npeak.longer %>% select(all_of(selected_var)),
+  table_44_cmps_npeak.longer %>% select(all_of(selected_var)),
+  rf_tt %>% select(all_of(selected_var)),
+  result_container %>% select(all_of(selected_var))
+)
+
+order_level <- table_cmps_neapk.long %>%
   filter(Metric == "cmps.maxbar", study == "Hamby 252") %>%
@@
 
-table.cmps_neapk.long <- table.cmps_neapk.long %>% mutate(
-  npeak = factor(npeak, levels = order.level)
-)
-
-npeak_convert <- with(table.cmps_neapk.long, {
+table_cmps_neapk.long <- table_cmps_neapk.long %>% mutate(
+  npeak = factor(npeak, levels = order_level)
+)
+
+npeak_convert <- with(table_cmps_neapk.long, {
   tt <- tibble(npeak = levels(npeak))
@@
 
-table.cmps_neapk.long <- table.cmps_neapk.long %>% left_join(
+table_cmps_neapk.long <- table_cmps_neapk.long %>% left_join(
   npeak_convert,
@@
 
-table.cmps_neapk.long <- table.cmps_neapk.long %>% mutate(
+table_cmps_neapk.long <- table_cmps_neapk.long %>% mutate(
   rf_status = if_else(npeak == "RF score* (Hare et al)",
@@
 
-table.cmps_neapk.long$Metric <-
-  table.cmps_neapk.long$Metric %>%
+table_cmps_neapk.long$Metric <-
+  table_cmps_neapk.long$Metric %>%
   factor(levels = c("cmps.max", "cmps.diff", "cmps.diff_scaled", "cmps.maxbar"))
 
-p.npeak_plot <- table.cmps_neapk.long %>%
+p.npeak_plot <- table_cmps_neapk.long %>%
   ggplot(aes(x = xstart + 3 * as.numeric(factor(Metric)) - 9)) +

### 2022-03-29 submissions/resubmission-ju-hofmann2/ju-hofmann.R

@@ -409,7 +409,7 @@ CMPS_hamby252_results_seg <- all_results_container$h252_seg
 CMPS_hamby252_results_npeak <- all_results_container$h252_npeak
 CMPS_hamby44_results_seg <- all_results_container$h44_seg
 CMPS_hamby44_results_npeak <- all_results_container$h44_npeak
-rf.results <- all_results_container$rf
+rf_results <- all_results_container$rf
 
 #### a global title for Hamby44 plots
 com.title44 <- expression(paste(
@@ -423,7 +423,7 @@ com.title252 <- expression(paste(
 
 
 ## ----rf-data-process, echo=FALSE--------------------------
-rf.tt <- lapply(rf.results, function(rf_result) {
+rf_tt <- lapply(rf_results, function(rf_result) {
   with(rf_result, {
     tibble(rf.diff, rf.max, rf.maxbar) %>%
       apply(2, compute_ss_ratio, label = type_truth, MS = FALSE)
@@ -432,65 +432,65 @@ rf.tt <- lapply(rf.results, function(rf_result) {
   do.call(rbind, .) %>%
   as_tibble()
 
-colnames(rf.tt) <- c("cmps.diff", "cmps.max", "cmps.maxbar")
+colnames(rf_tt) <- c("cmps.diff", "cmps.max", "cmps.maxbar")
 
-rf.tt$cmps.diff_scaled <- rf.tt$cmps.diff
+rf_tt$cmps.diff_scaled <- rf_tt$cmps.diff
 
-rf.tt$study <- c("Hamby 252", "Hamby 44")
-rf.tt <- rf.tt %>% pivot_longer(
+rf_tt$study <- c("Hamby 252", "Hamby 44")
+rf_tt <- rf_tt %>% pivot_longer(
   cols = c("cmps.diff", "cmps.max", "cmps.maxbar", "cmps.diff_scaled"),
   names_to = "Metric"
 )
 
-rf.tt$npeak <- "RF score* (Hare et al)"
+rf_tt$npeak <- "RF score* (Hare et al)"
 
 
 ## ----ss-original-cmps, echo=FALSE-------------------------
-result.container <- list()
+result_container <- list()
 
-result.container$npeak <-
+result_container$npeak <-
   c("5* (Chen et al)", "5-3-1* (Chen et al)", "5* (Chen et al)", "5-3-1* (Chen et al)")
[…]

### 2022-03-29 review_responds/review-responds-ju-hofmann2.md
one bullet point in the review was missing; now it's added
added one more note on the marked article

@@
 This global assignment is now removed and is replaced by an equivalent for loop.
+
+> It might be good to add a CITATION file and a README.md file to the package.
+
+The `README.md` file and `CITATION` file are now added to the package.
 
@@
 
+#### Note on the marked article
+\
+
+The `marked_article.pdf` in the same folder of the review responds is a marked version of the article, where the new added contents are highlighted in blue.
+The intention of this file is to allow the reviewers to quickly find out what has been changed for this revision.
+
 ## Reference

### 2022-03-30 review_responds/review-responds-ju-hofmann2.md
I massaged the wording a bit. looks good!

@@
 
-We thank you for all the encouraging words in the reviews. Your encouragement means a lot!
+We would like to thank the reviewers for the thorough review and the excellent comments.
 
@@
 
-`func_collection.R` is now removed from the supplementary materials since the most helper functions are included in the `cmpsR` package.
+`func_collection.R` is now removed from the supplementary materials.
+All the helper functions are included in the `cmpsR` package, and the code highlighted in the paper and for reproducing all images is attached separately.
 
@@
 
-Note that all the updates of the `cmpsR` package are only available on [github](https://github.com/willju-wangqian/cmpsR) and have not submitted to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother CRAN team for multiple times.
-Please make sure that you have the most updated version of the `cmpsR` package (version 0.1.2) from [github](https://github.com/willju-wangqian/cmpsR) before you execute any `R` codes that depends on it.
+Note that all the updates of the `cmpsR` package are only available on [github](https://github.com/willju-wangqian/cmpsR).
+We have not yet submitted the updates to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother the CRAN teammultiple times.
+Please make sure that you have the most updated version of the `cmpsR` package (version 0.1.2) from [github](https://github.com/willju-wangqian/cmpsR) before you execute any `R` code that depends on it.
+
+`install_github("willju-wangqian/cmpsR")`
 
@@
 
-We have added the legend for the lines presented in Figure 4b. And the grey boxes in Figure 4a is now darker than before.
+We have added the legend for the lines presented in Figure 4b and made the grey boxes in Figure 4a darker than before.
 
@@
 
-Thank you for your suggestion. There is no overlap between KM and KNM in Figure 9 and Figure 10. And in order to make the counts more visible, we have converted the counts to XXX
+Thank you for your suggestion. There is no overlap between KM and KNM in Figure 9 and Figure 10. And in order to make the counts more visible, we have converted the counts to proportions by group.
 

### 2022-03-31 review_responds/review-responds-ju-hofmann2.md
clean up the folder and finish the revision for this round

@@
 Note that all the updates of the `cmpsR` package are only available on [github](https://github.com/willju-wangqian/cmpsR).
-We have not yet submitted the updates to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother the CRAN teammultiple times.
+We have not yet submitted the updates to CRAN yet since we are looking forward to your further suggestions and advice and do not want to bother the CRAN team multiple times.
 Please make sure that you have the most updated version of the `cmpsR` package (version 0.1.2) from [github](https://github.com/willju-wangqian/cmpsR) before you execute any `R` code that depends on it.

### 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
ready for re-submission
clean up the folder and finish the revision for this round

@@
   # see ?rjournal_article for more information
-  - name: Wangqian W. Ju
+  - name: Wangqian Ju
     affiliation: Department of Statistics
@@
 
-ADD_LABELS_HIST <- TRUE
+ADD_LABELS_HIST <- FALSE
 ```
@@
 **cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command \code{get\_segs(x, len=50)} implements this step: it takes bullet signature \code{x} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length \code{len}, which are referred to as "basis segments".
-\wj{Note that the parameter} \code{len} \wj{determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison.
-The default value of} \code{len} \wj{is 50, which will result in about 25 basis segments for the example data of the package.
-}
+Note that the parameter \code{len} determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison.
+The default value of \code{len} is 50, which will result in about 25 basis segments for the example data of the package.
 
@@
 
-Note that there are several parameters in the CMPS algorithm that \wj{will affect the final results and} are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
+Note that there are several parameters in the CMPS algorithm that will affect the final results and are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
 In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
@@
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
-\wj{However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters.
-}
+However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters.
 The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
@@
 In order to show that our implementation of the CMPS algorithm is able to reproduce the results in @cmps and be used for other data sets, we applied our implementation to both Hamby set 252 and Hamby set 44.
-For the purpose of reproducibility, we present how we obtained bullet signatures from the Hamby set data and include code in the appendix: for both Hamby 252 and Hamby 44, we started with scans in the form of x3p files in the database.
+Here we present how we obtained bullet signatures from the Hamby set data: for both Hamby 252 and Hamby 44, we started with scans in the form of x3p files in the database.
 Following the framework proposed by @aoas, we used the same set of parameters, removed damaged bullet scans, obtained bullet signatures for each bullet land engraving, and removed outliers in bullet signatures.
@@
 
-```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3}
+```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"
@@
   subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
-  xlab(labels[1])
+  xlab(labels[1]) + 
+  theme(axis.text.x = element_text(size=7))
 p2 <- metric_plot_helper(
@@
 
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3, warning=FALSE}
+```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3, warning=FALSE}
 p1 <- metric_plot_helper(
@@
   subtitle = "npeaks_set: 5-3-1, seg_length: 61") +
-  xlab(labels[1])
+  xlab(labels[1]) + 
+  theme(axis.text.x = element_text(size=7))
 p2 <- metric_plot_helper(

### 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.tex
update variable names in ju-hofmann.R
clean up the folder and finish the revision for this round

@@
 Similarity of Bullets}
-\author{by Wangqian W. Ju and Heike Hofmann}
+\author{by Wangqian Ju and Heike Hofmann}
 
@@
   consecutive, non-overlapping and equal-length segments of length
-  \code{len}, which are referred to as ``basis segments''.
-  \wj{Note that the parameter} \code{len}
-  \wj{determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison. The default value of}
-  \code{len}
-  \wj{is 50, which will result in about 25 basis segments for the example data of the package. }
+  \code{len}, which are referred to as ``basis segments''. Note that the
+  parameter \code{len} determines the length of a basis segment and thus
+  affects the total number of basis segments, which is the upper limit
+  of the CMPS score of a comparison. The default value of \code{len} is
+  50, which will result in about 25 basis segments for the example data
+  of the package.
 \item
@@
 
-Note that there are several parameters in the CMPS algorithm that
-\wj{will affect the final results and} are left to the users to decide,
-such as the length of basis segments \code{seg\_length} in step 1, the
-number of peaks \code{npeaks\_set} identified on each level in step 2,
-and the length of the tolerance zone \code{Tx} in both step 2 and 3. In
-our implementation of the CMPS algorithm we used the parameters given in
-the original CMPS paper \citep{cmps} as the default values for these
+Note that there are several parameters in the CMPS algorithm that will
+affect the final results and are left to the users to decide, such as
+the length of basis segments \code{seg\_length} in step 1, the number of
+peaks \code{npeaks\_set} identified on each level in step 2, and the
+length of the tolerance zone \code{Tx} in both step 2 and 3. In our
+implementation of the CMPS algorithm we used the parameters given in the
+original CMPS paper \citep{cmps} as the default values for these
 parameters. However, the authors state that no cross-validation has been
@@
 scans. Further research is needed, until then users are advised to think
-of default values as starting values and consider alternatives.
-\wj{However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters. }
-The main function that combines all steps in the CMPS algorithm
-described above is called \code{extract\_feature\_cmps(...)}. Here we
-present it with its default parameters.
+of default values as starting values and consider alternatives. However,
+the evaluation framework based on the Sum of Squares Ratio introduced in
+the later section could be used to evaluate the choices of these
+parameters. The main function that combines all steps in the CMPS
+algorithm described above is called \code{extract\_feature\_cmps(...)}.
+Here we present it with its default parameters.
 
@@
 \citet{cmps} and be used for other data sets, we applied our
-implementation to both Hamby set 252 and Hamby set 44. For the purpose
-of reproducibility, we present how we obtained bullet signatures from
-the Hamby set data and include code in the appendix: for both Hamby 252
-and Hamby 44, we started with scans in the form of x3p files in the
-database. Following the framework proposed by \citet{aoas}, we used the
-same set of parameters, removed damaged bullet scans, obtained bullet
-signatures for each bullet land engraving, and removed outliers in
-bullet signatures. Note that researchers of \citet{cmps} applied the
+implementation to both Hamby set 252 and Hamby set 44. Here we present
+how we obtained bullet signatures from the Hamby set data: for both
+Hamby 252 and Hamby 44, we started with scans in the form of x3p files
+in the database. Following the framework proposed by \citet{aoas}, we
+used the same set of parameters, removed damaged bullet scans, obtained
+bullet signatures for each bullet land engraving, and removed outliers
+in bullet signatures. Note that researchers of \citet{cmps} applied the
 CMPS algorithm to bullet signatures as well but used a framework
@@
 
-\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_252}
+\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars }\label{fig:result1_252}
 \end{figure}
@@
 
-\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)} }\label{fig:result1_44}
+\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars }\label{fig:result1_44}
 \end{figure}
@@
   results used in the paper, and save the results in the \texttt{.csv}
-  format in the folder \texttt{data-csv}.
+  format in the folder \texttt{data-csv}. Please make sure that the
+  package versions of \texttt{bulletxtrctr} and \texttt{cmpsR} meet the
+  requirements.
 \item
@@
   other results presented in the paper.
-\item
-  \texttt{func\_collection.R}: this R script contains some helper
-  functions used by other R scripts.
 \end{itemize}
@@
 \address{%
-Wangqian W. Ju\\
+Wangqian Ju\\
 Department of Statistics\\%

### 2022-03-31 reproducible/supplementary-files-mar31/hamby252_npeak_result_generator.R

@@ -1,0 +1,335 @@
+################################################################################
+# Note: please read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+################################################################################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
+  library(bulletxtrctr)
+}
+if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
+  devtools::install_github("willju-wangqian/cmpsR")
+  library(cmpsR)
+}
+library(x3ptools)
+library(ggpubr)
+library(parallel)
+
+data_path <- "./data-csv/hamby252/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/hamby252_rf_result_generator.R

@@ -1,0 +1,311 @@
+################################################################################
+# Note: please read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+################################################################################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
+  devtools::install_github("willju-wangqian/cmpsR")
+  library(cmpsR)
+}
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+# define a local function for performing feature extraction in bulletxtrctr
+my_extract_feature_all <- function (aligned, striae, resolution, tmpfile = NULL, ...)
+{
+  feature <- value <- NULL
+  assert_that(!is.null(aligned), !is.null(striae), msg = "aligned and striae must not be NULL")
+  features <- apropos("^extract_feature_") # change: added a start anchor
+  features <- features[!str_detect(features, "extract_feature_cmps")] # change: exclude _cmps from the search list
+  dots <- list(...)
+  values <- features %>% purrr::map_dbl(.f = function(f) {
+    fun <- getFromNamespace(f, asNamespace("bulletxtrctr"))
+    fun_args <- names(formals(fun))
+    matching_args <- dots[names(dots) %in% fun_args]
+    if ("aligned" %in% fun_args) {
+      matching_args$aligned <- aligned$lands
+    }
+    if ("striae" %in% fun_args) {
+      matching_args$striae <- striae$lines
+    }
+    if ("resolution" %in% fun_args) {
+      matching_args$resolution <- resolution
+    }
+    res <- do.call(fun, matching_args)
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/hamby252_seg_result_generator.R

@@ -1,0 +1,322 @@
+################################################################################
+# Note: please read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+################################################################################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
+  devtools::install_github("willju-wangqian/cmpsR")
+  library(cmpsR)
+}
+library(ggpubr)
+library(parallel)
+
+data_path <- "./data-csv/hamby252/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
+
+#### obtain all comparisons
+b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### obtained ID for the damaged bullets;
+###### These IDs are identified by using a Shiny App called bulletinspectR
+tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
+
+#### Include the ground truth for Hamby252
+tmp.tibble <- tibble(bullet1 = b.cb[1,], 
+                     bullet2 = b.cb[2,])
+
+tmp.tibble <- tmp.tibble %>% mutate(
+  type = if_else(
+    bullet1 %>% str_extract("Br\\d+") ==
+      bullet2 %>% str_extract("Br\\d+"),
+    "KM",
+    "KNM"
+  ),
+  type = if_else(is.na(type), "Ukn", type)
+)
+
+###### StudyInfo.xlsx provides the ground truth for Hamby252 
+studyinfo <-
+  readxl::read_xlsx(
+    "./bullet_signatures_etc/StudyInfo.xlsx",
+    sheet = 3,
+    skip = 1
+  )
+
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/hamby44_npeak_result_generator.R

@@ -1,0 +1,334 @@
+################################################################################
+# Note: please read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+################################################################################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
+  library(bulletxtrctr)
+}
+if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
+  devtools::install_github("willju-wangqian/cmpsR")
+  library(cmpsR)
+}
+library(x3ptools)
+library(ggpubr)
+library(parallel)
+
+data_path <- "./data-csv/hamby44/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/hamby44_rf_result_generator.R

@@ -1,0 +1,312 @@
+################################################################################
+# Note: please read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+################################################################################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
+  devtools::install_github("willju-wangqian/cmpsR")
+  library(cmpsR)
+}
+library(ggpubr)
+library(parallel)
+library(assertthat)
+require(randomForest)
+
+# define a local function for performing feature extraction in bulletxtrctr
+my_extract_feature_all <- function (aligned, striae, resolution, tmpfile = NULL, ...)
+{
+  feature <- value <- NULL
+  assert_that(!is.null(aligned), !is.null(striae), msg = "aligned and striae must not be NULL")
+  features <- apropos("^extract_feature_") # change: added a start anchor
+  features <- features[!str_detect(features, "extract_feature_cmps")] # change: exclude _cmps from the search list
+  dots <- list(...)
+  values <- features %>% purrr::map_dbl(.f = function(f) {
+    fun <- getFromNamespace(f, asNamespace("bulletxtrctr"))
+    fun_args <- names(formals(fun))
+    matching_args <- dots[names(dots) %in% fun_args]
+    if ("aligned" %in% fun_args) {
+      matching_args$aligned <- aligned$lands
+    }
+    if ("striae" %in% fun_args) {
+      matching_args$striae <- striae$lines
+    }
+    if ("resolution" %in% fun_args) {
+      matching_args$resolution <- resolution
+    }
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/hamby44_seg_result_generator.R

@@ -1,0 +1,327 @@
+################################################################################
+# Note: please read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that func_collection.R and 
+# the data files mentioned in reproducible-readme.md are available
+################################################################################
+
+# set the working directory
+# setwd("~/your-path/supplementary-files")
+
+## Load the required packages
+library(tidyverse)
+if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
+  devtools::install_github("heike/bulletxtrctr", ref = "develop")
+  library(bulletxtrctr)
+}
+library(x3ptools)
+if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
+  devtools::install_github("willju-wangqian/cmpsR")
+  library(cmpsR)
+}
+library(ggpubr)
+library(parallel)
+
+data_path <- "./data-csv/hamby44/"
+
+## Data Processing
+
+#### load the data from reproducible/bullet_signatures_etc/
+b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
+
+#### obtain all comparisons
+bulletid.tb <- b44 %>% select(scan_id)
+bulletid.tb <- bulletid.tb %>% mutate(
+  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
+  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
+  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
+  bullet_id = paste(barrel_id, bullet)
+)
+b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
+b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
+p <- 1:595
+
+#### import indices of damaged scans
+###### These indices are identified by using a Shiny App called bulletinspectR
+idf.idx <- c(23,35,39,41,102,126,149)
+idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
+
+#### include the ground truth for Hamby44
+key.table <- tibble(
+  bullet.id = c("K",
+                "O",
+                "L",
+                "P",
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/rds_generator.R

@@ -1,0 +1,311 @@
+###############################
+# Note: read reproducible-readme.md first before reproducing the results
+# Please set the working directory properly so that ./data-csv/" is available
+###############################
+
+###############################
+# for the random forest model
+rf.results <- list()
+rf.results[[1]] <- read.csv(file = "./data-csv/hamby252/hamby252_rf_results.csv")
+rf.results[[2]] <- read.csv(file = "./data-csv/hamby44/hamby44_rf_results.csv")
+
+###############################
+# hamby 252 segments
+N <- 8 # the number of different sets of parameters
+CMPS_hamby252_results <- list() # a container for everything
+
+#### setup span1
+CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
+
+#### setup signature name
+CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
+# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
+
+#### setup npeaks_set
+CMPS_hamby252_results$npeaks_set <- lapply(1:N, function(t) c(5,3,1))
+
+#### setup seg_length
+CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
+
+#### setup Tx
+CMPS_hamby252_results$Tx <- as.list(rep(25, N))
+
+#### setup outlength
+CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
+
+#### create a plot title and a file name for each set of parameters
+CMPS_hamby252_results$titlee <- list()
+CMPS_hamby252_results$filename <- list()
+for (i in 1:N) {
+  CMPS_hamby252_results$titlee[[i]] <-
+    paste0(
+      "npeaks_set=c(",
+      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = ","),
+      ")",
+      ", len=",
+      CMPS_hamby252_results$seg_length[[i]],
+      ", Tx=",
+      CMPS_hamby252_results$Tx[[i]],
+      ", \nspan1=",
+      CMPS_hamby252_results$span1[[i]],
+      ", span2=0.03"
+    )
+  CMPS_hamby252_results$filename[[i]] <- 
+    paste(
+      "hamby252_segment",
+      CMPS_hamby252_results$span1[[i]]*100,
[…]

### 2022-03-31 reproducible/supplementary-files-mar31/test_reproducible.R

@@ -1,0 +1,24 @@
+# run all scripts
+source("./hamby44_seg_result_generator.R")
+source("./hamby44_npeak_result_generator.R")
+source("./hamby44_rf_result_generator.R")
+
+source("./hamby252_seg_result_generator.R")
+source("./hamby252_npeak_result_generator.R")
+source("./hamby252_rf_result_generator.R")
+
+# test if we get the same result
+new_files_name <- list.files("./data-csv", recursive = T, full.names = T)
+ogn_files_name <- list.files("./data-csv-Copy", recursive = T, full.names = T)
+
+for (i in 1:length(new_files_name)) {
+  tt1 <- read.csv(new_files_name[i])
+  tt2 <- read.csv(ogn_files_name[i])
+  
+  if(!identical(tt1,tt2)) print(i)
+}
+
+# 5, 22
+i <- 22
+new_files_name[i]
+ogn_files_name[i]

### 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.R

@@ -809,7 +809,7 @@ p.npeak_plot <- table_cmps_neapk.long %>%
   scale_fill_manual(values = cols_1, labels = labels)
 
 
-## ----result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)} ", fig.height=3----
+## ----result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3----
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"
 # knitr::include_graphics("img/hamby252_v1.png", dpi = 100)
 # CMPS_hamby252_results$plot[[2]]
@@ -817,7 +817,8 @@ p.npeak_plot <- table_cmps_neapk.long %>%
 p1 <- metric_plot_helper(
   CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.max",
   subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
-  xlab(labels[1])
+  xlab(labels[1]) + 
+  theme(axis.text.x = element_text(size=7))
 p2 <- metric_plot_helper(
   CMPS_hamby252_results_seg$cmps.table[[2]], "cmps.maxbar",
   subtitle = "npeaks_set: 5-3-1, seg_length: 50") +
@@ -847,11 +848,12 @@ p.result1_252
 #> )
 
 
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_npeak_result_generator.R

@@ -1,335 +1,0 @@
-################################################################################
-# Note: please read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that func_collection.R and 
-# the data files mentioned in reproducible-readme.md are available
-################################################################################
-
-# set the working directory
-# setwd("~/your-path/supplementary-files")
-
-## Load the required packages
-library(tidyverse)
-if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
-  devtools::install_github("heike/bulletxtrctr", ref = "develop")
-  library(bulletxtrctr)
-}
-if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
-  devtools::install_github("willju-wangqian/cmpsR")
-  library(cmpsR)
-}
-library(x3ptools)
-library(ggpubr)
-library(parallel)
-
-data_path <- "./data-csv/hamby252/"
-
-## Data Processing
-
-#### load the data from reproducible/bullet_signatures_etc/
-b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
-
-#### obtain all comparisons
-b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-#### obtained ID for the damaged bullets;
-###### These IDs are identified by using a Shiny App called bulletinspectR
-tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
-
-#### Include the ground truth for Hamby252
-tmp.tibble <- tibble(bullet1 = b.cb[1,], 
-                     bullet2 = b.cb[2,])
-
-tmp.tibble <- tmp.tibble %>% mutate(
-  type = if_else(
-    bullet1 %>% str_extract("Br\\d+") ==
-      bullet2 %>% str_extract("Br\\d+"),
-    "KM",
-    "KNM"
-  ),
-  type = if_else(is.na(type), "Ukn", type)
-)
-
-###### StudyInfo.xlsx provides the ground truth for Hamby252 
-studyinfo <-
-  readxl::read_xlsx(
-    "./bullet_signatures_etc/StudyInfo.xlsx",
-    sheet = 3,
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_rf_result_generator.R

@@ -1,311 +1,0 @@
-################################################################################
-# Note: please read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that func_collection.R and 
-# the data files mentioned in reproducible-readme.md are available
-################################################################################
-
-# set the working directory
-# setwd("~/your-path/supplementary-files")
-
-## Load the required packages
-library(tidyverse)
-if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
-  devtools::install_github("heike/bulletxtrctr", ref = "develop")
-  library(bulletxtrctr)
-}
-library(x3ptools)
-if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
-  devtools::install_github("willju-wangqian/cmpsR")
-  library(cmpsR)
-}
-library(ggpubr)
-library(parallel)
-library(assertthat)
-require(randomForest)
-
-# define a local function for performing feature extraction in bulletxtrctr
-my_extract_feature_all <- function (aligned, striae, resolution, tmpfile = NULL, ...)
-{
-  feature <- value <- NULL
-  assert_that(!is.null(aligned), !is.null(striae), msg = "aligned and striae must not be NULL")
-  features <- apropos("^extract_feature_") # change: added a start anchor
-  features <- features[!str_detect(features, "extract_feature_cmps")] # change: exclude _cmps from the search list
-  dots <- list(...)
-  values <- features %>% purrr::map_dbl(.f = function(f) {
-    fun <- getFromNamespace(f, asNamespace("bulletxtrctr"))
-    fun_args <- names(formals(fun))
-    matching_args <- dots[names(dots) %in% fun_args]
-    if ("aligned" %in% fun_args) {
-      matching_args$aligned <- aligned$lands
-    }
-    if ("striae" %in% fun_args) {
-      matching_args$striae <- striae$lines
-    }
-    if ("resolution" %in% fun_args) {
-      matching_args$resolution <- resolution
-    }
-    res <- do.call(fun, matching_args)
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/hamby252_seg_result_generator.R

@@ -1,322 +1,0 @@
-################################################################################
-# Note: please read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that func_collection.R and 
-# the data files mentioned in reproducible-readme.md are available
-################################################################################
-
-# set the working directory
-# setwd("~/your-path/supplementary-files")
-
-## Load the required packages
-library(tidyverse)
-if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
-  devtools::install_github("heike/bulletxtrctr", ref = "develop")
-  library(bulletxtrctr)
-}
-library(x3ptools)
-if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
-  devtools::install_github("willju-wangqian/cmpsR")
-  library(cmpsR)
-}
-library(ggpubr)
-library(parallel)
-
-data_path <- "./data-csv/hamby252/"
-
-## Data Processing
-
-#### load the data from reproducible/bullet_signatures_etc/
-b252 <- read_rds("./bullet_signatures_etc/BulletSignatures252.rds")
-
-#### obtain all comparisons
-b.cb <- unique(b252$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-#### obtained ID for the damaged bullets;
-###### These IDs are identified by using a Shiny App called bulletinspectR
-tr.id <- c("Br3-1-4", "Ukn-B-2", "Ukn-Q-4", "Br6-2-1", "Br9-2-4")
-
-#### Include the ground truth for Hamby252
-tmp.tibble <- tibble(bullet1 = b.cb[1,], 
-                     bullet2 = b.cb[2,])
-
-tmp.tibble <- tmp.tibble %>% mutate(
-  type = if_else(
-    bullet1 %>% str_extract("Br\\d+") ==
-      bullet2 %>% str_extract("Br\\d+"),
-    "KM",
-    "KNM"
-  ),
-  type = if_else(is.na(type), "Ukn", type)
-)
-
-###### StudyInfo.xlsx provides the ground truth for Hamby252 
-studyinfo <-
-  readxl::read_xlsx(
-    "./bullet_signatures_etc/StudyInfo.xlsx",
-    sheet = 3,
-    skip = 1
-  )
-
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_npeak_result_generator.R

@@ -1,334 +1,0 @@
-################################################################################
-# Note: please read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that func_collection.R and 
-# the data files mentioned in reproducible-readme.md are available
-################################################################################
-
-# set the working directory
-# setwd("~/your-path/supplementary-files")
-
-## Load the required packages
-library(tidyverse)
-if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
-  devtools::install_github("heike/bulletxtrctr", ref = "develop")
-  library(bulletxtrctr)
-}
-if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
-  devtools::install_github("willju-wangqian/cmpsR")
-  library(cmpsR)
-}
-library(x3ptools)
-library(ggpubr)
-library(parallel)
-
-data_path <- "./data-csv/hamby44/"
-
-## Data Processing
-
-#### load the data from reproducible/bullet_signatures_etc/
-b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
-
-#### obtain all comparisons
-bulletid.tb <- b44 %>% select(scan_id)
-bulletid.tb <- bulletid.tb %>% mutate(
-  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
-  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
-  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
-  bullet_id = paste(barrel_id, bullet)
-)
-b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
-b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-#### import indices of damaged scans
-###### These indices are identified by using a Shiny App called bulletinspectR
-idf.idx <- c(23,35,39,41,102,126,149)
-idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
-
-#### include the ground truth for Hamby44
-key.table <- tibble(
-  bullet.id = c("K",
-                "O",
-                "L",
-                "P",
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_rf_result_generator.R

@@ -1,312 +1,0 @@
-################################################################################
-# Note: please read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that func_collection.R and 
-# the data files mentioned in reproducible-readme.md are available
-################################################################################
-
-# set the working directory
-# setwd("~/your-path/supplementary-files")
-
-## Load the required packages
-library(tidyverse)
-if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
-  devtools::install_github("heike/bulletxtrctr", ref = "develop")
-  library(bulletxtrctr)
-}
-library(x3ptools)
-if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
-  devtools::install_github("willju-wangqian/cmpsR")
-  library(cmpsR)
-}
-library(ggpubr)
-library(parallel)
-library(assertthat)
-require(randomForest)
-
-# define a local function for performing feature extraction in bulletxtrctr
-my_extract_feature_all <- function (aligned, striae, resolution, tmpfile = NULL, ...)
-{
-  feature <- value <- NULL
-  assert_that(!is.null(aligned), !is.null(striae), msg = "aligned and striae must not be NULL")
-  features <- apropos("^extract_feature_") # change: added a start anchor
-  features <- features[!str_detect(features, "extract_feature_cmps")] # change: exclude _cmps from the search list
-  dots <- list(...)
-  values <- features %>% purrr::map_dbl(.f = function(f) {
-    fun <- getFromNamespace(f, asNamespace("bulletxtrctr"))
-    fun_args <- names(formals(fun))
-    matching_args <- dots[names(dots) %in% fun_args]
-    if ("aligned" %in% fun_args) {
-      matching_args$aligned <- aligned$lands
-    }
-    if ("striae" %in% fun_args) {
-      matching_args$striae <- striae$lines
-    }
-    if ("resolution" %in% fun_args) {
-      matching_args$resolution <- resolution
-    }
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/hamby44_seg_result_generator.R

@@ -1,327 +1,0 @@
-################################################################################
-# Note: please read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that func_collection.R and 
-# the data files mentioned in reproducible-readme.md are available
-################################################################################
-
-# set the working directory
-# setwd("~/your-path/supplementary-files")
-
-## Load the required packages
-library(tidyverse)
-if(!require(bulletxtrctr) || packageVersion("bulletxtrctr") < '0.2.1') {
-  devtools::install_github("heike/bulletxtrctr", ref = "develop")
-  library(bulletxtrctr)
-}
-library(x3ptools)
-if(!require(cmpsR) || packageVersion("cmpsR") < '0.1.2') {
-  devtools::install_github("willju-wangqian/cmpsR")
-  library(cmpsR)
-}
-library(ggpubr)
-library(parallel)
-
-data_path <- "./data-csv/hamby44/"
-
-## Data Processing
-
-#### load the data from reproducible/bullet_signatures_etc/
-b44 <- read_rds("./bullet_signatures_etc/BulletSignatures44.rds")
-
-#### obtain all comparisons
-bulletid.tb <- b44 %>% select(scan_id)
-bulletid.tb <- bulletid.tb %>% mutate(
-  barrel_id = sapply(strsplit(scan_id, "-"), "[[", 1),
-  bullet = sapply(strsplit(scan_id, "-"), "[[", 2),
-  land_id = sapply(strsplit(scan_id, "-"), "[[", 3),
-  bullet_id = paste(barrel_id, bullet)
-)
-b44$bullet_id <- bulletid.tb %>% pull(bullet_id)
-b.cb <- unique(b44$bullet_id) %>% utils::combn(m = 2)
-p <- 1:595
-
-#### import indices of damaged scans
-###### These indices are identified by using a Shiny App called bulletinspectR
-idf.idx <- c(23,35,39,41,102,126,149)
-idf.scan_id <- b44 %>% slice(idf.idx) %>% .$scan_id
-
-#### include the ground truth for Hamby44
-key.table <- tibble(
-  bullet.id = c("K",
-                "O",
-                "L",
-                "P",
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/rds_generator.R

@@ -1,311 +1,0 @@
-###############################
-# Note: read reproducible-readme.md first before reproducing the results
-# Please set the working directory properly so that ./data-csv/" is available
-###############################
-
-###############################
-# for the random forest model
-rf.results <- list()
-rf.results[[1]] <- read.csv(file = "./data-csv/hamby252/hamby252_rf_results.csv")
-rf.results[[2]] <- read.csv(file = "./data-csv/hamby44/hamby44_rf_results.csv")
-
-###############################
-# hamby 252 segments
-N <- 8 # the number of different sets of parameters
-CMPS_hamby252_results <- list() # a container for everything
-
-#### setup span1
-CMPS_hamby252_results$span1 <- as.list(rep(0.25, N))
-
-#### setup signature name
-CMPS_hamby252_results$signame <- as.list(rep("sigs25", N))
-# list("sigs75", "sigs25", "sigs25_1062", "sigs15")
-
-#### setup npeaks_set
-CMPS_hamby252_results$npeaks_set <- lapply(1:N, function(t) c(5,3,1))
-
-#### setup seg_length
-CMPS_hamby252_results$seg_length <- as.list(c(25, 50, 75, 100, 125, 150, 175, 200))
-
-#### setup Tx
-CMPS_hamby252_results$Tx <- as.list(rep(25, N))
-
-#### setup outlength
-CMPS_hamby252_results$outlength <- vector(mode = "list", length = N)
-
-#### create a plot title and a file name for each set of parameters
-CMPS_hamby252_results$titlee <- list()
-CMPS_hamby252_results$filename <- list()
-for (i in 1:N) {
-  CMPS_hamby252_results$titlee[[i]] <-
-    paste0(
-      "npeaks_set=c(",
-      paste(CMPS_hamby252_results$npeaks_set[[i]], collapse = ","),
-      ")",
-      ", len=",
-      CMPS_hamby252_results$seg_length[[i]],
-      ", Tx=",
-      CMPS_hamby252_results$Tx[[i]],
-      ", \nspan1=",
-      CMPS_hamby252_results$span1[[i]],
-      ", span2=0.03"
-    )
-  CMPS_hamby252_results$filename[[i]] <- 
-    paste(
-      "hamby252_segment",
-      CMPS_hamby252_results$span1[[i]]*100,
[…]

### 2022-03-31 submissions/resubmission-ju-hofmann2/supplementary-files/test_reproducible.R

@@ -1,24 +1,0 @@
-# run all scripts
-source("./hamby44_seg_result_generator.R")
-source("./hamby44_npeak_result_generator.R")
-source("./hamby44_rf_result_generator.R")
-
-source("./hamby252_seg_result_generator.R")
-source("./hamby252_npeak_result_generator.R")
-source("./hamby252_rf_result_generator.R")
-
-# test if we get the same result
-new_files_name <- list.files("./data-csv", recursive = T, full.names = T)
-ogn_files_name <- list.files("./data-csv-Copy", recursive = T, full.names = T)
-
-for (i in 1:length(new_files_name)) {
-  tt1 <- read.csv(new_files_name[i])
-  tt2 <- read.csv(ogn_files_name[i])
-  
-  if(!identical(tt1,tt2)) print(i)
-}
-
-# 5, 22
-i <- 22
-new_files_name[i]
-ogn_files_name[i]

### 2022-04-12 rj_format/rj-format-ju-hofmann/ju-hofmann.Rmd
change to rjtools

--- 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.Rmd
@@
 ---
-title: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets
+title: "An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets"
 header-includes:
@@
     - Ames, IA 50011
-thanks: |
-  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 abstract: >
@@
 An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
+thanks: |
+  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 preamble: |
   % Any extra LaTeX you need in the preamble
-
 bibliography: ju-hofmann.bib
-output: rticles::rjournal_article
+type: package
+output: 
+  rjtools::rjournal_web_article
 editor_options: 
@@
 ---
-
-```{=tex}
-\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
-\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
-\setlength{\parindent}{0pt}
-```
 
@@
 
-```{r setup_knitr, echo=FALSE}
+```{r setup-knitr, echo=FALSE}
 ## From Josh O'Brien's stackoverflow answer:
@@
 
-In this paper we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
+In this paper, we present an open-source implementation of the algorithm of the Congruent Matching Profile Segments (CMPS) method.
 @cmps developed the CMPS method for "objective comparison of striated tool marks" and demonstrated its use in some examples of comparing bullet signature correlations.
@@
 Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
-Our implementation is made available as part of the `R` package \pkg{cmpsR} on CRAN.
-
-According to the Uniform Crime Reporting Program of FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms" [@fbiucr].
+Our implementation is made available as part of the `R` package \CRANpkg{cmpsR} on CRAN.
+
+According to the Uniform Crime Reporting Program of the FBI (Federal Bureau of Investigation), "more than 76 percent (76.7) of the homicides for which the FBI received weapons data in 2020 involved the use of firearms" [@fbiucr].
 At the same time, the number of murder victims jumped between 2019 and 2020 by more than 23 percent (23.4) to 17754 [@fbiucr20].
@@
 Assessing the similarity between two bullets is based on a comparison of striation marks acquired during the firing process as bullets are propelled through the barrel.
-Current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
+The current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
 This practice has been criticized for its lack of objectivity and the associated problem of determining valid error rates [@pcast].
@@
 These scans played an important role in bringing objectivity into the field.
-In the following sections we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison,  and present results of applying our implementation to real data.
+In the following sections, we will: review the background of bullet signature comparisons, discuss how we followed the idea described by @cmps for the implementation of the CMPS algorithm, propose new metrics based on the CMPS score and a principled evaluation framework for algorithmic results comparison,  and present results of applying our implementation to real data.
 
@@
 The aim of the Hamby Study was to have firearms examiners identify which barrel each of the 15 questioned bullets was fired from.
-The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in \autoref{fig:bullet}.
+The Ruger P-85 barrels are traditionally rifled barrels with six grooves and lands as shown in Figure \@ref(fig:bullet).
 During the firing process, grooves and lands are engraved on a bullet.
@@
 
-The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages \pkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
+The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages \CRANpkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
 \pkg{x3ptools} is a package to read, write, and generally, process x3p files.
@@
 
-\autoref{fig:process} gives an overview of all of the steps in the process from scan to signatures.
-\autoref{fig:process}(a) shows a rendering of a 3D scan of a bullet land engraved area.
+Figure \@ref(fig:process) gives an overview of all of the steps in the process from scan to signatures.
+Figure \@ref(fig:process)(a) shows a rendering of a 3D scan of a bullet land engraved area.
 The raised portion of the surface on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs), the middle area shows a land-engraved area (LEA) with well expressed striation marks.
-The first step of obtaining the bullet signature is to extract a cross-section at a fixed height along the land engraving.
-
-The thin white horizontal line in \autoref{fig:process}(a) indicates which cross-section was identified by the algorithm to represent the LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional view.
-Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in \autoref{fig:process}(c) and \autoref{fig:process}(d)).
-A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature (\autoref{fig:process}(e)) and, finally, the **bullet signature** (\autoref{fig:process}(f)) is obtained as residuals of the cross-section and the fitted smooth.
+The first step of obtaining the bullet signature is to extract a cross-section at a fixed height on the land engraving.
+
+The thin white horizontal line in Figure \@ref(fig:process)(a) indicates which cross-section was identified by the algorithm to represent the LEA; Figure \@ref(fig:process)(b) shows the corresponding cross-sectional view.
+Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in Figure \@ref(fig:process)(c) and Figure \@ref(fig:process)(d)).
+A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature ( Figure \@ref(fig:process)(e)) and, finally, the **bullet signature** (Figure \@ref(fig:process)(f)) is obtained as residuals of the cross-section and the fitted smooth.
 Note, that in @cmps bullet signatures are referred to as bullet profiles.
 However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
-Bullet profiles are shown in panels (b), (c), and (d) of \autoref{fig:process}, while \autoref{fig:process}(f) shows the corresponding bullet signature.
-Identifying the groove engraved areas correctly is fundamental for a correct down-stream analysis of the signatures.
-To allow for a human-in-the middle inspection and intervention we have provided an interactive web-application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
+Bullet profiles are shown in panels (b), (c), and (d) of Figure \@ref(fig:process), while Figure \@ref(fig:process)(f) shows the corresponding bullet signature.
+Identifying the groove engraved areas correctly is fundamental for a correct downstream analysis of the signatures.
+To allow for a human-in-the-middle inspection and intervention we have provided an interactive web application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
 An example of the extraction process with corresponding code and parameter settings can be found in the "Supplementary materials".
@@
 (b) view of the cross-section of the land engraved area at the white line in (a).
-(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves.
+(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of the left and right grooves.
 (d) the crosscut data after chopping the left and right grooves.
 (e) the fitted curvature using LOESS.
-(f) after removing the curvature from the crosscut data, the bullet signature is obtained"}
+(f) after removing the curvature from the crosscut data, the bullet signature is obtained."}
 knitr::include_graphics("ju-hofmann_files/figure-latex/figure1_v2.png", dpi = 144)
@@
 
-In this example, the comparison between \code{sig1} and \code{sig2}, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between \code{sig1} and \code{sig3}, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 1.
+In this example, the comparison between `sig1` and `sig2`, two signatures coming from the same source (a known-match comparison), gets a CMPS score of 17; the comparison between `sig1` and `sig3`, two signatures coming from different sources (a known non-match comparison), gets a CMPS score of 1.
 
@@
 A further example that illustrates the main points is also included.
-In the section on 'Evaluation metrics" we introduce new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.
+In the section on 'Evaluation metrics", we introduce new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.
 The section "Results" presents the results of evaluating the \pkg{cmpsR} package using Hamby set 252 and Hamby set 44.
@@
 1.
-**cut the comparison signature into consecutive, non-overlapping and equal-length basis segments:** The command \code{get\_segs(x, len=50)} implements this step: it takes bullet signature \code{x} in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length \code{len}, which are referred to as "basis segments".
-Note that the parameter \code{len} determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison.
-The default value of \code{len} is 50, which will result in about 25 basis segments for the example data of the package.
+**cut the comparison signature into consecutive, non-overlapping, and equal-length basis segments:** The command `get_segs(x, len=50)` implements this step: it takes bullet signature `x` in the format of a numeric vector and cuts it into consecutive, non-overlapping and equal-length segments of length `len`, which are referred to as "basis segments".
+Note that the parameter `len` determines the length of a basis segment and thus affects the total number of basis segments, which is the upper limit of the CMPS score of a comparison.
+The default value of `len` is 50, which will result in about 25 basis segments for the example data of the package.
 
@@
 **identify candidate positions:** For each basis segment a set of candidate registration positions on the comparison signature is identified based on the segment's similarity to the reference signature.
-    In a first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
+    In the first step, the cross-correlation function of the segment to the reference is calculated, then a number of positions with high correlation values are identified as candidate positions.
     In case multiple segment lengths are considered, the length of each basis segment is expanded (by default it is doubled) and these two steps are repeated.
     Only when candidate positions coincide (or are similar enough), they are considered further.
-    \autoref{fig:segplots} and \autoref{fig:seg_all} illustrate these ideas.
-
-    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment \code{x} and the reference signature \code{y} using the function \code{get\_ccf4(x, y, ...)} as shown in \autoref{fig:segplot2}.
+    Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-web)', '\\@ref(fig:segplots)'))` and Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-all-web)', '\\@ref(fig:segall)'))` illustrate these ideas.
+
+    -   **Calculate the cross-correlation curve:** Calculate the cross-correlation curve between a basis segment `x` and the reference signature `y` using the function `get_ccf4(x, y, ...)` as shown in Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-web)(b)', '\\@ref(fig:segplot2)'))`.
 The position indicates the lag by which a basis segment is moved with respect to its original placement.
@@
     -   **Correlation peaks:** Two strategies referred to as "multi-peak inspection" and "multi-peak inspection at different segment lengths" in @cmps are used for identifying positions of correlation peaks as candidate positions.
-The latter is also called "multi-segment lengths strategy".
-The parameter \code{npeaks\_set} in \code{extract\_feature\_cmps(...)} determines which strategy to use and the number of candidate positions:
-
-        -   If \code{npeaks\_set} is an integer vector of length 1, for example \code{npeaks\_set = 5}, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
-        -   If \code{npeaks\_set} is an integer vector of length more than 1, for example \code{npeaks\_set = c(5, 3, 1)}, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
-\autoref{fig:seg_all} shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
+The latter is also called the "multi-segment lengths strategy".
+The parameter `npeaks_set` in `extract_feature_cmps(...)` determines which strategy to use and the number of candidate positions:
+
+        -   If `npeaks_set` is an integer vector of length 1, for example, `npeaks_set = 5`, the positions of the top five peaks in the cross-correlation curve are identified as candidate positions for registration.
+        -   If `npeaks_set` is an integer vector of length more than 1, for example, `npeaks_set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: calculate the cross-correlation function between a basis segment and the reference and identify positions of the top five peaks; double the segment length to a specified value, re-calculate the cross-correlation function, and identify three peaks; repeat this process and identify a single peak in the newly computed cross-correlation function.
+Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-all-web)', '\\@ref(fig:segall)'))` shows an example of three levels of basis segment 6 and their corresponding cross-correlation curves and identified peaks.
 Note that in @cmps the segment length is doubled at each level of a basis segment, but in the present implementation users are allowed to choose the segment length at each level.
-        -   \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)} computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
-The number of peaks detected is equal to \code{npeaks}, which is an integer.
-\code{segments}, \code{seg\_outlength}, and \code{nseg} determines the segment in the cross-correlation computation, and \code{comp} gives the reference signature.
-If the multi-segment lengths strategy is used, then \code{get\_ccr\_peaks(...)} is called in a \code{lapply()} for each level of the basis segment.
-The resulting list is called \code{ccr\_list}.
-
-    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called as a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by \code{Tx} in all segment levels.
+        -   `get_ccr_peaks(comp, segments, seg_outlength, nseg = 1, npeaks = 5)` computes the cross-correlation curve between a basis or increased segment and the reference signature and finds peaks in the cross-correlation curve.
+The number of peaks detected is equal to `npeaks`, which is an integer.
+`segments`, `seg_outlength`, and `nseg` determine the segment in the cross-correlation computation, and `comp` gives the reference signature.
+If the multi-segment lengths strategy is used, then `get_ccr_peaks(...)` is called in a `lapply()` for each level of the basis segment.
+The resulting list is called `ccr_list`.
+
+    -   **multi-segment lengths strategy:** with the multi-segment lengths strategy being used, a position is identified as a candidate position for registration and is called a "consistent correlation peak" if it results in a top peak in the cross-correlation curve with a tolerance zone determined by `Tx` in all segment levels.
 Note that in @cmps, a segment at its largest scale (highest level) always identifies one peak, but we do not have this requirement in our implementation.
 
-        -   the function \code{get\_seg\_scale(segments, nseg, out\_length)} is used to obtain the (potentially increased) version of a basis segment.
-\code{segments}, which is a list containing all basis segments generated by the function \code{get\_segs(...)} in step 1, and \code{nseg} are used to determine the basis segment to be increased.
-\code{out\_length} specifies the length of the output segment.
-        -   \code{get\_ccp(ccr\_list, Tx = 25)} tries to identify the "consistent correlation peak".
-\code{ccr\_list} is the result of \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx} determines the size of a tolerance zone used in identifying the consistent correlation peak.
-\code{get\_ccp(...)} returns \code{NULL} if there is no consistent correlation peak.
+        -   the function `get_seg_scale(segments, nseg, out_length)` is used to obtain the (potentially increased) version of a basis segment.
+`segments`, which is a list containing all basis segments generated by the function `get_segs(...)` in step 1, and `nseg` are used to determine the basis segment to be increased.
+`out_length` specifies the length of the output segment.
+        -   `get_ccp(ccr_list, Tx = 25)` tries to identify the "consistent correlation peak".
+`ccr_list` is the result of `lapply()` and `get_ccr_peaks(...)`, and `Tx` determines the size of a tolerance zone used in identifying the consistent correlation peak.
+`get_ccp(...)` returns `NULL` if there is no consistent correlation peak.
 
 3.
-**determine the congruent registration position:** A candidate position "receives" votes from basis segments that identify it or a close position within a tolerance zone of \code{Tx} as a candidate position in step 2.
+**determine the congruent registration position:** A candidate position "receives" votes from basis segments that identify it or a close position within a tolerance zone of `Tx` as a candidate position in step 2.
     Votes for all candidate positions are tallied, and the position with the highest number of votes gets chosen as the *congruent registration position*, indicating that most of the basis segments find their highly similar counterpart in the reference signature in terms of correlation at this registration position.
-    In case of ties the middle position is taken as the congruent registration position.
+    In the case of ties, the middle position is taken as the congruent registration position.
     Basis segments with a congruent registration position are called "congruent matching profile segments" (CMPS).
     The total number of CMPS is the CMPS score of the comparison.
-    \code{get\_CMPS(input\_ccp, Tx = 25)} is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
-
-Note that there are several parameters in the CMPS algorithm that will affect the final results and are left to the users to decide, such as the length of basis segments \code{seg\_length} in step 1, the number of peaks \code{npeaks\_set} identified on each level in step 2, and the length of the tolerance zone \code{Tx} in both step 2 and 3.
-In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
-However, the authors state that no cross-validation has been done - there might also be issues with respect to resolution of the scans.
+    `get_CMPS(input_ccp, Tx = 25)` is the function that tallies the votes and determines the congruent registration position and congruent matching profile segments (CMPS).
+
+Note that there are several parameters in the CMPS algorithm that will affect the final results and are left to the users to decide, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks_set` identified on each level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3.
+In our implementation of the CMPS algorithm, we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters.
+However, the authors state that no cross-validation has been done - there might also be issues with respect to the resolution of the scans.
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
 However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters.
-The main function that combines all steps in the CMPS algorithm described above is called \code{extract\_feature\_cmps(...)}.
+The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
 Here we present it with its default parameters.
@@
 
-The function \code{extract\_feature\_cmps} allows for the following input from users besides the previously discussed parameters \code{seg\_length}, \code{npeaks\_set}, and \code{Tx}:
-
--   \code{x} and \code{y} are two signatures: \code{x} serves as the comparison signature (which will be divided into basis segments) and \code{y} is the reference signature;
-
--   \code{include} determines the format of the function result.
-    Besides the \code{CMPS\_score}, other aspects of the comparison help in understanding how the \code{CMPS\_score} is computed.
-    By default \code{include} is set to \code{NULL} and only the \code{CMPS\_score} is returned; further results are included when \code{include} is (an abbreviation of) one of or a vector of the following strings: \code{"nseg"}, \code{"congruent\_pos"}, \code{"congruent\_seg\_idx"}, \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}.
-    If \code{include} is specified as \code{"full\_result"} (or its abbreviation), the output includes everything listed below.
-
-    -   \code{nseg}: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
-    -   \code{congruent\_pos}: the congruent registration position;
-    -   \code{congruent\_seg\_idx}: the indices of all congruent matching profile segments;
-    -   \code{ccp\_list}: a list showing identified candidate positions of all basis segments;
-    -   \code{pos\_df}: a data frame containing all candidate positions and their respective number of votes;
-    -   \code{segments}: a list containing all basis segments;
-    -   \code{parameters}: a list containing all input arguments of \code{extract\_feature\_cmps};
-
--   \code{outlength} specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
-    By default \code{outlength} is set to \code{NULL}, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
-
-In the remainder of the paper we showcase the use of the \pkg{cmpsR} functionality on some examples and present the results of applying it to two datasets.
+The function `extract_feature_cmps` allows for the following input from users besides the previously discussed parameters `seg_length`, `npeaks_set`, and `Tx`:
+
+-   `x` and `y` are two signatures: `x` serves as the comparison signature (which will be divided into basis segments) and `y` is the reference signature;
+
+-   `include` determines the format of the function result.
+    Besides the `CMPS_score`, other aspects of the comparison help in understanding how the `CMPS_score` is computed.
+    By default `include` is set to `NULL` and only the `CMPS_score` is returned; further results are included when `include` is (an abbreviation of) one of or a vector of the following strings: `"nseg"`, `"congruent_pos"`, `"congruent_seg_idx"`, `"segments"`, `"parameters"`, and `"full_result"`.
+    If `include` is specified as `"full_result"` (or its abbreviation), the output includes everything listed below.
+
+    -   `nseg`: the number of basis segments from the comparison signature; this is also the highest possible CMPS score of the comparison;
+    -   `congruent_pos`: the congruent registration position;
+    -   `congruent_seg_idx`: the indices of all congruent matching profile segments;
+    -   `ccp_list`: a list showing identified candidate positions of all basis segments;
+    -   `pos_df`: a data frame containing all candidate positions and their respective number of votes;
+    -   `segments`: a list containing all basis segments;
+    -   `parameters`: a list containing all input arguments of `extract_feature_cmps`;
+
+-   `outlength` specifies the segment length of a basis segment at each level under the multi-segment lengths strategy.
+    By default `outlength` is set to `NULL`, indicating that a basis segment should double its segment length at the next level and conforming to the description in @cmps .
+
+In the remainder of the paper, we showcase the use of the \pkg{cmpsR} functionality on some examples and present the results of applying it to two datasets.
 
@@
 
-\code{bullets\$sigs} is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in \autoref{fig:sigs}.
-\code{bullets\$source} contains the URLs to the corresponding x3p file containing the topographic scan from the NIST Ballistics Toolmark Research Database [@nistdb].
+`bullets$sigs` is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in Figure \@ref(fig:sigs).
+`bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan from the NIST Ballistics Toolmark Research Database [@nistdb].
 
@@
 
-The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects \code{sigs2} and \code{sigs1}, respectively.
+The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored in objects `sigs2` and `sigs1`, respectively.
 This comparison consists of a pair of signatures that are known to be a match -- a KM (known match) comparison.
@@
 
-In the first example, \code{npeaks\_set} is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object \code{cmps\_with\_multi\_scale}.
-For \code{cmps\_without\_multi\_scale} each basis segment is linked to the top 5 candidate positions.
-We use \code{include = "full\_result"} to capture all results.
+In the first example, `npeaks_set` is a vector of three integers, i.e. the algorithm uses the multi-segment lengths strategy to create the result object `cmps_with_multi_scale`.
+For `cmps_without_multi_scale` each basis segment is linked to the top 5 candidate positions.
+We use `include = "full_result"` to capture all results.
 In this example, the CMPS is 9 when using multiple segments, and 12 when using a single segment.
-As discussed in @cmps, using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score based method is walking the line between false positives and false negatives.
+As discussed in @cmps, using multi-segment lengths strategy can reduce the number of false positives when identifying candidate positions; however, any score-based method is walking the line between false positives and false negatives.
 As the number of false positives is reduced the number of false negatives might rise.
@@
 
-We also implemented graphing tools for visualizing results of the CMPS algorithm.
+We also implemented graphing tools for visualizing the results of the CMPS algorithm.
 The goal is to provide users with tools to inspect each of the basis segments and to help them have a better understanding of how the algorithm works.
-\autoref{fig:sigplots} shows the plots generated by the first graphing function, \code{cmps\_signature\_plot()}, and continues with the example above.
-\code{cmps\_signature\_plot()} takes the output of \code{extract\_feature\_cmps(..., include = "full\_result")} and returns a list of 5 elements.
+Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:sigplots-web)', '\\@ref(fig:sigplots)'))` shows the plots generated by the first graphing function, `cmps_signature_plot()`, and continues with the example above.
+`cmps_signature_plot()` takes the output of `extract_feature_cmps(..., include = "full_result")` and returns a list of 5 elements.
 It creates an overall impression of how the comparison signature aligns with the reference signature at the congruent registration position.
 
--   The first element is a plot called \code{segment\_shift\_plot}, shown in \autoref{fig:sigplot}.
+-   The first element is a plot called `segment_shift_plot`, shown in Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:sigplots-web)(a)', '\\@ref(fig:sigplot)'))`.
 On this plot the reference signature is drawn as a black line, congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.
 
--   The second plot is called \code{signature\_shift\_plot}, shown in \autoref{fig:sigplot2}.
+    ```{r sigplots-code-web1, eval=FALSE, echo=knitr::is_html_output()}
+    sig_plot <- cmps_signature_plot(
+      cmps_with_multi_scale
+    )
+
+    # (a)
+    sig_plot$segment_shift_plot
+    ```
+
+-   The second plot is called `signature_shift_plot`, shown in Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:sigplots-web)(b)', '\\@ref(fig:sigplot2)'))`.
 This visual presents both the comparison signature and the reference signature.
@@
 Congruent matching profile segments are highlighted by solid red lines.
+
+    ```{r sigplots-code-web2, eval=FALSE, echo=knitr::is_html_output()}
+    # (b)
+    sig_plot$signature_shift_plot
+    ```
+
+```{r sigplots-web, eval=knitr::is_html_output(), echo=FALSE, fig.cap="In (a) the black line shows the comparison signature; each red line segment shows one congruent matching profile segment.
+In (b) the black line shows the reference signature; the red line shows the comparison signature.
+Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.", out.width=".7\\textwidth", fig.align="center", fig.height=6}
+sig_plot <- cmps_signature_plot(
+      cmps_with_multi_scale
+    )
+
+ggarrange(sig_plot$segment_shift_plot, sig_plot$signature_shift_plot,
+          ncol = 1,
+          common.legend = FALSE, labels = c("(a)", "(b)"),
+          hjust = -0.1
+)
+```
 
@@
 ```
--   Other elements of this list are \code{seg\_shift} and \code{sig\_shift}.
-\code{sig\_shift} gives the congruent registration position, while \code{seg\_shift} is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
+-   Other elements of this list are `seg_shift` and `sig_shift`.
+`sig_shift` gives the congruent registration position, while `seg_shift` is a data frame showing the congruent matching profile segments and their identified candidate position closest to the congruent registration position.
 
@@
 
-While \code{cmps\_signature\_plot()} focuses on the signature level, \code{cmps\_segment\_plot()} focuses on the segment level.
-It provides the "full result" of \code{extract\_feature\_cmps()}, but also takes an argument, \code{seg\_idx}, indicating which segment should be inspected.
-When checking \code{sig\_plot\$seg\_shift} we notice that segment number 6 is not one of the congruent matching profile segments.
-We can therefore set \code{seg\_idx = 6} in \code{cmps\_segment\_plot()} and investigate the reason why this segment disagrees with the congruent registration position.
-
-For each segment scale, we have two plots: \code{segment\_plot} and \code{scale\_ccf\_plot}, as shown in \autoref{fig:segplots} for the example of segment number 6:
-
--   \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6 at level one (in its original length).
-We used \code{npeaks\_set = c(5, 3, 1)} in \code{extract\_feature\_cmps()} when calculating the CMPS score.
+While `cmps_signature_plot()` focuses on the signature level, `cmps_segment_plot()` focuses on the segment level.
+It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg_idx`, indicating which segment should be inspected.
+When checking `sig_plot$seg_shift` we notice that segment number 6 is not one of the congruent matching profile segments.
+We can therefore set `seg_idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
+
+For each segment scale, we have two plots: `segment_plot` and `scale_ccf_plot`, as shown in Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-web)', '\\@ref(fig:segplots)'))` for the example of segment number 6:
+
+-   Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-web)(a)', '\\@ref(fig:segplot)'))` is the `segment_plot` for basis segment 6 at level one (in its original length).
+We used `npeaks_set = c(5, 3, 1)` in `extract_feature_cmps()` when calculating the CMPS score.
 Therefore the top five peaks are identified in the cross-correlation curve at level one.
-Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the \code{segment\_plot}.
+Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
 The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
--   \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment 6 at level one.
+
+    ```{r segplots-code-web1, eval=FALSE, echo=knitr::is_html_output()}
+    seg_plot <- cmps_segment_plot(
+      cmps_with_multi_scale,
+      seg_idx = 6
+    )
+
+    # (a)
+    seg_plot[[1]]$segment_plot
+    ```
+
+-   Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-web)(b)', '\\@ref(fig:segplot2)'))` is the `scale_ccf_plot` of basis segment 6 at level one.
 It shows the cross-correlation curve computed by the reference signature and the level-one basis segment 6.
 The five highest peaks are marked by dots on the curve.
+
+    ```{r segplots-code-web2, eval=FALSE, echo=knitr::is_html_output()}
+    # (b)
+    seg_plot[[1]]$scale_ccf_plot
+    ```
+
+```{r segplots-web, eval=knitr::is_html_output(), echo=FALSE, fig.cap="Plot (a) shows segment_plot for segment 6 at level one.
+The original position of segment 6 is indicated by the solid black line.
+Positions, where the segment achieves the 5 highest cross-correlations, are indicated by the dashed line segments.
+The scale_ccf_plot in plot (b) shows the cross-correlation curve between the reference signature and segment 6 at level one.
+The five highest peaks are marked by dots.
+The vertical red dashed line indicates the congruent registration position; the green dashed line shows a peak position in the highest segment level; the blue dashed lines show the tolerance zone around the green dashed line.
+We can see that none of the five highest peaks at level one falls within the tolerance zone, indicating that there is no consistent correlation peak or a candidate position identified by basis segment 6 under the multi-segment lengths strategy.
+Thus, the basis segment 6 doesn't vote for the congruent registration position and is not a cmps.", out.width=".7\\textwidth", fig.align="center", fig.height=6}
+seg_plot <- cmps_segment_plot(
+  cmps_with_multi_scale,
+  seg_idx = 6
+)
+
+ggarrange(seg_plot[[1]]$segment_plot, seg_plot[[1]]$scale_ccf_plot,
+          ncol = 1,
+          common.legend = FALSE, labels = c("(a)", "(b)"),
+          hjust = -0.1
+)
+```
 
@@
 ```
-Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the \code{segment\_plot} and \code{scale\_ccf\_plot} of all three segment levels together, as shown in \autoref{fig:seg_all} with the help of \code{ggpubr::ggarrange()}.
-
-```{=tex}
-\begin{figure}
-```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
+
+Additionally, users can have more insights about why segment 6 is not a congruent matching profile segment if we put the `segment_plot` and `scale_ccf_plot` of all three segment levels together, as shown in Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-all-web)', '\\@ref(fig:segall)'))` with the help of `ggpubr::ggarrange()`.
+
+```{r segplots-all-web, eval=knitr::is_html_output(), echo=knitr::is_html_output(), fig.cap="Put segment_plot and scale_ccf_plot of all three levels together.
+We are identifying the five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks_set = c(5, 3, 1).
+The highest peak position at level three is marked by the green dashed line across all segment levels.
+However, the highest peak on level three does not coincide with any of the top five highest peaks at level one.
+This indicates that there is no consistent correlation peak or a candidate position for basis segment 6 under the multi-segment lengths strategy.", out.width=".7\\textwidth", fig.align="center", fig.height=6}
 library(ggpubr)
@@
 ```
-\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1).
+
+```{=tex}
+\begin{figure}
+```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
+library(ggpubr)
+
+ggarrange(
+  plotlist =
+    unlist(seg_plot,
+      recursive = FALSE
+    ),
+  ncol = 2,
+  nrow = 3
+)
+```
+\caption{\label{fig:segall} Put segment\_plot and scale\_ccf\_plot of all three levels together.
+We are identifying the five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1).
 The highest peak position at level three is marked by the green dashed line across all segment levels.
@@
 ```
-In \autoref{fig:seg_all}, the red vertical dashed line indicates the congruent registration position.
+In Figure `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(fig:segplots-all-web)', '\\@ref(fig:segall)'))`, the red vertical dashed line indicates the congruent registration position.
 We can see that the basis segment 6 does obtain a peak near the congruent registration position at level two and level three, respectively; however, this position doesn't give one of the five highest peaks at level one.
@@
 The identified top five peaks at level one are also examples of "false positive" peaks.
-The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of multi-segment lengths strategy.
+The "true positive" peak (the peak within the tolerance zone of the congruent registration position) is identified at level two and three by increasing the segment length, which justifies the usage of the multi-segment lengths strategy.
 
@@
 Here, we are working with bullets fired from Ruger P85 barrels with six lands and grooves.
-A comparison of two bullets therefore involves 36 land-to-land comparisons, resulting in 36 CMPS scores (as shown in \autoref{fig:tiles}).
+A comparison of two bullets, therefore, involves 36 land-to-land comparisons, resulting in 36 CMPS scores (as shown in Figure \@ref(fig:tiles)).
 In order to obtain a single similarity score of a bullet-level comparison, we need to summarize these 36 CMPS scores.
@@
 \begin{align}
-\mathcal{P}_k = \{ (i,j): i = 1, \dots, n ; \; j = (i + k) \;\mathrm{mod}\; n \}
+\mathcal{P}_k = \{ \left(i,j\right): i = 1, \dots, n ; \; j = \left(i + k\right) \;\mathrm{mod}\; n \}
 \end{align}
@@
 , where `mod` denotes the modulo operation.
-For example, $\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}$ when $n = 6$.
+For example, $\mathcal{P}_1 = \{ \left(1,2\right), \left(2,3\right), \left(3,4\right), \left(4,5\right), \left(5,6\right), \left(6,1\right) \}$ when $n = 6$.
 Let $k^*$ denote the index of the highest phase.
@@
 We can continue with the example used in previous sections.
-\code{bullets} contains bullet signatures of two bullets, \code{bullet1} and \code{bullet2}.
+`bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
 As mentioned before, each bullet has 6 land engravings, resulting in 6 bullet signatures.
 Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
-We use multi-segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in \autoref{fig:tiles}.
+We use multi-segment lengths strategy with default parameters to compute these CMPS scores, and the result is shown in Figure \@ref(fig:tiles).
 We can see that in this example,
@@
 \mathrm{\overline{CMPS}_{max}} &= \frac{1}{6} \sum_{(i,j) \in \mathcal{P}_1} c_{ij} \\
-                        &= \frac{1}{6} (c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}) \\
-                        &= \frac{1}{6} (3+17+14+10+15+16) \\
+                        &= \frac{1}{6} \left(c_{12} + c_{23} + c_{34} + c_{45} + c_{56} + c_{61}\right) \\
+                        &= \frac{1}{6} \left(3+17+14+10+15+16\right) \\
                         &= 12.5
@@
 \begin{align}
-\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n(n-1)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
+\mathrm{\overline{CMPS}_{diff}} = \left[  \frac{1}{n} \sum_{(i,j) \in \mathcal{P}_{k^*}} c_{ij}\right] - \left[  \frac{1}{n\left(n-1\right)} \sum_{(i,j) \notin \mathcal{P}_{k^*}} c_{ij}\right]
 \end{align}
@@
 
-Another issue with the CMPS score is that the highest possible CMPS score (the total number of basis segments) might differ across comparisons (as shown in \autoref{fig:tiles2}(a)) due to different lengths of bullet signatures and different lengths of basis segments specified by the parameter.
+Another issue with the CMPS score is that the highest possible CMPS score (the total number of basis segments) might differ across comparisons (as shown in Figure \@ref(fig:tiles2)(a)) due to different lengths of bullet signatures and different lengths of basis segments specified by the parameter.
 A CMPS score of 5 might indicate a non-match if the highest possible CMPS score is 30 but indicate a match if the highest possible CMPS score is 6.
@@
 ```
-The scaled CMPS scores of the above example are shown in \autoref{fig:tiles2}(b).
+The scaled CMPS scores of the above example are shown in Figure \@ref(fig:tiles2)(b).
 Compared to the original CMPS scores, scaled scores have values within the interval $[0, 1]$ regardless of the length of the basis segments and therefore make a comparison of values possible across different parameter choices.
-Similarly to the original CMPS scores, we will denote the scaled CMPS scores adjusted for out-of-phase background values by $\mathrm{\overline{CMPS^*}_{diff}}$.
-For example, $\mathrm{\overline{CMPS^*}_{diff}} = 0.498$ for \autoref{fig:tiles2}(b)
+Similar to the original CMPS scores, we will denote the scaled CMPS scores adjusted for out-of-phase background values by $\mathrm{\overline{CMPS^*}_{diff}}$.
+For example, $\mathrm{\overline{CMPS^*}_{diff}} = 0.498$ for Figure \@ref(fig:tiles2)(b)
 
@@
 \begin{align}
-V = \frac{\sum_k n_k (\bar{y}_{k.} - \bar{y}_{..})^2}{\sum_k \sum_l^{n_k} (y_{kl} - \bar{y}_{k.})^2 }.
+V = \frac{\sum_k n_k \left(\bar{y}_{k.} - \bar{y}_{..} \right)^2}{\sum_k \sum_l^{n_k} \left(y_{kl} - \bar{y}_{k.} \right)^2 }.
 \end{align}
@@
 But when algorithms achieve 100 percent accuracy and AUC value of 1, we need other measures such as the sum of squares ratio to further distinguish the performance of algorithms.
-In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced earlier and investigate effects of different parameter settings.
+In the following section, we will use the sum of squares ratio to compare the CMPS metrics introduced earlier and investigate the effects of different parameter settings.
 
@@
 
-\autoref{fig:result1_252} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy.
-The parameters we used in \code{extract\_feature\_cmps} for the CMPS algorithm are:
+Figure \@ref(fig:result1-252) shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ after we applied the CMPS algorithm to Hamby set 252 with the multi-segment lengths strategy.
+The parameters we used in `extract_feature_cmps` for the CMPS algorithm are:
 
@@
 
-As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in \autoref{fig:result1_252} are qualitatively equivalent to those presented in @cmps, showing a clear separation between scores based on comparisons from known matches (KM) and scores from comparisons of known non-matches (KNM) for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
-
-Additionally, to mimic the parameters used in @cmps, we set \code{seg\_length = 50} and \code{Tx = 25} to make sure that each basis segment has length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu m for Hamby set 252).
+As noted above, the CMPS scores we found here are not exactly the same as those presented in @cmps since we were not able to follow their framework, but the results presented in Figure \@ref(fig:result1-252) are qualitatively equivalent to those presented in @cmps, showing a clear separation between scores based on comparisons from known matches (KM) and scores from comparisons of known non-matches (KNM) for both $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$.
+
+Additionally, to mimic the parameters used in @cmps, we set `seg_length = 50` and `Tx = 25` to make sure that each basis segment has a length of 78.125 \textmu m and the tolerance zone is $\pm 39.0625$ \textmu m (one unit represents 1.5625 \textmu m for Hamby set 252).
 
@@
 
-```{r plot_computation, echo=FALSE, fig.width=8, fig.height = 8, out.width='\\linewidth'}
+```{r plot-computation, echo=FALSE, fig.width=8, fig.height = 8, out.width='\\linewidth'}
 # 252 - seg
@@
 
-```{r result1_252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \\texttt{seg\\_length = 50}, \\texttt{Tx = 25}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3}
+```{r result1-252, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; seg\\_length = 50, Tx = 25, npeaks\\_set = c(5,3,1); instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars.
+", fig.height=3}
 # [4] "span1=0.25, span2=0.03, rm_outliers = TRUE, 5025, 531"
@@
 
-Similar procedures are applied to Hamby set 44, and \autoref{fig:result1_44} shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-The parameters used in \code{extract\_feature\_cmps} are:
+Similar procedures are applied to Hamby set 44, and Figure \@ref(fig:result1-44) shows the distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
+The parameters used in `extract_feature_cmps` are:
 
@@
 
-Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we make \code{seg\_length = 61} and \code{Tx = 30} to ensure that the setup of Hamby set 44 is similar to that of Hamby set 252, resulting in basis segments of 78.69 \textmu m and the tolerance zone of $\pm 38.7$ \textmu m.
-
-As shown in \autoref{fig:result1_44}, again, we are able to see a clear separation between the known match comparisons and the known non-match comparisons, even though the separation is relatively small compared with that of Hamby set 252, which is also indicated by the sum of squares ratios.
+Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we make `seg_length = 61` and `Tx = 30` to ensure that the setup of Hamby set 44 is similar to that of Hamby set 252, resulting in basis segments of 78.69 \textmu m and the tolerance zone of $\pm 38.7$ \textmu m.
+
+As shown in Figure \@ref(fig:result1-44), again, we are able to see a clear separation between the known match comparisons and the known non-match comparisons, even though the separation is relatively small compared with that of Hamby set 252, which is also indicated by the sum of squares ratios.
 For this specific set of parameters, the sum of squares ratios are 8.87 and 10.64 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
@@
 
-```{r result1_44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \\texttt{seg\\_length = 61}, \\texttt{Tx = 30}, \\texttt{npeaks\\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars ", fig.height=3, warning=FALSE}
+```{r result1-44, echo=FALSE, out.width="400px", fig.cap="Distribution of $\\mathrm{CMPS_{max}}$ and $\\mathrm{\\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; seg\\_length = 61, Tx = 30, npeaks\\_set = c(5,3,1); instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars.
+", fig.height=3, warning=FALSE}
 p1 <- metric_plot_helper(
@@
 
-```{r param_seg_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter \\texttt{seg\\_length}).
+```{r param-seg-plot, echo=FALSE, out.width="400px", fig.cap="Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter seg\\_length).
 Only the $\\mathrm{CMPS_{max}}$ metric suggests that the default values for the basis segment length result in the best separation.
-Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones.
-For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results", fig.height=3, warning = FALSE}
+Better separation is achieved based on the modified CMPS metrics, including the newly suggested ones.
+For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results.
+", fig.height=3, warning = FALSE}
 p.seg_plot
@@
 
-```{r param_npeak_plot, echo=FALSE, out.width="400px", fig.cap="Comparison of CMPS results based on different strategies of number of peak selections.
+```{r param-npeak-plot, echo=FALSE, out.width="400px", fig.cap="Comparison of CMPS results based on different strategies of number of peak selections.
 Starred results compare CMPS performance with results published in the literature.
-Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but the random forest scores with the same logic.
+Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but on the random forest scores with the same logic.
 Since random forest scores lie within the interval $[0, 1]$, scaling the random forest scores will not change the results.", fig.height=3, warning = FALSE}
@@
 
-We investigated the effects of different sets of parameters at the example of both Hamby sets 252 and 44.
-More specifically, we investigated the separation achieved using the \pkg{cmpsR} implementation under various segment lengths (controlled by the parameter \code{seg\_length}).
-Specifically, we fixed the parameter \code{npeaks\_set} that controls the number of peaks at each segment level to be \code{npeaks\_set = c(5,3,1)} and modified the parameter \code{seg\_length}.
-\autoref{fig:param_seg_plot} shows that the default values of \code{seg\_length}  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
-However, we also see, that for Hamby set 252 a basis segment length of 75 is a better choice than the default segment length; a basis segment length of 122 results in a higher value of sum of squares ratio for Hamby 44.
-
-\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using different strategies for identifying peaks in the correlation structure between signatures.
+We investigated the effects of different sets of parameters in the example of both Hamby sets 252 and 44.
+More specifically, we investigated the separation achieved using the \pkg{cmpsR} implementation under various segment lengths (controlled by the parameter `seg_length`).
+Specifically, we fixed the parameter `npeaks_set` that controls the number of peaks at each segment level to be `npeaks_set = c(5, 3, 1)` and modified the parameter `seg_length`.
+Figure \@ref(fig:param-seg-plot) shows that the default values of `seg_length`  for Hamby 252 and Hamby 44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69 \textmu m, respectively) result in high values of the sum of squares ratio, no matter which CMPS metrics are used for an evaluation.
+However, we also see, that for Hamby set 252 a basis segment length of 75 is a better choice than the default segment length; a basis segment length of 122 results in a higher value of the sum of squares ratio for Hamby 44.
+
+Figure \@ref(fig:param-npeak-plot) shows the results of the CMPS algorithm using different strategies for identifying peaks in the correlation structure between signatures.
 Basis segment length is fixed to the default level for this evaluation.
-As can be seen in \autoref{fig:param_npeak_plot}, the default value of \code{npeaks\_set} (\code{npeaks\_set = c(5,3,1)}) leads to promising results in terms of the sum of squares ratio; however, other choices of \code{npeaks\_set} match and  exceed this sum of squares ratio value.
+As can be seen in Figure \@ref(fig:param-npeak-plot), the default value of `npeaks_set` (`npeaks_set = c(5, 3, 1)`) leads to promising results in terms of the sum of squares ratio; however, other choices of `npeaks_set` match and exceed this sum of squares ratio value.
 
@@
 
-What we can also observe in \autoref{fig:param_seg_plot} and \autoref{fig:param_npeak_plot} is that the values of the sum of squares ratio for Hamby 44 is lower than those for Hamby 252. 
+What we can also observe in Figure \@ref(fig:param-seg-plot) and Figure \@ref(fig:param-npeak-plot) is that the values of the sum of squares ratio for Hamby 44 is lower than those for Hamby 252. 
 This might be because determining the source is a harder task for Hamby 44 than for Hamby 252, but also suggests that the choice of parameters also depends on the resolution or the scanning process of the data set.
@@
 
-The purpose of the results shown in \autoref{fig:param_seg_plot} and \autoref{fig:param_npeak_plot} is not to determine the "best" parameters for the CMPS algorithm, but to show that the sum of squares ratio can be used as an evaluation measure to compare different parameters, metrics, or scans.
+The purpose of the results shown in Figure \@ref(fig:param-seg-plot) and Figure \@ref(fig:param-npeak-plot) is not to determine the "best" parameters for the CMPS algorithm, but to show that the sum of squares ratio can be used as an evaluation measure to compare different parameters, metrics, or scans.
 A pipeline that maximizes the sum of squares ratio might help researchers determine the set of parameters that work best for their data. 
@@
 
-@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for \code{npeaks\_set = 5} and \code{npeaks\_set = c(5,3,1)} with (presumably) Hamby 252.
-The values in these histograms allow us to calculate the sum of squares ratios and include the results in \autoref{fig:param_npeak_plot} as well.
-They are marked by an asterisk at the top right corner in \autoref{fig:param_npeak_plot}.
-The sum of squares ratios we obtained for \code{npeaks\_set = 5} and \code{npeaks\_set = c(5,3,1)} is slightly higher than those obtained from the histograms of @cmps. 
+@cmps present histograms of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for `npeaks_set = 5` and `npeaks_set = c(5, 3, 1)` with (presumably) Hamby 252.
+The values in these histograms allow us to calculate the sum of squares ratios and include the results in Figure \@ref(fig:param-npeak-plot) as well.
+They are marked by an asterisk at the top right corner in Figure \@ref(fig:param-npeak-plot).
+The sum of squares ratios we obtained for `npeaks_set = 5` and `npeaks_set = c(5, 3, 1)` is slightly higher than those obtained from the histograms of @cmps. 
 It's curious to see that for the Hamby 252 results published in @cmps the $\mathrm{{CMPS}_{max}}$ metric achieves values of the sum of squares ratio higher than those achieved by the $\mathrm{\overline{CMPS}_{max}}$ metric.
@@
 
-In \autoref{fig:param_npeak_plot}, we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
+In Figure \@ref(fig:param-npeak-plot), we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
 The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package \pkg{bulletxtrctr} [@bulletxtrctr].
-Similarly to the CMPS algorithm, this random forest model produces a  score to quantify the similarity of a land-by-land comparison.
+Similar to the CMPS algorithm, this random forest model produces a  score to quantify the similarity of a land-by-land comparison.
 The RF scores lie in an interval of [0,1] making them most comparable to the scaled CMPS scores.
 We applied the logic of $\mathrm{{CMPS}_{max}}$, $\mathrm{\overline{CMPS}_{max}}$, and $\mathrm{\overline{CMPS}_{diff}}$ to the random forest scores and obtained results of the random forest model for different metrics.
-As shown in \autoref{fig:param_npeak_plot}, the random forest model does not achieve the sum of squares ratio as high as those achieved by the top CMPS algorithms for Hamby 252, but it does achieve better results for Hamby 44.
-This might suggest that an inclusion of the CMPS score as an additional feature in the random forest model training might be beneficial for an overall separation to determine source.
-
-For details about the implementation, examples and results, please refer to the "Supplementary materials".
+As shown in Figure \@ref(fig:param-npeak-plot), the random forest model does not achieve the sum of squares ratio as high as those achieved by the top CMPS algorithms for Hamby 252, but it does achieve better results for Hamby 44.
+This might suggest that inclusion of the CMPS score as an additional feature in the random forest model training might be beneficial for an overall separation to determine the source.
+
+For details about the implementation, examples, and results, please refer to the "Supplementary materials".
 
@@
 
-In this paper we present the \pkg{cmpsR} package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
+In this paper, we present the \pkg{cmpsR} package, an open-source implementation of the Congruent Matching Profile Segments (CMPS) algorithm [@cmps], and apply it to two datasets in Hamby study [@hamby] to show its potential for further research.
 The CMPS algorithm was proposed by NIST in 2019 and was made for objective tool marks comparisons.
-We introduce the basic logic of the CMPS algorithm and lay out its implementation in the \pkg{cmpsR} package.
+We introduce the basic logic of the CMPS algorithm and layout its implementation in the \pkg{cmpsR} package.
 We also showcase the functionality of the \pkg{cmpsR} package with a small dataset example that is included in the package.
@@
 We also introduce a principled evaluation framework of algorithmic results using  a measure based on the sum of squares ratio. 
-We showcase the implementation with two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
-<!-- Additionally, we apply the \pkg{cmpsR} package to two datasets in Hamby study (Hamby set 252 and Hamby set 44).  -->
+We showcase the implementation with two datasets in the Hamby study (Hamby set 252 and Hamby set 44) and compare the CMPS algorithm using different sets of parameters and different metrics, following the evaluation framework based on the sum of squares ratio.
 The results obtained are promising:  we were both able to reproduce the results in @cmps qualitatively and achieve a clear separation between the known match (KM) comparisons and known non-match (KNM) comparisons in another bullet study.
-However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings vary between different datasets.
+However, the comparisons among different sets of parameters suggest that the optimal choice for parameter settings varies between different datasets.
 
@@
 The difference in parameter settings for optimal differentiation between same-source comparisons and different-source comparisons is therefore quite surprising.
-As next steps we need validation studies, similar to @vanderplas - trying out the CMPS algorithm on firearms and ammunition combinations that are different to test the limits of the algorithm.
+In the next steps, we need validation studies similar to @vanderplas - trying out the CMPS algorithm on different firearms and ammunition combinations to test the limits of the algorithm.
 The evaluation framework we proposed based on the sum of squares ratio will facilitate such studies and other validation of the algorithm.
@@
 
-The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards in the framework of open science.
+The open-source implementation of the CMPS algorithm provided by the \pkg{cmpsR} package is just one step towards to the framework of open science.
 Open science is particularly important to fields like forensic science where transparency and accuracy are critical to fair justice.

### 2022-04-12 rj_format/rj-format-ju-hofmann/ju-hofmann.tex
change to rjtools

--- 2022-03-31 submissions/resubmission-ju-hofmann2/ju-hofmann.tex
@@
 
-\newcommand{\hh}[1]{{\textcolor{orange}{#1}}}
-\newcommand{\wj}[1]{{\textcolor{blue}{#1}}}
-\setlength{\parindent}{0pt}
-
 \hypertarget{introduction}{%
@@
 
-In this paper we present an open-source implementation of the algorithm
+In this paper, we present an open-source implementation of the algorithm
 of the Congruent Matching Profile Segments (CMPS) method. \citet{cmps}
@@
 review, and improve. Our implementation is made available as part of the
-\texttt{R} package \pkg{cmpsR} on CRAN.
-
-According to the Uniform Crime Reporting Program of FBI (Federal Bureau
-of Investigation), ``more than 76 percent (76.7) of the homicides for
-which the FBI received weapons data in 2020 involved the use of
+\texttt{R} package \CRANpkg{cmpsR} on CRAN.
+
+According to the Uniform Crime Reporting Program of the FBI (Federal
+Bureau of Investigation), ``more than 76 percent (76.7) of the homicides
+for which the FBI received weapons data in 2020 involved the use of
 firearms'' \citep{fbiucr}. At the same time, the number of murder
@@
 two bullets is based on a comparison of striation marks acquired during
-the firing process as bullets are propelled through the barrel. Current
-state of art sees firearms examiners make an assessment of similarity
-based on a visual comparison, generally, using a comparison microscope
-\citep{afte}. This practice has been criticized for its lack of
-objectivity and the associated problem of determining valid error rates
-\citep{pcast}.
+the firing process as bullets are propelled through the barrel. The
+current state of art sees firearms examiners make an assessment of
+similarity based on a visual comparison, generally, using a comparison
+microscope \citep{afte}. This practice has been criticized for its lack
+of objectivity and the associated problem of determining valid error
+rates \citep{pcast}.
 
@@
 algorithms. These scans played an important role in bringing objectivity
-into the field. In the following sections we will: review the background
-of bullet signature comparisons, discuss how we followed the idea
-described by \citet{cmps} for the implementation of the CMPS algorithm,
-propose new metrics based on the CMPS score and a principled evaluation
-framework for algorithmic results comparison, and present results of
-applying our implementation to real data.
+into the field. In the following sections, we will: review the
+background of bullet signature comparisons, discuss how we followed the
+idea described by \citet{cmps} for the implementation of the CMPS
+algorithm, propose new metrics based on the CMPS score and a principled
+evaluation framework for algorithmic results comparison, and present
+results of applying our implementation to real data.
 
@@
 The Ruger P-85 barrels are traditionally rifled barrels with six grooves
-and lands as shown in \autoref{fig:bullet}. During the firing process,
-grooves and lands are engraved on a bullet. Firearms examiners use
-striation marks on land engraved areas (LEAs) for their visual
+and lands as shown in Figure \ref{fig:bullet}. During the firing
+process, grooves and lands are engraved on a bullet. Firearms examiners
+use striation marks on land engraved areas (LEAs) for their visual
 comparison. For algorithmic purposes, 3D topographical images of land
@@
 this paper was proposed by \citet{aoas} and is implemented in the
-\texttt{R} packages \pkg{x3ptools} \citep{x3ptools} and
+\texttt{R} packages \CRANpkg{x3ptools} \citep{x3ptools} and
 \pkg{bulletxtrctr} \citep{bulletxtrctr}. \pkg{x3ptools} is a package to
@@
 
-\autoref{fig:process} gives an overview of all of the steps in the
-process from scan to signatures. \autoref{fig:process}(a) shows a
+Figure \ref{fig:process} gives an overview of all of the steps in the
+process from scan to signatures. Figure \ref{fig:process}(a) shows a
 rendering of a 3D scan of a bullet land engraved area. The raised
@@
 step of obtaining the bullet signature is to extract a cross-section at
-a fixed height along the land engraving.
-
-The thin white horizontal line in \autoref{fig:process}(a) indicates
+a fixed height on the land engraving.
+
+The thin white horizontal line in Figure \ref{fig:process}(a) indicates
 which cross-section was identified by the algorithm to represent the
-LEA; \autoref{fig:process}(b) shows the corresponding cross-sectional
+LEA; Figure \ref{fig:process}(b) shows the corresponding cross-sectional
 view. Groove engraved areas are removed from the analysis as indicated
-by the vertical blue lines in \autoref{fig:process}(c) and
-\autoref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess}
-is fitted to capture the bullet curvature (\autoref{fig:process}(e))
-and, finally, the \textbf{bullet signature} (\autoref{fig:process}(f))
-is obtained as residuals of the cross-section and the fitted smooth.
-Note, that in \citet{cmps} bullet signatures are referred to as bullet
-profiles. However, to avoid confusion, we distinguish the notion of
-bullet signatures from bullet profiles. Bullet profiles are shown in
-panels (b), (c), and (d) of \autoref{fig:process}, while
-\autoref{fig:process}(f) shows the corresponding bullet signature.
-Identifying the groove engraved areas correctly is fundamental for a
-correct down-stream analysis of the signatures. To allow for a
-human-in-the middle inspection and intervention we have provided an
-interactive web-application, implemented as \texttt{R} Shiny App
-\citep{shiny}, \pkg{bulletinspectR} to identify and correct those
-errors. An example of the extraction process with corresponding code and
-parameter settings can be found in the ``Supplementary materials''. Note
-that the process of extracting signatures might be different from the
-one used in \citet{cmps} because no code or parameter settings are made
-available publicly.
+by the vertical blue lines in Figure \ref{fig:process}(c) and Figure
+\ref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess} is
+fitted to capture the bullet curvature ( Figure \ref{fig:process}(e))
+and, finally, the \textbf{bullet signature} (Figure
+\ref{fig:process}(f)) is obtained as residuals of the cross-section and
+the fitted smooth. Note, that in \citet{cmps} bullet signatures are
+referred to as bullet profiles. However, to avoid confusion, we
+distinguish the notion of bullet signatures from bullet profiles. Bullet
+profiles are shown in panels (b), (c), and (d) of Figure
+\ref{fig:process}, while Figure \ref{fig:process}(f) shows the
+corresponding bullet signature. Identifying the groove engraved areas
+correctly is fundamental for a correct downstream analysis of the
+signatures. To allow for a human-in-the-middle inspection and
+intervention we have provided an interactive web application,
+implemented as \texttt{R} Shiny App \citep{shiny}, \pkg{bulletinspectR}
+to identify and correct those errors. An example of the extraction
+process with corresponding code and parameter settings can be found in
+the ``Supplementary materials''. Note that the process of extracting
+signatures might be different from the one used in \citet{cmps} because
+no code or parameter settings are made available publicly.
 
@@
 (b) view of the cross-section of the land engraved area at the white line in (a).
-(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of left and right grooves.
+(c) the crosscut data plotted in 2D; blue vertical lines indicate the position of the left and right grooves.
 (d) the crosscut data after chopping the left and right grooves.
 (e) the fitted curvature using LOESS.
-(f) after removing the curvature from the crosscut data, the bullet signature is obtained}\label{fig:process}
+(f) after removing the curvature from the crosscut data, the bullet signature is obtained.}\label{fig:process}
 \end{figure}
@@
 
-In this example, the comparison between \code{sig1} and \code{sig2}, two
-signatures coming from the same source (a known-match comparison), gets
-a CMPS score of 17; the comparison between \code{sig1} and \code{sig3},
-two signatures coming from different sources (a known non-match
-comparison), gets a CMPS score of 1.
+In this example, the comparison between \texttt{sig1} and \texttt{sig2},
+two signatures coming from the same source (a known-match comparison),
+gets a CMPS score of 17; the comparison between \texttt{sig1} and
+\texttt{sig3}, two signatures coming from different sources (a known
+non-match comparison), gets a CMPS score of 1.
 
@@
 the main points is also included. In the section on 'Evaluation
-metrics'' we introduce new CMPS metrics that summarize land-level CMPS
+metrics'', we introduce new CMPS metrics that summarize land-level CMPS
 scores and a sum of squares ratio that can be used to evaluate
@@
 \item
-  \textbf{cut the comparison signature into consecutive, non-overlapping
-  and equal-length basis segments:} The command
-  \code{get\_segs(x, len=50)} implements this step: it takes bullet
-  signature \code{x} in the format of a numeric vector and cuts it into
-  consecutive, non-overlapping and equal-length segments of length
-  \code{len}, which are referred to as ``basis segments''. Note that the
-  parameter \code{len} determines the length of a basis segment and thus
-  affects the total number of basis segments, which is the upper limit
-  of the CMPS score of a comparison. The default value of \code{len} is
-  50, which will result in about 25 basis segments for the example data
-  of the package.
+  \textbf{cut the comparison signature into consecutive,
+  non-overlapping, and equal-length basis segments:} The command
+  \texttt{get\_segs(x,\ len=50)} implements this step: it takes bullet
+  signature \texttt{x} in the format of a numeric vector and cuts it
+  into consecutive, non-overlapping and equal-length segments of length
+  \texttt{len}, which are referred to as ``basis segments''. Note that
+  the parameter \texttt{len} determines the length of a basis segment
+  and thus affects the total number of basis segments, which is the
+  upper limit of the CMPS score of a comparison. The default value of
+  \texttt{len} is 50, which will result in about 25 basis segments for
+  the example data of the package.
 \item
@@
   identified based on the segment's similarity to the reference
-  signature. In a first step, the cross-correlation function of the
+  signature. In the first step, the cross-correlation function of the
   segment to the reference is calculated, then a number of positions
@@
   repeated. Only when candidate positions coincide (or are similar
-  enough), they are considered further. \autoref{fig:segplots} and
-  \autoref{fig:seg_all} illustrate these ideas.
+  enough), they are considered further. Figure \ref{fig:segplots} and
+  Figure \ref{fig:segall} illustrate these ideas.
 
@@
     \textbf{Calculate the cross-correlation curve:} Calculate the
-    cross-correlation curve between a basis segment \code{x} and the
-    reference signature \code{y} using the function
-    \code{get\_ccf4(x, y, ...)} as shown in \autoref{fig:segplot2}. The
-    position indicates the lag by which a basis segment is moved with
-    respect to its original placement. A position is considered ``good''
-    if it results in a peak in the cross-correlation between the basis
-    segment and the reference.
+    cross-correlation curve between a basis segment \texttt{x} and the
+    reference signature \texttt{y} using the function
+    \texttt{get\_ccf4(x,\ y,\ ...)} as shown in Figure
+    \ref{fig:segplot2}. The position indicates the lag by which a basis
+    segment is moved with respect to its original placement. A position
+    is considered ``good'' if it results in a peak in the
+    cross-correlation between the basis segment and the reference.
   \item
@@
     of correlation peaks as candidate positions. The latter is also
-    called ``multi-segment lengths strategy''. The parameter
-    \code{npeaks\_set} in \code{extract\_feature\_cmps(...)} determines
-    which strategy to use and the number of candidate positions:
+    called the ``multi-segment lengths strategy''. The parameter
+    \texttt{npeaks\_set} in \texttt{extract\_feature\_cmps(...)}
+    determines which strategy to use and the number of candidate
+    positions:
 
@@
     \item
-      If \code{npeaks\_set} is an integer vector of length 1, for
-      example \code{npeaks\_set = 5}, the positions of the top five
+      If \texttt{npeaks\_set} is an integer vector of length 1, for
+      example, \texttt{npeaks\_set\ =\ 5}, the positions of the top five
       peaks in the cross-correlation curve are identified as candidate
@@
     \item
-      If \code{npeaks\_set} is an integer vector of length more than 1,
-      for example \code{npeaks\_set = c(5, 3, 1)}, the multi-segment
-      lengths strategy will be used: calculate the cross-correlation
-      function between a basis segment and the reference and identify
-      positions of the top five peaks; double the segment length to a
-      specified value, re-calculate the cross-correlation function, and
-      identify three peaks; repeat this process and identify a single
-      peak in the newly computed cross-correlation function.
-      \autoref{fig:seg_all} shows an example of three levels of basis
-      segment 6 and their corresponding cross-correlation curves and
-      identified peaks. Note that in \citet{cmps} the segment length is
-      doubled at each level of a basis segment, but in the present
-      implementation users are allowed to choose the segment length at
-      each level.
-    \item
-      \code{get\_ccr\_peaks(comp, segments, seg\_outlength, nseg = 1, npeaks = 5)}
+      If \texttt{npeaks\_set} is an integer vector of length more than
+      1, for example, \texttt{npeaks\_set\ =\ c(5,\ 3,\ 1)}, the
+      multi-segment lengths strategy will be used: calculate the
+      cross-correlation function between a basis segment and the
+      reference and identify positions of the top five peaks; double the
+      segment length to a specified value, re-calculate the
+      cross-correlation function, and identify three peaks; repeat this
+      process and identify a single peak in the newly computed
+      cross-correlation function. Figure \ref{fig:segall} shows an
+      example of three levels of basis segment 6 and their corresponding
+      cross-correlation curves and identified peaks. Note that in
+      \citet{cmps} the segment length is doubled at each level of a
+      basis segment, but in the present implementation users are allowed
+      to choose the segment length at each level.
+    \item
+      \texttt{get\_ccr\_peaks(comp,\ segments,\ seg\_outlength,\ nseg\ =\ 1,\ npeaks\ =\ 5)}
       computes the cross-correlation curve between a basis or increased
@@
       cross-correlation curve. The number of peaks detected is equal to
-      \code{npeaks}, which is an integer. \code{segments},
-      \code{seg\_outlength}, and \code{nseg} determines the segment in
-      the cross-correlation computation, and \code{comp} gives the
+      \texttt{npeaks}, which is an integer. \texttt{segments},
+      \texttt{seg\_outlength}, and \texttt{nseg} determine the segment
+      in the cross-correlation computation, and \texttt{comp} gives the
       reference signature. If the multi-segment lengths strategy is
-      used, then \code{get\_ccr\_peaks(...)} is called in a
-      \code{lapply()} for each level of the basis segment. The resulting
-      list is called \code{ccr\_list}.
+      used, then \texttt{get\_ccr\_peaks(...)} is called in a
+      \texttt{lapply()} for each level of the basis segment. The
+      resulting list is called \texttt{ccr\_list}.
     \end{itemize}
@@
     lengths strategy being used, a position is identified as a candidate
-    position for registration and is called as a ``consistent
-    correlation peak'' if it results in a top peak in the
-    cross-correlation curve with a tolerance zone determined by
-    \code{Tx} in all segment levels. Note that in \citet{cmps}, a
-    segment at its largest scale (highest level) always identifies one
-    peak, but we do not have this requirement in our implementation.
+    position for registration and is called a ``consistent correlation
+    peak'' if it results in a top peak in the cross-correlation curve
+    with a tolerance zone determined by \texttt{Tx} in all segment
+    levels. Note that in \citet{cmps}, a segment at its largest scale
+    (highest level) always identifies one peak, but we do not have this
+    requirement in our implementation.
 
@@
     \item
-      the function \code{get\_seg\_scale(segments, nseg, out\_length)}
-      is used to obtain the (potentially increased) version of a basis
-      segment. \code{segments}, which is a list containing all basis
-      segments generated by the function \code{get\_segs(...)} in step
-      1, and \code{nseg} are used to determine the basis segment to be
-      increased. \code{out\_length} specifies the length of the output
+      the function
+      \texttt{get\_seg\_scale(segments,\ nseg,\ out\_length)} is used to
+      obtain the (potentially increased) version of a basis segment.
+      \texttt{segments}, which is a list containing all basis segments
+      generated by the function \texttt{get\_segs(...)} in step 1, and
+      \texttt{nseg} are used to determine the basis segment to be
+      increased. \texttt{out\_length} specifies the length of the output
       segment.
     \item
-      \code{get\_ccp(ccr\_list, Tx = 25)} tries to identify the
-      ``consistent correlation peak''. \code{ccr\_list} is the result of
-      \code{lapply()} and \code{get\_ccr\_peaks(...)}, and \code{Tx}
-      determines the size of a tolerance zone used in identifying the
-      consistent correlation peak. \code{get\_ccp(...)} returns
-      \code{NULL} if there is no consistent correlation peak.
+      \texttt{get\_ccp(ccr\_list,\ Tx\ =\ 25)} tries to identify the
+      ``consistent correlation peak''. \texttt{ccr\_list} is the result
+      of \texttt{lapply()} and \texttt{get\_ccr\_peaks(...)}, and
+      \texttt{Tx} determines the size of a tolerance zone used in
+      identifying the consistent correlation peak.
+      \texttt{get\_ccp(...)} returns \texttt{NULL} if there is no
+      consistent correlation peak.
     \end{itemize}
@@
   position ``receives'' votes from basis segments that identify it or a
-  close position within a tolerance zone of \code{Tx} as a candidate
+  close position within a tolerance zone of \texttt{Tx} as a candidate
   position in step 2. Votes for all candidate positions are tallied, and
@@
   signature in terms of correlation at this registration position. In
-  case of ties the middle position is taken as the congruent
+  the case of ties, the middle position is taken as the congruent
   registration position. Basis segments with a congruent registration
@@
   The total number of CMPS is the CMPS score of the comparison.
-  \code{get\_CMPS(input\_ccp, Tx = 25)} is the function that tallies the
-  votes and determines the congruent registration position and congruent
-  matching profile segments (CMPS).
+  \texttt{get\_CMPS(input\_ccp,\ Tx\ =\ 25)} is the function that
+  tallies the votes and determines the congruent registration position
+  and congruent matching profile segments (CMPS).
 \end{enumerate}
@@
 affect the final results and are left to the users to decide, such as
-the length of basis segments \code{seg\_length} in step 1, the number of
-peaks \code{npeaks\_set} identified on each level in step 2, and the
-length of the tolerance zone \code{Tx} in both step 2 and 3. In our
-implementation of the CMPS algorithm we used the parameters given in the
-original CMPS paper \citep{cmps} as the default values for these
+the length of basis segments \texttt{seg\_length} in step 1, the number
+of peaks \texttt{npeaks\_set} identified on each level in step 2, and
+the length of the tolerance zone \texttt{Tx} in both step 2 and 3. In
+our implementation of the CMPS algorithm, we used the parameters given
+in the original CMPS paper \citep{cmps} as the default values for these
 parameters. However, the authors state that no cross-validation has been
-done - there might also be issues with respect to resolution of the
+done - there might also be issues with respect to the resolution of the
 scans. Further research is needed, until then users are advised to think
@@
 parameters. The main function that combines all steps in the CMPS
-algorithm described above is called \code{extract\_feature\_cmps(...)}.
-Here we present it with its default parameters.
+algorithm described above is called
+\texttt{extract\_feature\_cmps(...)}. Here we present it with its
+default parameters.
 
@@
 
-The function \code{extract\_feature\_cmps} allows for the following
+The function \texttt{extract\_feature\_cmps} allows for the following
 input from users besides the previously discussed parameters
-\code{seg\_length}, \code{npeaks\_set}, and \code{Tx}:
+\texttt{seg\_length}, \texttt{npeaks\_set}, and \texttt{Tx}:
 
@@
 \item
-  \code{x} and \code{y} are two signatures: \code{x} serves as the
+  \texttt{x} and \texttt{y} are two signatures: \texttt{x} serves as the
   comparison signature (which will be divided into basis segments) and
-  \code{y} is the reference signature;
-\item
-  \code{include} determines the format of the function result. Besides
-  the \code{CMPS\_score}, other aspects of the comparison help in
-  understanding how the \code{CMPS\_score} is computed. By default
-  \code{include} is set to \code{NULL} and only the \code{CMPS\_score}
-  is returned; further results are included when \code{include} is (an
-  abbreviation of) one of or a vector of the following strings:
-  \code{"nseg"}, \code{"congruent\_pos"}, \code{"congruent\_seg\_idx"},
-  \code{"segments"}, \code{"parameters"}, and \code{"full\_result"}. If
-  \code{include} is specified as \code{"full\_result"} (or its
+  \texttt{y} is the reference signature;
+\item
+  \texttt{include} determines the format of the function result. Besides
+  the \texttt{CMPS\_score}, other aspects of the comparison help in
+  understanding how the \texttt{CMPS\_score} is computed. By default
+  \texttt{include} is set to \texttt{NULL} and only the
+  \texttt{CMPS\_score} is returned; further results are included when
+  \texttt{include} is (an abbreviation of) one of or a vector of the
+  following strings: \texttt{"nseg"}, \texttt{"congruent\_pos"},
+  \texttt{"congruent\_seg\_idx"}, \texttt{"segments"},
+  \texttt{"parameters"}, and \texttt{"full\_result"}. If
+  \texttt{include} is specified as \texttt{"full\_result"} (or its
   abbreviation), the output includes everything listed below.
@@
   \item
-    \code{nseg}: the number of basis segments from the comparison
+    \texttt{nseg}: the number of basis segments from the comparison
     signature; this is also the highest possible CMPS score of the
@@
   \item
-    \code{congruent\_pos}: the congruent registration position;
-  \item
-    \code{congruent\_seg\_idx}: the indices of all congruent matching
+    \texttt{congruent\_pos}: the congruent registration position;
+  \item
+    \texttt{congruent\_seg\_idx}: the indices of all congruent matching
     profile segments;
   \item
-    \code{ccp\_list}: a list showing identified candidate positions of
+    \texttt{ccp\_list}: a list showing identified candidate positions of
     all basis segments;
   \item
-    \code{pos\_df}: a data frame containing all candidate positions and
-    their respective number of votes;
-  \item
-    \code{segments}: a list containing all basis segments;
-  \item
-    \code{parameters}: a list containing all input arguments of
-    \code{extract\_feature\_cmps};
+    \texttt{pos\_df}: a data frame containing all candidate positions
+    and their respective number of votes;
+  \item
+    \texttt{segments}: a list containing all basis segments;
+  \item
+    \texttt{parameters}: a list containing all input arguments of
+    \texttt{extract\_feature\_cmps};
   \end{itemize}
 \item
-  \code{outlength} specifies the segment length of a basis segment at
+  \texttt{outlength} specifies the segment length of a basis segment at
   each level under the multi-segment lengths strategy. By default
-  \code{outlength} is set to \code{NULL}, indicating that a basis
+  \texttt{outlength} is set to \texttt{NULL}, indicating that a basis
   segment should double its segment length at the next level and
@@
 
-In the remainder of the paper we showcase the use of the \pkg{cmpsR}
+In the remainder of the paper, we showcase the use of the \pkg{cmpsR}
 functionality on some examples and present the results of applying it to
@@
 
-\code{bullets\$sigs} is a list of twelve numeric vectors corresponding
-to the twelve bullet signatures shown in \autoref{fig:sigs}.
-\code{bullets\$source} contains the URLs to the corresponding x3p file
+\texttt{bullets\$sigs} is a list of twelve numeric vectors corresponding
+to the twelve bullet signatures shown in Figure \ref{fig:sigs}.
+\texttt{bullets\$source} contains the URLs to the corresponding x3p file
 containing the topographic scan from the NIST Ballistics Toolmark
@@
 The signatures of Land 4 of Bullet 1 and Land 5 of Bullet 2 are stored
-in objects \code{sigs2} and \code{sigs1}, respectively. This comparison
-consists of a pair of signatures that are known to be a match -- a KM
-(known match) comparison. We compute the CMPS score using two versions
-of the CMPS algorithm:
+in objects \texttt{sigs2} and \texttt{sigs1}, respectively. This
+comparison consists of a pair of signatures that are known to be a match
+-- a KM (known match) comparison. We compute the CMPS score using two
+versions of the CMPS algorithm:
 
@@
 
-In the first example, \code{npeaks\_set} is a vector of three integers,
-i.e.~the algorithm uses the multi-segment lengths strategy to create the
-result object \code{cmps\_with\_multi\_scale}. For
-\code{cmps\_without\_multi\_scale} each basis segment is linked to the
-top 5 candidate positions. We use \code{include = "full\_result"} to
+In the first example, \texttt{npeaks\_set} is a vector of three
+integers, i.e.~the algorithm uses the multi-segment lengths strategy to
+create the result object \texttt{cmps\_with\_multi\_scale}. For
+\texttt{cmps\_without\_multi\_scale} each basis segment is linked to the
+top 5 candidate positions. We use \texttt{include\ =\ "full\_result"} to
 capture all results. In this example, the CMPS is 9 when using multiple
@@
 of false positives when identifying candidate positions; however, any
-score based method is walking the line between false positives and false
+score-based method is walking the line between false positives and false
 negatives. As the number of false positives is reduced the number of
@@
 
-We also implemented graphing tools for visualizing results of the CMPS
-algorithm. The goal is to provide users with tools to inspect each of
-the basis segments and to help them have a better understanding of how
-the algorithm works. \autoref{fig:sigplots} shows the plots generated by
-the first graphing function, \code{cmps\_signature\_plot()}, and
-continues with the example above. \code{cmps\_signature\_plot()} takes
-the output of
-\code{extract\_feature\_cmps(..., include = "full\_result")} and returns
-a list of 5 elements. It creates an overall impression of how the
-comparison signature aligns with the reference signature at the
+We also implemented graphing tools for visualizing the results of the
+CMPS algorithm. The goal is to provide users with tools to inspect each
+of the basis segments and to help them have a better understanding of
+how the algorithm works. Figure \ref{fig:sigplots} shows the plots
+generated by the first graphing function,
+\texttt{cmps\_signature\_plot()}, and continues with the example above.
+\texttt{cmps\_signature\_plot()} takes the output of
+\texttt{extract\_feature\_cmps(...,\ include\ =\ "full\_result")} and
+returns a list of 5 elements. It creates an overall impression of how
+the comparison signature aligns with the reference signature at the
 congruent registration position.
@@
 \item
-  The first element is a plot called \code{segment\_shift\_plot}, shown
-  in \autoref{fig:sigplot}. On this plot the reference signature is
-  drawn as a black line, congruent matching profile segments from the
-  comparison signature are overlaid in red at the congruent registration
-  position.
-\item
-  The second plot is called \code{signature\_shift\_plot}, shown in
-  \autoref{fig:sigplot2}. This visual presents both the comparison
+  The first element is a plot called \texttt{segment\_shift\_plot},
+  shown in Figure \ref{fig:sigplot}. On this plot the reference
+  signature is drawn as a black line, congruent matching profile
+  segments from the comparison signature are overlaid in red at the
+  congruent registration position.
+\item
+  The second plot is called \texttt{signature\_shift\_plot}, shown in
+  Figure \ref{fig:sigplot2}. This visual presents both the comparison
   signature and the reference signature. The comparison signature is
@@
 \item
-  Other elements of this list are \code{seg\_shift} and
-  \code{sig\_shift}. \code{sig\_shift} gives the congruent registration
-  position, while \code{seg\_shift} is a data frame showing the
-  congruent matching profile segments and their identified candidate
-  position closest to the congruent registration position.
+  Other elements of this list are \texttt{seg\_shift} and
+  \texttt{sig\_shift}. \texttt{sig\_shift} gives the congruent
+  registration position, while \texttt{seg\_shift} is a data frame
+  showing the congruent matching profile segments and their identified
+  candidate position closest to the congruent registration position.
 \end{itemize}
@@
 
-While \code{cmps\_signature\_plot()} focuses on the signature level,
-\code{cmps\_segment\_plot()} focuses on the segment level. It provides
-the ``full result'' of \code{extract\_feature\_cmps()}, but also takes
-an argument, \code{seg\_idx}, indicating which segment should be
-inspected. When checking \code{sig\_plot\$seg\_shift} we notice that
+While \texttt{cmps\_signature\_plot()} focuses on the signature level,
+\texttt{cmps\_segment\_plot()} focuses on the segment level. It provides
+the ``full result'' of \texttt{extract\_feature\_cmps()}, but also takes
+an argument, \texttt{seg\_idx}, indicating which segment should be
+inspected. When checking \texttt{sig\_plot\$seg\_shift} we notice that
 segment number 6 is not one of the congruent matching profile segments.
-We can therefore set \code{seg\_idx = 6} in \code{cmps\_segment\_plot()}
-and investigate the reason why this segment disagrees with the congruent
-registration position.
-
-For each segment scale, we have two plots: \code{segment\_plot} and
-\code{scale\_ccf\_plot}, as shown in \autoref{fig:segplots} for the
+We can therefore set \texttt{seg\_idx\ =\ 6} in
+\texttt{cmps\_segment\_plot()} and investigate the reason why this
+segment disagrees with the congruent registration position.
+
+For each segment scale, we have two plots: \texttt{segment\_plot} and
+\texttt{scale\_ccf\_plot}, as shown in Figure \ref{fig:segplots} for the
 example of segment number 6:
@@
 \begin{itemize}
-\tightlist
-\item
-  \autoref{fig:segplot} is the \code{segment\_plot} for basis segment 6
-  at level one (in its original length). We used
-  \code{npeaks\_set = c(5, 3, 1)} in \code{extract\_feature\_cmps()}
-  when calculating the CMPS score. Therefore the top five peaks are
-  identified in the cross-correlation curve at level one. Segment 6 is
-  plotted at the positions where these 5 peaks are identified with
-  dashed lines in the \code{segment\_plot}. The solid thick black line
-  shows the segment at its original position (which in this example is
-  very close to the actual registration position).
-\item
-  \autoref{fig:segplot2} is the \code{scale\_ccf\_plot} of basis segment
-  6 at level one. It shows the cross-correlation curve computed by the
-  reference signature and the level-one basis segment 6. The five
+\item
+  Figure \ref{fig:segplot} is the \texttt{segment\_plot} for basis
+  segment 6 at level one (in its original length). We used
+  \texttt{npeaks\_set\ =\ c(5,\ 3,\ 1)} in
+  \texttt{extract\_feature\_cmps()} when calculating the CMPS score.
+  Therefore the top five peaks are identified in the cross-correlation
+  curve at level one. Segment 6 is plotted at the positions where these
+  5 peaks are identified with dashed lines in the
+  \texttt{segment\_plot}. The solid thick black line shows the segment
+  at its original position (which in this example is very close to the
+  actual registration position).
+\item
+  Figure \ref{fig:segplot2} is the \texttt{scale\_ccf\_plot} of basis
+  segment 6 at level one. It shows the cross-correlation curve computed
+  by the reference signature and the level-one basis segment 6. The five
   highest peaks are marked by dots on the curve.
@@
 Additionally, users can have more insights about why segment 6 is not a
-congruent matching profile segment if we put the \code{segment\_plot}
-and \code{scale\_ccf\_plot} of all three segment levels together, as
-shown in \autoref{fig:seg_all} with the help of
-\code{ggpubr::ggarrange()}.
+congruent matching profile segment if we put the \texttt{segment\_plot}
+and \texttt{scale\_ccf\_plot} of all three segment levels together, as
+shown in Figure \ref{fig:segall} with the help of
+\texttt{ggpubr::ggarrange()}.
 
@@
 \end{adjustbox}
-\caption{\label{fig:seg_all} Put segment\_plot and scale\_ccf\_plot of all three levels together.
-We are identifying five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1).
+\caption{\label{fig:segall} Put segment\_plot and scale\_ccf\_plot of all three levels together.
+We are identifying the five highest peaks at level one, three peaks at level two, and one peak at level three since npeaks\_set = c(5, 3, 1).
 The highest peak position at level three is marked by the green dashed line across all segment levels.
@@
 
-In \autoref{fig:seg_all}, the red vertical dashed line indicates the
+In Figure \ref{fig:segall}, the red vertical dashed line indicates the
 congruent registration position. We can see that the basis segment 6
@@
 position) is identified at level two and three by increasing the segment
-length, which justifies the usage of multi-segment lengths strategy.
+length, which justifies the usage of the multi-segment lengths strategy.
 
@@
 engraved areas. Here, we are working with bullets fired from Ruger P85
-barrels with six lands and grooves. A comparison of two bullets
-therefore involves 36 land-to-land comparisons, resulting in 36 CMPS
-scores (as shown in \autoref{fig:tiles}). In order to obtain a single
+barrels with six lands and grooves. A comparison of two bullets,
+therefore, involves 36 land-to-land comparisons, resulting in 36 CMPS
+scores (as shown in Figure \ref{fig:tiles}). In order to obtain a single
 similarity score of a bullet-level comparison, we need to summarize
@@
 , where \texttt{mod} denotes the modulo operation. For example,
-\(\mathcal{P}_1 = \{ (1,2), (2,3), (3,4), (4,5), (5,6), (6,1) \}\) when
-\(n = 6\). Let \(k^*\) denote the index of the highest phase.
+\(\mathcal{P}_1 = \{ \left(1,2\right), \left(2,3\right), \left(3,4\right), \left(4,5\right), \left(5,6\right), \left(6,1\right) \}\)
+when \(n = 6\). Let \(k^*\) denote the index of the highest phase.
 
@@
 We can continue with the example used in previous sections.
-\code{bullets} contains bullet signatures of two bullets, \code{bullet1}
-and \code{bullet2}. As mentioned before, each bullet has 6 land
-engravings, resulting in 6 bullet signatures. Thus, there are 36
-pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\) values
-in total. We use multi-segment lengths strategy with default parameters
-to compute these CMPS scores, and the result is shown in
-\autoref{fig:tiles}. We can see that in this example,
+\texttt{bullets} contains bullet signatures of two bullets,
+\texttt{bullet1} and \texttt{bullet2}. As mentioned before, each bullet
+has 6 land engravings, resulting in 6 bullet signatures. Thus, there are
+36 pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\)
+values in total. We use multi-segment lengths strategy with default
+parameters to compute these CMPS scores, and the result is shown in
+Figure \ref{fig:tiles}. We can see that in this example,
 
@@
 score (the total number of basis segments) might differ across
-comparisons (as shown in \autoref{fig:tiles2}(a)) due to different
+comparisons (as shown in Figure \ref{fig:tiles2}(a)) due to different
 lengths of bullet signatures and different lengths of basis segments
@@
 
-The scaled CMPS scores of the above example are shown in
-\autoref{fig:tiles2}(b). Compared to the original CMPS scores, scaled
-scores have values within the interval \([0, 1]\) regardless of the
-length of the basis segments and therefore make a comparison of values
-possible across different parameter choices. Similarly to the original
-CMPS scores, we will denote the scaled CMPS scores adjusted for
-out-of-phase background values by \(\mathrm{\overline{CMPS^*}_{diff}}\).
-For example, \(\mathrm{\overline{CMPS^*}_{diff}} = 0.498\) for
-\autoref{fig:tiles2}(b)
+The scaled CMPS scores of the above example are shown in Figure
+\ref{fig:tiles2}(b). Compared to the original CMPS scores, scaled scores
+have values within the interval \([0, 1]\) regardless of the length of
+the basis segments and therefore make a comparison of values possible
+across different parameter choices. Similar to the original CMPS scores,
+we will denote the scaled CMPS scores adjusted for out-of-phase
+background values by \(\mathrm{\overline{CMPS^*}_{diff}}\). For example,
+\(\mathrm{\overline{CMPS^*}_{diff}} = 0.498\) for Figure
+\ref{fig:tiles2}(b)
 
@@
 sum of squares ratio to compare the CMPS metrics introduced earlier and
-investigate effects of different parameter settings.
+investigate the effects of different parameter settings.
 
@@
 
-\autoref{fig:result1_252} shows the distribution of
+Figure \ref{fig:result1-252} shows the distribution of
 \(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\) after we
@@
 lengths strategy. The parameters we used in
-\code{extract\_feature\_cmps} for the CMPS algorithm are:
+\texttt{extract\_feature\_cmps} for the CMPS algorithm are:
 
@@
 as those presented in \citet{cmps} since we were not able to follow
-their framework, but the results presented in \autoref{fig:result1_252}
-are qualitatively equivalent to those presented in \citet{cmps}, showing
-a clear separation between scores based on comparisons from known
-matches (KM) and scores from comparisons of known non-matches (KNM) for
-both \(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\).
+their framework, but the results presented in Figure
+\ref{fig:result1-252} are qualitatively equivalent to those presented in
+\citet{cmps}, showing a clear separation between scores based on
+comparisons from known matches (KM) and scores from comparisons of known
+non-matches (KNM) for both \(\mathrm{CMPS_{max}}\) and
+\(\mathrm{\overline{CMPS}_{max}}\).
 
 Additionally, to mimic the parameters used in \citet{cmps}, we set
-\code{seg\_length = 50} and \code{Tx = 25} to make sure that each basis
-segment has length of 78.125 \textmu m and the tolerance zone is
-\(\pm 39.0625\) \textmu m (one unit represents 1.5625 \textmu m for
-Hamby set 252).
+\texttt{seg\_length\ =\ 50} and \texttt{Tx\ =\ 25} to make sure that
+each basis segment has a length of 78.125 \textmu m and the tolerance
+zone is \(\pm 39.0625\) \textmu m (one unit represents 1.5625 \textmu m
+for Hamby set 252).
 
@@
 
-{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/result1_252-1}
-
-}
-
-\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; \texttt{seg\_length = 50}, \texttt{Tx = 25}, \texttt{npeaks\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars }\label{fig:result1_252}
+{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/result1-252-1}
+
+}
+
+\caption[Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252]{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 252; outliers are removed in bullet signatures; seg\_length = 50, Tx = 25, npeaks\_set = c(5,3,1); instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars.
+}\label{fig:result1-252}
 \end{figure}
@@
 
-Similar procedures are applied to Hamby set 44, and
-\autoref{fig:result1_44} shows the distribution of
-\(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\),
-respectively. The parameters used in \code{extract\_feature\_cmps} are:
+Similar procedures are applied to Hamby set 44, and Figure
+\ref{fig:result1-44} shows the distribution of \(\mathrm{CMPS_{max}}\)
+and \(\mathrm{\overline{CMPS}_{max}}\), respectively. The parameters
+used in \texttt{extract\_feature\_cmps} are:
 
@@
 Since the resolution of Hamby 44 is set to 1.29 \textmu m per unit, we
-make \code{seg\_length = 61} and \code{Tx = 30} to ensure that the setup
-of Hamby set 44 is similar to that of Hamby set 252, resulting in basis
-segments of 78.69 \textmu m and the tolerance zone of \(\pm 38.7\)
-\textmu m.
-
-As shown in \autoref{fig:result1_44}, again, we are able to see a clear
-separation between the known match comparisons and the known non-match
-comparisons, even though the separation is relatively small compared
-with that of Hamby set 252, which is also indicated by the sum of
-squares ratios. For this specific set of parameters, the sum of squares
-ratios are 8.87 and 10.64 for \(\mathrm{CMPS_{max}}\) and
+make \texttt{seg\_length\ =\ 61} and \texttt{Tx\ =\ 30} to ensure that
+the setup of Hamby set 44 is similar to that of Hamby set 252, resulting
+in basis segments of 78.69 \textmu m and the tolerance zone of
+\(\pm 38.7\) \textmu m.
+
+As shown in Figure \ref{fig:result1-44}, again, we are able to see a
+clear separation between the known match comparisons and the known
+non-match comparisons, even though the separation is relatively small
+compared with that of Hamby set 252, which is also indicated by the sum
+of squares ratios. For this specific set of parameters, the sum of
+squares ratios are 8.87 and 10.64 for \(\mathrm{CMPS_{max}}\) and
 \(\mathrm{\overline{CMPS}_{max}}\), respectively. This might suggest
@@
 
-{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/result1_44-1}
-
-}
-
-\caption{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; \texttt{seg\_length = 61}, \texttt{Tx = 30}, \texttt{npeaks\_set = c(5,3,1)}; instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars }\label{fig:result1_44}
+{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/result1-44-1}
+
+}
+
+\caption[Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44]{Distribution of $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$ for Hamby 44; outliers are removed in bullet signatures; seg\_length = 61, Tx = 30, npeaks\_set = c(5,3,1); instead of showing the counts on the y-axis, we present the observed proportions conditioned on KM group and KNM group to enhance the visibility of the bars.
+}\label{fig:result1-44}
 \end{figure}
@@
 
-{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/param_seg_plot-1}
-
-}
-
-\caption{Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter \texttt{seg\_length}).
+{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/param-seg-plot-1}
+
+}
+
+\caption[Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter seg\_length)]{Comparison of results from the CMPS algorithm based on different basis segment lengths (parameter seg\_length).
 Only the $\mathrm{CMPS_{max}}$ metric suggests that the default values for the basis segment length result in the best separation.
-Better separation is achieved based on the modified CMPS metrics, inclusing the newly suggested ones.
-For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results}\label{fig:param_seg_plot}
+Better separation is achieved based on the modified CMPS metrics, including the newly suggested ones.
+For Hamby 252 these metrics agree on a segment length of 75, and a segment length of 122 for Hamby 44 yields better results.
+}\label{fig:param-seg-plot}
 \end{figure}
@@
 
-{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/param_npeak_plot-1}
+{\centering \includegraphics[width=400px]{ju-hofmann_files/figure-latex/param-npeak-plot-1}
 
@@
 Starred results compare CMPS performance with results published in the literature.
-Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but the random forest scores with the same logic.
-Since random forest scores lie within the interval $[0, 1]$, scaling the random forest scores will not change the results.}\label{fig:param_npeak_plot}
+Results for the random forest score are represented with circles because the metrics are computed not based on the CMPS scores, but on the random forest scores with the same logic.
+Since random forest scores lie within the interval $[0, 1]$, scaling the random forest scores will not change the results.}\label{fig:param-npeak-plot}
 \end{figure}
@@
 
-We investigated the effects of different sets of parameters at the
+We investigated the effects of different sets of parameters in the
 example of both Hamby sets 252 and 44. More specifically, we
@@
 implementation under various segment lengths (controlled by the
-parameter \code{seg\_length}). Specifically, we fixed the parameter
-\code{npeaks\_set} that controls the number of peaks at each segment
-level to be \code{npeaks\_set = c(5,3,1)} and modified the parameter
-\code{seg\_length}. \autoref{fig:param_seg_plot} shows that the default
-values of \code{seg\_length} for Hamby 252 and Hamby 44 (50 for Hamby
-252 and 61 for Hamby 44, which represent 78.125 \textmu m and 78.69
-\textmu m, respectively) result in high values of the sum of squares
-ratio, no matter which CMPS metrics are used for an evaluation. However,
-we also see, that for Hamby set 252 a basis segment length of 75 is a
-better choice than the default segment length; a basis segment length of
-122 results in a higher value of sum of squares ratio for Hamby 44.
-
-\autoref{fig:param_npeak_plot} shows results of the CMPS algorithm using
-different strategies for identifying peaks in the correlation structure
-between signatures. Basis segment length is fixed to the default level
-for this evaluation. As can be seen in \autoref{fig:param_npeak_plot},
-the default value of \code{npeaks\_set} (\code{npeaks\_set = c(5,3,1)})
-leads to promising results in terms of the sum of squares ratio;
-however, other choices of \code{npeaks\_set} match and exceed this sum
-of squares ratio value.
+parameter \texttt{seg\_length}). Specifically, we fixed the parameter
+\texttt{npeaks\_set} that controls the number of peaks at each segment
+level to be \texttt{npeaks\_set\ =\ c(5,\ 3,\ 1)} and modified the
+parameter \texttt{seg\_length}. Figure \ref{fig:param-seg-plot} shows
+that the default values of \texttt{seg\_length} for Hamby 252 and Hamby
+44 (50 for Hamby 252 and 61 for Hamby 44, which represent 78.125
+\textmu m and 78.69 \textmu m, respectively) result in high values of
+the sum of squares ratio, no matter which CMPS metrics are used for an
+evaluation. However, we also see, that for Hamby set 252 a basis segment
+length of 75 is a better choice than the default segment length; a basis
+segment length of 122 results in a higher value of the sum of squares
+ratio for Hamby 44.
+
+Figure \ref{fig:param-npeak-plot} shows the results of the CMPS
+algorithm using different strategies for identifying peaks in the
+correlation structure between signatures. Basis segment length is fixed
+to the default level for this evaluation. As can be seen in Figure
+\ref{fig:param-npeak-plot}, the default value of \texttt{npeaks\_set}
+(\texttt{npeaks\_set\ =\ c(5,\ 3,\ 1)}) leads to promising results in
+terms of the sum of squares ratio; however, other choices of
+\texttt{npeaks\_set} match and exceed this sum of squares ratio value.
 
@@
 
-What we can also observe in \autoref{fig:param_seg_plot} and
-\autoref{fig:param_npeak_plot} is that the values of the sum of squares
+What we can also observe in Figure \ref{fig:param-seg-plot} and Figure
+\ref{fig:param-npeak-plot} is that the values of the sum of squares
 ratio for Hamby 44 is lower than those for Hamby 252. This might be
@@
 
-The purpose of the results shown in \autoref{fig:param_seg_plot} and
-\autoref{fig:param_npeak_plot} is not to determine the ``best''
+The purpose of the results shown in Figure \ref{fig:param-seg-plot} and
+Figure \ref{fig:param-npeak-plot} is not to determine the ``best''
 parameters for the CMPS algorithm, but to show that the sum of squares
@@
 \citet{cmps} present histograms of \(\mathrm{CMPS_{max}}\) and
-\(\mathrm{\overline{CMPS}_{max}}\) for \code{npeaks\_set = 5} and
-\code{npeaks\_set = c(5,3,1)} with (presumably) Hamby 252. The values in
-these histograms allow us to calculate the sum of squares ratios and
-include the results in \autoref{fig:param_npeak_plot} as well. They are
-marked by an asterisk at the top right corner in
-\autoref{fig:param_npeak_plot}. The sum of squares ratios we obtained
-for \code{npeaks\_set = 5} and \code{npeaks\_set = c(5,3,1)} is slightly
-higher than those obtained from the histograms of \citet{cmps}. It's
-curious to see that for the Hamby 252 results published in \citet{cmps}
-the \(\mathrm{{CMPS}_{max}}\) metric achieves values of the sum of
-squares ratio higher than those achieved by the
+\(\mathrm{\overline{CMPS}_{max}}\) for \texttt{npeaks\_set\ =\ 5} and
+\texttt{npeaks\_set\ =\ c(5,\ 3,\ 1)} with (presumably) Hamby 252. The
+values in these histograms allow us to calculate the sum of squares
+ratios and include the results in Figure \ref{fig:param-npeak-plot} as
+well. They are marked by an asterisk at the top right corner in Figure
+\ref{fig:param-npeak-plot}. The sum of squares ratios we obtained for
+\texttt{npeaks\_set\ =\ 5} and \texttt{npeaks\_set\ =\ c(5,\ 3,\ 1)} is
+slightly higher than those obtained from the histograms of \citet{cmps}.
+It's curious to see that for the Hamby 252 results published in
+\citet{cmps} the \(\mathrm{{CMPS}_{max}}\) metric achieves values of the
+sum of squares ratio higher than those achieved by the
 \(\mathrm{\overline{CMPS}_{max}}\) metric.
@@
 
-In \autoref{fig:param_npeak_plot}, we also included the sum of squares
-ratios computed from the random forest scores \citep{aoas} for different
-metrics. The random forest model presented in \citet{aoas} was trained
-at the Center for Statistics and Applications in Forensic Evidence
-(CSAFE) and is publicly available in the R package \pkg{bulletxtrctr}
-\citep{bulletxtrctr}. Similarly to the CMPS algorithm, this random
-forest model produces a score to quantify the similarity of a
-land-by-land comparison. The RF scores lie in an interval of {[}0,1{]}
+In Figure \ref{fig:param-npeak-plot}, we also included the sum of
+squares ratios computed from the random forest scores \citep{aoas} for
+different metrics. The random forest model presented in \citet{aoas} was
+trained at the Center for Statistics and Applications in Forensic
+Evidence (CSAFE) and is publicly available in the R package
+\pkg{bulletxtrctr} \citep{bulletxtrctr}. Similar to the CMPS algorithm,
+this random forest model produces a score to quantify the similarity of
+a land-by-land comparison. The RF scores lie in an interval of {[}0,1{]}
 making them most comparable to the scaled CMPS scores. We applied the
@@
 obtained results of the random forest model for different metrics. As
-shown in \autoref{fig:param_npeak_plot}, the random forest model does
+shown in Figure \ref{fig:param-npeak-plot}, the random forest model does
 not achieve the sum of squares ratio as high as those achieved by the
 top CMPS algorithms for Hamby 252, but it does achieve better results
-for Hamby 44. This might suggest that an inclusion of the CMPS score as
-an additional feature in the random forest model training might be
-beneficial for an overall separation to determine source.
-
-For details about the implementation, examples and results, please refer
-to the ``Supplementary materials''.
+for Hamby 44. This might suggest that inclusion of the CMPS score as an
+additional feature in the random forest model training might be
+beneficial for an overall separation to determine the source.
+
+For details about the implementation, examples, and results, please
+refer to the ``Supplementary materials''.
 
@@
 
-In this paper we present the \pkg{cmpsR} package, an open-source
+In this paper, we present the \pkg{cmpsR} package, an open-source
 implementation of the Congruent Matching Profile Segments (CMPS)
@@
 marks comparisons. We introduce the basic logic of the CMPS algorithm
-and lay out its implementation in the \pkg{cmpsR} package. We also
+and layout its implementation in the \pkg{cmpsR} package. We also
 showcase the functionality of the \pkg{cmpsR} package with a small
@@
 based on the sum of squares ratio. We showcase the implementation with
-two datasets in Hamby study (Hamby set 252 and Hamby set 44) and compare
-the CMPS algorithm using different sets of parameters and different
-metrics, following the evaluation framework based on the sum of squares
-ratio. The results obtained are promising: we were both able to
-reproduce the results in \citet{cmps} qualitatively and achieve a clear
-separation between the known match (KM) comparisons and known non-match
-(KNM) comparisons in another bullet study. However, the comparisons
-among different sets of parameters suggest that the optimal choice for
-parameter settings vary between different datasets.
+two datasets in the Hamby study (Hamby set 252 and Hamby set 44) and
+compare the CMPS algorithm using different sets of parameters and
+different metrics, following the evaluation framework based on the sum
+of squares ratio. The results obtained are promising: we were both able
+to reproduce the results in \citet{cmps} qualitatively and achieve a
+clear separation between the known match (KM) comparisons and known
+non-match (KNM) comparisons in another bullet study. However, the
+comparisons among different sets of parameters suggest that the optimal
+choice for parameter settings varies between different datasets.
 
@@
 optimal differentiation between same-source comparisons and
-different-source comparisons is therefore quite surprising. As next
-steps we need validation studies, similar to \citet{vanderplas} - trying
-out the CMPS algorithm on firearms and ammunition combinations that are
-different to test the limits of the algorithm. The evaluation framework
-we proposed based on the sum of squares ratio will facilitate such
-studies and other validation of the algorithm.
+different-source comparisons is therefore quite surprising. In the next
+steps, we need validation studies similar to \citet{vanderplas} - trying
+out the CMPS algorithm on different firearms and ammunition combinations
+to test the limits of the algorithm. The evaluation framework we
+proposed based on the sum of squares ratio will facilitate such studies
+and other validation of the algorithm.
 
@@
 The open-source implementation of the CMPS algorithm provided by the
-\pkg{cmpsR} package is just one step towards in the framework of open
+\pkg{cmpsR} package is just one step towards to the framework of open
 science. Open science is particularly important to fields like forensic

### 2022-04-12 rj_format/rjarticle/ju-hofmann.tex
change to rjtools

% !TeX root = RJwrapper.tex
\title{ToOoOlTiPs: An R Package for Customizable Tooltips in Interactive
Graphics}
\author{by Quietest Quokka and Bounciest Bilby}

\maketitle

\abstract{%
An abstract of less than 150 words.
}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Interactive data graphics provides plots that allow users to interact
them. One of the most basic types of interaction is through tooltips,
where users are provided additional information about elements in the
plot by moving the cursor over the plot.

This paper will first review some R packages on interactive graphics and
their tooltip implementations. A new package \CRANpkg{ToOoOlTiPs} that
provides customized tooltips for plot, is introduced. Some example plots
will then be given to showcase how these tooltips help users to better
read the graphics.

\hypertarget{background}{%
\section{Background}\label{background}}

Some packages on interactive graphics include \CRANpkg{plotly}
\citep{plotly} that interfaces with Javascript for web-based interactive
graphics, \CRANpkg{crosstalk} \citep{crosstalk} that specializes
cross-linking elements across individual graphics. The recent R Journal
paper \CRANpkg{tsibbletalk} \citep{RJ-2021-050} provides a good example
of including interactive graphics into an article for the journal. It
has both a set of linked plots, and also an animated gif example,
illustrating linking between time series plots and feature summaries.

\hypertarget{customizing-tooltip-design-with}{%
\section{\texorpdfstring{Customizing tooltip design with
\pkg{ToOoOlTiPs}}{Customizing tooltip design with }}\label{customizing-tooltip-design-with}}

\pkg{ToOoOlTiPs} is a packages for customizing tooltips in interactive
graphics, it features these possibilities.

\hypertarget{a-gallery-of-tooltips-examples}{%
\section{A gallery of tooltips
examples}\label{a-gallery-of-tooltips-examples}}

The \CRANpkg{palmerpenguins} data \citep{palmerpenguins} features three
penguin species which has a lovely illustration by Alison Horst in
Figure \ref{fig:penguins-alison}.

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth,height=0.3\textheight]{penguins} \caption[Artwork by \@allison\_horst]{Artwork by \@allison\_horst}\label{fig:penguins-alison}
\end{figure}
\end{Schunk}

Table \ref{tab:penguins-tab-static} prints at the first few rows of the
\texttt{penguins} data:

\begin{Schunk}
\begin{table}

\caption{\label{tab:penguins-tab-static}A basic table}
\centering
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{l|l|r|r|r|r|l|r}
\hline
species & island & bill\_length\_mm & bill\_depth\_mm & flipper\_length\_mm & body\_mass\_g & sex & year\\
\hline
Adelie & Torgersen & 39.1 & 18.7 & 181 & 3750 & male & 2007\\
\hline
Adelie & Torgersen & 39.5 & 17.4 & 186 & 3800 & female & 2007\\
\hline
Adelie & Torgersen & 40.3 & 18.0 & 195 & 3250 & female & 2007\\
\hline
Adelie & Torgersen & NA & NA & NA & NA & NA & 2007\\
\hline
Adelie & Torgersen & 36.7 & 19.3 & 193 & 3450 & female & 2007\\
\hline
Adelie & Torgersen & 39.3 & 20.6 & 190 & 3650 & male & 2007\\
\hline
\end{tabular}
\end{table}

\end{Schunk}

Figure \ref{fig:penguins-ggplot} shows an plot of the penguins data,
made using the \CRANpkg{ggplot2} package.

\begin{Schunk}
\begin{Sinput}
penguins %>% 
  ggplot(aes(x = bill_depth_mm, y = bill_length_mm, 
             color = species)) + 
  geom_point()
\end{Sinput}
\begin{figure}
\includegraphics{ju-hofmann_files/figure-latex/penguins-ggplot-1} \caption[A basic non-interactive plot made with the ggplot2 package on palmer penguin data]{A basic non-interactive plot made with the ggplot2 package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. Visit the online article to access the interactive version made with the plotly package.}\label{fig:penguins-ggplot}
\end{figure}
\end{Schunk}

\hypertarget{summary}{%
\section{Summary}\label{summary}}

We have displayed various tooltips that are available in the package
\pkg{ToOoOlTiPs}.

\bibliography{RJreferences.bib}

\address{%
Quietest Quokka\\
University of Little Mates\\%
Department of Letter Q\\ Somewhere, Australia\\
%
\url{https://www.britannica.com/animal/quokka}\\%
\textit{ORCiD: \href{https://orcid.org/0000-1721-1511-1101}{0000-1721-1511-1101}}\\%
\href{mailto:qquo@ulm.edu}{\nolinkurl{qquo@ulm.edu}}%
}

\address{%
Bounciest Bilby\\
University of Little Mates\\%
Department of Letter B\\ Somewhere, Australia\\
%
\url{https://www.britannica.com/animal/bilby}\\%
\textit{ORCiD: \href{https://orcid.org/0000-0002-0912-0225}{0000-0002-0912-0225}}\\%
\href{mailto:bbil@ulm.edu}{\nolinkurl{bbil@ulm.edu}}%
}

### 2022-04-12 rj_format/rj-format-ju-hofmann/ju-hofmann.R

@@ -1,0 +1,948 @@
+# Generated by `rjournal_article()` using `knitr::purl()`: do not edit by hand
+# Please edit ju-hofmann.Rmd to modify this file
+
+## ----setup, echo=FALSE, message=FALSE, warning=FALSE------
+library(knitr)
+library(kableExtra)
+library(tidyverse)
+library(patchwork)
+library(ggpubr)
+
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>",
+  out.width = "\\textwidth",
+  fig.align = "center",
+  #  cache=TRUE,
+  dpi = 144,
+  warning = FALSE,
+  message = FALSE
+)
+
+
+## ----setup-knitr, echo=FALSE------------------------------
+## From Josh O'Brien's stackoverflow answer:
+## http://stackoverflow.com/questions/11030898/knitr-how-to-align-code-and-plot-side-by-side
+## These two settings control text width in codefig vs. usual code blocks
+partWidth <- 35
+fullWidth <- 60
+options(width = fullWidth)
+
+##  (1) CHUNK HOOK FUNCTION
+##   First, to set R's textual output width on a per-chunk basis, we
+## need to define a hook function which temporarily resets global R's
+## option() settings, just for the current chunk
+knit_hooks$set(r.opts = local({
+  ropts <- NA
+  function(before, options, envir) {
+    if (before) {
+      ropts <<- options(options$r.opts)
+    } else {
+      options(ropts)
+    }
+  }
+}))
+
+## (2) OUTPUT HOOK FUNCTION
+
+##   Define a custom output hook function. This function processes _all_
+## evaluated chunks, but will return the same output as the usual one,
+## UNLESS a 'codefig' argument appeared in the chunk's header.  In that
+## case, wrap the usual textual output in LaTeX code placing it in a
+## narrower adjustbox environment and setting the graphics that it
+## produced in another box beside it.
+
+defaultChunkHook <- environment(knit_hooks[["get"]])$defaults$chunk
+
+codefigChunkHook <- function(x, options) {
+  main <- defaultChunkHook(x, options)
+  before <-
+    "\\vspace{1em}
+\\begin{adjustbox}{valign=t}
+\\begin{minipage}{.39\\textwidth}\n"
+  after <-
+    paste("\\vspace{1em}
+\\end{minipage}
[…]

### 2022-04-12 rj_format/rjarticle/ju-hofmann.R

@@ -1,0 +1,37 @@
+# Generated by `rjournal_article()` using `knitr::purl()`: do not edit by hand
+# Please edit ju-hofmann.Rmd to modify this file
+
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+library(plotly)
+library(ggplot2)
+library(palmerpenguins)
+
+
+## ----penguins-alison, out.width = "100%", out.height = "30%", fig.cap = "Artwork by \\@allison\\_horst", fig.alt="A picture of three different penguins with their species: Chinstrap, Gentoo, and Adelie. "----
+knitr::include_graphics("penguins.png")
+
+
+## ----penguins-tab-interactive, eval = knitr::is_html_output(), layout = "l-body-outset"----
+#> knitr::kable(head(penguins), format = "html", caption = "A basic table")
+
+
+## ----penguins-tab-static, eval = knitr::is_latex_output()---------------------
+knitr::kable(head(penguins), format = "latex", caption = "A basic table") %>% 
+  kableExtra::kable_styling(font_size = 7)
+
+
+## ----penguins-plotly, echo = TRUE, fig.height = 5, fig.cap="A basic interactive plot made with the plotly package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. When hovering on a point, a tooltip will show the exact value of the bill depth and length for that point, along with the species name.", include=knitr::is_html_output(), eval=knitr::is_html_output(), fig.alt = "A scatterplot of bill length against bill depth, both measured in millimetre. The three species are shown in different colours and loosely forms three clusters. Adelie has small bill length and large bill depth, Gentoo has small bill depth but large bill length, and Chinstrap has relatively large bill depth and bill length."----
+#> p <- penguins %>%
+#>   ggplot(aes(x = bill_depth_mm, y = bill_length_mm,
+#>              color = species)) +
+#>   geom_point()
+#> ggplotly(p)
+
+
+## ----penguins-ggplot, echo = TRUE, fig.height = 5, fig.cap="A basic non-interactive plot made with the ggplot2 package on palmer penguin data. Three species of penguins are plotted with bill depth on the x-axis and bill length on the y-axis. Visit the online article to access the interactive version made with the plotly package.", include=knitr::is_latex_output(), eval=knitr::is_latex_output()----
+penguins %>% 
[…]

### 2022-04-16 cover_letter/cover_letter.Rmd
ready to re-submit, check point 1, before switch to rtools
last knit, added motivation letter

@@
 title: "Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets"
-author: "Wangqian Ju and Heike Hofmann"
 date: "10/13/2021"
@@
 Wangqian Ju and Heike Hofmann  
+Department of Statistics  
+Iowa State University  
+Ames, Iowa, the United States  
+wju@iastate.edu
 
@@
 +   **data** folder: contains data to demonstrate the cmpsR package and reproduce various results in the paper. 
-+   **reproducible** folder: contains R scripts and data necessary to reproduce all aspects of this submission.
++   **supplementary-files.zip** folder: contains R scripts and data necessary to reproduce all aspects of this submission.
 +   **ju-hofmann_files/figure-latex** folder: contains figures and plots used in the paper

### 2022-04-28 rj_format/rj-format-ju-hofmann/ju-hofmann.Rmd
update rjtools format
added acknowledgement

@@
 An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
-thanks: |
-  This work was partially funded by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreement 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
 preamble: |
@@
 
+## Acknowledgement
+
+This work was funded (or partially funded) by the Center for Statistics and Applications in Forensic Evidence (CSAFE) through Cooperative Agreements 70NANB15H176 and 70NANB20H019 between NIST and Iowa State University, which includes activities carried out at Carnegie Mellon University, Duke University, University of California Irvine, University of Virginia, West Virginia University, University of Pennsylvania, Swarthmore College and University of Nebraska, Lincoln.
+
 ## Supplementary materials
@@
 -   `hamby*_result_generator.R`: these R scripts take the processed data of Hamby set 252 and Hamby set 44, generate preliminary results used in the paper, and save the results in the `.csv` format in the folder `data-csv`.
-Please make sure that the package versions of `bulletxtrctr` and `cmpsR` meet the requirements.
+Please make sure that the package versions of \pkg{bulletxtrctr} and `cmpsR` meet the requirements.
 -   `rds_generator.R`: this R script takes the generated `.csv` files and produce `CMPSpaper_results.rds`.

### 2022-04-28 rj_format/rj-format-ju-hofmann/ju-hofmann.tex
update rjtools format
added acknowledgement

@@
 
+\hypertarget{acknowledgement}{%
+\subsection{Acknowledgement}\label{acknowledgement}}
+
+This work was funded (or partially funded) by the Center for Statistics
+and Applications in Forensic Evidence (CSAFE) through Cooperative
+Agreements 70NANB15H176 and 70NANB20H019 between NIST and Iowa State
+University, which includes activities carried out at Carnegie Mellon
+University, Duke University, University of California Irvine, University
+of Virginia, West Virginia University, University of Pennsylvania,
+Swarthmore College and University of Nebraska, Lincoln.
+
 \hypertarget{supplementary-materials}{%
@@
   format in the folder \texttt{data-csv}. Please make sure that the
-  package versions of \texttt{bulletxtrctr} and \texttt{cmpsR} meet the
+  package versions of \pkg{bulletxtrctr} and \texttt{cmpsR} meet the
   requirements.

### 2022-09-29 rj_format/rj-format-ju-hofmann/ju-hofmann.Rmd
updated with mathjax

@@
 Graphing tools are implemented in the package as well for users to assess and understand the CMPS results.
-Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package \pkg{bulletxtrctr}.
+Initial tests were performed on bullet signatures generated from two sets of 3D scans in the Hamby study under the framework suggested by the R package `bulletxtrctr`.
 New metrics based on CMPS scores are introduced and compared with existing metrics.
-A measure called Sum of squares ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets.
-An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as methods comparison.
+A measure called sum of squares ratio is included, and how it can be used for evaluating different scans, metrics, or parameters is showcased with the Hamby study data sets.
+An open-source implementation of the CMPS algorithm makes the algorithm more accessible, generates reproducible results, and facilitates further studies of the algorithm such as method comparisons.
 preamble: |
@@
 output: 
-  rjtools::rjournal_web_article
+  rjtools::rjournal_web_article:
+    mathjax: local
 editor_options: 
@@
 Although @cmps conceptually describe the CMPS algorithm in their paper, the authors did not release an implementation of their method.
-Thus, our effort here is to introduce the CMPS method to the `R` [@R] community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
+Thus, our effort here is to introduce the CMPS method to the `R` community and provide an open-source, publicly available implementation of the algorithm to use, review, and improve.
 Our implementation is made available as part of the `R` package \CRANpkg{cmpsR} on CRAN.
@@
 Assessing the similarity between two bullets is based on a comparison of striation marks acquired during the firing process as bullets are propelled through the barrel.
-The current state of art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
+The current state of the art sees firearms examiners make an assessment of similarity based on a visual comparison, generally, using a comparison microscope [@afte].
 This practice has been criticized for its lack of objectivity and the associated problem of determining valid error rates [@pcast].
@@
 
-The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages \CRANpkg{x3ptools} [@x3ptools] and \pkg{bulletxtrctr} [@bulletxtrctr].
+The automated framework for extracting signatures from x3p files used in this paper was proposed by @aoas and is implemented in the `R` packages \CRANpkg{x3ptools} [@x3ptools] and `bulletxtrctr` [@bulletxtrctr].
 \pkg{x3ptools} is a package to read, write, and generally, process x3p files.
-The \pkg{bulletxtrctr} package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
+The `bulletxtrctr` package implements a pipeline for extracting and comparing signatures from scans of land-engraved areas.
 
@@
 Figure \@ref(fig:process)(a) shows a rendering of a 3D scan of a bullet land engraved area.
-The raised portion of the surface on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs), the middle area shows a land-engraved area (LEA) with well expressed striation marks.
+The raised portion of the surface on the left and right of the scan are parts of the adjacent groove engraved areas (GEAs), the middle area shows a land engraved area with well expressed striation marks.
 The first step of obtaining the bullet signature is to extract a cross-section at a fixed height on the land engraving.
@@
 The thin white horizontal line in Figure \@ref(fig:process)(a) indicates which cross-section was identified by the algorithm to represent the LEA; Figure \@ref(fig:process)(b) shows the corresponding cross-sectional view.
-Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in Figure \@ref(fig:process)(c) and Figure \@ref(fig:process)(d)).
-A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature ( Figure \@ref(fig:process)(e)) and, finally, the **bullet signature** (Figure \@ref(fig:process)(f)) is obtained as residuals of the cross-section and the fitted smooth.
-Note, that in @cmps bullet signatures are referred to as bullet profiles.
+Groove engraved areas are removed from the analysis as indicated by the vertical blue lines in Figure \@ref(fig:process)(c) and Figure \@ref(fig:process)(d).
+A non-parametric LOESS smooth [@loess] is fitted to capture the bullet curvature (Figure \@ref(fig:process)(e)) and, finally, the **bullet signature** (Figure \@ref(fig:process)(f)) is obtained as residuals of the cross-section and the fitted smooth.
+Note that in @cmps bullet signatures are referred to as bullet profiles.
 However, to avoid confusion, we distinguish the notion of bullet signatures from bullet profiles.
@@
 Identifying the groove engraved areas correctly is fundamental for a correct downstream analysis of the signatures.
-To allow for a human-in-the-middle inspection and intervention we have provided an interactive web application, implemented as `R` Shiny App [@shiny], \pkg{bulletinspectR} to identify and correct those errors.
+We have provided an interactive web application to allow for a human-in-the-middle inspection and intervention.
+It is implemented as an `R` Shiny App [@shiny] named `bulletinspectR` for identifying and correcting those errors.
 An example of the extraction process with corresponding code and parameter settings can be found in the "Supplementary materials".
@@
 Further research is needed to understand how to determine optimal threshold settings.
-The CMPS algorithm can assist firearm examiners with drawing a conclusion about the source of a comparison pair.
+The CMPS algorithm can assist firearms examiners with drawing a conclusion about the source of a comparison pair.
 Thus, in this paper we present an open-source implementation of the CMPS algorithm in the R package \pkg{cmpsR} available from both CRAN and Github.
@@
 A further example that illustrates the main points is also included.
-In the section on 'Evaluation metrics", we introduce new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.
+In the section on "Evaluation metrics", we introduce new CMPS metrics that summarize land-level CMPS scores and a sum of squares ratio that can be used to evaluate algorithmic results.
 The section "Results" presents the results of evaluating the \pkg{cmpsR} package using Hamby set 252 and Hamby set 44.
@@
 Further research is needed, until then users are advised to think of default values as starting values and consider alternatives.
-However, the evaluation framework based on the Sum of Squares Ratio introduced in the later section could be used to evaluate the choices of these parameters.
+However, the evaluation framework based on the sum of squares ratio introduced in the later section could be used to evaluate the choices of these parameters.
 The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`.
@@
 Signatures in the second row are ordered to be in phase with the signatures above, i.e.
-matching signatures are displayed on top of each other."}
+matching signatures are displayed on top of each other.
+On the x-axis is the length of the scan in millimeter, and on the y-axis is the relative height in micron."}
 signatures <- bullets %>% unnest(sigs)
@@
 More discussion and comparisons between the two versions of the CMPS algorithm will be presented in later sections.
-Note, that the multi-segment lengths method is slower because the algorithm is run once for each segment length.
+Note that the multi-segment lengths method is slower because the algorithm is run once for each segment length.
 
@@
 ```{r sigplots-web, eval=knitr::is_html_output(), echo=FALSE, fig.cap="In (a) the black line shows the comparison signature; each red line segment shows one congruent matching profile segment.
+Each grey rectangle highlights one congruent matching profile segment.
 In (b) the black line shows the reference signature; the red line shows the comparison signature.
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
+\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.
+Each grey rectangle highlights one congruent matching profile segment.}
 ```{r sigplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
@@
 Therefore the top five peaks are identified in the cross-correlation curve at level one.
-Segment 6 is plotted at the positions where these 5 peaks are identified with dashed lines in the `segment_plot`.
+Segment 6 is plotted at the positions where these five peaks are identified with dashed lines in the `segment_plot`.
 The solid thick black line shows the segment at its original position (which in this example is very close to the actual registration position).
@@
 
-```{=tex}
 \begin{align}
@@
 \end{align}
-```
 
@@
 `bullets` contains bullet signatures of two bullets, `bullet1` and `bullet2`.
-As mentioned before, each bullet has 6 land engravings, resulting in 6 bullet signatures.
+As mentioned before, each bullet has six land engravings, resulting in six bullet signatures.
 Thus, there are 36 pairwise bullet signature comparisons, resulting in 36 $c_{ij}$ values in total.
@@
 \end{align}
-```
+
 $\mathrm{\overline{CMPS}_{diff}}$ highlights the difference between CMPS scores of matching and non-matching comparisons.
@@
 \end{align}
-```
+
 The scaled CMPS scores of the above example are shown in Figure \@ref(fig:tiles2)(b).
@@
 \end{align}
-```
+
 where $\mu_k$ is the true mean of group $k$ and $e_{kl}$ is a random effect of different observations.
@@
 \end{align}
-```
+
 The numerator of the sum of squares ratio $V$ quantifies the variation between the two groups, while the denominator quantifies the variation within each group.
@@
 The sum of squares ratios are 20.64 and 28.96 for $\mathrm{CMPS_{max}}$ and $\mathrm{\overline{CMPS}_{max}}$, respectively.
-This indicates, that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.
+This indicates that even though scores from $\mathrm{CMPS_{max}}$ for known-match comparisons are larger than scores from the averaged version of $\mathrm{\overline{CMPS}_{max}}$, these scores achieve a better separation between the two groups of comparisons.
 
@@
 They also suggest that the two newly proposed metrics, $\mathrm{\overline{CMPS}_{diff}}$ and $\mathrm{\overline{CMPS^*}_{diff}}$,  lead to equally good or even better results as $\mathrm{\overline{CMPS}_{max}}$.
-Because $\mathrm{\overline{CMPS^*}_{diff}}$ relies on a scaled version of CMPS scores it is more comparable to other similarity scores and summarizes the out-of-phase background CMPS scores, making it superior to the other CMPS metrics.
+Because $\mathrm{\overline{CMPS^*}_{diff}}$ relies on a scaled version of CMPS scores, it is more comparable to other similarity scores and summarizes the out-of-phase background CMPS scores, making it superior to the other CMPS metrics.
 
@@
 In Figure \@ref(fig:param-npeak-plot), we also included the sum of squares ratios computed from the random forest scores [@aoas] for different metrics. 
-The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package \pkg{bulletxtrctr} [@bulletxtrctr].
+The random forest model presented in @aoas was trained at the Center for Statistics and Applications in Forensic Evidence (CSAFE) and is publicly available in the R package `bulletxtrctr` [@bulletxtrctr].
 Similar to the CMPS algorithm, this random forest model produces a  score to quantify the similarity of a land-by-land comparison.
@@
 -   `hamby*_result_generator.R`: these R scripts take the processed data of Hamby set 252 and Hamby set 44, generate preliminary results used in the paper, and save the results in the `.csv` format in the folder `data-csv`.
-Please make sure that the package versions of \pkg{bulletxtrctr} and `cmpsR` meet the requirements.
+Please make sure that the package versions of `bulletxtrctr` and `cmpsR` meet the requirements.
 -   `rds_generator.R`: this R script takes the generated `.csv` files and produce `CMPSpaper_results.rds`.

### 2022-09-29 rj_format/rj-format-ju-hofmann/ju-hofmann.tex
updated with mathjax

@@
 the Hamby study under the framework suggested by the R package
-\pkg{bulletxtrctr}. New metrics based on CMPS scores are introduced and
-compared with existing metrics. A measure called Sum of squares ratio is
-included, and how it can be used for evaluating different scans,
-metrics, or parameters is showcased with the Hamby study data sets. An
-open-source implementation of the CMPS algorithm makes the algorithm
-more accessible, generates reproducible results, and facilitates further
-studies of the algorithm such as methods comparison.
+\texttt{bulletxtrctr}. New metrics based on CMPS scores are introduced
+and compared with existing metrics. A measure called sum of squares
+ratio is included, and how it can be used for evaluating different
+scans, metrics, or parameters is showcased with the Hamby study data
+sets. An open-source implementation of the CMPS algorithm makes the
+algorithm more accessible, generates reproducible results, and
+facilitates further studies of the algorithm such as method comparisons.
 }
@@
 implementation of their method. Thus, our effort here is to introduce
-the CMPS method to the \texttt{R} \citep{R} community and provide an
-open-source, publicly available implementation of the algorithm to use,
-review, and improve. Our implementation is made available as part of the
-\texttt{R} package \CRANpkg{cmpsR} on CRAN.
+the CMPS method to the \texttt{R} community and provide an open-source,
+publicly available implementation of the algorithm to use, review, and
+improve. Our implementation is made available as part of the \texttt{R}
+package \CRANpkg{cmpsR} on CRAN.
 
@@
 the firing process as bullets are propelled through the barrel. The
-current state of art sees firearms examiners make an assessment of
+current state of the art sees firearms examiners make an assessment of
 similarity based on a visual comparison, generally, using a comparison
@@
 \texttt{R} packages \CRANpkg{x3ptools} \citep{x3ptools} and
-\pkg{bulletxtrctr} \citep{bulletxtrctr}. \pkg{x3ptools} is a package to
-read, write, and generally, process x3p files. The \pkg{bulletxtrctr}
-package implements a pipeline for extracting and comparing signatures
-from scans of land-engraved areas.
+\texttt{bulletxtrctr} \citep{bulletxtrctr}. \pkg{x3ptools} is a package
+to read, write, and generally, process x3p files. The
+\texttt{bulletxtrctr} package implements a pipeline for extracting and
+comparing signatures from scans of land-engraved areas.
 
@@
 portion of the surface on the left and right of the scan are parts of
-the adjacent groove engraved areas (GEAs), the middle area shows a
-land-engraved area (LEA) with well expressed striation marks. The first
-step of obtaining the bullet signature is to extract a cross-section at
-a fixed height on the land engraving.
+the adjacent groove engraved areas (GEAs), the middle area shows a land
+engraved area with well expressed striation marks. The first step of
+obtaining the bullet signature is to extract a cross-section at a fixed
+height on the land engraving.
 
@@
 by the vertical blue lines in Figure \ref{fig:process}(c) and Figure
-\ref{fig:process}(d)). A non-parametric LOESS smooth \citep{loess} is
-fitted to capture the bullet curvature ( Figure \ref{fig:process}(e))
+\ref{fig:process}(d). A non-parametric LOESS smooth \citep{loess} is
+fitted to capture the bullet curvature (Figure \ref{fig:process}(e))
 and, finally, the \textbf{bullet signature} (Figure
 \ref{fig:process}(f)) is obtained as residuals of the cross-section and
-the fitted smooth. Note, that in \citet{cmps} bullet signatures are
+the fitted smooth. Note that in \citet{cmps} bullet signatures are
 referred to as bullet profiles. However, to avoid confusion, we
@@
 correctly is fundamental for a correct downstream analysis of the
-signatures. To allow for a human-in-the-middle inspection and
-intervention we have provided an interactive web application,
-implemented as \texttt{R} Shiny App \citep{shiny}, \pkg{bulletinspectR}
-to identify and correct those errors. An example of the extraction
+signatures. We have provided an interactive web application to allow for
+a human-in-the-middle inspection and intervention. It is implemented as
+an \texttt{R} Shiny App \citep{shiny} named \texttt{bulletinspectR} for
+identifying and correcting those errors. An example of the extraction
 process with corresponding code and parameter settings can be found in
@@
 is needed to understand how to determine optimal threshold settings. The
-CMPS algorithm can assist firearm examiners with drawing a conclusion
+CMPS algorithm can assist firearms examiners with drawing a conclusion
 about the source of a comparison pair. Thus, in this paper we present an
@@
 how to use the \pkg{cmpsR} package. A further example that illustrates
-the main points is also included. In the section on 'Evaluation
+the main points is also included. In the section on ``Evaluation
 metrics'', we introduce new CMPS metrics that summarize land-level CMPS
@@
 of default values as starting values and consider alternatives. However,
-the evaluation framework based on the Sum of Squares Ratio introduced in
+the evaluation framework based on the sum of squares ratio introduced in
 the later section could be used to evaluate the choices of these
@@
 Signatures in the second row are ordered to be in phase with the signatures above, i.e.
-matching signatures are displayed on top of each other.}\label{fig:sigs}
+matching signatures are displayed on top of each other.
+On the x-axis is the length of the scan in millimeter, and on the y-axis is the relative height in micron.}\label{fig:sigs}
 \end{figure}
@@
 two versions of the CMPS algorithm will be presented in later sections.
-Note, that the multi-segment lengths method is slower because the
+Note that the multi-segment lengths method is slower because the
 algorithm is run once for each segment length.
@@
 \begin{subfigure}[t]{\textwidth}
-\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.}
+\caption{\label{fig:sigplot}The black line shows the comparison signature; each red line segment shows one congruent matching profile segment.
+Each grey rectangle highlights one congruent matching profile segment.}
 \vspace{1em}
@@
   curve at level one. Segment 6 is plotted at the positions where these
-  5 peaks are identified with dashed lines in the
+  five peaks are identified with dashed lines in the
   \texttt{segment\_plot}. The solid thick black line shows the segment
@@
 \texttt{bullet1} and \texttt{bullet2}. As mentioned before, each bullet
-has 6 land engravings, resulting in 6 bullet signatures. Thus, there are
-36 pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\)
+has six land engravings, resulting in six bullet signatures. Thus, there
+are 36 pairwise bullet signature comparisons, resulting in 36 \(c_{ij}\)
 values in total. We use multi-segment lengths strategy with default
@@
 \(\mathrm{CMPS_{max}}\) and \(\mathrm{\overline{CMPS}_{max}}\),
-respectively. This indicates, that even though scores from
+respectively. This indicates that even though scores from
 \(\mathrm{CMPS_{max}}\) for known-match comparisons are larger than
@@
 \(\mathrm{\overline{CMPS^*}_{diff}}\) relies on a scaled version of CMPS
-scores it is more comparable to other similarity scores and summarizes
+scores, it is more comparable to other similarity scores and summarizes
 the out-of-phase background CMPS scores, making it superior to the other
@@
 Evidence (CSAFE) and is publicly available in the R package
-\pkg{bulletxtrctr} \citep{bulletxtrctr}. Similar to the CMPS algorithm,
-this random forest model produces a score to quantify the similarity of
-a land-by-land comparison. The RF scores lie in an interval of {[}0,1{]}
-making them most comparable to the scaled CMPS scores. We applied the
-logic of \(\mathrm{{CMPS}_{max}}\), \(\mathrm{\overline{CMPS}_{max}}\),
-and \(\mathrm{\overline{CMPS}_{diff}}\) to the random forest scores and
+\texttt{bulletxtrctr} \citep{bulletxtrctr}. Similar to the CMPS
+algorithm, this random forest model produces a score to quantify the
+similarity of a land-by-land comparison. The RF scores lie in an
+interval of {[}0,1{]} making them most comparable to the scaled CMPS
+scores. We applied the logic of \(\mathrm{{CMPS}_{max}}\),
+\(\mathrm{\overline{CMPS}_{max}}\), and
+\(\mathrm{\overline{CMPS}_{diff}}\) to the random forest scores and
 obtained results of the random forest model for different metrics. As
@@
   format in the folder \texttt{data-csv}. Please make sure that the
-  package versions of \pkg{bulletxtrctr} and \texttt{cmpsR} meet the
+  package versions of \texttt{bulletxtrctr} and \texttt{cmpsR} meet the
   requirements.

### 2022-09-29 rj_format/rj-format-ju-hofmann/ju-hofmann.R

@@ -238,7 +238,7 @@ library(cmpsR)
 data(bullets)
 
 
-## ----sigs, echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row. Signatures in the second row are ordered to be in phase with the signatures above, i.e. matching signatures are displayed on top of each other."----
+## ----sigs, echo=FALSE, fig.cap="Signatures of all lands of bullet 1 in the top row, and of bullet 2 in the bottom row. Signatures in the second row are ordered to be in phase with the signatures above, i.e. matching signatures are displayed on top of each other. On the x-axis is the length of the scan in millimeter, and on the y-axis is the relative height in micron."----
 signatures <- bullets %>% unnest(sigs)
 signatures <- signatures %>% mutate(
   bulletland = factor(bulletland, levels = c(paste(rep(c(1, 2), each = 6), c(1:6, 2:6, 1), sep = "-")))
@@ -325,7 +325,7 @@ dframe$samesource <- with(dframe, bullet_to_land_predict(land1 = landA, land2 = 
 #> sig_plot$signature_shift_plot
 
 
-## ----sigplots-web, eval=knitr::is_html_output(), echo=FALSE, fig.cap="In (a) the black line shows the comparison signature; each red line segment shows one congruent matching profile segment. In (b) the black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.", out.width=".7\\textwidth", fig.align="center", fig.height=6----
+## ----sigplots-web, eval=knitr::is_html_output(), echo=FALSE, fig.cap="In (a) the black line shows the comparison signature; each red line segment shows one congruent matching profile segment. Each grey rectangle highlights one congruent matching profile segment. In (b) the black line shows the reference signature; the red line shows the comparison signature. Solid part shows the congruent matching profile segments, and the dashed part shows segments that do not agree with the congruent registration position.", out.width=".7\\textwidth", fig.align="center", fig.height=6----
 #> sig_plot <- cmps_signature_plot(
 #>       cmps_with_multi_scale
 #>     )
